### 2017-09-25 TF-vldb2018/sec-appendix.tex

\newpage
%\addtolength{\parskip}{0.25cm}
%\newpage

\addtolength{\parskip}{0.25cm}

\vspace{2ex}
\noindent
{\large \textbf{Appendix A: Detailed Algorithms}}
\label{sec-apd-algorithms}

\noindent
{\textbf{1. Procedure \rgraphsim (Section~\ref{subsec-teamF})}}

\vspace{-2ex}
\begin{figure}[h!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule
\vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Pattern graph $P(V_{P}, E_{P})$, ball $\ball([v, r])$.\\
{\sl Output:\/} The perfect subgraph $G_s$ of $\ball{[v,r]}$ \wrt $P$.\\
\sstab \bcc \hspace{1ex} \= \For each $u \in V_{P}$ \Do\\
\icc \>\hspace{2ex}\= $\matchs(u)$ := \{$w | w$ is in $\ball{[v, r]}$ and $l_P(u)\in l(w)$\};\\
\icc \> \While there are changes \Do\\
\icc \>\> \For each edge ($u, u'$) in $E_P$ and each node $w \in \matchs(u)$ \Do\\
\icc \>\>\hspace{2ex}\= \If there is no edge ($w, w'$) in $\ball{[v, r]}$ with $w' \in \matchs(u')$ \Then\\
\icc \>\>\>\hspace{2ex}\= $\matchs(u)$ := $\matchs(u) \setminus \{w\}$;\\
\icc \> \If there exists $|\matchs(u)|\not\in f_{P}(u)$ \Then \Return $\emptyset$;\\
\icc \> $\Reps$ := \{$(u,w) | u \in V_{P}, w \in \matchs(u)$\};\\
\icc \> Construct the perfect subgraph $G_s$ \wrt $\Reps$;\\
\icc \> \Return $G_s$;\\
}

\vspace{-5.5ex} \myhrule
}
\end{center}
\vspace{-4ex}
\caption{Procedure \rgraphsim} \label{alg-rsim}
\vspace{-2ex}
\end{figure}

As shown in Fig~\ref{alg-rsim}, given $P$ and ball $\ball{[v, r]}$,
\rgraphsim finds the perfect subgraph of $P$ and $\ball{[v, r]}$.
For each node $u$ in $V_{P}$, it first computes the set $\matchs(u)$ of candidate matches $w$ containing the label of $u$ (lines 1-2),
and then removes nodes from $\matchs(u)$ iteratively (lines 3-6).
A node $w$ is removed from $\matchs(u)$ if there is a adjacent node $u'$ of $u$,
but there exists no adjacent node $w'$ of $w$ such that $w'\in \matchs(u')$.
Finally, it checks whether the capacity bound on each node $u$ is satisfied (line 7).
If so, \rgraphsim constructs the perfect subgraph $G_s$ \wrt the maximum match relation $\Reps$ and returns it (lines 9-10).

\noindent
{\textbf{2. Algorithm \minp (Section~\ref{subsec-batch-opt})}}

\vspace{-2ex}
\begin{figure}[h!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Pattern graph $P(V_P$, $E_P)$.\\
{\sl Output:\/} A minimum equivalent pattern graph $P_m$ of $P$.\\
\sstab \bcc \hspace{1ex}\= \If $P$ is not a satisfiable pattern graph \Then \Return \bf{null}.\\
\icc \> Compute the maximum match relation $\Reps$ of $P \eps P$;\\
\icc \> Compute equivalent classes of nodes in $P$ based on $\Reps$;\\
\icc \> Create a node for each equivalent class in $P_m$;\\
\icc \> Connect different equivalent classes by necessary edges in $P_m$;\\
\icc \> Compute the intersection of capacity bounds on nodes in each\\
\>\hspace{0.5ex} equivalent class and put on the node in $P_m$;\\
\icc \> \Return $P_m$;\\
}
\vspace{-6ex}

\myhrule
}
\end{center}
\vspace{-4ex}
\caption{Algorithm \minp} \label{alg-minp}
\vspace{-2ex}
\end{figure}

As shown in Fig.~\ref{alg-minp}, given a pattern $P$, \minp returns a minimum equivalent pattern $P_m$ of $P$.
It firstly checks to see whether $P$ is satisfiable (line 1).
If so, it computes the maximum match relation $\Reps$ by treating $P$ as both pattern and data graph via graph simulation (line 2),
and then computes equivalent classes for nodes in $P$ such that $u$ and $w$ are in the same class iff both $(u, w)\in \Reps$ and $(w, u)\in \Reps$(line 3).
It constructs $P_m$ (lines 4-6) by
(a) creating a class node for $P_m$ for each equivalent class,
(b) connecting the class nodes for $P_m$ iff there exist edges in $P$ connecting two pattern nodes which belong to two equivalent classes, and
(c) computing the intersection of capacity bounds on pattern nodes in each equivalent class and put on the corresponding class node in $P_m$.
\looseness=-1

\vspace{-2ex}
\etitle{Correctness \& Complexity}. The correctness of \minp is assured by following.
(1) The maximum match relations returned by $P$ and $P_{m}$ on any data graph $G$ are always same via graph simulation.
(2) The generated capacity bound on each node in $P_{m}$ assures that, the matched nodes of $P_{m}$ in $G$ always satisfy all capacity bounds on the nodes in $P$, which are in the same equivalent class.
Till now, $P\equiv P_{m}$;
(3) For any $P'$ that $P'\equiv P_{m}$, $|P_{m}|\leq|P'|$.
Algorithm \minp is in $O(|P|^2)$ time, by the time complexity of graph simulation.

\noindent
{\textbf{3. Algorithm \kw{PFrag} (Section~\ref{subsec-framework})}}

Algorithm \kw{PFrag} works by connecting the {\em pattern fragmentation} problem to the
{\sc $(k, \nu)$-Balanced Partition} problem.
It is to divide the nodes of a graph into $k$ components such that each component is of size no more than $\nu\cdot\frac{|V|}{k}$, and the number of edges between different components is minimized.
As illustrated before, the $(k,\nu)$-balanced partition problem,
though is not approximable in general, has a number of sophisticated heuristic algorithms~\cite{AndreevR06}.

\vspace{-2ex}
\begin{figure}[h!]
\begin{center}
{\small
\begin{center}
\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} \= Pattern graph $P(V_{P},E_{P})$, integer $h$.\\
{\sl Output:\/} An $h$-fragmentation \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\} of $P$.\\
\sstab \bcc \hspace{0.5ex} \= $k$ := $h$; $\nu$ := $h$; $M_P$ := $|P|$; $M_C$ := 0;\\
\icc \> $({P}^\nu_{f1}, \ldots, {P}^\nu_{fh}, C^\nu)$ := $\kw{BalanceP}(k,\nu)$; \\
\icc \> $M^\nu_P$ := $\kw{max}\{|{P}^\nu_{f1}|, \ldots, |{P}^\nu_{fh}|\}$; $M^\nu_C$ := $|C^\nu|$;\\
\icc\> \While $\kw{max}\{M_P, M_C\} > \kw{max}\{M^\nu_P, M^\nu_C\}$ \Do\\
\icc \>\hspace{2ex}\= ${P}_{f1}$ := ${P}^\nu_{f1}$, \ldots, ${P}_{fh}$ := ${P}^\nu_{fh}$;\\
\icc \>\hspace{2ex}\= $C$ := $C^\nu$; $M_P$ := $M^\nu_P$; $M_C$ := $M^\nu_C$;\\
\icc \>\> \If $M^\nu_P \geq M^\nu_C$ \Then $\nu := \frac{\nu}{2}$ \Else $\nu := \frac{3\nu}{2}$;\\
\icc \>\> $({P}^\nu_{f1}, \ldots, {P}^\nu_{fh}, C)$ := $\kw{BalanceP}(k,\nu)$;\\
\icc \>\> $M^\nu_P$ := $\kw{max}\{|{P}^\nu_{f1}|, \ldots, |{P}^\nu_{fh}|\}$; $M^\nu_C$ := $|C^\nu|$;\\
\icc \> \Return \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\};
}
\vspace{-2.5ex} \myhrule
\end{center}
}
\end{center}
\vspace{-4ex}
\caption{Algorithm \kw{PFrag} \label{alg-pfrag}}
\vspace{-2ex}
\end{figure}

As shown in Fig.~\ref{alg-pfrag}, given $P$ and integer $h$,
\kw{PFrag} finds an $h$-fragmentation for $P$ by recursively invoking algorithm $\kw{BalanceP}(k,\nu)$ for the {\sc $(k,\nu)$-Balanced partition} problem ($\nu\geq 1$) with different $\nu$,
such that the final returned $h$-fragmentation strikes a balance between the size of each fragment ${P}_{fi}$ and the size of the cut $C$.
More specifically, \kw{PFrag} maintains $M_P$ and $M_C$ as the size of the largest fragment ${P}_{fi}$ and the size of the cut respectively.
Initially, it sets $M_P$ to $|P|$ and $M_C$ to 0 (line~1).
It then invokes \kw{BalanceP} with both $k$ and $\nu$ being $h$, \ie has no constraints on the size of fragments of $P$ (line~2).
After that, it iteratively checks whether the generated $h$-fragmentation can be improved (line~4) by adjusting $\nu$ in a {\em binary search style} (lines~4-9).
If the current size $M^\nu_P$ of the largest fragment is no smaller than the size $M^\nu_C$ of the cut,
it invokes \kw{BalanceP} with $h$ and $\frac{\nu}{2}$, or with $h$ and $\frac{3\nu}{2}$ otherwise (line~7).
It returns the $h$-fragmentation if it cannot be improved anymore (line~10).

\etitle{Correctness \& Complexity}.
The correctness is obvious as \kw{PFrag} always returns an $h$-fragmentation.
Algorithm~\kw{PFrag} runs in $O(\log h\cdot t_{\kw{BalanceP}})$, where $t_{\kw{BalanceP}}$ is the complexity of the algorithm for the {\sc $(k,\nu)$-Balanced Partition} problem. Indeed, \kw{PFrag} calls at most $\log h$ times \kw{BalanceP}, as $\nu\geq 1$.
\looseness=-1

\vspace{1ex}
\noindent
{\large \textbf{Appendix B: Detailed Proofs}}
\label{sec-apd-proofs}

\noindent
{\textbf{1. Proof of Proposition~\ref{thm-inc-grouprec-pat}}}

Incremental complexity is defined in terms of LP (locally persistent) graph algorithms \cite{Reps96}.
We also adopt the notion to prove unboundedness of graph algorithms for \dynteamF.

\vspace{-1.5ex}
The proofs below strictly follows the one in \cite{Reps96}.

\vspace{-1.5ex}
\begin{figure}[h!]
\label{fig-inc-complexity-data}
\begin{center}
\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of unit data update}
\vspace{-2ex}
\end{figure}

\etitle{(I) \dynteamF\, is unbounded for unit data update}.
%Following \cite{Reps96, FanWW13-tods},
Consider the following pattern and data graph, and unit data updates.
Let data graph $G$ consist of two chains ($a_1$, $b_1$, $c_1$, \ldots, $a_n$, $b_n$, $c_n$) and ($a_{n+1}$, $b_{n+1}$, $c_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$) where $a_i$, $b_i$ and $c_i$ have labels $A$, $B$ and $C$ respectively.
Let pattern graph be a triangle with nodes $a$, $b$ and $c$ with labels $A$, $B$ and $C$ respectively.
Consider two unit edge insertions $\delta_1$ = $(c_n$, $a_{n+1})^+$ and $\delta_2$ = $(c_{2n}$, $a_1)^+$,
and set $k = 1$ and $r$ = $6n$.
Let $H_1$ and $H_2$ denote the graphs $G\oplus \delta_1$ and $G\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(P, H_1) = L_{k}(P, H_2) = \emptyset$,
while $L_{k}(P, H_1\oplus \delta_2) \neq \emptyset$.
Assume that there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(G', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some graph $G'$.
Now consider the following two instances: the application of update $\delta_2$ to $G$ and the application of update $\delta_2$ to graph $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(G, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes of $H_1\oplus \delta_2$ are affected, while no node in $G\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage, this can happen only both $Trace(G, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in the graphs $G$ and $H_1$.
However, $H_1$ was obtained from $G$ by applying update $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $G$.
Therefore, $Trace(G, \delta_1)$ must also contain a visit to node $w$.
As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying change $\delta'$ to graph $G'$,
then every node on some path in $G'$ from a modified node of $\delta'$ to $w$ must have been visited.
Therefore, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ include visits to every node on the path from $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$ respectively.
Hence, the time taken for processing update $\delta_1$ to $G$ plus the time taken for processing update $\delta_2$ to $G$ must be no smaller than the distance between $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$, \ie $n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of the incremental algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.

\vspace{-1.5ex}
That is, \dynteamF\, is unbounded even for $k=1$ and unit data update.
\looseness=-1

\vspace{-1ex}
\begin{figure}[h!]
\label{fig-inc-complexity-pattern}
\begin{center}
\includegraphics[scale=0.31]{./fig/inc-complexity-proof-pattern.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of unit pattern update}
\vspace{-1.5ex}
\end{figure}

\vspace{-1ex}
\etitle{(II) \dynteamF\, is unbounded for unit pattern update}.
Consider the following pattern and data graph, and unit pattern updates.
Let data graph $G$ be a cycle ($a'_1$, $b'_1$, $c'_1$, $d'_1$, \ldots, $a'_m$, $b'_m$, $c'_m$, $d'_m$, $a'_1$),
where $a'_i$, $b'_i$, $c'_i$ and $d'_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Let pattern graph be a cycle ($a_1$, $b_1$, $c_1$, $d_1$, \ldots, $a_n$, $b_n$, $c_n$, $d_n$, $a_{n+1}$, $b_{n+1}$, $c_{n+1}$, $d_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$, $d_{2n}$, $a_1$) and two extra edges ($a_1$, $c_1$) and ($b_{n+1}$, $d_{n+1}$),
where $a_i$, $b_i$, $c_i$ and $d_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Consider two unit edge deletions $\delta_1$ = $(a_1$, $c_1)^-$ and $\delta_2$ = $(b_{n+1}$, $d_{n+1})^-$,
and set $k = 1$ and $r$ = $4m$.
Let $H_1$ and $H_2$ denote the graphs $P\oplus \delta_1$ and $P\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(H_1, G) = L_{k}(H_2, G) = \emptyset$,
while $L_{k}(H_1\oplus \delta_2, G) \neq \emptyset$.
Assume there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(P', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some pattern $P'$.
Now consider two instances: the application of update $\delta_2$ to $P$ and the application of update $\delta_2$ to $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(P, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes in $G$ for $H_1\oplus \delta_2$ are affected, while no node in $G$ for $P\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage,
this can happen only both $Trace(P, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in $P$ and $H_1$.
However, $H_1$ was obtained from $P$ by applying $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $P$.
Therefore, $Trace(P, \delta_1)$ must also contain a visit to node $w$.
%As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying update $\delta'$ to pattern $P'$,
%then every node in some path in $P'$ from a modified node of $\delta'$ to $w$ must have been visited.
According to the characteristics of locally persistent algorithms as illustrated in the data updates case,
$Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ include visits to every node on the path from $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$ respectively.
Hence, the time taken for processing $\delta_1$ to $P$ plus the time taken for processing $\delta_2$ to $P$ must be no smaller than the distance between $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$, \ie $4n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.
That is, \dynteamF\, is unbounded even for $k=1$ and unit pattern update.

\vspace{-1.5ex}
(1) and (2) together prove that \dynteamF\, is unbounded even for $k=1$ and unit pattern or data update.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\begin{widepage}
\vspace{-2ex}
\begin{center}
%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter}
\includegraphics[scale=0.37]{./fig/youtube-semantic-diameter.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-density}
\includegraphics[scale=0.37]{./fig/youtube-semantic-density.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity}
\includegraphics[scale=0.37]{./fig/youtube-semantic-capacity.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-link}
\includegraphics[scale=0.37]{./fig/youtube-semantic-link.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter-varyk}
\includegraphics[scale=0.37]{./fig/youtube-semantic-diameter-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-density-varyk}
\includegraphics[scale=0.37]{./fig/youtube-semantic-density-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity-varyk}
\includegraphics[scale=0.37]{./fig/youtube-semantic-capacity-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-link-varyk}
\includegraphics[scale=0.37]{./fig/youtube-semantic-link-varyk.eps}}
\vspace{-2.0ex}

\end{center}
\vspace{-2.0ex}
\caption{Performance evaluation of \optgrouprec for top-$k$ team formation problem}
\label{exp-semantic-effectiveness-youtube}
%\end{widepage}
%\vspace{-0.5ex}
\end{figure*}

\begin{figure*}[tb!]
%\begin{widepage}
\vspace{-1.5ex}
\begin{center}
%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-deletion.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-insertion.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-capchange.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)}]{\label{fig-exp-patinc-hyb-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-hybrid.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (deletions)}]{\label{fig-exp-datainc-del-youtube}
\includegraphics[scale=0.395]{./fig/youtube-data-deletion.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (insertions)}]{\label{fig-exp-datainc-ins-youtube}
\includegraphics[scale=0.395]{./fig/youtube-data-insertion.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (hybrid updates)}]{\label{fig-exp-datainc-hyb-youtube}
\includegraphics[scale=0.395]{./fig/youtube-data-hybrid.eps}}
\hspace{-1.7ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ (simultaneous)}\hspace{-4.5ex}]{\label{fig-exp-hyb-patdata-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-data.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-multi.eps}}
%\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi-youtube}
\includegraphics[scale=0.395]{./fig/youtube-data-multi.eps}}
%\hspace{-1.7ex}
\subfigure[{\scriptsize Varying $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-5.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
\includegraphics[scale=0.395]{./fig/youtube-pattern-data-multi.eps}}
%\hfill
\vspace{-2.5ex}

\end{center}
\vspace{-2.0ex}
\caption{Performance evaluation of \inc for dynamic top-$k$ team formation problem (\youtube)}
\label{exp-inc-youtube}
%\end{widepage}
\vspace{-4ex}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
{\textbf{2. Proof of Proposition~\ref{prop-fragmentation}}}

The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
is to decide whether there exists a fragmentation \{${P}_{f1}$, \ldots, $P_{fh}$, $C$\} such that,
(a) $\max_i |P_{fi}| \leq r_1\cdot\frac{|P|}{h}$ and (b) $|C|\leq r_2|P|$.

\vspace{-2ex}
\etitle{Upper bound.} We show the \NP upper bound by providing an \NP algorithm to determine whether there exists an $h$-fragmentation of $P$.\,Given $P$, the algorithm works as follows.
\looseness=-1

\vspace{-1.8ex}
\sstab{(1)} Guess an $h$-fragmentation ${\cal P}_h$ of $P$.

\vspace{-1.8ex}
\sstab{(2)} Check whether it satisfies restrictions of $r_1$ and $r_2$ (conditions (a) and (b) in the definition of $\kw{dOFGP}$).
If so, return yes, otherwise go to the first step and guess another instance.

\vspace{-1.5ex}
The algorithm is in \NP since step~(2) can be checked in \PTIME (liner time, indeed).

\vspace{-2.5ex}
\etitle{Lower bound.}
We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.

\vspace{-2ex}
An instance of the minimum cut problem is given an undirected graph $H=(V_{H},E_{H})$ and a positive integer $m$,
to find a set $S \subseteq E_{H}$ of edges whose removal leaves two disjoint connected components, with $|S|\leq m$.

\vspace{-2ex}
Given an instance of the minimum cut problem,
we construct an instance of $h$-fragmentation problem.
It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.

\noindent
{\textbf{3. Proof of Theorem~\ref{thm-compose}}}

We will prove the theorem by induction.
Given pattern $P(V_P,E_P)$ and its fragmentation \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\},
we use $P^{C}(V_{P^{C}},E_{P^{C}})$ to denote the pattern with $V_{P^{C}}$=$V_P$ and $E_{P^{C}}$=$E_P/C$.
%we use $P^{C}(V_P,E_P/C)$ to denote the pattern with the same node set $V_P$ with $P$, and edges excluding the cut $C$ from $E_P$.
Graph simulation is an iterative process to remove unmatched nodes from the candidate nodes,
as illustrated in Fig.~\ref{alg-rsim} (lines~1-6).
We utilize $M_{C}^{k}$ (resp. $M_{i}^{k}$, $M^{k}$) to denote the match relation for $P^{C}$ (resp. $P_{fi}$, $P$) in $\ball{}$ in the $kth$ iteration.
By the definition of graph simulation, we have $M_{C}^{k}$ = $\bigcup_{i=1}^{h}M_{i}^{k}$.
To prove $M\subseteq\bigcup_{i=1}^{h}M_{i}$,
we next prove $M^{k}\subseteq M_{C}^{k}$ for each iteration instead.

\vspace{-1.8ex}
\sstab{(1)} For $k=0$, \ie the initialization step of graph simulation algorithm,
the algorithm computes the set of candidate matches for each pattern node with the same label.
As $P$ and $P^{C}$ have exactly the same node set, we have $M^{0}= M_{C}^{0}$.

\vspace{-1.8ex}
\sstab{(2)} For $k=n$ $(n\geq 0)$, if $M^{n}\subseteq M_{C}^{n}$ exists, we prove $M^{n+1}\subseteq M_{C}^{n+1}$ exists in the $(n+1)th$ iteration.
Suppose both $(u,w)\in M^{n}$ and $(u,w)\in M_{C}^{n}$ exist,
and in the $(n+1)th$ iteration, $(u,w)$ is removed from $M_{C}^{n}$ if there is a adjacent node $u'$ of $u$ in $P_{C}$,
but there exists no adjacent node $w'$ of $w$ in $G$ such that $(u',w')\in M_{C}^{n}$.
Therefore, $(u,w)$ must be removed from $M^{n}$ as $E_{P^{C}} \subseteq E_{P}$,
that is, the edge $(u,u')$ in $E_{P^{C}}$ must belong to $E_{P}$.
Thus, we have $M^{n+1}\subseteq M_{C}^{n+1}$.

\vspace{-1.5ex}
By (1) and (2), we have proven that $M\subseteq\bigcup_{i=1}^{h}M_{i}$.

\vspace{1ex}
\noindent
{\large \textbf{Appendix C: Extra Experiments}}
\label{sec-apd-exp}

\vspace{-0.5ex}
The experimental results on a real-life dataset \youtube are reported here.

{\em \youtube}~\cite{youtubeWeb} contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos. We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.

\vspace{-1.8ex}
\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis, \denalk on \youtube \wrt three measurements.
The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.
We find \optgrouprec strikes a balance at capturing the practical requirements.

\vspace{-1.8ex}
\stitle{Exp-2: Efficiency of \inc for one set of updates}. Varying the amount of updates in one update set from 4.5\% to 45\% for pattern updates, 2.5\% to 25\% for data updates, and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
We find \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 31.5\%, 20\% and (27\%, 15\%).
%for hybrid pattern, hybrid data, and simultaneous pattern and data updates.

\vspace{-1.8ex}
\stitle{Exp-3: Efficiency of \inc for continuous sets of updates}. We generated 5 sets of updates,
varying the amount of updates from 4.5\% to 27\% for pattern updates, 2.5\% to 15\% for data updates,
and (4.5\%, 2.5\%) to (22.5\%, 12.5\%) for simultaneous pattern and data updates.
We evaluated the average time took by \inc to process these sets of updates one by one.
The results are reported in Fig.~\ref{fig-exp-patinc-multi-youtube} to~\ref{fig-exp-hyb-datapat-multi-youtube}.
We find \inc outperforms \optgrouprec when changes are no more than 27\%, 10\% and (13.5\%, 7.5\%) for continuous pattern, data and simultaneous updates respectively.

\vspace{-1.8ex}
\stitle{Exp-4: Physical storage of auxiliary structures}. It takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which need 114MB space to store itself,
\ie 50.8\% compared with the original dataset.

### 2017-09-25 TF-vldb2018/sec-appendix_pre.tex

%\newcommand{\EQ}{\kw{EQ}}

\addtolength{\parskip}{0.25cm}
\newpage
\section*{{\Large \sf APPENDIX A: Proofs}}
\label{sec-app-proofs}

\subsection*{Proof of Theorem~\ref{thm-esim-complexity}}

We will next show  \uppercase\expandafter{\romannumeral 1}) the problem is \NP-complete in general case, and the special cases when $P$ expresses only `at most' and `exactly' semantics. Then we will show that  \uppercase\expandafter{\romannumeral 2}) the problem is in \PTIME when $P$ expresses only `at least' semantic.

\stab
\uppercase\expandafter{\romannumeral 1}). Our routine to show \uppercase\expandafter{\romannumeral 1}) is firstly prove that in general case, the problem is in \NP, and then show that when $f_p(u)$ is restricted to $[1,1]$ for each $u \in V_p$, the problem in the general case and two special cases with `at most' and exactly' semantic are \NP-hard. As this special condition is contained in the three cases, such that the problem in these three cases are \NP-hard.

\etitle{Upper bound}.
We show the \NP upper bound by providing an \NP algorithm to determine whether $P \eeps G$ in
general case. Given a pattern graph $P$, a data graph $G$, the algorithm works as follows.
\be
\item Guess a subgraph $G_s(V_s,E_s)$ of $G$;
\item Check whether the following conditions hold:
\bi
\item [(a)] whether $G_s$ is a matched subgraph of $P$ in $G$ via graph simulation (with match relation $\Reps_D$);
\item [(b)] whether for each query node $u\in V_p$, the number of nodes $v\in V_s$ with $(u, v)\in \Reps_D$ falls into $f_p(u)$.
\ei
If yes, return `Yes', otherwise return to Step~1.
\ee

Note that the algorithm correctly determines whether $P \eeps G$. Moreover, the algorithm is in \NP since step~2 can be checked in \PTIME (quadratic time, indeed).

\etitle{Lower bound}.
We next show that it is \NP-hard to determine whether $P \eeps G$ even when $f_p(u)=[1,1]$ for each $u \in V_p$, by reduction from the 3\SAT\ problem, which is known \NP-complete~\cite{}.

An instance of the 3\SAT\ problem is given a collection $W=\{c_1,c_2,\cdots,c_m\}$ of clauses on a finite set of variables $U=\{x_1,x_2,\cdots,x_n\}$, such that $|c_j|=3$ for $1 \leq j \leq m$, and $c_j$ is of the form $\ell_1^j\vee \ell_2^j\vee \ell_3^j$, and $\ell_j^r$ is either
$x_i$ or $\overline{x_i}$, for $i\in [1, n]$ and $r\in [1, 3]$. The problem is to determine whether there exists a truth assignment for $U$ that satisfies all the clauses in $C$.

Given an instance $W$ and $U$ of the 3\SAT\ problem, we construct an instance of extended graph simulation problem, that is, a pattern graph $P(V_p$, $E_p$, $l_p$, $f_p)$, a data graph $G(V$, $E$, $l$, $w)$, such that all the clauses in $W$ are satisfiable if and only if $P \eeps G$.

\stab
1. We define $G(V$, $E$, $l$, $w)$ as follows:
\be
\item [(1)]$V$ consists of $m+2nm$ nodes, $C_1$, $C_2$, $\ldots$, $C_m$, $X_1^1$, $X_1^2$, $\ldots$, $X_1^m$, $\overline{X_1^1}$, $\overline{X_1^2}$, $\ldots$, $\overline{X_1^m}$, $\ldots$, $X_n^1$, $X_n^2$, $\ldots$, $X_n^m$, $\overline{X_n^1}$, $\overline{X_n^2}$, $\ldots$, $\overline{X_n^m}$, where $C_j$ corresponds to the clause $c_j$ in $W$ of 3\SAT problem, $X_i^1$, $X_i^2$, $\ldots$, $X_i^m$ and $\overline{X_i^1}$, $\overline{X_i^2}$, $\ldots$, $\overline{X_i^m}$ correspond to the literals $x_i$ and $\overline{x_i}$ in 3\SAT\ problem respectively.
\item [(2)]$E = E_1 \cup E_2$
\be
\item [(a)]$E_1$ consists of edges as follows: for each clause $c_j$ composed of $\ell_1^j\vee \ell_2^j\vee \ell_3^j$ where $\ell_s^j$ ($s\in [1,3], j\in [1, m]$) is a literal that is either $x_i$ or $\overline{x_i}$ ($i\in [1, n]$) for some variable $x_i$, there exists $3m$ edges in $G$, $(C_j, \kw{p}((\ell_1^j)^1))$, \ldots, $(C_j, \kw{p}((\ell_1^j))^m)$, $(C_j, \kw{p}((\ell_2^j)^1))$, \ldots, $(C_j, \kw{p}((\ell_2^j)^m))$, $(C_j, \kw{p}((\ell_3^j)^1))$, \ldots, $(C_j,
    \kw{p}((\ell_3^j)^m))$, where $\kw{p}((\ell_s^j))^t) = X_i^t$ if $\ell_s^j = x_i$ and $\kw{p}((\ell_k^j))^t) = \overline{X_i^t}$ if $\ell_k^j = \overline{x_i}$ ($t\in[1,m]$).
\item [(b)]$E_2$ consists of edges as follows: suppose $E_3$ consists of edges that connect any two nodes among the set of $2nm$ nodes $\{X_i^p|\forall i \in [1,n], p \in [1,m]\}$, \ie $\{(X_i^p, X_j^q)| \forall i,j \in [1,n], p,q \in [1,m]\}$; $E_4$ consists of the edges as $\{(X_i^p, \overline{X_i^q})| \forall i \in [1,n], p,q \in [1,m]\}$. Then we get $E_2=E_3/E_4$.
\ee
\item [(3)]$l$: labeling function is defined as follows:
\be
\item [(a)]$l(C_j)$=`$C_j$', for any $j \in [1,m]$;
\item [(b)]$l(X_i^j)$=`X', $l(\overline{X_i^j})$=`X', for any $i \in [1,n]$ and $j \in [1,m]$;
\ee
\item [(4)]$w$: weighting function is defined as $w(e)=1$, for any $e \in E$.
\ee

%%%%%%%%%%%%%%%%%%%%%%%%%%% Theorem 3
\begin{figure}[tb!]
\begin{center}
\includegraphics[scale=0.5]{./fig/complexity_egs.eps}
\caption{Data graph $G$ and pattern graph $P$ for the proof of
  Theorem~\ref{thm-esim-complexity}}
\label{fig-esim-complexity}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Intuitively, $G$ is to encode clauses $c_j$($j \in [1,m]$) and all truth assignments to variables $x_i$($i\in[1,n])$of 3\SAT\ problem. More specifically, (a) we encode clauses $c_j$ in terms of nodes $C_j$ and those edges connecting $C_j$ to $X_i^j$ in
$G$; (b) we use subgraphs of $G$ to encode truth assignments to variables $x_i$: a variable $x_i$ is set to true when a subgraph contains a node $X_i^{k_1}$ for some $k_1$ in $[1, m]$, and for any $k\in[1,m]$, $\overline{X_i^k}$ is not in the subgraph, and vice versa.

Observe the following.
(1) A subgraph $G_s$ is able to encode a truth assignment only when
node $X_i^{k_1}$ and $\overline{X_i^{k_2}}$ does not co-exist in
$G_s$, for any $i\in[1,n]$ and $k_1, k_2\in[1, m]$. We call this
kind of subgraphs {\em valid} subgraphs, if they also contain nodes
$C_1$, \ldots, $C_m$.
(2) A valid subgraph $G_s$ may correspond to multiple truth assignments
when there exist some $i\in [1,n]$ such that for any
$k_1,k_2\in[1,m]$, all $X_i^{k_1}$ and $\overline{X_i^{k_2}}$ nodes
are not in $G_s$. In this case, $G_s$ does not encode a truth
assignment for variable $x_i$. Obviously, a subgraph $G_s$ uniquely
determines a complete truth assignment, \ie determines the truth
values of all variables $x_i$, when it is a
valid subgraph and for each $i\in[1, n]$, there exists $k\in[1,
m]$ such that either $X_i^k$ or $\overline{X_i^k}$ is in $G_s$. We
call $G_s$ a {\em complete valid} subgraph of $G$. Note that we can
get at least one complete valid subgraph $G_s'$ of $G$ by expanding an
incomplete valid subgraph $G_s$ while ensuring it is always valid, without
changing the truth assignment to those variables $x_i$ that is already
encoded by $G_s$.
(3) Every truth assignment corresponds to a complete valid subgraph.
(4) The truth assignment $\mu_{G_S}$ encoded by a complete valid
subgraph $G_s$ evaluate clause $C_j$ in 3\SAT\ problem to true if and only
if there exists an edge connecting node $C_j$ and some node with
label `X', \ie some node $X_i^k$ or $\overline{X_i^k}$, for some
$i\in[1,n], k\in[1,m]$.

\stab
2. We define $P(V_p$, $E_p$, $l_p$, $f_p)$ as follows:
\be
\item [(1)]$V_p$ consists of $2m$ nodes, $C_1'$, $C_2'$, $\ldots$, $C_m'$, $X_1'$, $X_2'$, $\ldots$, $X_m'$.
\item [(2)]$E_p = E_{p1} \cup E_{p2}$, where $E_{p1}$ consists of the edges connecting each $C_j'$ to $X_j'$, for each $j \in [1,m]$; $E_{p2}$ consists of edges $\{(X_i',X_j')| \forall i,j \in [1,m]\}$, \ie graph(\{$X_1'$,$X_2'$,$\ldots$,$X_m'$\}, $E_{p2}$) is a complete graph.
\item [(3)]$l_p$: labeling function is defined as follows:
\be
\item [(a)]$l_p(C_j')$=`$C_j$', for any $j \in [1,m]$;
\item [(b)]$l(X_j')$=`X', $l(\overline{X_j'})$=`X', for any $j \in [1,m]$;
\ee
\item [(4)]$f_p$: $f_p(u)=[1,1]$, for any $u \in V_p$.
\ee

Intuitively, if $P$ matches $G$ via node bounded simulation. Then it must be (1) $C_j'$ in $P$ matches $C_j$ in $G$, for each $j \in [1,m]$; and (2) $X_j'$ in $P$ matches  $X_i^k$ or $\overline{X_i^k}$ in $G$ for each $j \in [1,m]$, any $i \in [1,n]$, $k \in [1,m]$.

Note that if $P \eeps G$ with match relation $\Reps_s$, $G_s$ is the matched subgraph of $G$ \wrt $\Reps_s$. From the analysis above we know that $G_s$ must be a valid subgraph and for any $i\in[1,n]$ and $k_1, k_2\in[1,m]$, nodes $X_i^{k_1}$ and $\overline{X_i^{k_2}}$ cannot be in $G_{\Reps_s}$ simultaneously since nodes $X_i'$ in $P$ form into a complete graph.

We are now ready to show that $P \eeps G$ if and only if there exists a truth assignment $\mu_X$ to variables $x_i(i\in[1,n])$ such that all the clauses in $W$ are satisfiable.

\stab
$\Rightarrow$
Suppose $P$ matches $G$ via extended graph simulation with match relation $\Reps_s$. As shown above, the match subgraph $G_s$ must be a valid subgraph of $G$. Note there exists an edge connecting each node $C_j$ with a node with label `X' ($\forall j\in [1,m]$), thus the truth assignment $\mu_{G_s}$ encoded by the valid subgraph $G_s$ evaluate clause $C_j$ in 3\SAT\ problem to true. Thus there exists a truth assignment $\mu_{G_{cs}}$ that is encoded by an expanded complete valid subgraph $G_{cs}$ of $G_s$ in $G$ such that all the clauses in $W$ are satisfiable.

\stab
$\Leftarrow$
Assume that there exists a truth assignment $\mu_X$ such that all the clauses in $W$ are satisfiable. Then there exists a corresponding complete valid subgraph $G_{cs}$ of
$G$ that encodes $\mu_X$, and moreover, each node $C_j$ ($1 \leq i \leq m$) is connected to some nodes with label `X' in $G_{cs}$. According to the definition of 3\SAT\ problem, each clause $c_j$ is of the form $\ell_1^j\vee \ell_2^j\vee \ell_3^j$, such that there must exists at least one literal $\ell_k^j$ ($k \in [1,3]$) with value be true ensuring clause $c_j$ is true. Thus there exists a subgraph $G_s$ of $G_{cs}$ that (1) each node $C_j$ in $G_s$ is connected to only one node with label `X'; and (2) each node label with `X' is connected to only one node $C_j$ in $G_s$; (3) as for any $i\in[1,n]$ and $k_1, k_2\in[1,m]$, nodes $X_i^{k_1}$ and $\overline{X_i^{k_2}}$ cannot be in $G_{\Reps_s}$ simultaneously, thus all the nodes with label `X' form a complete graph. Therefore, $P\eeps G_s$, and by the definition of extended graph simulation(graph simulation), thus $P\eeps G$.

%%%%%%%%%%%%%At-least-ptime-algorithm%%%%%%%%%%%
\stab
\uppercase\expandafter{\romannumeral 2}). We next provide a \PTIME algorithm that determines whether $P \eeps G$ with `at least' semantic. Given a pattern graph $P$, a data graph $G$, the algorithm works as follows.
\be
\item Compute the maximum match relation $\Reps$ of $P$ and $G$ via graph simulation.
\item For each $u \in V_p$, $f_p(u)=[x_u,|V_p|]$  if $|\Reps(u)| < x_u$, return `No'.
\item Return `Yes' after checking all the nodes in $P$.
\ee

Note that the algorithm correctly determines whether $P \eeps G$ with `at least' semantic in quadratic time.

\subsection*{Proof of Theorem~\ref{thm-esim-den-opt-complexity}}

The problem in general case and special cases with `exactly' and `at most' semantic are \NP-hard, as their corresponding extended graph simulation decision problems are \NP-hard.
We next show the problem in special case with `at least' semantic is \NP-hard.

We first show the problem is in \NP and then show it is \NP-hard.\\
\etitle{Upper bound}.
We show the \NP upper bound by providing an \NP algorithm. Given a pattern graph $P$,
a data graph $G$, and a positive rational number $\xi$, the algorithm works as follows.
\be
\item Guess a subgraph $G_s$ of $G$;
\item Check whether the following conditions hold:
\bi
\item [(a)] whether $G_s$ is a matched subgraph of $P$ in $G$ via graph simulation (with match relation $R_D$);
\item [(b)] whether for each query node $u\in V_p$, the number of nodes $v\in V_s$ with $(u, v)\in \Reps_D$ falls into $f_p(u)$.
\item [(c)] whether the density $\eta_{G_s}$ is no less than $\xi$.
\ei
If yes, return `Yes', otherwise return to Step~1.
\ee

Note that the algorithm correctly determines whether there exists a matched subgraph of $P$ in $G$ and the density of the matched subgraph is no less than $\xi$. Moreover, the algorithm is in \NP since step~2 can be checked in \PTIME (quadratic time, indeed).

\etitle{Lower bound}.
We next show the problem is \NP-hard by reduction from the $k$-clique problem, which is known \NP-complete~\cite{}.

An instance of $k$-clique is given a undirected graph $G_c(V_c,E_c)$ and an integer $k \leq |V_c|$, and is to determine whether there exists a $k$-clique in $G_c$. Given an instance $G_c$ and $k$ of the $k$-clique problem, we construct an instance of densest extended graph simulation with `at least' semantic problem, that is, a pattern graph $P(V_p$, $E_p$, $l_p$, $f_p)$, a data graph $G(V$, $E$, $l$, $w)$, and a positive rational number $\xi$, such that there exists a $k$-clique in $G_c$ if and only if $P \eeps_{den} G$ with `at least' semantic \wrt $\xi$.
\be
\item We define $P(V_p$, $E_p$, $l_p$, $f_p)$ as follows:
\bi
\item [(1)] $V_q = \{u_1,u_2,u_3,u_4,u_5\}$, where the labels $l_p(u_1)$ and $l_p(u_2)$ of nodes $u_1$ and $u_2$ are `A', the label $l_p(u_3)$ of node $u_3$ is `B', the labels $l_p(u_4)$ and $l_p(u_5)$ of nodes $u_4$ and $u_5$ are `C'.
\item [(2)] $E_q = \{(u_1, u_2), (u_1, u_3), (u_2, u_3), (u_3, u_4), (u_3, u_5), (u_4, u_5)\}$.
\item [(3)] We already know that for each node $u$ in $V_q$, $f_p$ is assigned to be $[x_u, |V_q|]$. Then we set $x_{u_1}, x_{u_2},x_{u_3},x_{u_4}$ and $x_{u_5}$ of nodes $u_1, u_2, u_3, u_4$ and $u_5$ to be $n_1, n_1, 1, k$ and $k$, respectively.
\ei
\item We define $G(V$, $E$, $l$, $w)$ as follows:
\bi
\item [(1)] $V = V_1 \cup \{v_0\} \cup V_2$ where
\bi
\item [(a)] $V_1$ consists of $n_1$ nodes, all with label `A';
\item [(b)] the label $l(v_0)$ of $v_0$ is `B';
\item [(c)] $V_2$ consists of $n_2=|V_c|$ nodes (where $V_c$ is the set of nodes in the instance of the $k$-clique problem), all with label `C', and $n_2\leq\sqrt{2n_1^2+2n_1}-n_1-1$.
\ei
\item [(2)] $E = E_1 \cup E_{v_0} \cup E_2$ where
\bi
\item [(a)] $E_1$ consists of $\frac{n_1(n_1-1)}{2}$ edges with nodes in $V_1$, $E_1=\{(v,v')|v,v'\in V_1\}$, namely, $(V_1,E_1)$ is a complete graph with $n_1$ nodes labeled with `A';
\item [(b)] $E_{v_0}=\{(v_0,v_1)|v_1\in V_1\}\cup\{(v_0,v_2)|v_2\in V_2\}$, that is, a set of $n_1+n_2$ edges that connect $v_0$ with all nodes in $V_1$ and $V_2$.
\item [(c)] $E_2$ is derived according to $E_c$ of $G_c$. More specifically, $V_2$ consists of $n_2=|V_c|$ nodes, for each $(v_1, v_2)\in E_c$, there exists an edges $(v_1, v_2)$ in $E$.
\item [(d)] the weight of each edge in $E$ is set to 1.
\ei
\item [(3)] We set $\xi=\frac{n_1^2+n_1+k^2+k}{2(n_1+k+1)}$.
\ei
\ee

We next show that $G_c$ has a k-clique if and only if $P \eeps_{den} G$ with `at least' semantic \wrt $\xi$.

\stab
{$\Rightarrow$}
Assume $G_c$ has a k-clique with a set $V_c^* \subseteq V_c$ of $k$ nodes. We will show that the subgraph $G_s(V_s=V_1\cup\{v_0\}\cup V^*, E_s=E_1\cup E_{v_0}\cup E^*)$ of $G$ matches $P$ via densest extended graph simulation with `at least' semantic, where $V^*$ corresponds to $V_c^*$, consisting $k$ nodes in $V_2$, and $E^*$ consists of $\frac{k(k-1)}{2}$ edges connecting each pair of nodes in $V^*$.Obviously, $G_s$ matches $P$ via extended graph simulation; and then, the density $\eta_{G_s}=\frac{n_1^2+n_1+k^2+k}{2(n_1+k+1)}$, is no less than $\xi$ (equal to, indeed).

\stab
{$\Leftarrow$}
Suppose there exists a subgraph $G_s(V_s,E_s)$ that matches $P$ via densest extended graph simulation with `at least' semantic. Obviously $V_s=V_1\cup\{v_0\}\cup V^*$ and $E_s=E_1\cup E_{v_0}\cup E^*$, where $E^*=\{(v,v')|v,v'\in V^*\}$. Due to the symmetrical structural character of pattern graph $P$, for any node $v \in V_{G_s}$, and $v \in mat(u_4)$, $v$ must be contained in $mat(u_5)$, where node $u_4$ and $u_5$ are mentioned in the definition for $P$, and vice versa. Thus $V^*$ contains at least $k$ nodes in $V_2$, and the density $\eta_{G_s}$ is no less than $\frac{n_1^2+n_1+k^2+k}{2(n_1+k+1)}$. We next show that $(V^*,E^*)$ must be a $k$-clique, namely, there exists a $k$-clique in $G_c$.
Let $|V^*|=n^*$ and $|E^*|=m^*$. Then $k \leq n^* \leq n_2$ and $k-1 \leq m^* \leq \frac{n^*(n^*-1)}{2}$. We can find the density of $G_s$ is

\[\begin{split}
\eta_{G_s} =
\frac{\frac{n_1(n_1-1)}{2}+n_1+n^*+m^*}{n_1+n^*+1} \leq \frac{\frac{n_1(n_1-1)}{2}+n_1+ n^* +
  \frac{n^*(n^*-1)}{2}}{n_1+n^*+1}\\
  \leq \frac{\frac{n_1(n_1-1)}{2} + n_1 + k + \frac{k(k-1)}{2}}{n_1 + k + 1} = \xi
\end{split}\]

Note that:
\be
\item the first inequality follows from the fact that the density is larger when $(V^*,E^*)$ constitutes a complete subgraph of $(V_2,E_2)$ with $n^*$ nodes;
\item the second inequality holds when $k \leq n^* \leq n_2 \leq \sqrt{2n_1^2+2n_1}-n_1-1$, $\eta_{G_s}$ decreases when $n^*$ increases, and the equality holds when $n^*=k$.
\ee
Apparently, when there exists such a subgraph $G_s$ that matches $P$ \wrt $\xi$, we have that $(V^*,E^*)$ of $G_s$ must be a $k$-clique. Thus we can easily find that there exists a corresponding $k$-clique in $G_c$.

\subsection*{Proof of Theorem~\ref{thm-esim-dia-opt-complexity}}

The problem in general case and special cases with `exactly' and `at most' semantic are \NP-hard, as their corresponding extended graph simulation decision problems are \NP-hard.
We next show the problem in special case with `at least' semantic is \NP-hard.

We first show the problem is in \NP and then show it is \NP-hard.\\
\etitle{Upper bound}.
We show the \NP upper bound by providing an \NP algorithm. Given a pattern graph $P$,
a data graph $G$, and a positive rational number $\varphi$, the algorithm works as follows.
\be
\item Guess a subgraph $G_s$ of $G$;
\item Check whether the following conditions hold:
\bi
\item [(a)] whether $G_s$ is a matched subgraph of $P$ in $G$ via graph simulation (with match relation $R_D$);
\item [(b)] whether for each query node $u\in V_p$, the number of nodes $v\in V_s$ with $(u, v)\in \Reps_D$ falls into $f_p(u)$.
\item [(c)] whether the diameter $dia_{G_s}$ is no more than $\varphi$.
\ei
If yes, return `Yes', otherwise return to Step~1.
\ee

Note that the algorithm correctly determines whether there exists a matched subgraph of $P$ in $G$ and the diameter of the matched subgraph is no more than $\varphi$. Moreover, the algorithm is in \NP since step~2 can be checked in \PTIME (quadratic time, indeed).

\etitle{Lower bound}.
We next show the problem is \NP-hard by reduction from the $k$-clique problem, which is known \NP-complete~\cite{}.

An instance of $k$-clique is given a undirected graph $G_c(V_c,E_c)$ and an integer $k \leq |V_c|$, and is to determine whether there exists a $k$-clique in $G_c$. Given an instance $G_c$ and $k$ of the $k$-clique problem, we construct an instance of minimum-diameter extended graph simulation with `at least' semantic problem, that is, a pattern graph $P(V_p$, $E_p$, $l_p$, $f_p)$, a data graph $G(V$, $E$, $l$, $w)$, and a positive rational number $\varphi$, such that there exists a $k$-clique in $G_c$ if and only if $P \eeps_{dia} G$ with `at least' semantic \wrt $\varphi$.
\be
\item We define $P(V_p$, $E_p$, $l_p$, $f_p)$ as follows:
\bi
\item [(1)] $V_q = \{u_1, \ldots, u_t, v_1, v_2, w_1, \ldots, w_t\}$, $t \geq 1$, where the labels $l_p(v_1)$ and $l_p(v_2)$ of nodes $v_1$ and $v_2$ are `A', the labels $l_p(u_1)$ and $l_p(w_1)$ of nodes $u_1$ and $w_1$ are `$B_1$', the labels $l_p(u_2)$ and $l_p(w_2)$ of nodes $u_2$ and $w_2$ are `$B_2$', $\ldots$, and the labels $l_p(u_t)$ and $l_p(w_t)$ of nodes $u_t$ and $w_t$ are `$B_t$'.
\item [(2)] $E_q$ = \{$(u_t, u_{t-1})$, $(u_{t-1}, u_{t-2})$, \ldots, $(u_2, u_1)$, $(u_1, v_1)$, $(v_1, v_2)$, $(v_2, w_1)$, $(w_1, u_2)$, \ldots, $(w_{t-2}, w_{t-1})$, $(w_{t-1}, w_t)\}$.
\item [(3)] We already know that for each node $u$ in $V_q$, $f_p$ is assigned to be $[x, +\infty]$. Then we set $x_{u_1}$, $\ldots$, $x_{u_t}$, $x_{v_1}$, $x_{v_2}$, $x_{w_1}$, $\ldots$, $x_{w_t}$ of nodes $u_1$, $\ldots$, $u_t$, $v_1$, $v_2$, $w_1$, $\ldots$, $w_t$ all to be $k$.
\ei
\item We define $G(V$, $E$, $l$, $w)$ as follows:
\bi
\item [(1)] $V = V_0 \cup V_1 \cup V_2 \cup \ldots \cup V_t$ where
\bi
\item [(a)] $V_0$ consists of $n_1=|V_c|$ nodes (where $V_c$ is the set of nodes in the instance of the $k$-clique problem), all with label `A',
\item [(b)] $V_1$ consists of $n_1$ nodes, all label with `$B_1$'; $V_2$ consists of $n_1$ nodes, all label with `$B_2$'; \ldots; $V_t$ consists of $n_1$ nodes, all label with `$B_t$';
\ei
\item [(2)] $E = E_0 \cup E_1 \cup E_2 \cup \ldots \cup E_t$ where
\bi
\item [(a)] $E_0$ is derived according to $E_c$ of $G_c$. More specifically, $V_1$ consists of $n_1=|V_c|$ nodes, for each $(v_1, v_2)\in E_c$, there exists an edges $(v_1, v_2)$ in $E_1$.
\item [(b)] $E_1$ consists of $n_1$ edges connect each node in $V_1$ to one node in $V_0$, that is, for each $v' \in V_1$, there exists only one node $v \in V_0$, there is an edge $(v', v)$ in $E_1$, and there is no other node $v'' \in V_1$ with an edge $(v'', v)$ in $E_1$. Then the same holds for $E_i$ where $2 \leq i \leq t$, $E_i$ consists of $n_1$ edges connect each node in $V_i$ to one node in $V_{i-1}$.
\item [(c)] the weight of each edge in $E$ is set to 1.
\ei
\item [(3)] We set $\varphi=2t+1$.
\ei
\ee

Intuitively, each node label with `A' in $G$ is connected with a subgraph ($\{v_1, $\ldots$, v_t\}$, $\{(v_1, v_2), $\ldots$, (v_{t-1}, v_t)\}$, $l(v_i)=`B_i'$, $w(e)=1$), and the diameter of the subgraph is $t-1$.

We next show that $G_c$ has a k-clique if and only if $P \eeps_{dia} G$ with `at least' semantic \wrt $\varphi$.

\stab
{$\Rightarrow$}
Assume $G_c$ has a k-clique with a set $V_c^* \subseteq V_c$ of $k$ nodes. We will show that the subgraph $G_s(V_s=V_0^* \cup V_1^* \cup \ldots \cup V_t^*$, $E_s=E_0^* \cup E_1^* \cup \ldots \cup E_t^*$) of $G$ matches $P$ via minimum-diameter extended graph simulation with `at least' semantic, where (1) $V_0^*$ corresponds to $V_c^*$, consisting $k$ nodes in $V_0$, and $E_0^*$ consists of $\frac{k(k-1)}{2}$ edges connecting each pair of nodes in $V_0^*$; (2) for $1 \leq j \leq t$, $V_j^*$ consists of $k$ nodes in $V_j$, and $E_j^*$ consists of $k$ edges connecting nodes in $V_j^*$ with nodes in $V_{j-1}^*$. Obviously, $G_s$ matches $P$ via extended graph simulation; and moreover, the diameter $dia_{G_s}=2t+1$, is no more than $\varphi$ (equal to, indeed).

\stab
{$\Leftarrow$}
Suppose there exists a subgraph $G_s(V_s,E_s)$ that matches $P$ via minimum-diameter extended graph simulation with `at least' semantic. Assuming $V_s=V_0^* \cup V_1^* \cup \ldots \cup V_t^*$, according to the character of pattern graph $P$, $V_0^*$ consists of at least $k$ nodes in $V_0$ and $V_1^*$ consists of at least $k$ nodes in $V_1$, and the same holds for $V_2$, $\ldots$, $V_t$. If there is a node $v_0 \in V_0^*$, the connected node $v_1 \in V_1$ must be contained in $V_1^*$, sequentially, the connected nodes $v_j \in V_j$ must be contained in $V_j^*$, for $2 \leq j \leq t$, thus we have $|V_0^*|=|V_1^*|=\ldots=|V_t^*| \geq k$. Assume $E_s=E_0^* \cup E_1^* \cup \ldots \cup E_t^*$, where $E_0^*$ consists edges connecting nodes in $V_0^*$, and $E_1^*$ consists of $|V_1^*|$ edges connecting nodes in $V_1^*$ with nodes in $V_0^*$, and similarly for $E_2$, $\ldots$, $E_t$. Apparently, each node in $G_s$ label with `A' is connected with a subgraph with diameter $t-1$. As the diameter of $G_s$ is no more than $\varphi$, we say that $E_0^*$ must contain the edges connecting each pair of nodes in $V_0^*$, such that $dia_{G_s}=2t+1$, equal with $\varphi$. If not, the diameter of $G_s$ must be greater than $\varphi$.

Apparently, we have shown that when there exists such a subgraph $G_s$ that matches $P$ \wrt $\varphi$, we have that subgraph ($V_0^*$, $E_0^*$) of $G_s$ must be a clique with no less than $k$ nodes. Thus we can easily find that there exists a corresponding $k$-clique in $G_c$.

%%%%%%%%%%%%%Approximation hardness%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{theorem}
\label{thm-esim-den-appro-hardness}
Unless \NP = P, the exactly and at most case of densest extended graph simulation problem cannot be approximated within any factor in \PTIME.
\end{theorem}

\subsection*{Proof of Theorem~\ref{thm-esim-den-appro-hardness}}
We can prove it by contradiction. Suppose there exists a \PTIME $\alpha$-approximation algorithm $\aleph$ can solve densest extended graph simulation problem in exactly (at most) case, where $\alpha$ represents any variables and constants. Then by executing $\aleph$, we can get a result matched subgraph $G_{rs}$ with density $\xi$, supposing the density of the optimal matched subgraph is $\xi^*$, such that $\xi\leq\alpha\xi^*$. This implies that the algorithm $\aleph$ can correctly determines the densest extended graph simulation problem in exactly (at most) case in \PTIME, which contradicts the complexity of the problem in Theorem~\ref{thm-esim-den-opt-complexity}. Thus we say that there exists no bounded approximation algorithm for the exactly (at most) case of densest extended graph simulation problem.

NEED a L-reduction.........

\begin{theorem}
\label{thm-esim-dia-appro-hardness}
Unless \NP = P, the exactly and at most case of minimum-diameter extended graph simulation problem cannot be approximated within any factor in \PTIME.
\end{theorem}

\subsection*{Proof of Theorem~\ref{thm-esim-dia-appro-hardness}}
It can be proved similar with Theorem~\ref{thm-esim-den-appro-hardness}.

\section*{{\Large \sf APPENDIX B: added}}

\subsection*{1. Introduction}
\stitle{Related work}.
There is a considerable amount of study related to our work can be classified into three categories: team formulation, keywords on graphs, graph pattern matching and graph density.

\stitle{Team formulation}. Lappas et al.~\cite{Lappas09} is the first to consider team formulation problem while minimizing the communication cost. By formalizing communication cost as diameter and the total weights of minimum spanning tree(MST) induced by the team, Lapps et al have proved the problem is \NP-hard, and they have proposed an approximation algorithms for minimizing the diameter with a guarantee 2 and a greedy algorithm with no approximation ratio for MST. Authors of~\cite{Kargar11} proposed a new communication cost function of minimizing the sum of distances between each pair of skill holders and provided a 2-approximation algorithm. They also introduced the problem of finding a team of experts with a leader while considering another new communication cost function of minimizing the the sum of distance between the leader and each of the skill holders in the team. Authors of~\cite{Chengte10,GajewarS12} generalized this problem to the case where for each required skill, multiple  experts possessing the skill are desired. \cite{Chengte10} utilized MST as the metric of communication cost, but they have proposed algorithms with no approximation ratio. In \cite{GajewarS12}, density based measures are used as objectives, they have proposed a 3-approximation algorithm for single skill team formation problem(sTF), and  greedy algorithm with no approximation ratio for multiple skill team formation problem(mTF).

\stitle{Keywords on Graphs}.

\stitle{Graph pattern matching}. Graph pattern matching is often defined according to subgraph isomorphism~\cite{Aggarwal10,Galla06}, an \NP-complete problem. However, it is too restrictive to catch sensible matches in most cases, as it requires match subgraphs to have exactly the same topology as the pattern graph. Subsequently, to reduce the time complexity, graph simulation~\cite{ccs} has been adopted for pattern graph matching which can be determined in quadratic time. It devotes to preserve the child relationship of pattern graph, but it may fail to capture the topology of graphs and yield false matches or too large a match relation. To rectify these problems, strong simulation~\cite{MaCFHW11} imposes two additional constraints on graph simulation: the duality to preserve both parent and child relationships, also referred to as dual simulation~\cite{MaCFHW11}, and the locality to eliminate excessive matches. It is capable of capturing the topology in graph pattern matching and can be determined in cubic time.

\stitle{Graphs density}.
As mentioned above, \cite{GajewarS12} has utilized density as a measure of collaborative compatibility, and the problem of finding densest subgraphs has been well-studied these years. Given a undirected data graph, finding a subgraph with maximum density~\cite{Goldberg84} can be solved optimally in polynomial time. However when there is a size constraint specified, the densest-k-subgraph problem, namely, finding a densest subgraph with exactly $k$ vertices becomes \NP-hard~\cite{FeigeML01,FeigePK01}. The algorithm developed by Feige et al. achieves the best approximation ratio for now~\cite{FeigePK01}. Andersen et al~\cite{Andersen09} considered the problem of finding dense subgraphs with specified upper and lower bounds on the number of vertices, the densest-at-least-k-subgraph (Dalks) problem and the densest-at-most-k-subgraph (Damks) problem. Khuller et al~\cite{Khuller09} have shown that Dalks is \NP-complete. Andersen et al have shown that Damks is nearly as hard to approximate as Dks and gave constant factor approximation algorithms for Dalks.

\subsection*{2. Extended Graph Simulation}

\subsection*{2.2. Graph Pattern Matching Revisited}
\begin{prop}
\label{prop-specialcase-clique}
Given a pattern graph $P(V_p$,$E_p)$, which is a clique, and the capacity on all the pattern nodes is $[|V_p|, |V_p|]$, and given a data graph $G(V_g$,$E_g)$. If $P \eeps G$, and the matched subgraph is $G_s$, then $G_s$ may be a clique with $|V_p|$ nodes.
\end{prop}

As shown in Fig.~\ref{fig-cliquecase}, $P \eeps G$, the matched subgraphs $G_{s1}$ is a clique, while $G_{s2}$ is not a clique.

%%%%%%%%%%%%%%%%%%%%%%%%%%% Theorem 3
\begin{figure}[tb!]
\begin{center}
\includegraphics[scale=0.4]{./fig/cliquecase.eps}
\caption{Data graph $G$ and pattern graph $P$ for Proposition~\ref{prop-specialcase-clique}}
\label{fig-cliquecase}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{2.3. Group Recommendations}

We know from Theorem~\ref{thm-esim-complexity} that given pattern graph $P$ and data graph $G$, it is \NP-complete to determine whether $P \eeps G$. Consequently, there may be exponential subgraphs of $G$ that matches $P$ via extended graph simulation. In the context of group recommendation, the user may want to search for the subgraph $G_s$ with high match quality, \ie the group with all members collaborating effectively.\cite{} has proposed a novel method utilizing density, the definition has been mentioned in Section~\ref{sec-gpm}, to measure the collaborative quality of a group formation.

In this section, we utilize density as a measure to tackle with the problem of searching for the best group, \ie finding group with excellent collaborative affinity proportional to the density of the induced subgraph.

\stitle{Densest extended graph simulation}. Given pattern graph $P$, data graph $G$, and a positive rational number $\xi$. Data graph $G$ {\em matches} pattern graph $P$  via {\em densest extended graph simulation}, denoted by $P \eeps_{den} G$, if there exists a connected subgraph $G_s[V_s, E_s]$ in $G$ that satisfies the following:

\vspace{0.5ex}
\ni(1) $P \eeps G$ with the maximum match relation $\Reps$;

\vspace{0.5ex}
\ni(2) the density of $G_s$ is is no less than $\xi$;

\begin{theorem}
\label{thm-esim-den-opt-complexity}
Given pattern graph $P$, data graph $G$, and a positive rational number $\xi$. It is \NP-complete to determine whether $P \eeps_{den} G$.
\end{theorem}

\textbf{Proof} We prove that in general case, three special cases are all \NP-complete: the `exactly', the `at least', the `at most' semantic.\\

We utilize another metric diameter as a measure to deal with the problem of searching for the best group, \ie finding group with any two members communicate efficiently and effectively in a short distance.

\stitle{Minimum-diameter extended graph simulation}. Given pattern graph $P$, data graph $G$, and a positive rational number $\varphi$. Data graph $G$ {\em matches} pattern graph $P$  via {\em densest extended graph simulation}, denoted by $P \eeps_{dia} G$, if there exists a connected subgraph $G_s[V_s, E_s]$ in $G$ that satisfies the following:

\vspace{0.5ex}
\ni(1) $P \eeps G$ with the maximum match relation $\Reps$;

\vspace{0.5ex}
\ni(2) the diameter of $G_s$ is is no more than $\varphi$;

\begin{theorem}
\label{thm-esim-dia-opt-complexity}
Given pattern graph $P$, data graph $G$, and a positive rational number $\xi$. It is \NP-complete to determine whether $P \eeps_{dia} G$.
\end{theorem}

\textbf{Proof} We prove that in general case, three special cases are all \NP-complete: the `exactly', the `at least', the `at most' semantic.

\subsection*{3. Computing Extended Graph Simulations}

\subsubsection*{3.1 Algorithms for graph pattern matching via maximum-density extended graph simulation}

\textbf{\emph{general case}}\\
We will now provide an algorithm for graph pattern matching via maximum-density extended graph simulation in general case.
\begin{figure}[t]
\vspace{-2ex}
\begin{center}
{\small

\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/}Pattern graph $P(V_p$, $E_p$, $f_p)$,
data graph $G(V$,$E$,$w)$.\\
{\sl Output:\/} The matched subgraph $G_{maxs}$ of $G$ with large density $w.r.t.$ $P$\\
\bcc \quad $S_G$:=GraphSimulation$(G,P)$;\\
\icc \quad constructs the set of connected components\\
\quad $\{G_{c1}, G_{c2}, \cdots, G_{cn}\}$ of $G$ \wrt $\{S_{c1}, S_{c2}, \cdots, S_{cn}\}$ and $P$;\\
\icc \quad for each ${G_c}_i (1 \leq i\leq n)$ do\\
\icc \quad\quad ${G_{cds}}_i$:=Densubgraph(${G_c}_i$, ${S_c}_i$, $P$);\\
\icc $G_{maxs}:=\arg\min_{1 \leq i\leq n}{G_{cds}}_i$;\\
\icc return $G_{maxs}$;
}

\mat{0ex}{
\textbf{Procedure GraphSimulation}$(G,P)$\\
\sstab {\sl Input:\/}Pattern graph $P(V_P$, $E_P$, $f_P)$,
data graph $G(V$,$E$,$w)$.\\
{\sl Output:\/} The maximum match relation $S_G$ of $P$ and $G$\\
\bcc \quad for each $v \in V_P$ do\\
\icc \quad\quad sim($v$):=\{$u$ $|$ $u$ is in $G$ and $l_P(u)=l_G(v)$\};\\
\icc \quad while there are changes do\\
\icc \quad\quad for each edge $(v,v')$ in $E_P$ and each node $u \in sim(v)$ do\\
\icc \quad\quad\quad if there is no edge $(u,u')$ in $G$ with $u' \in sim(v')$\\
\icc \quad\quad\quad then sim($v$):=sim($v$)$\backslash$\{$u$\};\\
\icc \quad\quad if sim($v$)=$\emptyset$ then return $\emptyset$;\\
\icc $S_G$:=\{$(v,u)$ $|$ $v \in V_P$, $u \in sim(v)$\};\\
\icc return $S_G$;\\
}

\mat{0ex}{
\textbf{Procedure Densubgraph}$(G,P)$\\
\sstab {\sl Input:\/} Pattern graph $P(V_P$, $E_P$, $f_P)$, data graph $G_c(V_c$, $E_c$, $w_c)$,\\
 \quad\quad\quad match relation $S_c$.\\
{\sl Output:\/}  The matched subgraph $G_{cds}$ of $G_c$ with large density $\wrt$ $P$.\\
\bcc \quad while $G_c$ not satisfy the supremum capacity requirements on all the pattern nodes\\
\icc \quad\quad for each $v \in V_c$ do\\
\icc \quad\quad\quad $AFW[v]:=\sum_{vv' \in E_c}{w_{vv'}}$;\\
\icc \quad\quad $v_{min}:=\arg\min_{v\in V_c}AFW[v]$;\\
\icc \quad\quad \{$AFN[v_{min}], S_c$\}:=incrementalAlg($P,G_c,S_c,v_{min}$);\\
\icc \quad\quad remove $AFN[v_{min}]$ and the related edges from $G_c$;\\
\icc \quad\quad if there is a pattern node $u$ having $|$sim$(u)| < inf(l_p(u))$ (sim$(u)\in S_c$)\\
\icc \quad\quad then return $\emptyset$;\\
\icc $G_{cds}:=G_c;$\\
\icc return $G_{cds}$;
}

\mat{0ex}{
\textbf{Procedure incrementalAlg}$(P, G_c, S_c, v)$\\
\sstab {\sl Input:\/} Pattern graph $P(V_p, E_p, l_p, f_p)$, data graph $G_c(V_c,E_c,l_c,w_c)$,\\
\quad\quad\quad the node $v$ to be removed from $G_c$, and the old maximum match $S_c$.\\
{\sl Output:\/} The set $\Delta$ of affected nodes in $G_c$ and the new maximum match $S_c$.\\
\bcc \quad $AFF$:= all the adjacent edges of $v$;\\
\icc \quad $wSet:=\emptyset$; $\Delta:=\{v\}$;\\
\icc \quad for all $(v,v')\in AFF$ do\\
\icc \quad\quad for all $(u,u')\in E_p$ having $v' \in mat(u')$ and $v\in mat(u)$ do\\
\icc \quad\quad\quad if $adjacent(l_p(u),v')\cap mat(u)=\emptyset$ then\\
\icc \quad\quad\quad\quad $wSet$.push($(u',v')$);\\
\icc \quad\quad\quad\quad while ($wSet\neq \emptyset$) do\\
\icc \quad\quad\quad\quad\quad $(u',v'):=wSet$.pop();\\
\icc \quad\quad\quad\quad\quad $\Delta:=\Delta\cup \{v'\}$; $S_c:=S_c\backslash\{(u',v')\}$;\\
\icc \quad\quad\quad\quad\quad for all $(u',u'')\in E_p$ do\\
\icc \quad\quad\quad\quad\quad\quad for all $v''\in adjacent(l_p(u''),v')\cap mat(u'')$ do\\
\icc \quad\quad\quad\quad\quad\quad\quad if $adjacent(l_p(u'),v'')\cap mat(u')=\emptyset$ then \\
\icc \quad\quad\quad\quad\quad\quad\quad\quad $wSet$.push($(u'',v'')$);\\
\icc if there is a pattern node $u$ having mat($u$)=$\emptyset$ then\\
\icc return $\Delta$ and $S_c$;
}

\vspace{-2.5ex} \myhrule

}
\end{center}
\vspace{-4ex}
\caption{Filter } \label{cenAlg-Select}
\vspace{-3ex}
\end{figure}

\be
\item step 1: compute simulation relation $R$ of $P$ and $G$, as well as the matched subgraph $G_R$ of $P$ in $G$;
\item step 2: select the node $v$ that has the least negative impact on the overall density of the matched subgraph;
\item step 3: remove $v$ from the matched subgraph, as well as those related nodes and edges that are not valid due the the removal of $v$ according to the decremental method, check whether the remaining subgraph satisfy the bound requirements.\\
    \textbf{repeat} step 2 and 3 until all the at-most bounds hold, and output the last subgraph of $G_R$ as result, otherwise return `No'.
\ee

\stitle{Remark}.  There are several points can be optimized in the algorithm.
\be
\item [(1)] The time complexity of the algorithm is $O(|V||P||G|)$.
\item [(2)] The algorithm devotes to search for subgraphs with great density, but the probability it cannot find any subgraphs satisfying the node-bounded requirements is high. We could conduct the optimization of balancing the accuracy and density, such as the removing order of nodes.
\item [(3)] Combine with incremental algorithm.(decremental method utilized in step3)
\item [(4)] Connectivity check $O(|G|)$.
\ee

\textbf{\emph{at least case}}\\
In at least case, due to the complexity of the problem, there maybe exists an approximation algorithm with good property.

\stitle{Remark}.  A basic $O(n)$-approximation algorithm is as below, by only executing graph simulation.
\be
\item step 1: compute simulation relation $R$ of $P$ and $G$, as well as the matched subgraph $G_R$ of $P$ in $G$;
\item step 2: check whether any connected component of $G_R$ satisfy the node-bounded requirements and return the subgraph, otherwise return `No'.
\ee

\subsubsection*{3.2 Algorithms for graph pattern matching via minimum-diameter extended graph simulation}

\textbf{\emph{general case}}\\
We will now provide an algorithm for graph pattern matching via minimum-diameter extended graph simulation in general case.

\begin{figure}[t]
\vspace{-2ex}
\begin{center}
{\small

\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/}Pattern graph $P(V_p$, $E_p$, $f_p)$,
data graph $G(V$,$E$,$w)$.\\
{\sl Output:\/} The matched subgraph $G_{mins}$ of $G$ with large density $w.r.t.$ $P$\\
\bcc \quad $S_G$:=GraphSimulation$(G,P)$;\\
\icc \quad constructs the set of connected components\\
\quad $\{G_{c1}, G_{c2}, \cdots, G_{cn}\}$ of $G$ \wrt $\{S_{c1}, S_{c2}, \cdots, S_{cn}\}$ and $P$;\\
\icc \quad for each ${G_c}_i (1 \leq i\leq n)$ do\\
\icc \quad\quad ${G_{cms}}_i$:=MinDiasubgraph(${G_c}_i$, ${S_c}_i$, $P$);\\
\icc $G_{mins}:=\arg\min_{1 \leq i\leq n}{G_{cms}}_i$;\\
\icc return $G_{mins}$;
}

\mat{0ex}{
\textbf{Procedure GraphSimulation}$(G,P)$\\
\sstab {\sl Input:\/}Pattern graph $P(V_P$, $E_P$, $f_P)$,
data graph $G(V$,$E$,$w)$.\\
{\sl Output:\/} The maximum match relation $S_G$ of $P$ and $G$\\
\bcc \quad for each $v \in V_P$ do\\
\icc \quad\quad sim($v$):=\{$u$ $|$ $u$ is in $G$ and $l_P(u)=l_G(v)$\};\\
\icc \quad while there are changes do\\
\icc \quad\quad for each edge $(v,v')$ in $E_P$ and each node $u \in sim(v)$ do\\
\icc \quad\quad\quad if there is no edge $(u,u')$ in $G$ with $u' \in sim(v')$\\
\icc \quad\quad\quad then sim($v$):=sim($v$)$\backslash$\{$u$\};\\
\icc \quad\quad if sim($v$)=$\emptyset$ then return $\emptyset$;\\
\icc $S_G$:=\{$(v,u)$ $|$ $v \in V_P$, $u \in sim(v)$\};\\
\icc return $S_G$;\\
}

\mat{0ex}{
\textbf{Procedure MinDiasubgraph}$(G,P)$\\
\sstab {\sl Input:\/} Pattern graph $P(V_P$, $E_P$, $f_P)$, data graph $G_c(V_c$, $E_c$, $w_c)$,\\
 \quad\quad\quad match relation $S_c$.\\
{\sl Output:\/}  The matched subgraph $G_{cms}$ of $G_c$ with large density $\wrt$ $P$.\\
\bcc \quad while $G_c$ not satisfy the supremum capacity requirements on all the pattern nodes\\
\icc \quad randomly pick a node $v \in V_c$;\\
\icc \quad for each $v' \in V_c$ do\\
\icc \quad\quad $dis[v']$:=the total weight of the path from $v$ to $v'$;\\
\icc \quad $v_{max}:=\arg\max_{v' \in V_c}dis[v']$;\\
\icc \quad\quad \{$AFN[v_{max}], S_c$\}:=incrementalAlg($P,G_c,S_c,v_{max}$);\\
\icc \quad\quad remove $AFN[v_{max}]$ and the related edges from $G_c$;\\
\icc \quad\quad if there is a pattern node $u$ having $|$sim$(u)| < inf(l_p(u))$ (sim$(u)\in S_c$)\\
\icc \quad\quad then return $\emptyset$;\\
\icc $G_{cms}:=G_c;$\\
\icc return $G_{cms}$;
}

\mat{0ex}{
\textbf{Procedure incrementalAlg}$(P, G_c, S_c, v)$\\
\sstab {\sl Input:\/} Pattern graph $P(V_p, E_p, l_p, f_p)$, data graph $G_c(V_c,E_c,l_c,w_c)$,\\
\quad\quad\quad the node $v$ to be removed from $G_c$, and the old maximum match $S_c$.\\
{\sl Output:\/} The set $\Delta$ of affected nodes in $G_c$ and the new maximum match $S_c$.\\
\bcc \quad $AFF$:= all the adjacent edges of $v$;\\
\icc \quad $wSet:=\emptyset$; $\Delta:=\{v\}$;\\
\icc \quad for all $(v,v')\in AFF$ do\\
\icc \quad\quad for all $(u,u')\in E_p$ having $v' \in mat(u')$ and $v\in mat(u)$ do\\
\icc \quad\quad\quad if $adjacent(l_p(u),v')\cap mat(u)=\emptyset$ then\\
\icc \quad\quad\quad\quad $wSet$.push($(u',v')$);\\
\icc \quad\quad\quad\quad while ($wSet\neq \emptyset$) do\\
\icc \quad\quad\quad\quad\quad $(u',v'):=wSet$.pop();\\
\icc \quad\quad\quad\quad\quad $\Delta:=\Delta\cup \{v'\}$; $S_c:=S_c\backslash\{(u',v')\}$;\\
\icc \quad\quad\quad\quad\quad for all $(u',u'')\in E_p$ do\\
\icc \quad\quad\quad\quad\quad\quad for all $v''\in adjacent(l_p(u''),v')\cap mat(u'')$ do\\
\icc \quad\quad\quad\quad\quad\quad\quad if $adjacent(l_p(u'),v'')\cap mat(u')=\emptyset$ then \\
\icc \quad\quad\quad\quad\quad\quad\quad\quad $wSet$.push($(u'',v'')$);\\
\icc if there is a pattern node $u$ having mat($u$)=$\emptyset$ then\\
\icc return $\Delta$ and $S_c$;
}

\vspace{-2.5ex} \myhrule

}
\end{center}
\vspace{-4ex}
\caption{Filter } \label{cenAlg-Select}
\vspace{-3ex}
\end{figure}

\be
\item step 1: compute simulation relation $R$ of $P$ and $G$, as well as the matched subgraph $G_R$ of $P$ in $G$;
\item step 2: randomly pick a node $v$ in $G_R$ and calculate the distances to all the nodes in $G_R$;
\item step 3: remove the node that is farthest from $v$, removing the related nodes and edges  according to the decremental method, check whether the remaining subgraph satisfy the bound requirements.\\
    \textbf{repeat} step 3 until the there exists any at-least bound does not hold, and output the last subgraph of $G_R$ as result, otherwise return `No'.
\ee

\stitle{Remark}.  The time complexity of the algorithm is $O(|V||P||G|)$. There are several points can be optimized in the algorithm.
\be
\item [(1)] In step3, remove a set of nodes that is farthest from $v$ instead of only one node.(Binary search)
\item [(2)] In step2, instead of randomly pick a node $v$ in $G_R$, we can randomly pick a node in the set of nodes with same label which have the least cardinality.
\item [(2)] Combine with incremental algorithm.(decremental method utilized in step3)
\ee

\textbf{\emph{at least case}}\\
In at least case, due to the complexity of the problem, there maybe exists an approximation algorithm with good property.

### 2017-09-25 TF-vldb2018/sec-conclusion.tex

\vspace{-2ex}
\section{Conclusion}
\label{sec-conclusion}

We have introduced a graph pattern matching approach for (dynamic) top-$k$ team formation problem.
We have proposed team simulation,
%based on which we have developed an efficient batch algorithm for top-k team formation.
and also  developed a unified incremental framework to handle continuous pattern and data updates, separately and simultaneously.
We have experimentally verified the effectiveness and efficiency of the batch and incremental algorithms.
\looseness=-1

A couple of topics are targeted for future work.  First, an interesting topic is to develop distributed algorithms for top-$k$ team formation.
Second, the study of dynamic algorithms for query updates is in its infancy,
and hence, an important topic is to develop such algorithms for various problems.

### 2017-09-25 TF-vldb2018/sec-dynamicTopk.tex

\newcommand{\changedinc}{\kw{Changed}}
\newcommand{\cut}{\kw{CUT}}
\newcommand{\imr}{\kw{IMR}}
\newcommand{\imrs}{\kw{IMRs}}
\newcommand{\fb}{\kw{FBM}}
\newcommand{\bs}{\kw{BS}}
\newcommand{\fs}{\kw{FS}}
\newcommand{\bfc}{\kw{BF}}
\newcommand{\upl}{\kw{UP}}
%\newcommand{\fbm}{\kw{FBM}}
\newcommand{\fbmatstruct}{\kw{FBMatStruct}}
\newcommand{\matchindex}{\kw{MatStaIndex}}
\newcommand{\matchimr}{\kw{MatchIMR}}
\newcommand{\for}{\kw{FOR}}
\newcommand{\while}{\kw{WHIlE}}
\newcommand{\allmatch}{\kw{mat}}
\newcommand{\affnode}{\kw{affnode}}

\newcommand{\ms}{\kw{SHOUDfs}}
\newcommand{\ballfilter}{\kw{SHOUDbfc}}

\newcommand{\dens}{\kw{den}}
\newcommand{\identifyaffball}{\kw{IdABall}}
\newcommand{\patedgeinsert}{\kw{patEIns}}
\newcommand{\incmatch}{\kw{IncMatch}}
\newcommand{\wmatchindex}{\kw{wMatStaCode}}
\newcommand{\cflag}{\kw{cflag}}
\newcommand{\dflag}{\kw{dflag}}
\newcommand{\gflag}{\kw{gflag}}
\newcommand{\rflag}{\kw{rflag}}

\newcommand{\incgrpat}{\kw{kPatIncGPM}}
\newcommand{\incgrdata}{\kw{kDataIncGPM}}
\newcommand{\dyngr}{\kw{kDynGPM}}
\newcommand{\affballx}{\kw{AffB}}
\newcommand{\affballsx}{\kw{AffBs}}
\newcommand{\affballacc}{\kw{AffBall^{acc}}}
\newcommand{\affballaccs}{\kw{AffBalls^{acc}}}
\newcommand{\affballimr}{\kw{AffBall^{imr}}}
\newcommand{\affballimrs}{\kw{AffBalls^{imr}}}
\newcommand{\patinc}{\kw{dynamicPG}}
%\newcommand{\patinc}{{\sc dynPG}\xspace}
%\newcommand{\datainc}{{\sc dynDG}\xspace}
\newcommand{\datainc}{\kw{dynamicDG}}
\newcommand{\optpatinc}{\kw{SHOULDoptinc}}
\newcommand{\inc}{\kw{dynamic}}
\newcommand{\matchs}{\kw{R}}
\newcommand{\comb}{\kw{combine}}
\newcommand{\optinc}{\kw{optDynamic}}

\newcommand{\incp}{\kw{dynamicP}}
\newcommand{\incd}{\kw{dynamicG}}

\section{A Unified Incremental Method}
\label{sec-dynamictopk}

\revise{
%In last section, we have studied the top-$k$ team formation problem.
Based on the dynamic top-$k$ team formation problem defined in Section~\ref{subsec-dynteamF}, 
in this section, we first theoretically analyze the challenges and design principles, 
and then develop a unified incremental framework for \dynteamF.
For convenience, the notations used are summarized in Table~\ref{tab-notation}.}

\revise{
By Theorem~\ref{thm-tsim-radius}, we know that $P$ matches a ball $\ball{[v, t]}$ ($t \in [1,r-1]$), only when $P$ matches ball $\ball{[v, r]}$ via graph simulation, 
and the match results for $\ball{[v, t]}$ can be derived from the matches for $\ball{[v, r]}$.
Therefore, we only concern about balls $\ball{[v, r]}$ in the incremental process, and finally compute the matches for balls $\ball{[v, t]}$ after we get the matches for ball $\ball{[v, r]}$.
Note that in the following when we refer to a ball, we indicate the ball with radius $r$ by default.}

%Moreover, incremental algorithms typically maintain some auxiliary data structures, which are specifically designed for the update types and need to be maintained by the incremental algorithms. An incremental algorithm for \dyngr should be able to design auxiliary structures to store information needed for both pattern and data increments and maintain it for future ({\em both}) pattern and data increments. This raises even more challenges in designing incremental algorithms for \dyngr, compared to those for \incgrpat and \incgrdata alone.

\eat{%%%EAT
Like data incremental problems, it would be nice to have {\em bounded incremental algorithms}~\cite{Reps96} for pattern incremental problems, which are a class of incremental algorithms whose time complexity depends on the sizes of $P$ and $\changedinc$, which is the changes to the input and output only (\ie $\Delta P$ and the difference between $PG_k(P, G)$ and $PG_k(P\oplus\Delta P, G)$),
and is independent of the size of $G$ and $PG_k(P, G)$.
However, due to the inherent difference between pattern increments and data increments, and the presence of top-$k$ semantic, they are not available for \incgrpat, as shown below.
We say an incremental problem is bounded if it has a bounded incremental algorithm described as above, and is unbounded otherwise.

Similar to the negative results in \cite{FanLMTWW10,FanWW13-tods}

The following results show that even we consider pattern or data increments alone, traditional bounded incremental algorithms are not available for \dyngr already.

%\begin{theorem}
%\label{thm-inc-grouprec-pat}
%$\incgrpat(P,G,k,PG_k(P,G),\Delta P)$ is unbounded, even when
%\bi
%\item $\Delta P$ is
%(a) a single-edge insert,
%(b) a single-edge delete,
%(c) a single-node insert,
%(d) a single-node delete, or
%(e) a single-node-capacity change;
%\item $k$ is 1 or $n$, where $n$ is the number of nodes in $G$.
%\ei
%\end{theorem}
%
%Moreover, due to the presence of top-$k$ semantic, the bounded incremental property is not available for \incgrdata either, as shown below.
%
%\begin{theorem}
%\label{thm-inc-grouprec-data}
%$\incgrdata(P,G,k,PG_k(P,G),\Delta G)$ is unbounded, even when
%\bi
%\item $\Delta G$ is
%(a) a single-edge insert,
%(b) a single-edge delete,
%(c) a single-node insert,
%(d) a single-node delete, or
%\item $k$ is 1 or $n$, where $n$ is the number of nodes in $G$.
%\ei
%\end{theorem}

}%%%EAT

\stitle{Incremental complexity analysis}. As observed in~\cite{Reps96}, the complexity of an incremental algorithm should be measured by the size $|\aff|$ of {\em the changes} in the input and output, rather than the entire input, to measure the amount of work absolutely necessary to be performed for the problem.

An incremental problem is said to be {\em bounded} if it can be solved by an algorithm whose complexity is a function of $|\aff|$ alone, and {\em unbounded}, otherwise.
Unfortunately, \dynteamF\, is unbounded, similar to the observations in \cite{FanLMTWW10,FanWW13-tods}.

\begin{prop}
\label{thm-inc-grouprec-pat}
The \dynteamF\, problem is unbounded, even for $k$ = 1 and unit pattern or data updates.
\end{prop}

\begin{example}
\label{exm-pattern-challenge}
Continue Example~\ref{exm-motivation-inc}, and consider updates $\Delta P_1$ or $\Delta G_1$ that obviously may introduce new matches.
%For convenience of presentation, we treat $\Delta P_1$ and $\Delta G_1$ separately.

\sstab
(1) For $\Delta P_1$, $\ball{[\kw{PM_1}, 2]}$ already matches $P$, and may produce more matched nodes for $P_1\oplus \Delta P_1$,
thus a re-computation for perfect subgraphs in the ball is needed.
For all other balls, $\Delta P_1$ may turn unmatched nodes to matched and may produce perfect subgraphs,
thus re-computation is also needed.
\looseness=-1

\sstab
(2) For $\Delta G_1$, it produces a new perfect subgraph for $P$ in $G_1\oplus\Delta G_1$,
\ie the connected component containing \kw{PM_2}.
The question is how to directly find new and maintain previous answers without redundant computation.
\looseness=-1
\end{example}

%\subsection{Analyses of Challenges}
%\label{subsec-challenges}

\begin{table}[tb!]
	%\vspace{-2ex}
	%\vspace{2ex}
	\begin{center}
		\begin{small}
			%\vspace{-2ex}
			\scriptsize
			\begin{tabular}{|c|l|}
				\hline
				{\bf Notations}             &  {\bf Description}     \\
				\hline\hline
				$P,G$                     &  pattern and data graphs       \\ \hline
				$\ball{[v, r]}$              &  a ball in $G$ with center node $v$ and radius $r$  \\ \hline
				$L_k(P, G)$                  &  the list of top-$k$ perfect subgraphs in $G$ for $P$  \\ \hline
				$\Delta P, \Delta G$       &  pattern and data updates       \\ \hline
				$\oplus$                    &  applying updates $\Delta P$ and $\Delta G$ to $P$ and $G$       \\ \hline
				${\cal P}_{h}=\{P_{fi}, C\}$     &  pattern fragmentation: $h$ fragments and cut    \\ \hline
				$\affballsx$                &  affected balls       \\ \hline
				$M(P_{fi}, \ball{[v,r]})$    &  the maximum match relation in $\ball{[v,r]}$ for $P_{fi}$   \\ \hline
				$\tilde{M}(P,G)$            &  fragment-ball matches (auxiliary structure)     \\ \hline
				$\fs$, $\bs$              &  fragment status, ball status (auxiliary structure) \\    \hline
				$\fb$                       &  fragment-ball-match index, containing $\fs, \bs$ \\    \hline
				$\bfc$, $\upl$              &  ball filter, update planner (auxiliary structure) \\    \hline
			\end{tabular}
			\vspace{-2ex}
		\end{small}
		\caption{Notations}
		\label{tab-notation}
		\vspace{-6ex}
	\end{center}
\end{table}

We next analyze the difficulties and principles of designing incremental algorithms for \dynteamF{} from three aspects.

%impacts of pattern and data updates, maintenance of proper auxiliary information, and support of simultaneous pattern and data updates.

\stitle{(1) Impacts of pattern and data updates}. It is necessary to identify and localize the impacts of pattern/data updates.
As indicated by Proposition~\ref{thm-inc-grouprec-pat} and Example~\ref{exm-pattern-challenge},
one can verify that (a) a unit pattern update is likely to result in the entire change in previous results,
such that all balls need to be accessed and all matches need to be re-computed;
%
and (b) data updates directly change the structure of data graphs, and its impact may be global, such that the entire data graph may need to be accessed to re-compute matches.

%It is rather better to identify the changes in match results in response to data updates, to minimize unnecessary recomputation.
%However, the identification can be difficult and time-consuming.
%It is crucial to identify which parts of $G$ are affected by the data updates and updates match results only within them.
%However, the identification can be difficult and time-consuming.
%The number of affected balls may vary with different data updates.

\stitle{(2) Maintenance of auxiliary information}.
Auxiliary data on intermediate or final results for $P$ in $G$ are typically maintained for incremental computation \cite{Reps96,FanWW13-tods}.
How to design light-weight and effective auxiliary structures is the key.
One may want to store $M(P,G)$, the match relations of $P$ for all balls in $G$,
as adopted by existing incremental pattern matching algorithms for data updates \cite{FanWW13-tods}.
However, the impact of $\Delta P$ is global, as shown in Example~\ref{exm-pattern-challenge}.
By storing $M(P,G)$, for pattern edge/node deletions, it has to recompute matches for all balls, \ie the entire $M(P,G)$.
Thus, storing $M(P,G)$ could be useless, not to mention $L_{k}(P,G)$, the list of top-$k$ perfect subgraphs for $P$ in $G$ \wrt $M(P,G)$.

\stitle{(3) Support of continuous pattern and data updates}.
%Previous research on incremental problems typically focus on increments to the data parts instead of the queries,
%and if exist, the dynamic algorithms either support pattern or data updates, not both of them~\cite{MottinGReform15,FanWW13-tods}.
A practical solution should support continuous pattern and data updates, separately and simultaneously, which further raises difficulties on the design of auxiliary data structures and on incremental algorithms.

%\subsection{A Unified Incremental Approach}
%\label{subsec-framework}

\vspace{1.0ex}
We next develop an incremental approach to handling pattern and data updates in a unified framework, based on {\em pattern fragmentation} and {\em affected balls}
to localize the impacts of pattern and data updates and to reduce the cost of maintaining auxiliary structures and computations.

%In light of the challenges, it is desirable to devise a unified efficient incremental approach to handle both $\Delta P$ and $\Delta G$,
%which can reduce the cost for maintaining auxiliary structures and computing final results,
%by restricting the update impacts from global to local.
%Therefore, we propose the {\em dynamic top-$k$ graph pattern matching} model to solve \dynteamF\.
%\looseness=-1

\stitle{Pattern fragmentation}. We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
if (1) $\bigcup_{i=1}^{h}V_{fi}=V_{P}$, (2) $V_{fi}\cap V_{fj} = \emptyset$ for any $i\ne j\in[1, h]$,
(3) $E_{fi}$ is exactly the edges in $P$ on $V_{fi}$, and (4) $C=E_P \setminus (E_{f1}\cup\ldots\cup E_{fh})$.

We also refer to $P_{fi}$ ($i\in[1,h]$) as a {\em fragment} of $P$, and $C$ as a {\em cut} of $P$, respectively.

Observe that by pattern fragmentation, a pattern update on $P$ is either on a fragment $P_{fi}$ or on the cut $C$ of $P$, and, in this way, the impact of pattern updates is localized. %to some extent.

\vspace{0.5ex}
Graph simulation has a nice property as follows.

\vspace{-0.5ex}
\begin{theorem}
\label{thm-compose}
Let $\{P_{f1},\ldots,P_{fh}\}$ be an $h$-fragmentation of pattern $P$.
For any ball $\ball{}$ in $G$, let $M_i$ ($i\in[1,h]$) be the maximum match relation in $\ball{}$ for $P_{fi}$ via graph simulation,
and $M$ be the maximum match relation in $\ball{}$ for $P$ via graph simulation, respectively,
then $M\subseteq\bigcup_{i=1}^{h}M_{i}$.
\end{theorem}

We also say that $M_i$ is a {\em partial match relations} in ball $\ball{}$ for $P$ via graph simulation.
%By Theorem~\ref{thm-compose}, instead of computing $M$ in $\ball{}$ \wrt\ $P$ directly, we can compute $M$ by first computing each $M_i$ in $\ball{}$ \wrt\ $P_{fi}$,
%and then combining them together.
By the nature of graph simulation~\cite{infsimu95}, $\bigcup_{i=1}^{h}M_{i}$ is actually intermediate results for computing $M$.
%such that the method above does not incur additional computation cost.
After we have the maximum match relation $M$ for $P$ in $\ball{}$, via graph simulation, we can further produce the result for $P$ in  $\ball{}$ via team simulation, by a capacity check.

That is, based on pattern fragmentation, we store and maintain $\tilde{M}(P,G)$ \wrt ${\cal P}_{h}$ for the incremental process,
\ie the maximum match relations for all pattern fragments of $P$ in all balls of $G$, via graph simulation.
Moreover, its space cost is light-weight, as shown in the experiments section.
%\revise{
%Moreover, by Theorem~\ref{thm-tsim-radius}, the match results in balls $\ball{[v, t]}$ ($1 \leq t < r$) can be easily derived from the %matches in ball $\ball{[v, r]}$.
%Thus, we only store the maximum match relations for all pattern fragments of $P$ in the balls with radius $r$ of $G$.}
%which will be shown to be much more informative than storing $M(P,G)$ and $L_{k}(P,G)$.
%Its space cost is light-weight, and takes 25MB only, together with all indexes for \citationd that needs 36MB to store itself.

%Indeed, it only takes 25MB and 65MB to store $\tilde{M}(P,G)$ along with all other indexes for Citation and YouTube,  which need 36MB and 114MB, respectively, for storing the entire data graphs.

We already know that pattern updates $\Delta P$ on $P$ can be treated as the updates $\Delta P$ on $P_{fi}$ or $C$ of $P$.
%If we have cached the maximum match relations of all pattern fragments,
By storing $\tilde{M}(P,G)$, we can get $\bigcup_{i=1}^{h}M_{i}$ for a ball $\ball{}$.
Then we can do an update computation on $M_i$ while leaving other parts unchanged. That is, to compute $P_{fi}\oplus\Delta P(\ball{})$ instead of $P\oplus\Delta P(\ball{})$, and to combine $P_{fi}\oplus\Delta P(\ball{})$ with the other parts to derive $P\oplus\Delta P(\ball{})$.
Even better, the updates $\Delta P$ on $C$ of $P$ only involve with the combination process, avoiding the computation for any pattern fragments.

Intuitively, we want (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.
Thus we define the {\em pattern fragmentation} problem. Given $P$ and a positive integer $h$, it is to find
an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized.
\revise{The bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size
	while minimizing the cut size between pattern fragments.}

\eat{%%%EAT2017-8-2}
Given $P$ and a positive integer $h$, the {\em pattern fragmentation}  problem is to find
an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized.
%
Intuitively, we want (1)  to avoid skewed updates by making all fragments roughly the same size and (2) to  minimize the efforts to assemble the partial matches of all fragments.
}%%%EAT2017-8-2

\vspace{0.5ex}
The problem is intractable, as shown below.

\vspace{-0.5ex}
\begin{prop}
	\label{prop-fragmentation}
	The pattern fragmentation problem is \NP-complete, even for $h$ = 2.
\end{prop}

\vspace{-0.5ex}
However, $P$ and $h$ are typically small in practice~\cite{FanLMTWW10}, \eg $|P|=15$ and $h=3$.
In light of this, we give a heuristic algorithm, denoted by \kw{PFrag}, for the problem, and is shown in the Appendix.
\kw{PFrag} works by connecting pattern fragmentation to the widely studied {\sc $(k, \nu)$-Balanced Partition} problem \cite{AndreevR06},
which is not approximable in general, but has efficient and sophisticated heuristic algorithms~\cite{metis-KarypisK98a}.

\vspace{1.0ex}
So far, we have restricted the impact of pattern updates from the entire $P$ to a fraction of $P$.
We further localize the impact of pattern and data updates  with {\em affected balls} to avoid computing and updating match relations for all balls.

\stitle{Affected balls (\affballsx)}.
We say a ball in $G$ is {\em affected} \wrt an incremental algorithm \algorithm{A}, and pattern and data updates,
if \algorithm{A} accesses the ball again.
We use $||\affballsx||$ and $|\affballsx|$ to denote the cardinality and total size of \affballsx, respectively.

%We say that a ball is {\em affected} \wrt an incremental algorithm \algorithm{A} and a set of pattern and data updates if \algorithm{A} re-constructs the ball again using the data graph.

%
Indeed, \affballsx are those balls with a possibility to have final results \wrt $\Delta P$ and $\Delta G$.
We only access \affballsx, and ignore the rest balls.
Specifically, (1) for $\Delta P$, it allows us to avoid computing updated partial relations for an updated fragment in every ball;
and (2) for $\Delta G$, the locality property of team simulation supports to localize the update impacts to a set of balls whose structures are changed by $\Delta G$.
%we just do the computation for the balls whose structure is changed due to $\Delta G$.
\looseness=-1

\stitle{Remark}. By pattern fragmentation and affected balls, we essentially localize the impact of pattern and data updates from the entire to a fraction of $P$ and from all to a subset of balls in $G$ for team simulation.

%\vspace{-0.5ex}
\stitle{Algorithm \inc}. We now provide a unified incremental algorithm \inc  to handle both pattern and data updates.

Given $P$ with its $h$-fragmentation ${\cal P}_{h}$, $G$, two integers $k, r$,
and auxiliary structures such as the partial match relations for all pattern fragments and all balls (radius $r$),
while auxiliary structures are to be presented in next section,
the algorithm consists of three steps for $\Delta P$ and $\Delta G$, as follows.

\etitle{(1) Identifying \affballsx}.
Algorithm \inc invokes two different procedures to identify \affballsx for separate $\Delta P$ or $\Delta G$, respectively.
For  simultaneous $\Delta P$ and $\Delta G$, \inc takes the union of the \affballsx produced by  the two procedures.

\etitle{(2) Update partial match relations in \affballsx}.
For a ball affected by $\Delta P$, \inc updates the partial match relations for the updated pattern fragments with incremental computation;
For a ball affected by $\Delta G$, \inc updates the partial match relations for all pattern fragments;
And, for a ball affected by both $\Delta P$ and $\Delta G$, \inc follows the same way as $\Delta G$ only.
Meanwhile, auxiliary structure \fb (to be seen shortly) is updated for handling continuous separate and simultaneous pattern and data updates.

\etitle{(3) Combining partial match relations}. \inc combines all partial relations for a subset of \affballsx and computes the top-$k$ perfect subgraphs within them and their inner balls.

\vspace{0.5ex}
Observe that \inc handles pattern/data updates in a unified way. Better still, it holds a nice property as follows.

\begin{theorem}
\label{thm-framework-inc}
With $\tilde{M}(P,G)$ and \fb \wrt an $h$-fragmentation of $P$, given $\Delta P$ and $\Delta G$,
the incremental algorithm \inc processes $\Delta P$ and $\Delta G$ in time
determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
\end{theorem}

We shall prove Theorem~\ref{thm-framework-inc} by providing specific techniques for \inc and analyzing its time complexity in Section~\ref{sec-IncAlg}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\eat{%%%EAT
Theorem~\ref{thm-inc-grouprec-pat} and ~\ref{thm-inc-grouprec-data} show that, conventional bounded incremental algorithms are not available for $\incgrpat$ and $\incgrdata$ even for unit update only.
The main reasons are three challenges introduced by pattern/data incremental and the top-$k$ semantic, summarized as follows.

\sstab {\bf Challenge (1): impacts of pattern or data changes}.
The first challenge is how to identify and restrict, if possible, the impacts of pattern or data changes. This is nontrivial.
(a) Due to the nature of pattern changes, a unit update on pattern graph may have impact on all perfect graphs in $PG(P,G)$, or even add new matches. Indeed, for any algorithm takes input as $P$, $G$, $k'$, $PG_k(P,G)$ and $\Delta P$, it has to access entire $G$ (every ball in $G$), even when $\Delta P$ is a unit update, $k' = 1$ and $k = |V_G|$. That is, the impacts of a pattern update can be global.
(b) Data changes may also cause complicated impacts on both the ball structures and the number of balls in $G$. For one thing, the number of balls in $G$ may increase or decrease with new data changes; for another, the match relations in existing balls may have to be re-computed since the structure of balls may change.
These impacts may vary over updates, and require us to identify them.
% the number of balls used by the TEAM simulation, and the
% For data changes, an edge/node delete (insert) may turn a matched node unmatched (unmatched node matched). We need to recompute new matches for all balls when we do not know which balls will contain matches due to the structure changes.

\sstab {\bf Challenge (2): necessary auxiliary information}.
The second challenge comes from the uninformative in the output top-$k$ perfect graphs of the team simulation.
(a) Due to the top-$k$ semantics, $PG_k(P,G)$ contains only top-$k$ perfect graphs \wrt match relations in $M(P,G)$, which could be extremely uninformative even when $k$ is large, as any changes in the results may requires the knowledge of all perfect graphs to enforce the top-$k$ semantics.
(b) Worse still, for pattern changes, even all perfect subgraphs $PG(P,G)$ are precomputed and cached, it can provide no help for pattern incremental when there are pattern edge/node deletes, as indicated in example~\ref{exm-pattern-challenge}.
(c) Traditional incremental algorithms typically maintain some auxiliary data structures to accelerate the incremental process. However, the physical storage is limited in practice, and essential structures needed for team simulation may not be able to fit in the storage budget.
Indeed, we examined basic structures for team simulation and using real-life data to validate whether they are suitable as auxiliary structures.
%
(i) The first candidate is the balls, since balls of the data graph are the basic computation unit for team simulation. We test the cost of cache them. The results are discouraging.
It will take about 361GB, 437GB and 222GB for Citation, YouTube and Synthetic data ($10^7$ nodes) when $r$ is set to 3, and 338GB, 420GB and 222GB even when compression technique is adopted. This shows that precomputing and caching all balls in $G$ as auxiliary information is impractical.
(ii) Another choice is to precompute and store $M(P,G)$, as adopted by some pattern incremental algorithms~\cite{FanWW13-tods}.
However, as indicated in Challenge (1), the impact of $\Delta P$ is global. By storing $M(P,G)$, for edge/node inserts or capacity changes, the incremental process can get match results by updating all matches in $M(P,G)$ for all balls in $G$; worse still, for edge/node deletes, it has to recompute all matches in $M(P,G)$ for all balls in $G$. Therefore, storing $M(P,G)$ cannot improve the incremental process in many cases, worst still, it even takes extra cost to maintain $M(P,G)$.
}%%%EAT

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
	\begin{center}
		\subfigure{\label{fig-auxstr-index}
			\includegraphics[scale=0.585]{./fig/fig-auxstr-index.eps}}
		\subfigure{\label{fig-inc-maintain-unit}
			\quad\quad \vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-unit.eps}}
		\subfigure{\label{fig-inc-maintain-batch}
			\vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-batch.eps}}
		\vspace{-3ex}
		\caption{Example auxiliary data structures}
		\label{fig-auxiliary-structures}
		\vspace{-3ex}
	\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-09-25 TF-vldb2018/sec-expt.tex

\section{Experimental Study}
\label{sec-expt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\begin{widepage}
%\vspace{-1.5ex}
\begin{center}

\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-diameter}
\includegraphics[scale=0.37]{./fig/citation-semantic-diameter.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-density}
\includegraphics[scale=0.37]{./fig/citation-semantic-density.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-capacity}
\includegraphics[scale=0.37]{./fig/citation-semantic-capacity.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-link}
\includegraphics[scale=0.37]{./fig/citation-semantic-link.eps}}
\vspace{-2.5ex}

\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-diameter-varyk}
\includegraphics[scale=0.37]{./fig/citation-semantic-diameter-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-density-varyk}
\includegraphics[scale=0.37]{./fig/citation-semantic-density-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-capacity-varyk}
\includegraphics[scale=0.37]{./fig/citation-semantic-capacity-varyk.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-link-varyk}
\includegraphics[scale=0.37]{./fig/citation-semantic-link-varyk.eps}}
\vspace{-2.0ex}
\end{center}

%\vspace{-2ex}
\vspace{-3ex}
\caption{Performance evaluation of algorithm \optgrouprec for top-$k$ team formation}
\label{exp-semantic-effectiveness-citation}
%\end{widepage}
\vspace{-3.0ex}
\end{figure*}

%We next present an experimental study using both real-life and synthetic data.
We conducted four sets of experiments to evaluate the performance of
(1) \optgrouprec for the top-$k$ team formation problem,
(2) \inc for the dynamic top-$k$ team formation problem
\wrt single set of (a) pattern updates, (b) data updates, and (c) simultaneous pattern and data updates;
(3) \inc \wrt continuous sets of pattern and data updates; and
(4) the extra space cost of auxiliary structures used by \inc.

\stitle{Experimental Settings.} We use the following settings.

%\subsection{Experimental Settings}
%We used the following real-life and synthetic datasets.
\etitle{Data graphs.} We used a real-life and a synthetic dataset.

\ni (1) {\em \citationd}~\cite{citationWeb} contains 1.39M paper nodes and 3.02M paper-paper citation edges.
We used its undirected version, where edges indicate the relevance relationship. We generated 200 labels based on phrase clustering of paper titles.

%\ni (2) {\em \youtube}~\cite{youtubeWeb} contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos. We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.

\ni (2) We adopted the LFR-benchmark graph model~\cite{AndreaSF08} to generate synthetic graphs (\synthetic) with community structure as existed in real-life networks. It is controlled by three parameters: the number $n$ of nodes, the average degree $d$ of nodes, and the number $l$ of node labels.
%Given $n, d$, and $l$, the generator produces a graph with $n$ nodes, $n*d/2$ edges, and the nodes are labeled from a set of $l$ labels.

\etitle{Pattern generator}.
We implemented a generator to produce pattern graphs, controlled by 4 parameters:
the number of nodes $|V_P|$, the number of edges $|E_P|$, label $l_{P}$ for each node from
an alphabet of labels in the corresponding data graphs,
and capacity bound $f_{P}$ for each node.

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09}; 
%firstly proposed the team formation problem;
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}. 
%which has the same goal with our algorithms; and
Among algorithms for \teamF, \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

We used a PC with Intel Core i5-4570 CPU and 16GB of memory. We randomly generated 3 sets of input and repeated 5 times for each test. The average is reported here.
All the findings on \youtube are reported in the Appendix.

%\subsection{Experimental Results}

\stitle{Experimental Results.} In all the experiments, we set $k=10$, $r=2$, $h=3$, $(|V_{P}|,$ $|E_{P}|)$ to be (10,12),
and capacity bounds to be [1,10] by default.
When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
\looseness=-1
%All the findings on \youtube are reported in the Appendix.

\stitle{Exp-1: Efficiency of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis and \denalk.

Algorithms \mindia, \minsumdis and \denalk do not scale well on large graphs.
Indeed,  (1) \mindia and \minsumdis take more than $8$ hours to finish their preprocessing, \ie computing all-pair-shortest-paths, and (2) \denalk takes more than 24 hours even when $k=1$ on \citationd.
By contrast, \optgrouprec takes around 100 seconds on \citationd by default settings.
Hence, we report the effectiveness of these algorithms on a sampled data graph with $10,000$ nodes on \citationd only.
%We further evaluate the efficiency of \optgrouprec in the incremental experiments.
%\looseness=-1

\stitle{Exp-2: Effectiveness of \optgrouprec}.  We generated pattern graphs for \optgrouprec, and the corresponding queries (labels requirements) for \mindia, \minsumdis and \denalk, and manually checked the quality of matches returned by them. 
\looseness=-1

\eat{%%%
\etitle{(1) Case study.}
We find \optgrouprec is able to identify sensible matches meeting the practical requirements.
We illustrate this with a real-life example pattern graph.

As shown in Fig.~\ref{fig-exp-1-effect-citation}, pattern graph $P_C$ is to find
(a) a set of papers in \citationd that ``Databases'', ``Data Mining'' and ``Artificial Intelligence'' papers are related to each other;
(b) ``Data Mining'' papers are related to ``Software Engineering'' papers; and
(c) the required number of papers for each domain is shown on $P_C$.
In \citationd, nodes are papers with unique id from different domains,
with labels indicating their domains, and they only match the nodes of $P_C$
with the same geometry shapes, \ie circles, ellipses and squares.

The match result of $P_C$ is shown in Figure~\ref{fig-exp-1-effect-citation}.
Observe that subgraph $G_C$ is the top-1 match result found by \optgrouprec for $P_C$, but cannot be found by \mindia, \minsumdis and \denalk, while $G'_C$ and $G''_C$ are the top-1 results found by \mindia and \minsumdis respectively.
The top-1 result found by \denalk is the densest component composed of 819 nodes (omitted).
These tell us that \optgrouprec has more expressive power than the other team formation algorithms
by identifying sensible matches satisfying the structural and capacity requirements.}%%%EAT

To evaluate the quality of teams found by the above four algorithms for \teamF, we defined four quality measures. 
Consider a matched subgraph $G_S$ and pattern $P(V_P, E_P)$.

\noindent {(a) [{\em Diameter}]}: the diameter of $G_S$.

\noindent {(b) [{\em Density}]}: the density of $G_S$.

\noindent {(c) [{\em Node satisfiability}]}: $\eta_V(G_S, P)$ = $\#\kw{sat}_V(G_S, P) / |V_P|$, where $\#\kw{sat}_V(G_S, P)$ is the number of nodes in $P$ that are satisfied by $G_S$, in which we say a pattern node $u$ is satisfied by $G_S$ if there are a set $V_u$ of nodes in $G_S$ that match $u$ and moreover, $V_u$ satisfies the capacity constraints on $u$.

\noindent {(d) [{\em Edge satisfiability}]}: $\eta_E(G_S, P)$ = $\#\kw{sat}_E(G_S,P)/|E_P|$, where $\#\kw{sat}_E(G_S,P)$ is the number of edges in $P$ satisfied by $G_S$, in which we say an edge $(u_1, u_2)$ is satisfied by $G_S$ if for each $v_1$ in $G_S$ that matches $u_1$,
there exists $(v_1, v_1')$ in $G_S$ so that $v_1'$ matches $u_2$, and for each  $v_2$ in $G_S$ that matches $u_2$, there exists $(v_2, v_2')$ in $G_S$ such that $v_2'$ matches $u_1$.
\looseness=-1

Note that (a) and (b) are two traditional quality measures utilized by existing team formation algorithms.
Intuitively, $\eta_V(G_S, P)$ (resp. $\eta_E(G_S,P)$) measures how well $G_S$ meets the node capacity requirements (resp. structural constraints) in $P$, and their values fall in $[0, 1]$.

\etitle{(i) Impacts of $|V_{P}|$}. Varying the number $|V_{P}|$ of
nodes in $P$ from 4 to 16, we took the average value of top-$k$ teams found by  \optgrouprec, \mindia, \minsumdis and \denalk \wrt five quality measures.
The results are reported in Figures \ref{fig-exp-semantic-citation-diameter}-\ref{fig-exp-semantic-citation-link}.

Observe the following.
%
(1) In Fig.~\ref{fig-exp-semantic-citation-diameter}, the diameter of teams found by \optgrouprec is less than \mindia and \minsumdis, but the teams are with a small diameter, \eg less than \denalk, because of the ball restriction of \optgrouprec;
(2) in Fig.~\ref{fig-exp-semantic-citation-density}, the density of teams found by \optgrouprec is less than \denalk, while is higher than \mindia and \minsumdis;
(3) in Fig.~\ref{fig-exp-semantic-citation-capacity}, the node satisfiability of teams found by \optgrouprec, \ie 1.0 in all cases, is much higher than \mindia, \minsumdis and \denalk, \ie less than 0.2; and
(4) in Fig.~\ref{fig-exp-semantic-citation-link}, the teams found by \optgrouprec come with a higher edge satisfiability , \ie 1.0 in all cases, compared to less than 0.6 by \mindia, \minsumdis and \denalk.

\etitle{(ii) Impacts of $k$}. Varying $k$ from 1 to 20, we report the results in Figures
\ref{fig-exp-semantic-citation-diameter-varyk}-\ref{fig-exp-semantic-citation-link-varyk}.
Observe that the quality of teams found by the four algorithms shows the same rule as varying $|V_{P}|$, and the quality is not sensitive to $k$, a desirable property when top-$k$ semantics is concerned.

\warn{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and capacity satisfiability, and pertains a good team collaboration compatibility \wrt density and diameter.}

\begin{figure*}[tb!]
%\begin{widepage}
\begin{center}
%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del}
\includegraphics[scale=0.38]{./fig/union-pattern-deletion.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins}
\includegraphics[scale=0.38]{./fig/union-pattern-insertion.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap}
\includegraphics[scale=0.38]{./fig/union-pattern-capchange.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)\hspace{-8.5ex}}]{\label{fig-exp-patinc-hyb}
\includegraphics[scale=0.38]{./fig/union-pattern-hybrid.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (deletions)}]{\label{fig-exp-datainc-del}
\includegraphics[scale=0.38]{./fig/union-data-deletion.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (insertions)}]{\label{fig-exp-datainc-ins}
\includegraphics[scale=0.38]{./fig/union-data-insertion.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ (hybrid updates)}\hspace{-5.5ex}]{\label{fig-exp-datainc-hyb}
\includegraphics[scale=0.38]{./fig/union-data-hybrid.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ (simultaneous)}\hspace{-8.5ex}]{\label{fig-exp-hyb-patdata}
\includegraphics[scale=0.38]{./fig/union-pattern-data.eps}}
\vspace{-2.5ex}

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi}
\includegraphics[scale=0.38]{./fig/union-pattern-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi}
\includegraphics[scale=0.38]{./fig/union-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi}
\includegraphics[scale=0.38]{./fig/union-pattern-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying Datasets}]{\label{fig-exp-extraspace}
\includegraphics[scale=0.38]{./fig/union-space.eps}}
\vspace{-2ex}

\end{center}
\vspace{-3ex}
\caption{Performance evaluation of algorithm \inc for dynamic top-$k$ team formation (Cit: \citationd, Syn: \synthetic)}
\label{exp-inc}
%\end{widepage}
\vspace{-3ex}
\end{figure*}

\stitle{Exp-3: Efficiency of \inc for single set of updates}. We evaluated the efficiency of algorithm \inc for processing one set of pattern updates, data updates and simultaneous pattern and data updates vs. algorithm \optgrouprec on \citationd and \synthetic, respectively.

\etitle{(i) Pattern updates}. We fixed $(|V_{P}|,$ $|E_{P}|)$ to be $(10, 12)$, and varied the number $|\Delta P|$ of unit updates from 1 to 11, corresponding to 4.5\% to 49.5\% in
Figs. \ref{fig-exp-patinc-del}, \ref{fig-exp-patinc-ins}, \ref{fig-exp-patinc-cap} and \ref{fig-exp-patinc-hyb},
which show the results when $\Delta P$ contains (edge and node) deletions, (edge and node) insertions, capacity changes and hybrid pattern updates (5 types) respectively,
while keeping the proportion for each type equal.

We find the following.
(1) \inc outperforms \optgrouprec even when deletions are no more than 40.5\% on \citationd and 49.5\% on \synthetic;
%When the changes are no more than 27\%, \optinc improves \optgrouprec by over 50\% and 94\% on Citation and synthetic data, respectively.
\inc consistently does better than \optgrouprec due to the early-return strategy.
%This verifies the effectiveness of early-return strategy.
(2) \inc improves \optgrouprec to a large extent when only processes insertions and capacity changes.
(3) For the same $|\Delta P|$, \inc needs less time to process insertions than deletions.
%\eg it takes 26 seconds to handle 5 pattern deletions, but only 1 second to process insertions of the same size on Citation.
(4) When processes hybrid pattern updates, \inc outperforms \optgrouprec when changes are no more than (31.5\%, 40.5\%) on (\citationd, \synthetic);
%When the changes are no more than 27\%, \optinc improves \optgrouprec by over 33\% and 90\% on Citation and synthetic data, respectively.
%\inc takes more time than \optgrouprec when the changes are more than (36\%, 40.5\%) on (\citationd, \synthetic).
It is because all balls are identified as \affballsx when pattern updates accumulate to a certain extent.

\etitle{(ii) Data updates}. For (edge and node) deletions (resp. insertions) on datasets,
\eg\ \citationd with $|G|=4.4M$,
we varied $|G|$ from $4.4M$ to $2.22M$ (resp. from $3.05M$ to $4.4M$) in $4.5\%$ decrements (resp.\,$4\%$ increments) by randomly picking a subset of nodes and edges and removing from $G$ (resp. inserting into $G$);
For hybrid data updates (4 types), we randomly sampled a subgraph $G_s$ and removed from $G$, obtaining the initial $G$. %obtaining the initial $G$ with $|G|=3.66M$.
We varied $|G|$ by firstly removing a subset of nodes and edges from $G$ and then inserting a subset of nodes and edges from $G_s$ into $G$, in total  $4\%$ updates.
%The data updates generation method is same on synthetic data.
The results are shown in Figures \ref{fig-exp-datainc-del}, \ref{fig-exp-datainc-ins} and \ref{fig-exp-datainc-hyb}.

We find the following.
(1) \inc outperforms \optgrouprec when insertions are no more than 28\% and 32\% on \citationd and \synthetic (resp. 40.5\% and 45\% for deletions).
%When the changes are 16\% for insertions (resp. 20\% for deletions), \optinc improves \optgrouprec by over 42\% and 24\% (resp. 70\% and 91\%).
(2) For the same $|\Delta G|$, \inc needs less time to process deletions than insertions.
(3) We have conducted a survey: the user increment on Facebook~\cite{facebookStat} and Twitter~\cite{twitterStat} daily reaches 1.23\textperthousand\ and 2.47\textperthousand.
Therefore, \inc is able to handle the increments accumulated in dozens of days on Facebook and Twitter
at a high efficiency.
(4) \inc outperforms \optgrouprec when hybrid data updates are no more than 32\% and 36\% on \citationd and \synthetic respectively.

\etitle{(iii) Simultaneous pattern and data updates}.  Varying the number of hybrid pattern updates from 1 to 7 and the amount of hybrid data updates from 4\% to 28\% together, corresponding to (4.5\%, 4\%) to (31.5\%, 28\%) for $(\Delta P, \Delta G)$ in Fig.~\ref{fig-exp-hyb-patdata}. We find that \inc outperforms \optgrouprec when $(\Delta P, \Delta G)$ is no more than (22.5\%, 20\%) and (27\%, 24\%) on \citationd and \synthetic, respectively.

\stitle{Exp-4: Efficiency of \inc for continuous sets of updates}. We evaluated \inc for a serial sets of pattern updates, data updates and simultaneous pattern and data updates vs. \optgrouprec on \citationd and \synthetic.

\etitle{(i) Pattern updates}. We generated $5$ sets of hybrid pattern updates, varying the number of updates of each set from $1$ to $7$.
We tested the average time took by \inc to finish all these sets one by one.
The results are reported in Fig.~\ref{fig-exp-patinc-multi}.

Recall that \inc adopts a lazy update policy, which definitely affects the processing time of next updates.
However, we find \inc outperforms \optgrouprec \wrt average time, when the number of hybrid  pattern updates in each set is no more than (27\%, 31.5\%)  on (\citationd, \synthetic). This verifies the effectiveness of our lazy update policy.

\etitle{(ii) Data updates}. The setting is same as above. Varying the the amount of hybrid data updates in each set from 4\% to 24\%,
the results are reported in Fig.~\ref{fig-exp-datainc-multi}.
We find that \inc outperforms \optgrouprec when hybrid data updates are no more than (24\%, 28\%) on (\citationd, \synthetic).

\etitle{(iii) Simultaneous pattern and data updates}. Using the same setting and varying the simultaneous pattern and data updates $(\Delta P, \Delta G)$ from (4.5\%, 4\%) to (27\%, 24\%) in Fig.~\ref{fig-exp-hyb-datapat-multi},
We find that \inc outperforms \optgrouprec when updates in each set are no more than (18\%, 16\%) and (22.5\%, 20\%)
on \citationd and \synthetic, respectively.
%\looseness=-1

\eat{%%%EAT
\begin{table}[h!]
%\vspace{-1ex}
\begin{center}
\begin{small}
%\vspace{-2ex}
\scriptsize
\begin{tabular}{|c|c|c|c|}
\hline
{\bf Datasets}       &  {\bf Auxiliary sizes}  &  {\bf Graph sizes}  &  {\bf Ratio} \\
\hline\hline
{\bf \citationd}            &  25MB       &        36MB    &     69.4\%   \\ \hline
{\bf \synthetic}       &  130MB       &        482MB      &     26.9\%   \\ \hline
\end{tabular}
\vspace{-1.5ex}
\end{small}
\caption{Extra space of auxiliary data structures}
\label{tab-extraspace}
\vspace{-5ex}
\end{center}
\end{table}
}%%%EAT

\stitle{Exp-5: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-extraspace}, the incremental algorithm \inc takes (25MB, 130MB) extra space to store all its auxiliary structures on (\citationd, \synthetic), which need (36MB, 482MB) space to store themselves.
That is, the auxiliary structures are light-weight, and only take (69.4\%, 26.9\%) extra space compared with the original datasets.

%\begin{table}[h!]
%\vspace{-2ex}
%\vspace{2ex}
%\begin{center}
%\begin{small}
%%\vspace{-2ex}
%\scriptsize
%\begin{tabular}{|c|c|c|}
%\hline
%{\bf Storage}       &  {\bf Citation}  &  {\bf Synthetic}   \\
%\hline\hline
%{\bf Auxiliary}            &  25MB       &        130MB           \\ \hline
%{\bf Datasets}       &  36MB       &        482MB           \\ \hline
%{\bf Ratio}           &  69.4\%     &        26.9\%          \\ \hline
%\end{tabular}
%\vspace{-1.5ex}
%\end{small}
%\caption{Physical storage}
%\label{tab-notation}
%%\vspace{-7.5ex}
%\end{center}
%\end{table}

\stitle{Summary}. From these tests, we find the following.

\sstab(1) Our graph pattern matching approach is effective at capturing the practical requirements of top-$k$ team formation.

\sstab(2) Our batch algorithm for  top-$k$ team formation is efficient,
\eg it took 110s when $|V|=1.39M$ and $|V_P|=10$.

\sstab (3) Our incremental algorithm for dynamic top-$k$ team formation is able to process continuous pattern and data updates, separately and simultaneously,
and it is more promising than its batch counterpart,
even (a) when changes are 34\% for pattern updates, 31\% for data updates, and (25\%, 22\%) for simultaneous pattern and data updates on average,
and (b) when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuously simultaneous pattern and data updates on average.

### 2017-09-25 TF-vldb2018/sec-intro.tex

\section{Introduction}
\label{sec-intro}

Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
the {\em top-$k$ team formation} problem (\teamF) is to find a list of $k$ highly collaborative teams of experts in $G$ such that each satisfies the skill requirements of the task.
Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed for \teamF,
and fall into two categories in terms of the way to improve the collaborative compatibility of team members:
 (1) minimizing team communication costs,
defined with \eg the diameter, minimum spanning tree and the sum of pairwise member distances of the induced subgraph~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}, and
(2) maximizing team communication relations,
\eg the density of the induced subgraph~\cite{GajewarS12,realTeamForm13}.
Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting that introduces a lower bound on the number individuals with a specific skill in a team, and an upper bound of the team members, respectively.

\begin{example}
\label{exm-motivation}
Consider a recommendation network $G_1$ taken from \cite{TerveenM05} as depicted in Fig.~\ref{fig-motivation-example},
in which (a) a node denotes a person labeled with her expertise, \eg project manager (\kw{PM}), software architect (\kw{SA}), software developer (\kw{SD}), software tester (\kw{ST}),
user interface designer (\kw{UD}) and business analyst (\kw{BA}),
and (b) an edge indicates the collaboration relationship between two persons, \eg ($\kw{PM_{1}}$, $\kw{UD_{1}}$) indicates $\kw{PM_{1}}$ worked well with $\kw{UD_{1}}$ within previous projects.

An HR manager may help to set up a team for developing a new software product,
and she searches $G_1$ (without dashed edges) for proper candidates.
The desired team has
(1) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
(2) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.

\eat{
One may want to look for candidate teams with existing methods,
 (1) by minimizing the {\em team diameter} \cite{Lappas09},
which returns the team with $\{\kw{BA_3}$, \kw{PM_3}, \kw{UD_4}, \kw{SA_4}, \kw{SD_4}, $\kw{ST_4}\}$,
(2) by minimizing the {\em sum of all-pair distances} of teams \cite{Kargar11},
which returns exactly the same team as (1) in this case,
or (3) by maximizing the {\em team density} \cite{GajewarS12}, which returns the team consisting of the nodes of the two connected components in $G_1$ with \kw{PM_1} and \kw{BA_3} (excluding \kw{UD_2}, \kw{PM_3}, \kw{UD_4}, \kw{SA_4}).

However, one may notice that these teams only satisfy the skill requirement, and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints. Indeed, the team found in (1) and (2) is connected by \kw{BA_3} only, and the team found in (3) has loose collaborations among its members.
Further, the capacity constraint in \cite{GajewarS12,realTeamForm13} needs to be extended to express the capacity bounds here.
That is, existing methods are not appropriate for identifying the above desired teams.
}%%%EAT

\revise{One can verify that none of existing methods suffice to identify the above desired team.
They can only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13} in search condition (1),
while cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints in search condition (2) (see details in Example~\ref{exa-teamF}).}
 \end{example}

\eat{ It is because existing methods fall short of capturing the collaboration relations between specific team members, \ie the topology constraint (condition (2)).
However, in practice, it is rather important to take the functionality of different members into consideration~\cite{MerzSeeber15};
and few of them consider the capacity constraint (in condition (1)), and even consider, they always focus on the lower bounds~\cite{GajewarS12}, which results in a large quantity.

 and the number of team members is less than the cardinality requirement of the task
One can verify none of existing methods suffice to express the above requirements.

One can find none of the teams could work well in practice: the team found by (a) and (b) is connected by only one member \kw{BA} and the number of team members is less than the cardinality requirement of the task;
and the size of the team found by (c) is too large. It is because existing methods fall short of capturing the collaboration relations between specific team members, \ie the topology constraint (condition (2)).
However, in practice, it is rather important to take the functionality of different members into consideration~\cite{MerzSeeber15};
and few of them consider the capacity constraint (in condition (1)), and even consider, they always focus on the lower bounds~\cite{GajewarS12}, which results in a large quantity.}%%%EAT

\begin{figure}[tb!]
\begin{center}
\includegraphics[scale=1.15]{./fig/motivation-example.eps}
\end{center}
\vspace{-3.5ex}
\caption{Motivation example}
\label{fig-motivation-example}
\vspace{-5ex}
\end{figure}

\eat{
A natural question is how to further capture the {\em structural and capacity constraints} in a unified model for team formation?
We essentially introduce a revision of graph pattern matching, an extension of graph simulation~\cite{infsimu95} and strong simulation~\cite{MaCFHW14}, for team formation to fill in this gap.
}%%%EAT

A natural question is how to further capture the {\em structural and capacity constraints} in a unified model for team formation?
We essentially introduce a revision of {\em graph pattern matching} for team formation to fill in this gap.

Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.  Intuitively, patterns $P$ capture the structural constraint, and we extend graph pattern matching semantics to solve the team formation problem. As shown in Fig.~\ref{fig-motivation-example},  the desired team requirement can be expressed by the pattern graph $P_1$ (ignore dashed edges), such that the nodes represent the skill requirements, the edges specify the topology constraint, and the bounds on nodes are the capacity constraint.

%Especially, {\em strong simulation} introduces duality and locality into simulation, and shows a good balance between its computational complexity and its ability to preserve graph topology~\cite{MaCFHW14}.

\vspace{1.0ex}
Finding desired teams typically needs a lot of labor efforts, and it is even common for professionals to refine search conditions multiple times in order to find ideal teams~\cite{SajjadPG12,HabibiP15}. 
Moreover, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. That is, team formation is accompanied with a highly dynamic environment.
%
\revise{However, it is often too costly to recompute top-$k$ teams from scratch in response to pattern and data updates.
These highlight the need for incremental algorithms to compute the updated top-$k$ teams.
As opposed to batch algorithms, incremental algorithms avoid re-computing from scratch by re-using previous results.
Traditional incremental algorithms for graph queries including graph pattern matching queries are proposed to compute changes in response to data updates, which has a lot of work~\cite{FanLMTWW10,FanWW13-tods,FanHT17}. 
However, the study on incremental algorithms for graph pattern updates is in its vacancy.

\eat{
Given a pattern graph $P$ and a data graph $G$, the graph pattern matching results $P(G)$ in $G$ for $P$ and changes $\Delta G$ to $G$ as input, 
the traditional incremental matching problem is to compute changes $\Delta O$ to $P(G)$ such that $P(G\oplus\Delta G)$=$P(G)\oplus \Delta O$.
Here $\oplus$ denotes applying changes $\Delta S$ to $S$, when $S$ is data graph $G$ or query result $P(G)$.
It is to improve response time by reducing computations on big $G$ to small $\Delta G$ and $\Delta O$.}%%%EAT

\begin{example}
\label{exm-motivation-inc}
Recall $P_{1}$ and $G_{1}$ in Example~\ref{exm-motivation} and continue.

\sstab{(1)} When the manager get the match result, \ie the top-$k$ teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$, 
she may find $P_1$ is too restrictive to find possible matches.
Therefore, she enters a pattern update $\Delta P_1$ on $P_1$, composed of an edge 
deletion $(\kw{SD},\kw{ST})^-$.
We denote $P_{1}\oplus\Delta P_{1}$ the updated pattern.
It is much better to derive $P_{1}\oplus\Delta P_{1}(G_{1})$ from $P_{1}(G_{1})$
than a computation for $P_{1}\oplus\Delta P_{1}$ in $G_{1}$ from scratch.
%\looseness=-1

\sstab{(2)} When a data update $\Delta G_1$ comes on $G_1$, composed of an edge insertion $(\kw{SD_3},\kw{ST_3})^+$.
Similar with (1), it is better to compute $P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.

\sstab{(3)} Even better, when it comes to the case pattern $\Delta P_{1}$ and data updates $\Delta G_{1}$ come together, it is desirable to compute $P_{1}\oplus\Delta P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.
\end{example}

This motivates us to study the {\em dynamic top-k team formation} problem (\dynteamF), to handle continuous 
pattern and data updates, separately and simultaneously.
As a basis of \dynteamF, we also investigate the incremental problem for graph pattern queries on pattern updates. 
The definition can be formulated along the same lines with the existing data incremental problem.
%different with data incremental algorithms that preserve some desirable properties that the recomputation can be {\em bounded}  by the changes in the input and output as the impact of data updates can be localized~\cite{Reps96, FanLMTWW10,FanWW13-tods,FanHT17}, 
However, devising pattern incremental algorithms is quite challenging as the impact of pattern updates is global,
due to the inherent hardness of the problem.
Despite of this, we devise an effective unified incremental approach for the \dynteamF\, problem.

\warn{To our knowledge, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting considered so far.}

\stitle{Contributions}. To this end,  we introduce a graph pattern matching approach for (dynamic) top-$k$ team formation.

\revise{
\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation problem. 
It extends existing methods by incorporating the structural and capacity constraints using pattern graphs (Section~\ref{sec-tsim}).
We formulate the dynamic top-$k$ team formation problem, to handle separate and simultaneous pattern and data updates,
in order to cope with the highly dynamic environment of team formation (Section~\ref{sec-tsim}).
\warn{To the best of our knowledge, this work gives the first investigation on pattern and simultaneous pattern and data incremental computations.} 
}

\revise{
\stab (2) We develop a \warn{quadruplicate} batch algorithm with two optimization techniques for computing top-$k$ teams via team simulation.} 
We also study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching (Section~\ref{sec-tsimAlg}).
We develop a unified approach to handling the need for both pattern and data updates.
We first prove that the dynamic top-$k$ team formation problem is unbounded even for single pattern or data updates, by extending the notion of incremental boundedness~\cite{Reps96}.
In light of this, we then propose an incremental strategy based on {\em pattern fragmentation} and {\em affected balls} to localize the effects of pattern and data updates (Sections~\ref{sec-dynamictopk}). 
We finally develop a unified incremental algorithm for dealing with separate and simultaneous pattern and data updates,
with an optimization technique with the {\em early return} property for incremental top-$k$ algorithms, an analogy of the traditional early termination property (Sections~\ref{sec-IncAlg}).

\eat{%%%%%%%%%%%%%%%%move to section 3

As opposed to batch algorithms that recompute new match results from scratch,
incremental algorithms \cite{inc-survey} have been proposed to compute new match results,
by reusing and updating previous cached results according to the changes in input.
\looseness=-1

\begin{example}
\label{exm-motivation-inc}
Recall $P_{1}$ and $G_{1}$ in Fig.~\ref{fig-motivation-example} and continue.

\sstab{(1)} When the user gets the matched teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$, she may find $P_1$ is too restrictive to find possible teams.
Therefore, she enters pattern updates $\Delta P_1$ on $P_1$, composed of an edge deletion $(\kw{SD},\kw{ST})^-$.
We denote $P_{1}\oplus\Delta P_{1}$ the revised pattern.
It is much better to derive $P_{1}\oplus\Delta P_{1}(G_{1})$ from $P_{1}(G_{1})$
than a computation for $P_{1}\oplus\Delta P_{1}$ in $G_{1}$ from scratch.
\looseness=-1

\sstab{(2)} When data updates $\Delta G_1$ come on $G_1$, composed of an edge insertion $(\kw{SD_3},\kw{ST_3})^+$.
Similarly with (1), it is better to compute $P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.

\sstab{(3)} Even better, when it comes to the case pattern $\Delta P_{1}$ and data updates $\Delta G_{1}$ come together, it is desirable to compute $P_{1}\oplus\Delta P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.
\end{example}
}%%%%%%%%EAT

\eat{%%%EAT
%Hence, there is an urgent need to study the team formation problem in a dynamic setting.
These encourage us to propose the {\em dynamic top-$k$ team formation} problem (\dynteamF),
to handle separate and simultaneous pattern and data updates.
However, the problem is non-trivial.
There has been a bunch of work on data incremental algorithms on graphs~\cite{Reps96,FanWW13-tods},
but less work on handling pattern updates is known, and furthermore less work on handling both data and pattern updates is known. The challenges comes from three aspects:
(a) the nature of pattern updates, pattern updates have significant impacts on the match results.
A unit update is likely to result in the entire change in match results, such that all previous match results need to be re-computed, which is actually a costly batch computation;
(b) the demand to design light weight and effective auxiliary data structures for the dynamic team formation problem, concerning the space consumption and the efficiency;
and (c) the requirement to design a {\em one-method-fits-two} model, to support pattern and data updates simultaneously and separately.

To solve the {\em top-$k$ team formation} problem and the {\em dynamic top-$k$ team formation} problem, several fundamental problems call for a full treatment.
(1) How to extend graph pattern matching for top-$k$ team formation to retain the properties in existing methods, and pursue more practical usage,
%such as combine capacity bound and structural constraints on matched results,
without sacrificing the efficiency?
(2) How to efficiently support pattern updates for, \eg user query adjustments on patterns, by reusing previous cached results as much as possible?
(3) How to handle data updates to meet the practical requirements?
(4) How to design a unified incremental model to handle both pattern and data updates efficiently in a simultaneous manner?
}%%%EAT

\eat{
\stitle{Contributions}. To this end,  we introduce a graph pattern matching approach for (dynamic) team formation.

\stab (1) We propose {\em team simulation} for top-$k$ team formation, a revision of traditional graph pattern matching,
which extends existing methods {\em strong simulation} for team formation by incorporating the structural and capacity constraints using pattern graphs  (Section~\ref{sec-tsim}).
We also study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching.
We finally develop an efficient cubic batch algorithm with two optimization techniques, \ie density based filtering and pattern minimization, for computing top-$k$ teams via team simulation.

\stab (2) We formulate the dynamic top-$k$ team formation problem, and develop a unified approach to handling the need for both pattern and data updates (Sections~\ref{sec-dynamictopk} \& \ref{sec-IncAlg}).
We first prove that the  problem is unbounded even for single pattern or data updates, by extending the notion of incremental boundedness~\cite{Reps96}.
In light of this, we then propose an incremental strategy based on {\em pattern fragmentation} and {\em affected balls} to localize the effects of pattern and data updates. We finally develop a unified incremental algorithm for dealing with continuous pattern and data updates, separately and simultaneously,
with an optimization technique with the {\em early return} property for incremental top-$k$ algorithms, an analogy of the traditional early termination property.
}%%%EAT

\eat{%%%EAT
\stab (3) Using real-life and synthetic graphs, we experimentally verify the effectiveness and efficiency of the static and dynamic top-$k$ graph pattern matching model and optimization techniques, for separate and simultaneous pattern and data updates, for solving \teamF\,and \dynteamF\,problems.
{\bf Add details}
}%%%EAT

\stab (3) Using real-life data (\citationd) and synthetic data (\synthetic), we demonstrate the effectiveness and efficiency of our graph pattern matching approach for (dynamic) team formation (Section~\ref{sec-expt}).
We find that (a) our method is able to identify more sensible teams than existing team formation methods \wrt \eat{three} practical measurements,
and (b) our incremental algorithm outperforms our batch algorithm, even when changes reach 34\% for pattern updates, 31\% for data updates and (25\%, 22\%) for simultaneous pattern and data updates, and when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuous simultaneous pattern and data updates, respectively.

All detailed proofs are available  in the Appendix.

\stitle{Related work}. Previous work can be classified as follows.

%\etitle{Graph pattern matching}.

 Graph simulation \cite{infsimu95} and its extensions have been introduced for graph pattern matching~\cite{FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}, in which {\em strong simulation} introduces duality and locality into simulation~\cite{MaCFHW14}, and shows a good balance between its computational complexity and its ability to preserve graph topology. Furthermore, \cite{FanCount16} already adopts capacity bounds on the edges of pattern graphs via subgraph isomorphism, and \cite{FanWWXin13} uses graph pattern matching to find single experts, instead of a team of experts. In this study, team simulation is proposed for team formation as an extension of graph simulation and strong simulation on undirected graphs with capacity constraints on pattern graphs.

%\etitle{Team formation}.

There has been a host of work on team formation by minimizing the communication cost of team members, based on the diameter, density, minimum spanning tree, Steiner tree, and sum of pairwise member distances among others \cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12,LiTongCao15}, which are essentially  a specialized class of keyword search on graphs~\cite{Aggarwal10}. Similar to~\cite{Kargar11}, we are to find top-$k$ teams. However, \cite{Kargar11} adopted Lawler's procedure \cite{Lawler1972}, and is inappropriate for large graphs. We also adopt {\em density}  as the communication cost, which shows a better performance~\cite{GajewarS12}, and further require that all team members are {\em close to each other} (located in the same balls), along the same lines as~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}. 
\revise{Except for simply minimizing the communication cost among team members, 
\cite{HuangLv16,Kargar11} consider minimizing the cost among team members and team leaders.}
Different from these work, we introduce {\em structural constraints}, in terms of graph pattern matching~\cite{FanLMTWW10,MaCFHW14}, into team formation, while retaining the capacity bounds on specific team members like~\cite{realTeamForm13,GajewarS12}.

%\etitle{Incremental computations}.

Incremental algorithms (see \cite{inc-survey,FanHT17} for a survey) have proven usefulness in a variety of applications,
and have been studied for graph pattern matching~\cite{FanLMTWW10,FanWW13-tods} and team formation \cite{ArisLuca12} as well.
However, \cite{inc-survey,FanHT17,FanLMTWW10,FanWW13-tods} only consider data updates,
and \cite{ArisLuca12} only consider continuous coming new tasks. In this work, we  deal with both pattern and data updates for team formation, and support both insertions and deletions. To our knowledge, this is the first study on pattern updates, and is the most general and practical dynamic setting considered so far.

{Query reformulation (\aka query rewriting /modification) is to generate alternative queries that may produce better answers,
and has been studied for structured queries~\cite{MottinEmpty13}, keyword queries~\cite{YaoQReform12} and graph queries~\cite{MottinGReform15}.
However, different from our study of handling pattern updates, the focus of query reformulation is not on incremental computations.

%\etitle{Top-k queries}.

Although top-$k$ queries (see~\cite{IlyasBS08} for a survey) have been studied for both graph pattern matching and team formation~\cite{Kargar11},
they have never been studied for both team formation and graph pattern matching  in a dynamic setting.

\eat{
\etitle{Query reformulation}. \textcolor{blue}{Query reformulation (\aka query rewriting/modification) is to provide users with a set of specializations of the original query that may better capture their search intent.
It has been studied for structured queries~\cite{MottinEmpty13}, keyword queries~\cite{YaoQReform12} and graph queries~\cite{MottinGReform15}.
However, they all aim at automatically providing alternative queries (\eg supergraphs~\cite{MottinGReform15}) to users,
while care less about answering the changed queries.
In this work, we focus on handling query modification from users and how to quickly return the answers based on previous answers.}
}

\eat{%%%EAT
To retain the properties in existing methods, and pursue more practical usage, we incorporate the capacity bounds, density measure and locality into graph simulation as the matching semantics.

When a user inputs a pattern graph into a system with a data graph already stored in it, and gets the match result, sometimes he or she may find that the query is not appropriate in some sense after an analysis on the result. Then the user probably makes some small adjustments on the pattern graph. However, it is expensive to recompute the matches from scratch via batch algorithm due to the slight change in pattern graph, and this comes the convenience for executing incremental graph matching, which just computes changes in the match result corresponding to the updates in pattern graph.
}%%%EAT

### 2017-09-25 TF-vldb2018/sec-related.tex

\section{Related Work}
\label{sec-related}

%We categorize the related work as follows.

\stitle{Team formation}. There has been a host of work on team formation by minimizing the communication cost of team members, defined with the diameter, density, minimum spanning tree, Steiner tree, and sum of pairwise member distances among others~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12,LiTongCao15}.
Similar to~\cite{Kargar11}, we are to find the top-$k$ teams. However,
\cite{Kargar11} adopted Lawler's procedure \cite{Lawler1972}, which makes it hard to work on large data graphs. We also adopted {\em density}  as the communication cost, which shows a better performance~\cite{GajewarS12}. However, we further require that all team members are {\em close to each other} (located in the same balls), along the same lines as~\cite{Lappas09,Kargar11}.  Moreover, graph pattern matching has been used to search single experts, instead of a team of experts~\cite{FanWWXin13}. Different from these work, we introduce {\em structural constraints}, in terms of graph pattern matching~\cite{FanLMTWW10,MaCFHW14}, into team formation.

\eat{Team formulation with minimum communication cost in  terms of the diameter and minimum spanning tree was firstly studied in~\cite{Lappas09},
followed by

Afterwards, authors of~\cite{Kargar11,Kargar11,GajewarS12,SamikKVM12} extended and proposed new communication cost metrics or incorporated more constraints. \cite{GajewarS12,realTeamForm13} incorporated the number requirements for each required skill considering real-life factors, \cite{SamikKVM12} incorporated constraints ensures that no user is overloaded by the task assignment, and \cite{LiTongCao15} proposed the team member replacement problem to efficiently find a good candidate to replace a unavailable team member.

 simply maximizing density may return a quite large team and not practical in real life. We not only require the density to be large, but also require the distance between team members to be closed, as ~\cite{Lappas09,Kargar11} do.

  and~\cite{realTeamForm13},
 we incorporate the density metric as the communication cost, and the capacity constraint into

 while the others are devoted to find only one best team. However, the adaption of Lawler's

Our work differs from the prior work in the following. By adopting graph pattern matching semantic for team formation, (1) we can assign structural constraints between different skills, while ~\cite{Lappas09,Kargar11,realTeamForm13} only require the diameter or MST or the sum of distance between members of the team to be small, which can all be ensured by our model(the diameter bound in $r$-simulation semantic).

(2) We find top-$k$ best teams which is same with ~\cite{Kargar11}, while the others are devoted to find only one best team. However, the adaption of Lawler's procedure to find top-$k$ answers ~\cite{Kargar11} adopted prohibited it to execute on large data graphs. Because it execute $k$ rounds algorithms to find $k$ answers.

(3) We adopted density as proposed in ~\cite{GajewarS12} as our communication cost metric to rank for top-$k$ results. As illustrate by them, the density based communication cost is thus performing better than the previous. However, simply maximizing density may return a quite large team and not practical in real life. We not only require the density to be large, but also require the distance between team members to be closed, as ~\cite{Lappas09,Kargar11} do.

(4) We can assign upper and lower bound for each required skill, at this point, closer to our work is ~\cite{realTeamForm13}, however, it cannot satisfy other requirements.....

(5) A common shortcoming is that previous algorithms cannot execute on large data graphs which is essential in the big data era.

Closer to this work is ~\cite{FanWWXin13}, they have adopted graph pattern matching semantic to search for experts satisfying topology constraints. However, they could not find a team of experts for a given task.

}

\stitle{Graph pattern matching}. Recently, {\em graph simulation} \cite{infsimu95} and its extensions have been introduced for graph pattern matching~\cite{FanLMTWW10,FanLMTW11,MaCFHW14,Guanfeng15}, in which {\em strong simulation} introduces duality and locality into simulation~\cite{MaCFHW14}, and shows a good balance between its computational complexity and its ability to preserve graph topology.
$R$-simulation proposed in this work is an extension of strong simulation on undirected graphs with capacity constraints on pattern graphs.

\eat{
Closer to our work is ~\cite{MaCFHW14}. It proposed strong simulation, imposing two additional constraints on graph simulation: duality and locality. It is capable of capturing the topology in graph pattern matching and can be determined in cubic time.

, via subgraph isomorphism~\cite{Ullmann76}, an \NP-complete problem. To lower its complexity, various extensions of graph simulation have been considered instead~\cite{FanLMTWW10,FanLMTW11,MaCFHW14,Guanfeng15}. Graph simulation can be determined in quadratic time. However, the low complexity may cause the extended notions fail to capture the topology of graphs, and yield false matches or too large a match relation. Closer to our work is ~\cite{MaCFHW14}. It proposed strong simulation, imposing two additional constraints on graph simulation: duality and locality. It is capable of capturing the topology in graph pattern matching and can be determined in cubic time. This work differs from strong simulation in that we combine capacity bounds on pattern nodes to find matches satisfying the capacity requirements.
}

\stitle{Incremental computations}. Incremental algorithms (see \cite{inc-survey} for a survey) have proven usefulness in a variety of areas,
and have been studied for both graph pattern matching~\cite{FanLMTWW10,FanWW13-tods} and team formation \cite{ArisLuca12}.
However, \cite{FanLMTWW10,FanWW13-tods} only consider data changes,
and \cite{ArisLuca12} only consider continuous coming new tasks. In this work, we both deal with pattern and data updates for $r$-simulation, and allow both node/edge insertions and deletions, which is a much more general setting that has not been studied in \cite{ArisLuca12,FanLMTWW10,FanWW13-tods}.

\eat{
, and
For graph pattern matching problem, ~\cite{FanLMTWW10,FanWW13-tods} have proposed incremental algorithms dealing with data changes defined in terms of graph simulation, bounded simulation and subgraph isomorphism.

%\cite{FanWW2014} investigated the issue to answer graph pattern queries using graph pattern views.
%For team formation problem, \cite{GastonMarie05} studied the team formation problem on multi-agent networks in a setting where agents could adapt their network connectivity.
\cite{ArisLuca12} proposed the online algorithms that assemble teams to deal with continuous coming tasks. team data inc.

Our work differs from the prior work in the following.
(1) \cite{FanLMTWW10,FanWW13-tods} focused on dynamic computing strategies only concerning with data changes, while we provided a unified framework to deal with both data and pattern changes.
(2) For pattern change issue, \cite{FanWW2014} focused on accelerating the process to answer new queries with stored graph views, which are not capable to handle pattern changes.
%\cite{ArisLuca12} focussed more on the load balancing aspect when dealing with a series of tasks. While we focus on immediately answering queries of users with given pattern changes to the original patterns.
(3) \cite{FanLMTWW10,FanWW13-tods} have proved there exist bounded algorithms for single-data-edge deletion updates based on conventional incremental algorithms. However, existing approaches based on conventional incremental algorithms are proved unbounded when pattern incremental is concerned for any pattern update. Thus, we proposed a partition based framework comes with theoretical bounds in terms of \affballsx and \affballaccs that are essential for any incremental algorithms.
}

\stitle{Top-k queries}. Although top-$k$ queries (see~\cite{IlyasBS08} for a survey) have been investigated for both graph pattern matching and team formation~\cite{FanWW2013,Kargar11}.
However, to our knowledge, neither team formation nor graph pattern matching  has been studied in a dynamic setting for top-$k$ queries.

\eat{
There has been works exploring top-$k$ query answering in both graph pattern matching and team formation~\cite{FanWW2013,Kargar11}.
\cite{FanWW2013} studied the diversified top-$k$ graph pattern matching problem defined in terms of simulation.
\cite{Kargar11} designed a procedure to find top-$k$ teams, which is an adaption of Lawler's procedure~\cite{Lawler1972} for calculating the top-$k$ answers to discrete optimization problems.
This work differs from them in that besides finding top-$k$ teams in a static case, we consider finding top-$k$ teams in a pattern and data incremental manner.
Closer to this work is \cite{EVMK12}, which devoted to discover top-$k$ dense subgraphs in a stream of graphs.
It proposed a procedure with early termination property, a superior property which can accelerate the top-$k$ computing process.
However, they utilize a sliding window to find top-$k$ dense subgraphs only contained in the window, such that their top-$k$ procedure is similar with the static case.
It is difficult to use early termination for incremental algorithms. We define the {\em early return property}, an analogy to the early termination property for traditional top-$k$ algorithms and prove that our dynamic framework pertains this property.
}

\eat{

\stitle{Team formulation}. finding a team of exports
group recommendations
\stitle{Keywords on Graphs}.
\stitle{Graph pattern matching}.
Subgraph Isomorphism; Graph Simulation; Dual Simulation; strong simulation.
\stitle{Graphs density}.
\stitle{Diversity}.

\stitle{Graph pattern matching}.
Graph pattern matching is often defined according to subgraph isomorphism~\cite{Aggarwal10,Galla06}, an \NP-complete problem. However, it is too restrictive to catch sensible matches in most cases, as it requires match subgraphs to have exactly the same topology as the pattern graph. Subsequently, to reduce the time complexity, graph simulation~\cite{ccs} has been adopted for pattern graph matching which can be determined in quadratic time. It devotes to preserve the child relationship of pattern graph, but it may fail to capture the topology of graphs and yield false matches or too large a match relation. To rectify these problems, strong simulation~\cite{MaCFHW11} imposes two additional constraints on graph simulation: the duality to preserve both parent and child relationships, also referred to as dual simulation~\cite{MaCFHW11}, and the locality to eliminate excessive matches. It is capable of capturing the topology in graph pattern matching and can be determined in cubic time.

\stitle{Team formulation}.
Lappas et al.~\cite{Lappas09} is the first to consider team formulation problem while minimizing the communication cost. By formalizing communication cost as diameter and the total weights of minimum spanning tree(MST) induced by the team, Lapps et al have proved the problem is \NP-hard, and they have proposed an approximation algorithms for minimizing the diameter with a guarantee 2 and a greedy algorithm with no approximation ratio for MST. Authors of~\cite{Kargar11} proposed a new communication cost function of minimizing the sum of distances between each pair of skill holders and provided a 2-approximation algorithm. They also introduced the problem of finding a team of experts with a leader while considering another new communication cost function of minimizing the the sum of distance between the leader and each of the skill holders in the team. Authors of~\cite{GajewarS12} generalized this problem to the case where for each required skill, multiple  experts possessing the skill are desired.
%\cite{Chengte10} utilized MST as the metric of communication cost, but they have proposed algorithms with no approximation ratio.
In \cite{GajewarS12}, density based measures are used as objectives, they have proposed a 3-approximation algorithm for single skill team formation problem(sTF), and  greedy algorithm with no approximation ratio for multiple skill team formation problem(mTF).

\stitle{Graphs density}.
As mentioned above, \cite{GajewarS12} has utilized density as a measure of collaborative compatibility, and the problem of finding densest subgraphs has been well-studied these years. Given a undirected data graph, finding a subgraph with maximum density~\cite{Goldberg84} can be solved optimally in polynomial time. However when there is a size constraint specified, the densest-k-subgraph problem, namely, finding a densest subgraph with exactly $k$ vertices becomes \NP-hard~\cite{FeigeML01,FeigePK01}. The algorithm developed by Feige et al. achieves the best approximation ratio for now~\cite{FeigePK01}. Andersen et al~\cite{Andersen09} considered the problem of finding dense subgraphs with specified upper and lower bounds on the number of vertices, the densest-at-least-k-subgraph (Dalks) problem and the densest-at-most-k-subgraph (Damks) problem. Khuller et al~\cite{Khuller09} have shown that Dalks is \NP-complete. Andersen et al have shown that Damks is nearly as hard to approximate as Dks and gave constant factor approximation algorithms for Dalks.

}

### 2017-09-25 TF-vldb2018/sec-tsim.tex

\newcommand{\grouprec}{\kw{batch}}
\newcommand{\optgrouprec}{\kw{batch}}
%\newcommand{\grouprecopt}{\kw{kTeamFormOpt}}
\newcommand{\minp}{\kw{minP}}
\newcommand{\rgraphsim}{\kw{undigSim}}
\newcommand{\incsim}{\kw{incSim}}

\section{Dynamic Team Formation}
\label{sec-tsim}

\revise{
We first propose {\em team simulation}, an extension of traditional graph pattern matching.
We then formally introduce the {\em top-$k$ team formation} problem via team simulation.
We finally present the {\em dynamic top-$k$ team formation} problem.}

\eat{
In this section, we first present basic notations of graphs, and then propose team simulation, an extension of traditional graph pattern matching.
We finally formally introduce the top-$k$ team formation problem via team simulation, and propose a cubic algorithm with two optimization techniques.

\subsection{Data Graphs and Pattern Graphs}
\label{subsec-graphdefs}

\stitle{Data graphs}.
A {\em data graph} is a labeled undirected graph $G(V, E, l)$, where
(1) $V$ is a finite set of nodes;
(2) $E \subseteq V \times V$, in which $(u, u')$ or $(u', u)$ $\in E$ denotes an undirected edge between nodes $u$ and $u'$; and
(3) $l$ is a total labeling function that maps each node in $V$ to a set of labels.

%; and(4) $w$ is a total weight function that maps each edge in $E$ to a positive rational number.

Intuitively, the node labels carry the content of the node, \eg skills, keywords, blogs, rating~\cite{AmerYahiaBB07}.
The edges specify the affinity or collaborative compatibility among nodes~\cite{GajewarS12}.

\stitle{Pattern graphs}.
A {\em pattern graph} (or simply pattern) is an undirected graph $P(V_P$, $E_P$, $l_P$, $f_P)$, in which
(1) $V_P$ and $E_P$ are the set of nodes and the set of edges, respectively;
(2) $l_P$ is a total labeling function that maps each node in $V_P$ to a single label; and
(3) $f_P$ is a total capacity function such that for each node $u\in V_P$, $f_P(u)$ is a closed interval $[x, y]$, where $x\le y$ are non-negative integers.

Intuitively, $f_P(u)$ specifies a range bound for node $u$,
indicating the required quantity for the matched nodes in data graphs.
Note that for traditional graph patterns~\cite{Galla06, b-matching,FanLMTWW10,FanCount16}, bounds are typically carried on edges, not on nodes.
\looseness=-1

\begin{example}
\label{exm-pattern}
Consider pattern graph $P_1$ and data graph $G_1$ in Fig.~\ref{exm-motivation}. Observe that there is a capacity bound on each node in $P_1$.
For example, capacity bound [1,2] on node \kw{SD} in $P_1$ indicates in the match result,
there should be at least one and at most two nodes matched with \kw{SD}.
\end{example}

\stitle{Remarks}. We assume \kwlog~that pattern graphs are connected, as a common practice.
We also simply denote data graphs $G(V, E, l$) as  $G(V, E)$ and pattern graphs $P(V_P$, $E_P$, $l_P$, $f_P)$ as $P(V_P$, $E_P)$, respectively.
Furthermore, the size $|G|$ of data graphs $G$ (resp. $|P|$ of pattern graphs $P$) is the total number of nodes and edges in $G$ (resp. $P$).
}%%%EAT

\eat{%%%%%%%%%%%%%%%%
We shall use the following notation

\etitle{Subgraphs}.
Graph $H(V_s, E_s,  l_{H})$ is a {\em subgraph} of data graph $G(V, E, l)$, denoted as $G[V_s, E_s]$, if
(1) for each node $u\in V_s$, $u\in V$ and $l_{H}(u) = l(u)$, and
(2) for each edge $e\in E_s$, $e\in E$. % and $w_{H}(e) = w(e)$.
That is, subgraph $G[V_s, E_s]$ only contains a subset of nodes and a subset of edges of graph $G$.

We also denote subgraph $G[V_s, E_s]$ as subgraph $G[V_s]$, if $E_{s}$ is exactly

Similarly, we can define {\em subgraphs for pattern graphs}, which further requires the preservation of the node capacity.

\etitle{Induced subgraphs}. An {\em induced subgraph} $G_{s}(V_{s}, E_{s})$ is composed of vertices $V_{s}$ who is a subset of the vertices $V$ of graph $G(V, E)$, and together with the edge set $E_{s}$ whose endpoints are both in $V_{s}$ in $G(V, E)$.

\etitle{Subpatterns}.
Pattern $Q(V_s, E_s,  l_{q}, f_{q})$ is a {\em subpattern} of pattern $P(V_p$, $E_p$, $l_p$, $f_p)$, denoted as $P[V_s, E_s]$, if
(1) for each node $u\in V_s$, $u\in V$, $l_{q}(u) = l_p(u)$ and $f_{q}(u) = f_p(u)$, and
(2) for each edge $e\in E_s$, $e\in E$. % and $w_{H}(e) = w(e)$.
That is, subpattern $G[V_s, E_s]$ only contains a subset of nodes and a subset of edges of pattern $P$.}

% \etitle{Connected components}.
% A {\em connected component} of a graph is a subgraph in which any two nodes are connected to each other by undirected paths,
% and which is only connected to the nodes of itself, \ie a connected component is maximal.
% A graph that is itself connected has exactly one connected component, which is the entire graph.

\eat{%%%%%%%%%%%
\etitle{Neighbors}. We say that node $u'$ is a {\em neighbor} of node $u$ if there is an edge between $u$ and $u'$ in a data or pattern graph.

\etitle{Paths}.
A {\em simple path} (or simply a {\em path}) $\rho$ is a sequence of nodes $v_1/\ldots/v_n$ with no repeated nodes, and, moreover, for each $i\in[1, n-1]$, $(v_i$, $v_{i+1})$ is an edge in $G$. The {\em length} of a path $\rho$ is the number of edges in $\rho$.

A graph is {\em connected} if for each pair of nodes, there exists a  path connecting them.

\etitle{Distances}. Given two nodes $v$ and $v'$ in a graph $G$, the {\em  distance} from $v$ to $v'$,
denoted by $\dist(v,v')$, is  the shortest length of all {\em paths}
from $v$ to $v'$ in $G$.
}

\eat{%%%%%%%%%%
\etitle{Diameter}. The {\em diameter} of a connected graph $G$,  denoted by $\diameter{G}$, is the longest shortest distance of all pairs of nodes in $G$, \ie $\diameter{G}$ = $\kw{max}(\kw{dis}(v,v'))$ for all nodes $v,v'$ in $G$.
}%%%%%%%%%%%%%%

\eat{
\etitle{Distances}. The {\em length} of a path $\rho$ is
the sum of the weights of its constituent edges, \ie $\sum_{i=1}^{n-1} w(v_i, v_{i+1})$.

Given two nodes $v, v'$ in a graph $G$, the {\em distance} from $v$ to $v'$,
denoted by $\dist(v,v')$, is the length of the shortest {\em path}
from $v$ to $v'$ in $G$.
}

%\vspace{-4ex}
\subsection{Pattern Matching for Team Formation}
\label{subsec-extsim}

\revise{
We first extend pattern graphs of traditional graph pattern matching to carry capacity requirements,
and then define team simulation on undirected graphs.}
%We then redefine strong simulation on directed graphs, originally defined on directed graphs~\cite{MaCFHW14}.}

We start with basic notations.

\stitle{Data graphs.} A {\em data graph} is a labeled undirected graph $G(V$, $E$, $l)$, where $V$ and $E$ are the sets of nodes and edges, respectively; and $l$ is a total labeling function that maps each node in $V$ to a set of labels.

\stitle{Pattern graphs}.
A {\em pattern graph} (or simply pattern) is an undirected graph $P(V_P$, $E_P$, $l_P$, $f_P)$, in which
(1) $V_P$ and $E_P$ are the set of nodes and the set of edges, respectively;
(2) $l_P$ is a total labeling function that maps each node in $V_P$ to a single label; and
(3) $f_P$ is a total capacity function such that for each node $u\in V_P$, $f_P(u)$ is a closed interval $[x, y]$, where $x\le y$ are non-negative integers.

Intuitively, $f_P(u)$ specifies a range bound for node $u$,
indicating the required quantity for the matched nodes in data graphs.
Note that for traditional patterns~\cite{Galla06, b-matching,FanLMTWW10,FanCount16}, bounds are typically carried on edges, not on nodes.

We also also denote data and pattern graphs as $G(V$, $E)$ and $P(V_{P}$, $E_{P})$ respectively. The size of $G$ (resp. $P$), denoted by $|G|$ (resp. $|P|$), is defined to be the total number of nodes and edges in $G$ (resp. $P$).

%We define $r$-simulation by extending graph simulation~\cite{infsimu95,FanLMTWW10,MaCFHW14} on undirected graphs  and introducing capacity constraints.

\eat{As strong simulation is an extension of graph simulation, which is also defined on directed graphs~\cite{infsimu95,FanLMTWW10}, 
We now redefine graph simulation on undirected graphs. Consider a pattern graph $P(V_P$, $E_P)$ and a data graph $G(V$, $E)$.
}%%%EAT

We now redefine graph simulation on undirected graphs, which is originally defined on directed graphs~\cite{infsimu95,FanLMTWW10}. Consider pattern graph $P(V_P$, $E_P)$ and data graph $G(V$, $E)$.

\stitle{Graph simulation}. Data graph $G$ {\em matches} pattern graph $P$ via
graph simulation, denoted by $P \eps G$, if there exists a binary {\em match relation} $\Reps \subseteq V_P \times V$ in $G$ for $P$ such that

\vspace{0.5ex}
\ni
(1) for each $(u, v) \in \Reps$, the label of $u$ matches one label in the label set of $v$, \ie $l_{P}(u) \in l(v)$; and

\vspace{0.5ex}
\ni
(2) for each node  $u\in V_P$, there exists $v\in V$ such that
(a) $(u, v) \in \Reps$, and
(b) for each adjacent node $u'$ of $u$ in $P$, there exists a adjacent node $v'$ of $v$
in $G$ such that $(u',v') \in \Reps$.

For any $G$ that matches $P$, there exists a {\em unique maximum} match relation via graph simulation~\cite{infsimu95}.

We then introduce the notions of balls and match graphs.

%While there may be multiple match relations in a graph $G$ for a pattern graph $P$,
%there exists a unique {\em maximum} match relation $\Reps_m$ in $G$ for $P$ such that for any match relation $R$ in $G$ for $P$, $\Reps \subseteq \Reps_m$,

\eat{%%%EAT
Intuitively, graph simulation preserves the label match and
neighborhood relationships between pattern graphs and the matched data graphs~\cite{FanLMTWW10,MaCFHW14}.

Following from \cite{FanLMTWW10,MaCFHW14}, the revised graph simulation above is well-defined, as shown below.
%Following from \cite{FanLMTWW10,MaCFHW14}, it is easy to know that the graph simulation revised above has the following.

\begin{prop}
\label{prop-sim-maximum-match}
For any data graph $G$ and pattern graph $P$  such that $P\eps G$, via graph simulation, there is a unique maximum match relation in $G$ for $P$.
\end{prop}
}%%%EAT

\etitle{Balls}. For a node $v$ in data graph $G$ and a non-negative integer $r$,
the {\em ball} with {\em center} $v$ and {\em radius} $r$  is a subgraph of $G$,
denoted by $\ball{[v, r]}$, such that (1) all nodes $v'$ are in $\ball{[v, r]}$, if
the number of hops between $v'$ and $v$, $\hop(v', v)$, is no more than $r$, and (2) it has exactly the edges
appearing in $G$ over the same node set.

\eat{%%EAT
Intuitively, a ball is a connected graph such that all node pairs have bounded hops.
Indeed, as observed in~\cite{Buchan2004}, when social distance increases, the
closeness of relationships decreases and the  relationships may become
irrelevant. Hence it often suffices in practice to consider only those
matches of a pattern graph that fall in a small ball.
}%%%EAT

\etitle{Match graphs}. The {\em match} graph $\wrt$ a binary relation $\Reps\subseteq V_P\times V$ is a subgraph $G_s$ of data graph $G$, in which
(1)  a node $v\in V_s$ if and only if it is in $\Reps$, and
(2) it has exactly the edges
appearing in $G$ over the same node set.

Intuitively, the match graph $G_s$ $\wrt$ $\Reps$ is the induced subgraph of
$G$ such that its nodes play a role in $\Reps$.

\eat{%%%%EAT
\stitle{Induced match graphs}. Consider a binary relation $\Reps\subseteq V_q\times V$.
The {\em induced match} graph $\wrt$ $\Reps$ is a induced subgraph $G[V_s, E_s]$ of $G$, in which
(1) a node $v\in V_s$ if and only if it is in $\Reps$, and
(2) an edge $(v,v')\in E_s$ if and only if $v$ and $v'$ are in $\Reps$.
%
Intuitively, the induced match graph $G[V_s, E_s]$ $\wrt$ $\Reps$ is the induced subgraph of $G$ such that each of its nodes plays a role in $\Reps$, together with the adjacent edges in $G$.
}%%%%%%%%%EAT

We are now ready to define team simulation, by extending graph simulation to incorporate the locality constraints enforced by balls, and the capacity bounds carried by patterns.
\looseness=-1

%\vspace{-1ex}
\stitle{Team simulation}. Data graph $G$ {\em matches} pattern $P$  via
team simulation \wrt a radius $r$, denoted by $P \eeps G$, if
there exists a {\em ball} $\ball{[v, t]}$ ($t \in [1,r]$, $t \in Z$) in $G$, such that

\vspace{0.5ex}
\ni(1) $P\eps \ball{[v, t]}$, with the maximum match relation $\Reps$ and the match graph $G_s$ $\wrt$ $\Reps$; and

\vspace{0.5ex}
\ni(2) for each node $u\in V_P$, the number of nodes $v\in V_s$  with $(u, v)\in \Reps$ falls into $f_P(u)$.

\vspace{0.5ex}
We refer to  $G_s$ as a {\em perfect} subgraph of $G$ \wrt $P$.

Intuitively, (1) pattern graphs $P$ capture the structural and capacity constraints, and (2) a perfect subgraph $G_s$ of pattern $P$ corresponds to a desired team, which is required to satisfy the following conditions:
(a) $G_s$ itself is located in a ball $\ball{[v, t]}$  where $t \in [1,r]$ as a match graph; and
(b) $G_s$ satisfies the capacity constraints carried over pattern $P$.

\begin{example}
\label{exm-rsimulation}
Consider $P_1$ and $G_1$ in Fig.~\ref{exm-motivation}.
When team simulation with $r=2$ is adopted, $P_1$ matches $G_1$ as there is a perfect subgraph in $G_1$,
\ie the connected component of $G_1$ containing $\kw{PM_{1}}$, which resides in ball
$\ball{[\kw{PM_1}, 2]}$.
It maps \kw{PM}, \kw{BA}, \kw{UD}, \kw{SA}, \kw{SD} and \kw{ST} in $P_1$ to \kw{PM_1}, \kw{BA_1}, \{\kw{UD_1}, \kw{UD_2}\}, \{\kw{SA_1}, \kw{SA_2}\}, \{\kw{SD_1}, \kw{SD_2}\} and \{\kw{ST_1}, \kw{ST_2}\}, respectively.

One can easily verify that
(a) $P_1\eps \ball{[\kw{PM_{1}}, 2]}$, and the ball is exactly the match graph here,
and (b) the capacity bounds on all pattern nodes are satisfied.
\end{example}
\looseness=-1

\eat{%%%170720
\stitle{Remarks}.
(1) Graph simulation is a special case of team simulation on undirected graphs,
when the capacity on each pattern node is $[1, +\infty]$, and $r$ is no less than the diameter of data graphs.
%
(2) Further, strong simulation is also a special case of team simulation on undirected graphs,  when the capacity on each pattern node is $[1, +\infty]$,
$r$ is equal to the diameter of pattern graphs, and match graphs only involve with those edges matching edges in pattern graphs.
}%%%EAT170720

\revise{
\stitle{Remarks}.
(1) Team simulation differs from graph simulation and strong simulation in the existence of capacity bounds on pattern graphs and its ability to capture matches on undirected graphs.
%
(2) As for locality constraint, different from strong simulation that requires the matched nodes to locate in a ball with a fixed given radius, team simulation adopts a more natural setting that the radius of the balls is flexible, only less than a user specified upper bound.

%(2) Graph simulation (resp. strong simulation) is a special case of team simulation on undirected graphs when the capacity on each pattern node is $[1, +\infty]$, and $r$ is no less than (resp. equal to) the diameter of data graphs (resp. pattern graphs).

}

\eat{%%%EAT
\stitle{Remarks}.
(1) Graph simulation is a special case of (1) team simulation for undirected graphs,
when the capacity on each pattern node is $[1, +\infty]$ and $r$ is no less than the diameter of data graphs.
%
(2) Graph simulation~\cite{FanLMTWW10} and dual simulation~\cite{MaCFHW14} are equal on undirected graphs.
Hence, many good properties of dual simulation naturally carry over to graph simulation on undirected graphs.
%
(3) {\bf The difference of matched graphs between strong simulation and T-simulation.}
}%%%EAT

%and also a special case of (2) subgraph isomorphism, when the labels on pattern nodes are different from each other and the capacity on each pattern node is $[1, 1]$.

%(1) Graph simulation and its extensions were originally proposed on directed graphs.
%They were introduced for social networks analysis~\cite{BrynielssonHKMS10}, and for graph pattern matching~\cite{FanLMTWW10,FanLMTW11} due to its low \PTIME
%computational complexity~\cite{infsimu95}.

\eat{%%%%%%%%

When given a pattern graph, we first make a examination on it ensuring that there exist data graphs in which we can find matches using the pattern graph. If the answer is true, we can execute the following computing work. Otherwise, we require the user to retype in another pattern graph.
}

\eat{%%%170720
\begin{figure}[tb!]
%\vspace{-1ex}
\begin{center}
\includegraphics[scale=1.28]{./fig/consistency_motivation.eps}
\end{center}
\vspace{-3ex}
\caption{Pattern graphs}
\vspace{-4ex}
\label{fig-consistency-example}
\end{figure}

\stitle{Pattern satisfiability}.
We say that a pattern $P$ is {\em satisfiable} iff there exists a data graph $G$ such that $P \eeps G$.

Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
pattern graphs may be unsatisfiable for team simulation, due to the presence of capacity constraints enforced on patterns. We illustrate this with an example below.
%\looseness=-1

\begin{example}
\label{exm-consistency}
\ni(1)  Consider pattern $P_2$ in Fig.~\ref{fig-consistency-example}.
One can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $u$ in $G$, if $u$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.

\sstab(2) Pattern $P_1$ in Fig.~\ref{exm-motivation} is satisfiable as $P_1 \eeps G_1$.
\end{example}

The good news is that checking the satisfiability of pattern graphs can be done in low polynomial time.

\begin{prop}
\label{prop-pattern-consistency}
The satisfiability of patterns $P$ can be checked in $O(|P|^2)$ time.
\end{prop}

\proofS By treating $P$ as both data and pattern graphs, compute the maximum match relation $M$ in $P$ for $P$, via graph simulation.
Indeed, pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. Observe that the size of $M$ is bounded by $|P|^2$.
\eop

Pattern graphs are typically small, and we only consider  satisfiable patterns in the sequel, by Proposition~\ref{prop-pattern-consistency}.
}

\subsection{Top-k Team Formation}
\label{subsec-teamF}

 Given $P$, $G$ and two positive integers $r$, $k$, the {\em top-$k$ team formation} problem, denoted as \teamF{(P, G, k)},
is to find a list $L_{k}$ of $k$ perfect subgraphs (\ie teams) with the top-$k$ largest density in $G$ for $P$, via team simulation.
\looseness=-1

Here the {\em density}\, $\density{G}$ of graph $G(V, E)$ is $|E|/|V|$, where $|E|$ and $|V|$ are the number of edges and the number of nodes respectively, \revise{as commonly used in data mining applications~\cite{maximumDenseSubgraph,EVMK12}}.
Intuitively, the larger $\density{G}$ is, the more collaborative a team is.
In this way, not only the two objective functions of existing team formation methods are preserved,
\ie the locality retained by balls and the density function in selecting top-$k$ results,
but also the relationships among members and the capacity constraint on patterns.

\revise{
\begin{example}
\label{exa-teamF}
Consider $P_1, G_1$ in Fig.~\ref{exm-motivation} and $r=2$.
We simply set $k=1$, as most existing algorithms for \teamF{} only compute the best team, instead of top-$k$ teams.

One may want to look for candidate teams with existing methods, satisfying the search conditions in Example \ref{exm-motivation}:
(a) by minimizing the {\em team diameter} \cite{Lappas09},
which returns the team with $\{\kw{BA_3}$, \kw{PM_3}, \kw{UD_4}, \kw{SA_4}, \kw{SD_4}, $\kw{ST_4}\}$;
(b) by minimizing the {\em sum of all-pair distances} of teams \cite{Kargar11},
which returns exactly the same team as (a) in this case;
or (c) by maximizing the {\em team density} \cite{GajewarS12}, which returns the team consisting of the nodes of the two connected components in $G_1$ with \kw{PM_1} and \kw{BA_3} (excluding \kw{UD_2}, \kw{PM_3}, \kw{UD_4}, \kw{SA_4}).

However, one may notice that these teams only satisfy the skill requirement, \ie the search condition (1) in Example \ref{exm-motivation}, and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints. 
Indeed, the team found in (a) and (b) is connected by \kw{BA_3} only, and the team found in (c) has loose collaborations among its members.
That is, existing methods are not appropriate for identifying the the desired teams.

When team simulation is adopted, it returns the perfect subgraph in Example \ref{exm-rsimulation} with its density = 1.4,
satisfying both search condition (1) and (2), better than the teams found by the existing methods as shown above.
\end{example}}

\eat{%%%EAT
\sstab
(a) Algorithm \mindia~\cite{Lappas09} is to find a team with the {\em minimum diameter}, and returns $\{\kw{BA_3}$, \kw{PM_3}, \kw{UD_4}, \kw{SA_4}, \kw{SD_4}, $\kw{ST_4}\}$.

\sstab
(b) Algorithm \minsumdis~\cite{Kargar11} aims at minimizing the sum of all-pair distances, which is an extension of \mindia, and it returns exactly the same team as \mindia in this case.

\sstab
(c) Algorithm \denalk~\cite{GajewarS12} is to find a team with the {\em largest density}, and
returns the subgraph consisting of the two connected components of $G_1$ containing \kw{PM_1} and \kw{BA_3} respectively (excluding \kw{UD_1},\kw{PM_3},\kw{UD_4},\kw{SA_4}), whose density is 1.5.
%Indeed, larger density always results in a larger quantity.

\sstab
(d) Our team simulation returns the perfect subgraph in Example \ref{exm-rsimulation} with its density = 1.4 as the best team.

One can see that only team simulation captures the topology, cardinality and collaboration requirements of teams.
}%%%EAT

\eat{%%%EAT170720
\begin{figure}[t!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule
\vspace{-3ex}
\mat{0ex}{
\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $k, r$.\\
{\sl Output:\/} The list $L_{k}$ of top-$k$ teams\\
\sstab \bcc \hspace{1ex} \= $L_{k} := \emptyset$;\\
\icc \> \For each ball $\ball{[v,r]}$ in $G$ \Do\\
\icc \>\hspace{2ex}\= $G_s$ := \rgraphsim$(P, \ball{[v,r]})$;\\
\icc \>\> \If $\density{G_s}>$ the density of the $k$-th result in $L_{k}$ \Then\\
%\icc \>\> \If $\density{G_s}>$ the density of $kth$ result in $L_{k}$ and there exists\\
%     \>\>\hspace{0.5ex}   no $G'_s$ in $L_{k}$ that is same with $G_{s}$ \Then\\
\icc \>\>\hspace{2ex}\= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$;\\
\icc \> \Return $L_{k}$.
}

\vspace{-4ex} \myhrule
}
\end{center}
\vspace{-3ex}
\caption{Algorithm \grouprec} \label{alg-grouprec}
\vspace{-4ex}
\end{figure}

We now present an algorithm for \teamF{} via team simulation.

\stitle{Algorithm for Top-k Team Formation.} Given $P$, $G$, and two integers $r$ and $k$, an algorithm, referred to as \grouprec, is shown in Fig.~\ref{alg-grouprec}.
\grouprec is to find the set of perfect subgraphs $G_s$ by inspecting those balls $\ball{[v, r]}$ centered at each node $v$ of $G$, and returns the top-$k$ densest ones.
It computes the perfect subgraph $G_s$ of $P$ in the ball $\ball{[v,r]}$ via team simulation by invoking \rgraphsim(lines 2-3).
Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10},
by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.
In the process, \grouprec maintains the top-$k$ non-repeated perfect subgraphs with current top-$k$ largest density (lines 4-5), and returns them when all balls are processed (line 6).

\begin{example}
\label{exa-alg-batch} Consider $r=2$ and $k=2$.

\sstab(1) For $P_1$ and $G_1$ (ignore dashed edges) in Fig.~\ref{fig-motivation-example},
 \grouprec returns the team found in Example~\ref{exm-rsimulation} as its only answer.

\sstab(2) For $P_1$ and $G_1$ (with dashed edges), \grouprec returns the team in (1) as the best,
and the connected component containing \kw{PM_2} with its density = 1 as the second best.
\end{example}

\stitle{Correctness \& complexity analyses}. The correctness of algorithm \grouprec is assured by the following.
(1) There is a unique perfect subgraph in each ball of $G$.
(2) The correctness of \rgraphsim can be verified along the same lines as for simulation~\cite{infsimu95}.
(3) The list $L_{k}$ always maintains the current top-$k$ teams with largest density.
It takes $O(|V||P||G|)$ time to compute team simulation for all balls,
and $O(|V|\cdot(|V_{G_s}|^2+|G_s|))$ time to maintain the top-$k$ teams.
Thus \grouprec is in $O(|V|\cdot(|P||G|+|V_{G_s}|^2))$ time.
}%%%EAT170720

\subsection{Dynamic Top-k Team Formation}
\label{subsec-dynteamF}

We next introduce dynamic top-$k$ team formation.
%For convenience, the notations used are summarized in Table~\ref{tab-notation}.

\stitle{Pattern updates}. There are five types of pattern updates:
%
(1) {\em edge insertions} connecting nodes in $P$,
%
(2) {\em edge deletions} disconnecting nodes in $P$,
%
(3) {\em node insertions} attaching new nodes to $P$,
%
(4) {\em node deletions} removing nodes from $P$, and
%
(5) {\em capacity changes} adjusting the node capacities in $P$,
%
while $P$  remains connected in all cases.

\stitle{Data updates}. There are four types of data updates, which can be
defined along the same lines as the first four types of pattern updates.
Further, different from pattern updates, there is no need to keep $G$ connected for data updates.

\stitle{Dynamic top-$k$ team formation}. Given $P$, $G$, two positive integers $r$, $k$, the list $L_{k}(P,G)$ of top-$k$ perfect subgraphs for $P$ in $G$,
a set of pattern updates $\Delta P$ and a set of data updates $\Delta G$,
the {\em dynamic top-k team formation} problem, denoted by \dynteamF{(P, G, k, L_{k}, \Delta P, \Delta G)},
is to find a list of $k$ perfect subgraphs with the top-$k$ largest density for $P\oplus\Delta P$ in $G\oplus\Delta G$, via team simulation.

It is worth mentioned that the \dynteamF{} problem covers a broad range of dynamic conditions,
\ie handling continuous separate and simultaneous pattern and data updates. 
Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$.
 $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.

\eat{
\begin{example}
\label{exm-dyn-team}
Recall $P_1$, $G_1$, $\Delta P_1$ and $\Delta G_1$ in Example \ref{exm-motivation-inc} (3), and set $r=2$ and $k=2$.
When get the top-$2$ teams for $P_1$ in $G_1$, \ie $L_k(P_1,G_1)$,
\dynteamF{} is to find the top-$2$ teams for $P_{1}\oplus\Delta P_{1}$ in $G_{1}\oplus\Delta G_{1}$ via team simulation.
\end{example}}%%%EAT

\eat{%%%EAT170720
\subsection{Optimization Techniques}
\label{subsec-batch-opt}
%We next prove there exists a better way to find top-$k$ perfect subgraphs. Two optimization techniques are provided.
We next develop two optimizations for algorithm \grouprec.
%\looseness=-1

\stitle{Density based filtering}. This technique allows algorithm \grouprec to compute the top-$k$ perfect subgraphs \wrt $P$ without necessarily computing team simulation for all balls in $G$. The important issue is how can tell whether a ball has the possibility to have one of the final top-$k$ results.
%If the answer is yes, we should check team simulation for that ball; Otherwise, we just skip the ball to the remaining balls.
The idea is, given a ball $\ball{[v,r]}$ in $G$, we calculate the upper bound of $\density{\hat{G}_s}$,
where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
If the bound is larger than the current $k$-th result, \ie there is possibility the final answer resides in the ball, compute team simulation in it \wrt $P$;
Otherwise, skip the ball to the remaining balls to avoid redundant team simulation computing.

The problem here is how to efficiently compute the upper bound of $\density{\hat{G}_s}$ for each ball in $G$.
As the best densest subgraph algorithms are in $O(|\ball{[v,r]}|^3)$ time \cite{maximumDenseSubgraph}, which is costly,
we utilize an important result in~\cite{EVMK12}, shown as follows.

\begin{lemma}
\label{lemma-approximation-bound}
Let $\density{H_{c}}$ and $\density{H_{d}}$ be the density of the maximum core  $H_{C}$  and the  densest subgraph $H_{d}$ of graph $H$. Then (1) $\density{H_{c}}\leq \density{H_{d}} \leq 2*\density{H_{c}}$; and (2) there exists an algorithm that computes $\density{H_{c}}$ in $O(|E_H|)$ time~\cite{EVMK12}.
\end{lemma}

Here the maximum core $H_{C}$ of a graph $H$ is a subgraph of $H$ whose node degree is at least $\rho$, where $\rho$ is the maximum possible one. By Lemma~\ref{lemma-approximation-bound}, we use $2*\density{H_{c}}$ as the density upper bound for filtering unnecessary balls.

\stitle{Pattern minimization}.
Minimizing patterns is an effective way for improving the efficiency of querying graphs.

%\looseness=-1

We say two pattern graphs $P$ and $P'$ are {\em equivalent via team simulation}, denoted by $P\equiv P'$, iff they return the same result on any data graph $G$ via team simulation. We say $P$ is {\em minimum} if for any other $P'$ such that $P\equiv P'$, $|P|\leq |P'|$.

\begin{theorem}
\label{thm-pattern-minimization}
For any pattern $P$, (1) there exists a unique minimum equivalent pattern $P_m$ via team simulation;
and (2) there exists an algorithm finding $P_m$ in $(|P|^2)$ time.
\end{theorem}

We propose an algorithm to minimize patterns (\ie\ \minp in the Appendix), which
 computes the maximum match relation $\Reps$ \wrt graph simulation by treating $P$ as both pattern and data graphs,
combines equivalent nodes \wrt $\Reps$, and merges capacity bounds on equivalent nodes.

\begin{example}
Takes as input the pattern $P_3$ shown in Fig.~\ref{fig-consistency-example}.
By Proposition~\ref{prop-pattern-consistency}, it determines that pattern $P_3$ is satisfiable.
By algorithm \minp, it constructs the minimum equivalent pattern graph $P_{3m}$ of $P_3$, shown in Fig.~\ref{fig-consistency-example}.
\end{example}

Note that algorithm \grouprec is finally incorporated with the above two optimization techniques.
}%%%EAT170720

%\stitle{Remarks.}
%By utilizing \grouprec (\optgrouprec) for \teamF,
%it is worth to mention we not only preserve both two objective functions in existing \teamF\, algorithms,
%\ie the locality retained by balls and the density function in selecting top-$k$ results,
%but also captures more practical usages,
%\ie the structural relations between team members and the budget restriction controlled by capacity bounds on patterns.

%Given a graph $H$, they have illustrated that the density of the maximum core of a graph $H$ is a (1/2)-approximation of the density of the densest subgraph of $H$. That is, the density of the densest subgraph of $H$ is at most twice of the density of maximum core, and there exists accurate linear time algorithm for calculating maximum core of a graph. Such that we can use the density of maximum core as an upper bound of the densest subgraph of $H$.

%Besides, algorithm \grouprec builds balls only using the set of data nodes with labels included in pattern nodes, instead of using all data nodes, which is an effective improvement.

\eat{
{\bf 1. more details are needed.}

{\bf 2. Add an example.}

{\bf 3. Add Correctness and Complexity.}

{\bf 4. why not for k: space issues for preprocessing}

\textbf{to add: (1) the analyses and experiments on the space of balls: (a) directly store all balls (nodes and the edges for border nodes), (b) using reference method~\cite{NavlakhaRS08} to compress the balls}

This is to justify the solution that stores no balls.

\textbf{to add: (2) the analyses and experiments on the counter filters:}

This is to justify the solution of bloom filters and bitmap index.
}

### 2017-09-25 TF-vldb2018/sec-tsimAlg.tex

\section{Finding Top-k Teams}
\label{sec-tsimAlg}

\begin{figure}[tb!]
	%\vspace{-1ex}
	\begin{center}
		\includegraphics[scale=1.28]{./fig/consistency_motivation.eps}
	\end{center}
	\vspace{-3ex}
	\caption{Pattern graphs}
	\vspace{-4ex}
	\label{fig-consistency-example}
\end{figure}

\revise{
We devise a \warn{quadruplicate} time algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for strong simulation~\cite{MaCFHW14}.}

\stitle{Pattern satisfiability}.
Given a pattern $P$, \grouprec firstly checks whether $P$ is satisfiable. We say that a pattern $P$ is {\em satisfiable} iff there exists a data graph $G$ such that $P$ matches $G$ via team simulation, \ie $P \eeps G$.

Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
pattern graphs may be unsatisfiable for team simulation, due to the presence of capacity constraints enforced on patterns. We illustrate this with an example below.
%\looseness=-1

\begin{example}
\label{exm-consistency}
\ni(1)  Consider pattern $P_2$ in Fig.~\ref{fig-consistency-example}.
One can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $u$ in $G$, if $u$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.

\sstab(2) Pattern $P_1$ in Fig.~\ref{exm-motivation} is satisfiable as $P_1 \eeps G_1$.
\end{example}

The good news is that checking the satisfiability of pattern graphs can be done in low polynomial time.

\begin{prop}
\label{prop-pattern-consistency}
The satisfiability of patterns $P$ can be checked in $O(|P|^2)$ time.
\end{prop}

\proofS By treating $P$ as both data and pattern graphs, compute the maximum match relation $M$ in $P$ for $P$, via graph simulation.
Indeed, pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. Observe that the size of $M$ is bounded by $|P|^2$.
\eop

\eat{%%%170721
Pattern graphs are typically small, and we only consider  satisfiable patterns in the sequel, by Proposition~\ref{prop-pattern-consistency}.
}%%%170721

\revise{
\stitle{Incremental computing for radius varied balls}. Recall that given $G$, $P$, $k$ and $r$, \teamF\,is to find top-$k$ teams within balls $\ball{[v, t]}$, where $v \in V$ and $t \in [1,r]$.
%centered at each node in $G$ with radius $t$ varying from 1 to $r$.
However, it is extremely costly to construct all such balls, \ie $r|V|$ balls, to compute perfect subgraphs residing in them. 
Instead, \grouprec only constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$ 
where $v \in V$ and radius is $r$ , 
and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$ who shares the same center node. The correctness of \grouprec is assured by the theorem below.

\vspace{-1ex}
\begin{theorem}
	\label{thm-tsim-radius}
	Given $P$, ball $\ball{[v, r]}$ and $\ball{[v, t]}$ ($t \in[1,$ $r-1]$) in $G$,
	(1) if $P\eps \ball{[v, t]}$, then $P\eps \ball{[v, r]}$; and
	(2) if $G_s$ (resp. $G'_s$) is the match graph \wrt the maximum match relation $M$ (resp. $M'$) in $\ball{[v, r]}$ (resp. $\ball{[v, t]}$) for $P$ via graph simulation, then $M' \subset M$, and $G'_s$ is a subgraph of $G_s$.	
\end{theorem}
\looseness=-1

When we get the match graph $G_s$ in $\ball{[v, r]}$ for $P$ via graph simulation, to compute the perfect subgraph in $\ball{[v, t]}$ ($t \in [1,r-1]$) for $P$ via team simulation, we need to 
(1) first identify the subgraph $G_s^{t}$ in $G_s$ belonging to $\ball{[v, t]}$, which can be easily identified in the process for constructing $\ball{[v, r]}$ without extra computation; 
(2) check whether $G_s^{t}$ is already a match graph for $P$ in $\ball{[v, t]}$ via graph simulation; if not, remove the unmatched nodes and edges from $G_s^{t}$ until find the match graph $G'_s$ for $P$ in $\ball{[v, t]}$. This can be achieved by executing an efficient incremental process in~\cite{FanWW13-tods}; and
(3) finally check whether capacity bounds are satisfied. If so, $G'_s$ is the perfect subgraph in $\ball{[v, r]}$ for $P$ via team simulation.}

\stitle{Density based filtering}. Although we have reduced a significant amount of computation by only computing team simulation for a number of $|V|$ balls by the incremental optimization above, we can further optimize the process by adopting the density based filtering technique.
%A typical idea to devise algorithms for \teamF\, is to compute the perfect subgraph within each ball and maintains the top-$k$ non-repeated perfect subgraphs with current top-$k$ largest density, and returns them when all balls are processed.
%This technique allows algorithm \grouprec to compute the top-$k$ perfect subgraphs \wrt $P$ without necessarily computing team simulation for all balls in $G$. 
It allows \grouprec to compute team simulation for much less than $|V|$ balls. 
The crucial issue is how can tell whether a ball has the possibility to have one of the final top-$k$ results in itself or in its inner balls with the same center node.
%If the answer is yes, we should check team simulation for that ball; Otherwise, we just skip the ball to the remaining balls.
The idea is, given a ball $\ball{[v,r]}$, we calculate the upper bound of $\density{\hat{G}_s}$,
where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
If the bound is larger than the current $k$-th result, \ie there is possibility the final answer resides in the ball or the inner balls, compute team simulation for it;
Otherwise, skip the ball to the remaining balls to avoid redundant team simulation computing.

The problem here is how to efficiently compute the upper bound of $\density{\hat{G}_s}$ for each ball in $G$.
As the best densest subgraph algorithms are in $O(|\ball{[v,r]}|^3)$ time \cite{maximumDenseSubgraph}, which is costly,
we utilize an important result in~\cite{EVMK12}, shown below.

\begin{lemma}
	\label{lemma-approximation-bound}
	Let $\density{H_{c}}$ and $\density{H_{d}}$ be the density of the maximum core  $H_{C}$  and the  densest subgraph $H_{d}$ of graph $H$. Then (1) $\density{H_{c}}\leq \density{H_{d}} \leq 2*\density{H_{c}}$; and (2) there exists an algorithm that computes $\density{H_{c}}$ in $O(|E_H|)$ time~\cite{EVMK12}.
\end{lemma}

Here the maximum core $H_{C}$ of a graph $H$ is a subgraph of $H$ whose node degree is at least $\rho$, where $\rho$ is the maximum possible one. By Lemma~\ref{lemma-approximation-bound}, we use $2*\density{H_{c}}$ as the density upper bound for filtering unnecessary balls.

We are now ready to present algorithm \grouprec for \teamF{}.

\revise{
\stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
It firstly checks whether $P$ is satisfiable (line 1). 
If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the early termination condition holds (lines 3-6).
If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see Appendix),
an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the incremental algorithm in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11, see Appendix).}
%Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
%by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.

\stitle{Correctness \& complexity analyses}. The correctness of \grouprec is assured by the following.
%(1) There is a unique perfect subgraph in each ball of $G$.
(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as for simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
(2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
\warn{
It takes $O(|P|^2)$ to check pattern satisfiability, $O(|V||P||G|)$ to compute team simulation, $O(r|V||V_{P}||E|)$ to incrementally compute matches in inner balls, and $O(|V||E|)$  to compute the density of the maximum core for $|V|$ balls.
Thus \grouprec is in $O(|P|^2+|V||P||G|+r|V||V_{P}||E|)$. However, actual time is much less due to early termination and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.}
\looseness=-1

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule
			\vspace{-3ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $k, r$.\\
				{\sl Output:\/} Top-$k$ densest teams.\\
				\sstab \bcc \hspace{1ex}\= \If $P$ is unsatisfiable \Then \Return $nil$;\\
				\icc \> $L_{k} := \emptyset$;\\
				\icc \> \For each ball $\ball{[v,r]}$ in $G$ \Do\\
				\icc \>\hspace{2ex}\= compute the maximum core $\ball{}_{C}$ of the ball $\ball{[v,r]}$;\\
				\icc \>\> \If 2*$\density{\ball{}_C} <$  the density of the $k$-th result in $L_{k}$ \Then\\
				\icc  \>\>\hspace{2ex}\= \Return $L_{k}[0:k-1]$;\\
				\icc \>\> $G_s$ := \rgraphsim$(P, \ball{[v,r]})$; \\
				\icc \>\> If $G_s$ satisfy capacity bounds on $P$ \Then Insert $G_s$ into $L_{k}$;\\
				\icc \>\> \For each ball $\ball{[v,t]}$ with $t\in[1,r-1]$ \Do\\
				\icc \>\>\hspace{2ex}\= $G'_s$ := \kw{incSim}$(G_s, P, \ball{[v,t]})$;\\
				\icc \>\>\> If $G'_s$ satisfy capacity bounds on $P$ \Then Insert $G'_s$ into $L_{k}$;\\
				%\icc \>\> \If $\density{G_s}>$ the density of the $k$-th result in $L_{k}$ \Then\\
				%\icc \>\> \If $\density{G_s}>$ the density of $kth$ result in $L_{k}$ and there exists\\
				%     \>\>\hspace{0.5ex}   no $G'_s$ in $L_{k}$ that is same with $G_{s}$ \Then\\
				%\icc \>\>\hspace{2ex}\= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$;\\
				\icc \>\, \Return $L_{k}[0:k-1]$.
			}

			\vspace{-4ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \grouprec} 
	\label{alg-grouprec}
	\vspace{-4ex}
\end{figure}

### 2017-09-25 TF-vldb2018/subsec-Ginc.tex

\subsection{Dealing with Data Updates}
\label{subsec-Ginc}

We next propose \incd to handle $\Delta G$, followed the steps in Section~\ref{sec-dynamictopk}.
Given auxiliary structures $\tilde{M}(P,G)$ and \fb,
we show how to combine procedures \identifyaffball, \incmatch and \comb for computing match results for $P$ in $G \oplus \Delta G$.
%
\incmatch and \comb handle $\Delta G$ basically the same as $\Delta P$, so we mainly show how \identifyaffball identifies \affballsx \wrt $\Delta G$.

\stitle{Procedure \identifyaffball}.
Given $G$, $\Delta G$, and \fb, \identifyaffball identifies \affballsx according to the lemma as follows.

\begin{lemma}
\label{lemma-incgrdata-affballs}
A ball $\ball{[v,r]}$ with center node $v$ in $G$ is identified as an \affballx \wrt $\Delta G$ and \fb,

\sstab{(1)} for some unit data update $\delta$ of $\Delta G$, where
(a) $\delta$ is an edge insertion/deletion, $(w_1,w_2)^+/(w_1,w_2)^-$, and $v\in V_{\ball{[w_1,r]}}\cap V_{\ball{[w_2,r]}}$, or
(b) $\delta$ is a node insertion/deletion, $(w,(w,w'))^+$/$(w)^-$, and $v\in V_{\ball{[w,r]}}$; or

\sstab{(2)} when $\ball{[v,r]}$ has type code $(1,\ldots,1)$  in \fb.
\end{lemma}

We say a ball which satisfies condition (1) is a {\em structural affected} ball,
\ie the structure of the ball is changed due to the exertion of some updates in $\Delta G$.
%The correctness of procedure \identifyaffball is guaranteed by the following.

\vspace{-0.5ex}
\begin{prop}
\label{prop-affected-datainc}
Given $P$, $G$ and $\Delta G$, if there is a perfect subgraph for $P$ in  ball $\widehat{G\oplus\Delta G}{[v,r]}$ of $G\oplus \Delta G$,
then $\ball{[v,r]}$ must be an affected ball produced by procedure \identifyaffball.
%Given data graph $G$, pattern graph $P$ and data updates $\Delta G$,
%the top-k perfect graphs in $G\oplus \Delta G$ for $P$ must be contained in \affballsx.
\end{prop}

\eat{
\proofS
The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
\identifyaffball filters out the balls that cannot match all fragments,
and there are no data updates on the ball.
\eop}

The proof is deferred to Appendix.

Different from pattern updates, procedure \incmatch recomputes partial match relations in $\tilde{M}(P,G)$
for each pattern fragment of $P$ in each {\em structural affected} ball;
and no computation is needed for \affballsx that only satisfy condition (2) in Lemma~\ref{lemma-incgrdata-affballs}.
Procedure \comb combines the partial relations \wrt $\Delta G$ in the same way as handling $\Delta P$.

\stitle{Updating \fb}. Algorithm \incd also updates \fb for all \affballsx.
In addition to updating the links from \fs to \bs in \fb as for pattern updates,
\incd maintains \bs by
(a) removing (resp. inserting new) entries from (resp. to) \bs corresponding to balls whose center nodes are removed from (resp. inserted to) $G$, due to node deletions (resp. node insertions);
and (b) updating the \kw{den} item in \bs \wrt $\Delta G$.
These updates can be done in $O(|\affballsx|)$ time.

\begin{example}
\label{exa-Ginc}
Consider $P_1$ and $G_1$ (both without dashed edges) in Fig.~\ref{fig-motivation-example}, and \fb in Fig.~\ref{fig-auxiliary-structures}(a).
When $\Delta G_1=(\kw{SD_3},\kw{ST_3})^+$ comes,
by Lemma~\ref{lemma-incgrdata-affballs},
\identifyaffball identifies $\ball{[\kw{SD_3}, 2]}$, $\ball{[\kw{ST_3},2]}$, $\ball{[\kw{SA_3}, 2]}$ and $\ball{[\kw{PM_2}, 2]}$ as {\em structural affected} balls,
together with balls with $tc$ $(1, 1)$ in \fb as \affballsx, \ie $\ball{[\kw{PM_1}, 2]}$, while filtering out all other balls.
\end{example}

\stitle{Algorithm \incd.} Given $\tilde{M}(P,G)$, \fb and data updates $\Delta G$,
\incd computes the match results for $P$ in $G \oplus \Delta G$, and maintains
auxiliary structures by invoking procedures \identifyaffball, \incmatch and \comb sequentially.

\stitle{Correctness \& complexity analyses}. The correctness of \incd \wrt $\Delta G$ follows from Proposition~\ref{prop-affected-datainc} and the correctness of \incmatch and \comb.
\incd is overall in
$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}\bigcup_{i\in[1,h]}$ $r|M(P_{fi}, \widehat{G\oplus\Delta G})|$+$r|P||\affballsx|)$ time \wrt $\Delta G$, while $r$ is small, \ie 2 or 3  (See Appendix).
\looseness=-1

\eat{
The correctness of \incd \wrt $\Delta G$ is assured by the correctness of
\identifyaffball (by Proposition~\ref{prop-affected-datainc}) and procedures \incmatch and \comb (proved along the same lines as for pattern updates).

One can verify that procedure \identifyaffball is in $O(|\affballsx|)$ time,
\incmatch is in $O(|P||\affballsx|)$ time, and \comb is in $O(\bigcup_{i\in[1,h]}|M(P_{fi}, \widehat{G\oplus\Delta G})|)$ time.
Thus, algorithm \incd is in
$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}|M(P_{fi}, \widehat{G\oplus\Delta G})|+|P||\affballsx|)$ time \wrt $\Delta G$.}%%%EAT

\stitle{Remarks}. Note that the running time of \incd is determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$,
and hence the part for data updates in Theorem~\ref{thm-framework-inc} is proved. This also completes the proof of Theorem~\ref{thm-framework-inc}.

\subsection{Unifying Pattern and Data Updates}
\label{subsec-completePG}

We are now ready to provide algorithm \inc, integrating \incp and \incd, \revise{which are presented in Section~\ref{subsec-Qinc} and Section~\ref{subsec-Ginc}, respectively,} to process continuous pattern and data updates, separately and simultaneously.

Algorithm \inc is able to handle {\em simultaneous} $\Delta P$ and $\Delta G$, because of the consistency in:
(1) the processes for handling $\Delta P$ and $\Delta G$, which follow the same steps in Section~\ref{sec-dynamictopk};
(2) auxiliary data structures for supporting $\Delta P$ and $\Delta G$; and
(3) the combination procedures, which suffice to support simultaneous pattern and data updates.

Observe that \inc can handle {\em continuous} simultaneous $\Delta P$ and $\Delta G$,
as \inc incrementally maintains the auxiliary structures for continuous coming $\Delta P$ and $\Delta G$.

### 2017-09-25 TF-vldb2018/subsec-Qinc.tex

\subsection{Dealing with Pattern Updates}
\label{subsec-Qinc}

We present algorithm \incp to handle pattern updates $\Delta P$, followed the steps in Section~\ref{sec-dynamictopk}, and
an early return optimization technique for \incp.
%Note that for any $h$-fragmentation ${\cal P}_h$ of $P$, $|{\cal P}_h|$ = $|P|$.

%\ie identifying \affballsx (Section~\ref{subsubsec-affball}), updating $\tilde{M}(P,G)$ within \affballsx (Section~\ref{subsubsec-updtm}), and combining to get final results (Section~\ref{subsubsec-combine}).

\subsubsection{Identifying Affected Balls}
\label{subsubsec-affball}

We first develop procedure \identifyaffball to identify \affballsx,
which utilizes auxiliary structures \fb and \bfc.

\stitle{Procedure \identifyaffball}.
Given an $h$-fragmentation ${\cal P}_{h}$ of $P$, $\Delta P$,
(1) it updates \bfc by processing all unit updates in $\Delta P$.
(2) For each $i\in [1, 2^h]$, it then executes a bitwise \kw{AND} operation (\&) between type code $tc_i$ of \fs in \fb and updated $fc_{i\Delta}$ in \bfc, \ie $tc_i\& fc_{i\Delta}$.
(3) Finally, if $tc_i\& fc_{i\Delta} = fc_{i\Delta}$, \identifyaffball refers to \bs in \fb to mark the balls with type code $tc_i$ as \affballsx, and resets $fc_{i\Delta}$ to $(1, \ldots, 1)$.

%If there exists a single-edge delete on pattern fragments or single-node insert/delete in $\Delta P$, then \identifyaffball returns all such \affballsx as \affballaccs. Intuitively, \affballsx are those balls that may contain new matches due to the pattern updates, while \affballaccs are those ones that cannot be computed from $P$ and $\tilde{M}(P,G)$ due to node inserts/deletes or edge deletes on pattern fragments in $\Delta P$.

\begin{example}
\label{exa-identifyaffball}
Consider the input and auxiliary structures in Example~\ref{exa-matchindex}, and \bfc in Fig.~\ref{fig-auxiliary-structures}.

\sstab(1) When $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$,
\bfc is updated as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).
\identifyaffball identifies balls with type code $(1, 1)$ and $(1, 0)$ as \affballsx,
\ie $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$.
Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.

\sstab(2) Consider another case when $\Delta P'_1$ comes with $\delta_1$ and $\delta_2$, where $\delta_1$ is same as above and $\delta_2 = (\kw{BA},\kw{UD})^+$. \bfc is updated as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(c), and \identifyaffball identifies the same \affballsx as above.
\end{example}

In real-life networks, the quantity of balls with type code ($0,\ldots,0$) is several orders of magnitude larger than that of balls who match with at least one pattern fragment. By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$),
it can reduce a large amount of redundant computations.

\begin{prop}
\label{prop-canaffballs}
For any ball $\ball{[v,r]}$ in $G$, if there exists a perfect subgraph of $P\oplus \Delta P$ in $\ball{[v,r]}$,
then $\ball{[v,r]}$ must be an affected ball produced by procedure \identifyaffball.
\end{prop}

The proof is deferred to Appendix.

\eat{
\proofS
When $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
\identifyaffball identifies \affballsx who already match with each fragment of $P$;
Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
there must exist an update in $\Delta P$ on $P_{fi}$,
such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.
\eop}

%\vspace{1ex}
\stitle{Lazy update policy}. To reduce computation, \incp only updates the partial relations for \affballsx in $\tilde{M}(P,G)$ for computing  $L_k(P\oplus \Delta P, G)$.
%However, the filtered balls are still in need for handling future pattern updates $\Delta P'$,
%and their partial match relations are outdated \wrt $P\oplus \Delta P$.
However, those partial relations in the filtered balls also needs an update for handling future updates $\Delta P'$, but
definitely become outdated \wrt $P\oplus \Delta P$. 
Hence, \incp needs a smart policy to maintain those match relations in the filtered balls. 
%$L_k(P\oplus \Delta P \oplus \Delta P', G)$ even though $\tilde{M}(P,G)$ are not updated entirely for all balls.

To do this, algorithm \incp maintains the status of all unit updates applied to $P$ so far, and processes unit updates in $\Delta P$ as {\em late} as possible, while having no effects on future updates $\Delta P'$, \ie a {\em lazy update policy}.
%In other words, the match results for each $\Delta P$ can be returned as {\em early} as possible.

Algorithm \incp utilizes auxiliary structure \upl together with the $cflag$ item in \bs.
When handling current $\Delta P$, for each ball $\ball{}$, $\ball{}[\kw{cflag}]$ records the id of the latest processed unit pattern update for $\ball{}$, and is initialized to $0$.
When future $\Delta P'$ comes, for any \affballx $\ball{}$ \wrt $\Delta P'$ and any fragment $P_{fi}$,
\incp computes $M(P_{fi}\oplus\Delta P'_{fi}, \ball{})$ based on $M(P_{fi}, \ball{})$ by procedure \incmatch (to see in Section~\ref{subsubsec-updtm}),
where $\Delta P'_{fi}$ consists of the unit updates stored in $T(P_{fi})$ whose ids are larger than $\ball{}[\kw{cflag}]$ in \bs.

\begin{example}
\label{exa-lazyupdate}
Continue Example~\ref{exa-identifyaffball}.
(1) Balls $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$ are \affballsx, and
\upl is shown in Fig.~\ref{fig-inc-maintain-unit}.

\sstab(a) \upl is updated \wrt\ $\Delta P_1=\{\delta_1\}$.
\incp updates the partial relations for $P_{f2}$ \wrt\ $\delta_1$ in the two balls,
and sets their $cflag$ in \bs to $\delta_1$, as the status shown in Fig.~\ref{fig-auxstr-index}.

\sstab
(b) Afterwards, $\Delta P_2$ with an edge insertion $\delta_2 = (\kw{BA},\kw{UD})^+$ comes.
\identifyaffball updates \bfc and \upl as shown in Fig.~\ref{fig-inc-maintain-unit} and identifies balls with $tc$ $(1, 1)$ as \affballsx, \eg $\ball{[\kw{PM_1},2]}$.

\sstab
(c) Finally, $\Delta P_3$ with a node deletion $\delta_3$ = $(\kw{UD})^-$ comes.
\identifyaffball identifies $tc$ $(1, 1)$, $(0, 1)$ and $(0, 0)$ as \affballsx.
Take ball $\ball{[\kw{BA_3}, 2]}$ for example, which is the first time identified as an \affballx.
By referring to \upl, \incp updates the partial relations for $P_{f1}$ \wrt\ $\{\delta_2, \delta_3\}$,
and for $P_{f2}$ \wrt\ $\{\delta_1\}$.
\looseness=-1

\sstab
(2) In the case when $\Delta P'_i$ contains multiple\eat{unit} updates, \bfc and \upl are updated accordingly as shown in Fig.~\ref{fig-auxiliary-structures}(c).
\end{example}

\vspace{-.5ex}

\subsubsection{Updating Fragment-Ball Matches}
\label{subsubsec-updtm}

We then update the partial match relations for \affballsx in $\tilde{M}(P,G)$ \wrt $\Delta P$,
by procedure \incmatch.

\stitle{Procedure \incmatch}. Given $h$-fragmentation ${\cal P}_{h}$ of $P$, $G$, $\tilde{M}(P,G)$, $\Delta P$, \upl and \affballsx \wrt $\Delta P$.
\incmatch updates $M(P_{fi}, \ball{})$ to $M(P_{fi}\oplus\Delta P_{fi}, \ball{})$ in $\tilde{M}(P,G)$ for each fragment $P_{fi}$ and each \affballx $\ball{}$.
Recall that $\Delta P_{fi}$ consists of unprocessed unit updates accumulated in \upl applied to $P_{fi}$.
%Recall that $\Delta P_{fi}$ consists of the unit updates in $\Delta P$ applied to $P_{fi}$ we get from \upl.
We show how to update $M(P_{fi}, \ball{})$ in different cases.

%\eetitle{(1) Capacity changes in $\Delta P_{fi}$ or updates on $C$ only}.

\eetitle{(1) There exist edge/node deletions in $\Delta P_{fi}$}.
In this case, \incmatch accesses the \affballx $\ball{[v,r]}$ in $G$.
It simply computes the maximum match relations for $P_{fi}\oplus \Delta P_{fi}$ in $\ball{[v,r]}$
by procedure \rgraphsim in $O(|P_{fi}\oplus \Delta P_{fi}||\ball{[v,r]}|)$ time.

\eetitle{(2) No edge/node deletions in $\Delta P_{fi}$}.
\incmatch processes updates of the same type together in this case.

\eetitle{(2).i Capacity changes in $\Delta P_{fi}$ or updates on $C$}.
In this case, no computation is needed for maintaining \revise{partial relations for} \affballsx at all,
\ie $M(P_{fi}\oplus\Delta P_{fi}, \ball{}) = M(P_{fi}, \ball{})$.
\warn{Only a capacity check and an inner ball results check in the combination procedure are needed} (to see in Section~\ref{subsubsec-combine}).

%It is same for the updates on cut edges $C$ of ${\cal P}_{h}$ of $P$, which are also processed by the combination procedure.

%\eetitle{(3) Edge insertions in $\Delta P_{fi}$ only}.
\eetitle{(2).i Edge insertions in $\Delta P_{fi}$}.
In this case, \incmatch calls procedure \patedgeinsert to process edge insertions.
% $|\Delta P_{fi}|$ times.

\begin{figure}[t!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule
\vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} $M(P_{fi}, \ball{[v,r]})$, $\ball{[v,r]}$, pattern edge insertion $\delta$ = $(u,u')^+$.\\
{\sl Output:\/} $M(P_{fi}\oplus \delta, \ball{[v,r]})$.\\
\sstab \bcc \hspace{1ex} \= $\kw{RMv}:=\emptyset$;\\
\icc \> \For \Each $u \in V_{P}$ \Do $\matchs(u)$ := \{$w | (u,w) \in M(P_{fi}, \ball{[v,r]})$\};\\
\icc \> \For \Each node $w \in \matchs(u)$\eat{in $M(P_{fi},\ball{[v,r]})$} \Do\\
\icc \>\hspace{2ex}\= \If there exists no $(w, w')\in E_{\ball{[v,r]}}$ with $w' \in \matchs(u')$ \Then\\
\icc \>\>\hspace{2ex}\= $\kw{RMv}.\kw{push}([u,w])$;\\
\icc \> \For \Each node $w' \in \matchs(u')$\eat{$M(P_{fi},\ball{[v,r]})$} \Do\\
\icc \>\> \If there exists no $(w', w)\in E_{\ball{[v,r]}}$ with $w \in \matchs(u)$ \Then\\
\icc \>\>\> $\kw{RMv}.\kw{push}([u',w'])$;\\
\icc \> \While $\kw{RMv}\neq \emptyset$ \Do\\
\icc \>\hspace{2ex}\= $[u,w]:=\kw{RMv}.\kw{pop}$(); $\matchs(u):=\matchs(u)\setminus\{w\}$;\\
\icc \>\> \For \Each $(u,u')\in E_{P_{fi}}$ \Do\\
\icc \>\>\hspace{2ex}\= \For \Each $(w, w')\in E_{\ball{[v,r]}}$ with $w' \in \matchs(u')$ \Do\\
\icc \>\>\>\hspace{2ex}\= \If there is no $(w', w'')\in E_{\ball{[v,r]}}$ with $w'' \in \matchs(u)$ \Then\\
\icc \>\>\>\>\hspace{2ex}\= \kw{RMv}.\kw{push}([$u',w'$]);\\
\icc \> \If there is a node $u\in V_{P_{fi}}$ with $|\matchs(u)| = 0$ \Then $\matchs(\cdot):=\emptyset$;\\
\icc \> $M(P_{fi}\oplus \delta, \ball{[v,r]})$ := \{$(u,w) | u \in V_{P}, w \in \matchs(u)$\};\\
\icc \> \Return $M(P_{fi}\oplus \delta, \ball{[v,r]})$;
}
\vspace{-2.5ex} \myhrule
}
\end{center}
\vspace{-3ex}
\caption{Procedure \patedgeinsert} \label{alg-patedgeinsert}
\vspace{-5ex}
\end{figure}

\stitle{Procedure \patedgeinsert}.
Given $M(P_{fi}, \ball{[v,r]})$ (also represented by $\matchs(\cdot)$), $\ball{[v,r]}$ and an edge insertion $\delta=(u,u')$, \patedgeinsert computes $M(P_{fi}\oplus\delta, \ball{[v,r]})$ {\em incrementally}, as shown in Fig.~\ref{alg-patedgeinsert},
along the same lines as for data incremental graph simulation~\cite{FanWW13-tods}.
\patedgeinsert first finds the directly affected data nodes which need to be removed from $\matchs(\cdot)$ due to the edge insertion to $P_{fi}$,
and pushes them along with the matched pattern nodes into $\kw{RMv}$ (lines 3-8).
It then recursively identifies and removes the nodes in $\matchs(\cdot)$ affected by the previous removed nodes (lines 9-14).
The recursive process is executed by utilizing a stack $\kw{RMv}$.
If there exists a pattern node $u$ with empty $\matchs(u)$, then $\matchs(\cdot)$ is set to $\emptyset$ (line 15).
Finally, \patedgeinsert returns the updated $\matchs(\cdot)$ for $P_{fi}\oplus \delta$ (lines 16-17).
\looseness=-1

\begin{example}
\label{exa-edge-insertion}
Consider case (1)-(b) in Example~\ref{exa-lazyupdate}.
Given $\delta_2 = (\kw{BA},\kw{UD})^+$, and $M(P_{f1}, \ball{}_{\kw{PM_1}})$, which is composed of nodes \kw{PM_1}, \kw{BA_1} and \{\kw{UD_1},\kw{UD_2}\} mapped to nodes \kw{PM}, \kw{BA} and \kw{UD} in $P_{f1}$.
To compute the updated $M(P_{f1}\oplus \delta_2, \ball{}_{\kw{PM_1}})$,
\patedgeinsert removes \kw{UD_2} which is directly affected by $\delta_2$, and finds no other nodes need to be removed.
\end{example}

%When update the partial match relations for fragment $P_{f2}$ \wrt\ $\delta_2 = (\kw{BA},\kw{UD})^+$ in ball $\ball{[\kw{PM_1},2]}$,
%and $M(P_{f2}, \ball{[\kw{PM_1},2]})$ is composed of nodes \kw{PM_1}, \kw{BA_1} and \{\kw{UD_1},\kw{UD_2}\}
%mapped to nodes \kw{PM}, \kw{BA} and \kw{UD} in $P_1$,
%\patedgeinsert removes \kw{UD_2} which is directly affected by $\delta_2$,
%and finds no other nodes need to be removed.

%\eetitle{(4) Node insertions in $\Delta P_{fi}$ only}. 
\eetitle{(2).ii Node insertions in $\Delta P_{fi}$}. 
Node insertions are handled in the same way as edge insertions, by extending \patedgeinsert.

Given a node insertion $\delta$ = $(u,(u,u'))^+$, where $u$ is a newly inserted node,
to compute the updated $M(P_{fi}\oplus \delta, \ball{[v,r]})$,
\incmatch firstly computes the set of nodes $\matchs(u)$ in $\ball{[v,r]}$ which have the same label with $u$, and then calls \patedgeinsert($M(P_{fi}, \ball{[v,r]})$, $\ball{[v,r]}$, $(u,u')$) to get the updated result.

\vspace{0.5ex}
\stitle{Updating \fb.} After updating $\tilde{M}(P,G)$,
\incp updates \fb for all \affballsx, by changing the links according to the updated partial relations in $\tilde{M}(P,G)$, and also updating the \kw{cflag} item in \bs, which is in $O(||\affballsx||)$ time.

\subsubsection{Combining Fragment-Ball Matches}
\label{subsubsec-combine}

Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb. Observe that only the balls from \affballsx which match with all pattern fragments of $P\oplus \Delta P$ can enter the combination process.

\stitle{Procedure \comb}. For an \affballx $\ball{[v,r]}$, \comb invokes $\patedgeinsert(\bigcup_{i\in [1, h]}M(P_{fi},\ball{[v,r]}), \ball{[v,r]}, C\oplus \Delta C)$
to compute the maximum match relations of $P\oplus \Delta P$ for $\ball{[v,r]}$ incrementally,
where $\Delta C$ consists of the edge insertions/deletions in $\Delta P$ applied to the cut edges $C$.
It then checks whether the capacity bounds, together with the updates on them, are satisfied.
If so, it constructs the perfect subgraph \wrt the match relations above.
\warn{It then checks the inner balls results together with the capacity bounds} and finally returns the list of top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$.

\begin{example}
\label{exa-combination}
Continue Example~\ref{exa-lazyupdate}-(1), after \incp updated partial relations for \affballsx \wrt $\Delta P_3$,
balls $\ball{[\kw{PM_1},2]}$, $\ball{[\kw{PM_2},2]}$ and $\ball{[\kw{BA_3},2]}$ enter the combination process.

\sstab
(1) For $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$, as $C\oplus \Delta C=\{(\kw{PM},\kw{SA})\}$,
\comb finds that there is an \kw{SA_i} (resp.\,\kw{PM_j}) connecting to \kw{PM_j} (resp.\,\kw{SA_i}),
and the capacity bounds are satisfied. 
\warn{For inner balls, based on above results, \comb finds that no perfect subgraphs reside in $\ball{[\kw{PM_1},1]}$ and $\ball{[\kw{PM_2},1]}$.}
Hence it returns above two perfect subgraphs in two balls.

\sstab
(2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
\warn{So no results are in it and its inner balls.}
\end{example}

\subsubsection{Early Return Optimization Technique}
\label{subsubsec-Inc-opt}

%As introduced in last section, the {\em lazy update manner} accelerates the process to return updated top-$k$ perfect subgraphs by postponing the processing of each unit pattern update.
We propose an optimization technique for \incp to further speed-up the incremental computations, by making use of the top-$k$ semantics.
%
We first define {\em early return} for incremental top-$k$ algorithms, analogous to {\em early termination} for batch top-$k$ algorithms~\cite{FaginLotem03}.

\stitle{Early return}. An algorithm has the {\em early return property},
if for pattern $P$ with updates $\Delta P$ and for any data graph $G$,
it outputs $L_k(P\oplus \Delta P, G)$ as early as possible without the need to update match relations for every \affballx,
while the updates can be executed in background.

\begin{prop}
\label{prop-early-return}
There exists an algorithm for the dynamic top-$k$ team formation problem with early return property.
\end{prop}

We prove \incp retains the early return property.
Recall the density based filtering optimization for algorithm \optgrouprec in Section~\ref{sec-tsimAlg}.
\incp also utilizes density upper bounds for pruning a portion of \affballsx.
More specifically, given $P$ and $G$, \incp maintains the density upper bound for each ball in the $den$ item in \bs, \ie $\ball{}[\kw{den}]$,
calculated according to Lemma~\ref{lemma-approximation-bound}.
Thus, given $\Delta P$, if the top-$k$ densest perfect subgraphs found so far are denser than the density upper bound of the remaining \affballsx,
\incp\ {\em outputs} the current top-$k$ densest perfect subgraphs as $L_k(P\oplus \Delta P, G)$,
while continuing updating $\tilde{M}(P, G)$ in \affballsx in {\em background}.

Note that the early return optimization is  effective for pattern updates, but not for data updates and the case when $\Delta P$ contains node insertions with new labels (expertise).

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule \vspace{-2ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} \= $P$, $h$-fragmentation ${\cal P}_{h}$, $G$, integers $r$ and $k$, $\Delta P$, and\\
				\>auxiliary structures $\tilde{M}(P,G)$, \fb, \bfc and \upl.\\
				{\sl Output:\/} Top-$k$ perfect subgraphs for $P \oplus \Delta P$ in $G$.\\
				\sstab \bcc \hspace{1ex} \= $L_{k}$ := $\emptyset$;\\
				\icc \> \affballsx\ :=  $\identifyaffball({\cal P}_h, \Delta P, \fb, \bfc)$;\\
				\icc \> Sort \affballsx by $\ball{}[\kw{den}]$ in non-ascending order;\\
				\icc \> \For \Each $\ball{[v,r]}$ in \affballsx \Do\quad/* non-ascending order */\\
				\icc \> \hspace{3ex} \= \If $|L_{k}| \geq k$ \And $\ball{[v,r]}[\kw{den}] \leq \density{L_{k}[k]}$ \Then \\
				\icc \>\>\hspace{2ex} \= \bf{Output} $L_{k}[0:k-1]$.\quad/* early-return optimization*/\\
				%/* Running in background after returning top-$k$ results for $\Delta P$ */\\
				\icc \>\>$\incmatch(M(P_{fi},\ball{[v,r]}),\ball{[v,r]}, \Delta P_{fi})$ $(i\in[1,h])$;\\
				\>\> /* runs in the background */\\
				\icc \>\> $S_{G_s} := \comb(\bigcup_{i\in [1, h]}M(P_{fi},\ball{[v,r]}), \ball{[v,r]}, C\oplus \Delta C)$;\\
				\icc \>\> Insert the set of perfect subgraphs in $S_{G_s}$ into $L_{k}$;\\
				\icc \> \Return $L_{k}[0:k-1]$.
				%\icc \>\> \If $|L_{k}| < k$ or $\kw{den}(G_s) > \density{L_{k}[k]}$ \Then\\
				%\icc \>\>\hspace{2ex} \= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$.
				%\icc \hspace{-0.2ex}/*b*\hspace{-0.6ex}/\>\>Update the record of $\ball{[v,r]}$ in \fb;
			}
			\vspace{-2.5ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \incp} \label{alg-optInc}
	\vspace{-4ex}
\end{figure}

\subsubsection{The Complete Algorithm for Pattern Updates}
\label{subsubsec-completedynamicP}

Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,
algorithm \incp computes the maximum match relations of $P \oplus \Delta P$ in $G$ with early return property, and maintains auxiliary structures simultaneously by invoking procedure \identifyaffball, \incmatch and \comb one by one.

\stitle{Algorithm \incp}. It works as follows, as shown in Fig.~\ref{alg-optInc}.
For each $\Delta P$, \incp firstly sets the result list $L_{k}$ to empty,
and identifies \affballsx \wrt $\Delta P$ by \identifyaffball (lines 1-2).
It then sorts \affballsx by their density upper bounds $\ball{}[\kw{den}]$ in \bs in non-ascending order (line 3),
and accesses \affballsx sequentially by this order (lines 4-10).
Whenever it comes to next \affballx $\ball{[v,r]}$, it firstly checks whether there are already $k$ perfect subgraphs found in $L_{k}$, and moreover,
the density of the $k$th (smallest) perfect subfgraph in $L_{k}$ is larger than $\ball{[v,r]}[\kw{den}]$ (line 5).
If so, \incp immediately outputs $L_{k}$ as final results (line 6),
and then continues to update $\tilde{M}(P,G)$ for those \affballsx in background by \incmatch (line 7);
Otherwise, \incp updates the partial relations and combines them by \comb to get the set of perfect subgraphs $S_{G_s}$ in $\ball{[v,r]}$ and its inner balls (lines 7-8).
It then inserts the set of perfect subgraphs in $S_{G_s}$ into $L_{k}$ (line 9).
%It updates $L_{k}$ by inserting the set of perfect subgraphs in $S_{G_s}$ into $L_{k}$ (line 9).

\stitle{Correctness \& complexity analysis}.
The correctness of \incp is assured by the correctness of \identifyaffball (Proposition~\ref{prop-canaffballs}), \incmatch, \comb, and early return property (Lemma~\ref{lemma-approximation-bound}).
\incp is in $O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|$ + $r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|$) + $r|P \oplus \Delta P||\affballsx|$+$|\Delta P|)$ time \wrt $\Delta P$, while $r$ is small, \ie 2 or 3 (See Appendix).

\eat{
\stitle{Correctness \& complexity analysis}. The correctness of \incp \wrt $\Delta P$ is assured by
the correctness of (a) \identifyaffball (by Proposition~\ref{prop-canaffballs});
(b) \incmatch, which is assured by the correctness of \rgraphsim that has been proved previously, and of \patedgeinsert. Indeed, \patedgeinsert only removes
nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
(c) \comb, whose analysis follows the same way as for \patedgeinsert; and
(d) the early return property (by Lemma~\ref{lemma-approximation-bound}).

Procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$ time, where it takes $O(2^{h}\cdot|\Delta P|)$ time to update \bfc, $O(2^{h}\cdot h)$ to do the AND-operation, and $O(||\affballsx||)$ to identify \affballsx.
%Thus, procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$.
As $h$ is typically small, \eg 2 to 5, thus \identifyaffball is in $O(|\Delta P|+||\affballsx||)$;
\patedgeinsert is in $O(|M(P_{fi}, \ball{[v,r]})|+|V_{P_{fi}}||E_{\ball{[v,r]}}|)$ time.
Indeed, the recursive process for checking invalid nodes in $M(P_{fi}, \ball{[v,r]})$ is bounded by $O(|V_{P_{fi}}||E_{\ball{[v,r]}}|)$,
and the process to update $M(P_{fi}, \ball{[v,r]})$ is bounded by the size of its changes, which is monotonically decreasing;
According to \patedgeinsert,
\comb is in $O(|\bigcup^{h}_{i=1} M(P_{fi}\oplus\Delta P_{fi},\ball{[v,r]})|+|V_{P\oplus \Delta P}||E_{\ball{[v,r]}}|)$ time.

Putting these together, algorithm \incp is in
$O(|\Delta P|$ + $\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|+|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|) + |P \oplus \Delta P||\affballsx|)$ time \wrt $\Delta P$.
}%%%EAT

%\vspace{0.5ex}
\stitle{Remarks}. The running time of \incp is determined by $P$, $\Delta P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
Hence the part for pattern updates in Theorem~\ref{thm-framework-inc} is proved.

### 2017-09-25 TF-vldb2018/subsec-auxstr.tex

\subsection{Auxiliary Data Structures}
\label{subsec-auxstr}

Auxiliary structures fall into two classes:
maintain partial matches and handle pattern incremental computing. Consider an $h$-fragmentation \{$P_{f1}, \ldots, P_{fh}, C$\} of pattern $P(V_P, E_P)$, data graph $G(V, E)$, and pattern updates $\Delta P$.

\vspace{0.5ex}
(I) Data structures in the first class are as follows.

\etitle{(1) Fragment status (\fs)} consists of $2^h$ boolean vectors $(b_1,\ldots,b_h)$, referred to as {\em type code (tc)}, where $b_i$ $(i\in [1,h])$ is either 0 or 1. Recall that $h$ is very small, \eg 3.

We use \fs to classify the match status of balls in $G$ into $2^h$ types \wrt ${\cal P}_h$.
For a ball with type code $(b_1,\ldots,b_h)$, $b_i$ is 1 iff $P_{fi}$ matches the ball via graph simulation.

\vspace{0.4ex}
\etitle{(2) Ball status (\bs)} consists of $|V|$ triples $(bid, cflag, den)$, such that $bid$ is the $id$ of a ball,
$cflag$ is the id of the latest processed unit pattern update for the ball (initially set to $0$),
and $den$ is the density upper bound of subgraphs in the ball.
\looseness=-1

We use \bs to store the basic information for balls in $G$.

\vspace{0.4ex}
\etitle{(3) Fragment-ball matches} of $P$ in $G$, denote as $\tilde{M}(P,G)$,
are $\bigcup_{i\in[1,h], v\in V} M(P_{fi},\ball{[v,r]})$,
such that $M(P_{fi},\ball{[v,r]})$ is the maximum match relation for $P_{fi}$ in ball $\ball{[v,r]}$, via graph simulation,
and there are in total $|V|$ balls.

Here $\tilde{M}(P,G)$ is used to store match relations for the pattern fragments of $P$ in all balls of $G$. Instead of storing a single $\tilde{M}(P, G)$, we organize $\tilde{M}(P, G)$ in terms of the match status between pattern fragments and balls, \ie\ \fs and \bs.

\vspace{0.4ex}
\etitle{(4) Fragment-ball-match index (\fb)} links \fs and \bs together, to form the {\em fragment-ball-match index}. Then \fb is linked to $\tilde{M}(P,G)$. \revise{The details are shown below.}

For each record of ball $\ball{[v,r]}$ in \bs, (a) there is a link from its type code in \fs pointing to the record; and
(b) there is another link from the record to a set of $M({P}_{fi}, \ball{[v,r]})$ $(i\in [1,h])$ in $\tilde{M}(P,G)$,
if the type code with which the ball is associated has $b_i = 1$, \ie $M({P}_{fi}, \ball{[v,r]})$ is not empty.

Intuitively, \fb indexes the partial match relations $\tilde{M}(P,G)$ based on the match status of balls \wrt ${\cal P}_h$.

\begin{example}
\label{exa-matchindex}
Consider $P_1$ and $G_1$ (both without dashed edges) in Fig.~\ref{exm-motivation}, $r=2$, $k=2$, $h=2$,
auxiliary structures $\tilde{M}(P,G)$ and \fb\,that are shown in Fig.~\ref{fig-auxiliary-structures}(a).
$P_1$ is divided into fragments $P_{f1}$ and $P_{f2}$ by algorithm \kw{PFrag},
so there are $2^2=4$ type codes in \fs.
For balls linked with $tc$ $(1, 1)$, \eg ball $\ball{[\kw{PM_1},2]}$,
there are matches to both $P_{f1}$ and $P_{f2}$ in the ball.
Besides, there exist balls $\ball{[\kw{PM_2},2]}$, $\ball{[\kw{BA_3},2]}$ and $\ball{[\kw{PM_4},2]}$
linked with $tc$ $(1, 0)$, $(0, 1)$ and $(0, 0)$ respectively.
We only consider these 4 balls in the sequel.
\end{example}

%Algorithm \inc uses \fb in step (1) and $\tilde{M}(P,G)$ in step (2), and updates both of them in step (2).

\vspace{0.5ex}
(II) Data structures in the second class are as follows.

\vspace{0.5ex}
\etitle{(1) Ball filter  (\bfc)} consists of $2^{h}$ boolean vectors $(b_1$, $\ldots$, $b_h)$, referred to as {\em filtering code (fc)},
such that each $fc$ in \bfc corresponds to a type code $tc$ in \fs.
Each $b_i$ $(i\in [1, h])$ in an $fc$ of \bfc is initially set to $1$,
and is updated for each unit pattern update $\delta$ in $\Delta P$:
(a) when $\delta$ is an edge deletion or a node deletion to ${P}_{fi}$,
the $i$-th bit of all the $2^{h}$ filtering codes in \bfc is set to $0$; Otherwise, (b) \bfc remains intact.

%Algorithm \inc updates and uses \bfc in step (1) for identifying \affballsx for pattern updates.
\vspace{0.5ex}
\etitle{(2) Update planner (\upl)} consists of $h+1$ stacks $T({P}_{f1})$, $\ldots$, $T({P}_{fh})$, $T(C)$.
Stack $T(P_{fi})$ $(i\in [1,h])$ (resp. $T(C)$) records all unit updates in all arrived pattern updates $\Delta P_1$, $\ldots$, $\Delta P_{N}$ that are applied to fragment $P_{fi}$ (resp. $C$) of $P$.
Initially, all of them are empty.
They are dynamically updated for each unit update in each set of coming pattern updates.
\looseness=-1

%Algorithm \inc updates \upl in step (1) to organize and accumulate unit pattern updates to pattern fragments, and uses \upl in step (2) to update $\tilde{M}(P,G)$ in \affballsx.

%More specifically, we use (a) {\em fragment-ball status index} and (b) {\em ball status index} to organize $\tilde{M}(P, G)$ in terms of the match status between balls and pattern fragments. We then link them to the fragment-ball matches, to form an integrated organization of $\tilde{M}(P, G)$, called {\em fragment-ball math struct}, denoted by \fb.

### 2017-09-25 TF-vldb2018/sec-appendix.tex

@@
 \noindent
-{\textbf{1. Procedure \rgraphsim (Section~\ref{subsec-teamF})}}
+{\textbf{1. Procedure \rgraphsim (Section~\ref{sec-tsimAlg})}}
 
@@
 \mat{0ex}{
-\sstab {\sl Input:\/} Pattern graph $P(V_{P}, E_{P})$, ball $\ball([v, r])$.\\
+\sstab {\sl Input:\/} Pattern graph $P(V_{P}, E_{P})$ and ball $\ball([v, r])$.\\
 {\sl Output:\/} The perfect subgraph $G_s$ of $\ball{[v,r]}$ \wrt $P$.\\
@@
 
+\eat{%%EAT
 \noindent
@@
 Algorithm \minp is in $O(|P|^2)$ time, by the time complexity of graph simulation.
+}%%%EAT
 
 \noindent
-{\textbf{3. Algorithm \kw{PFrag} (Section~\ref{subsec-framework})}}
+{\textbf{3. Algorithm \kw{PFrag} (Section~\ref{sec-dynamictopk})}}
 
-Algorithm \kw{PFrag} works by connecting the {\em pattern fragmentation} problem to the
+\kw{PFrag} works by connecting the {\em pattern fragmentation} problem to the
 {\sc $(k, \nu)$-Balanced Partition} problem.
@@
 \mat{0ex}{
-\sstab {\sl Input:\/} \= Pattern graph $P(V_{P},E_{P})$, integer $h$.\\
+\sstab {\sl Input:\/} \= Pattern graph $P(V_{P},E_{P})$ and integer $h$.\\
 {\sl Output:\/} An $h$-fragmentation \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\} of $P$.\\
@@
 
+\vspace{-1.5ex}
 \etitle{Correctness \& Complexity}.
@@
 \noindent
-{\textbf{1. Proof of Proposition~\ref{thm-inc-grouprec-pat}}}
+{\textbf{1. Proof of Theorem~\ref{thm-tsim-radius}}}
+
+\noindent
+{\textbf{2. Proof of Proposition~\ref{thm-inc-grouprec-pat}}}
 
@@
 \noindent
-{\textbf{2. Proof of Proposition~\ref{prop-fragmentation}}}
+{\textbf{3. Proof of Theorem~\ref{thm-compose}}}
+
+We will prove the theorem by induction.
+Given pattern $P(V_P,E_P)$ and its fragmentation \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\},
+we use $P^{C}(V_{P^{C}},E_{P^{C}})$ to denote the pattern with $V_{P^{C}}$=$V_P$ and $E_{P^{C}}$=$E_P/C$.
+%we use $P^{C}(V_P,E_P/C)$ to denote the pattern with the same node set $V_P$ with $P$, and edges excluding the cut $C$ from $E_P$.
+Graph simulation is an iterative process to remove unmatched nodes from the candidate nodes,
+as illustrated in Fig.~\ref{alg-rsim} (lines~1-6).
+We utilize $M_{C}^{k}$ (resp. $M_{i}^{k}$, $M^{k}$) to denote the match relation for $P^{C}$ (resp. $P_{fi}$, $P$) in $\ball{}$ in the $kth$ iteration.
+By the definition of graph simulation, we have $M_{C}^{k}$ = $\bigcup_{i=1}^{h}M_{i}^{k}$.
+To prove $M\subseteq\bigcup_{i=1}^{h}M_{i}$,
+we next prove $M^{k}\subseteq M_{C}^{k}$ for each iteration instead.
+
+\vspace{-1.8ex}
+\sstab{(1)} For $k=0$, \ie the initialization step of graph simulation algorithm,
+the algorithm computes the set of candidate matches for each pattern node with the same label.
+As $P$ and $P^{C}$ have exactly the same node set, we have $M^{0}= M_{C}^{0}$.
+
+\vspace{-1.8ex}
+\sstab{(2)} For $k=n$ $(n\geq 0)$, if $M^{n}\subseteq M_{C}^{n}$ exists, we prove $M^{n+1}\subseteq M_{C}^{n+1}$ exists in the $(n+1)th$ iteration.
+Suppose both $(u,w)\in M^{n}$ and $(u,w)\in M_{C}^{n}$ exist,
+and in the $(n+1)th$ iteration, $(u,w)$ is removed from $M_{C}^{n}$ if there is a adjacent node $u'$ of $u$ in $P_{C}$,
+but there exists no adjacent node $w'$ of $w$ in $G$ such that $(u',w')\in M_{C}^{n}$.
+Therefore, $(u,w)$ must be removed from $M^{n}$ as $E_{P^{C}} \subseteq E_{P}$,
+that is, the edge $(u,u')$ in $E_{P^{C}}$ must belong to $E_{P}$.
+Thus, we have $M^{n+1}\subseteq M_{C}^{n+1}$.
+
+\vspace{-1.5ex}
+By (1) and (2), we have proven that $M\subseteq\bigcup_{i=1}^{h}M_{i}$.
+
+\noindent
+{\textbf{4. Proof of Proposition~\ref{prop-fragmentation}}}
 
@@
 \noindent
-{\textbf{3. Proof of Theorem~\ref{thm-compose}}}
+{\textbf{5. Proof of Proposition~\ref{prop-canaffballs}}}
 
-We will prove the theorem by induction.
-Given pattern $P(V_P,E_P)$ and its fragmentation \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\},
-we use $P^{C}(V_{P^{C}},E_{P^{C}})$ to denote the pattern with $V_{P^{C}}$=$V_P$ and $E_{P^{C}}$=$E_P/C$.
-%we use $P^{C}(V_P,E_P/C)$ to denote the pattern with the same node set $V_P$ with $P$, and edges excluding the cut $C$ from $E_P$.
-Graph simulation is an iterative process to remove unmatched nodes from the candidate nodes,
-as illustrated in Fig.~\ref{alg-rsim} (lines~1-6).
-We utilize $M_{C}^{k}$ (resp. $M_{i}^{k}$, $M^{k}$) to denote the match relation for $P^{C}$ (resp. $P_{fi}$, $P$) in $\ball{}$ in the $kth$ iteration.
-By the definition of graph simulation, we have $M_{C}^{k}$ = $\bigcup_{i=1}^{h}M_{i}^{k}$.
-To prove $M\subseteq\bigcup_{i=1}^{h}M_{i}$,
-we next prove $M^{k}\subseteq M_{C}^{k}$ for each iteration instead.
+We will prove the proposition by contradiction.
+When $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
+\identifyaffball identifies \affballsx who already match with each fragment of $P$;
+Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
+there must exist an update in $\Delta P$ on $P_{fi}$,
+such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
+Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.
 
-\vspace{-1.8ex}
-\sstab{(1)} For $k=0$, \ie the initialization step of graph simulation algorithm,
-the algorithm computes the set of candidate matches for each pattern node with the same label.
-As $P$ and $P^{C}$ have exactly the same node set, we have $M^{0}= M_{C}^{0}$.
+\noindent
+{\textbf{6. Proof of Proposition~\ref{prop-affected-datainc}}}
 
-\vspace{-1.8ex}
-\sstab{(2)} For $k=n$ $(n\geq 0)$, if $M^{n}\subseteq M_{C}^{n}$ exists, we prove $M^{n+1}\subseteq M_{C}^{n+1}$ exists in the $(n+1)th$ iteration.
-Suppose both $(u,w)\in M^{n}$ and $(u,w)\in M_{C}^{n}$ exist,
-and in the $(n+1)th$ iteration, $(u,w)$ is removed from $M_{C}^{n}$ if there is a adjacent node $u'$ of $u$ in $P_{C}$,
-but there exists no adjacent node $w'$ of $w$ in $G$ such that $(u',w')\in M_{C}^{n}$.
-Therefore, $(u,w)$ must be removed from $M^{n}$ as $E_{P^{C}} \subseteq E_{P}$,
-that is, the edge $(u,u')$ in $E_{P^{C}}$ must belong to $E_{P}$.
-Thus, we have $M^{n+1}\subseteq M_{C}^{n+1}$.
-
-\vspace{-1.5ex}
-By (1) and (2), we have proven that $M\subseteq\bigcup_{i=1}^{h}M_{i}$.
+The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
+\identifyaffball filters out the balls that cannot match all fragments,	and there are no data updates on the ball.
 
@@
 \vspace{-0.5ex}
-The experimental results on a real-life dataset \youtube are reported here.
 
-{\em \youtube}~\cite{youtubeWeb} contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos.
+We also used another real-life dataset {\em \youtube}~\cite{youtubeWeb} for experimental verification.
+It contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos.
 We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.
 
+\vspace{-1.5ex}
+The experimental results on \youtube are reported here.
+
 \vspace{-1.8ex}
-\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis, \denalk on \youtube \wrt three measurements.
+\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis, \denalk on \youtube \wrt four quality measures.
 The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.

### 2017-09-25 TF-vldb2018/subsec-Qinc.tex

@@
 The proof is deferred to Appendix.
-
-\eat{
-\proofS
-When $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
-\identifyaffball identifies \affballsx who already match with each fragment of $P$;
-Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
-there must exist an update in $\Delta P$ on $P_{fi}$,
-such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
-Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.
-\eop}
 

### 2017-09-25 TF-vldb2018/sec-conclusion.tex

@@
-\vspace{-2ex}
 \section{Conclusion}
@@
 We have proposed team simulation,
-%based on which we have developed an efficient batch algorithm for top-k team formation.
-and also  developed a unified incremental framework to handle continuous pattern and data updates, separately and simultaneously.
+based on which we have developed a \eat{efficient}batch algorithm for top-k team formation.
+We have also  developed a unified incremental framework to handle continuous pattern and data updates, separately and simultaneously.
 We have experimentally verified the effectiveness and efficiency of the batch and incremental algorithms.

### 2017-09-26 TF-vldb2018/sec-appendix.tex

@@
 %\begin{widepage}
-\vspace{-2ex}
+%\vspace{-2ex}
 \begin{center}
@@
 \subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter}
-\includegraphics[scale=0.37]{./fig/youtube-semantic-diameter.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-density}
-\includegraphics[scale=0.37]{./fig/youtube-semantic-density.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-semantic-density.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity}
-\includegraphics[scale=0.37]{./fig/youtube-semantic-capacity.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-link}
-\includegraphics[scale=0.37]{./fig/youtube-semantic-link.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-semantic-link.eps}}
 \vspace{-2.5ex}
@@
 \subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter-varyk}
-\includegraphics[scale=0.37]{./fig/youtube-semantic-diameter-varyk.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter-varyk.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-density-varyk}
-\includegraphics[scale=0.37]{./fig/youtube-semantic-density-varyk.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-semantic-density-varyk.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity-varyk}
-\includegraphics[scale=0.37]{./fig/youtube-semantic-capacity-varyk.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity-varyk.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-link-varyk}
-\includegraphics[scale=0.37]{./fig/youtube-semantic-link-varyk.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-semantic-link-varyk.eps}}
 \vspace{-2.0ex}
@@
 \end{center}
-\vspace{-2.0ex}
+\vspace{-3.0ex}
 \caption{Performance evaluation of \optgrouprec for top-$k$ team formation problem}
@@
 %\begin{widepage}
-\vspace{-1.5ex}
+%\vspace{-1.5ex}
 \begin{center}
@@
 \subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-pattern-deletion.eps}}
-\hspace{-1.7ex}
+\includegraphics[scale=0.38]{./fig/youtube-pattern-deletion.eps}}
+\hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-pattern-insertion.eps}}
-\hspace{-1.7ex}
+\includegraphics[scale=0.38]{./fig/youtube-pattern-insertion.eps}}
+\hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-pattern-capchange.eps}}
-\hspace{-1.7ex}
-\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)}]{\label{fig-exp-patinc-hyb-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-pattern-hybrid.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-pattern-capchange.eps}}
+\hspace{0.2ex}
+\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)\hspace{-8.5ex}}]{\label{fig-exp-patinc-hyb-youtube}
+\includegraphics[scale=0.38]{./fig/youtube-pattern-hybrid.eps}}
 \vspace{-2.5ex}
@@
 \subfigure[{\scriptsize Varying $|\Delta G|$ (deletions)}]{\label{fig-exp-datainc-del-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-data-deletion.eps}}
-\hspace{-1.7ex}
+\includegraphics[scale=0.38]{./fig/youtube-data-deletion.eps}}
+\hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|\Delta G|$ (insertions)}]{\label{fig-exp-datainc-ins-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-data-insertion.eps}}
-\hspace{-1.7ex}
-\subfigure[{\scriptsize Varying $|\Delta G|$ (hybrid updates)}]{\label{fig-exp-datainc-hyb-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-data-hybrid.eps}}
-\hspace{-1.7ex}
-\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ (simultaneous)}\hspace{-4.5ex}]{\label{fig-exp-hyb-patdata-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-pattern-data.eps}}
+\includegraphics[scale=0.38]{./fig/youtube-data-insertion.eps}}
+\hspace{0.2ex}
+\subfigure[{\scriptsize Varying $|\Delta G|$ (hybrid updates)}\hspace{-5.5ex}]{\label{fig-exp-datainc-hyb-youtube}
+\includegraphics[scale=0.38]{./fig/youtube-data-hybrid.eps}}
+\hspace{0.2ex}
+\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ (simultaneous)}\hspace{-8.5ex}]{\label{fig-exp-hyb-patdata-youtube}
+\includegraphics[scale=0.38]{./fig/youtube-pattern-data.eps}}
 \vspace{-2.5ex}
@@
 \subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-pattern-multi.eps}}
-%\hspace{-1.7ex}
+\includegraphics[scale=0.38]{./fig/youtube-pattern-multi.eps}}
+\hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-data-multi.eps}}
-%\hspace{-1.7ex}
-\subfigure[{\scriptsize Varying $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-5.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
-\includegraphics[scale=0.395]{./fig/youtube-pattern-data-multi.eps}}
-%\hfill
-\vspace{-2.5ex}
+\includegraphics[scale=0.38]{./fig/youtube-data-multi.eps}}
+\hspace{0.2ex}
+\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
+\includegraphics[scale=0.38]{./fig/youtube-pattern-data-multi.eps}}
+\hspace{0.2ex}
+\subfigure[{\scriptsize Storage sizes}]{\label{fig-exp-extraspace}
+\includegraphics[scale=0.38]{./fig/youtube-space.eps}}
+\vspace{-2ex}
 
 \end{center}
-\vspace{-2.0ex}
+\vspace{-3.0ex}
 \caption{Performance evaluation of \inc for dynamic top-$k$ team formation problem (\youtube)}
@@
 %\end{widepage}
-\vspace{-4ex}
+\vspace{-3.0ex}
 \end{figure*}
@@
 \stitle{Exp-2: Efficiency of \inc for one set of updates}.
-Varying the amount of updates in one update set from 4.5\% to 45\% for pattern updates, 2.5\% to 25\% for data updates, and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
-We find \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 31.5\%, 20\% and (27\%, 15\%).
+Varying the amount of updates in one update set from 4.5\% to 49.5\% for pattern updates, 2.5\% to 27.5\% (resp.
+3\% to 33\%) for data insertions and hybrid data updates (resp.
+data deletions), and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous pattern and data updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
+We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%).
 %for hybrid pattern, hybrid data, and simultaneous pattern and data updates.

### 2017-09-26 TF-vldb2018/sec-expt.tex

@@
 \subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-diameter}
-\includegraphics[scale=0.37]{./fig/citation-semantic-diameter.eps}}
+\includegraphics[scale=0.38]{./fig/citation-semantic-diameter.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-density}
-\includegraphics[scale=0.37]{./fig/citation-semantic-density.eps}}
+\includegraphics[scale=0.38]{./fig/citation-semantic-density.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-capacity}
-\includegraphics[scale=0.37]{./fig/citation-semantic-capacity.eps}}
+\includegraphics[scale=0.38]{./fig/citation-semantic-capacity.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $|V_{P}|$ (\citationd)}]{\label{fig-exp-semantic-citation-link}
-\includegraphics[scale=0.37]{./fig/citation-semantic-link.eps}}
+\includegraphics[scale=0.38]{./fig/citation-semantic-link.eps}}
 \vspace{-2.5ex}
@@
 \subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-diameter-varyk}
-\includegraphics[scale=0.37]{./fig/citation-semantic-diameter-varyk.eps}}
+\includegraphics[scale=0.38]{./fig/citation-semantic-diameter-varyk.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-density-varyk}
-\includegraphics[scale=0.37]{./fig/citation-semantic-density-varyk.eps}}
+\includegraphics[scale=0.38]{./fig/citation-semantic-density-varyk.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-capacity-varyk}
-\includegraphics[scale=0.37]{./fig/citation-semantic-capacity-varyk.eps}}
+\includegraphics[scale=0.38]{./fig/citation-semantic-capacity-varyk.eps}}
 \hspace{0.2ex}
 \subfigure[{\scriptsize Varying $k$ (\citationd)}]{\label{fig-exp-semantic-citation-link-varyk}
-\includegraphics[scale=0.37]{./fig/citation-semantic-link-varyk.eps}}
+\includegraphics[scale=0.38]{./fig/citation-semantic-link-varyk.eps}}
 \vspace{-2.0ex}
@@
 
+\vspace{-0.2ex}
 \stitle{Experimental Settings.} We use the following settings.
@@
 %We used the following real-life and synthetic datasets.
-\etitle{Data graphs.} We used a real-life and a synthetic dataset.
+\vspace{-0.3ex}
+\etitle{Data graphs.} We used two real-life and a synthetic dataset.
 
@@
 %Given $n, d$, and $l$, the generator produces a graph with $n$ nodes, $n*d/2$ edges, and the nodes are labeled from a set of $l$ labels.
+
+\ni (3) We also used real-life data \youtube~\cite{youtubeWeb} (see Appendix).
 
@@
 We used a PC with Intel Core i5-4570 CPU and 16GB of memory. We randomly generated 3 sets of input and repeated 5 times for each test. The average is reported here.
-All the findings on \youtube are reported in the Appendix.
+%We also used another real-life dataset \youtube, which will be reported in the Appendix.
 
@@
 \stitle{Exp-2: Effectiveness of \optgrouprec}.
-We generated pattern graphs for \optgrouprec, and the corresponding queries (labels requirements) for \mindia, \minsumdis and \denalk, and manually checked the quality of matches returned by them.
+We generated pattern graphs for \optgrouprec, and the corresponding queries (labels requirements) for \mindia, \minsumdis and \denalk, and checked the quality of matches returned by them.
 \looseness=-1

### 2017-09-26 TF-vldb2018/sec-appendix.tex

@@
 {\textbf{1. Proof of Theorem~\ref{thm-tsim-radius}}}
+
+\revise{
+Proofs
+
+}
 
@@
 
+\revise{
 The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
@@
 It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
-Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.
+Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.}
 
@@
 
-We will prove the proposition by contradiction.
-When $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
+\warn{The proposition is correct as when $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.}
 \identifyaffball identifies \affballsx who already match with each fragment of $P$;
@@
 The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
-\identifyaffball filters out the balls that cannot match all fragments,	and there are no data updates on the ball.
+\identifyaffball filters out the balls that cannot match all $h$ pattern fragments,	and there are no data updates on the ball.
 

### 2017-09-26 TF-vldb2018/sec-dynamicTopk.tex

@@
 
+\vspace{0.8ex}
 Intuitively, we want (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.

### 2017-09-26 TF-vldb2018/sec-appendix.tex

@@
 
-\revise{
 The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
@@
 
+\revise{
 \vspace{-2.5ex}
@@
 Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.}
+
+\eat{%%%% Wrong proof %%%
+\vspace{-2.5ex}
+\etitle{Lower bound.}
+We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
+by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.
+
+\vspace{-2ex}
+An instance of the minimum cut problem is given an undirected graph $H=(V_{H},E_{H})$ and a positive integer $m$,
+to find a set $S \subseteq E_{H}$ of edges whose removal leaves two disjoint connected components, with $|S|\leq m$.
+
+\vspace{-2ex}
+Given an instance of the minimum cut problem,
+we construct an instance of $h$-fragmentation problem.
+It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
+Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.
+}%%EAT
 

### 2017-09-26 TF-vldb2018/sec-appendix.tex

@@
 
-\vspace{-2ex}
+\vspace{-1ex}
 An instance of the minimum cut problem is given an undirected graph $H=(V_{H},E_{H})$ and a positive integer $m$,
@@
 
-\vspace{-2ex}
+\vspace{-1ex}
 Given an instance of the minimum cut problem,
@@
 
-\warn{The proposition is correct as when $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.}
+The proposition is correct as when $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
 \identifyaffball identifies \affballsx who already match with each fragment of $P$;

### 2017-09-26 TF-vldb2018/sec-dynamicTopk.tex

--- 2017-09-25 TF-vldb2018/sec-dynamicTopk.tex
@@
 
-Intuitively, we want (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.
+\vspace{0.8ex}
+\revise{During the incremental process, we typically want} (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.
 Thus we define the {\em pattern fragmentation} problem. Given $P$ and a positive integer $h$, it is to find
 an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized. 
-\revise{The bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size
+\revise{Intuitively, the bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size
 	while minimizing the cut size between pattern fragments.}
@@
 
-\vspace{0.5ex}
 The problem is intractable, as shown below.

### 2017-09-26 TF-vldb2018/sec-intro.tex

@@
 \revise{
-\stab (2) We develop a \warn{quadruplicate} batch algorithm with two optimization techniques for computing top-$k$ teams via team simulation.} 
+\stab (2) We develop a batch algorithm with two optimization techniques for computing top-$k$ teams via team simulation.} 
 We also study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching (Section~\ref{sec-tsimAlg}).

### 2017-09-26 TF-vldb2018/sec-tsimAlg.tex

@@
 \revise{
-We devise a \warn{quadruplicate} time algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for strong simulation~\cite{MaCFHW14}.}
+We devise an algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for strong simulation~\cite{MaCFHW14}.}
 
@@
 %centered at each node in $G$ with radius $t$ varying from 1 to $r$.
-However, it is extremely costly to construct all such balls, \ie $r|V|$ balls, to compute perfect subgraphs residing in them. 
+However, it is extremely costly to construct all such balls, \ie $r\cdot|V|$ balls, to compute perfect subgraphs residing in them. 
 Instead, \grouprec only constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$ 

### 2017-09-27 TF-vldb2018/sec-appendix.tex

@@
 \noindent
-{\textbf{3. Algorithm \kw{PFrag} (Section~\ref{sec-dynamictopk})}}
+{\textbf{2. Algorithm \kw{PFrag} (Section~\ref{sec-dynamictopk})}}
 
@@
 \revise{
-Proofs
+We will prove Theorem~\ref{thm-tsim-radius} (1) firstly.
+We know that $P\eps \ball{[v, t]}$, and $M_t$ is a match relation for $P$ in $\ball{[v, t]}$.
+Since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, 
+there must exist a binary relation $M_r$ such that for any $(u, v) \in M_t$, where $u$ is a pattern node and $v$ is the matched data node of $u$ in $\ball{[v, t]}$, 
+$(u, v) \in M_r$ holds, where $v$ is the matched data node of $u$ in $\ball{[v, r]}$, \ie $M_t \subset M_r$.
+Since $M_t$ is a match relation for $P$ in $\ball{[v, t]}$ and $M_t \subset M_r$, by the definition of graph simulation, then $P\eps \ball{[v, r]}$ and $M_r$ is a match relation for $P$ in $\ball{[v, r]}$.
 
+\vspace{-1ex}	
+We will prove Theorem (2) using the lemma below.
+
+\vspace{-2.7ex}
+\begin{lemma}
+	\label{lemma-innerball}
+	For any data graphs $G_1$ and $G_2$, pattern graph $P$. If $G_1$ is a subgraph of $G_2$,
+	then $M_1 \subset M_2$, where $M_i$ $(i=1,2)$ is the maximum match relation for $P$ in $G_i$ via graph simulation. 
+\end{lemma}
+\vspace{-2.5ex}
+
+We next prove the lemma and then use the lemma to prove Theorem~\ref{thm-tsim-radius} (2).
+
+\vspace{-2.3ex}
+\stitle{Proofs of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
+We know that $G_1$ is a subgraph of $G_2$, and suppose $M_1 \not\subset M_2$.
+That is, there exists a pair of nodes $(u, v) \in M_1$, where $u$ is a pattern node 
+and $v$ is the matched data node of $u$, but $(u, v) \not\in M_2$.
+By the definition of graph simulation, from $(u, v) \in M_1$, we know that for any child node $u'$ of $u$ in $P$,
+there exists a child node $v'$ of $v$ in $G_1$ such that $(u', v') \in M_1$.
+From $(u, v) \not\in M_2$, we know that there exists a child node $u''$ of $u$ in $P$, 
+but there exist no child nodes $v''$ of $v$ in $G_2$, such that $(u'', v'') \eps M_2$.
+The process to compute maximum match relations for graph simulation is a recursive process to 
+remove invalid matches from the initialized match relations $M$.
+Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, so $(u, v)$ is removed from $M_2$.
+As $G_1$ is a subgraph of $G_2$, so $(u, v)$ should also be removed from $M_1$, 
+such that $(u, v) \not\in M_1$.
+This contradicts the assumption that $(u, v) \in M_1$, and we get the lemma proved.
+\eop
+
+\vspace{-1.5ex}
+By Lemma~\ref{lemma-innerball}, since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, then $M' \subset M$.
+By the definition of match graphs, since $M' \subset M$, then $G'_s$ is a subgraph of $G_s$.
 }

### 2017-09-27 TF-vldb2018/sec-appendix.tex

@@
 We will prove Theorem~\ref{thm-tsim-radius} (1) firstly.
-We know that $P\eps \ball{[v, t]}$, and $M_t$ is a match relation for $P$ in $\ball{[v, t]}$.
+We know that $P\eps \ball{[v, t]}$, and suppose that $M_t$ is a binary match relation for $P$ in $\ball{[v, t]}$.
 Since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, 
@@
 \vspace{-1.5ex}
-\begin{figure}[h!]
+\begin{figure}[ht!]
 \label{fig-inc-complexity-data}
@@
 \caption{Unboundedness of unit data update}
-\vspace{-2ex}
+\vspace{-4ex}
 \end{figure}
@@
 \vspace{-1ex}
-\begin{figure}[h!]
+\begin{figure}[ht!]
 \label{fig-inc-complexity-pattern}
@@
 \caption{Unboundedness of unit pattern update}
-\vspace{-1.5ex}
+\vspace{-4ex}
 \end{figure}
@@
 \hspace{0.2ex}
-\subfigure[{\scriptsize Storage sizes}]{\label{fig-exp-extraspace}
+\subfigure[{\scriptsize Storage sizes}]{\label{fig-exp-youtube-extraspace}
 \includegraphics[scale=0.38]{./fig/youtube-space.eps}}
@@
 \vspace{-1.8ex}
-\stitle{Exp-4: Physical storage of auxiliary structures}. It takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which need 114MB space to store itself,
+\stitle{Exp-4: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-youtube-extraspace},
+it takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which need 114MB space to store itself,
 \ie 50.8\% compared with the original dataset.

### 2017-09-27 TF-vldb2018/sec-tsimAlg.tex

@@
 If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
-otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see Appendix),
+otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see full version~\cite{fullvldb18}),
 an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
-It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the incremental algorithm in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11, see Appendix).}
+It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the incremental algorithm in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11, see~\cite{fullvldb18}).}
 %Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}

### 2017-09-27 TF-vldb2018/subsec-Ginc.tex

@@
 
-\eat{
-\proofS
-The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
-\identifyaffball filters out the balls that cannot match all fragments,
-and there are no data updates on the ball.
-\eop}
-
-The proof is deferred to Appendix.
+The proof is deferred to the full version~\cite{fullvldb18}.
 
@@
 \incd is overall in
-$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}\bigcup_{i\in[1,h]}$ $r|M(P_{fi}, \widehat{G\oplus\Delta G})|$+$r|P||\affballsx|)$ time \wrt $\Delta G$, while $r$ is small, \ie 2 or 3  (See Appendix).
+$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}\bigcup_{i\in[1,h]}$ $r|M(P_{fi}, \widehat{G\oplus\Delta G})|$+$r|P||\affballsx|)$ time \wrt $\Delta G$, while $r$ is small, \ie 2 or 3  (See~\cite{fullvldb18}).
 \looseness=-1

### 2017-09-27 TF-vldb2018/subsec-Qinc.tex

@@
 
-The proof is deferred to Appendix.
+The proof is deferred to the full version~\cite{fullvldb18}.
 
@@
 The correctness of \incp is assured by the correctness of \identifyaffball (Proposition~\ref{prop-canaffballs}), \incmatch, \comb, and early return property (Lemma~\ref{lemma-approximation-bound}).
-\incp is in $O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|$ + $r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|$) + $r|P \oplus \Delta P||\affballsx|$+$|\Delta P|)$ time \wrt $\Delta P$, while $r$ is small, \ie 2 or 3 (See Appendix).
+\incp is in $O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|$ + $r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|$) + $r|P \oplus \Delta P||\affballsx|$+$|\Delta P|)$ time \wrt $\Delta P$, while $r$ is small, \ie 2 or 3 (See full version~\cite{fullvldb18}).
 

### 2017-09-27 TF-vldb2018/sec-tsimAlg.tex

@@
 an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
-It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the incremental algorithm in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11, see~\cite{fullvldb18}).}
+It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the data incremental algorithms in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11).}
 %Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}

### 2017-09-27 TF-vldb2018/sec-appendix.tex

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tb!]
-%\begin{widepage}
-%\vspace{-2ex}
-\begin{center}
-%\hspace{-5.5ex}
-\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter}
-\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-density}
-\includegraphics[scale=0.38]{./fig/youtube-semantic-density.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity}
-\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-link}
-\includegraphics[scale=0.38]{./fig/youtube-semantic-link.eps}}
-\vspace{-2.5ex}
-
-%\hspace{-5.5ex}
-\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter-varyk}
-\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter-varyk.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-density-varyk}
-\includegraphics[scale=0.38]{./fig/youtube-semantic-density-varyk.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity-varyk}
-\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity-varyk.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-link-varyk}
-\includegraphics[scale=0.38]{./fig/youtube-semantic-link-varyk.eps}}
-\vspace{-2.0ex}
-
-\end{center}
-\vspace{-3.0ex}
-\caption{Performance evaluation of \optgrouprec for top-$k$ team formation problem}
-\label{exp-semantic-effectiveness-youtube}
-%\end{widepage}
-%\vspace{-0.5ex}
-\end{figure*}
-
-\begin{figure*}[tb!]
-%\begin{widepage}
-%\vspace{-1.5ex}
-\begin{center}
-%\hspace{-5.5ex}
-\subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-pattern-deletion.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-pattern-insertion.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-pattern-capchange.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)\hspace{-8.5ex}}]{\label{fig-exp-patinc-hyb-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-pattern-hybrid.eps}}
-\vspace{-2.5ex}
-
-%\hspace{-5.5ex}
-\subfigure[{\scriptsize Varying $|\Delta G|$ (deletions)}]{\label{fig-exp-datainc-del-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-data-deletion.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $|\Delta G|$ (insertions)}]{\label{fig-exp-datainc-ins-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-data-insertion.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $|\Delta G|$ (hybrid updates)}\hspace{-5.5ex}]{\label{fig-exp-datainc-hyb-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-data-hybrid.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ (simultaneous)}\hspace{-8.5ex}]{\label{fig-exp-hyb-patdata-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-pattern-data.eps}}
-\vspace{-2.5ex}
-
-%\hspace{-5.5ex}
-\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-pattern-multi.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-data-multi.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
-\includegraphics[scale=0.38]{./fig/youtube-pattern-data-multi.eps}}
-\hspace{0.2ex}
-\subfigure[{\scriptsize Storage sizes}]{\label{fig-exp-youtube-extraspace}
-\includegraphics[scale=0.38]{./fig/youtube-space.eps}}
-\vspace{-2ex}
-
-\end{center}
-\vspace{-3.0ex}
-\caption{Performance evaluation of \inc for dynamic top-$k$ team formation problem (\youtube)}
-\label{exp-inc-youtube}
-%\end{widepage}
-\vspace{-3.0ex}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \noindent
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tb!]
+	%\begin{widepage}
+	%\vspace{-2ex}
+	\begin{center}
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-density}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-density.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-link}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-link.eps}}
+		\vspace{-2.5ex}
+
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter-varyk}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter-varyk.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-density-varyk}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-density-varyk.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity-varyk}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity-varyk.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-link-varyk}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-link-varyk.eps}}
+		\vspace{-2.0ex}
+
+	\end{center}
+	\vspace{-3.0ex}
+	\caption{Performance evaluation of \optgrouprec for top-$k$ team formation problem}
+	\label{exp-semantic-effectiveness-youtube}
+	%\end{widepage}
+	%\vspace{-0.5ex}
+\end{figure*}
+
+\begin{figure*}[tb!]
+	%\begin{widepage}
+	%\vspace{-1.5ex}
+	\begin{center}
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-deletion.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-insertion.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-capchange.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)\hspace{-8.5ex}}]{\label{fig-exp-patinc-hyb-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-hybrid.eps}}
+		\vspace{-2.5ex}
+
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $|\Delta G|$ (deletions)}]{\label{fig-exp-datainc-del-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-data-deletion.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta G|$ (insertions)}]{\label{fig-exp-datainc-ins-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-data-insertion.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta G|$ (hybrid updates)}\hspace{-5.5ex}]{\label{fig-exp-datainc-hyb-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-data-hybrid.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ (simultaneous)}\hspace{-8.5ex}]{\label{fig-exp-hyb-patdata-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-data.eps}}
+		\vspace{-2.5ex}
+
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-multi.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-data-multi.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-data-multi.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Storage sizes}]{\label{fig-exp-youtube-extraspace}
+			\includegraphics[scale=0.38]{./fig/youtube-space.eps}}
+		\vspace{-2ex}
+
+	\end{center}
+	\vspace{-3.0ex}
+	\caption{Performance evaluation of \inc for dynamic top-$k$ team formation problem (\youtube)}
+	\label{exp-inc-youtube}
+	%\end{widepage}
+	\vspace{-3.0ex}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \vspace{1ex}
 \noindent
-{\large \textbf{Appendix C: Extra Experiments}}
+{\large \textbf{Appendix C: Detailed Correctness \& Complexity Analysis}}
+\label{sec-apd-complexity}
+
+\noindent
+{\textbf{1. Algorithm \incp (Section~\ref{subsec-Qinc})}}
+
+The correctness of \incp \wrt $\Delta P$ is assured by
+the correctness of (a) \identifyaffball (by Proposition~\ref{prop-canaffballs});
+(b) \incmatch, which is assured by the correctness of \rgraphsim that has been proved, and of \patedgeinsert. Indeed, \patedgeinsert only removes
+nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
+(c) \comb, whose analysis follows the same way as for \patedgeinsert; and
+(d) the early return property (by Lemma~\ref{lemma-approximation-bound}).
+
+\vspace{-1ex}
+Procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$ time, where it takes $O(2^{h}\cdot|\Delta P|)$ time to update \bfc, $O(2^{h}\cdot h)$ to do the AND-operation, and $O(||\affballsx||)$ to identify \affballsx.
+%Thus, procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$.
+As $h$ is typically small, \eg 2 to 5, thus \identifyaffball is in $O(|\Delta P|+||\affballsx||)$;
+\patedgeinsert is in $O(|M(P_{fi}, \ball{[v,r]})|+|V_{P_{fi}}||E_{\ball{[v,r]}}|)$ time.
+Indeed, the recursive process for checking invalid nodes in $M(P_{fi}, \ball{[v,r]})$ is bounded by $O(|V_{P_{fi}}||E_{\ball{[v,r]}}|)$,
+and the process to update $M(P_{fi}, \ball{[v,r]})$ is bounded by the size of its changes, which is monotonically decreasing;
+According to \patedgeinsert,
+\comb is in $O(|\bigcup^{h}_{i=1} rM(P_{fi}\oplus\Delta P_{fi},\ball{[v,r]})|+r|V_{P\oplus \Delta P}||E_{\ball{[v,r]}}|)$ time.
+
+\vspace{-1ex}
+Putting these together, algorithm \incp is in
+$O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|+r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|) + r|P \oplus \Delta P||\affballsx|$ +$|\Delta P|)$ time \wrt $\Delta P$.
+
+\noindent
+{\textbf{2. Algorithm \incd (Section~\ref{subsec-Ginc})}}
+
+The correctness of \incd \wrt $\Delta G$ is assured by the correctness of
+\identifyaffball (by Proposition~\ref{prop-affected-datainc}) and procedures \incmatch and \comb (proved along the same lines as for pattern updates).
+
+\vspace{-1ex}
+One can verify that procedure \identifyaffball is in $O(|\affballsx|)$,
+\incmatch for all fragments and all \affballsx is in $O(|P||\affballsx|)$ time, and \comb is in $O(\bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|$ + $r|V_{P}||E_{\widehat{G\oplus\Delta G}}|)$ time.
+Thus, algorithm \incd is in
+$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|+r|P||\affballsx|)$ time \wrt $\Delta G$.
+\looseness=-1
+
+\vspace{1ex}
+\noindent
+{\large \textbf{Appendix D: Extra Experiments}}
 \label{sec-apd-exp}

### 2017-09-27 TF-vldb2018/subsec-Ginc.tex

@@
 
-\eat{
-The correctness of \incd \wrt $\Delta G$ is assured by the correctness of
-\identifyaffball (by Proposition~\ref{prop-affected-datainc}) and procedures \incmatch and \comb (proved along the same lines as for pattern updates).
-
-One can verify that procedure \identifyaffball is in $O(|\affballsx|)$ time,
-\incmatch is in $O(|P||\affballsx|)$ time, and \comb is in $O(\bigcup_{i\in[1,h]}|M(P_{fi}, \widehat{G\oplus\Delta G})|)$ time.
-Thus, algorithm \incd is in
-$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}|M(P_{fi}, \widehat{G\oplus\Delta G})|+|P||\affballsx|)$ time \wrt $\Delta G$.}%%%EAT
-
 \stitle{Remarks}. Note that the running time of \incd is determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$,

### 2017-09-27 TF-vldb2018/subsec-Qinc.tex

@@
 
-\eat{
-\stitle{Correctness \& complexity analysis}. The correctness of \incp \wrt $\Delta P$ is assured by
-the correctness of (a) \identifyaffball (by Proposition~\ref{prop-canaffballs});
-(b) \incmatch, which is assured by the correctness of \rgraphsim that has been proved previously, and of \patedgeinsert. Indeed, \patedgeinsert only removes
-nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
-(c) \comb, whose analysis follows the same way as for \patedgeinsert; and
-(d) the early return property (by Lemma~\ref{lemma-approximation-bound}).
-
-Procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$ time, where it takes $O(2^{h}\cdot|\Delta P|)$ time to update \bfc, $O(2^{h}\cdot h)$ to do the AND-operation, and $O(||\affballsx||)$ to identify \affballsx.
-%Thus, procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$.
-As $h$ is typically small, \eg 2 to 5, thus \identifyaffball is in $O(|\Delta P|+||\affballsx||)$;
-\patedgeinsert is in $O(|M(P_{fi}, \ball{[v,r]})|+|V_{P_{fi}}||E_{\ball{[v,r]}}|)$ time.
-Indeed, the recursive process for checking invalid nodes in $M(P_{fi}, \ball{[v,r]})$ is bounded by $O(|V_{P_{fi}}||E_{\ball{[v,r]}}|)$,
-and the process to update $M(P_{fi}, \ball{[v,r]})$ is bounded by the size of its changes, which is monotonically decreasing;
-According to \patedgeinsert,
-\comb is in $O(|\bigcup^{h}_{i=1} M(P_{fi}\oplus\Delta P_{fi},\ball{[v,r]})|+|V_{P\oplus \Delta P}||E_{\ball{[v,r]}}|)$ time.
-
-Putting these together, algorithm \incp is in
-$O(|\Delta P|$ + $\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|+|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|) + |P \oplus \Delta P||\affballsx|)$ time \wrt $\Delta P$.
-}%%%EAT
-
 %\vspace{0.5ex}

### 2017-09-27 TF-vldb2018/sec-appendix.tex

--- 2017-09-27 TF-vldb2018/sec-appendix.tex
@@
 
-\revise{
 We will prove Theorem~\ref{thm-tsim-radius} (1) firstly.
@@
 By the definition of match graphs, since $M' \subset M$, then $G'_s$ is a subgraph of $G_s$.
-}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tb!]
+	%\begin{widepage}
+	%\vspace{-2ex}
+	\begin{center}
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-density}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-density.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|V_{P}|$ (\youtube)}]{\label{fig-exp-semantic-youtube-link}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-link.eps}}
+		\vspace{-2.5ex}
+
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-diameter-varyk}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-diameter-varyk.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-density-varyk}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-density-varyk.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-capacity-varyk}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-capacity-varyk.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $k$ (\youtube)}]{\label{fig-exp-semantic-youtube-link-varyk}
+			\includegraphics[scale=0.38]{./fig/youtube-semantic-link-varyk.eps}}
+		\vspace{-2.0ex}
+
+	\end{center}
+	\vspace{-3.0ex}
+	\caption{Performance evaluation of \optgrouprec for top-$k$ team formation problem}
+	\label{exp-semantic-effectiveness-youtube}
+	%\end{widepage}
+	%\vspace{-0.5ex}
+\end{figure*}
+
+\begin{figure*}[tb!]
+	%\begin{widepage}
+	%\vspace{-1.5ex}
+	\begin{center}
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-deletion.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-insertion.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-capchange.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)\hspace{-8.5ex}}]{\label{fig-exp-patinc-hyb-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-hybrid.eps}}
+		\vspace{-2.5ex}
+
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $|\Delta G|$ (deletions)}]{\label{fig-exp-datainc-del-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-data-deletion.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta G|$ (insertions)}]{\label{fig-exp-datainc-ins-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-data-insertion.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta G|$ (hybrid updates)}\hspace{-5.5ex}]{\label{fig-exp-datainc-hyb-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-data-hybrid.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ (simultaneous)}\hspace{-8.5ex}]{\label{fig-exp-hyb-patdata-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-data.eps}}
+		\vspace{-2.5ex}
+
+		%\hspace{-5.5ex}
+		\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-multi.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-data-multi.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
+			\includegraphics[scale=0.38]{./fig/youtube-pattern-data-multi.eps}}
+		\hspace{0.2ex}
+		\subfigure[{\scriptsize Storage sizes}]{\label{fig-exp-youtube-extraspace}
+			\includegraphics[scale=0.38]{./fig/youtube-space.eps}}
+		\vspace{-2ex}
+
+	\end{center}
+	\vspace{-3.0ex}
+	\caption{Performance evaluation of \inc for dynamic top-$k$ team formation problem (\youtube)}
+	\label{exp-inc-youtube}
+	%\end{widepage}
+	\vspace{-3.0ex}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \vspace{1ex}
 \noindent
-{\large \textbf{Appendix C: Extra Experiments}}
+{\large \textbf{Appendix C: Detailed Correctness \& Complexity Analysis}}
+\label{sec-apd-complexity}
+
+\noindent
+{\textbf{1. Algorithm \incp (Section~\ref{subsec-Qinc})}}
+
+The correctness of \incp \wrt $\Delta P$ is assured by
+the correctness of (a) \identifyaffball (by Proposition~\ref{prop-canaffballs});
+(b) \incmatch, which is assured by the correctness of \rgraphsim that has been proved in Section~\ref{sec-tsimAlg}, and the correctness of of \patedgeinsert. Indeed, \patedgeinsert only removes
+nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
+(c) \comb, whose analysis follows the same way as that for \patedgeinsert; and
+(d) the early return property (by Lemma~\ref{lemma-approximation-bound}).
+
+\vspace{-1.5ex}
+Procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$ time, where it takes $O(2^{h}\cdot|\Delta P|)$ time to update \bfc, $O(2^{h}\cdot h)$ to do the AND-operation, and $O(||\affballsx||)$ to identify \affballsx.
+%Thus, procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$.
+As $h$ is typically small, \eg 2 to 5, thus \identifyaffball is in $O(|\Delta P|+||\affballsx||)$;
+\patedgeinsert is in $O(|M(P_{fi}, \ball{[v,r]})|+|V_{P_{fi}}||E_{\ball{[v,r]}}|)$ time.
+Indeed, the recursive process for checking invalid nodes in $M(P_{fi}, \ball{[v,r]})$ is bounded by $O(|V_{P_{fi}}||E_{\ball{[v,r]}}|)$,
+and the process to update $M(P_{fi}, \ball{[v,r]})$ is bounded by the size of its changes, which is monotonically decreasing;
+According to \patedgeinsert,
+\comb is in $O(|\bigcup^{h}_{i=1} rM(P_{fi}\oplus\Delta P_{fi},\ball{[v,r]})|+r|V_{P\oplus \Delta P}||E_{\ball{[v,r]}}|)$ time.
+
+\vspace{-1.5ex}
+Putting these together, algorithm \incp is in
+$O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|+r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|) + r|P \oplus \Delta P||\affballsx|$ +$|\Delta P|)$ time \wrt $\Delta P$.
+
+\noindent
+{\textbf{2. Algorithm \incd (Section~\ref{subsec-Ginc})}}
+
+The correctness of \incd \wrt $\Delta G$ is assured by the correctness of
+\identifyaffball (by Proposition~\ref{prop-affected-datainc}) and procedures \incmatch and \comb,
+which can be proved along the same lines as for pattern updates.
+
+\vspace{-1.5ex}
+One can verify that procedure \identifyaffball is in $O(|\affballsx|)$,
+\incmatch for all fragments and all \affballsx is in $O(|P||\affballsx|)$ time, and \comb is in $O(\bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|$ + $r|V_{P}||E_{\widehat{G\oplus\Delta G}}|)$ time.
+Therefore, algorithm \incd is in
+$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|+r|P||\affballsx|)$ time \wrt $\Delta G$.
+
+\vspace{1ex}
+\noindent
+{\large \textbf{Appendix D: Extra Experiments}}
 \label{sec-apd-exp}

### 2017-09-27 TF-vldb2018/sec-expt.tex

@@
 
-\ni (3) We also used real-life data \youtube~\cite{youtubeWeb} (see Appendix).
+\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb} (see~\cite{fullvldb18}).
 
@@
 \sstab(2) Our batch algorithm for  top-$k$ team formation is efficient,
-\eg it took 110s when $|V|=1.39M$ and $|V_P|=10$.
+\eg it took 116s when $|V|=1.39M$ and $|V_P|=10$.
 
@@
 and it is more promising than its batch counterpart,
-even (a) when changes are 34\% for pattern updates, 31\% for data updates, and (25\%, 22\%) for simultaneous pattern and data updates on average,
+even (a) when changes are 36\% for pattern updates, 34\% for data updates, and (25\%, 22\%) for simultaneous pattern and data updates on average,
 and (b) when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuously simultaneous pattern and data updates on average.

### 2017-09-27 TF-vldb2018/sec-intro.tex

@@
 We find that (a) our method is able to identify more sensible teams than existing team formation methods \wrt \eat{three} practical measurements,
-and (b) our incremental algorithm outperforms our batch algorithm, even when changes reach 34\% for pattern updates, 31\% for data updates and (25\%, 22\%) for simultaneous pattern and data updates, and when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuous simultaneous pattern and data updates, respectively.
+and (b) our incremental algorithm outperforms our batch algorithm, even when changes reach 36\% for pattern updates, 34\% for data updates and (25\%, 22\%) for simultaneous pattern and data updates, and when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuous simultaneous pattern and data updates, respectively.
 
-All detailed proofs are available  in the Appendix.
+All detailed proofs are available  in the full version~\cite{fullvldb18}.
 

### 2017-09-27 TF-vldb2018/sec-intro.tex

@@
 
-\warn{To our knowledge, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
-not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting considered so far.}
+\warn{To our knowledge, no previous work studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
+not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting considered so far.
+\looseness=-1
+}
 

### 2017-09-27 TF-vldb2018/sec-intro.tex

--- 2017-09-27 TF-vldb2018/sec-intro.tex
@@
 \eg the density of the induced subgraph~\cite{GajewarS12,realTeamForm13}.
-Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting that introduces a lower bound on the number individuals with a specific skill in a team, and an upper bound of the team members, respectively.
+Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting that introduces a lower bound on the number of individuals with a specific skill in a team, and an upper bound of the total team members, respectively.
 
@@
 
-\revise{One can verify that none of existing methods suffice to identify the above desired team.
+\revise{One can verify that none of existing methods suffice to identify the above desired teams.
 They can only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13} in search condition (1),
@@
 Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.
-Intuitively, patterns $P$ capture the structural constraint, and we extend graph pattern matching semantics to solve the team formation problem.
+Intuitively, patterns $P$ captures the structural constraint, and we extend graph pattern matching semantics to solve the team formation problem.
 As shown in Fig.~\ref{fig-motivation-example},  the desired team requirement can be expressed by the pattern graph $P_1$ (ignore dashed edges), such that the nodes represent the skill requirements, the edges specify the topology constraint, and the bounds on nodes are the capacity constraint.
@@
 
-\sstab{(1)} When the manager get the match result, \ie the top-$k$ teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$, 
-she may find $P_1$ is too restrictive to find possible matches.
+\sstab{(1)} When the manager gets the match result, \ie the top-$k$ teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$, 
+she may find $P_1$ is too restrictive to find sensible matches.
 Therefore, she enters a pattern update $\Delta P_1$ on $P_1$, composed of an edge 
@@
 \warn{To our knowledge, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
-not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting considered so far.}
+not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting studied so far.} 
+\looseness = -1
 

### 2017-09-28 TF-vldb2018/sec-intro.tex

@@
 pattern and data updates, separately and simultaneously.
-As a basis of \dynteamF, we also investigate the incremental problem for graph pattern queries on pattern updates. 
-The definition can be formulated along the same lines with the existing data incremental problem.
+As a basis of \dynteamF, we also investigate the incremental problem for graph pattern matching on pattern updates. 
+The definition can be formulated along the same line with existing data incremental problems.
 %different with data incremental algorithms that preserve some desirable properties that the recomputation can be {\em bounded}  by the changes in the input and output as the impact of data updates can be localized~\cite{Reps96, FanLMTWW10,FanWW13-tods,FanHT17},

### 2017-09-28 Gruba/01-intro.tex
v2.0
v2.0

\section{\textcolor{red}{Introduction}}
\label{sec:intro}

\begin{comment}
\textbf{Motivation}

\textbf{Example}

\textbf{Challenge}

\textbf{Contribution}

\textcolor{blue}{organization of the sections}

%This section shall look into the principle of each component in Processing Runtime subsystem, putting forth a full-fledged system.

\end{comment}

%zhu begin

The rapid development of social network is accompanied by the generation of tremendous user-generated contents. People not only consume information but also publish or share messages. An interesting function in many existing Social Network Applications is reposting (e.g, reposting someone else's microblog on weibo.com). Modeling reposting behavior is of vital significance for Social Network Applications, which can help them to mine potential benefits, predict bursting events and so on. \par

Modeling reposting behavior has attracted attention from both academia and industry. However, many existing works have certain limitations. First, most of them mainly studied how to model reposting behavior for a single user or for the whole users. Considering the huge amount of users in Social Network , modeling for a single user is not easy. What's more, it can also make our model too particular. Modeling for the whole users is also not a good idea, which may get a inaccuracy model. Secondly, how to extract users's features, especially the extraction of users's interest, is a challenging problem.\par
To this end, we extract each user's features firstly, including user's basic information, behavior information and interests, then perform users clustering to divide users into groups and model reposting behavior of each user group respectively. The main contributions of this work can be summarized as follows:\par
\begin{itemize}
\item   We construct a large collection of microblogs from a real microblog service. It contains users's information, microblog content and part of the social network information of related users.
\item   Instead of modeling for a single user or the whole users, we divide all users into several groups by users clustering and model for each group.
\item	We propose a noval method to extract user interests from user generated texts.
\item	We develop a demo system for visualization of single user's profiling and each group's information.
\end{itemize}

This article is organized as follows: In Section 2, we introduce the framework of our work. We then describe our methodology in section 3, including features extraction, how we cluster users into groups, and how to model reposting behavior. Section 4 presents and discusses the experimental results. Section 5 discusses related work followed by conclusions in Section 6.\par

### 2017-09-28 Gruba/03-fe.tex
v2.0
v2.0

% jing @ 0927
% back to algorithm for interest features
% add motivation, intuition, etc

%clear points
%road map
%detail of each step, with motivation

\section{Feature Extractor}
\label{sec:fe}

With the underlying data in Data Storage subsystem, Feature Extractor is responsible for ``mining'' the user characteristics, resulting three features for each user.
These features are \textit{Info Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Info Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.

\subsection{Info Feature}

\textit{Info Feature} employs a vector $I$ to cover the basic info of user.
\begin{equation}
\label{eq:info}
	I = (\#R_s,\ \#E_s,\ R_{ee},\ \#B_s,\ R_{oc},\ U_t)
\end{equation}
where each variable is illustrated in Table \ref{tbl:fe-info}.
Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} blogs and blogs that are originally created by the user.

\begin{table}[!htb]
\centering
\caption{Illustration of Variables in Info Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
\#$R_s$				& number of followers				\\	\midrule
\#$E_s$				& number of followees				\\	\midrule
\multirow{2}{*}{$R_{ee}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#R_s}{\#E_s}$}	\\
 						&                       									\\	\midrule
\#$B_s$				& number of blogs owned by the user				\\	\midrule
\multirow{2}{*}{$R_{oc}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#(B_s | R(B)==1)}{\#(B_s | R(B)==0)}$}	\\
 						&                       									\\	\midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule              
\end{tabular}
\end{table}

%mutex category
%type 0 is assumed to be representative

%replace 50 and 5 by variables of threshold

\begin{table}[!htb]
\centering
\caption{Category of Info}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{value}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
0                       & $\#E_s \le 50 \ \& \ \#R_s \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_s}{\#R_s} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_s}{\#E_s} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule              
\end{tabular}
\end{table}

\subsection{Behavior Feature}

Unlike \textit{Info Feature}, \textit{Behavior Feature} shows several statistics regarding the user's \retg{} behavior.
Such statistics include:
\begin{itemize}
	\item a value showing the average number of \retd{} blogs per week: $\#W_r$
	\item a normalized vector regarding the time distribution of a user's \retg{} behavior: $P_t\ = (p'_0,\ p'_1,\ ...,\ p'_{11})$, where $p'_0$ is the probability that the \retg{} activity happens from 0am to 2am, $p'_1$ is the probability that the \retg{} activity happens from 2am to 4am, and so on.
	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_g\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} blogs is within 1 min. Ditto for $p''_1$ (1 min to 1 hour), $p''_2$ (1 to 12 hours), $p''_3$ (12 to 24 hours), $p''_4$ (24 to 48 hours) and  $p''_5$ (more than 48 hours).
\end{itemize}

Hence, \textit{Behavior Feature} $H$ per user comes with:
\begin{equation}
\label{eq:beha}
	H = (\#W_r,\ P_t,\ P_g)
\end{equation}
where $\#W_r$, $P_t$ and $P_g$ are illustrated as above.

\subsection{Interest Feature}

Different from the straightforward notions of \textit{Info Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics. 
In short, with a given lexicon consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the probability that the said user matches a \textit{topic}.

\begin{definition}
\label{def:lexi}
A lexicon $L = \{t\}$ consists of a set of topics while each topic $t = \{c\}$ is associated with a list of cell words $\{c\}$. Each cell word $c$ refers to one unique word in $L$.
\end{definition}

\begin{definition}
\label{def:bw}
%used \label{def:blog} previously
With a given user $u$, each blog $b \in B_s(u)$ could be decomposed into a set of words $\{w\}$, i.e., $b = \{w\}$.
\end{definition}

\begin{definition}
\label{def:inte}
The interest feature of a given user is a normalized vector 
\begin{equation}
\label{eq:inte}
P_f\ = (p_0,\ p_1,\ ...,\ p_{x-1})
\end{equation}
in which the said user matches $x$ \textit{topics} in lexicon and $p_i$ refers to the similarity of the user and each matched topic (interest). The definition of such similarity shall be detailed in each scenario (explicit/implicit interest analysis, towards words/topics, etc).
\end{definition}

In \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a blog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, \{t\})$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.

For instance, the following steps depict the ``mining'' process of the interest feature $P_f$ for a user $u$.

\textit{Step 1:} Each blog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.

\textit{Step 2:} Explicit interests are explored. Specifically, every word $w$ is sent to match each cell word $c$ of lexicon topics. 
If $w$ and $c$ are identical, $sim(w, c) = 1$. 
Otherwise, $sim(w, c) = 0$. 
As to the similarity of $b$ against a lexicon topic $t$, it is:
\begin{equation}
\label{eq:bt}
sim(b, t) = \sum_{\substack{i, j}} sim(w_i, c_j)
\end{equation}
where $sim(w_i, c_j)$ refers to the similarity of a word pair.

If $sim(b, t)$ satisfies a certain threshold, topic $t$ is labeled to blog $b$; 
the user $u$ is then discovered having an explicit interest (topic) $t$.
Thus, by looking into the similarity of $b$ against all topics in lexicon, the explicit interests of $u$ is returned, in the form of interest feature (see Definition \ref{def:inte}).

If none of $sim(b, t)$ could meet the threshold, i.e., explicit interest discovery over user $u$ fails, go to \textit{Step 3} and \textit{Step 4} in parallel, so as to ``mine'' the implicit interests of $u$.

\textit{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF \refe{} to calculate the weight distribution of words in blog $b$: 
\begin{equation}
\label{eq:tf}
W_f = \{(w_i, p_i)\}
\end{equation}
where $w_i$ refers to a single word, of which the weight is $p_i$, with $\sum_{\substack{i}} p_i = 1$.

To compute such weight $p_i$ for word $w_i$, a metric $p''_i$ is first calculated as:
\begin{equation}
\label{eq:tf-w}
p''_i = \frac{|b_i|}{|b|} * log(\frac{|D_i|}{|D|})
\end{equation}
in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in blog $b$ and $|b|$ the total occurrences of all words in $b$.
Ditto for $|D_i|$ and $|D|$, except that the scope is the overall dataset, rather than a single blog $b$.

Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight} (see Definition \ref{eq:tf}).
Go to \textit{Step 5}.

\textit{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA \refe{} to result the word weight distribution of blog $b$. 
Unlike TF-IDF \refe{}, Twitter-LDA \refe{} first trains the overall blogs, allocating each blog with a \textit{tag}. 
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\}
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$.
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
Go to \textit{Step 6}.

\textit{Step 5:} TF-IDF \refe{} based similarity is calculated.
For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
\end{equation}
where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and:
\begin{equation}
\label{eq:sim-tf2}
sim(w_i, t) = \sum_{\substack{j}} sim(w_i, c_j)
\end{equation}
Go to \textit{Step 7}.

\textit{Step 6:} Accordingly, Twitter-LDA \refe{} based similarity is available.
Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
\begin{equation}
\label{eq:sim-tw1}
sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
\end{equation}
where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and:
\begin{equation}
\label{eq:sim-tw2}
sim(w'_i, t) = \sum_{\substack{j}} sim(w'_i, c_j)
\end{equation}
Go to \textit{Step 7}.

\textit{Step 7:} Hence, the similarity of a blog $b$ against a lexicon topic $t$ is given by:
\begin{equation}
\label{eq:simbt}
sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t)
\end{equation}
where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF \refe{} and Twitter-LDA \refe{}.
Go to \textit{Step 8}.

\textit{Step 8:} Repeat the above steps (Step 1 to Step 7) for the blog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$. 
Such computation further extends to all the blogs owned by user $u$, such that: 
$\forall b_m \in B_s(u)$, $\forall t_k \in L$, there exists a similarity of $sim(b_m, t_k)$.
Hence, the overall similarity of user $u$ over lexicon topics $\{t\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
\begin{equation}
\label{eq:simul}
S(u, L) = (s_0,\ s_1,\ ...,\ s_{n-1})
\end{equation}
where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic $t_k$, which is given by:
\begin{equation}
\label{eq:simul-2}
s_k = \sum_{\substack{m}} sim(b_m, t_k)
\end{equation}

Among the $n$ dimensions of $S(u,\ L)$, those with top $x$ similarity values are selected to label the implicit interests of user $u$, which results an $x$ dimensional vector $P_f$ as described in Definition \ref{def:inte}.
Similarly, interest features of all users are returned.

As a result, the \textit{Feature Data} for every user $u$, written as $F(u)$, is given by:
\begin{equation}
\label{eq:fu}
	F(u) = (I,\ H,\ P_f)
\end{equation}
where $I$, $H$ and $P_f$ refer to \textit{Info Feature}, \textit{Behavior Feature} and \textit{Interest Feature} separately (see formulas \ref{eq:info}, \ref{eq:beha} and \ref{def:inte}).
And it could be written as a vector:
\begin{equation}
\label{eq:fu-flat}
	F(u) = (\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)
\end{equation}
where each dimension refers to a data item of \sys{}.

### 2017-09-28 Gruba/04-uc.tex
v2.0
v2.0

\section{User Clusterer}
\label{sec:uc}

%clear points
%road map
%detail of each step, with motivation
%proof if applicable
%self-explain

Providing the \textit{Feature Data}, User Clusterer takes the charge of grouping each user concerned into a proper cluster.
Algorithm \ref{alg:uc} illustrates such overall procedure.

The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l}); 
then, each user obtains a coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged coefficient value of all users serves as the coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

\begin{algorithm}[t]
\caption{User Clustering in \sys{}}
\label{alg:uc}

\begin{algorithmic}[1]
\State Input: \textit{Feature Data} of users $\{F(u)\}$, the minimum/maximum number of clusters $N_i$ and $N_a$
\State Output: Optimal user clustering result $R$
\\
\ForAll {$t \in [N_i, N_a]$} \label{enu}
	\State group users $\{u\}$ into $t$ clusters by $\{F(u)\}$ \label{task}
	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$ \label{l}
	\ForAll {$u \in \{u\}$}
		\State in-cluster distance $d_i(u)$ \label{v-b}
		\State out-cluster distance $d_o(u)$
		\State coefficient value $v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$ \label{v-e}
	\EndFor
	\State $v(t)\ =\ Avg\{v(u)\}$ \label{avg}
\EndFor
\If {$v(a)\ ==\ \ Max\{v(t)\}$} \label{opti}
	\State $R$ = $R'(a)$
\EndIf
\State \bfseries{return} $R$
\end{algorithmic}
\end{algorithm}

Next, we shall now first detail how \sys{} performs the clustering task and subsequently illustrate the computation regarding the metric of coefficient value.

\subsection{Clustering in \sys{}}
\label{sec:cluster}

In \sys{}, the clustering rests on an optimized K-Prototype \refe{} algorithm, named K-Gru in this work. 
Similar as K-Prototype, K-Gru randomly selects the cluster kernels among samples and employs the minimum distance between them to determine an initial result, upon which the clustering tasks are iterated until the results are stable.

Unlike K-Prototype that supports vector samples in which each dimension is of numerical/categorical, K-Gru could also handle the case where a dimension is one normalized vector.
%
Recall the sample data for User Clusterer, i.e., \textit{Feature Data} in form of vectors (see formula \ref{eq:fu-flat}), of which the data type regarding each dimension is shown as Table \ref{tbl:data-type}.

\begin{table}[!htb]
\centering
\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_s$, $\#E_s$, $R_{ee}$, $\#B_s$, $R_{oc}$, $\#W_r$				\\	\midrule
categorical data			& $U_t$				\\	\midrule
normalized vectors			& $P_t$, $P_g$, $P_f$			\\ \bottomrule              
\end{tabular}
\end{table}

As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers, categories and normalized vectors. 
For simplicity, we shall first illustrate the distance calculation of the simple vectors with mono data type on each dimension and then demonstrate that of complex vectors in K-Gru.

Given two numerical vectors $Y'\ = (y'_0, y'_1, ...)$ and $Z'\ = (z'_0, z'_1, ...)$, the \od{} \refe{} between $Y'$ and $Z'$ is given by :
%
\begin{equation}
\label{eq:od}
D_n(Y', Z') = \sum_{\substack{e}} (y_e - z_e)^2
\end{equation}

As to the categorical vectors $Y''\ = (y''_0, y''_1, ...)$ and  $Z''\ = (z''_0, z''_1, ...)$, the \hd{} \refe{} of $Y''$ and $Z''$ is:
%
\begin{equation}
\label{eq:hd}
D_h(Y'', Z'') = \sum_{\substack{e}} H_e
\end{equation} 
where $H_e$ refers to the \hd{} over each dimension, with $H_e\ =\ 1$ if $y''_e$ and $z''_e$ share the identical value, and $H_e\ =\ 0$ otherwise.

Regarding two vectors where each dimension is a normalized vector per se, Cosine Similarity \refe{} is leveraged to compute the distance.
Then, the distance between such two vectors $Y^{\ast}\ = (Y^{\ast}_0, Y^{\ast}_1, ...)$ and $Z^{\ast}\ = (Z^{\ast}_0, Z^{\ast}_1, ...)$ is:
%
\begin{equation}
\label{eq:vd}
D_v(Y^{\ast}, Z^{\ast}) = \sum_{\substack{e}} Y^{\ast}_e \cdot Z^{\ast}_e
\end{equation} 
where $\cdot$ refers to the dot product operation between two normalized vectors $Y^{\ast}_e$ and $Z^{\ast}_e$.

Hence, the said distance regarding the complex vectors ($Y\ =\ (Y_0, Y_1, ...)$ and $Z\ =\ (Z_0, Z_1, ...)$ ) in K-Gru, named \gd{}, could be deduced as:
%
\begin{equation}
\label{eq:gd}
D_g(Y, Z) = \sum_{\substack{e}} G_e
\end{equation}
where the distance on each dimension $G_e$ is given by:
%
\begin{equation}
\label{eq:ge}
G_e =
  \begin{cases}
    (Y_e - Z_e)^2       & \quad \text{if } Y_e/Z_e \text{ is numerical}\\
    H_e\ (1\ or\ 0)       	& \quad \text{if } Y_e/Z_e \text{ is categorical}\\
    Y_e \cdot Z_e  		& \quad \text{if } Y_e/Z_e \text{ is of normalized vector}
  \end{cases}
\end{equation}

\subsection{Coefficient Metric Computation}
\label{sec:compu}

In \sys{}, coefficient value serves as the fundamental criteria for the optimal clustering selection.
Providing a clustering result, each user is associated with a cluster.
For a given user $u$ of cluster $l$, we employ the vector $Y$ to denote the \textit{Feature Data} as in formula \ref{eq:fu-flat}.

\begin{definition}
\label{def:di}
The in-cluster distance $d_i(u)$ is the average distance to all the other users in the same cluster, i.e., $\forall u'' \in l$ \& $u \neq u''$:
\begin{equation}
	d_i(u) = Avg\{D_g(Y_u, Y_u'')\}
\end{equation} 
\end{definition}

\begin{definition}
\label{def:do}
The out-cluster distance $d_o(u)$ is measured as the minimum of the distances $\{d^{\ast}\}$ between $u$ and other clusters ($\forall l' \neq l$), i.e.:
\begin{equation}
	d_o(u) = Min\{d^{\ast}(u, l')\}
\end{equation}
where $d^{\ast}$ is given by:
\begin{equation}
	d^{\ast}(u, l') = Avg\{D_g(Y_u, Y_u')\}\ \forall u' \in l'
\end{equation}  
\end{definition}

\begin{definition}
\label{def:coef}
The coefficient value $v(u)$ is thus concluded:
\begin{equation}
\label{eq:coef}
v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}	
\end{equation}
\end{definition}

Intuitively, a good clustering solution should result bigger $d_o$ and smaller $d_i$, such that samples with obvious differences go to various clusters and vice versa.
When $d_o$ is far more than $d_i$, coefficient value approaches to 1.
Hence, the larger coefficient value is, the better clustering performs, by which the optimal solution is selected.

### 2017-09-28 Gruba/05-gm.tex
v2.0
v2.0

\section{Group Modeler}
\label{sec:gm}

%clear points
%road map
%detail of each step, with motivation

Recall the central problem of \sys{}, where the \retg{} behaviors of users are modeled.
Specifically, such model is built by Group Modeler for each user group and thus named as group model.
To avoid ambiguity, we shall use the term of \textit{items} to denote the data for training the group model.
A given \textit{item} is either positive or negative.

\begin{definition}
\label{def:gm-it}
An item $E$ involves a blog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of $b$'s owner.
\begin{equation}
\label{eq:gm-it}
E \in
  \begin{cases}
    \text{positive items}       & \quad \text{if } f \text{ \retd{} } b\\
    \text{negative items}  		& \quad \text{if } f \text{ did not \ret{} } b
  \end{cases}
\end{equation}
\end{definition}

And the data of item $E$ could be further divided into three parts.
\begin{itemize}
	\item \textit{User Part} contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.
	\item \textit{Blog Part} consists of a metric $C_h$, referring to the correlation between blog contents and recent events returned by Ring \refe{}. $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}). Specifically, each event could be viewed as a topic $t$, over which the correlation of a blog $b$ could be obtained by formula \ref{eq:simbt}.
	\item \textit{Interaction Part} includes three correlation metrics. They are of blog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent blogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$. 
\end{itemize}
As a result, the obtained group model could learn what does a positive/negative item look like over each metric mentioned above.

### 2017-09-28 Gruba/06-perf.tex
v2.0
v2.0

\section{\textcolor{red}{Performance Evaluation}}
\label{sec:perf}

%zhu begin

In this section, we validated the effectiveness of our methods, including features extraction, users clustering and reposting behavior modeling.

\subsubsection{Experimental Setup}

The data we used in this study was crawled from Sina Microblog, which allows users to follow with each other. When user A follows B, A is called the follower of B and B is called the friend of A. User B's behaviors such as posting and reposting will be visible to A. User A can choose microblogs to repost which was posted (or reposted) by user B. Our data set was crawled by the following ways. Firstly, we selected 43500 users randomly from the public Microblog stream. We crawled the basic information of these users, including gender, province, number of microblogs, city, number of followers, number of friends, signature, nickname, etc. In addition, we also crawled all the microblogs the user posted or reposted. The microblog information including the number of it has been reposted, the number of it has been commented, the number of it has been liked, type of the microblog (be posted or reposted by the user), the location where the microblog was posted, the content of the microblog, the device the microblog was posted by, the time when the microblog was posted and so on. In addition, we can get part of one user's friends from the microblogs that user reposted. So we also collected some users's friends's information and microblogs. Table \ref{tab:Data_statistics} lists the statistics information of the data set. Another dataset we used here was 1000 labeled microblogs selected from the microblogs we crawled. We labeled each microblog with categories in the cell lexicon.\par

\begin{table}[!h]
\centering
    \caption{statistics information of Dataset }     % NOTE!  caption goes _before_ the table contents !!
    \label{tab:Data_statistics}
    \begin{small}
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    \cline{2-5}
    {\bfseries DataSet} & {\bfseries  \#Users}         & {\bfseries \#Microblogs}     & {\bfseries \#Posts}    & {\bfseries \#Reposts}     \\
    \hline
    WeiBo         & 410000 & 157943530		& 77234797 & 80708733	\\
    \hline
    \end{tabular}
    \end{small}
\end{table}

\paragraph{Features Extraction}
One user's basic and behavioral information can be obtained either from the data set straightly or from the statistics information of user's microblogs. As for user's interests, we proposed a novel method to do interest extraction. Here we compared our method using different parameters with method that just using TF-IDF or Twitter-LDA. To evaluate the performance of the method, we labeled 1000 microblogs with categories of the cell lexicon. One microblog may belong to one or several categories. Considering it's a multi-label problem, our evaluation metrics here are accuracy, precision and recall as described in \cite{IEEEexample:journals/tkde/ZhangZ14}. Let $S = {(x_i,Y_i)| 1 \le i \le p)}$ be the test set and $m(\cdot)$ be the mapping method. The accuracy, precision and recall are defined as equation \eqref{accuracy_m}, \eqref{precision_m} and \eqref{recall_m}.\par

\begin{equation}\label{accuracy_m}
accuracy_m = \frac{1}{p} \sum_{i=1}^{p} \frac{\mid Y_i \cap m(x_i) \mid}{\mid Y_i \cup m(x_i) \mid}
\end{equation}

\begin{equation}\label{precision_m}
precision_m = \frac{1}{p} \sum_{i=1}^{p} \frac{\mid Y_i \cap m(x_i) \mid}{\mid m(x_i) \mid}
\end{equation}

\begin{equation}\label{recall_m}
recall_m = \frac{1}{p} \sum_{i=1}^{p} \frac{\mid Y_i \cap m(x_i) \mid}{\mid Y_i \mid}
\end{equation}

\paragraph{Users Clustering}
We used the data generated by features extraction to perform users clustering. Each sample contains user's basic features, behavioral features and interests features. Silhouette coefficient \cite{IEEEexample:books/mk/HanKP2011} was used as our evaluation metric here. For each sample $i$, let $a(i)$ be the average dissimilarity of $i$ with all other data within the same cluster. Let $b(i)$ be the lowest average dissimilarity of $i$ to any other cluster, of which $i$ is not a member. We now get the silhouette of sample $i$ as equation \eqref{silhouetteOfi}. Then silhouette coefficient of the result with N samples can be got as equation \eqref{silhouette}.\par

\begin{equation}\label{silhouetteOfi}
s(i) = \frac{b(i)-a(i)}{max\{b(i),a(i)\}}
\end{equation}

\begin{equation}\label{silhouette}
silhouette = \frac{1}{N} \sum_{i=1}^{N} s(i)
\end{equation}

\paragraph{Reposting Behavior Modeling}
For analyzing reposting behavior, we firstly divided users into groups by users clustering. For each group, we randomly selected microblogs reposted by users of the group as positive samples, and selected microblogs ,which were reposted by a friend of one user in the group but not reposted by this user, as negative samples. Then we generated final samples with features described in subsection \ref{subsec:RepostingBehaviorPrediction}. We have carefully chosen algorithm to compare with our method. Here we compared our method with \cite{IEEEexample:conf/ijcai/ZhangLTCL13}, which studied a state-of-art idea of social influence locality for modeling users¡¯ reposting behaviors in the microblog network. We use accuracy, recall and f-measure as our evaluation metrics.\par

All experiments were conducted on a machine with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of Memory, running 64 bit Windows 7 professional system. Each experiment was repeated 5 times, and the average is reported here. In all the experiments, we fixed parameters to their default values. The parameters with their descriptions and default values are presented in Table \ref{tab:Parameters}. \par

\begin{table}[!h]
\centering
    \caption{Parameters used in the experiments with their descriptions.  }
    % NOTE!  caption goes _before_ the table contents !!
    \label{tab:Parameters}
    \begin{small}
    \begin{tabular}{|c|l|c|}
    \hline
    {\bfseries Parameters} & {\bfseries  Descriptions}                       & {\bfseries Default}     \\
    \hline
                       & threshold for selecting                             & \\
    $\epsilon$         & the categories when considering                     & 3\\
                       & the number of overlapped words.                     & \\
    \hline
                       & weight for mapping value                            & \\	
    $\alpha$           & by performing Procedure 1                           & 0.7\\
    \hline
                       & threshold number for                                & \\
    $k$                & selecting categories when                           & 3\\
                       & performing mapping algorithm.                       &	\\
    \hline
    $k_1$              & min number of clusters                              & 2	\\
    \hline
    $k_2$              & max number of clusters                              & 10	\\
    \hline
    \end{tabular}
    \end{small}
\end{table}

\subsubsection{Performance and Analysis}

\paragraph{Features Extraction}

To accurately extract user's interests feature, we proposed a novel method that combined the method of Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF to tag the microblog with 512 categories. We performed an experiment to compare three methods which only using Twitter-LDA, only using TF-IDF, and combining the two with different value of $\alpha$. Fig \ref{fig:Interests} shows the results of the experiment. From the results, we can see that when combining the two, we got a better performance. We also developed a demo system for visualization of users's features, fig. \ref{fig:userFeatures} shows one case of a user.

\begin{comment}
\begin{figure}[h]
	\centerline{\psfig{figure=IMAGE/features/Interests.eps,height=50.54mm,width=82mm}}
	\caption{Visualization for User Features.}
	\label{fig:Interests}
\end{figure}
\end{comment}

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{IMAGE/features/Interests}
\caption{Visualization for User Features.}
\label{fig:Interests}
\end{figure}

\begin{comment}
\begin{figure}[h]
	\centerline{\psfig{figure=IMAGE/features/userfeatures.eps,height=120.54mm,width=92mm} }
	\caption{Visualization for User Features.}
	\label{fig:userFeatures}
\end{figure}
\end{comment}

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{IMAGE/features/userfeatures}
\caption{Visualization for User Features.}
\label{fig:userFeatures}
\end{figure}

\paragraph{User Clustering}

We performed users clustering on the 43500 users we selected through the method described in subsection \ref{subsec:UserClustering}. In addition, we reconstructed five datasets which were randomly selected from the 43500 users and each dataset had 10000 users. The results are list in Fig. \ref{fig:sample_clustering}. From the results, we can draw the following observations:
(1) On the whole dataset with 43500 users, the clustering method got its largest coefficient when the number of clusters was four.
(2) On the five datasets with 10000 users, the clustering method got its largest coefficient on four datasets when the number of clusters is four and one dataset when the number of clusters is three. Based on the observations, we thought it a reasonable result dividing 43500 users into four groups.\par

We carefully analyzed the four groups we obtained through users clustering. (1)Most of users of the group one are male, and they are mainly distributed in Beijing. What's more, most of these users have similar amount of friends and followers. The most active time of this group are mainly distributed between 10 am and 12 am. (2)The users of group two are mostly female, they are also mainly distributed in Beijing. Most of users also have similar amount of friends and followers as group one. The most active time of this group are mainly distributed between 22 pm and 24 pm. (3)The users of group three are mostly male, and they are distributed in a wide range of provinces. Most of users have the number of followers far more than friends. Users of this group are active both in 10-12 am and 22-24 pm. (4)Most of users of group four are female, and they are distributed in a wide range of provinces as group three. Most of these users have the number of followers far more than friends. And the most active time of this group are mainly distributed between 22 pm and 24 pm. We also found that the distribution of the number of users's microblogs of each group is similar. We visualized the users's interests using words cloud, the difference between groups is obvious, excepting that group one and group three have similar interests.

\begin{comment}
\begin{figure}[h]
	\centerline{\psfig{figure=IMAGE/clustering/Clustering.eps,width=80.7mm} }
	\caption{The Results of Users Clustering Performed on Six Datasets}
	\label{fig:sample_clustering}
\end{figure}
\end{comment}

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{IMAGE/clustering/Clustering}
\caption{The Results of Users Clustering Performed on Six Datasets}
\label{fig:sample_clustering}
\end{figure}

\begin{figure}
  \centering
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/11.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/12.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/13.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/14.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/15.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/16.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/17.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/18.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/19.eps}}
  \caption{The Statistics of User Group One}
  \label{fig:subfig} %% label for entire figure
\end{figure}
\begin{figure}
  \centering
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/21.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/22.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/23.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/24.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/25.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/26.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/27.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/28.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/29.eps}}
  \caption{The Statistics of User Group Two}
  \label{fig:subfig} %% label for entire figure
\end{figure}
\begin{figure}
  \centering
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/31.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/32.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/33.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/34.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/35.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/36.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/37.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/38.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/39.eps}}
  \caption{The Statistics of User Group Three}
  \label{fig:subfig} %% label for entire figure
\end{figure}
\begin{figure}
  \centering
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/41.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/42.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/43.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/44.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/45.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/46.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/47.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/48.eps}}
  \subfigure{
      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/49.eps}}
  \caption{The Statistics of User Group Four}
  \label{fig:subfig} %% label for entire figure
\end{figure}

\paragraph{Reposting Behavior Modeling}
By performing users clustering, we got four user groups. We generated instances by the method as described in subsection \ref{subsec:RepostingBehaviorPrediction}. However, we observed that positive instances (reposting) and negative instances (un-reposting) are much unbalanced. Thus we randomly select a subset of negative instances with the equal number of positive number for experiments. We compared our method with \cite{IEEEexample:conf/ijcai/ZhangLTCL13}, the results are list in figure \ref{fig:comparisons}, here we call our method as reposting model for group(RMG). The result suggests that our method had a better performance than LRC-BQ in most cases.\par

 \begin{figure}
  \centering
  \subfigure[Precision Of RMG	and LRC-BQ]{
    \label{fig:subfig:a} %% label for first subfigure
    \includegraphics[width=0.4\textwidth]{IMAGE/model/precision.eps}}
  \hspace{1in}
  \subfigure[Recall Of RMG and LRC-BQ]{
    \label{fig:subfig:b} %% label for second subfigure
    \includegraphics[width=0.4\textwidth]{IMAGE/model/recall.eps}}
  \hspace{1in}
  \subfigure[F-Measure Of RMG and LRC-BQ]{
    \label{fig:subfig:c} %% label for second subfigure
    \includegraphics[width=0.4\textwidth]{IMAGE/model/F-Measure.eps}}
  \caption{Comparison Of RMG and LRC-BQ}
  \label{fig:comparisons} %% label for entire figure
\end{figure}

We further try different features and their combinations for modeling reposting behaviors, they are user-based information(UI), microblog-based information(MI), interaction information(II) and their combinations. The results are list in in figure \ref{fig:performances}. The result suggests that the MI and UI perform similarly for modeling group one and group three, MI performs better than UI and II on group four. Combining all the three types of features can get similar performance with the combination of UI and MI on group two and group three, and the two combinations perform better than all other combinations. As for group one and group four, using UI and MI can get the best performance, which indicates that there in deed exists strong correlation between the reposting behavior and the two types information.

 \begin{figure}
  \centering
  \subfigure[Precision of RMG Using Different Features]{
    \label{fig:subfig:a} %% label for first subfigure
    \includegraphics[width=0.4\textwidth]{IMAGE/model/precisionofdifferentfeatures.eps}}
  \hspace{1in}
  \subfigure[Recall of RMG Using Different Features]{
    \label{fig:subfig:b} %% label for second subfigure
    \includegraphics[width=0.4\textwidth]{IMAGE/model/recallofdifferentfeatures.eps}}
  \hspace{1in}
  \subfigure[F-Measure of RMG Using Different Features]{
    \label{fig:subfig:c} %% label for second subfigure
    \includegraphics[width=0.4\textwidth]{IMAGE/model/fmeasureofdifferentfeatures.eps}}
  \caption{Performance Of RMG Using Different Features}
  \label{fig:performances} %% label for entire figure
\end{figure}

\paragraph{Time Report}

### 2017-09-28 Gruba/07-rela.tex
v2.0
v2.0

\section{\textcolor{red}{Related Work}}
\label{sec:rela}

%zhu begin
The rapid development of social network is accompanied by the generation of tremendous user-generated contents. Message forwarding (e.g., reposting on weibo.com) is one of the most popular functions in many existing social networks. Behavior modeling of social media users has received great attention in recent years, and has become a research hot spot of academies and industries. In this section, we will introduce the related work of user modeling in social network from the aspects of user features analysis, user groups mining and user behaviors modeling.\par

Social media users's features we mentioned here include users's basic information, behavior features and interests features. Users's basic information include the users's gender, age, region, occupation and other personal information. There are many researches for analyzing users's basic information, such as users's racial information analysis \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, users's gender inference \cite{IEEEexample:conf/emnlp/CiotSR13}, users's actual age inference \cite{IEEEexample:conf/icde/ParkHHL09}, user political tendency analysis (e.g. \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, \cite{IEEEexample:conf/acl/VolkovaCD14}), user policy orientation analysis\cite{IEEEexample:kosinski2013private}, user's geo-location and occupation mining\cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}, etc. Most of these methods analyze the unknown attributes by using classification or regression model.\par

Social medias users's behaviors mainly refers to the reposting, posting and commenting behaviors. Users's behaviors also have certain characteristics and regularity. As mentioned in \cite{IEEEexample:jiang2013understanding}, it found that the behavior of a user exhibits the power-law distribution at the time interval, and the power-law distribution is related to users's schedule. Guo Z et al.\cite{IEEEexample:conf/music/GuoLTL12} analyzed the behavior of microblog users, the difference between the activity of users in different periods, and obtained the distribution of individual behavior on time.\par
Users's behaviors are largely driven by user interests, so it's of vital importance to model users's interests. Zhiyuan et al.\cite{IEEEexample:journals/fcsc/LiuCS12} modeled users's interests through mining keywords. They extracted keywords from the users's microblogs by the combination of words frequency and translation model. Xu Z et al.\cite{IEEEexample:conf/webi/XuLXY11} proposed a method which extended user topic model to analyze users's interests. Michelson M et al.\cite{IEEEexample:conf/and/MichelsonM10} analyzed interests  based on a knowledge base. They used a knowledge base to identify and classify the entities in twitters of one user, then generate the user's interests category subtree to express his interests. Lim K H et al.\cite{IEEEexample:conf/wikis/LimD13} analyzed the celebrities a user mentioned, then they got the preference degree of the user in different interests categories. Bhattacharya P et al.\cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} proposed a method to extract a user's interests by analyzing the experts he followed. By digging a list of certain topics of the custom experts the user follows, they got the user's interests profiling. Wei Feng et al.\cite{IEEEexample:conf/icde/FengW14} studied the methods mapping tweets to hashtags to get users's preferences for hashtags.\par

Considering the fact that the amount of users in Social Medias is so huge, modeling for each user is not a good idea. In addition, modeling for a single user may make the model too particular. There are also some studies on the user groups analysis. Some researches studied how to classify users under a specific situation. For instance, Marco Pennacchiotti et al.\cite{IEEEexample:conf/icwsm/PennacchiottiP11} classified users by race, political tendencies and so on. In addition, research for user community mining is a hot spot. Jaewon Yang et al.\cite{IEEEexample:conf/wsdm/YangL13} proposed a method based on non-negative matrix decomposition to mine user community. Yiye Ruan et al.\cite{IEEEexample:conf/www/RuanFP13} considered user's friends and user's text content into their method when measuring the similarity between users for clustering. He et al. \cite{IEEEexample:he2014overlapping}
only considered the relationship between friends, and used the edge aggregation coefficient as a measure of clustering. Hiroaki Shiokawa et al.\cite{IEEEexample:conf/aaai/ShiokawaFO13} used the modular degree as a clustering standard and proposed an incremental algorithm to mine user community.\par

As for behavior prediction, Jing Zhang et al.\cite{IEEEexample:journals/tkdd/ZhangTLLX15} proposed a method of analyzing users's reposting behavior from the perspective of influence. Some researchers (e.g. \cite{IEEEexample:conf/wsdm/FengW13}, \cite{IEEEexample:conf/ijcai/ZhangLTCL13}) find that the user's reposting behavior is largely influenced by the relationship between friends, so they consider user's friend structure information into their models. Bo Jiang et al. \cite{IEEEexample:conf/cikm/JiangLSW15} proposed a method that combined matrix decomposition and microblogs clustering to analyze the user's reposting behavior. Zhang et al.\cite{IEEEexample:zhang2015retweet} proposed non-parametric statistical models to combine structural, textual, and temporal information together to predict reposting behavior. Considering the situation that users's not reposting does not mean that users are not interested in it, the users may just did not see it, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} applied a collaborative filtering method to the reposting behavior analysis.

### 2017-09-28 Gruba/08-conclu.tex
v2.0
v2.0

\section{\textcolor{red}{Conclusions}}
\label{sec:conclu}

%zhu begin

In this paper, we studied to model reposting behavior of group users in microblog. We first extracted users's features including basic features, behavior features and interests features. Meanwhile, we proposed a novel method to extract user interests from the user generated texts. By performing users clustering, we divided users into several groups and modeled reposting behavior of each group users respectively. The final experiment shows that our model have strong predictive power. What's more, we developed a demo system to display the profiling for users and groups. As future work, it is interesting to study other methods to improve the accuracy of interests extraction.

### 2017-09-28 TF-vldb2018/sec-intro.tex

@@
 Furthermore, \cite{FanCount16} already adopts capacity bounds on the edges of pattern graphs via subgraph isomorphism, and \cite{FanWWXin13} uses graph pattern matching to find single experts, instead of a team of experts.
-In this study, team simulation is proposed for team formation as an extension of graph simulation and strong simulation on undirected graphs with capacity constraints on pattern graphs.
+In this study, team simulation is proposed for team formation as an extension of graph simulation and strong simulation on undirected graphs with capacity constraints on the nodes of pattern graphs.
 

### 2017-09-28 TF-vldb2018/sec-intro.tex

@@
 However, \cite{Kargar11} adopted Lawler's procedure \cite{Lawler1972}, and is inappropriate for large graphs.
-We also adopt {\em density}  as the communication cost, which shows a better performance~\cite{GajewarS12}, and further require that all team members are {\em close to each other} (located in the same balls), along the same lines as~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}.
+We also adopt {\em density}  as the communication cost, which shows a better performance~\cite{GajewarS12}, and further require that all team members are {\em close to each other} (located in the same balls), along the same line with~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}.
 \revise{Except for simply minimizing the communication cost among team members, 

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 However, \cite{inc-survey,FanHT17,FanLMTWW10,FanWW13-tods} only consider data updates,
-and \cite{ArisLuca12} only consider continuous coming new tasks.
+and \cite{ArisLuca12} only considers continuous coming new tasks.
 In this work, we  deal with both pattern and data updates for team formation, and support both insertions and deletions.

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 
-Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
-the {\em top-$k$ team formation} problem (\teamF) is to find a list of $k$ highly collaborative teams of experts in $G$ such that each satisfies the skill requirements of the task.
+%Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
+The {\em top-$k$ team formation} problem (\teamF) is to find a list of $k$ highly collaborative teams of experts such that every team satisfies the skill requirements of a certain task.
 Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed for \teamF,
 and fall into two categories in terms of the way to improve the collaborative compatibility of team members:
- (1) minimizing team communication costs,
+ (a) minimizing team communication costs,
 defined with \eg the diameter, minimum spanning tree and the sum of pairwise member distances of the induced subgraph~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}, and
-(2) maximizing team communication relations,
+(b) maximizing team communication relations,
 \eg the density of the induced subgraph~\cite{GajewarS12,realTeamForm13}.
-Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting that introduces a lower bound on the number of individuals with a specific skill in a team, and an upper bound of the total team members, respectively.
+Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting by introducing a lower bound on the number of individuals with a specific skill in a team, and an upper bound of the total team members, respectively.
 
@@
 
-An HR manager may help to set up a team for developing a new software product,
-and she searches $G_1$ (without dashed edges) for proper candidates.
-The desired team has
-(1) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
-(2) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.
+A headhunt helps to set up a team for developing a software product by searching proper candidates from $G_1$ (ignore dashed edges).
+A desired team has
+(a) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
+(b) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.
 
@@
 
-\revise{One can verify that none of existing methods suffice to identify the above desired teams.
-They can only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13} in search condition (1),
-while cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints in search condition (2) (see details in Example~\ref{exa-teamF}).}
+One may verify that existing methods \cite{Lappas09,Kargar11,GajewarS12,GajewarS12,realTeamForm13}, can hardly find a desired team.
+They only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13}  (condition (a)), and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints (condition (b)).
  \end{example}
@@
 \end{center}
-\vspace{-3.5ex}
+\vspace{-3ex}
 \caption{Motivation example}
 \label{fig-motivation-example}
-\vspace{-5ex}
+\vspace{-4ex}
 \end{figure}
@@
 A natural question is how to further capture the {\em structural and capacity constraints} in a unified model for team formation?
-We essentially introduce a revision of {\em graph pattern matching} for team formation to fill in this gap.
-
+We  introduce a revision of {\em graph pattern matching} for team formation to fill in this gap.
+% 
 Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.
-Intuitively, patterns $P$ captures the structural constraint, and we extend graph pattern matching semantics to solve the team formation problem.
-As shown in Fig.~\ref{fig-motivation-example},  the desired team requirement can be expressed by the pattern graph $P_1$ (ignore dashed edges), such that the nodes represent the skill requirements, the edges specify the topology constraint, and the bounds on nodes are the capacity constraint.
+Essentially, we utilize patterns to captures the structural constraint, and revise the semantics of graph pattern matching for team formation.
+For instance, a desired team requirement can be specified by the pattern $P_1$ (ignore dashed edges) in Fig.~\ref{fig-motivation-example}, in which nodes represent the skill requirements,  edges specify the topology constraint, and the bounds on nodes are the capacity constraint.
 
@@
 
-\vspace{1.0ex}
-Finding desired teams typically needs a lot of labor efforts, and it is even common for professionals to refine search conditions multiple times in order to find ideal teams~\cite{SajjadPG12,HabibiP15}.
-Moreover, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. That is, team formation is accompanied with a highly dynamic environment.
-%
-\revise{However, it is often too costly to recompute top-$k$ teams from scratch in response to pattern and data updates.
+Another issue it that team formation is accompanied with a highly dynamic situation.
+It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}.
+Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}.
+We illustrate this with an example.
+
+\begin{example}
+\label{exm-motivation-inc}
+Consider $P_{1}$ and $G_{1}$ in Example~\ref{exm-motivation} again.
+
+\sstab{(1)} % When the manager gets the match result, \ie the top-$k$ teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$,
+One may find that $P_1$ is too restrictive to find any sensible match in  $G_{1}$.
+Hence, she needs to refine the pattern by updating $P_1$ with $\Delta P_{1}$, \eg an edge
+deletion $(\kw{SD},\kw{ST})^-$.
+%We denote $P_{1}\oplus\Delta P_{1}$ the updated pattern.
+%It is much better to derive $P_{1}\oplus\Delta P_{1}(G_{1})$ from $P_{1}(G_{1})$
+%than a computation for $P_{1}\oplus\Delta P_{1}$ in $G_{1}$ from scratch.
+%\looseness=-1
+
+\sstab{(2)} It is also common that a data update $\Delta G_1$ comes on $G_1$, \eg an edge insertion $(\kw{SD_3},\kw{ST_3})^+$.
+%Similar with (1), it is better to compute $P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.
+
+\sstab{(3)} Finally, it can be the case when pattern update $\Delta P_{1}$  and data update $\Delta G_{1}$ come simultaneously on $P_1$ and $G_1$.
+%,  $P_{1}\oplus\Delta P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally
+\end{example}
+
+This motivates us to study the {\em dynamic top-k team formation} problem, to handle continuous
+pattern and data updates, separately and simultaneously.
+It is known that incremental algorithms avoid re-computing from scratch by re-using previous results~\cite{inc-survey}.
+However, incremental algorithms of graph pattern matching for pattern updates has not been investigated, though there exist incremental algorithms of graph pattern matching for dealing with data updates~\cite{FanLMTWW10,FanWW13-tods,FanHT17}.
+Further, it is also challenging for incremental algorithms to handle simultaneous pattern and data updates  in a unified way.
+
+\eat{
+often too costly to recompute top-$k$ teams from scratch in response to pattern and data updates.
 These highlight the need for incremental algorithms to compute the updated top-$k$ teams.
@@
 
-\eat{
 Given a pattern graph $P$ and a data graph $G$, the graph pattern matching results $P(G)$ in $G$ for $P$ and changes $\Delta G$ to $G$ as input,
@@
 Here $\oplus$ denotes applying changes $\Delta S$ to $S$, when $S$ is data graph $G$ or query result $P(G)$.
-It is to improve response time by reducing computations on big $G$ to small $\Delta G$ and $\Delta O$.}%%%EAT
+It is to improve response time by reducing computations on big $G$ to small $\Delta G$ and $\Delta O$.
 
-\begin{example}
-\label{exm-motivation-inc}
-Recall $P_{1}$ and $G_{1}$ in Example~\ref{exm-motivation} and continue.
-
-\sstab{(1)} When the manager gets the match result, \ie the top-$k$ teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$, 
-she may find $P_1$ is too restrictive to find sensible matches.
-Therefore, she enters a pattern update $\Delta P_1$ on $P_1$, composed of an edge 
-deletion $(\kw{SD},\kw{ST})^-$.
-We denote $P_{1}\oplus\Delta P_{1}$ the updated pattern.
-It is much better to derive $P_{1}\oplus\Delta P_{1}(G_{1})$ from $P_{1}(G_{1})$
-than a computation for $P_{1}\oplus\Delta P_{1}$ in $G_{1}$ from scratch.
-%\looseness=-1
-
-\sstab{(2)} When a data update $\Delta G_1$ comes on $G_1$, composed of an edge insertion $(\kw{SD_3},\kw{ST_3})^+$.
-Similar with (1), it is better to compute $P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.
-
-\sstab{(3)} Even better, when it comes to the case pattern $\Delta P_{1}$ and data updates $\Delta G_{1}$ come together, it is desirable to compute $P_{1}\oplus\Delta P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.
-\end{example}
-
-This motivates us to study the {\em dynamic top-k team formation} problem (\dynteamF), to handle continuous 
-pattern and data updates, separately and simultaneously.
 As a basis of \dynteamF, we also investigate the incremental problem for graph pattern matching on pattern updates.
@@
 
-\warn{To our knowledge, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
-not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting studied so far.} 
+ }%%%EAT
+
 \looseness = -1
@@
 in order to cope with the highly dynamic environment of team formation (Section~\ref{sec-tsim}).
-\warn{To the best of our knowledge, this work gives the first investigation on pattern and simultaneous pattern and data incremental computations.} 
+
 }
@@
 
+To our knowledge, this work is among the first to study simultaneous pattern and data incremental computations, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}, not to mention continuous and simultaneous pattern and data updates.
+This is  the most general dynamic setting for incremental computations.
+
 All detailed proofs are available  in the full version~\cite{fullvldb18}.

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 
-\revise{
-\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation problem.
-It extends existing methods by incorporating the structural and capacity constraints using pattern graphs (Section~\ref{sec-tsim}).
-We formulate the dynamic top-$k$ team formation problem, to handle separate and simultaneous pattern and data updates,
-in order to cope with the highly dynamic environment of team formation (Section~\ref{sec-tsim}).
-
-}
+\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation (Section~\ref{sec-tsim}).
+It extends existing methods by incorporating the structural and capacity constraints using pattern graphs .
+To cope with the highly dynamic environment of team formation, we also formulate the dynamic top-$k$ team formation problem  (Section~\ref{sec-tsim}), for handling separate and simultaneous pattern and data updates.
 

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 
-\revise{
-\stab (2) We develop a batch algorithm with two optimization techniques for computing top-$k$ teams via team simulation.}
-We also study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching (Section~\ref{sec-tsimAlg}).
-We develop a unified approach to handling the need for both pattern and data updates.
-We first prove that the dynamic top-$k$ team formation problem is unbounded even for single pattern or data updates, by extending the notion of incremental boundedness~\cite{Reps96}.
-In light of this, we then propose an incremental strategy based on {\em pattern fragmentation} and {\em affected balls} to localize the effects of pattern and data updates (Sections~\ref{sec-dynamictopk}).
-We finally develop a unified incremental algorithm for dealing with separate and simultaneous pattern and data updates,
-with an optimization technique with the {\em early return} property for incremental top-$k$ algorithms, an analogy of the traditional early termination property (Sections~\ref{sec-IncAlg}).
+\stab (2) We develop a batch algorithm for computing top-$k$ teams via team simulation (Section~\ref{sec-tsimAlg}).
+We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching .
+We also propose two optimization techniques: incrementally computing radius varied balls and density based filtering for speeding up computations.
+
+\stab (3) We develop a unified approach to handling the need for both pattern and data updates (Sections~\ref{sec-dynamictopk} and~\ref{sec-IncAlg}).
+Due to the inherent difficulty of the problem, we propose an incremental strategy based on {\em pattern fragmentation} and {\em affected balls} by localizing the effects of pattern and data updates, and we develop a unified incremental algorithm for dealing with separate and simultaneous pattern and data updates,
+with an optimization technique with the {\em early return} property for incremental top-$k$ algorithms, an analogy of the traditional early termination property.
 
@@
 
-\stab (3) Using real-life data (\citationd) and synthetic data (\synthetic), we demonstrate the effectiveness and efficiency of our graph pattern matching approach for (dynamic) team formation (Section~\ref{sec-expt}).
+\stab (4) Using real-life data (\citationd) and synthetic data (\synthetic), we demonstrate the effectiveness and efficiency of our graph pattern matching approach for (dynamic) team formation (Section~\ref{sec-expt}).
 We find that (a) our method is able to identify more sensible teams than existing team formation methods \wrt \eat{three} practical measurements,

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 We also adopt {\em density}  as the communication cost, which shows a better performance~\cite{GajewarS12}, and further require that all team members are {\em close to each other} (located in the same balls), along the same line with~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}.
-\revise{Except for simply minimizing the communication cost among team members,
-\cite{HuangLv16,Kargar11} consider minimizing the cost among team members and team leaders.}
+Except for simply minimizing the communication cost among team members,
+\cite{HuangLv16,Kargar11} consider minimizing the cost among team members and team leaders.
 Different from these work, we introduce {\em structural constraints}, in terms of graph pattern matching~\cite{FanLMTWW10,MaCFHW14}, into team formation, while retaining the capacity bounds on specific team members like~\cite{realTeamForm13,GajewarS12}.

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 
-Another issue it that team formation is accompanied with a highly dynamic situation.
+Another issue is that team formation is accompanied with a highly dynamic situation.
 It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}.
@@
 We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching .
-We also propose two optimization techniques: incrementally computing radius varied balls and density based filtering for speeding up computations.
+We also propose two optimization techniques, incrementally computing radius varied balls and density based filtering, for speeding up computations.
 

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 
-{Query reformulation (\aka query rewriting /modification) is to generate alternative queries that may produce better answers,
+{Query reformulation (\aka query rewriting) is to generate alternative queries that may produce better answers,
 and has been studied for structured queries~\cite{MottinEmpty13}, keyword queries~\cite{YaoQReform12} and graph queries~\cite{MottinGReform15}.

### 2017-09-29 TF-vldb2018/sec-tsim.tex

@@
 \newcommand{\minp}{\kw{minP}}
-\newcommand{\rgraphsim}{\kw{undigSim}}
+\newcommand{\rgraphsim}{\kw{undirgSim}}
 \newcommand{\incsim}{\kw{incSim}}
@@
 
-\revise{
-We first propose {\em team simulation}, an extension of traditional graph pattern matching.
+We first propose {\em team simulation}, a revision of traditional graph pattern matching.
 We then formally introduce the {\em top-$k$ team formation} problem via team simulation.
-We finally present the {\em dynamic top-$k$ team formation} problem.}
+We finally present the {\em dynamic top-$k$ team formation} problem.
 
@@
 
-\revise{
 We first extend pattern graphs of traditional graph pattern matching to carry capacity requirements,
-and then define team simulation on undirected graphs.}
+and then define team simulation on undirected graphs.
 %We then redefine strong simulation on directed graphs, originally defined on directed graphs~\cite{MaCFHW14}.}
@@
 \vspace{0.5ex}
-\ni(2) for each node $u\in V_P$, the number of nodes $v\in V_s$  with $(u, v)\in \Reps$ falls into $f_P(u)$.
+\ni(2) for each node $u$ in $P$, the number of nodes $v$ in $G_s$  with $(u, v)\in \Reps$ falls into $f_P(u)$.
 
@@
 \label{exm-rsimulation}
-Consider $P_1$ and $G_1$ in Fig.~\ref{exm-motivation}.
-When team simulation with $r=2$ is adopted, $P_1$ matches $G_1$ as there is a perfect subgraph in $G_1$,
-\ie the connected component of $G_1$ containing $\kw{PM_{1}}$, which resides in ball
-$\ball{[\kw{PM_1}, 2]}$.
-It maps \kw{PM}, \kw{BA}, \kw{UD}, \kw{SA}, \kw{SD} and \kw{ST} in $P_1$ to \kw{PM_1}, \kw{BA_1}, \{\kw{UD_1}, \kw{UD_2}\}, \{\kw{SA_1}, \kw{SA_2}\}, \{\kw{SD_1}, \kw{SD_2}\} and \{\kw{ST_1}, \kw{ST_2}\}, respectively.
+Consider pattern $P_1$ and data graph $G_1$ in Fig.~\ref{exm-motivation}, and  team simulation with $r=2$ is adopted.
 
-One can easily verify that
-(a) $P_1\eps \ball{[\kw{PM_{1}}, 2]}$, and the ball is exactly the match graph here,
-and (b) the capacity bounds on all pattern nodes are satisfied.
+One can easily verify that $P_1$ matches $G_1$  via team simulation, \ie $P_1 \eeps G_1$, 
+as (a) there is a perfect subgraph in in ball
+$\ball{[\kw{PM_1}, 2]}$, \ie the connected component of $G_1$ containing $\kw{PM_{1}}$, which maps \kw{PM}, \kw{BA}, \kw{UD}, \kw{SA}, \kw{SD} and \kw{ST} in $P_1$ to \kw{PM_1}, \kw{BA_1}, \{\kw{UD_1}, \kw{UD_2}\}, \{\kw{SA_1}, \kw{SA_2}\}, \{\kw{SD_1}, \kw{SD_2}\} and \{\kw{ST_1}, \kw{ST_2}\}, respectively, and, moreover, (b) the capacity bounds on all pattern nodes are satisfied.
 \end{example}
-\looseness=-1
 
@@
 
-\revise{
 \stitle{Remarks}.
-(1) Team simulation differs from graph simulation and strong simulation in the existence of capacity bounds on pattern graphs and its ability to capture matches on undirected graphs.
-%
-(2) As for locality constraint, different from strong simulation that requires the matched nodes to locate in a ball with a fixed given radius, team simulation adopts a more natural setting that the radius of the balls is flexible, only less than a user specified upper bound.
+(1) Team simulation differs from graph simulation~\cite{infsimu95} and strong simulation~\cite{MaCFHW14} in the existence of capacity bounds on pattern graphs and its ability to capture matches on undirected graphs.
+
+\sstab(2) Different from strong simulation with balls having a fixed radius (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is flexible, only less than a user specified upper bound.
 
@@
 pattern graphs).
-
-}
 

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 %Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
-The {\em top-$k$ team formation} problem (\teamF) is to find a list of $k$ highly collaborative teams of experts such that every team satisfies the skill requirements of a certain task.
-Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed for \teamF,
+The {\em top-$k$ team formation} problem is to find a list of $k$ highly collaborative teams of experts such that every team satisfies the skill requirements of a certain task.
+Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed,
 and fall into two categories in terms of the way to improve the collaborative compatibility of team members:
@@
 
-One may verify that existing methods \cite{Lappas09,Kargar11,GajewarS12,GajewarS12,realTeamForm13}, can hardly find a desired team.
+One may verify that existing methods \cite{Lappas09,Kargar11,GajewarS12,realTeamForm13}, can hardly find a desired team.
 They only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13}  (condition (a)), and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints (condition (b)).
@@
 Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.
-Essentially, we utilize patterns to captures the structural constraint, and revise the semantics of graph pattern matching for team formation.
+Essentially, we utilize patterns to capture the structural constraint, and revise the semantics of graph pattern matching for team formation.
 For instance, a desired team requirement can be specified by the pattern $P_1$ (ignore dashed edges) in Fig.~\ref{fig-motivation-example}, in which nodes represent the skill requirements,  edges specify the topology constraint, and the bounds on nodes are the capacity constraint.
@@
 
-Another issue is that team formation is accompanied with a highly dynamic situation.
+Another issue is that team formation is accompanied with a highly dynamic environment.
 It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}.
 Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}.
-We illustrate this with an example.
+We show this with an example.
 
@@
 \stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation (Section~\ref{sec-tsim}).
-It extends existing methods by incorporating the structural and capacity constraints using pattern graphs .
+It extends existing methods by incorporating the structural and capacity constraints using pattern graphs.
 To cope with the highly dynamic environment of team formation, we also formulate the dynamic top-$k$ team formation problem  (Section~\ref{sec-tsim}), for handling separate and simultaneous pattern and data updates.

### 2017-09-29 TF-vldb2018/sec-tsim.tex

@@
 
-\sstab(2) Different from strong simulation with balls having a fixed radius (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is flexible, only less than a user specified upper bound.
+\sstab(2) Different from strong simulation with balls having a fixed radius (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is flexible, and is only less than a user specified upper bound.
 

### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

@@
 \revise{
-We devise an algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for strong simulation~\cite{MaCFHW14}.}
+We devise an algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for \warn{strong simulation}~\cite{MaCFHW14}.}
 
@@
 \ni(1)  Consider pattern $P_2$ in Fig.~\ref{fig-consistency-example}.
-One can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $u$ in $G$, if $u$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.
+One can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $v$ in $G$, if $v$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.
 

### 2017-09-29 TF-vldb2018/sec-tsim.tex

@@
 
- Given $P$, $G$ and two positive integers $r$, $k$, the {\em top-$k$ team formation} problem, denoted as \teamF{(P, G, k)},
+ Given pattern $P$, data graph $G$, and two positive integers $r, k$, the {\em top-$k$ team formation} problem, denoted as \teamF{(P, G, k)},
 is to find a list $L_{k}$ of $k$ perfect subgraphs (\ie teams) with the top-$k$ largest density in $G$ for $P$, via team simulation.
@@
 
-Here the {\em density}\, $\density{G}$ of graph $G(V, E)$ is $|E|/|V|$, where $|E|$ and $|V|$ are the number of edges and the number of nodes respectively, \revise{as commonly used in data mining applications~\cite{maximumDenseSubgraph,EVMK12}}.
+Here the {\em density}\, $\density{G}$ of graph $G(V, E)$ is $|E|/|V|$, where $|E|$ and $|V|$ are the number of edges and the number of nodes respectively, as commonly used in data mining applications~\cite{maximumDenseSubgraph,EVMK12}.
 Intuitively, the larger $\density{G}$ is, the more collaborative a team is.
@@
 
-\revise{
 \begin{example}
@@
 Consider $P_1, G_1$ in Fig.~\ref{exm-motivation} and $r=2$.
-We simply set $k=1$, as most existing algorithms for \teamF{} only compute the best team, instead of top-$k$ teams.
+We simply set $k=1$, as most existing solutions for \teamF{} only compute the best team \cite{Lappas09,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12}, instead of top-$k$ teams.
 
-One may want to look for candidate teams with existing methods, satisfying the search conditions in Example \ref{exm-motivation}:
-(a) by minimizing the {\em team diameter} \cite{Lappas09},
-which returns the team with $\{\kw{BA_3}$, \kw{PM_3}, \kw{UD_4}, \kw{SA_4}, \kw{SD_4}, $\kw{ST_4}\}$;
-(b) by minimizing the {\em sum of all-pair distances} of teams \cite{Kargar11},
-which returns exactly the same team as (a) in this case;
-or (c) by maximizing the {\em team density} \cite{GajewarS12}, which returns the team consisting of the nodes of the two connected components in $G_1$ with \kw{PM_1} and \kw{BA_3} (excluding \kw{UD_2}, \kw{PM_3}, \kw{UD_4}, \kw{SA_4}).
+One may want to look for candidate teams with existing methods, satisfying the search requirement in Example \ref{exm-motivation}:
+\ni(1) by minimizing the {\em team diameter} \cite{Lappas09},
+which returns the team with $\{\kw{BA_3}$, \kw{PM_3}, \kw{UD_4}, \kw{SA_4}, \kw{SD_4}, $\kw{ST_4}\}$,
 
-However, one may notice that these teams only satisfy the skill requirement, \ie the search condition (1) in Example \ref{exm-motivation}, and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints.
-Indeed, the team found in (a) and (b) is connected by \kw{BA_3} only, and the team found in (c) has loose collaborations among its members.
+\ni(2) by minimizing the {\em sum of all-pair distances} of teams \cite{Kargar11},
+which returns exactly the same team as (a) in this case, or
+
+\ni(3) by maximizing the {\em team density} \cite{GajewarS12}, which returns the team with all the nodes in the two connected components in $G_1$ with \kw{PM_1} and \kw{BA_3}, except \kw{UD_2}, \kw{PM_3}, \kw{UD_4}, \kw{SA_4}.
+
+One may already notice that these teams only satisfy the skill requirement, \ie condition (a) in Example \ref{exm-motivation}, and cannot guarantee  the specific collaboration relationships among team members.
+Indeed, the team found in (1) and (2) is connected by \kw{BA_3} only, and the team found in (3) has loose collaborations among its members.
 That is, existing methods are not appropriate for identifying the the desired teams.
@@
 When team simulation is adopted, it returns the perfect subgraph in Example \ref{exm-rsimulation} with its density = 1.4,
-satisfying both search condition (1) and (2), better than the teams found by the existing methods as shown above.
-\end{example}}
+satisfying both conditions (a) and (b), much better than those teams found by the above existing methods.
+\end{example}
 

### 2017-09-29 TF-vldb2018/sec-tsim.tex

@@
 
-\stitle{Dynamic top-$k$ team formation}. Given $P$, $G$, two positive integers $r$, $k$, the list $L_{k}(P,G)$ of top-$k$ perfect subgraphs for $P$ in $G$,
+\stitle{Dynamic top-$k$ team formation}. Given pattern $P$, data graph $G$, two positive integers $r$, $k$, the list $L_{k}(P,G)$ of top-$k$ perfect subgraphs for $P$ in $G$,
 a set of pattern updates $\Delta P$ and a set of data updates $\Delta G$,
@@
 
-It is worth mentioned that the \dynteamF{} problem covers a broad range of dynamic conditions,
+It is worth mentioning that \dynteamF{} covers a broad range of dynamic situations,
 \ie handling continuous separate and simultaneous pattern and data updates.
-Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$.
+Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$, and
  $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 A desired team has
-(a) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
-(b) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.
+(i) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
+(ii) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.
 
@@
 One may verify that existing methods \cite{Lappas09,Kargar11,GajewarS12,realTeamForm13}, can hardly find a desired team.
-They only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13}  (condition (a)), and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints (condition (b)).
+They only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13}  (condition (i)), and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints (condition (ii)).
  \end{example}
@@
 \stab (2) We develop a batch algorithm for computing top-$k$ teams via team simulation (Section~\ref{sec-tsimAlg}).
-We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching .
+We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching.
 We also propose two optimization techniques, incrementally computing radius varied balls and density based filtering, for speeding up computations.

### 2017-09-29 TF-vldb2018/sec-tsim.tex

@@
 %\vspace{-4ex}
-\subsection{Pattern Matching for Team Formation}
+\subsection{Team Formation}
 \label{subsec-extsim}
@@
 Consider $P_1, G_1$ in Fig.~\ref{exm-motivation} and $r=2$.
-We simply set $k=1$, as most existing solutions for \teamF{} only compute the best team \cite{Lappas09,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12}, instead of top-$k$ teams.
+We simply set $k=1$, as most existing solutions for \teamF{} only compute the best team \cite{Lappas09,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12}.
 
@@
 
-One may already notice that these teams only satisfy the skill requirement, \ie condition (a) in Example \ref{exm-motivation}, and cannot guarantee  the specific collaboration relationships among team members.
+One may already notice that these teams only satisfy the skill requirement, \ie condition (i) in Example \ref{exm-motivation}, and cannot guarantee  the specific collaboration relationships among team members.
 Indeed, the team found in (1) and (2) is connected by \kw{BA_3} only, and the team found in (3) has loose collaborations among its members.
@@
 When team simulation is adopted, it returns the perfect subgraph in Example \ref{exm-rsimulation} with its density = 1.4,
-satisfying both conditions (a) and (b), much better than those teams found by the above existing methods.
+satisfying both conditions (i) and (ii), much better than those teams found by the above existing methods.
 \end{example}
@@
 
-\stitle{Pattern updates}. There are five types of pattern updates:
+\stitle{Pattern updates ($\Delta P$)}. There are five types of pattern updates:
 %
@@
 
-\stitle{Data updates}. There are four types of data updates, which can be
+\stitle{Data updates ($\Delta G$)}. There are four types of data updates,
 defined along the same lines as the first four types of pattern updates.

### 2017-09-29 TF-vldb2018/sec-appendix.tex

@@
 \noindent
-{\textbf{1. Proof of Theorem~\ref{thm-tsim-radius}}}
+{\textbf{1. Proof of Proposition~\ref{prop-pattern-consistency}}}
+
+The satisfiability of patterns $P$ can be checked by treating $P$ as both data and pattern graphs, and computing the maximum match relation $M$ in $P$ for $P$, via graph simulation.
+Indeed, pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. 
+Observe that computing graph simulation and the size of $M$ is bounded by $|P|^2$.
+
+\noindent
+{\textbf{2. Proof of Theorem~\ref{thm-tsim-radius}}}
 
@@
 \noindent
-{\textbf{2. Proof of Proposition~\ref{thm-inc-grouprec-pat}}}
+{\textbf{3. Proof of Proposition~\ref{thm-inc-grouprec-pat}}}
 
@@
 \noindent
-{\textbf{3. Proof of Theorem~\ref{thm-compose}}}
+{\textbf{4. Proof of Theorem~\ref{thm-compose}}}
 
@@
 \noindent
-{\textbf{4. Proof of Proposition~\ref{prop-fragmentation}}}
+{\textbf{5. Proof of Proposition~\ref{prop-fragmentation}}}
 
@@
 \noindent
-{\textbf{5. Proof of Proposition~\ref{prop-canaffballs}}}
+{\textbf{6. Proof of Proposition~\ref{prop-canaffballs}}}
 
@@
 \noindent
-{\textbf{6. Proof of Proposition~\ref{prop-affected-datainc}}}
+{\textbf{7. Proof of Proposition~\ref{prop-affected-datainc}}}
 

### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

--- 2017-09-27 TF-vldb2018/sec-tsimAlg.tex
@@
 	\begin{center}
-		\includegraphics[scale=1.28]{./fig/consistency_motivation.eps}
+		\includegraphics[scale=1.38]{./fig/consistency_motivation.eps}
 	\end{center}
 	\vspace{-3ex}
-	\caption{Pattern graphs}
+	\caption{Pattern satisfiability}
 	\vspace{-4ex}
@@
 
-\revise{
-We devise an algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for strong simulation~\cite{MaCFHW14}.}
+In this section, we first study the pattern satisfiability problem for team formation, then introduce two  two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.
+
+% with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for \warn{strong simulation}~\cite{MaCFHW14}.
 
 \stitle{Pattern satisfiability}.
-Given a pattern $P$, \grouprec firstly checks whether $P$ is satisfiable.
-We say that a pattern $P$ is {\em satisfiable} iff there exists a data graph $G$ such that $P$ matches $G$ via team simulation, \ie $P \eeps G$.
-
 Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
-pattern graphs may be unsatisfiable for team simulation, due to the presence of capacity constraints enforced on patterns. We illustrate this with an example below.
+there exist pattern graphs that do not match any data graph via team simulation, due to the presence of capacity constraints enforced on patterns. We illustrate this with an example below.
 %\looseness=-1
@@
 \label{exm-consistency}
-\ni(1)  Consider pattern $P_2$ in Fig.~\ref{fig-consistency-example}.
-One can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $u$ in $G$, if $u$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.
+\ni(1) For pattern $P_2$ in Fig.~\ref{fig-consistency-example},
+one can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $v$ in $G$, if $v$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.
 
-\sstab(2) Pattern $P_1$ in Fig.~\ref{exm-motivation} is satisfiable as $P_1 \eeps G_1$.
+\sstab(2) However, pattern $P'_2$ in Fig.~\ref{fig-consistency-example} is satisfiable as $P'_2 \eeps G_2$, and pattern $P_1$ in Fig.~\ref{exm-motivation} is also satisfiable as $P_1 \eeps G_1$.
 \end{example}
 
+%Given a pattern $P$, \grouprec firstly checks whether $P$ is satisfiable.
+
+We say that a pattern $P$ is {\em satisfiable} iff there exists a data graph $G$ such that $P$ matches $G$ via team simulation, \ie $P \eeps G$.
 The good news is that checking the satisfiability of pattern graphs can be done in low polynomial time.
@@
 
-\proofS By treating $P$ as both data and pattern graphs, compute the maximum match relation $M$ in $P$ for $P$, via graph simulation.
-Indeed, pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds.
-Observe that the size of $M$ is bounded by $|P|^2$.
-\eop
+By treating $P$ as both data and pattern graphs, compute the maximum match relation $M$ in $P$ for $P$, via graph simulation.
+Then pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds.
+Observe that the size of $M$ is bounded by $|P|^2$, and pattern graphs are also small.
+
+By Proposition~\ref{prop-pattern-consistency}, we shall consider  satisfiable pattern graphs only  in the sequel.
 

### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

@@
 
-\stitle{Pattern satisfiability}.
+\subsection{Pattern Satisfiability}
 Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
-there exist pattern graphs that do not match any data graph via team simulation, due to the presence of capacity constraints enforced on patterns. We illustrate this with an example below.
+there exist pattern graphs match no data graphs via team simulation, due to the presence of capacity constraints on patterns. We illustrate this with an example.
 %\looseness=-1
@@
 Then pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds.
-Observe that the size of $M$ is bounded by $|P|^2$, and pattern graphs are also small.
+Observe that the size of $M$ is bounded by $|P|^2$, and pattern graphs are typically small.
 
@@
 
-\revise{
-\stitle{Incremental computing for radius varied balls}. Recall that given $G$, $P$, $k$ and $r$, \teamF\,is to find top-$k$ teams within balls $\ball{[v, t]}$, where $v \in V$ and $t \in [1,r]$.
+\subsection{Batch Algorithm}
+
+\stitle{Handling radius varied balls}. \teamF{} is to find top-$k$ teams within balls $\ball{[v, t]}$, where $v \in V$ and $t \in [1,r]$.
 %centered at each node in $G$ with radius $t$ varying from 1 to $r$.
-However, it is extremely costly to construct all such balls, \ie $r\cdot|V|$ balls, to compute perfect subgraphs residing in them.
-Instead, \grouprec only constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$
-where $v \in V$ and radius is $r$ ,
-and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$ who shares the same center node.
-The correctness of \grouprec is assured by the theorem below.
+However, it is very costly to construct all $r|V|$ balls, and to compute perfect subgraphs in all of them.
+Indeed it is also not necessary, and it only needs to constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$
+where $v \in V$ and radius is $r$, and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$, as shown below.
 
@@
 
-When we get the match graph $G_s$ in $\ball{[v, r]}$ for $P$ via graph simulation, to compute the perfect subgraph in $\ball{[v, t]}$ ($t \in [1,r-1]$) for $P$ via team simulation, we need to
+When we have the match graph $G_s$ in $\ball{[v, r]}$ for $P$ via graph simulation, to compute the perfect subgraph in $\ball{[v, t]}$ ($t \in [1,r-1]$) for $P$ via team simulation, we need to
 (1) first identify the subgraph $G_s^{t}$ in $G_s$ belonging to $\ball{[v, t]}$, which can be easily identified in the process for constructing $\ball{[v, r]}$ without extra computation;
@@
 This can be achieved by executing an efficient incremental process in~\cite{FanWW13-tods}; and
-(3) finally check whether capacity bounds are satisfied. If so, $G'_s$ is the perfect subgraph in $\ball{[v, r]}$ for $P$ via team simulation.}
+(3) finally check whether capacity bounds are satisfied. If so, $G'_s$ is the perfect subgraph in $\ball{[v, r]}$ for $P$ via team simulation.
 
-\stitle{Density based filtering}.
-Although we have reduced a significant amount of computation by only computing team simulation for a number of $|V|$ balls by the incremental optimization above, we can further optimize the process by adopting the density based filtering technique.
-%A typical idea to devise algorithms for \teamF\, is to compute the perfect subgraph within each ball and maintains the top-$k$ non-repeated perfect subgraphs with current top-$k$ largest density, and returns them when all balls are processed.
-%This technique allows algorithm \grouprec to compute the top-$k$ perfect subgraphs \wrt $P$ without necessarily computing team simulation for all balls in $G$.
-It allows \grouprec to compute team simulation for much less than $|V|$ balls.
-The crucial issue is how can tell whether a ball has the possibility to have one of the final top-$k$ results in itself or in its inner balls with the same center node.
-%If the answer is yes, we should check team simulation for that ball; Otherwise, we just skip the ball to the remaining balls.
-The idea is, given a ball $\ball{[v,r]}$, we calculate the upper bound of $\density{\hat{G}_s}$,
+\stitle{Density based ball filtering}. We further reduce the number of balls to speedup the process by adopting the density based filtering technique.
+The key idea is to tell whether a ball is possible to produce one of the final top-$k$ matches.
+
+Given a ball $\ball{[v,r]}$, we calculate the upper bound of $\density{\hat{G}_s}$,
 where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
-If the bound is larger than the current $k$-th result, \ie there is possibility the final answer resides in the ball or the inner balls, compute team simulation for it;
-Otherwise, skip the ball to the remaining balls to avoid redundant team simulation computing.
+If the bound is larger than the current $k$-th result, \ie there is a possibility the for the ball;
+Otherwise, we the ball is simply ignored to avoid redundant computations for  team simulation.
 
-The problem here is how to efficiently compute the upper bound of $\density{\hat{G}_s}$ for each ball in $G$.
+The trick part is how to efficiently compute the upper bound of $\density{\hat{G}_s}$ for each ball in $G$.
 As the best densest subgraph algorithms are in $O(|\ball{[v,r]}|^3)$ time \cite{maximumDenseSubgraph}, which is costly,
@@
 
-We are now ready to present algorithm \grouprec for \teamF{}.
+We are now ready to present our batch algorithm for \teamF{}.
 
-\revise{
 \stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
@@
 an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
-It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the data incremental algorithms in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11).}
+It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the data incremental algorithms in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11).
 %Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
@@
 (2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
-\warn{
 It takes $O(|P|^2)$ to check pattern satisfiability, $O(|V||P||G|)$ to compute team simulation, $O(r|V||V_{P}||E|)$ to incrementally compute matches in inner balls, and $O(|V||E|)$  to compute the density of the maximum core for $|V|$ balls.
 Thus \grouprec is in $O(|P|^2+|V||P||G|+r|V||V_{P}||E|)$.
-However, actual time is much less due to early termination and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.}
-\looseness=-1
+However, actual time is much less due to early termination and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.
 

### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

@@
 
-Given a ball $\ball{[v,r]}$, we calculate the upper bound of $\density{\hat{G}_s}$,
+Given a ball $\ball{[v,r]}$, we compute the density upper bound  $\density{\hat{G}_s}$,
 where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
-If the bound is larger than the current $k$-th result, \ie there is a possibility the for the ball;
-Otherwise, we the ball is simply ignored to avoid redundant computations for  team simulation.
+If the bound is larger than the density of the current $k$-th result, \ie there is a possibility the for the ball;
+Otherwise, the ball is simply ignored to avoid redundant computations.
 

### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

@@
 
-In this section, we first study the pattern satisfiability problem for team formation, then introduce two  two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.
+In this section, we first study the pattern satisfiability problem for team formation, then introduce two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.
 
@@
 \subsection{Batch Algorithm}
+
+We then introduce two techniques for optimizing the computation of team simulation.
 

### 2017-09-29 TF-vldb2018/sec-intro.tex

@@
 
-Another issue is that team formation is accompanied with a highly dynamic environment.
-It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}.
+Another issue lies in that team formation is accompanied with a highly dynamic environment.
+It typically needs many efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}.
 Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}.

### 2017-09-29 TF-vldb2018/sec-dynamicTopk.tex

@@
 
-\section{A Unified Incremental Method}
+\section{A Unified Incremental Solution}
 \label{sec-dynamictopk}
 
-\revise{
-%In last section, we have studied the top-$k$ team formation problem.
-Based on the dynamic top-$k$ team formation problem defined in Section~\ref{subsec-dynteamF}, 
-in this section, we first theoretically analyze the challenges and design principles, 
+In this section, we first analyze the challenges and design principles of dynamic top-$k$ team formation,
 and then develop a unified incremental framework for \dynteamF.
-For convenience, the notations used are summarized in Table~\ref{tab-notation}.}
+For convenience, the notations used are summarized in Table~\ref{tab-notation}.
+
+\subsection{Analyses of Dynamic Team Formation}
 
@@
 			\end{tabular}
-			\vspace{-2ex}
+			\vspace{-1ex}
 		\end{small}
@@
 
-%\subsection{A Unified Incremental Approach}
+\subsection{A Unified Incremental Approach}
 %\label{subsec-framework}
@@
 However, $P$ and $h$ are typically small in practice~\cite{FanLMTWW10}, \eg $|P|=15$ and $h=3$.
-In light of this, we give a heuristic algorithm, denoted by \kw{PFrag}, for the problem, and is shown in the Appendix.
+In light of this, we give a heuristic algorithm, denoted by \kw{PFrag}, for the problem, and is shown in the
+full version~\cite{fullvldb18}.
 \kw{PFrag} works by connecting pattern fragmentation to the widely studied {\sc $(k, \nu)$-Balanced Partition} problem \cite{AndreevR06},

### 2017-09-30 TF-vldb2018/sec-tsim.tex

@@
 
- Given pattern $P$, data graph $G$, and two positive integers $r, k$, the {\em top-$k$ team formation} problem, denoted as \teamF{(P, G, k)},
+ Given pattern $P$, data graph $G$, and two positive integers $r$ and $k$, the {\em top-$k$ team formation} problem, denoted as \teamF{(P, G, k)},
 is to find a list $L_{k}$ of $k$ perfect subgraphs (\ie teams) with the top-$k$ largest density in $G$ for $P$, via team simulation.
@@
 \ni(2) by minimizing the {\em sum of all-pair distances} of teams \cite{Kargar11},
-which returns exactly the same team as (a) in this case, or
+which returns exactly the same team as (1) in this case, or
 
@@
 
-We next introduce dynamic top-$k$ team formation.
+We now introduce dynamic top-$k$ team formation.
 %For convenience, the notations used are summarized in Table~\ref{tab-notation}.
@@
 
-\stitle{Dynamic top-$k$ team formation}. Given pattern $P$, data graph $G$, two positive integers $r$, $k$, the list $L_{k}(P,G)$ of top-$k$ perfect subgraphs for $P$ in $G$,
+\stitle{Dynamic top-$k$ team formation}. Given pattern $P$, data graph $G$, positive integers $r$ and $k$, the list $L_{k}(P,G)$ of top-$k$ perfect subgraphs for $P$ in $G$,
 a set of pattern updates $\Delta P$ and a set of data updates $\Delta G$,
@@
 
+Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$, and
+ $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.
  It is worth mentioning that \dynteamF{} covers a broad range of dynamic situations,
 \ie handling continuous separate and simultaneous pattern and data updates.
-Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$, and
- $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.
 

### 2017-09-30 TF-vldb2018/sec-tsimAlg.tex

@@
 Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
-there exist pattern graphs match no data graphs via team simulation, due to the presence of capacity constraints on patterns. We illustrate this with an example.
+there exist patterns that cannot match any data graph via team simulation, due to the presence of capacity constraints on patterns. We illustrate this with an example.
 %\looseness=-1
@@
 However, it is very costly to construct all $r|V|$ balls, and to compute perfect subgraphs in all of them.
-Indeed it is also not necessary, and it only needs to constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$
+Indeed it is also not necessary, and it only needs to construct and compute the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$
 where $v \in V$ and radius is $r$, and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$, as shown below.
@@
 where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
-If the bound is larger than the density of the current $k$-th result, \ie there is a possibility the for the ball;
+If the bound is larger than the density of the current $k$-th result, \ie there is a possibility for the ball;
 Otherwise, the ball is simply ignored to avoid redundant computations.
@@
 It firstly checks whether $P$ is satisfiable (line 1).
-If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the early termination condition holds (lines 3-6).
-If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
+If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the
+density based ball filtering condition holds (lines 3-6).
+If so, it skips the current ball, and moves to the next one;
 otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see full version~\cite{fullvldb18}),
@@
 %(1) There is a unique perfect subgraph in each ball of $G$.
-(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as for simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
+(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as graph simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
 (2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
@@
 Thus \grouprec is in $O(|P|^2+|V||P||G|+r|V||V_{P}||E|)$.
-However, actual time is much less due to early termination and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.
+However, actual time is much less due to density based ball filtering and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.
 
@@
 			\mat{0ex}{
-				\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $k, r$.\\
+				\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $r$ and $r$.\\
 				{\sl Output:\/} Top-$k$ densest teams.\\
@@
 				\icc \>\> \If 2*$\density{\ball{}_C} <$  the density of the $k$-th result in $L_{k}$ \Then\\
-				\icc  \>\>\hspace{2ex}\= \Return $L_{k}[0:k-1]$;\\
+				\icc  \>\>\hspace{2ex}\= \Continue;\\
 				\icc \>\> $G_s$ := \rgraphsim$(P, \ball{[v,r]})$; \\
@@
 	\label{alg-grouprec}
-	\vspace{-4ex}
+	\vspace{-3ex}
 \end{figure}

### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

@@
 
-\revise{
-By Theorem~\ref{thm-tsim-radius}, we know that $P$ matches a ball $\ball{[v, t]}$ ($t \in [1,r-1]$), only when $P$ matches ball $\ball{[v, r]}$ via graph simulation,
+By Theorem~\ref{thm-tsim-radius}, pattern $P$ matches a ball $\ball{[v, t]}$ ($t \in [1,r-1]$), only if $P$ matches ball $\ball{[v, r]}$ via graph simulation,
 and the match results for $\ball{[v, t]}$ can be derived from the matches for $\ball{[v, r]}$.
-Therefore, we only concern about balls $\ball{[v, r]}$ in the incremental process, and finally compute the matches for balls $\ball{[v, t]}$ after we get the matches for ball $\ball{[v, r]}$.
-Note that in the following when we refer to a ball, we indicate the ball with radius $r$ by default.}
+Therefore, the key of the incremental computation is to deal with the balls $\ball{[v, r]}$ with radius $r$.
+In the sequel, a ball has a radius $r$ by default.
 
@@
 
+We first analyze the inherent computational complexity of the dynamic top-$k$ team formation.
+
 \stitle{Incremental complexity analysis}.
-As observed in~\cite{Reps96}, the complexity of an incremental algorithm should be measured by the size $|\aff|$ of {\em the changes} in the input and output, rather than the entire input, to measure the amount of work absolutely necessary to be performed for the problem.
+As observed in~\cite{Reps96,inc-survey}, the complexity of incremental algorithms should be measured by the size $|\aff|$ of {\em the changes} in the input and output, rather than the entire input, to measure the amount of work essentially to be performed for the problem.
 
-An incremental problem is said to be {\em bounded} if it can be solved by an algorithm whose complexity is a function of $|\aff|$ alone, and {\em unbounded}, otherwise.
-Unfortunately, \dynteamF\, is unbounded, similar to the observations in \cite{FanLMTWW10,FanWW13-tods}.
+An incremental problem is said to be {\em bounded} if it can be solved by an algorithm whose complexity is a function of $|\aff|$ alone, and is {\em unbounded}, otherwise.
+Unsurprisingly, the dynamic top-$k$ team formation problem is unbounded, similar to the other extensions of graph simulation \cite{FanLMTWW10,FanWW13-tods}.
 
@@
 \label{thm-inc-grouprec-pat}
-The \dynteamF\, problem is unbounded, even for $k$ = 1 and unit pattern or data updates.
+The \dynteamF{} problem is unbounded, even for $k$ = 1 and unit pattern or data updates.
 \end{prop}
+
+We then illustrate the impact of pattern and data updates on the matching results.
 
@@
 \label{exm-pattern-challenge}
-Continue Example~\ref{exm-motivation-inc}, and consider updates $\Delta P_1$ or $\Delta G_1$ that obviously may introduce new matches.
+Continue Example~\ref{exm-motivation-inc} with $\Delta P_1$ and $\Delta G_1$.
+
+% that obviously may introduce new matches.
 %For convenience of presentation, we treat $\Delta P_1$ and $\Delta G_1$ separately.
@@
 (1) For $\Delta P_1$, $\ball{[\kw{PM_1}, 2]}$ already matches $P$, and may produce more matched nodes for $P_1\oplus \Delta P_1$,
-thus a re-computation for perfect subgraphs in the ball is needed.
+thus a re-computation for perfect subgraphs is needed.
 For all other balls, $\Delta P_1$ may turn unmatched nodes to matched and may produce perfect subgraphs,
 thus re-computation is also needed.
-\looseness=-1
 
@@
 (2) For $\Delta G_1$, it produces a new perfect subgraph for $P$ in $G_1\oplus\Delta G_1$,
-\ie the connected component containing \kw{PM_2}.
-The question is how to directly find new and maintain previous answers without redundant computation.
-\looseness=-1
+\ie the connected component having \kw{PM_2}.
+%The question is how to directly find new and maintain previous answers without redundant computation.
 \end{example}
@@
 
-\subsection{A Unified Incremental Approach}
+\subsection{Unified Incremental Framework}
 %\label{subsec-framework}

### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

@@
 
-We then illustrate the impact of pattern and data updates on the matching results.
+We then illustrate the impact of pattern and data updates on the matching results with an example.
 
@@
 
-We next analyze the difficulties and principles of designing incremental algorithms for \dynteamF{} from three aspects.
+We finally discuss the challenges and principles of designing incremental algorithms for \dynteamF{} from three aspects.
 
@@
 
-\stitle{(1) Impacts of pattern and data updates}. It is necessary to identify and localize the impacts of pattern/data updates.
-As indicated by Proposition~\ref{thm-inc-grouprec-pat} and Example~\ref{exm-pattern-challenge},
-one can verify that (a) a unit pattern update is likely to result in the entire change in previous results,
-such that all balls need to be accessed and all matches need to be re-computed;
-%
-and (b) data updates directly change the structure of data graphs, and its impact may be global, such that the entire data graph may need to be accessed to re-compute matches.
+\stitle{(1) Impacts of pattern and data updates}.
+Beyond Proposition~\ref{thm-inc-grouprec-pat} and Example~\ref{exm-pattern-challenge}, one can also verify that (a) unit pattern updates are likely to result in the entire change in previous results, such that all balls need to be accessed and all matches need to be re-computed,
+and (b) the impact of data updates can also be global, such that the entire data graph may need to be accessed to re-compute matches.
+Hence, the key is to identify and localize the impacts of pattern and data updates.
 
@@
 Auxiliary data on intermediate or final results for $P$ in $G$ are typically maintained for incremental computation \cite{Reps96,FanWW13-tods}.
-How to design light-weight and effective auxiliary structures is the key.
+How to design light-weight and effective auxiliary structures is critical.
 One may want to store $M(P,G)$, the match relations of $P$ for all balls in $G$,
@@
 %and if exist, the dynamic algorithms either support pattern or data updates, not both of them~\cite{MottinGReform15,FanWW13-tods}.
-A practical solution should support continuous pattern and data updates, separately and simultaneously, which further raises difficulties on the design of auxiliary data structures and on incremental algorithms.
+A practical solution should support continuous pattern and data updates, separately and simultaneously, which further increases difficulties on the design of auxiliary data structures and incremental algorithms.
 

### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

@@
 
-\vspace{1.0ex}
-We next develop an incremental approach to handling pattern and data updates in a unified framework, based on {\em pattern fragmentation} and {\em affected balls}
-to localize the impacts of pattern and data updates and to reduce the cost of maintaining auxiliary structures and computations.
+Nevertheless, we develop an incremental approach to handling pattern and data updates in a unified framework, by utilizing {\em pattern fragmentation} and {\em affected balls} to localize the impacts of pattern and data updates, and to reduce the cost of maintaining auxiliary structures and computations.
 
@@
 
-\stitle{Pattern fragmentation}. We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
+\stitle{(i) Localization with pattern fragmentation}.
+We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
 if (1) $\bigcup_{i=1}^{h}V_{fi}=V_{P}$, (2) $V_{fi}\cap V_{fj} = \emptyset$ for any $i\ne j\in[1, h]$,
@@
 
-We also refer to $P_{fi}$ ($i\in[1,h]$) as a {\em fragment} of $P$, and $C$ as a {\em cut} of $P$, respectively.
+We also say $P_{fi}$ ($i\in[1,h]$) as a {\em fragment} of $P$, and $C$ as a {\em cut} of $P$, respectively.
 
-Observe that by pattern fragmentation, a pattern update on $P$ is either on a fragment $P_{fi}$ or on the cut $C$ of $P$, and, in this way, the impact of pattern updates is localized. %to some extent.
-
-\vspace{0.5ex}
-Graph simulation has a nice property as follows.
+Observe that by pattern fragmentation, a pattern update on $P$ is either on a fragment $P_{fi}$ or on the cut $C$ of $P$, and, in this way, the impact of pattern updates is localized.
+Moreover, graph simulation holds a nice property on pattern fragmentation, as shown below.
 
@@
 Let $\{P_{f1},\ldots,P_{fh}\}$ be an $h$-fragmentation of pattern $P$.
-For any ball $\ball{}$ in $G$, let $M_i$ ($i\in[1,h]$) be the maximum match relation in $\ball{}$ for $P_{fi}$ via graph simulation,
-and $M$ be the maximum match relation in $\ball{}$ for $P$ via graph simulation, respectively,
+For any ball $\ball{}_i$ in $G$, let $M_i$ ($i\in[1,h]$) be the maximum match relation in $\ball{}_i$ for $P_{fi}$ via graph simulation,
+and $M$ be the maximum match relation in $\ball{}_i$ for $P$ via graph simulation, respectively,
 then $M\subseteq\bigcup_{i=1}^{h}M_{i}$.
@@
 
-We also say that $M_i$ is a {\em partial match relations} in ball $\ball{}$ for $P$ via graph simulation.
+We also say that $M_i$ is a {\em partial match relation} in ball $\ball{}_i$ for $P$ via graph simulation.
 %By Theorem~\ref{thm-compose}, instead of computing $M$ in $\ball{}$ \wrt\ $P$ directly, we can compute $M$ by first computing each $M_i$ in $\ball{}$ \wrt\ $P_{fi}$,
 %and then combining them together.
-By the nature of graph simulation~\cite{infsimu95}, $\bigcup_{i=1}^{h}M_{i}$ is actually intermediate results for computing $M$.
+By the nature of graph simulation~\cite{infsimu95}, $\bigcup_{i=1}^{h}M_{i}$ is actually an intermediate result of $M$.
 %such that the method above does not incur additional computation cost.
-After we have the maximum match relation $M$ for $P$ in $\ball{}$, via graph simulation, we can further produce the result for $P$ in  $\ball{}$ via team simulation, by a capacity check.
+Once we have the maximum match relation $M$ for $P$ in $\ball{}_i$, via graph simulation, we can further produce the result for $P$ in  $\ball{}$ via team simulation, by a capacity check.
 
-That is, based on pattern fragmentation, we store and maintain $\tilde{M}(P,G)$ \wrt ${\cal P}_{h}$ for the incremental process,
-\ie the maximum match relations for all pattern fragments of $P$ in all balls of $G$, via graph simulation.
-Moreover, its space cost is light-weight, as shown in the experiments section.
+That is, based on pattern fragmentation, we maintain 
+an auxiliary structure for storing fragment-ball matches for incremental computations,
+\ie $\tilde{M}(P,G)$ \wrt ${\cal P}_{h}$ that is the maximum match relations for all pattern fragments of $P$ in all balls of $G$, via graph simulation.
+Moreover, its space cost is light-weight, as will be shown in the experimental study.
 %\revise{
@@
 
-We already know that pattern updates $\Delta P$ on $P$ can be treated as the updates $\Delta P$ on $P_{fi}$ or $C$ of $P$.
+%We already know that pattern updates $\Delta P$ on $P$ can be treated as the updates $\Delta P$ on $P_{fi}$ or $C$ of $P$.
 %If we have cached the maximum match relations of all pattern fragments,
-By storing $\tilde{M}(P,G)$, we can get $\bigcup_{i=1}^{h}M_{i}$ for a ball $\ball{}$.
-Then we can do an update computation on $M_i$ while leaving other parts unchanged.
-That is, to compute $P_{fi}\oplus\Delta P(\ball{})$ instead of $P\oplus\Delta P(\ball{})$, and to combine $P_{fi}\oplus\Delta P(\ball{})$ with the other parts to derive $P\oplus\Delta P(\ball{})$.
-Even better, the updates $\Delta P$ on $C$ of $P$ only involve with the combination process, avoiding the computation for any pattern fragments.
+By storing $\tilde{M}(P,G)$, we have $\bigcup_{i=1}^{h}M_{i}$ for each ball $\ball{}$,
+and we can simply update $M_i$ while leaving other parts untouched.
+That is, we indeed compute for $P_{fi}\oplus\Delta P(\ball{})$, instead of $P\oplus\Delta P(\ball{})$, and combine all $P_{fi}\oplus\Delta P(\ball{})$ derive $P\oplus\Delta P(\ball{})$.
+Even better, the updates $\Delta P$ on $C$ of $P$ only involve with a simple combination process, avoiding the computation for any pattern fragments.
 
-\vspace{0.8ex}
-\revise{During the incremental process, we typically want} (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.
-Thus we define the {\em pattern fragmentation} problem. Given $P$ and a positive integer $h$, it is to find
+For a better incremental process, we typically want (1) to avoid skewed updates by balancing the sizes of all fragments, and (2) to minimize the efforts to assemble the partial matches of all fragments.
+Thus we define and investigate the {\em pattern fragmentation} problem.
+
+Given pattern $P$ and a positive integer $h$, it is to find
 an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized.
-\revise{Intuitively, the bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size
-	while minimizing the cut size between pattern fragments.}
+Intuitively, the bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size while minimizing the cut size.
 
@@
 
-\vspace{1.0ex}
-So far, we have restricted the impact of pattern updates from the entire $P$ to a fraction of $P$.
-We further localize the impact of pattern and data updates  with {\em affected balls} to avoid computing and updating match relations for all balls.
+\stitle{(ii) Localization with affected balls (\affballsx)}.
+We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computing and updating match relations for all balls.
 
-\stitle{Affected balls (\affballsx)}.
 We say a ball in $G$ is {\em affected} \wrt an incremental algorithm \algorithm{A}, and pattern and data updates,

### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

@@
 
-\stitle{(i) Localization with pattern fragmentation}.
+\stitle{(1) Localization with pattern fragmentation}.
 We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
@@
 
-\vspace{-0.5ex}
 However, $P$ and $h$ are typically small in practice~\cite{FanLMTWW10}, \eg $|P|=15$ and $h=3$.
@@
 
-\stitle{(ii) Localization with affected balls (\affballsx)}.
+\stitle{(2) Localization with affected balls (\affballsx)}.
 We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computing and updating match relations for all balls.
 
-We say a ball in $G$ is {\em affected} \wrt an incremental algorithm \algorithm{A}, and pattern and data updates,
+We say that a ball in $G$ is {\em affected} \wrt an incremental algorithm \algorithm{A}, and pattern and data updates,
 if \algorithm{A} accesses the ball again.
@@
 
-\stitle{Remark}.
+%\stitle{Remark}.
 By pattern fragmentation and affected balls, we essentially localize the impact of pattern and data updates from the entire to a fraction of $P$ and from all to a subset of balls in $G$ for team simulation.
@@
 %\vspace{-0.5ex}
-\stitle{Algorithm \inc}. We now provide a unified incremental algorithm \inc  to handle both pattern and data updates.
+\stitle{(3) Algorithm \inc}. We now provide a unified incremental solution to handle both pattern and data updates.
 
-Given $P$ with its $h$-fragmentation ${\cal P}_{h}$, $G$, two integers $k, r$,
-and auxiliary structures such as the partial match relations for all pattern fragments and all balls (radius $r$),
-while auxiliary structures are to be presented in next section,
+Given pattern $P$ with its $h$-fragmentation ${\cal P}_{h}$, data graph $G$, two integers $r$ and $k$,
+and auxiliary structures (to be introduced in Section \ref{sec-IncAlg}) such as the partial match relations for all pattern fragments and all balls (radius $r$),
 the algorithm consists of three steps for $\Delta P$ and $\Delta G$, as follows.

### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

@@
 %\vspace{-0.5ex}
-\stitle{(3) Algorithm \inc}. We now provide a unified incremental solution to handle both pattern and data updates.
+\stitle{(3) Algorithm framework}. We now provide a unified incremental algorithm to handle both pattern and data updates,
+based on pattern fragmentation and affected balls.
 
@@
 and auxiliary structures (to be introduced in Section \ref{sec-IncAlg}) such as the partial match relations for all pattern fragments and all balls (radius $r$),
-the algorithm consists of three steps for $\Delta P$ and $\Delta G$, as follows.
+algorithm \inc  consists of three steps for $\Delta P$ and $\Delta G$, as follows.
 

### 2017-09-30 TF-vldb2018/sec-tsimAlg.tex

@@
 %(1) There is a unique perfect subgraph in each ball of $G$.
-(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as graph simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
-(2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
+
+\sstab(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as graph simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
+
+\sstab(2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
 It takes $O(|P|^2)$ to check pattern satisfiability, $O(|V||P||G|)$ to compute team simulation, $O(r|V||V_{P}||E|)$ to incrementally compute matches in inner balls, and $O(|V||E|)$  to compute the density of the maximum core for $|V|$ balls.
@@
 			\mat{0ex}{
-				\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $r$ and $r$.\\
+				\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $r$ and $k$.\\
 				{\sl Output:\/} Top-$k$ densest teams.\\
@@
 				\icc \>\hspace{2ex}\= compute the maximum core $\ball{}_{C}$ of the ball $\ball{[v,r]}$;\\
-				\icc \>\> \If 2*$\density{\ball{}_C} <$  the density of the $k$-th result in $L_{k}$ \Then\\
+				\icc \>\> \If 2*$\density{\ball{}_C} \le$  the density of the $k$-th result in $L_{k}$ \Then\\
 				\icc  \>\>\hspace{2ex}\= \Continue;\\
 				\icc \>\> $G_s$ := \rgraphsim$(P, \ball{[v,r]})$; \\
-				\icc \>\> If $G_s$ satisfy capacity bounds on $P$ \Then Insert $G_s$ into $L_{k}$;\\
+				\icc \>\> If $G_s$ satisfies capacity bounds on $P$ \Then Insert $G_s$ into $L_{k}$;\\
 				\icc \>\> \For each ball $\ball{[v,t]}$ with $t\in[1,r-1]$ \Do\\
 				\icc \>\>\hspace{2ex}\= $G'_s$ := \kw{incSim}$(G_s, P, \ball{[v,t]})$;\\
-				\icc \>\>\> If $G'_s$ satisfy capacity bounds on $P$ \Then Insert $G'_s$ into $L_{k}$;\\
+				\icc \>\>\> If $G'_s$ satisfies capacity bounds on $P$ \Then Insert $G'_s$ into $L_{k}$;\\
 				%\icc \>\> \If $\density{G_s}>$ the density of the $k$-th result in $L_{k}$ \Then\\

### 2017-09-30 TF-vldb2018/sec-intro.tex

@@
 It extends existing methods by incorporating the structural and capacity constraints using pattern graphs.
-To cope with the highly dynamic environment of team formation, we also formulate the dynamic top-$k$ team formation problem  (Section~\ref{sec-tsim}), for handling separate and simultaneous pattern and data updates.
+To cope with the highly dynamic environment of team formation, we also formulate the dynamic top-$k$ team formation problem  (Section~\ref{sec-tsim}), for dealing with pattern and data updates, separately and simultaneously.
 
@@
 We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching.
-We also propose two optimization techniques, incrementally computing radius varied balls and density based filtering, for speeding up computations.
+We also propose two optimization techniques, handling radius varied balls and density based filtering, for speeding up the process of computations.
 

### 2017-09-30 TF-vldb2018/sec-expt.tex

@@
 
-\vspace{-0.2ex}
-\stitle{Experimental Settings.} We use the following settings.
+\subsection{Experimental Settings}
+
+ We used the following settings.
 
@@
 
-\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb} (see~\cite{fullvldb18}).
+\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The description of the dataset can be found in the full version~\cite{fullvldb18}.
 
@@
 
-%\subsection{Experimental Results}
+\subsection{Experimental Results}
 
-\stitle{Experimental Results.} In all the experiments, we set $k=10$, $r=2$, $h=3$, $(|V_{P}|,$ $|E_{P}|)$ to be (10,12),
+We present our findings. In all the experiments, we set $k=10$, $r=2$, $h=3$, $(|V_{P}|,$ $|E_{P}|)$ to be (10,12),
 and capacity bounds to be [1,10] by default.
 When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
-\looseness=-1
-%All the findings on \youtube are reported in the Appendix.
+All the findings on \youtube are reported in the Appendix.
 

### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

@@
 \stitle{(2) Localization with affected balls (\affballsx)}.
-We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computing and updating match relations for all balls.
+We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computations.
 
@@
 
-\etitle{(1) Identifying \affballsx}.
+\etitle{(i) Identifying \affballsx}.
 Algorithm \inc invokes two different procedures to identify \affballsx for separate $\Delta P$ or $\Delta G$, respectively.
@@
 
-\etitle{(2) Update partial match relations in \affballsx}.
+\etitle{(ii) Update partial match relations in \affballsx}.
 For a ball affected by $\Delta P$, \inc updates the partial match relations for the updated pattern fragments with incremental computation;
@@
 
-\etitle{(3) Combining partial match relations}. \inc combines all partial relations for a subset of \affballsx and computes the top-$k$ perfect subgraphs within them and their inner balls.
+\etitle{(iii) Combining partial match relations}. \inc combines all partial relations for a subset of \affballsx and computes the top-$k$ perfect subgraphs within them and their inner balls.
 
@@
 			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-batch.eps}}
-		\vspace{-3ex}
+		\vspace{-2ex}
 		\caption{Example auxiliary data structures}
 		\label{fig-auxiliary-structures}
-		\vspace{-3ex}
+		\vspace{-4ex}
 	\end{center}

### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

@@
 
-\vspace{0.5ex}
-Observe that \inc handles pattern/data updates in a unified way. Better still, it holds a nice property as follows.
-
-\begin{theorem}
-\label{thm-framework-inc}
-With $\tilde{M}(P,G)$ and \fb \wrt an $h$-fragmentation of $P$, given $\Delta P$ and $\Delta G$,
-the incremental algorithm \inc processes $\Delta P$ and $\Delta G$ in time
-determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
-\end{theorem}
-
-We shall prove Theorem~\ref{thm-framework-inc} by providing specific techniques for \inc and analyzing its time complexity in Section~\ref{sec-IncAlg}.
+Observe that \inc handles pattern and data updates, separately and simultaneously, in a unified way.
 

### 2017-09-30 TF-vldb2018/subsec-auxstr.tex

@@
 They are dynamically updated for each unit update in each set of coming pattern updates.
-\looseness=-1
+
+Better still, it holds a nice property as follows.
+\begin{theorem}
+\label{thm-framework-inc}
+With $\tilde{M}(P,G)$ and \fb \wrt an $h$-fragmentation of $P$, given $\Delta P$ and $\Delta G$,
+the incremental algorithm \inc processes $\Delta P$ and $\Delta G$ in time
+determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
+\end{theorem}
+
+We shall prove Theorem~\ref{thm-framework-inc} by providing specific techniques for \inc and analyzing its time complexity in Section~\ref{sec-IncAlg}.
 

### 2017-09-30 TF-vldb2018/sec-expt.tex

@@
 
- We used the following settings.
+ We used the following datasets and settings.
 
@@
 
-\ni (1) {\em \citationd}~\cite{citationWeb} contains 1.39M paper nodes and 3.02M paper-paper citation edges.
-We used its undirected version, where edges indicate the relevance relationship. We generated 200 labels based on phrase clustering of paper titles.
+\ni (1) {\em \citationd}~\cite{citationWeb} is a real-life dataset containing 1.39M paper nodes and 3.02M paper-paper citation edges.
+We used its undirected version, where edges indicate the relevance relationship. We generated 200 node labels based on phrase clustering of paper titles.
 
@@
 
-\ni (2) We adopted the LFR-benchmark graph model~\cite{AndreaSF08} to generate synthetic graphs (\synthetic) with community structure as existed in real-life networks.
+\ni (2) We generated synthetic data graphs (\synthetic) with community structures as existed in real-life networks, by adopting the LFR-benchmark graph model~\cite{AndreaSF08}.
 It is controlled by three parameters: the number $n$ of nodes, the average degree $d$ of nodes, and the number $l$ of node labels.
@@
 We implemented a generator to produce pattern graphs, controlled by 4 parameters:
-the number of nodes $|V_P|$, the number of edges $|E_P|$, label $l_{P}$ for each node from
+the number of nodes $|V_P|$, the number of edges $|E_P|$, the label $l_{P}$ for each node from
 an alphabet of labels in the corresponding data graphs,
-and capacity bound $f_{P}$ for each node.
+and the capacity bound $f_{P}$ for each node.
 
@@
 (3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
-(a) \mindia is to minimize the team diameter~\cite{Lappas09}; 
-%firstly proposed the team formation problem;
+(a) \mindia is to minimize the team diameter~\cite{Lappas09}, and is firstly proposed for the team formation problem;
 (b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
-(c) \denalk is to maximize the team density~\cite{GajewarS12}. 
-%which has the same goal with our algorithms; and
-Among algorithms for \teamF, \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
+(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
+Among algorithms for \teamF, most of them including  \mindia and \denalk only compute the best team,
+while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
 Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.
@@
 When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
-All the findings on \youtube are reported in the Appendix.
+Aqll the findings on \youtube are reported in the Appendix.
 

### 2017-09-30 Gruba/01-intro.tex
v2.1
v2.1

@@
-\section{\textcolor{red}{Introduction}}
+\section{Introduction}
 \label{sec:intro}
 
-\begin{comment}
-\textbf{Motivation}
+Social media is overwhelming nowadays, with massive users on Facebook \refe{}, Twitter \refe{} and Weibo \refe{} while the number of users keeps increasing.
+These users behave variously, knowledge of which is significant in recommendation system, activity prediction and Big Thing analysis.
+Hence emerges the demand of developing systems and algorithms that could properly model user behaviors, which has attracted the attention from both academia and industry.
 
-\textbf{Example}
+Central to user behavior modeling, is the need to choose the unit of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating these units.
+Already, there exist work of building a single model for all the users \refe{}.
+Apparently, such model bears the limitation of being coarse.
+On the other hand, modeling each user is not practical, due to the tremendous number of users.
 
-\textbf{Challenge}
+The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
+Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well. 
+As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
 
-\textbf{Contribution}
-
-\textcolor{blue}{organization of the sections}
-
-%This section shall look into the principle of each component in Processing Runtime subsystem, putting forth a full-fledged system.
-
-\end{comment}
-
-%zhu begin
-
-The rapid development of social network is accompanied by the generation of tremendous user-generated contents.
-People not only consume information but also publish or share messages.
-An interesting function in many existing Social Network Applications is reposting (e.g, reposting someone else's microblog on weibo.com).
-Modeling reposting behavior is of vital significance for Social Network Applications, which can help them to mine potential benefits, predict bursting events and so on.
-\par
-
-Modeling reposting behavior has attracted attention from both academia and industry.
-However, many existing works have certain limitations.
-First, most of them mainly studied how to model reposting behavior for a single user or for the whole users.
-Considering the huge amount of users in Social Network , modeling for a single user is not easy.
-What's more, it can also make our model too particular.
-Modeling for the whole users is also not a good idea, which may get a inaccuracy model.
-Secondly, how to extract users's features, especially the extraction of users's interest, is a challenging problem.\par
-To this end, we extract each user's features firstly, including user's basic information, behavior information and interests, then perform users clustering to divide users into groups and model reposting behavior of each user group respectively.
-The main contributions of this work can be summarized as follows:\par
+The contributions of this work include:
 \begin{itemize}
-\item   We construct a large collection of microblogs from a real microblog service. It contains users's information, microblog content and part of the social network information of related users.
-\item   Instead of modeling for a single user or the whole users, we divide all users into several groups by users clustering and model for each group.
-\item	We propose a noval method to extract user interests from user generated texts.
-\item	We develop a demo system for visualization of single user's profiling and each group's information.
+\item We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model in literature.
+\item We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/recent interests and explicit/implicit interests.
+\item We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.
 \end{itemize}
 
-This article is organized as follows: In Section 2, we introduce the framework of our work.
-We then describe our methodology in section 3, including features extraction, how we cluster users into groups, and how to model reposting behavior.
-Section 4 presents and discusses the experimental results.
-Section 5 discusses related work followed by conclusions in Section 6.\par
+The rest of this paper is organized as follows.
+Section \ref{sec:overv} first gives the problem formulation and subsequently overviews \sys{}'s components, principle of which are detailed in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
+Section \ref{sec:perf} provides the performance evaluation.
+Related work is presented in Section \ref{sec:rela}.
+Finally, Section \ref{sec:conclu} concludes the work.

### 2017-09-30 Gruba/02-overview.tex
v2.1
v2.1

\section{\sys{} Overview}
\label{sec:overv}

%This section shall look into the principle of each component in Processing Runtime subsystem, putting forth a full-fledged system.

\subsection{Problem Formulation}
% {user, blog, user-blog} => model
% query (a user u, a blog b that is created or forwarded by u's friend)
% returns: Y/N u shall forward b

We consider people's \retg{} behavior in social media.
For simplicity, with a given user, we assume that blogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
All our results could straightforwardly generalize to alternative candidate scopes.
%e.g., the like/unlike behavior against the candidate of remarking [double check the network language; register a Facebook]
%e.g., positive comments in the overall comments

\begin{definition}
\label{def:blog}
A blog $B = (O, T, M, R)$ consists of the owner $O$ (a.k.a. user in this paper) to whom $B$ belongs (either created or \retd{}), the timestamp $T$ showing when $B$ is generated, the blog message $M$ and a bit $R$ denoting $B$ is \retd{} (1) or originally created (0) by the owner $O$.
\end{definition}

\begin{comment}
\begin{definition}
A blog $B = (O, T, M, C)$ consists of the owner $O$ to whom $B$ belongs (either created or \retd{}), the timestamp $T$ showing when $B$ is generated, the blog message $M$ and a set of counters $C_s(B) = \{\#comment,\ \#like,\ \#\ret{}\}$ regarding the number of being commented, liked, and \retd{}.
\end{definition}
\end{comment}

\begin{definition}
\label{def:user}
A user $U = (B_s, R_s, E_s)$ consists of three sets regarding the user's blogs $B_s$, followers $R_s$ and followees $E_s$ separately.
Each follower/followee per se refers to a user.
\end{definition}

The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.

Informally, providing a set of users $\{U\}$ and the associated blogs $\{B\}$, as well as a blog query $b$ and a follower of $O(b)$ written as $f$, i.e., $f \in R_s(O(b))$, \sys{} shall build a \retg{} model for $(\{U\},\ \{B\})$, upon which Y/N is returned regarding whether $f$ shall \ret{} $b$.

\subsection{\sys{} Framework}
\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}, comprising three subsystems: Data Storage, Processing Runtime and Profile Demonstrator.

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{figures/architecture}
\caption{\sys{} Architecture}
\label{fig:framework}
\end{figure}

% #like and #comment are saved; could generalize \sys{} to model the liking behavior (among commented blogs)
\begin{comment}
\begin{figure}[!htb]
\centering
\includegraphics[width=.99\linewidth]{figures/microblog}
\caption{Blog Data in \sys{}}
\label{fig:blog}
\end{figure}
\end{comment}

\begin{comment}
\begin{figure}[!htb]
\centering
\includegraphics[width=.99\linewidth]{figures/user}
\caption{User Data in \sys{}}
\label{fig:user}
\end{figure}
\end{comment}

\textbf{Data Storage.} The underlying Data Storage subsystem stores data to be processed by \sys{}, i.e., data of blogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

\textbf{Processing Runtime.}
In the heart of \sys{} lies the Processing Runtime subsystem, which consists of three major components as follows.
\begin{enumerate}
	\item Feature Extractor: By coalescing the blog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored data by Feature Extractor and serve as the input of User Clusterer.
	\item User Clusterer: Providing the user-based features, User Clusterer takes charge of the clustering task such that each user falls into a proper group. 
	\item Group Modeler: For each group obtained by User Clusterer, Group Modeler employs both positive and negative samples to train a model, over which the testing of users' \retg{} behavior is performed.
\end{enumerate}

\textbf{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator subsystem for visualization. 
For the time being, Profile Demonstrator presents \tbc{}.

### 2017-09-30 Gruba/06-perf.tex
v2.1
v2.1

@@
 \label{sec:perf}
-
-%zhu begin
-
-In this section, we validated the effectiveness of our methods, including features extraction, users clustering and reposting behavior modeling.
-
-\subsubsection{Experimental Setup}
-
-The data we used in this study was crawled from Sina Microblog, which allows users to follow with each other.
-When user A follows B, A is called the follower of B and B is called the friend of A.
-User B's behaviors such as posting and reposting will be visible to A.
-User A can choose microblogs to repost which was posted (or reposted) by user B.
-Our data set was crawled by the following ways.
-Firstly, we selected 43500 users randomly from the public Microblog stream.
-We crawled the basic information of these users, including gender, province, number of microblogs, city, number of followers, number of friends, signature, nickname, etc.
-In addition, we also crawled all the microblogs the user posted or reposted.
-The microblog information including the number of it has been reposted, the number of it has been commented, the number of it has been liked, type of the microblog (be posted or reposted by the user), the location where the microblog was posted, the content of the microblog, the device the microblog was posted by, the time when the microblog was posted and so on.
-In addition, we can get part of one user's friends from the microblogs that user reposted.
-So we also collected some users's friends's information and microblogs.
-Table \ref{tab:Data_statistics} lists the statistics information of the data set.
-Another dataset we used here was 1000 labeled microblogs selected from the microblogs we crawled.
-We labeled each microblog with categories in the cell lexicon.\par
-
-\begin{table}[!h]
-\centering
-    \caption{statistics information of Dataset }     % NOTE!  caption goes _before_ the table contents !!
-    \label{tab:Data_statistics}
-    \begin{small}
-    \begin{tabular}{|l|l|l|l|l|}
-    \hline
-    \cline{2-5}
-    {\bfseries DataSet} & {\bfseries  \#Users}         & {\bfseries \#Microblogs}     & {\bfseries \#Posts}    & {\bfseries \#Reposts}     \\
-    \hline
-    WeiBo         & 410000 & 157943530		& 77234797 & 80708733	\\
-    \hline
-    \end{tabular}
-    \end{small}
-\end{table}
-
-\paragraph{Features Extraction}
-One user's basic and behavioral information can be obtained either from the data set straightly or from the statistics information of user's microblogs.
-As for user's interests, we proposed a novel method to do interest extraction.
-Here we compared our method using different parameters with method that just using TF-IDF or Twitter-LDA.
-To evaluate the performance of the method, we labeled 1000 microblogs with categories of the cell lexicon.
-One microblog may belong to one or several categories.
-Considering it's a multi-label problem, our evaluation metrics here are accuracy, precision and recall as described in \cite{IEEEexample:journals/tkde/ZhangZ14}.
-Let $S = {(x_i,Y_i)| 1 \le i \le p)}$ be the test set and $m(\cdot)$ be the mapping method.
-The accuracy, precision and recall are defined as equation \eqref{accuracy_m}, \eqref{precision_m} and \eqref{recall_m}.\par
-
-\begin{equation}\label{accuracy_m}
-accuracy_m = \frac{1}{p} \sum_{i=1}^{p} \frac{\mid Y_i \cap m(x_i) \mid}{\mid Y_i \cup m(x_i) \mid}
-\end{equation}
-
-\begin{equation}\label{precision_m}
-precision_m = \frac{1}{p} \sum_{i=1}^{p} \frac{\mid Y_i \cap m(x_i) \mid}{\mid m(x_i) \mid}
-\end{equation}
-
-\begin{equation}\label{recall_m}
-recall_m = \frac{1}{p} \sum_{i=1}^{p} \frac{\mid Y_i \cap m(x_i) \mid}{\mid Y_i \mid}
-\end{equation}
-
-\paragraph{Users Clustering}
-We used the data generated by features extraction to perform users clustering.
-Each sample contains user's basic features, behavioral features and interests features.
-Silhouette coefficient \cite{IEEEexample:books/mk/HanKP2011} was used as our evaluation metric here.
-For each sample $i$, let $a(i)$ be the average dissimilarity of $i$ with all other data within the same cluster.
-Let $b(i)$ be the lowest average dissimilarity of $i$ to any other cluster, of which $i$ is not a member.
-We now get the silhouette of sample $i$ as equation \eqref{silhouetteOfi}.
-Then silhouette coefficient of the result with N samples can be got as equation \eqref{silhouette}.\par
-
-\begin{equation}\label{silhouetteOfi}
-s(i) = \frac{b(i)-a(i)}{max\{b(i),a(i)\}}
-\end{equation}
-
-\begin{equation}\label{silhouette}
-silhouette = \frac{1}{N} \sum_{i=1}^{N} s(i)
-\end{equation}
-
-\paragraph{Reposting Behavior Modeling}
-For analyzing reposting behavior, we firstly divided users into groups by users clustering.
-For each group, we randomly selected microblogs reposted by users of the group as positive samples, and selected microblogs ,which were reposted by a friend of one user in the group but not reposted by this user, as negative samples.
-Then we generated final samples with features described in subsection \ref{subsec:RepostingBehaviorPrediction}.
-We have carefully chosen algorithm to compare with our method.
-Here we compared our method with \cite{IEEEexample:conf/ijcai/ZhangLTCL13}, which studied a state-of-art idea of social influence locality for modeling users¡¯ reposting behaviors in the microblog network.
-We use accuracy, recall and f-measure as our evaluation metrics.\par
-
-All experiments were conducted on a machine with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of Memory, running 64 bit Windows 7 professional system.
-Each experiment was repeated 5 times, and the average is reported here.
-In all the experiments, we fixed parameters to their default values.
-The parameters with their descriptions and default values are presented in Table \ref{tab:Parameters}.
-\par
-
-\begin{table}[!h]
-\centering
-    \caption{Parameters used in the experiments with their descriptions.  }
-    % NOTE!  caption goes _before_ the table contents !!
-    \label{tab:Parameters}
-    \begin{small}
-    \begin{tabular}{|c|l|c|}
-    \hline
-    {\bfseries Parameters} & {\bfseries  Descriptions}                       & {\bfseries Default}     \\
-    \hline
-                       & threshold for selecting                             & \\
-    $\epsilon$         & the categories when considering                     & 3\\
-                       & the number of overlapped words.                     & \\
-    \hline
-                       & weight for mapping value                            & \\	
-    $\alpha$           & by performing Procedure 1                           & 0.7\\
-    \hline
-                       & threshold number for                                & \\
-    $k$                & selecting categories when                           & 3\\
-                       & performing mapping algorithm.                       &	\\
-    \hline
-    $k_1$              & min number of clusters                              & 2	\\
-    \hline
-    $k_2$              & max number of clusters                              & 10	\\
-    \hline
-    \end{tabular}
-    \end{small}
-\end{table}
-
-\subsubsection{Performance and Analysis}
-
-\paragraph{Features Extraction}
-
-To accurately extract user's interests feature, we proposed a novel method that combined the method of Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF to tag the microblog with 512 categories.
-We performed an experiment to compare three methods which only using Twitter-LDA, only using TF-IDF, and combining the two with different value of $\alpha$.
-Fig \ref{fig:Interests} shows the results of the experiment.
-From the results, we can see that when combining the two, we got a better performance.
-We also developed a demo system for visualization of users's features, fig.
-\ref{fig:userFeatures} shows one case of a user.
-
-\begin{comment}
-\begin{figure}[h]
-	\centerline{\psfig{figure=IMAGE/features/Interests.eps,height=50.54mm,width=82mm}}
-	\caption{Visualization for User Features.}
-	\label{fig:Interests}
-\end{figure}
-\end{comment}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=.96\linewidth]{IMAGE/features/Interests}
-\caption{Visualization for User Features.}
-\label{fig:Interests}
-\end{figure}
-
-\begin{comment}
-\begin{figure}[h]
-	\centerline{\psfig{figure=IMAGE/features/userfeatures.eps,height=120.54mm,width=92mm} }
-	\caption{Visualization for User Features.}
-	\label{fig:userFeatures}
-\end{figure}
-\end{comment}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=.96\linewidth]{IMAGE/features/userfeatures}
-\caption{Visualization for User Features.}
-\label{fig:userFeatures}
-\end{figure}
-
-\paragraph{User Clustering}
-
-We performed users clustering on the 43500 users we selected through the method described in subsection \ref{subsec:UserClustering}.
-In addition, we reconstructed five datasets which were randomly selected from the 43500 users and each dataset had 10000 users.
-The results are list in Fig.
-\ref{fig:sample_clustering}.
-From the results, we can draw the following observations:
-(1) On the whole dataset with 43500 users, the clustering method got its largest coefficient when the number of clusters was four.
-(2) On the five datasets with 10000 users, the clustering method got its largest coefficient on four datasets when the number of clusters is four and one dataset when the number of clusters is three.
-Based on the observations, we thought it a reasonable result dividing 43500 users into four groups.\par
-
-We carefully analyzed the four groups we obtained through users clustering.
-(1)Most of users of the group one are male, and they are mainly distributed in Beijing.
-What's more, most of these users have similar amount of friends and followers.
-The most active time of this group are mainly distributed between 10 am and 12 am.
-(2)The users of group two are mostly female, they are also mainly distributed in Beijing.
-Most of users also have similar amount of friends and followers as group one.
-The most active time of this group are mainly distributed between 22 pm and 24 pm.
-(3)The users of group three are mostly male, and they are distributed in a wide range of provinces.
-Most of users have the number of followers far more than friends.
-Users of this group are active both in 10-12 am and 22-24 pm.
-(4)Most of users of group four are female, and they are distributed in a wide range of provinces as group three.
-Most of these users have the number of followers far more than friends.
-And the most active time of this group are mainly distributed between 22 pm and 24 pm.
-We also found that the distribution of the number of users's microblogs of each group is similar.
-We visualized the users's interests using words cloud, the difference between groups is obvious, excepting that group one and group three have similar interests.
-
-\begin{comment}
-\begin{figure}[h]
-	\centerline{\psfig{figure=IMAGE/clustering/Clustering.eps,width=80.7mm} }
-	\caption{The Results of Users Clustering Performed on Six Datasets}
-	\label{fig:sample_clustering}
-\end{figure}
-\end{comment}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=.96\linewidth]{IMAGE/clustering/Clustering}
-\caption{The Results of Users Clustering Performed on Six Datasets}
-\label{fig:sample_clustering}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/11.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/12.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/13.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/14.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/15.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/16.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/17.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/18.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/19.eps}}
-  \caption{The Statistics of User Group One}
-  \label{fig:subfig} %% label for entire figure
-\end{figure}
-\begin{figure}
-  \centering
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/21.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/22.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/23.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/24.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/25.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/26.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/27.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/28.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/29.eps}}
-  \caption{The Statistics of User Group Two}
-  \label{fig:subfig} %% label for entire figure
-\end{figure}
-\begin{figure}
-  \centering
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/31.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/32.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/33.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/34.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/35.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/36.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/37.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/38.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/39.eps}}
-  \caption{The Statistics of User Group Three}
-  \label{fig:subfig} %% label for entire figure
-\end{figure}
-\begin{figure}
-  \centering
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/41.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/42.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/43.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/44.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/45.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/46.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/47.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/48.eps}}
-  \subfigure{
-      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/49.eps}}
-  \caption{The Statistics of User Group Four}
-  \label{fig:subfig} %% label for entire figure
-\end{figure}
-
-\paragraph{Reposting Behavior Modeling}
-By performing users clustering, we got four user groups.
-We generated instances by the method as described in subsection \ref{subsec:RepostingBehaviorPrediction}.
-However, we observed that positive instances (reposting) and negative instances (un-reposting) are much unbalanced.
-Thus we randomly select a subset of negative instances with the equal number of positive number for experiments.
-We compared our method with \cite{IEEEexample:conf/ijcai/ZhangLTCL13}, the results are list in figure \ref{fig:comparisons}, here we call our method as reposting model for group(RMG).
-The result suggests that our method had a better performance than LRC-BQ in most cases.\par
-
- \begin{figure}
-  \centering
-  \subfigure[Precision Of RMG	and LRC-BQ]{
-    \label{fig:subfig:a} %% label for first subfigure
-    \includegraphics[width=0.4\textwidth]{IMAGE/model/precision.eps}}
-  \hspace{1in}
-  \subfigure[Recall Of RMG and LRC-BQ]{
-    \label{fig:subfig:b} %% label for second subfigure
-    \includegraphics[width=0.4\textwidth]{IMAGE/model/recall.eps}}
-  \hspace{1in}
-  \subfigure[F-Measure Of RMG and LRC-BQ]{
-    \label{fig:subfig:c} %% label for second subfigure
-    \includegraphics[width=0.4\textwidth]{IMAGE/model/F-Measure.eps}}
-  \caption{Comparison Of RMG and LRC-BQ}
-  \label{fig:comparisons} %% label for entire figure
-\end{figure}
-
-We further try different features and their combinations for modeling reposting behaviors, they are user-based information(UI), microblog-based information(MI), interaction information(II) and their combinations.
-The results are list in in figure \ref{fig:performances}.
-The result suggests that the MI and UI perform similarly for modeling group one and group three, MI performs better than UI and II on group four.
-Combining all the three types of features can get similar performance with the combination of UI and MI on group two and group three, and the two combinations perform better than all other combinations.
-As for group one and group four, using UI and MI can get the best performance, which indicates that there in deed exists strong correlation between the reposting behavior and the two types information.
-
- \begin{figure}
-  \centering
-  \subfigure[Precision of RMG Using Different Features]{
-    \label{fig:subfig:a} %% label for first subfigure
-    \includegraphics[width=0.4\textwidth]{IMAGE/model/precisionofdifferentfeatures.eps}}
-  \hspace{1in}
-  \subfigure[Recall of RMG Using Different Features]{
-    \label{fig:subfig:b} %% label for second subfigure
-    \includegraphics[width=0.4\textwidth]{IMAGE/model/recallofdifferentfeatures.eps}}
-  \hspace{1in}
-  \subfigure[F-Measure of RMG Using Different Features]{
-    \label{fig:subfig:c} %% label for second subfigure
-    \includegraphics[width=0.4\textwidth]{IMAGE/model/fmeasureofdifferentfeatures.eps}}
-  \caption{Performance Of RMG Using Different Features}
-  \label{fig:performances} %% label for entire figure
-\end{figure}
-
-\paragraph{Time Report}

### 2017-09-30 Gruba/07-rela.tex
v2.1
v2.1

@@
 \label{sec:rela}
-
-%zhu begin
-The rapid development of social network is accompanied by the generation of tremendous user-generated contents.
-Message forwarding (e.g., reposting on weibo.com) is one of the most popular functions in many existing social networks.
-Behavior modeling of social media users has received great attention in recent years, and has become a research hot spot of academies and industries.
-In this section, we will introduce the related work of user modeling in social network from the aspects of user features analysis, user groups mining and user behaviors modeling.\par
-
-Social media users's features we mentioned here include users's basic information, behavior features and interests features.
-Users's basic information include the users's gender, age, region, occupation and other personal information.
-There are many researches for analyzing users's basic information, such as users's racial information analysis \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, users's gender inference \cite{IEEEexample:conf/emnlp/CiotSR13}, users's actual age inference \cite{IEEEexample:conf/icde/ParkHHL09}, user political tendency analysis (e.g.
-\cite{IEEEexample:conf/icwsm/PennacchiottiP11}, \cite{IEEEexample:conf/acl/VolkovaCD14}), user policy orientation analysis\cite{IEEEexample:kosinski2013private}, user's geo-location and occupation mining\cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}, etc.
-Most of these methods analyze the unknown attributes by using classification or regression model.\par
-
-Social medias users's behaviors mainly refers to the reposting, posting and commenting behaviors.
-Users's behaviors also have certain characteristics and regularity.
-As mentioned in \cite{IEEEexample:jiang2013understanding}, it found that the behavior of a user exhibits the power-law distribution at the time interval, and the power-law distribution is related to users's schedule.
-Guo Z et al.\cite{IEEEexample:conf/music/GuoLTL12} analyzed the behavior of microblog users, the difference between the activity of users in different periods, and obtained the distribution of individual behavior on time.\par
-Users's behaviors are largely driven by user interests, so it's of vital importance to model users's interests.
-Zhiyuan et al.\cite{IEEEexample:journals/fcsc/LiuCS12} modeled users's interests through mining keywords.
-They extracted keywords from the users's microblogs by the combination of words frequency and translation model.
-Xu Z et al.\cite{IEEEexample:conf/webi/XuLXY11} proposed a method which extended user topic model to analyze users's interests.
-Michelson M et al.\cite{IEEEexample:conf/and/MichelsonM10} analyzed interests  based on a knowledge base.
-They used a knowledge base to identify and classify the entities in twitters of one user, then generate the user's interests category subtree to express his interests.
-Lim K H et al.\cite{IEEEexample:conf/wikis/LimD13} analyzed the celebrities a user mentioned, then they got the preference degree of the user in different interests categories.
-Bhattacharya P et al.\cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} proposed a method to extract a user's interests by analyzing the experts he followed.
-By digging a list of certain topics of the custom experts the user follows, they got the user's interests profiling.
-Wei Feng et al.\cite{IEEEexample:conf/icde/FengW14} studied the methods mapping tweets to hashtags to get users's preferences for hashtags.\par
-
-Considering the fact that the amount of users in Social Medias is so huge, modeling for each user is not a good idea.
-In addition, modeling for a single user may make the model too particular.
-There are also some studies on the user groups analysis.
-Some researches studied how to classify users under a specific situation.
-For instance, Marco Pennacchiotti et al.\cite{IEEEexample:conf/icwsm/PennacchiottiP11} classified users by race, political tendencies and so on.
-In addition, research for user community mining is a hot spot.
-Jaewon Yang et al.\cite{IEEEexample:conf/wsdm/YangL13} proposed a method based on non-negative matrix decomposition to mine user community.
-Yiye Ruan et al.\cite{IEEEexample:conf/www/RuanFP13} considered user's friends and user's text content into their method when measuring the similarity between users for clustering.
-He et al.
-\cite{IEEEexample:he2014overlapping}
-only considered the relationship between friends, and used the edge aggregation coefficient as a measure of clustering.
-Hiroaki Shiokawa et al.\cite{IEEEexample:conf/aaai/ShiokawaFO13} used the modular degree as a clustering standard and proposed an incremental algorithm to mine user community.\par
-
-As for behavior prediction, Jing Zhang et al.\cite{IEEEexample:journals/tkdd/ZhangTLLX15} proposed a method of analyzing users's reposting behavior from the perspective of influence.
-Some researchers (e.g.
-\cite{IEEEexample:conf/wsdm/FengW13}, \cite{IEEEexample:conf/ijcai/ZhangLTCL13}) find that the user's reposting behavior is largely influenced by the relationship between friends, so they consider user's friend structure information into their models.
-Bo Jiang et al.
-\cite{IEEEexample:conf/cikm/JiangLSW15} proposed a method that combined matrix decomposition and microblogs clustering to analyze the user's reposting behavior.
-Zhang et al.\cite{IEEEexample:zhang2015retweet} proposed non-parametric statistical models to combine structural, textual, and temporal information together to predict reposting behavior.
-Considering the situation that users's not reposting does not mean that users are not interested in it, the users may just did not see it, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} applied a collaborative filtering method to the reposting behavior analysis.

### 2017-09-30 Gruba/08-conclu.tex
v2.1
v2.1

@@
 \label{sec:conclu}
-
-%zhu begin
-
-In this paper, we studied to model reposting behavior of group users in microblog.
-We first extracted users's features including basic features, behavior features and interests features.
-Meanwhile, we proposed a novel method to extract user interests from the user generated texts.
-By performing users clustering, we divided users into several groups and modeled reposting behavior of each group users respectively.
-The final experiment shows that our model have strong predictive power.
-What's more, we developed a demo system to display the profiling for users and groups.
-As future work, it is interesting to study other methods to improve the accuracy of interests extraction.

### 2017-09-30 TF-vldb2018/subsec-auxstr.tex

@@
 
-\vspace{0.5ex}
-(I) Data structures in the first class are as follows.
+\stab(I) Data structures in the first class are as follows.
 
@@
 \vspace{0.4ex}
-\etitle{(4) Fragment-ball-match index (\fb)} links \fs and \bs together, to form the {\em fragment-ball-match index}. Then \fb is linked to $\tilde{M}(P,G)$. \revise{The details are shown below.}
+\etitle{(4) Fragment-ball-match index (\fb)} links \fs and \bs together, to form the {\em fragment-ball-match index}. Then \fb is linked to $\tilde{M}(P,G)$. The details are shown below.
 
@@
 auxiliary structures $\tilde{M}(P,G)$ and \fb\,that are shown in Fig.~\ref{fig-auxiliary-structures}(a).
-$P_1$ is divided into fragments $P_{f1}$ and $P_{f2}$ by algorithm \kw{PFrag},
+
+\ni (1) Pattern $P_1$ is divided into fragments $P_{f1}$ and $P_{f2}$ by algorithm \kw{PFrag},
 so there are $2^2=4$ type codes in \fs.
-For balls linked with $tc$ $(1, 1)$, \eg ball $\ball{[\kw{PM_1},2]}$,
+
+\ni (2) For balls linked with $tc$ $(1, 1)$, \eg ball $\ball{[\kw{PM_1},2]}$,
 there are matches to both $P_{f1}$ and $P_{f2}$ in the ball.
@@
 linked with $tc$ $(1, 0)$, $(0, 1)$ and $(0, 0)$ respectively. 
-We only consider these 4 balls in the sequel.
+%
+For simplicity, we consider these 4 balls only in the sequel.
 \end{example}
@@
 
-\vspace{0.5ex}
-(II) Data structures in the second class are as follows.
+These structures enforce a nice property as follows.
+
+\begin{theorem}
+\label{thm-framework-inc}
+With $\tilde{M}(P,G)$ and \fb \wrt an $h$-fragmentation of $P$, given $\Delta P$ and $\Delta G$,
+the incremental algorithm \inc processes $\Delta P$ and $\Delta G$ in time
+determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
+\end{theorem}
+
+We shall prove Theorem~\ref{thm-framework-inc} by providing specific techniques for \inc and analyzing its time complexity.
+
+\stab(II) Data structures in the second class are as follows.
 
@@
 Stack $T(P_{fi})$ $(i\in [1,h])$ (resp. $T(C)$) records all unit updates in all arrived pattern updates $\Delta P_1$, $\ldots$, $\Delta P_{N}$ that are applied to fragment $P_{fi}$ (resp. $C$) of $P$.
-Initially, all of them are empty.
-They are dynamically updated for each unit update in each set of coming pattern updates.
-
-Better still, it holds a nice property as follows.
-\begin{theorem}
-\label{thm-framework-inc}
-With $\tilde{M}(P,G)$ and \fb \wrt an $h$-fragmentation of $P$, given $\Delta P$ and $\Delta G$,
-the incremental algorithm \inc processes $\Delta P$ and $\Delta G$ in time
-determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
-\end{theorem}
-
-We shall prove Theorem~\ref{thm-framework-inc} by providing specific techniques for \inc and analyzing its time complexity in Section~\ref{sec-IncAlg}.
+Initially, all of them are empty, and are dynamically updated for each unit update in each coming set of  pattern updates.
 

### 2017-09-30 TF-vldb2018/sec-expt.tex

@@
 
-\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The description of the dataset can be found in the full version~\cite{fullvldb18}.
+\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The detailed information of the dataset is available in the full version~\cite{fullvldb18}.
 
@@
 (3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
-(a) \mindia is to minimize the team diameter~\cite{Lappas09}, and is firstly proposed for the team formation problem;
+(a) \mindia is to minimize the team diameter~\cite{Lappas09},
+\revise{and is firstly proposed for the team formation problem;}
 (b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
 (c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
-Among algorithms for \teamF, most of them including  \mindia and \denalk only compute the best team,
+Among algorithms for \teamF, \revise{most of them including  \mindia and \denalk only compute the best team,}
 while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
@@
 When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
-Aqll the findings on \youtube are reported in the Appendix.
+All the findings on \youtube are reported in the full version~\cite{fullvldb18}.
 
-\stitle{Exp-1: Efficiency of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis and \denalk.
+\stitle{Exp-1: Efficiency of \optgrouprec}. We firstly evaluated the efficiency of \optgrouprec vs. \mindia, \minsumdis and \denalk.
+We generated pattern graphs for \optgrouprec, and the corresponding queries (labels requirements) for \mindia, \minsumdis and \denalk.
 
 Algorithms \mindia, \minsumdis and \denalk do not scale well on large graphs.
-Indeed,  (1) \mindia and \minsumdis take more than $8$ hours to finish their preprocessing, \ie computing all-pair-shortest-paths, and (2) \denalk takes more than 24 hours even when $k=1$ on \citationd.
-By contrast, \optgrouprec takes around 100 seconds on \citationd by default settings.
+Indeed,  (1) \mindia and \minsumdis took more than $8$ hours to finish their preprocessing, \ie computing all-pair-shortest-paths; 
+and (2) \denalk took more than 24 hours even when $k=1$ on \citationd.
+By contrast, \optgrouprec took around 100 seconds on \citationd by default settings.
 Hence, we report the effectiveness of these algorithms on a sampled data graph with $10,000$ nodes on \citationd only.
 %We further evaluate the efficiency of \optgrouprec in the incremental experiments.
-%\looseness=-1
 
-\stitle{Exp-2: Effectiveness of \optgrouprec}.
-We generated pattern graphs for \optgrouprec, and the corresponding queries (labels requirements) for \mindia, \minsumdis and \denalk, and checked the quality of matches returned by them.
-\looseness=-1
+\stitle{Exp-2: Effectiveness of \optgrouprec}. We then evaluated the efficiency of \optgrouprec vs. \mindia, \minsumdis and \denalk by checking the quality of matches returned by them.
 
@@
 
-Note that (a) and (b) are two traditional quality measures utilized by existing team formation algorithms.
+Note that (a) and (b) are two traditional quality measures utilized by existing team formation algorithms~\cite{GajewarS12,realTeamForm13,Lappas09,Kargar11}.
 Intuitively, $\eta_V(G_S, P)$ (resp. $\eta_E(G_S,P)$) measures how well $G_S$ meets the node capacity requirements (resp. structural constraints) in $P$, and their values fall in $[0, 1]$.
@@
 \etitle{(i) Impacts of $|V_{P}|$}. Varying the number $|V_{P}|$ of
-nodes in $P$ from 4 to 16, we took the average value of top-$k$ teams found by  \optgrouprec, \mindia, \minsumdis and \denalk \wrt five quality measures.
+nodes in $P$ from 4 to 16, we took the average value of top-$k$ teams found by  \optgrouprec, \mindia, \minsumdis and \denalk \wrt four quality measures.
 The results are reported in Figures \ref{fig-exp-semantic-citation-diameter}-\ref{fig-exp-semantic-citation-link}.
@@
 Observe the following.
-%
-(1) In Fig.~\ref{fig-exp-semantic-citation-diameter}, the diameter of teams found by \optgrouprec is less than \mindia and \minsumdis, but the teams are with a small diameter, \eg less than \denalk, because of the ball restriction of \optgrouprec;
-(2) in Fig.~\ref{fig-exp-semantic-citation-density}, the density of teams found by \optgrouprec is less than \denalk, while is higher than \mindia and \minsumdis;
-(3) in Fig.~\ref{fig-exp-semantic-citation-capacity}, the node satisfiability of teams found by \optgrouprec, \ie 1.0 in all cases, is much higher than \mindia, \minsumdis and \denalk, \ie less than 0.2; and
-(4) in Fig.~\ref{fig-exp-semantic-citation-link}, the teams found by \optgrouprec come with a higher edge satisfiability , \ie 1.0 in all cases, compared to less than 0.6 by \mindia, \minsumdis and \denalk.
+(1) The diameters of teams found by \optgrouprec are comparable to those of \mindia and \minsumdis, which are in particularly designed to minimize the diameters, as shown in Fig.~\ref{fig-exp-semantic-citation-diameter}.
+This is ensured by the use of balls in \optgrouprec.
+(2) The densities of teams found by \optgrouprec, though are smaller than \denalk which is specialized for maximizing team densities, are larger than \mindia and \minsumdis, as shown Fig.~\ref{fig-exp-semantic-citation-density}.
+(3) The node satisfiability of teams found by \optgrouprec is much higher than \mindia, \minsumdis and \denalk, \eg 1.0 vs.
+no larger than 0.2 in all cases as in Fig.~\ref{fig-exp-semantic-citation-capacity}.
+(4) The teams found by \optgrouprec come with a higher edge satisfiability , \ie 1.0 in all cases, compared to smaller than 0.6 by \mindia, \minsumdis and \denalk, as shown in Fig.~\ref{fig-exp-semantic-citation-link}.
+
+%%
+%\revise{(1) In Fig.~\ref{fig-exp-semantic-citation-diameter}, the diameter of teams found by \optgrouprec is less than \mindia and \minsumdis, but the teams are with a small diameter, \eg less than \denalk, because of the ball restriction of \optgrouprec;}
+%(2) in Fig.~\ref{fig-exp-semantic-citation-density}, the density of teams found by \optgrouprec is less than \denalk, while is higher than \mindia and \minsumdis;
+%(3) in Fig.~\ref{fig-exp-semantic-citation-capacity}, the node satisfiability of teams found by \optgrouprec, \ie 1.0 in all cases, is much higher than \mindia, \minsumdis and \denalk, \ie less than 0.2; and
+%(4) in Fig.~\ref{fig-exp-semantic-citation-link}, the teams found by \optgrouprec come with a higher edge satisfiability , \ie 1.0 in all cases, compared to less than 0.6 by \mindia, \minsumdis and \denalk.
 
@@
 
-\warn{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and capacity satisfiability, and pertains a good team collaboration compatibility \wrt density and diameter.}
+\revise{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and capacity satisfiability, and pertains a good team collaboration compatibility \wrt density and diameter.}
 

### 2017-09-30 TF-vldb2018/sec-expt.tex

@@
 (a) \mindia is to minimize the team diameter~\cite{Lappas09},
-\revise{and is firstly proposed for the team formation problem;}
+\revise{which is firstly proposed for the team formation problem;}
 (b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
 (c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
-Among algorithms for \teamF, \revise{most of them including  \mindia and \denalk only compute the best team,}
+\revise{Most of the algorithms for \teamF, including  \mindia and \denalk, only compute the best team,}
 while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
@@
 This is ensured by the use of balls in \optgrouprec.
-(2) The densities of teams found by \optgrouprec, though are smaller than \denalk which is specialized for maximizing team densities, are larger than \mindia and \minsumdis, as shown Fig.~\ref{fig-exp-semantic-citation-density}.
+(2) The densities of teams found by \optgrouprec, though are smaller than \denalk which is specialized for maximizing team densities, are larger than \mindia and \minsumdis, as in Fig.~\ref{fig-exp-semantic-citation-density}.
 (3) The node satisfiability of teams found by \optgrouprec is much higher than \mindia, \minsumdis and \denalk, \eg 1.0 vs.
 no larger than 0.2 in all cases as in Fig.~\ref{fig-exp-semantic-citation-capacity}.
-(4) The teams found by \optgrouprec come with a higher edge satisfiability , \ie 1.0 in all cases, compared to smaller than 0.6 by \mindia, \minsumdis and \denalk, as shown in Fig.~\ref{fig-exp-semantic-citation-link}.
+(4) The teams found by \optgrouprec come with a higher edge satisfiability , \eg 1.0 in all cases, compared to smaller than 0.6 by \mindia, \minsumdis and \denalk, as shown in Fig.~\ref{fig-exp-semantic-citation-link}.
 
@@
 
-\revise{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and capacity satisfiability, and pertains a good team collaboration compatibility \wrt density and diameter.}
+\revise{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and node satisfiability, and pertains a good team collaboration compatibility \wrt diameter and density.}
 

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

@@
 
-\sstab(1) When $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$,
-\bfc is updated as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).
-\identifyaffball identifies balls with type code $(1, 1)$ and $(1, 0)$ as \affballsx,
-\ie $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$.
-Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.
+\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, and
+\bfc is updated accordingly as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).
+
+\identifyaffball first identifies balls with type code $(1, 1)$ and $(1, 0)$ as \affballsx,
+\ie $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$, and then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.
 
@@
 
-The proof is deferred to the full version~\cite{fullvldb18}.
+%The proof is deferred to the full version~\cite{fullvldb18}.
 
@@
 \caption{Procedure \patedgeinsert} \label{alg-patedgeinsert}
-\vspace{-5ex}
+\vspace{-4ex}
 \end{figure}

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

@@
 (1) it updates \bfc by processing all unit updates in $\Delta P$.
-(2) For each $i\in [1, 2^h]$, it then executes a bitwise \kw{AND} operation (\&) between type code $tc_i$ of \fs in \fb and updated $fc_{i\Delta}$ in \bfc, \ie $tc_i\& fc_{i\Delta}$.
-(3) Finally, if $tc_i\& fc_{i\Delta} = fc_{i\Delta}$, \identifyaffball refers to \bs in \fb to mark the balls with type code $tc_i$ as \affballsx, and resets $fc_{i\Delta}$ to $(1, \ldots, 1)$.
+(2) For each $j\in [1, 2^h]$, it then executes a bitwise \kw{AND} operation (\&) between type code $tc_j$ of \fs in \fb and updated filtering code $fc_{j\Delta}$ in \bfc, \ie $tc_j\& fc_{j\Delta}$.
+(3) Finally, if $tc_j\& fc_{j\Delta} = fc_{j\Delta}$, \identifyaffball refers to \bs in \fb to mark the balls with type code $tc_j$ as \affballsx, and resets $fc_{j\Delta}$ to $(1, \ldots, 1)$.
+\revise{This is because the condition holds as long as
+(a) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ is 0, \ie there exists an edge/node deletion on ${P}_{fi}$; or
+(b) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ and $tc_j$ are both 1, \ie  balls with $tc_j$ already match with ${P}_{fi}$, although there are no edge/node deletions on ${P}_{fi}$.}
 

### 2017-09-30 TF-vldb2018/subsec-Ginc.tex

@@
 \sstab{(1)} for some unit data update $\delta$ of $\Delta G$, where
-(a) $\delta$ is an edge insertion/deletion, $(w_1,w_2)^+/(w_1,w_2)^-$, and $v\in V_{\ball{[w_1,r]}}\cap V_{\ball{[w_2,r]}}$, or
-(b) $\delta$ is a node insertion/deletion, $(w,(w,w'))^+$/$(w)^-$, and $v\in V_{\ball{[w,r]}}$; or
+(a) $\delta$ is an edge insertion/deletion, $(w_1,w_2)^+/(w_1,w_2)^-$ and $v$ in  both $\ball{[w_1,r]}$  and $\ball{[w_2,r]}$, or
+(b) $\delta$ is a node insertion/deletion, $(w,(w,w'))^+$/$(w)^-$ and $v$ in $\ball{[w,r]}$; or
 

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

@@
 \eetitle{(2) No edge/node deletions in $\Delta P_{fi}$}.
-\incmatch processes updates of the same type together in this case.
+\incmatch processes updates of the same type together in this case as follows.
 
-\eetitle{(2).i Capacity changes in $\Delta P_{fi}$ or updates on $C$}.
-In this case, no computation is needed for maintaining \revise{partial relations for} \affballsx at all,
+\sstab{(i) Capacity changes in $\Delta P_{fi}$ or updates on $C$}.
+In this case, no computation is needed for maintaining partial relations for \affballsx at all,
 \ie $M(P_{fi}\oplus\Delta P_{fi}, \ball{}) = M(P_{fi}, \ball{})$.
-\warn{Only a capacity check and an inner ball results check in the combination procedure are needed} (to see in Section~\ref{subsubsec-combine}).
+Only a capacity check and an inner ball check in the combination procedure are needed (to see in Section~\ref{subsubsec-combine}).
 
@@
 %\eetitle{(3) Edge insertions in $\Delta P_{fi}$ only}.
-\eetitle{(2).i Edge insertions in $\Delta P_{fi}$}.
+\sstab{(ii) Edge insertions in $\Delta P_{fi}$}.
 In this case, \incmatch calls procedure \patedgeinsert to process edge insertions.
@@
 along the same lines as for data incremental graph simulation~\cite{FanWW13-tods}.
-\patedgeinsert first finds the directly affected data nodes which need to be removed from $\matchs(\cdot)$ due to the edge insertion to $P_{fi}$,
+\patedgeinsert first finds the directly affected data nodes that need to be removed from $\matchs(\cdot)$ due to the edge insertion to $P_{fi}$,
 and pushes them along with the matched pattern nodes into $\kw{RMv}$ (lines 3-8).
@@
 To compute the updated $M(P_{f1}\oplus \delta_2, \ball{}_{\kw{PM_1}})$,
-\patedgeinsert removes \kw{UD_2} which is directly affected by $\delta_2$, and finds no other nodes need to be removed.
+\patedgeinsert removes \kw{UD_2} that is directly affected by $\delta_2$, and finds no other nodes need to be removed.
 \end{example}
@@
 %\eetitle{(4) Node insertions in $\Delta P_{fi}$ only}.
-\eetitle{(2).ii Node insertions in $\Delta P_{fi}$}.
+\sstab{(iii) Node insertions in $\Delta P_{fi}$}.
 Node insertions are handled in the same way as edge insertions, by extending \patedgeinsert.
@@
 to compute the updated $M(P_{fi}\oplus \delta, \ball{[v,r]})$,
-\incmatch firstly computes the set of nodes $\matchs(u)$ in $\ball{[v,r]}$ which have the same label with $u$, and then calls \patedgeinsert($M(P_{fi}, \ball{[v,r]})$, $\ball{[v,r]}$, $(u,u')$) to get the updated result.
+\incmatch firstly computes the set of nodes $\matchs(u)$ in $\ball{[v,r]}$ that have the same label with $u$, and then calls \patedgeinsert($M(P_{fi}, \ball{[v,r]})$, $\ball{[v,r]}$, $(u,u')$) to get the updated result.
 
@@
 Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb.
-Observe that only the balls from \affballsx which match with all pattern fragments of $P\oplus \Delta P$ can enter the combination process.
+Observe that only the balls from \affballsx that match with all pattern fragments of $P\oplus \Delta P$ can enter the combination process.
 
@@
 If so, it constructs the perfect subgraph \wrt the match relations above.
-\warn{It then checks the inner balls results together with the capacity bounds} and finally returns the list of top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$.
+It then checks the inner balls together with the capacity bounds, and finally returns the list of top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$.
 
@@
 and the capacity bounds are satisfied.
-\warn{For inner balls, based on above results, \comb finds that no perfect subgraphs reside in $\ball{[\kw{PM_1},1]}$ and $\ball{[\kw{PM_2},1]}$.}
-Hence it returns above two perfect subgraphs in two balls.
+For inner balls, based on above results, \comb finds that no perfect subgraphs reside in $\ball{[\kw{PM_1},1]}$ and $\ball{[\kw{PM_2},1]}$.
+Hence it returns the above two perfect subgraphs in two balls.
 
@@
 (2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
-\warn{So no results are in it and its inner balls.}
+Hence, there are no matches found in it and its inner balls.
 \end{example}
@@
 				\icc \> \hspace{3ex} \= \If $|L_{k}| \geq k$ \And $\ball{[v,r]}[\kw{den}] \leq \density{L_{k}[k]}$ \Then \\
-				\icc \>\>\hspace{2ex} \= \bf{Output} $L_{k}[0:k-1]$.\quad/* early-return optimization*/\\
+				\icc \>\>\hspace{2ex} \= \bf{Output} $L_{k}[0:k-1]$. /* early-return optimization*/\\
 				%/* Running in background after returning top-$k$ results for $\Delta P$ */\\

### 2017-09-30 TF-vldb2018/subsec-Ginc.tex

@@
 
-We next propose \incd to handle $\Delta G$, followed the steps in Section~\ref{sec-dynamictopk}.
+We next propose \incd to handle $\Delta G$, following the framework in Section~\ref{subsec-framework}.
 Given auxiliary structures $\tilde{M}(P,G)$ and \fb,
-we show how to combine procedures \identifyaffball, \incmatch and \comb for computing match results for $P$ in $G \oplus \Delta G$.
+we put together procedures \identifyaffball, \incmatch and \comb for computing match results for $P$ in $G \oplus \Delta G$.
 %
-\incmatch and \comb handle $\Delta G$ basically the same as $\Delta P$, so we mainly show how \identifyaffball identifies \affballsx \wrt $\Delta G$.
+As procedures \incmatch and \comb handle $\Delta G$ basically the same as $\Delta P$, so we mainly show how \identifyaffball identifies \affballsx \wrt $\Delta G$.
 
@@
 
-\stitle{Remarks}. Note that the running time of \incd is determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$,
-and hence the part for data updates in Theorem~\ref{thm-framework-inc} is proved. This also completes the proof of Theorem~\ref{thm-framework-inc}.
-
 \subsection{Unifying Pattern and Data Updates}
@@
 
-We are now ready to provide algorithm \inc, integrating \incp and \incd, \revise{which are presented in Section~\ref{subsec-Qinc} and Section~\ref{subsec-Ginc}, respectively,} to process continuous pattern and data updates, separately and simultaneously.
+We are now ready to provide algorithm \inc, integrating \incp and \incd, presented in Sections~\ref{subsec-Qinc} and~\ref{subsec-Ginc}, respectively, to process continuous pattern and data updates, separately and simultaneously.
 
@@
 as \inc incrementally maintains the auxiliary structures for continuous coming $\Delta P$ and $\Delta G$.
+
+%\vspace{0.5ex}
+\stitle{Remarks}. Note that (a) the running time of \incp is determined by $P$, $\Delta P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$, and
+(b) the running time of \incd is determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
+From these, we complete the proof of Theorem~\ref{thm-framework-inc}.

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

@@
 
-We present algorithm \incp to handle pattern updates $\Delta P$, followed the steps in Section~\ref{sec-dynamictopk}, and
+We present algorithm \incp to handle pattern updates $\Delta P$, followed the steps in Section~\ref{subsec-framework}, and
 an early return optimization technique for \incp.
@@
 (2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
-Hence, there are no matches found in it and its inner balls.
+So there no matches are found.
 \end{example}
@@
 \incp is in $O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|$ + $r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|$) + $r|P \oplus \Delta P||\affballsx|$+$|\Delta P|)$ time \wrt $\Delta P$, while $r$ is small, \ie 2 or 3 (See full version~\cite{fullvldb18}).
-
-%\vspace{0.5ex}
-\stitle{Remarks}. The running time of \incp is determined by $P$, $\Delta P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
-Hence the part for pattern updates in Theorem~\ref{thm-framework-inc} is proved.

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

@@
 
-\subsubsection{Identifying Affected Balls}
-\label{subsubsec-affball}
+%\subsubsection{Identifying Affected Balls}
+%\label{subsubsec-affball}
 
-We first develop procedure \identifyaffball to identify \affballsx,
-which utilizes auxiliary structures \fb and \bfc.
+\stab{\bf (1) Identifying affected balls}. 
+We first develop procedure \identifyaffball,
+which utilizes auxiliary structures \fb and \bfc, to identify \affballsx.
 
@@
 
-\vspace{-.5ex}
+%\vspace{-2ex}
+%\subsubsection{Updating Fragment-Ball Matches}
+%\label{subsubsec-updtm}
 
-\subsubsection{Updating Fragment-Ball Matches}
-\label{subsubsec-updtm}
-
-We then update the partial match relations for \affballsx in $\tilde{M}(P,G)$ \wrt $\Delta P$,
+\stab{\bf (2) Updating Fragment-Ball matches}. We then update the partial match relations for \affballsx in $\tilde{M}(P,G)$ \wrt $\Delta P$,
 by procedure \incmatch.
@@
 
-\subsubsection{Combining Fragment-Ball Matches}
-\label{subsubsec-combine}
+%\subsubsection{Combining Fragment-Ball Matches}
+%\label{subsubsec-combine}
 
+\stab{\bf (3) Combining Fragment-Ball matches}.
 Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb.
@@
 
-\subsubsection{Early Return Optimization Technique}
-\label{subsubsec-Inc-opt}
+%\subsubsection{Early Return Optimization Technique}
+%\label{subsubsec-Inc-opt}
 
+\stab{\bf (4) Early return optimization technique}. 
 %As introduced in last section, the {\em lazy update manner} accelerates the process to return updated top-$k$ perfect subgraphs by postponing the processing of each unit pattern update.
@@
 
-\subsubsection{The Complete Algorithm for Pattern Updates}
-\label{subsubsec-completedynamicP}
+%\subsubsection{The Complete Algorithm for Pattern Updates}
+%\label{subsubsec-completedynamicP}
 
+\stab{\bf (5) The complete algorithm for pattern updates}.
 Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

@@
 
-\stab{\bf (1) Identifying affected balls}. 
+\stab{\bf (I) Identifying affected balls}. 
 We first develop procedure \identifyaffball,
@@
 
-\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, and
-\bfc is updated accordingly as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).
+\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, \revise{and all four $fc$ in \bfc are updated from $fc$ (1, 1) to $fc_{\Delta}$ (1, 0), as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).}
 
-\identifyaffball first identifies balls with type code $(1, 1)$ and $(1, 0)$ as \affballsx,
-\ie $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$, and then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.
+\revise{Procedure \identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx, 
+	since $tc (1, 1) \& fc_{\Delta}(1, 1) = fc_{\Delta}(1, 1)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.}
+Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.
 
@@
 
-\stab{\bf (2) Updating Fragment-Ball matches}. We then update the partial match relations for \affballsx in $\tilde{M}(P,G)$ \wrt $\Delta P$,
+\stab{\bf (II) Updating Fragment-Ball matches}. We then update the partial match relations for \affballsx in $\tilde{M}(P,G)$ \wrt $\Delta P$,
 by procedure \incmatch.
@@
 
-\stab{\bf (3) Combining Fragment-Ball matches}.
+\stab{\bf (III) Combining Fragment-Ball matches}.
 Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb.
@@
 
-\stab{\bf (4) Early return optimization technique}. 
+\stab{\bf (IV) Early return optimization technique}. 
 %As introduced in last section, the {\em lazy update manner} accelerates the process to return updated top-$k$ perfect subgraphs by postponing the processing of each unit pattern update.
@@
 
-\stab{\bf (5) The complete algorithm for pattern updates}.
+\stab{\bf (V) The complete algorithm for pattern updates}.
 Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

@@
 \stab{\bf (I) Identifying affected balls}.
-We first develop procedure \identifyaffball,
-which utilizes auxiliary structures \fb and \bfc, to identify \affballsx.
+We first develop procedure \identifyaffball to identify \affballsx with structures \fb and \bfc, .
 
@@
 (3) Finally, if $tc_j\& fc_{j\Delta} = fc_{j\Delta}$, \identifyaffball refers to \bs in \fb to mark the balls with type code $tc_j$ as \affballsx, and resets $fc_{j\Delta}$ to $(1, \ldots, 1)$.
-\revise{This is because the condition holds as long as
-(a) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ is 0, \ie there exists an edge/node deletion on ${P}_{fi}$; or
-(b) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ and $tc_j$ are both 1, \ie  balls with $tc_j$ already match with ${P}_{fi}$, although there are no edge/node deletions on ${P}_{fi}$.}
+The condition $tc_j\& fc_{j\Delta} = fc_{j\Delta}$ holds as long as
+(a) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ is 0, \ie there exists an edge/node deletion on ${P}_{fi}$, or
+(b) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ and $tc_j$ are both 1, \ie  balls with $tc_j$ already match with ${P}_{fi}$, though there are no edge/node deletions on ${P}_{fi}$.
 
@@
 
-\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, \revise{and all four $fc$ in \bfc are updated from $fc$ (1, 1) to $fc_{\Delta}$ (1, 0), as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).}
+\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, and all four $fc$ in \bfc are updated from $fc$ (1, 1) to $fc_{\Delta}$ (1, 0), as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).
 
-\revise{Procedure \identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx, 
-	since $tc (1, 1) \& fc_{\Delta}(1, 1) = fc_{\Delta}(1, 1)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.}
+Procedure \identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx,
+	since $tc (1, 1) \& fc_{\Delta}(1, 1) = fc_{\Delta}(1, 1)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.
 Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.

### 2017-09-30 TF-vldb2018/sec-intro.tex

@@
 
-A headhunt helps to set up a team for developing a software product by searching proper candidates from $G_1$ (ignore dashed edges).
+A headhunt helps to set up a team for a software product by searching proper candidates from $G_1$ (ignore dashed edges).
 A desired team has
 (i) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
-(ii) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.
+(ii) \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.
 
@@
 
-\begin{figure}[tb!]
-\begin{center}
-\includegraphics[scale=1.15]{./fig/motivation-example.eps}
-\end{center}
-\vspace{-3ex}
-\caption{Motivation example}
-\label{fig-motivation-example}
-\vspace{-4ex}
-\end{figure}
-
 \eat{
@@
 We show this with an example.
+
+\begin{figure}[tb!]
+\vspace{-2ex}
+\begin{center}
+\includegraphics[scale=1.15]{./fig/motivation-example.eps}
+\end{center}
+\vspace{-3ex}
+\caption{Motivation example}
+\label{fig-motivation-example}
+\vspace{-4ex}
+\end{figure}
 

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

@@
 (3) Finally, if $tc_j\& fc_{j\Delta} = fc_{j\Delta}$, \identifyaffball refers to \bs in \fb to mark the balls with type code $tc_j$ as \affballsx, and resets $fc_{j\Delta}$ to $(1, \ldots, 1)$.
+\revise{This is because \affballsx are balls that have the possibility to match all updated pattern fragments.}
 The condition $tc_j\& fc_{j\Delta} = fc_{j\Delta}$ holds as long as
-(a) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ is 0, \ie there exists an edge/node deletion on ${P}_{fi}$, or
+(a) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ is 0, \ie there exists an edge/node deletion on ${P}_{fi}$, \revise{which may produce more matched nodes}, or
 (b) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ and $tc_j$ are both 1, \ie  balls with $tc_j$ already match with ${P}_{fi}$, though there are no edge/node deletions on ${P}_{fi}$.

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

--- 2017-09-30 TF-vldb2018/subsec-Qinc.tex
@@
 (3) Finally, if $tc_j\& fc_{j\Delta} = fc_{j\Delta}$, \identifyaffball refers to \bs in \fb to mark the balls with type code $tc_j$ as \affballsx, and resets $fc_{j\Delta}$ to $(1, \ldots, 1)$.
+This is because \affballsx are balls that have the possibility to match all updated pattern fragments.
 The condition $tc_j\& fc_{j\Delta} = fc_{j\Delta}$ holds as long as
-(a) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ is 0, \ie there exists an edge/node deletion on ${P}_{fi}$, or
+(a) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ is 0, \ie there exists an edge/node deletion on ${P}_{fi}$, which may produce more matched nodes, or
 (b) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ and $tc_j$ are both 1, \ie  balls with $tc_j$ already match with ${P}_{fi}$, though there are no edge/node deletions on ${P}_{fi}$.
@@
 \sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, and all four $fc$ in \bfc are updated from $fc$ (1, 1) to $fc_{\Delta}$ (1, 0), as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).
-
-Procedure \identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx,
+% 
+\identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx,
 	since $tc (1, 1) \& fc_{\Delta}(1, 1) = fc_{\Delta}(1, 1)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

@@
 \identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx,
-	since $tc (1, 1) \& fc_{\Delta}(1, 1) = fc_{\Delta}(1, 1)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.
+	since $tc (1, 1) \& fc_{\Delta}(1, 0) = fc_{\Delta}(1, 0)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.
 Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.

### 2017-09-30 TF-vldb2018/subsec-Ginc.tex

@@
 %\vspace{0.5ex}
-\stitle{Remarks}. Note that (a) the running time of \incp is determined by $P$, $\Delta P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$, and
-(b) the running time of \incd is determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
-From these, we complete the proof of Theorem~\ref{thm-framework-inc}.
+\stitle{Remark}. Note that the running time of \incp and \incd is determined by \{$P, \Delta P, \tilde{M}(P,G)$, $\affballsx$\} 
+and \{$P, \tilde{M}(P,G)$, $\affballsx$\}, respectively, not directly depending on $G$.
+From this, we complete the proof of Theorem~\ref{thm-framework-inc}.

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

--- 2017-09-30 TF-vldb2018/subsec-Qinc.tex
@@
 (3) Finally, if $tc_j\& fc_{j\Delta} = fc_{j\Delta}$, \identifyaffball refers to \bs in \fb to mark the balls with type code $tc_j$ as \affballsx, and resets $fc_{j\Delta}$ to $(1, \ldots, 1)$.
-This is because \affballsx are balls that have the possibility to match all updated pattern fragments.
+%This is because \affballsx are balls that have the possibility to match all updated pattern fragments.
 The condition $tc_j\& fc_{j\Delta} = fc_{j\Delta}$ holds as long as
@@
 
-In real-life networks, the quantity of balls with type code ($0,\ldots,0$) is several orders of magnitude larger than that of balls who match with at least one pattern fragment.
+In practice, the number of balls with type code ($0,\ldots,0$) is much larger than those balls matching with at least one pattern fragment.
 By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$),
-it can reduce a large amount of redundant computations.
+ redundant computations are avoid.
 

### 2017-09-30 TF-vldb2018/sec-expt.tex

@@
 (3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
-(a) \mindia is to minimize the team diameter~\cite{Lappas09},
-\revise{which is firstly proposed for the team formation problem;}
+(a) \mindia is to minimize the team diameter~\cite{Lappas09}, which is firstly proposed for the team formation problem;
 (b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
 (c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
-\revise{Most of the algorithms for \teamF, including  \mindia and \denalk, only compute the best team,}
+Most of the algorithms for \teamF, including  \mindia and \denalk, only compute the best team,
 while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
@@
 
-\revise{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and node satisfiability, and pertains a good team collaboration compatibility \wrt diameter and density.}
+These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and node satisfiability, and pertains a good team collaboration compatibility \wrt diameter and density.
 
@@
 
-\etitle{(i) Pattern updates}. We generated $5$ sets of hybrid pattern updates, varying the number of updates of each set from $1$ to $7$.
+\etitle{(i) Pattern updates}. We generated $5$ sets of hybrid pattern updates, varying the number of updates in each set from $1$ to $7$.
 We tested the average time took by \inc to finish all these sets one by one.
@@
 Recall that \inc adopts a lazy update policy, which definitely affects the processing time of next updates.
-However, we find \inc outperforms \optgrouprec \wrt average time, when the number of hybrid  pattern updates in each set is no more than (27\%, 31.5\%)  on (\citationd, \synthetic).
+However, we find \inc outperforms \optgrouprec \wrt average time, when the amount of hybrid  pattern updates in each set is no more than (27\%, 31.5\%)  on (\citationd, \synthetic).
 This verifies the effectiveness of our lazy update policy.
 
-\etitle{(ii) Data updates}. The setting is same as above. Varying the the amount of hybrid data updates in each set from 4\% to 24\%,
+\etitle{(ii) Data updates}. The setting is same as above. Varying the amount of hybrid data updates in each set from 4\% to 28\%,
 the results are reported in Fig.~\ref{fig-exp-datainc-multi}.
@@
 \etitle{(iii) Simultaneous pattern and data updates}.
-Using the same setting and varying the simultaneous pattern and data updates $(\Delta P, \Delta G)$ from (4.5\%, 4\%) to (27\%, 24\%) in Fig.~\ref{fig-exp-hyb-datapat-multi},
+Using the same setting and varying the simultaneous pattern and data updates $(\Delta P, \Delta G)$ from (4.5\%, 4\%) to (31.5\%, 28\%) in Fig.~\ref{fig-exp-hyb-datapat-multi},
 We find that \inc outperforms \optgrouprec when updates in each set are no more than (18\%, 16\%) and (22.5\%, 20\%)

### 2017-10-01 TF-vldb2018/sec-dynamicTopk.tex

@@
 
-\subsection{Unified Incremental Framework}
-%\label{subsec-framework}
+\subsection{A Unified Incremental Framework}
+\label{subsec-framework}
 
@@
 
-\stitle{(1) Localization with pattern fragmentation}. 
-We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
+\stitle{(I) Localization with pattern fragmentation}.
+We say that \{$P_{f1}(V_{f1}, E_{f1})$, $\ldots$, $P_{fh}(V_{fh}, E_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
 if (1) $\bigcup_{i=1}^{h}V_{fi}=V_{P}$, (2) $V_{fi}\cap V_{fj} = \emptyset$ for any $i\ne j\in[1, h]$,
@@
 Let $\{P_{f1},\ldots,P_{fh}\}$ be an $h$-fragmentation of pattern $P$.
-For any ball $\ball{}_i$ in $G$, let $M_i$ ($i\in[1,h]$) be the maximum match relation in $\ball{}_i$ for $P_{fi}$ via graph simulation,
-and $M$ be the maximum match relation in $\ball{}_i$ for $P$ via graph simulation, respectively,
+For any ball $\ball{}$ in $G$, let $M_i$ ($i\in[1,h]$) be the maximum match relation in $\ball{}$ for $P_{fi}$ via graph simulation,
+and $M$ be the maximum match relation in $\ball{}$ for $P$ via graph simulation, respectively,
 then $M\subseteq\bigcup_{i=1}^{h}M_{i}$.
@@
 
-We also say that $M_i$ is a {\em partial match relation} in ball $\ball{}_i$ for $P$ via graph simulation.
+We also say that $M_i$ is a {\em partial match relation} in ball $\ball{}$ for $P$ via graph simulation.
 %By Theorem~\ref{thm-compose}, instead of computing $M$ in $\ball{}$ \wrt\ $P$ directly, we can compute $M$ by first computing each $M_i$ in $\ball{}$ \wrt\ $P_{fi}$,
@@
 %such that the method above does not incur additional computation cost.
-Once we have the maximum match relation $M$ for $P$ in $\ball{}_i$, via graph simulation, we can further produce the result for $P$ in  $\ball{}$ via team simulation, by a capacity check.
+Once we have the maximum match relation $M$ for $P$ in $\ball{}$, via graph simulation, we can further produce the result for $P$ in  $\ball{}$ via team simulation, by a capacity check.
 
@@
 and we can simply update $M_i$ while leaving other parts untouched.
-That is, we indeed compute for $P_{fi}\oplus\Delta P(\ball{})$, instead of $P\oplus\Delta P(\ball{})$, and combine all $P_{fi}\oplus\Delta P(\ball{})$ derive $P\oplus\Delta P(\ball{})$.
-Even better, the updates $\Delta P$ on $C$ of $P$ only involve with a simple combination process, avoiding the computation for any pattern fragments.
+That is, we indeed compute for $P_{fi}\oplus\Delta P(\ball{})$, instead of $P\oplus\Delta P(\ball{})$, and combine all $P_{fi}\oplus\Delta P(\ball{})$ to derive $P\oplus\Delta P(\ball{})$.
+Even better, the updates $\Delta P$ on the cut $C$ of $P$ only involve with a simple combination process, avoiding the computation for any pattern fragments.
 
@@
 
-\stitle{(2) Localization with affected balls (\affballsx)}.
+\stitle{(II) Localization with affected balls (\affballsx)}.
 We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computations.
@@
 %\vspace{-0.5ex}
-\stitle{(3) Algorithm framework}. We now provide a unified incremental algorithm to handle both pattern and data updates,
+\stitle{(III) Algorithm framework}. We now provide a unified incremental algorithm to handle both pattern and data updates,
 based on pattern fragmentation and affected balls.
@@
 
-\etitle{(i) Identifying \affballsx}.
+\etitle{(1) Identifying \affballsx}.
 Algorithm \inc invokes two different procedures to identify \affballsx for separate $\Delta P$ or $\Delta G$, respectively.
@@
 
-\etitle{(ii) Update partial match relations in \affballsx}.
+\etitle{(2) Update partial match relations in \affballsx}.
 For a ball affected by $\Delta P$, \inc updates the partial match relations for the updated pattern fragments with incremental computation;
 For a ball affected by $\Delta G$, \inc updates the partial match relations for all pattern fragments;
-And, for a ball affected by both $\Delta P$ and $\Delta G$, \inc follows the same way as $\Delta G$ only.
-Meanwhile, auxiliary structure \fb (to be seen shortly) is updated for handling continuous separate and simultaneous pattern and data updates.
+And, for a ball affected by both $\Delta P$ and $\Delta G$, \inc follows the same way as it does for $\Delta G$ only.
+Meanwhile, auxiliary structure \fb (to be seen shortly) is updated for handling continuously separate and simultaneous pattern and data updates.
 
-\etitle{(iii) Combining partial match relations}. \inc combines all partial relations for a subset of \affballsx and computes the top-$k$ perfect subgraphs within them and their inner balls.
+\etitle{(3) Combining partial match relations}. \inc combines all partial relations for a subset of \affballsx and computes the top-$k$ perfect subgraphs within them and their inner balls.
 
@@
 		\label{fig-auxiliary-structures}
-		\vspace{-4ex}
+		\vspace{-5ex}
 	\end{center}

### 2017-10-01 TF-vldb2018/sec-intro.tex

@@
 We find that (a) our method is able to identify more sensible teams than existing team formation methods \wrt \eat{three} practical measurements,
-and (b) our incremental algorithm outperforms our batch algorithm, even when changes reach 36\% for pattern updates, 34\% for data updates and (25\%, 22\%) for simultaneous pattern and data updates, and when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuous simultaneous pattern and data updates, respectively.
+and (b) our incremental algorithm outperforms our batch algorithm, even when changes reach 36\% for pattern updates, 34\% for data updates and (25\%, 22\%) for simultaneous pattern and data updates, and when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuously simultaneous pattern and data updates, respectively.
 
@@
 However, \cite{inc-survey,FanHT17,FanLMTWW10,FanWW13-tods} only consider data updates,
-and \cite{ArisLuca12} only considers continuous coming new tasks.
+and \cite{ArisLuca12} only considers continuously coming new tasks.
 In this work, we  deal with both pattern and data updates for team formation, and support both insertions and deletions.

### 2017-10-01 TF-vldb2018/subsec-Qinc.tex

@@
 
-In practice, the number of balls with type code ($0,\ldots,0$) is much larger than those balls matching with at least one pattern fragment.
-By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$),
- redundant computations are avoid.
+In practice, the number of balls with type code ($0,\ldots,0$) is much larger than that of balls match with some pattern fragments, which is further larger than the number of \affballsx.
+By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$), redundant computations are avoid.
 

### 2017-10-01 TF-vldb2018/sec-expt.tex

@@
 (2) \inc for the dynamic top-$k$ team formation problem
-\wrt single set of (a) pattern updates, (b) data updates, and (c) simultaneous pattern and data updates;
-(3) \inc \wrt continuous sets of pattern and data updates; and
+\wrt single sets of (a) pattern updates, (b) data updates, and (c) simultaneous pattern and data updates,
+(3) \inc \wrt continuous sets of pattern and data updates, and
 (4) the extra space cost of auxiliary structures used by \inc.
@@
 \vspace{-0.3ex}
-\etitle{Data graphs.} We used two real-life and a synthetic dataset.
+\etitle{Data graphs.} We used two real-life and a synthetic datasets.
 

### 2017-10-01 TF-vldb2018/sec-expt.tex

@@
 
-%\ni (2) {\em \youtube}~\cite{youtubeWeb} contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos.
+\ni (2) {\em \youtube}~\cite{youtubeWeb} contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos.
 We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.
 
-\ni (2) We generated synthetic data graphs (\synthetic) with community structures as existed in real-life networks, by adopting the LFR-benchmark graph model~\cite{AndreaSF08}.
+\ni (3) We generated synthetic data graphs (\synthetic) with community structures as existed in real-life networks, by adopting the LFR-benchmark graph model~\cite{AndreaSF08}.
 It is controlled by three parameters: the number $n$ of nodes, the average degree $d$ of nodes, and the number $l$ of node labels.
@@
 
-\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The detailed information of the dataset is available in the full version~\cite{fullvldb18}.
+%\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The detailed information of the dataset is available in the full version~\cite{fullvldb18}.
 

### 2017-10-01 TF-vldb2018/subsec-Qinc.tex

--- 2017-09-30 TF-vldb2018/subsec-Qinc.tex
@@
 
-In practice, the number of balls with type code ($0,\ldots,0$) is much larger than those balls matching with at least one pattern fragment.
-By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$),
- redundant computations are avoid.
+%In practice, the number of balls with type code ($0,\ldots,0$) is much larger than that of balls match with some pattern fragments, which is further larger than the number of \affballsx.
+By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$), redundant computations are avoid.
 
@@
 \ie $M(P_{fi}\oplus\Delta P_{fi}, \ball{}) = M(P_{fi}, \ball{})$.
-Only a capacity check and an inner ball check in the combination procedure are needed (to see in Section~\ref{subsubsec-combine}).
+Only a capacity check and an inner ball check in the combination procedure are needed (to be seen immediately).
 

### 2017-10-01 TF-vldb2018/sec-expt.tex

@@
 
+ We used the following real-life and synthetic datasets.
+
+%\subsection{Experimental Settings}
+
+\vspace{-0.3ex}
+\etitle{Real-life graphs.} We used two real-life graphs.
+
+\ni (1) {\em \citationd}~\cite{citationWeb} contains 1.39M paper nodes and 3.02M paper-paper citation edges.
+We used its undirected version, where edges indicate the relevance relationship. We generated 200 labels based on phrase clustering of paper titles.
+
+\ni (2) {\em \youtube}~\cite{youtubeWeb} contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos.
+We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.
+
+\etitle{Synthetic graph generator.} We generated synthetic graphs (\synthetic) with community structures as existed in real-life, by adopting the LFR-benchmark graph model~\cite{AndreaSF08}.
+It is controlled by three parameters: the number $n$ of nodes, the average degree $d$ of nodes, and the number $l$ of node labels.
+
+\eat{
  We used the following datasets and settings.
 
-%\subsection{Experimental Settings}
-%We used the following real-life and synthetic datasets.
-\vspace{-0.3ex}
 \etitle{Data graphs.} We used two real-life and a synthetic datasets.
@@
 %\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The detailed information of the dataset is available in the full version~\cite{fullvldb18}.
+}%%%EAT
 

### 2017-10-01 TF-vldb2018/subsec-Ginc.tex

@@
 
-Observe that \inc can handle {\em continuous} simultaneous $\Delta P$ and $\Delta G$,
-as \inc incrementally maintains the auxiliary structures for continuous coming $\Delta P$ and $\Delta G$.
+Observe that \inc can handle {\em continuously} simultaneous $\Delta P$ and $\Delta G$,
+as \inc incrementally maintains the auxiliary structures for continuously coming $\Delta P$ and $\Delta G$.
 

### 2017-10-01 TF-vldb2018/subsec-Qinc.tex

@@
 \stab{\bf (I) Identifying affected balls}.
-We first develop procedure \identifyaffball to identify \affballsx with structures \fb and \bfc, .
+We first develop procedure \identifyaffball to identify \affballsx with structures \fb and \bfc.
 
@@
 %
-\identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx,
-	since $tc (1, 1) \& fc_{\Delta}(1, 1) = fc_{\Delta}(1, 1)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.
+\identifyaffball identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx,
+	since $tc (1, 1) \& fc_{\Delta}(1, 0) = fc_{\Delta}(1, 0)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.
 Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.
@@
 By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$), redundant computations are avoid.
+
+The correctness of \identifyaffball is ensured by the following.
 
@@
 %and their partial match relations are outdated \wrt $P\oplus \Delta P$.
-However, those partial relations in the filtered balls also needs an update for handling future updates $\Delta P'$, but
+However, those partial relations in the filtered balls also need an update for handling future updates $\Delta P'$, but
 definitely become outdated \wrt $P\oplus \Delta P$.
@@
 When future $\Delta P'$ comes, for any \affballx $\ball{}$ \wrt $\Delta P'$ and any fragment $P_{fi}$,
-\incp computes $M(P_{fi}\oplus\Delta P'_{fi}, \ball{})$ based on $M(P_{fi}, \ball{})$ by procedure \incmatch (to see in Section~\ref{subsubsec-updtm}),
+\incp computes $M(P_{fi}\oplus\Delta P'_{fi}, \ball{})$ based on $M(P_{fi}, \ball{})$ by procedure \incmatch (to be seen shortly),
 where $\Delta P'_{fi}$ consists of the unit updates stored in $T(P_{fi})$ whose ids are larger than $\ball{}[\kw{cflag}]$ in \bs.
@@
 Whenever it comes to next \affballx $\ball{[v,r]}$, it firstly checks whether there are already $k$ perfect subgraphs found in $L_{k}$, and moreover,
-the density of the $k$th (smallest) perfect subfgraph in $L_{k}$ is larger than $\ball{[v,r]}[\kw{den}]$ (line 5).
+the density of the $k$th (smallest) perfect subgraph in $L_{k}$ is larger than $\ball{[v,r]}[\kw{den}]$ (line 5).
 If so, \incp immediately outputs $L_{k}$ as final results (line 6),

### 2017-10-01 TF-vldb2018/subsec-Qinc.tex

@@
 \sstab{(iii) Node insertions in $\Delta P_{fi}$}.
-Node insertions are handled in the same way as edge insertions, by extending \patedgeinsert.
+Node insertions are handled in a similar way as edge insertions, by extending \patedgeinsert.
 
@@
 (2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
-So there no matches are found.
+Hence, no  sensible matches are found.
 \end{example}
@@
 Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,
-algorithm \incp computes the maximum match relations of $P \oplus \Delta P$ in $G$ with early return property, and maintains auxiliary structures simultaneously by invoking procedure \identifyaffball, \incmatch and \comb one by one.
+algorithm \incp computes the top-k perfect subgraphs for $P \oplus \Delta P$ in $G$ with early return property, and maintains auxiliary structures simultaneously by invoking procedure \identifyaffball, \incmatch and \comb one by one.
 

### 2017-10-01 TF-vldb2018/subsec-Ginc.tex

@@
 \sstab{(1)} for some unit data update $\delta$ of $\Delta G$, where
-(a) $\delta$ is an edge insertion/deletion, $(w_1,w_2)^+/(w_1,w_2)^-$ and $v$ in  both $\ball{[w_1,r]}$  and $\ball{[w_2,r]}$, or
-(b) $\delta$ is a node insertion/deletion, $(w,(w,w'))^+$/$(w)^-$ and $v$ in $\ball{[w,r]}$; or
+(a) $\delta$ is an edge insertion/deletion, $(w_1,w_2)^+/(w_1,w_2)^-$ and $v$ is in  both $\ball{[w_1,r]}$  and $\ball{[w_2,r]}$, or
+(b) $\delta$ is a node insertion/deletion, $(w,(w,w'))^+$/$(w)^-$ and $v$ is in $\ball{[w,r]}$; or
 
@@
 \incd is overall in
-$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}\bigcup_{i\in[1,h]}$ $r|M(P_{fi}, \widehat{G\oplus\Delta G})|$+$r|P||\affballsx|)$ time \wrt $\Delta G$, while $r$ is small, \ie 2 or 3  (See~\cite{fullvldb18}).
+$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}\bigcup_{i\in[1,h]}$ $r|M(P_{fi}, \widehat{G\oplus\Delta G})|$+$r|P||\affballsx| + |\Delta G|)$ time \wrt $\Delta G$, while $r$ is small, \ie 2 or 3  (See~\cite{fullvldb18}).
 \looseness=-1
@@
 Algorithm \inc is able to handle {\em simultaneous} $\Delta P$ and $\Delta G$, because of the consistency in:
-(1) the processes for handling $\Delta P$ and $\Delta G$, which follow the same steps in Section~\ref{sec-dynamictopk};
+(1) the processes for handling $\Delta P$ and $\Delta G$, which follow the same steps in Section~\ref{subsec-framework};
 (2) auxiliary data structures for supporting $\Delta P$ and $\Delta G$; and
@@
 \stitle{Remark}. Note that the running time of \incp and \incd is determined by \{$P, \Delta P, \tilde{M}(P,G)$, $\affballsx$\}
-and \{$P, \tilde{M}(P,G)$, $\affballsx$\}, respectively, not directly depending on $G$.
+and \{$P, \Delta G, \tilde{M}(P,G)$, $\affballsx$\}, respectively, not directly depending on $G$.
 From this, we complete the proof of Theorem~\ref{thm-framework-inc}.

### 2017-10-02 Gruba/03-fe.tex
v3.0
v3.0

@@
 
-If $sim(b, t)$ satisfies a certain threshold, topic $t$ is labeled to blog $b$; 
+If $sim(b, t)$ satisfies a certain threshold (3 by default) , topic $t$ is labeled to blog $b$; 
 the user $u$ is then discovered having an explicit interest (topic) $t$.
@@
 \end{equation}
-where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$.
+where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ by default).
 %
@@
 
-Among the $n$ dimensions of $S(u,\ L)$, those with top $x$ similarity values are selected to label the implicit interests of user $u$, which results an $x$ dimensional vector $P_f$ as described in Definition \ref{def:inte}.
+Among the $n$ dimensions of $S(u,\ L)$, those with top $x$ (3 in \sys{}) similarity values are selected to label the implicit interests of user $u$, which results an $x$ dimensional vector $P_f$ as described in Definition \ref{def:inte}.
 Similarly, interest features of all users are returned.

### 2017-10-02 Gruba/06-perf.tex
v3.0
v3.0

@@
-\section{\textcolor{red}{Performance Evaluation}}
+\section{Performance Evaluation}
 \label{sec:perf}
+
+\subsection{Experimental Setting}
+
+Experiments were run on a machine with two Intel Xeon E5C2630 2.4GHz CPUs and 64 GB of Memory, running 64 bit Windows 7 professional system.
+
+We have employed a real-world dataset Sina \refe{} that consists of 24 million blogs that are associated with 43.5K users.
+
+With respect to the parameters of \sys{}, we use the default values as mentioned in previous sections.
+Particularly, in Feature Extractor, for practical reason, we employed a smaller testing dataset to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature}; 
+in User Cluster, we studied the clustering solutions with the minimum/maximum number of clusters 2 and 10;
+in Behavior Modeler, a user's recent 30 days blogs are used for short-term interest analysis and popular words of the latest 24 hours are returned by Ring \refe{} as the Big Thing keyword.
+
+\subsection{Result and Analysis}
+Next, we shall report the performance of \sys{} over each component.
+
+\textbf{Feature Extractor}
+%
+Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values. 
+Apparently, \sys{} results the optimal results when $\alpha$ is 0.7, upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million blogs.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=.96\linewidth]{figures/Interests}
+\caption{Testing Results with Various $\alpha$ \tbc{}}
+\label{fig:fe}
+\end{figure}
+
+\textbf{User Clusterer}
+%
+Fig.\ \ref{fig:uc} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number from 2 to 10.
+Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users and \textit{Data1,...,5} contains 10K randomly selected users each.
+Except for \textit{Data1}, solutions with 4 clusters sweep.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=.96\linewidth]{figures/clustering}
+\caption{Silhouette Coefficient Values for Various Cluster Numbers over Different Testing Datasets \tbc{}}
+\label{fig:uc}
+\end{figure}
+
+\textbf{Behavior Modeler}
+%
+Fig.\ \ref{fig:10} shows the performance of \sys{} against state of the art approach LRC-BQ \refe{}.
+We compare the metrics of precision, recall, as well as $F_1$ score.
+LRC-BQ \refe{} does not deal with user grouping.
+Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering), but also examine \sys{} versus LRC-BQ \refe{} in the case that all users are in mono group (i.e., ``All-Users'').
+The results are interesting in that:
+\begin{itemize}
+	\item With user clustering, \sys{} performs better than LRC-BQ \refe{} in most cases.
+	\item For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ \refe{}.
+\end{itemize}
+
+\begin{figure}
+  \centering
+  \subfigure[Precision]{
+    \label{fig:10-a} 
+    \includegraphics[width=0.4\textwidth]{figures/precision.eps}}
+  \hspace{1in}
+  \subfigure[Recall]{
+    \label{fig:10-b} 
+    \includegraphics[width=0.4\textwidth]{figures/recall.eps}}
+  \hspace{1in}
+  \subfigure[$F_1$ Score]{
+    \label{fig:10-c} 
+    \includegraphics[width=0.4\textwidth]{figures/F-Measure.eps}}
+  \caption{Performance of \sys{} Versus LRC-BQ \tbc{}}
+  \label{fig:10} 
+\end{figure}
+
+Fig.\ \ref{fig:11} explores the performance of \sys{} when using alternative data items for modeling.
+By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), blogs (MI) and interactions (II).
+How about using other combinations of the above item(s)?
+As shown in Fig.\ \ref{fig:11}, the default setting wins in most cases.
+
+\begin{figure}
+  \centering
+  \subfigure[Precision]{
+    \label{fig:11-a} 
+    \includegraphics[width=0.4\textwidth]{figures/precisionofdifferentfeatures.eps}}
+  \hspace{1in}
+  \subfigure[Recall]{
+    \label{fig:11-b} 
+    \includegraphics[width=0.4\textwidth]{figures/recallofdifferentfeatures.eps}}
+  \hspace{1in}
+  \subfigure[$F_1$ Score]{
+    \label{fig:11-c} 
+    \includegraphics[width=0.4\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
+  \caption{\sys{} Performance of Using Various Data Items for Modeling \tbc{}}
+  \label{fig:11}
+\end{figure}

### 2017-10-02 Gruba/08-conclu.tex
v3.0
v3.0

@@
-\section{\textcolor{red}{Conclusions}}
+\section{Conclusions}
 \label{sec:conclu}
+
+In this work, we have presented \sys{}, a system to model users' \retg{} behavior in social media. 
+\sys{} departures from related works by grouping users into clusters, during which features of info, behavior and interests are involved. 
+Specially, we have studied interest features from various perspectives, such as long-term/recent interests and explicit/implicit interests. 
+Last, we provided the performance evaluation of \sys{} by using real-world datasets and comparing against state of the art approaches, showing its benefits.

### 2017-10-02 TF-vldb2018/sec-tsimAlg.tex

@@
 
-In this section, we first study the pattern satisfiability problem for team formation, then introduce two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.
+%In this section, we first study the pattern satisfiability problem for team formation, then introduce two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.
 
+In this section, we develop a batch algorithm for top-$k$ team formation.
+We first study the pattern satisfiability problem for team simulation, then introduce two optimization techniques, and finally we present our batch algorithm.
 % with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for \warn{strong simulation}~\cite{MaCFHW14}.
@@
 	\label{alg-grouprec}
-	\vspace{-3ex}
+	\vspace{-4ex}
 \end{figure}

### 2017-10-02 TF-vldb2018/subsec-Qinc.tex

@@
 
-We present algorithm \incp to handle pattern updates $\Delta P$, followed the steps in Section~\ref{subsec-framework}, and
+We present algorithm \incp to handle pattern updates $\Delta P$, following the steps in Section~\ref{subsec-framework}, and
 an early return optimization technique for \incp.
@@
 				\icc \> \For \Each $\ball{[v,r]}$ in \affballsx \Do\quad/* non-ascending order */\\
-				\icc \> \hspace{3ex} \= \If $|L_{k}| \geq k$ \And $\ball{[v,r]}[\kw{den}] \leq \density{L_{k}[k]}$ \Then \\
+				\icc \> \hspace{3ex} \= \If $|L_{k}| \geq k$ \And $\ball{[v,r]}[\kw{den}] \leq \density{L_{k}[k-1]}$ \Then \\
 				\icc \>\>\hspace{2ex} \= \bf{Output} $L_{k}[0:k-1]$. /* early-return optimization*/\\

### 2017-10-02 TF-vldb2018/subsec-auxstr.tex

@@
 maintain partial matches and handle pattern incremental computing.
-Consider an $h$-fragmentation \{$P_{f1}, \ldots, P_{fh}, C$\} of pattern $P(V_P, E_P)$, data graph $G(V, E)$, and pattern updates $\Delta P$.
+Consider an $h$-fragmentation ${\cal P}_h$ = \{$P_{f1}, \ldots, P_{fh}, C$\} of pattern $P(V_P, E_P)$, data graph $G(V, E)$, and pattern updates $\Delta P$.
 
@@
 
-We use \fs to classify the match status of balls in $G$ into $2^h$ types \wrt ${\cal P}_h$.
+We use \fs to classify the match status of balls in $G$ into $2^h$ types $\wrt$ ${\cal P}_h$.
 For a ball with type code $(b_1,\ldots,b_h)$, $b_i$ is 1 iff $P_{fi}$ matches the ball via graph simulation.
@@
 %
-For simplicity, we consider these 4 balls only in the sequel.
+For simplicity, we use these 4 balls only in the following analysis.
 \end{example}

### 2017-10-04 TF-vldb2018/full/sec-appendix-cp.tex

%\newcommand{\EQ}{\kw{EQ}}
\newpage
\addtolength{\parskip}{0.25cm}
\newpage
\section*{\Large \sf APPENDIX-cp}
\label{sec-proofs}

\subsection{Optimization Techniques for Algorithm \grouprec}.
%
\begin{figure}[tb!]
\vspace{2ex}
\begin{center}
{\small

\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Pattern graph $P(V_p$, $E_p$, $l_p$, $f_p)$.\\
{\sl Output:\/} A minimum equivalent pattern graph $P_m$ of $P$.\\
\bcc \quad if $P$ is not a consistent pattern graph then return null.\\
\icc \quad Compute the maximum match relation $S$ of $P \eps P$;\\
\icc \quad Compute equivalent classes of nodes in $P$ based on $S$;\\
\icc \quad Create a node for each equivalent class in $P_m$;\\
\icc \quad Connect different equivalent classes by necessary edges in $P_m$;\\
\icc \quad Compute the intersection of interval bounds on pattern nodes in \\each equivalent class and put on the corresponding node in $P_m$;\\
\icc return $P_m$;\\
}
\vspace{-2.5ex}

\myhrule
}
\end{center}
\vspace{-4ex}
\caption{minP} \label{minP-alg}
\vspace{-3ex}
\end{figure}

%
We next present optimization techniques for algorithm \grouprec, by means of query minimization, as stated below, yielding the optimization algorithm \grouprecopt.

Query minimization is important for any query language. Minimizing pattern graphs is an effective way for improving the efficiency of querying data graphs. By Proposition~\ref{prop-pattern-consistency}, a pattern graph can be determined whether is satisfiable or not in quadratic time. Once we know a pattern graph is consistent, the $r$-simulation computing process can be optimized by minimizing the pattern graphs.

We say two pattern graphs $P$ and $P'$ are {\em equivalent via $r$-simulation}, denoted by $P\equiv P'$, iff for any data graph $G$, $P(G) = P'(G)$ via $r$-simulation. We say $P$ is {\em minimum} if for any other pattern graph $P'$ such that $P\equiv P'$, $|P|\leq |P'|$.

\eat{
\begin{theorem}
\label{thm-pattern-minimization-ap}
For any pattern graph $P$ and radius $r$, (1) there exists a unique minimum equivalent pattern graph $P_m$, via $r$-simulation with, that finds the same maximum match relation on any data graph; (2) taking the intersection of interval bounds on pattern nodes in each equivalent class in $P_m$, and putting it on the corresponding pattern node in $P_m$, $P$ and $P_m$ are equivalent via $r$-simulation; and (3) there exists a quadratic time algorithm to find its minimum equivalent pattern graph.
\end{theorem}
}

\begin{theorem}
\label{thm-pattern-minimization-ap}
For any pattern graph $P(V_p, E_p)$ and radius $r$, (1) there exists a unique minimum equivalent pattern graph $P_m$ via $r$-simulation;
and (2) there exists an algorithm that finds $P_m$ in $((|V_p|+|E_p|)^2)$ time.
\end{theorem}

\eat{
\stitle{Remarks}.
(1) A pattern graph $P$ may have multiple minimum equivalent pattern graphs $P_m^1$, $P_m^2$,..., $P_m^k$, of the same size but are not isomorphic to each other. Their structures must be exactly same, while the capacity on the corresponding nodes may be different, but they still return the same match result on any data graph.
%
(2) There exists method to get a unique minimum equivalent pattern graph, which takes linear time. Is unifying step necessary? Adopt or not?
}

\etitle{Algorithm \minp} As a proof of Theorem~\ref{thm-pattern-minimization}, we present Algorithm \minp to minimize pattern graphs as shown in Fig.~\ref{minP-alg}. It takes as input a pattern graph $P$, and outputs a minimum equivalent pattern graph $P_m$ of $P$ via graph simulation and some capacity bound computing. For any pattern graph $P$, it first checks to see whether $P$ is consistent. If the answer is yes, it then executes the following minimization steps. In the minimization process, It first computes the maximum match relation $R$ by treating $P$ as both a pattern and a data graph(line 2). It then computes equivalent classes for nodes in $P$ such that $u$ and $v$ are in the same class iff both $(u, v)\in R$ and $(v, u)\in R$ (line 3). Finally, it constructs the minimum equivalent pattern graph $P_m$ as follows (lines 4-6).(a) For each equivalent class \kw{eq}, it creates a node \kw{eq} for $P_m$; (b) there is an edge (\kw{eq}, \kw{eq'}) in $P_m$ iff there exist nodes $u \in \kw{eq}$ and $u' \in \kw{eq'}$ such that there is an edge $(u, u')$ in $P_m$; and (c) it computes the intersection of capacity bounds on pattern nodes in each equivalent class \kw{eq} and put on the corresponding node \kw{eq} in $P_m$.

\eat{%%%%%%%%%%%EAT
\begin{figure}[tb!]
\vspace{-2ex}
\begin{center}
{\small

\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Pattern graph $P(V_p$, $E_p$, $l_p$, $f_p)$.\\
{\sl Output:\/} A minimum equivalent pattern graph $P_m$ of $P$.\\
\bcc \quad if $P$ is not a consistent pattern graph then return null.\\
\icc \quad Compute the maximum match relation $R$ of $P \eps P$;\\
\icc \quad Compute equivalent classes of nodes in $P$ based on $R$;\\
\icc \quad Create a node for each equivalent class in $P_m$;\\
\icc \quad Connect different equivalent classes by necessary edges in $P_m$;\\
\icc \quad Compute the intersection of interval bounds on pattern nodes in \\each equivalent class and put on the corresponding node in $P_m$;\\
\icc return $P_m$;\\
}
\vspace{-2.5ex}

\myhrule
}
\end{center}
\vspace{-4ex}
\caption{\minp} \label{minP-alg}
\vspace{-3ex}
\end{figure}
}%%%%%%%%%%%%%EAT

\begin{example}
Takes as input the pattern graph $P_3$ given in Fig.~\ref{fig-consistency-example}. Algorithm works as follows. By Proposition~\ref{prop-pattern-consistency}, it determines that $P_3$ is a consistent pattern graph. In the minimization process, it first computes the maximum match relation $S$ by taking $P_3$ as both pattern and data graph, producing $S$ = \{$(A, A)$, $(B_1, B_2)$, $(B_2, B_1)$, $(C_i, C_j)$\} ($i,j \in [1,3]$). It then computes three equivalent classes: $\kw{eq_A}$=\{$A$\}, $\kw{eq_B}$=\{$B_1, B_2$\}, and $\kw{eq_C}$=\{$C_1, C_2, C_3$\}. Finally, it constructs the minimum equivalent pattern graph $P_m$ of $P$, as shown in Fig.~\ref{fig-consistency-example}. (a) For each equivalent class $\kw{eq_A}$, $\kw{eq_B}$ and $\kw{eq_C}$, it creates node labeled with $A$, $B$, and $C$ respectively; (b) it creates an edge $(A,B)$ connecting the class nodes of $\kw{eq_A}$ and $\kw{eq_B}$ in $P_m$, as there exists an edge $(u,v)$ in $P_3$ with $u \in \kw{eq_A}$ and $v \in \kw{eq_B}$, the same for edge $(B,C)$; and (c) for equivalent class $eq_B$, it computes the intersection of interval bounds on pattern nodes in it, that is, $[1,3]\cap[2,5] = [2,3]$, and [1,1], [3,4] for $eq_A$, $eq_C$. At last it puts them on the corresponding nodes in $P_{3m}$.
\end{example}

\etitle{Correctness and Complexity}. The correctness of Algorithm \minp is assured by the following. (1) $P_m \equiv P$, ensuring they return exactly the same result on any data graph; and (2) $P_m$ is minimum in size, \ie there is no other equivalent query $P'$ smaller than $P_m$.

Algorithm minP is in $O((|V_p|+|E_p|)^2)$ time. Indeed, step 1 (line 2), 2 (line 3), 3 (line 4-5) and 4 (line 6) of minP take $O((|V_p|+|E_p|)^2)$ time, $O(|V_p|^2)$ time, $O(|E_p|)$ time and $O(|V_p|^2)$ time, respectively.

Besides, algorithm \grouprecopt builds balls only using the set of data nodes with labels included in pattern nodes, instead of using all data nodes, which is an effective improvement for algorithm \grouprec.

\eat{
\stitle{Algorithm $\incgrpat^+$}

\begin{figure}[hb!]
\vspace{-2ex}
\begin{center}
{\small

\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Pattern graph $Pt_i(V_{Pt_i}$, $E_{Pt_i})$, data ball $\ball{w,r}$, $mat_i(\cdot)$,\\ and an edge $e=(u,u')$ to be inserted into $Pt_i$.\\
{\sl Output:\/} The updated match relation $mat_i(\cdot)$.\\
\bcc \quad $AFNode:=\emptyset$;\\
\icc \quad for each node $v \in mat_i(u)$ do\\
\icc \quad\quad if there is no $v' \in mat_i(u')$ with $(v, v')\in V_{\hat{G}}$\\
\icc \quad\quad then $AFNode:=AFNode \cup \{v\}$;\\
\icc \quad for each node $v' \in mat_i(u')$ do\\
\icc \quad\quad if there is no $v \in mat_i(u)$ with $(v', v)\in V_{\hat{G}}$\\
\icc \quad\quad then $AFNode:=AFNode \cup \{v'\}$;\\
\icc \quad for each node $v \in AFNode$ do\\
\icc \quad\quad $wSet:=\emptyset$;\\
\icc \quad\quad for each adjacent edge $(v,v')$ of $v$ do\\
\icc \quad\quad\quad for all $(u,u')\in E_p$ having $v \in mat_i(u)$ and $v'\in mat_i(u')$ do\\
\icc \quad\quad\quad\quad if $adjacent(l_p(u),v')\cap mat_i(u)=\emptyset$ then\\
\icc \quad\quad\quad\quad\quad $wSet$.push($(u',v')$);\\
\icc \quad\quad\quad\quad\quad while ($wSet\neq \emptyset$) do\\
\icc \quad\quad\quad\quad\quad\quad $(u',v'):=wSet$.pop();\\
\icc \quad\quad\quad\quad\quad\quad $mat_i(u')=mat_i(u')\backslash\{v'\}$;\\
\icc \quad\quad\quad\quad\quad\quad for all $(u',u'')\in E_p$ do\\
\icc \quad\quad\quad\quad\quad\quad\quad for all $v''\in adjacent(l_p(u''),v')\cap mat_i(u'')$ do\\
\icc \quad\quad\quad\quad\quad\quad\quad\quad if $adjacent(l_p(u'),v'')\cap mat_i(u')=\emptyset$ then \\
\icc \quad\quad\quad\quad\quad\quad\quad\quad\quad $wSet$.push($(u'',v'')$);\\
\icc if there is a pattern node $u$ having $|mat_i(u)| = 0$ then $mat_i=\emptyset$\\
\icc return $mat_i(\cdot)$;
}

\vspace{-2.5ex} \myhrule
}
\end{center}
\vspace{-4ex}
\caption{$\incgrpat^+$} \label{incpat-unit-insert}
\vspace{-3ex}
\end{figure}
}

\stitle{Linear $2$-approximation for density upper bounding}.
Given a ball $\ball{v,r}$ in $G$ and a pattern $P$, it computes density bound $ub$ to the perfect graph $\hat{G}_s$ of $P$ in $\ball{v,r}$ in $O(|\ball{v,r}|)$ time, such that $\kw{den}(\hat{G}_s) \leq d_{\kw{max}} \leq ub$, where $\kw{den}(\hat{G}_s)$ is the density of $\hat{G}_s$ and $d_{\kw{max}}$ is the density of the densest subgraph of $\ball{v,r}$.
Therefore, we can treat $ub$ as an upper bound on the density of $\hat{G}_s$. More specifically, it computes the $ub$ in three steps, as follows.

\sstab (1) Filter out to get a subgraph $\hat{G}_P$ from ball $\ball{v,r}$ such that $\hat{G}_P$ contains nodes with labels appeared in $P$ only, and the induced edges, in $O(|\ball{v,r}|)$ time.

\sstab (2) Compute the density $d$ of the {\em maximum core} of $\hat{G}_P$ in $O(|\hat{G}_P|)$ time.

\sstab (3) Return $2d$ as the density upper bound for $\hat{G}_s$ in $\ball{v,r}$.

Here the maximum core of a graph $G$ is defined as follows~\cite{EVMK12}.
A $l$-core of a graph $G$ is a subgraph $G_l$ of $G$ such that, each node in $G_l$ has degree no smaller than $l$.
A maximum core of a graph $G$ is a $l$-core $G_l$ of $G$ such that, for any non-empty $l'$-core $G_{l'}$ of $G$, $l'\leq l$. It is known that the maximum core of a graph $G$ can be computed in $O(|G|)$ time.

The following result ensures the above linear time algorithm returns $ub$ with the property claim above.

\begin{prop}
\label{prop-approximation-bound}
Given a graph $G$, let $d$ be the density of the maximum core of $G$, and $d_{\kw{max}}$ is the density of the densest subgraph of $G$, then $d\leq d_{\kw{max}} \leq 2d$.
\end{prop}

\subsection{NP-hardness}

We first formulate the {\em optimal $m$-fragmentation problem} ($\kw{OFGP}(P,m)$) as a bi-criteria optimization problem as follows.
\bi
\item Input: pattern graph $P$, an integer $m$.
\item Output: an $m$-fragmentation ${\cal P}_{m}$ composed of ${Pf}_1$, \ldots, ${Pf}_m$ and $F$ of $P$ such that (a) $\max_i |{Pf}_i|$ = $\max_i (|V_{{Pf}_i}| + |E_{{Pf}_i}|)$ is minimized; and (b) $|F|$ is minimized.
\ei
%Here $w(u)$ (resp. $w(e)$) is to represent the probability that a pattern update was applied to node $u$ (resp. edge $e$) in, \eg history pattern update workload, and can be set to 1 if no historical information is known.
That is, the problem is to implement the ``divide and conquer'' incremental strategy of the framework by finding a good $m$-fragmentation ${Pf}_1$, \ldots, ${Pf}_m$ and $F$ of the pattern graph such that
(i) the chances of the fragments ${Pf}_i$ to be updated are roughly the same, which further guarantees that the update time on any pattern fragment ${Pf}_i$ will be roughly equal, and the update time in all fragments is also minimized; and
(ii) the size of $F$ is also minimized such that the combination cost is minimized.

The decision version of $\kw{OFGP}(P, m)$, denoted by $\kw{dOFGP}(P, m, r_1, r_2)$, is to decide whether there exists a fragmentation ${Pf}_1$, \ldots, ${Pf}_m$ and $F$ such that, (a) $\max_i |{Pf}_i| \leq r_1\cdot\frac{|P|}{m}$ and (b) $|F|\leq r_2|P|$.
The corresponding single-criteria {\em cut}-minimization (resp. {\em fragment}-minimization) problem of $\kw{OFGP}(P, m)$, denoted by $\kw{OFFGP}(P, m, r)$ (resp. $\kw{OPFGP}(P, m, r)$), is to find an $m$-fragmentation ${Pf}_1$, \ldots, ${Pf}_m$ and $F$ such that $\max_i |{Pf}_i| \leq r\cdot\frac{|P|}{m}$ (resp. $|F|\leq r\cdot |P|$) and $|F|$ (resp. $\max_i |{Pf}_i|$) is minimized.

The problems are hard, as shown below.

\begin{prop}
\label{thm-fragmentation-hardness}
(1) $\kw{dOFGP}(P, m, r_1, r_2)$ is \NP-complete. It remains \NP-hard even $m$ = 2.

\sstab (2) Both $\kw{OFFGP}(P, m, r)$ and $\kw{OPFGP}(P, m, r)$ are \NPO-hard.
\end{prop}

Here \NPO is the class of all \NP optimization problems. An
\NPO-complete problem is \NP-hard to optimize, and is among the
hardest \NP optimization problems.

\begin{proofS}
(1) We show $\kw{dOFGP}$ is in \NP by giving an \NP algorithm that first guesses an $m$-cut $F$, and then check whether it divides $P$ into an $m$-fragmentation ${Pf}_1$, \ldots, ${Pf}_m$ such that $\max_i |{Pf}_i| \leq r_1\frac{|P|}{m}$ and $|F|\leq r_2|P|$. We show it is \NP-hard by reduction from the {\sc Minimum Bisection} problem, which is known \NP-hard even when $k=2$.
(2) We shown both $\kw{OFFGP}(P, m, r)$ and $\kw{OPFGP}(P, m, r)$ are \NPO-hard by proving that it is \NP-hard to decide whether there exists a feasible solution to both of them ({\bf To be verified}).
Indeed, there is no polynomial time approximation algorithm can guarantee a finite approximation ratio for $\kw{OFFGP}(P,m,r=1)$~\cite{AndreevR06}.
\end{proofS}

In light of Theorem~\ref{thm-fragmentation-hardness}, we give a heuristic algorithm, denoted by \kw{PFrag} and shown in Fig.~\ref{alg-PFrag}, for $\kw{OFGP}(P,m)$.
Algorithm \kw{PFrag} works by connecting $\kw{OFGP}(P,m)$ to the {\sc $(k, \nu)$-Balanced Partition} problem, which is to divided the vertices of a graph into $k$ components such that each component is of size more than $\nu\cdot\frac{n}{k}$, so that the number of edges between different compopents is minimized. The $(k,\nu)$-balanced partition problem, though is not approximable in general, has a number of sophisticated heuristic algorithms~\cite{AndreevR06}.

%%%%%%%%%%%%%%%%%%%%%Algorithm PFrag
\begin{figure}[t]
\begin{center}
{\small
\begin{center}
\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} \= Pattern graph $P$, integer $m$.\\
{\sl Output:\/} An $m$-fragmentation ${Pf}_1$, \ldots, ${Pf}_m$, $F$ of $P$.\\
\stab \bcc \hspace{0.5ex} \= $k$ = $m$; $\nu$ = $m$; $M_P$ = $|P|$; $M_F$ = 0;\\
\icc \> $({Pf}^\nu_1, \ldots, {Pf}^\nu_m, F^\nu)$ := $\kw{BalanceP}(k,\nu)$; \\
\icc \> $M^\nu_P$ := $\kw{max}\{|{Pf}^\nu_1|, \ldots, |{Pf}^\nu_m|\}$; $M^\nu_F$ = $|F^\nu|$;\\
\icc\> \While $\kw{max}\{M_P, M_F\} > \kw{max}\{M^\nu_P, M^\nu_F\}$ \Do\\
\icc \>\hspace{2ex}\= ${Pf}_1$ := ${Pf}^\nu_1$, \ldots, ${Pf}_m$ := ${Pf}^\nu_m$;\\
\icc \>\hspace{2ex}\= $F$ := $F^\nu$; $M_P$ := $M^\nu_P$; $M_F$ := $M^\nu_F$;\\
\icc \>\> \If $M^\nu_P \geq M^\nu_F$ \Then $\nu := \frac{\nu}{2}$ \Else $\nu := \frac{3\nu}{2}$;\\
\icc \>\> $({Pf}^\nu_1, \ldots, {Pf}^\nu_m, F)$ := $\kw{BalanceP}(k,\nu)$;\\
\icc \>\> $M^\nu_P$ := $\kw{max}\{|{Pf}^\nu_1|, \ldots, |{Pf}^\nu_m|\}$; $M^\nu_F$ = $|F^\nu|$;\\
\icc \> \Return ${Pf}_1$, \ldots, ${Pf}_m$, $F$;
}
\vspace{-2.5ex} \myhrule
\end{center}
}
\end{center}
\vspace{-4ex}
\caption{Algorithm \kw{PFrag} \label{alg-PFrag}}
\vspace{-3ex}
\end{figure}

Given a pattern $P$ and an integer $m$, algorithm \kw{PFrag} finds an $m$-fragmentation for $P$ by recursively invoking algorithm $\kw{BalanceP}(k,\nu)$ for the {\sc $(k,\nu)$-Balanced partition} problem with different $\nu$, such that the final returned $m$-fragmentation strikes a balance between the size of each fragment ${Pf}_i$ of $P$ and the size of the cut $F$.
More specifically, \kw{PFrag} maintains $M_P$ and $M_F$ as the size of the maximum fragment of ${Pf}_i$  and the size of the cut in the $m$-fragmentation, respectively. Initially, it sets $M_p$ to $|P|$ and $M_F$ to 0 (line~1).
It then invokes \kw{BalanceP} with both $k$ and $\nu$ being $m$, \ie has no constraints on the size of fragments of $P$ (line~2).
After that, it iteratively checks whether the generated $m$-fragmentation can be improved (line~4) by adjusting $m$ in a {\em binary search style} (lines~4-9). If the current size of maximum fragment $M^\nu_P$ is no smaller than the size $M^\nu_F$ of the cut, it invokes \kw{BalanceP} with $m$ and $\frac{\nu}{2}$, and with $m$ and $\frac{3\nu}{2}$ otherwise (line~7). It returns the $m$-fragmentation if it cannot be improved anymore in this way (line~10).

\stitle{Correctness \& Complexity}.
The correctness is obvious as \kw{PFrag} always returns $m$-fragmentations.
Algorithm~\kw{PFrag} runs in $O(\log m\cdot t_{\kw{BalanceP}})$ time, where $t_{\kw{BalanceP}}$ is the complexity of the algorithm for the {\sc $(k,\nu)$-Balanced Partition} problem. Indeed, \kw{PFrag} calls at most $\log m$ times \kw{BalanceP}.\\

\stitle{Remark}. Given pattern $P$, an $m$-fragmentation ${\cal P}_{m}$ of $P$, a data
graph $G$ and $\tilde{M}(P,G)$, one can construct \matchindex of $O(2^{m} + |V|)$ bits
 within $O(|V|)$ time.

\subsection{Proof of Proposition~\ref{thm-inc-grouprec-pat}}

\begin{figure}[tb!]
\label{fig-inc-complexity-data}
\begin{center}
\includegraphics[scale=0.3]{./fig/inc-complexity-proof-data.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of single data update}
\vspace{-5ex}
\end{figure}

To show the unboundedness, we need to define what is an allowed algorithm to be discussed.  Here we adopt the notion of LP (locally persistent) graph algorithms \cite{Reps96} for proving unboundedness of graph algorithms.

The proof strictly follows the one in \cite{Reps96}.

\etitle{(1) \dyngr is unbounded for single data update}.
Following \cite{Reps96, FanWW13-tods}, consider the following pattern and data graphs, and single data updates. Let data graph $G$ consist of two chains ($a_1$, $b_1$, $c_1$, \ldots, $a_n$, $b_n$, $c_n$) and ($a_{n+1}$, $b_{n+1}$, $c_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$) where $a_i$, $b_i$ and $c_i$ have labels $A$, $B$ and $C$ respectively. Let pattern graph be a triangle with nodes $a$, $b$ and $c$ (labels are $A$, $B$ and $C$ respectively). Consider two single-edge insertions $\delta_1$ = ($c_n$, $a_{n+1}$) and $\delta_2$ = $(c_{2n}, a_1)$. Let $k = 1$ and $r$ = $6n$. Let $H_1$ and $H_2$ denote the graphs $G\oplus \delta_1$ and $G\oplus \delta_2$, respectively. Obviously, $PG_1(P, G) = PG_1(P, H_1) = PG_1(P, H_2) = \emptyset$, while $PG_1(P, H_1\oplus \delta_2) \neq \emptyset$. Assume that there exists a locally persistent incremental algorithm ${\cal A}$ for \dyngr. Let $Trace(G', \delta')$ denote the sequence of steps executed by the algorithm in processing some change $\delta'$ to some graph $G'$. Now consider the following two instances: the application of update $\delta_2$ to $G$ and the application of update $\delta_2$ to graph $H_1$. Obviously, the update procedure must behave differently in these two cases, and $Trace(G, \delta_2)$ must be different from $Trace(H_1, \delta_2)$ (because many vertices of $H_1\oplus \delta_2$ are affected, while no node in $G\oplus \delta_2$ is affected). Since a locally persistent algorithm makes use of no global storage, this can happen only both $Trace(G, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in the graphs $G$ and $H_1$. However, $H_1$ was obtained from $G$ by applying change $\delta_1$. Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $G$. Therefore, $Trace(G, \delta_1)$ must also contain a visit to node $w$. As a characteristic of locally persistent algorithms is that if a vertex $w$ is visited during the updating of applying change $\delta'$ to graph $G'$, then every node in some path in $G'$ from a modified node of $\delta'$ to $w$ must have been visited.
Therefore, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ both contain a visit to $w$, from the nodes in $\delta_1$ and $\delta_2$, respectively. Thus, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ include visits to every node on some path from $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$ respectively. Hence, the time taken for processing change $\delta_1$ to $G$ plus the time taken for processing change $\delta_2$ to $G$ must be no smaller than the distance between $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$, \ie $n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1. Thus, the algorithm is not a bounded locally persistent incremental algorithm, which contradicts the assumption. That is, \dyngr is unbounded even for $k=1$ and single data update.

\begin{figure}[tb!]
\label{fig-inc-complexity-pattern}
\begin{center}
\includegraphics[scale=0.3]{./fig/inc-complexity-proof-pattern.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of single pattern update}
\vspace{-5ex}
\end{figure}

\etitle{(2) \dyngr is unbounded for single pattern update}.
Consider the following pattern and data graphs, and single pattern updates. Let data graph $G$ be a cycle ($a_1^G$, $b_1^G$, $c_1^G$, $d_1^G$, \ldots, $a_m^G$, $b_m^G$, $c_m^G$, $d_m^G$, $a_1^G$), where $a_i$, $b_i$, $c_i$ and $d_i$ have labels $A$, $B$, $C$ and $D$ respectively. Let pattern graph be a cycle ($a_1$, $b_1$, $c_1$, $d_1$, \ldots, $a_n$, $b_n$, $c_n$, $d_n$, $a_{n+1}$, $b_{n+1}$, $c_{n+1}$, $d_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$, $d_{2n}$, $a_1$) and two extra edges ($a_1$, $c_1$) and ($b_{n+1}$, $d_{n+1}$), where $a_i$, $b_i$, $c_i$ and $d_i$ have labels $A$, $B$, $C$ and $D$ respectively. Consider two single-edge deletions $\delta_1$ = ($a_1$, $c_1$) and $\delta_2$ = ($b_{n+1}$, $d_{n+1}$). Let $k = 1$ and $r$ = $4m$. Let $H_1$ and $H_2$ denote the graphs $P\oplus \delta_1$ and $P\oplus \delta_2$, respectively. Obviously, $PG_1(P, G) = PG_1(H_1, G) = PG_1(H_2, G) = \emptyset$, while $PG_1(H_1\oplus \delta_2, G) \neq \emptyset$. Assume that there exists a locally persistent incremental algorithm ${\cal A}$ for \dyngr. Let $Trace(P', \delta')$ denote the sequence of steps executed by the algorithm in processing some change $\delta'$ to some graph $P'$. Now consider the following two instances: the application of update $\delta_2$ to $P$ and the application of update $\delta_2$ to graph $H_1$. Obviously, the update procedure must behave differently in these two cases, and $Trace(P, \delta_2)$ must be different from $Trace(H_1, \delta_2)$ (because many vertices of $H_1\oplus \delta_2$ are affected, while no node in $P\oplus \delta_2$ is affected). Since a locally persistent algorithm makes use of no global storage, this can happen only both $Trace(P, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in the graphs $P$ and $H_1$. However, $H_1$ was obtained from $P$ by applying change $\delta_1$. Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $P$. Therefore, $Trace(P, \delta_1)$ must also contain a visit to node $w$. As a characteristic of locally persistent algorithms is that if a vertex $w$ is visited during the updating of applying change $\delta'$ to graph $P'$, then every node in some path in $P'$ from a modified node of $\delta'$ to $w$ must have been visited.
Therefore, $Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ both contain a visit to $w$, from the nodes in $\delta_1$ and $\delta_2$, respectively. Thus, $Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ include visits to every node on some path from $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$ respectively. Hence, the time taken for processing change $\delta_1$ to $P$ plus the time taken for processing change $\delta_2$ to $P$ must be no smaller than the distance between $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$, \ie $n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1. Thus, the algorithm is not a bounded locally persistent incremental algorithm, which contradicts the assumption. That is, \dyngr is unbounded even for $k=1$ and single data update.

(1) and (2) together prove that \dyngr is unbounded even for $k=1$ and single pattern or data updates.

\subsection{Proof of Theorem~\ref{thm-fragmentation}}

The decision version of $\kw{OFGP}(P, m)$, denoted by $\kw{dOFGP}(P, m, r_1, r_2)$, is to decide whether there exists a fragmentation ${Pf}_1$, \ldots, ${Pf}_m$ and $F$ such that, (a) $\max_i |{Pf}_i| \leq r_1\cdot\frac{|P|}{m}$ and (b) $|F|\leq r_2|P|$.

\etitle{Upper bound}.
We show the \NP upper bound by providing an \NP algorithm to determine whether there exists an $m$-fragmentation of $P$. Given a pattern graph $P$, the algorithm works as follows.
\bi
\item Guess an $m$-fragmentation ${\cal P}_m$ of $P$;
\item check whether it satisfies restrictions of $r_1$ and $r_2$ (conditions (a) and (b) in the definition of decision problem $\kw{dOFGP}$, if so, return yes, otherwise go to the first step and guess another instance.
\ei

The algorithm is in \NP since step~2 can be checked in \PTIME (liner time, indeed).

\etitle{Lower bound}.
We next show that it is \NP-hard to determine whether there exists an $m$-fragmentation and remains \NP-hard even $m$ = 2, by reduction from the minimum cut problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/~viggo/wwwcompendium/node85.html}.

An instance of the minimum cut problem is given a undirected graph $H=(V,E)$ and a positive integer $k$, find a set $S \subseteq E$ of edges whose removal leaves two disjoint connected components, with $|S|\leq k$.

Given an instance of the minimum cut problem, we construct an instance of $m$-fragmentation problem, it can be achieved by taking $H$ as $P$, $m=2$, and setting $r_1=m$, $r2 = k/|P|$. Indeed, the minimum cut problem is a special case of the of $m$-fragmentation problem.

\subsection{Experiment}

\ni(1) {\em YouTube} provides a video network with video-video edges\footnote{\small http://netsg.cs.sfu.ca/youtubedata/} indicate recommendation relationships. We also used the undirected version of it, the edges between two videos indicate the correlate relationships. The dataset has 2,028,274 nodes and 12,218,972 edges, and we generated 403 labels according to the genre and age attributes of videos.

We generated the labels by the following routine. Each video in YouTube contains a set of attributes, \eg uploader, age, category, length. There are 13 categories in the data, and the age is calculated in terms of days. We classified the age into 31 periods, each contained 35 days. We then combined the period and the category attribute, get total 403 labels.

%\etitle{Multiple batch updates}. We secondly evaluated the performance of \optpatinc to process multiple batch updates. We fixed the number of hybrid unit updates in each batch update to be 3, and executed 5 batches one by one. We fixed the hybrid updates ratio with the same setting as in the hybrid updates experiment. X-axis represents the order of 5 batch updates, and Y-axis represents the elapsed time of each batch.
%
%The results are shown in Figures ~\ref{fig-exp-patinc-citation-multibatch}, ~\ref{fig-exp-patinc-youtube-multibatch} and ~\ref{fig-exp-patinc-synthetic-multibatch}. We find the following.
%(a) \optpatinc improves \grouprec by 12\% on on Citation and YouTube, 15\% on synthetic data in average for all batches.
%(b) The time increases with the coming of batch updates, while still pertains high efficiency in returning top-$k$ results. This justifies the effectiveness of {\em lazy update manner} developed in Section~\ref{subsubsec-affball}. Note that the case the elapsed time of \optpatinc surpasses \grouprec did not happen here. This is because even when all balls are identified as \affballsx, \optpatinc need not to process all accumulated pattern updates for them.
%Due to {\em update planner}, \optpatinc had already processed part of pattern updates for the set of \affballsx identified in the previous batches.
%(c) The time taken by \optpatinc on the 3$th$ batch update is the highest and further decreased a lot from the 4$th$ batch update. This is because all balls are identified as \affballsx on the 3$th$ batch update and the accumulated pattern updates stored in {\em update planner} are all processed. This makes the number of \affballsx identified and the elapsed time taken by \optpatinc on the 4$th$ batch update less. These justifies the effectiveness of the incremental model for pattern changes we have developed.

The results are shown in Figures ~\ref{fig-exp-patinc-citation-impper}, ~\ref{fig-exp-patinc-youtube-impper} and ~\ref{fig-exp-patinc-synthetic-impper}. We find the following.
(a) \kw{Affected} significantly improves \kw{Baseline} for 5 kinds of updates, especially for single-insertion updates. For multiple batch updates, \kw{Affected} outperforms \kw{Baseline} by 38\%, 54\% and 77\% on Citation, YouTube and synthetic data.
(b) \kw{ElrReturn} improves \kw{Baseline} a lot, especially for single-deletion updates. This is because more pattern nodes/edges removed from patterns will yield more results, which will enhance the pruning power.
(c) By utilizing the two techniques together, \grouprec outperforms \kw{Baseline} by 40\%, 56\% and 77\% on Citation, YouTube and synthetic data for multiple batch updates.

%\begin{figure*}[tb!]
%%\vspace{-2ex}
%\begin{center}
%
%\hfill
%\subfigure[{\small Real-life matches on Citation}]{\label{fig-exp-1-effect-citation}
%\includegraphics[scale=0.88]{./fig/exp-real-match-citation.eps}}
%\hfill
%\subfigure[{\small Vary $P$ (Citation)}]{\label{fig-exp-semantic-citation-density}
%\includegraphics[scale=0.39]{./fig/citation-semantic-density.eps}}
%\hfill
%\subfigure[{\small Vary $P$ (Citation)}]{\label{fig-exp-semantic-citation-capacity}
%\includegraphics[scale=0.39]{./fig/citation-semantic-capacity.eps}}
%\hfill
%\vspace{-2.5ex}
%
%\hfill
%\subfigure[{\small Vary $P$ (Citation)}]{\label{fig-exp-semantic-citation-link}
%\includegraphics[scale=0.39]{./fig/citation-semantic-link.eps}}
%\hfill
%\subfigure[{\small Vary $k$ (Citation)}]{\label{fig-exp-semantic-citation-density-varyk}
%\includegraphics[scale=0.39]{./fig/citation-semantic-density-varyk.eps}}
%\hfill
%\subfigure[{\small Vary $k$ (Citation)}]{\label{fig-exp-semantic-citation-capacity-varyk}
%\includegraphics[scale=0.39]{./fig/citation-semantic-capacity-varyk.eps}}
%\hfill
%\subfigure[{\small Vary $k$ (Citation)}]{\label{fig-exp-semantic-citation-link-varyk}
%\includegraphics[scale=0.39]{./fig/citation-semantic-link-varyk.eps}}
%\hfill
%\vspace{-2.5ex}
%
%\end{center}
%\vspace{-2.5ex}
%\caption{Performance evaluation of top-$k$ team formation semantic}
%\label{exp-semantic-effectiveness} \vspace{-2ex}
%\end{figure*}
%
%
%\begin{figure*}[tb!]
%%\vspace{-2ex}
%\begin{center}
%
%\hfill
%\subfigure[{\small Vary deletions (Citation)}]{\label{fig-exp-patinc-citation-del}
%\includegraphics[scale=0.314]{./fig/citation-pattern-deletion.eps}}
%\hfill
%\subfigure[{\small Vary insertions (Citation)}]{\label{fig-exp-patinc-citation-ins}
%\includegraphics[scale=0.314]{./fig/citation-pattern-insertion.eps}}
%\hfill
%\subfigure[{\small Vary capacity (Citation)}]{\label{fig-exp-patinc-citation-cap}
%\includegraphics[scale=0.314]{./fig/citation-pattern-capchange.eps}}
%\hfill
%\subfigure[{\small Vary hybrid updates (Citation)}]{\label{fig-exp-patinc-citation-hyb}
%\includegraphics[scale=0.314]{./fig/citation-pattern-hybrid.eps}}
%\hfill
%\subfigure[{\small Vary workloads (Citation)}]{\label{fig-exp-patinc-citation-multibatch}
%\includegraphics[scale=0.314]{./fig/citation-pattern-multi.eps}}
%\hfill
%\vspace{-2.5ex}
%
%\end{center}
%\vspace{-4ex}
%\caption{Performance evaluation of pattern incremental algorithms}
%\label{exp-patinc-efficiency} \vspace{-2ex}
%\end{figure*}
%
%
%\begin{figure*}[tb!]
%%\vspace{-2ex}
%\begin{center}
%
%\hfill
%\subfigure[{\small Vary data deletions (Citation)($\times 10^{4}$)}]{\label{fig-exp-datainc-citation-del}
%\includegraphics[scale=0.395]{./fig/citation-data-deletion.eps}}
%\hfill
%\subfigure[{\small Vary data insertions (Citation)($\times 10^{4}$)}]{\label{fig-exp-datainc-citation-ins}
%\includegraphics[scale=0.395]{./fig/citation-data-insertion.eps}}
%\hfill
%\subfigure[{\small Vary data hybrid updates (Citation)}]{\label{fig-exp-datainc-citation-hyb}
%\includegraphics[scale=0.395]{./fig/citation-data-hybrid.eps}}
%\hfill
%\subfigure[{\small Vary degree 1 (Synthetic)}]{\label{fig-exp-patinc-citation-multiworkload}
%\includegraphics[scale=0.395]{./fig/citation-pattern-multi.eps}}
%\hfill
%\vspace{-2.5ex}
%
%\end{center}
%\vspace{-4ex}
%\caption{Performance evaluation of data incremental algorithms}
%\label{exp-datainc-efficiency} \vspace{-2ex}
%\end{figure*}

%\etitle{Techniques comparison}. In this set of experiments we evaluated the effectiveness of (1)
%{\em affected balls identification}, and (2) {\em early-return strategy}. We implemented another three algorithms: (a) \kw{Baseline}, update $\tilde{M}(P,G)$ for all pattern updates and all balls in $G$; (b) \kw{Affected}, incorporating {\em affected balls} into \kw{Baseline}; (c) \kw{ElrReturn}, incorporating {\em early-return strategy} into \kw{Baseline}. Along with \grouprec, incorporating both {\em affected balls} and {\em early-return strategy} into \kw{Baseline}, we test to see the improved percentage of \kw{Affected}, \kw{ElrReturn} and \grouprec compared with \kw{Baseline}.

\subsection{To Read}

\stitle{Space analysis of all auxiliary structures}.

\etitle{Fragment-ball status index}. The time to construct Fragment-ball status index is bounded by $O(2^hh)$, and the storage space is $2^hh$, which is small compared to $G$ ($h$ is typically small, \eg 3 or 4, as shown in Section~\ref{sec-expt}). The index does not change during the following incremental process.

\etitle{Ball status index}. The time to construct Fragment-ball status index is bounded by $O(|V|)$, and the storage space is $3V$. The time to maintain the index is bounded by $O(||\affballsx||)$ ($||\affballsx||$ denotes the number of \affballsx). As it need to update the match status, \cflag and optional density bound \dens of each \affballx, after the incremental computation on partial match results.

\etitle{Fragment-ball matches}. The time to construct Fragment-ball matches is bounded by $O(|P|\Sigma_{v\in G}|\ball{v, r}|)$, and the storage space is $|P|\Sigma_{v\in G}|\ball{v, r}|$. Due to the cubic complexity, we adopt the storage strategy to bound the storage consumption within $|G|$. Given pattern update $\Delta P$ and data update $\Delta G$, the time to maintain the fragment-ball matches is bounded by $O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}(|\Delta P||M(P, \hat{G})|^2 + |P \oplus \Delta P||\affballsx|)$. Indeed, the time to maintain fragment-ball matches by refining on previous stored matches in processing certain updates in $\Delta P$ is bounded by $O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}(|\Delta P||M(P, \hat{G})|^2)$, and the time to maintain fragment-ball matches by recomputing matches in in processing certain updates $\Delta P$ and all updates in $\Delta G$ is bounded by $O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}(|P \oplus \Delta P||\affballsx|)$

\etitle{Ball filtering code}. The time to construct ball filtering code is bounded by $O(2^hh)$, and the storage space is $2^hh$. Given pattern update $\Delta P$, the time to maintain the code is in $O(2^h|\Delta P|)$. As for each single pattern update, the incremental process changes at most all $2^h$ type codes in the ball filtering code.

\etitle{Update planner}. The update planner is empty at beginning of the incremental process, it records the id of all single pattern updates. Given pattern update $\Delta P$, the time to maintain it is bounded by $O(|\Delta P|)$, and the storage space is $|\Delta P|$.

In summary, by storing the fragment-ball matches within storage size bound $|G|$, it can be assured the total size of auxiliary structure is $2^{h+1}h+|G|+3|V|+|\Delta P|$.

The time to construct them is bounded by $O(2^{h}h+|P|\Sigma_{v\in G}|\ball{v, r}|)$, and the time to maintain it is bounded by $O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}(|\Delta P||M(P, \hat{G})|^2 + |P \oplus \Delta P||\affballsx|)+2^h|\Delta P|)$

In the experiment, we find that at beginning of the incremental process, it takes 17MB and 120MB to store fragment-ball status index, ball status index and ball filtering code on Citation and synthetic data, compared to 36MB and 482MB to store the entire data graph. For storing fragment-ball matches, whose space complexity is rather higher, however, in practice, it cannot have that much matches due to the constraints carried by pattern graphs. It only takes 6MB and 4MB to store fragment-ball matches on Citation and synthetic data.

\stitle{The Facebook and Twitter statistics}.

We have conducted a survey on real-life network. The user increments on Facebook\footnote{\small http://www.statista.com/statistics/264810/number-of-monthly-active-facebook-users-worldwide/} and Twitter \footnote{\small http://www.statista.com/statistics/282087/number-of-monthly-active-twitter-users/} network daily reaches 1.23\textperthousand\ and 2.47\textperthousand. According to the statistics before, \datainc can process much more than 10\% increments at a high efficiency, which means \datainc can process the increments efficiently accumulated in 40 days and 81 days on Facebook and Twitter.

\stitle{The running example on incremental problem}.

\begin{example}
\label{exm-pattern-challenge-cp}
Consider pattern graph $P_1$ (without dashed lines) and data graph $G_1$ of Fig.~\ref{exm-motivation}, and fix $r=2$. When set $k=|V_{G_1}|=24$, meaning $PG_k(P,G)$ = $PG(P,G)$, \ie we have all perfect subgraphs as input for incremental process, that is the one resides in $\ball{SA_1, 2}$ and the other one in $\ball{SA_2, 2}$. For simplicity, we only consider the case there are no matched subgraphs in $G_1$, that satisfy the structural constraints but pruned by capacity constraints. We set $k'=1$, meaning we only want to find top-1 perfect subgraph in updated $P_1$ and $G_1$.

(1) When a pattern update comes, containing only an edge delete $(\kw{SD},\kw{ST})^-$, which will turn more unmatched nodes to matched. $\ball{SA_1, 2}$ and $\ball{SA_2, 2}$ certainly contain matches for the updated pattern structure but need recomputed for new matched nodes and further capacity constraint check. For all the other balls, the update will introduce matches within them and we need to compute for all.

(2) When a pattern update comes, containing only an edge insert $(\kw{BA},\kw{UD})^-$, which will turn matched nodes to unmatched, it means the balls do not have matches for $P$ will not have matches for the updated pattern graph. Therefore, we can get updated subgraphs by incremental computation on the results in $\ball{SA_1, 2}$ and $\ball{SA_2, 2}$.

(3) When a pattern update comes, containing only a capacity change on pattern node $\kw{UD}$, the lower bound changes from 1 to 2. We can get updated subgraphs by checking the results in $\ball{SA_1, 2}$ and $\ball{SA_2, 2}$.

(4) Consider another case when a data edge delete $(\kw{UD_5},\kw{ST_4})^-$ comes, which will turn matched nodes to unmatched. We need to identify the balls that are affected by the data changes, which can be time-consuming. However, if a ball do not have matches for $P$ in $G$, it cannot have matches for $P$ in the updated $G$, and do not need to check for new results.

(5) Consider another case when a data edge insert $(\kw{PM_3},\kw{BA_3})^+$ comes, which will certainly introduce new matches. We need to identify the balls that are affected by the data changes. Unlike the delete case, no matter a ball have matches or not for $P$ in $G$ may have matches for $P$ in the updated $G$, and should be checked for new results.

\end{example}

{\bf Section 3}:

In light of the challenges, we propose a unified incremental framework for $\dyngr$.
By designing novel auxiliary structures, the framework effectively localizes the impacts of pattern and data changes by (a) decomposing the maximum match relation $M(P, G)$ \wrt structure of pattern $P$ and balls in $G$, and (b) effectively restricting, localizing and locating impacts of changes to small parts of the decomposed $M(P,G)$.
More specifically, the structure contains two components: (1) {\em fragment-ball matches}, to achieve (a) decomposing and storing $M(P, G)$; and (2) index structures to achieve (b) identifying affected parts in the fragment-ball matches \wrt pattern and data changes.

The auxiliary structure is designed based on the following two observation.

\etitle{(1) The computation of graph simulation is decomposable}.
The computation of the match relation $R$ of a pattern $P$ in a data graph $G$ via graph simulation, which is the building block of $r$-simulation, is {\em decomposable} with {\em no overhead}. More specifically, we can compute $R$ in two phases:
we first break down $P$ into fragments $Pf_{1}$, \ldots, $Pf_{m}$, by removing a set $F$ of pattern edges; we then compute $R$ in two steps:
(a) computing match relation $R_{i}$ of $Pf_{i}$ in $G$ and (b) combining $R_{1}$, \ldots, $R_{m}$ into $R$ with $F$.
Indeed, both of the two steps can be implemented with the standard and fastest graph simulation algorithm~\cite{infsimu95}.
The benefit of this decomposed computation of $R$ is obviously: for any pattern changes, which has global impacts on $G$, we can restrict its impacts {\em within $R_{i}$}, where $R_{i}$ is the maximum match relation of $Pf_{i}$ in $G$. That is, instead of trying to recompute $R$ for $P$ and $G$ from scratch, by using $R_{1}$, \ldots, $R_{m}$, we can {\em control} the impacts of pattern changes, which are global with traditional approaches.
Moreover, this benefit comes with {\em no cost}. Indeed, let the computation cost (total steps) of steps (a) and (b) to be $C_{a}$ and $C_{b}$, and let $C$ be the cost of directly computing $R$ with $P$ and $G$, then by the nature of the graph simulation computation, one can verify that $C_{a} + C_{b} = C$, for any $P$, $G$ and any fragmentation $Pf_{1}$, \ldots, $Pf_{m}$ and $F$ of $P$.

This motivates us to store match relations with pattern fragments, instead of patterns as in conventional approaches. The framework makes use of this idea by maintaining the fragment-ball matches, which will be discussed later.

\etitle{(2) Impacts of pattern and data changes are localizable}.
Since the computation unit of $r$-simulation are balls of the data graph, and the impacts of pattern and data changes can be localized within those {\em affected balls}, who (a) are impacted by the changes and (b) have the possibility to contain match results. In other words, we only need to compute the new match relations in these affected balls. This gives us another dimension to localize the impacts of pattern and data changes, from the data graph perspective. The difficulty includes how to efficiently identify the affected balls, and how to update their match results \wrt pattern and data changes afterwards. This motivates us to devise index structures that organizes pattern fragments and balls effectively.

\begin{figure}[tb!]
\label{fig-framework}
\begin{center}
\includegraphics[scale=0.43]{./fig/inc-framework.eps}
\end{center}
\vspace{-3ex}
\caption{Incremental framework}
\vspace{-5ex}
\end{figure}

We are now ready to introduce the framework.

\stitle{Framework}. The framework, shown in Fig.~\ref{fig-framework}, consists of five components as follows.

\etitle{(1) Pattern fragmentation}, which breaks down the pattern graph into fragments while keeping its structure integrity.

\etitle{(2) Building auxiliary structures}, which initializes auxiliary structures to localize impacts of pattern and data changes.

\etitle{(3) Indentifying affected balls}, which makes use of the auxiliary structure to localizing the impacts.

\etitle{(4) Updating auxiliary structures}, which processes the auxiliary structure with pattern and data updates.

\etitle{(5) Combining partial results}, which combines processed partial matches to the final updated match results.

We below first present the auxiliary structures in Sections~\ref{subsubsec-fragmentation} and \ref{subsubsec-structure}. We then show how the framework handles the challenges with these structures in Section~\ref{subsubsec-handle}.

\subsubsection{Fragment-ball Matches}
\label{subsubsec-fragmentation}
We first discuss the pattern fragmentation (steps (1)) of the framework. Based on it, we then introduce the {\em fragment-ball match} structure.

\stitle{Fragment-ball matches}.
The {\em fragment-ball matches} $\tilde{M}(P,G)$ of pattern $P$ in data graph $G(V,E)$ \wrt $m$-fragmentation ${Pf}_1$, \ldots, ${Pf}_m$ is the set $\bigcup_{i\in[1,m], v\in V} M({Pf}_i, \ball{v,r})$, where $\ball{v,r}$ is the ball of $G$ with center $v$ and radius $r$, and $M({Pf}_i, \ball{v,r})$ is the maximum match relation of ${Pf}_i$ in ball $\ball{v,r}$.

Observe that, compared to $PG_k(P,G)$ or $M(P,G)$, $\tilde{M}(P, G)$ is much more informative to help localizing the impacts of pattern and data changes, and moreover, is of the same size asymptotically.

\subsubsection{Organizing Fragment-ball Matches}
\label{subsubsec-structure}

We next introduce the second part of the auxiliary structure, to organize the fragment-ball matches and to localize of impacts \wrt input changes.

\stitle{(1) Organize fragment-ball matches}.
Instead of storing fragment-ball matches $\tilde{M}(P, G)$ in a set, we organize $\tilde{M}(P, G)$ with two structures for the convenience of localizing the impacts in it.
More specifically, we use (a) {\em fragment-ball status index} and (b) {\em ball status index} to organize $\tilde{M}(P, G)$ in terms of the match status between balls and pattern fragments. We then link them to the fragment-ball matches, to form an integrated organization of $\tilde{M}(P, G)$, called {\em fragment-ball math struct}, denoted by \fb.

\etitle{Fragment-ball status index}. Given an $m$-fragmentation ${\cal P}_m$ of $P$, it consists of $2^m$ tuples of boolean values $(b_1, b_2, \ldots, b_m)$ that classify balls in $G$ \wrt ${\cal P}_m$, referred to as {\em type codes}, where each $b_i (i\in [1,m])$ is either 0 or 1,
such that, for each ball that are classified with type code $(b_1, b_2, \ldots, b_m)$, $b_i (i\in [1, m])$ is 1 if and only if $Pf_i$ has matches in it. Intuitively, it is to encode the match relationships between pattern fragments and balls, which will be used for organizing fragment-ball matches.

\etitle{Ball status index}. It consists of $|V_G|$ triples $(bid, cflag, den)$, where $bid$ is an integer recording the $id$ of a ball, $cflag$ is an integer recording the id of a pattern update , and $den$ is a natural number recording the density bound of the ball. The usage of $cflag$ and $den$ is illustrated in next section.

\etitle{Fragment-ball match struct} (\fb). We next link fragment-ball matches, fragment-ball status index and ball status index together, referred to as {\em fragment-ball match struct} and denoted by \fb, as follows.
For each type code $tc$ = $(b_{1}, \ldots, b_{m})$ in the fragment-ball status component, there is a link from $tc$ to a record in the ball status component for a ball $\ball{v,r}$ such that if $b_i$ is 1, then fragment ${Pf}_{i}$ of ${\cal P}_{m}$ has a match in $\ball{v,r}$, and we say that ball $\ball{v,r}$ is of type $tc$.
For each ball $\ball{v,r}$, there exists a pointer from the record of $\ball{v,r}$ in the ball status component to $M({Pf}_{i}, \ball{v,r}) (i\in [1, m])$ in $\tilde{M}(P,G)$, if it is associated to a type code $tc$ with $tc[i] = 1$, \ie $M({Pf}_{i}, \ball{v,r})$ is not empty.

\begin{example}
\label{exa-matchindex}
An example of \fbmatstruct is illustrated in Fig.~\ref{fig-auxstr-index}, with pattern graph $P_1$ (without dashed edges) and data graph $G_1$ in Fig.~\ref{exm-motivation}, $r=2$, $k=k'=2$, and $m=2$, \ie $P_1$ is divided into fragments $Pf_{1}$ and $Pf_{2}$ according to Algorithm \kw{PFrag} shown in Fig.~\ref{alg-PFrag}. \fbmatstruct consists of three parts: structure (i) the fragment-ball status index, structure (ii) the local status index and (iii) the fragment-ball matches.
In structure (i), there are $2^2=4$ type codes that classify balls of $G_1$ into 4 types.
For balls linked from type code (1, 1), \eg balls $\ball{\kw{SA_1},2}$ and $\ball{\kw{SA_2},2}$, there are matches to both $Pf_{1}$ and $Pf_{2}$ in them.
For balls connected to type code (1, 0), \eg ball $\ball{\kw{PM_2},2}$, as depicted in Fig.~\ref{exm-motivation}, the left part of the dashed vertical line (II) together with node \kw{SA_1} and the related edge. There exist matches for $Pf_{2}$, but no matches for $Pf_{1}$ in the ball.
For balls connected to type code (0, 1), \eg ball $\ball{\kw{SA_3},2}$, there exist matches for $Pf_{1}$, but no matches for $Pf_{2}$.
For balls connected to type code (0, 0), \eg ball $\ball{\kw{BA_3},2}$, there exist no match for either of $Pf_{1}$ or $Pf_{2}$. We only consider these 5 balls shown in the figure in the following.
\end{example}

\stitle{(2) Localizing impacts in fragment-ball matches}.
We next introduce the structure for identifying {\em affected balls}. We firstly give a formal definition of {\em affected balls} below. We then describe the structure, called {\em ball filtering code}.

\etitle{Affected balls}.
For any pattern $P$, $m$-fragmentation ${\cal P}_{m}$, data graph $G$, update $\Delta P$, update $\Delta G$, and fragment-ball matches $\tilde{M}(P,G)$,
we say a ball $\ball{v,r}$ is an {\em affected ball} \wrt $P$, ${\cal P}_{m}$, $G$, $\tilde{M}(P,G)$, $\Delta P$ and $\Delta G$, denoted by \affballx, if for any algorithm $\Gamma$
that takes as input $P$, ${\cal P}_{m}$, $G$, $\tilde{M}(P,G)$, $\Delta P$ and $\Delta G$,
and computes $P\oplus\Delta P(G\oplus\Delta G)$ by updating $\tilde{M}(P,G)$ in terms of balls, $\Gamma$ has to check for update in $M(P,\ball{v,r})$.
That is, \affballsx are balls of $G$ that have to be checked for update in {\em fragment-ball matches} by any correct pattern incremental algorithm in the presence of $\tilde{M}(P,G)$.

It is worth mentioned that a pattern edge/node insert will turn a matched node to unmatched, and a pattern edge/node delete will turn a unmatched node to matched.
Given a pattern fragmentation $Pf_{1}$, \ldots, $Pf_{m}$ of $P$, $\Delta P$ and a ball $\ball{v,r}$, if there exists a perfect subgraph in $\ball{v,r}$ for $P \oplus P$, then the following is true.
Suppose (1) $\Delta P$ contains (a) only an edge/node insert on $Pf_{1}$, (b) only a capacity change or (c) only an edge insert/delete on the cut edges, there exist (partial) matches for each fragment of $P$ in $\tilde{M}(P,G)$;
(2) $\Delta P$ contains only an edge/node delete on $Pf_{1}$, there exist (partial) matches for $Pf_{2}$, \ldots, $Pf_{m}$ of $P$ in $\tilde{M}(P,G)$;

The framework utilizes this idea to filter out balls cannot match with $P \oplus P$, based on the current partial match status, and regard the other candidate balls who may contain perfect subgraphs as {\em affected balls}. It restrict the pattern change impact from global to local, by turning the incremental computation for all balls to {\em affected balls} in $G$.

According to \fbmatstruct, all balls in $G$ are classified to $2^m$ types. For pattern update $\Delta P$, we will next present the auxiliary structure {\em ball filtering code} to identify \affballsx \wrt $\Delta P$, referred to as \ballfilter.
More specifically,  \ballfilter is used to encode whether $\Delta P$ causes a need to update $\tilde{M}(P,G)$ and further whether causes a visit to a ball in $G$.

\etitle{Ball filtering code} (\ballfilter).
Given an $m$-fragmentation ${\cal P}_{m}$ of pattern $P$, and $\Delta P$, \ballfilter for $P$ \wrt $\Delta P$ consists of $2^{m}$ tuples of $m$-bit boolean strings, referred to as {\em filtering codes}. They are all initially set to $fc=\underbrace{11\ldots 1}_{m}$, corresponding to a type code in {\em fragment-ball status index}, and are updated for all unit update $\delta$ in $\Delta P$:
(i) when $\delta$ is a single-node delete $(u)^{-}$ or a single-edge delete $(u_{1}, u_{2})^{-}$ to fragment ${Pf}_{i}$ of ${\cal P}_{m}$, the $i$-th bit of the ball filtering code for $P$ is set to 0; otherwise, (ii) \ballfilter remains unchanged.

For data update $\Delta G$, the ball based team formation semantic provides the convenience for localizing data change impacts, allowing us to find the set of affected balls, and only compute matches within them. The method to identify \affballsx \wrt $\Delta G$ involves some structural computation on $G$, which will be shown in in Section~\ref{sec-IncAlg}.

\begin{example}
\label{exa-ball-filtering-code}
An example of \ballfilter is illustrated in Fig.~\ref{fig-inc-maintain-unit}, with pattern graph $P_1$ and data graph $G_1$ in Fig.~\ref{exm-motivation}. The \ballfilter contains $2^{2}=4$ $2$-bit boolean strings and are all initialized to be $11$, as shown in the first column in the \ballfilter table. When a batch update $\Delta P_1$ comes, which contains one single update $\delta_1$, a single-edge deletion $(\kw{SD},\kw{ST})^-$, which is included in $Pf_{1}$. Thus all the 4 boolean strings change to 10, as shown in the second column.

Consider another case a batch update $\Delta P_5$ comes, which contains two single update $\delta_1$ and $\delta_2$, a single-edge deletion $(\kw{SD},\kw{ST})^-$ in $Pf_{1}$ and a single-edge insert $(\kw{BA},\kw{UD})^+$ in $Pf_{2}$. The \ballfilter changes as shown in the second column in Fig.~\ref{fig-inc-maintain-batch}, the 4 boolean strings are also 10, which is same with the former case as the edge insert does not change \ballfilter.

Consider the third case a data edge insert $(\kw{PM_3},\kw{BA_3})^+$ comes, the match results must be contained in (1) the balls with type code (1,1), and (2) the balls centered with $\kw{SA_3}$, $\kw{PM_3}$, $\kw{UD_4}$, $\kw{BA_3}$ and $\kw{UD_5}$. For (1), we only need to retrieve partial match results from $\tilde{M}(P,G)$ and compute to get final results; for (2), we need to access $G$ to update the partial results in $\tilde{M}(P,G)$ and further compute to get final results. The method to identify \affballsx for $\Delta G$ will be discussed later.
\end{example}

\eat{%%%%%%%%%%%
a triple $B_{i}(\checkflag,
\dens, \densityflag)$ for ball $B_{i}$ (suppose balls in $G$ are numbered from $1$ to $V$), such that, $B_{i}[\checkflag]$ recors which update in $\Delta P$ has been processed up by the last time when the $i$-th ball in $G$ is treated as an \affball when processing updates in $\Delta P$ one by one; $B_{i}[\dens]$ records the density of ball $B_{i}$, which will be used later to optimize the process of reusing results in $\tilde{M}(P,G)$; and $B_{i}[\densityflag]$ records a flag denoting whether we need to refresh the $B_{i}[\dens]$ or not.
For each type code $tc$ = $(b_{1}, \ldots, b_{m})$ in the fragment-ball status component, there is also a link from $c$ to records in the local status component for balls $B_{i}$ such that fragment $P_{i}$ of ${\cal P}_{m}$ has a match in $B_{i}$, and say that ball $B_{i}$ is of type $tc$.
For each ball $B_{i}$ ($i\in [1, |V|])$, there exists a pointer from the record of $B_{i}$ in the local status component to $M(P_{j}, B_{i}) (j\in [1, m])$ if it is associated to a type code $tc$ with $tc[P_{j}] = 1$, \ie
$M(P_{j}, B_{i})$ is not empty.
}%EAT%%%%%%%%%%%

%Based on ${\cal P}_{m}$ and $\tilde{M}(P,G)$, we are readily to define the notion of {\em affected balls} \wrt $\Delta P$ and $\Delta G$.

\stitle{Auxiliary structure storage principle}. One typically has a budget on the size of space that can be used for storing auxiliary structure. We set the space bound to $C\cdot |G|$, where $C$ is small.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
\begin{center}
\hspace{-4ex}
\subfigure{\label{fig-auxstr-index}
\includegraphics[scale=0.56]{./fig/fig-auxstr-index.eps}}
\subfigure{\label{fig-inc-maintain-unit}
\hspace{-1.5ex} \vrule \hspace{0.3ex} \hfill
\includegraphics[scale=0.55]{./fig/fig-inc-maintain-unit.eps}}
\subfigure{\label{fig-inc-maintain-batch}
\hspace{-1.5ex} \vrule \hspace{0.3ex} \hfill
\includegraphics[scale=0.55]{./fig/fig-inc-maintain-batch.eps}}
\caption{Auxiliary data structures}
\label{fig-auxiliary-data-structures}
\end{center}
\vspace{-4ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Handling challenges}
\label{subsubsec-handle}

With the auxiliary structures, the framework can achieve the following.
%, which solves the challenges raise at the beginning of the section.

\begin{theorem}
\label{thm-pattern-incremental}
For any pattern $P$, an $m$-fragmentation ${\cal P}_{m}$ of $P$, and data graph $G$,
with the auxiliary structure, there exists an incremental algorithm underlying the framework for \dyngr such that, for any batch update $(\Delta P, \Delta G)$, it can computes $(P\oplus \Delta P)(G\oplus \Delta G)$ in time determined by $P$, $\Delta P$, $\Delta G$, $\tilde{M}(P, G)$ and \affballx only, and is not directly dependent of $|G|$.
\end{theorem}

Based on this, below we discuss how the framework handles the challenges raised in Sectioin~\ref{subsec-challenges}. We prove Theorem~\ref{thm-pattern-incremental} by providing such algorithms in Section~\ref{sec-IncAlg}.

\sstab {\bf Solution (1): localizing changes impacts}. To solve challenge (1), the framework computes new matches in a ``{\em global-to-local}'' way with \fb and \ballfilter structures.

\sstab (I) for $\Delta P$, by storing $\tilde{M}(P,G)$ and the indexes in \fbmatstruct, it changes the problem of updating $PG_k(P,G)$ or $M(P,G)$ for $\Delta P$ to $P$, into updating $M({Pf}_i, G)$ for fragments ${Pf}_i$ to which $\Delta P$ apply, and then merging all $M({Pf}_i, G)$ together to $M(P\oplus \Delta P, G)$, which gives $PG(P\oplus \Delta P, G)$. This process localize the pattern change impacts from the whole patterns to pattern fragments.

\sstab (II) for $\Delta P$/$\Delta G$, by identifying \affballsx, it changes the problem of updating $\tilde{M}(P,G)$ for each ball in $G$, into updating $\tilde{M}(P, \ball{v,r})$ only within the set of \affballsx, and then merging all $M({Pf}_i, \ball{v,r})$ together to $M(P\oplus \Delta P, G\oplus \Delta G)$ within \affballsx, which gives $PG(P\oplus \Delta P,G\oplus \Delta G)$. This process localizes the pattern and data change impacts only to the related balls that may contain {\em new} match results \wrt $P$, $G$, \fbmatstruct, $\Delta P$ and $\Delta G$.

These two techniques restrict the pattern and data change impacts to those updated pattern fragments and the set of related balls in $G$, instead of entire $P$ and $G$. As will be shown later, this process theoretically effectively reduces the computation cost when compared to computing from scratch or computing from $M(P,G)$ directly via conventional unbounded incremental algorithms.

\sstab {\bf Solution (2): informative auxiliary data structures and space budget storage method}.

\sstab (I) To solve the problem what information to store in challenge (2), the framework maintains the {\em fragment-ball matches} $\tilde{M}(P,G)$,
 which has the following advantages compared to store $PG_k(P,G)$ directly as conventional incremental algorithms, or store $M(P,G)$ as some pattern incremental algorithms ~\cite{FanWW13-tods}.
 (i) On one hand, by the nature of graph simulation based algorithms~\cite{infsimu95}, the partial match relations $M({Pf}_i, \ball{v,r})$ in $\tilde{M}(P,G)$ are actually intermediate results for computing $M(P,\ball{v,r})$ (and thus $PG_k(P,G)$), which do not incur higher maintenance cost than maintaining $PG_k(P,G)$ as conventional incremental algorithms.
(ii) On the other hand, $\tilde{M}(P,G)$, together with $P$, is more informative than $PG_k(P,G)$ and even $M(P,G)$, as both $PG_k(P,G)$ and $M(P,G)$ can be naturally derived from $\tilde{M}(P,G)$ and $P$ by conducting graph simulation algorithms over $\tilde{M}(P,G)$ without additional computation cost, \ie $O(C_{\tilde{M}(P,G)} + C_{\tilde{M}\ra M}) = O(C_{M(P,G)})$, where $C_{\tilde{M}(P,G)}$ is the cost of computing $\tilde{M}(P,G)$ from $P$ and $G$, $C_{\tilde{M}\ra M}$ is the cost of computing $M(P,G)$ from $\tilde{M}(P,G)$ and $P$, and $C_{M(P,G)}$ is the cost of computing $M(P,G)$ directly from $P$ and $G$.

\sstab (II) To solve the problem on how to store information with space budget in challenge (2), the framework obeys the storage principle proposed above to store all auxiliary structures.
Moreover, the size of the auxiliary structure is not an overhead, as its size is comparable to the size of the match relation $M(P, G)$ of $P$ in $G$, which has anyway to be stored in the process of computing of $PG_{k}(P, G)$.
More specifically, observe that the total size of the auxiliary structures is $O(|\Sigma_{Pf\in {\cal P}_{m}}\Sigma_{v\in G}|Pf||\ball{v,r}|)$ + $C_{m}$ = $O(|P|\Sigma_{v\in G}|\ball{v,r}|)$ + $C_{m}$, where $C_{m}$ = $2^{m}$ is small compared to $G$ ($m$ is typically small, \eg 3 or 4, as shown in Section~\ref{sec-expt}). Observe that the match relation $M(P, G)$ is also of size $O(|P|\Sigma_{v\in G}|\ball{v, r}|)$, which has to be stored in the computation of $PG_{k}(P, G)$.

%\textbf{Space analysis of all auxiliary structures: the space of $\tilde{M}(P,G)$ is bounded by $O(|V||P||G|)$, two indexes: $O(|2^m+V_G|)$, ballfiltercode: $O(2^m)$.. the time of construct $\tilde{M}(P,G)$ is $O(|V||P||G|)$, two indexes: $O(|2^m+V_G|)$, ballfiltercode: $O(2^m)$.}

Despite of this, we next show how to, given a pattern graph $P$, a data graph $G(V,E)$, a size bound factor $C$ and an $m$-fragmentation $({Pf}_1, \ldots, {Pf}_m, F)$ of $P$,  construct $\tilde{M}^{C}(P,G)$ of size no larger than $C|G|$. Remember that $\tilde{M}(P,G)$ is the set $\bigcup_{i\in[1,m], v\in V} M({Pf}_i, \ball{G}[v,r])$. We below show how to pick a subset $\tilde{M}^C(P,G)$ of $\tilde{M}(P,G)$ such that the chances that $\tilde{M}^C(P,G)$ can best support our incremental approach.
To do this, we first define a ranking function that assigns scores to balls in $G$. We then show how to maintain the bounded size $\tilde{M}^{C}(P,G)$ through the whole computation.

\etitle{Ranking function}.
Given a data graph $G$, an $m$-fragmentation ${\cal P}_m$, we define a ranking function $\rho(\cdot)$ satisfying the following.
For each ball $\ball{v,r}$, $\rho(\ball{v,r})$ is a $(h, s)$, where $h\in [1, m]$ is an integer, $s$ is a real number, such that
\bi
\item [(i)] there are $h$ fragments in ${\cal P}_m$ to which $P$ matches;
\item [(ii)] $s = \dfrac{h}{\sum_{i\in [1,m]} |M(Pf_i, \ball{v,r})|}$.
\ei

Given two balls $\ball{v,r}$ and $\ball{v',r}$, we say $\ball{v,r}$ is ranked higher than $\ball{v',r}$ \wrt $\rho(\cdot)$, if
\bi
\item [(1)] $h_v > h_{v'}$; {\bf or}
\item [(2)] $h_v = h_{v'}$ and $s_v > s_{v'}$,
\ei
where $\rho(\ball{v,r}) = (h_v, s_v)$ and $\rho(\ball{v',r}) = (h_{v'}, s_{v'})$.

Intuitively, $\ball{v,r}$ ranks higher than $\ball{v', r}$ when (1) there are more pattern fragments matches $\ball{v,r}$ than $\ball{v',r}$, this is because the more pattern fragments have matches in a ball, the higher possibility it has a perfect subgraph with the updated $P$ and $G$; (2) If the number of fragments matches the two are equal, but it takes smaller space to store partial match relations of fragments in $\ball{v,r}$ than in $\ball{v',r}$, we adopt this method because with the equal space budget, it contains more information and can store more partial matches in terms of balls, surely reducing the computation work on computing balls and partial matches in the following incremental process.

\etitle{Maintaining $\tilde{M}^C(P,G)$}.
We next describe how to maintain $\tilde{M}^C(P,G)$. We processes balls of $G$ one by one. For each ball $\ball{v,r}$, we computes its ranking score $(h_v, s_v)$ by the ranking function $\rho(\cdot)$ defined above.
If there are enough space to store partial match relations in $\ball{v,r}$ in $\tilde{M}^C(P,G)$ within the space budget $C|G|$, we put it into $\tilde{M}^C(P,G)$. Otherwise, we check whether there are balls whose partial match relations are stored in $\tilde{M}^C(P,G)$ but rank lower than $\ball{v,r}$. If the total size of partial match relations in these balls is larger than that in $\ball{v,r}$, we then replace partial match relations in the lowest ranked balls in $\tilde{M}^C(P,G)$ with the ones in $\ball{v,r}$ instead. If no such balls found, then we do not put partial match relations in $\ball{v,r}$ into $\tilde{M}^C(P,G)$.

\sstab {\bf Solution (3): support for both pattern and data graph changes}. The unified framework can process pattern and data changes together or in any arbitrary order. This is because for pattern or data updates, the framework processes them following the same routine. More specifically,

\sstab (I) the framework constructs the same auxiliary structures \fbmatstruct for incremental computation;

\sstab (II) for either $\Delta P$, $\Delta G$ or $\Delta P$ and $\Delta G$ together, the incremental process identifies \affballsx by taking the union of \affballsx \wrt $\Delta P$ and \affballsx \wrt $\Delta G$.

\sstab (III) for the set of \affballsx, the incremental process updates the partial results in $\tilde{M}(P,G)$ and maintains the other auxiliary structures \wrt $\Delta P$ and $\Delta G$. It then combines the updated partial results to get the final match results.

{\bf Section 4}:

\stab
\etitle{(1) Updating update planner and \ballfilter}. When a batch update $\Delta P$ arrives, the update planner is updated by processing all unit updates in $\Delta P$ in an ascending order by their update IDs. \ballfilter is also updated \wrt $\Delta P$.

\stab
\etitle{(2) Identifying \affballsx}. \patinc then invokes \identifyaffball to identify \affballsx due to the arrival of $\Delta P$.

\stab
\etitle{(2) Compute partial match relations in \affballsx}. For each ball $\ball{v,r}$ that is marked as \affballx, for each pattern fragment ${Pf}_i$, computes $M({Pf}_i\oplus \Delta {Pf}_i, \ball{v,r})$ from $M({Pf}_i, \ball{v,r})$ by using the methods which will proposed in Section~\ref{subsubsec-ball}, where $\Delta {Pf}_i$ consists of all unit updates stored in $T({Pf}_i)$ with update IDs larger then $\ball{v,r}[\cflag]$ in \matchindex.

\stab
\etitle{(4) Combining partial match relations}. \patinc then uses the method which will proposed in Section~\ref{subsubsec-merge} to merge $M({Pf}_i\oplus \Delta {Pf}_i, \ball{v,r})$ computed above for all \affballsx along with updates in $T(F)$ to the cut $F$ of $P$. \patinc outputs the top-$k$ results of this step as answers to the current batch update received.

\stab
\etitle{(5) Updating \matchindex}. To handle future batch updates, \patinc also updates \matchindex by setting $\ball{v,r}[\cflag]$ to $\kw{id}_\delta$ for each ball $\ball{v,r}$ marked as \affballx. \patinc then checks on the match status of the ball according to $M({Pf}_i\oplus \Delta {Pf}_i, \ball{v,r})$ and updates the link from the corresponding type code $tc$ in fragment-ball status component to the record of $\ball{v,r}$ in the ball status component. \patinc finally sets all balls non \affballsx at the end and reset the corresponding $fc$ in \ballfilter of \affballsx to 11.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\stitle{Remark}. When $\Delta P$ contains a node-insert update with new label on the node, the density upper bound stored in $\ball{v,r}[\kw{den}]$ for each ball $\ball{v,r}$ needs to be refreshed as Step (1) of the linear approximation algorithm has to be recomputed. We handle this by
(i) extending the ball status component of \matchindex for each ball $\ball{v,r}$ with a new field called \dflag, which is a natural number that indicates whether the density of a ball needs to be refreshed; and
(ii) extending the fragment-ball status component of \matchindex for each match status with a new field called \rflag, which is a natural number that decides whether the density upper bound of all balls of the current type code are updated (omitted).
With these, algorithm \optpatinc is able to
\bi
\item [(a)] determine whether $\ball{v,r}[\kw{den}]$ needs update for each \affballx $\ball{v,r}$ in $O(1)$ time; and
\item [(b)] decide whether the density upper bounds of all \affballsx are updated within $O(2^m)$ time ($m$ is the number of fragment of pattern $P$ and is typically very small), {\em independent of the number of \affballsx}.
\ei

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Bounded Storage Principle}

In summary, the space of the entire auxiliary structures is $2^{h+1}h+ \sizeof(fbm)+3|V|+|\Delta P|$.  One typically has a budget on the size of space that can be used for storing auxiliary structure. We set the space bound to $\sizeof(fbm)\le \sizeof(G)$, where $C$ is small.

In the experiment, we find that at beginning of the incremental process, it takes 17MB and 120MB to store fragment-ball status index, ball status index and ball filtering code on Citation and synthetic data, compared to 36MB and 482MB to store the entire data graph. For storing fragment-ball matches, whose space complexity is rather higher, however, in practice, it cannot have that much matches due to the constraints carried by pattern graphs. It only takes 6MB and 4MB to store fragment-ball matches on Citation and synthetic data.

\stitle{Ranking based space bounding policy}.
Given a data graph $G$, an $m$-fragmentation ${\cal P}_m$, we define a ranking function $\rho(\cdot)$ satisfying the following.
For each ball $\ball{v,r}$, $\rho(\ball{v,r})$ is a $(h, s)$, where $h\in [1, m]$ is an integer, $s$ is a real number, such that
\bi
\item [(i)] there are $h$ fragments in ${\cal P}_m$ to which $P$ matches;
\item [(ii)] $s = \dfrac{h}{\sum_{i\in [1,m]} |M(Pf_i, \ball{v,r})|}$.
\ei

Given two balls $\ball{v,r}$ and $\ball{v',r}$, we say $\ball{v,r}$ is ranked higher than $\ball{v',r}$ \wrt $\rho(\cdot)$, if
\bi
\item [(1)] $h_v > h_{v'}$; {\bf or}
\item [(2)] $h_v = h_{v'}$ and $s_v > s_{v'}$,
\ei
where $\rho(\ball{v,r}) = (h_v, s_v)$ and $\rho(\ball{v',r}) = (h_{v'}, s_{v'})$.

Intuitively, $\ball{v,r}$ ranks higher than $\ball{v', r}$ when (1) there are more pattern fragments matches $\ball{v,r}$ than $\ball{v',r}$, this is because the more pattern fragments have matches in a ball, the higher possibility it has a perfect subgraph with the updated $P$ and $G$; (2) If the number of fragments matches the two are equal, but it takes smaller space to store partial match relations of fragments in $\ball{v,r}$ than in $\ball{v',r}$, we adopt this method because with the equal space budget, it contains more information and can store more partial matches in terms of balls, surely reducing the computation work on computing balls and partial matches in the following incremental process.

### 2017-10-04 TF-vldb2018/full/sec-appendix.tex

--- 2017-09-29 TF-vldb2018/sec-appendix.tex
@@
 \mat{0ex}{
-\sstab {\sl Input:\/} Pattern graph $P(V_{P}, E_{P})$ and ball $\ball([v, r])$.\\
-{\sl Output:\/} The perfect subgraph $G_s$ of $\ball{[v,r]}$ \wrt $P$.\\
+\sstab {\sl Input:\/} Pattern graph $P(V_{P}, E_{P})$ and ball $\ball{[v, r]}$.\\
+{\sl Output:\/} The match graph $G_s$ for $P$ in $\ball{[v, r]}$ .\\
 \sstab \bcc \hspace{1ex} \= \For each $u \in V_{P}$ \Do\\
@@
 \icc \>\>\>\hspace{2ex}\= $\matchs(u)$ := $\matchs(u) \setminus \{w\}$;\\
-\icc \> \If there exists $|\matchs(u)|\not\in f_{P}(u)$ \Then \Return $\emptyset$;\\
+\icc \>\> \If $\matchs(u)$ = $\emptyset$ \Then \Return $\emptyset$;\\
 \icc \> $\Reps$ := \{$(u,w) | u \in V_{P}, w \in \matchs(u)$\};\\
-\icc \> Construct the perfect subgraph $G_s$ \wrt $\Reps$;\\
+\icc \> Construct the match graph $G_s$ \wrt $\Reps$;\\
 \icc \> \Return $G_s$;\\
@@
 As shown in Fig~\ref{alg-rsim}, given $P$ and ball $\ball{[v, r]}$,
-\rgraphsim finds the perfect subgraph of $P$ and $\ball{[v, r]}$.
+\rgraphsim finds the match graph for $P$ in $\ball{[v, r]}$.
 For each node $u$ in $V_{P}$, it first computes the set $\matchs(u)$ of candidate matches $w$ containing the label of $u$ (lines 1-2),
-and then removes nodes from $\matchs(u)$ iteratively (lines 3-6).
+and then removes nodes from $\matchs(u)$ iteratively (lines 3-7).
 A node $w$ is removed from $\matchs(u)$ if there is a adjacent node $u'$ of $u$,
 but there exists no adjacent node $w'$ of $w$ such that $w'\in \matchs(u')$.
-Finally, it checks whether the capacity bound on each node $u$ is satisfied (line 7).
-If so, \rgraphsim constructs the perfect subgraph $G_s$ \wrt the maximum match relation $\Reps$ and returns it (lines 9-10).
+If so, \rgraphsim constructs the match graph $G_s$ \wrt the maximum match relation $\Reps$ and returns it (lines 8-10).
 

### 2017-10-04 TF-vldb2018/full/sec-expt.tex

--- 2017-10-01 TF-vldb2018/sec-expt.tex
@@
 \ni (1) {\em \citationd}~\cite{citationWeb} contains 1.39M paper nodes and 3.02M paper-paper citation edges.
-We used its undirected version, where edges indicate the relevance relationship. We generated 200 labels based on phrase clustering of paper titles.
+We used its undirected version, where edges indicate the relevance relationship, and generated 200 labels based on phrase clustering of paper titles.
 
@@
 \etitle{Algorithms}. We implemented the following algorithms, all in C++:
-(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
+(1) algorithm \optgrouprec for \teamF, (2) incremental algorithm \inc for \dynteamF,
 (3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
-(a) \mindia is to minimize the team diameter~\cite{Lappas09}, which is firstly proposed for the team formation problem;
-(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
+(a) \mindia is to minimize the team diameter~\cite{Lappas09}, which is firstly proposed for the team formation problem,
+(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}, and
 (c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
 Most of the algorithms for \teamF, including  \mindia and \denalk, only compute the best team,
-while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
+while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure \cite{Lawler1972}.
 Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.
@@
 \vspace{-2ex}
-
 \end{center}
-\vspace{-3ex}
+\vspace{-2.5ex}
 \caption{Performance evaluation of algorithm \inc for dynamic top-$k$ team formation (Cit: \citationd, Syn: \synthetic)}
@@
 %\end{widepage}
-\vspace{-3ex}
+\vspace{-2.5ex}
 \end{figure*}
@@
 at a high efficiency.
-(4) \inc outperforms \optgrouprec when hybrid data updates are no more than 32\% and 36\% on \citationd and \synthetic respectively.
+(4) \inc outperforms \optgrouprec when hybrid data updates are no more than 32\% and 36\% on \citationd and \synthetic, respectively.
 
@@
 \stitle{Exp-5: Physical storage of auxiliary structures}.
-As shown in Fig.~\ref{fig-exp-extraspace}, the incremental algorithm \inc takes (25MB, 130MB) extra space to store all its auxiliary structures on (\citationd, \synthetic), which need (36MB, 482MB) space to store themselves.
+As shown in Fig.~\ref{fig-exp-extraspace}, the incremental algorithm \inc takes (25MB, 130MB) extra space to store all its auxiliary structures on (\citationd, \synthetic), while they need (36MB, 482MB) space to store themselves.
 That is, the auxiliary structures are light-weight, and only take (69.4\%, 26.9\%) extra space compared with the original datasets.
@@
 \sstab(2) Our batch algorithm for  top-$k$ team formation is efficient,
-\eg it took 116s when $|V|=1.39M$ and $|V_P|=10$.
+\eg it only took 116s when $|V|=1.39M$ and $|V_P|=10$.
 

### 2017-10-04 TF-vldb2018/full/sec-opt.tex

\section{Optimization with Graph Filtering}
\label{sec-opt}

In this section, we propose graph filtering based optimization techniques to
enhance the algorithm proposed in Section~\ref{sec-topk}.

Our optimization techniques works for the following scenario.
We have a local data graph $G$ and a user specified positive integer $r$, and
we want to find top-$k$ group recommendations for each {\em online query}
$\langle Q, k\rangle$, where $Q$ is a pattern graph and $k$ is a positive
integer, \ie find the top-$k$ densest valid groups for $Q$ of $G$ \wrt $r$ for
each online query $\langle Q,k\rangle$.

The optimization is based on an idea of graph filtering: filter out the candidates that are not possible to contain results as early as possible. After executing top-$k$ offline process and before executing top-$k$ online process, we can employ a filtering process on $BL$ to remove the balls that are not possible to contain valid groups, which we refer to as false balls. And that will certainly reduce the execution time in finding out top-$k$ results. It contains a filtering offline preprocessing process over the set of balls in $BL$, and a filtering online process for each input query, in which we utilize an effective and efficient pruning strategy to remove false balls from $BL$ as many as possible. Finally, we can execute top-$k$ online process on the revised ball list $BL$.

In filtering offline process, we need to identify some pruning rules, which is usually executed based on features selected from candidates. In filtering online process, given a query graph, if there exists a feature that the query graph has while a data ball does not have, the data ball will be eliminated from the candidate set safely. \textcolor[rgb]{0.00,0.00,1.00}{TO be more CONCRETE!}

\subsection{Offline(\&online): Building Hybrid Star-feature Indices}

\stitle{Star-feature selection}

When deal with directed graphs, as we have seen in section~\ref{subsec-extsim}, graph simulation preserves the labels and the child relationship of a graph pattern in its match. When it comes to undirected graphs, graph simulation still preserves the label relationship, and preserves the neighbor relationship of a graph pattern in its match instead of child relationship in directed graphs. Therefore, we utilize the ``neighbor relationship" character as the pruning rule, and use the feature ``star" to represent the ``neighbor relationship" character. A star is a graph structure with a center node in the middle and a set of neighbor nodes adjacent with the center node. For each ball $\ball{v, r}$ in data graph $G$, and for each node $w$ in the ball, we construct one corresponding star-feature, eg..., so we get a set of star-features $F$ for each ball.

For all the balls $\ball{v, r}[1]$, $\ball{v, r}[2]$,...,$\ball{v, r}[n]$ in data graph $G$, we construct the corresponding feature sets $F[1]$,$F[2]$,...,$F[n]$. When a pattern graph comes, we construct the corresponding star-feature set $FP$ and compare it with $F[i]$ ($1\leq i\leq n$) of $\ball{v, r}[i]$. For each feature $fp$ in $FP$, if there exists a feature $f$ in $F[i]$ containing $fp$ as a substructure, then there may exist a matching result in $\ball{v, r}[i]$ and need further validation in the top-$k$ process. Otherwise, $\ball{v, r}[i]$ is pruned from candidate set safely.

In the above indices construction, for each ball $\ball{v, r}[i]$ ($1\leq i\leq n$) with $m_i$ nodes, we construct $m_i$ star-features. But it may be a waste of time and space to retrieve and store such lots of features, we can retrieve less features with stronger filtering power, making a balance between complexity and the pruning power. Therefore, We will improve this by adopting the next two star-feature selection strategies respectively.

Given a graph $H$, we want to select as few star-features as possible, which requires each star-feature to have strong pruning power and differ from other star-features obviously. This inspires us to think about the star minimization problem we will discuss in this section.

\etitle{Star minimization problem}. Given a graph $H(V_h, E_h)$, Star minimization problem is to select a set of star-features $F$ from $H$, with the union of edges of star-features in $F$ covering all the edges in $E_h$, while $|F|$ is minimized.

\begin{theorem}
\label{thm-star-mini-complexity}
Given a graph $H(V_h, E_h)$, and a positive integer $\xi$, it is \NP-complete to determine whether there exists a star-feature set $F$ with the union of edges of star-features in it covering all the edges in $E_h$, and the number of items in $F$ is no larger than $\xi$.
\end{theorem}

\textbf{Approximation hardness:}

\begin{theorem}
\label{thm-star-mini-complexity}
There exists a factor 2 approximation algorithm for the Star minimization problem.
\end{theorem}

We present the 2-approximation algorithm in Fig.~\ref{star-min-alg}.

\begin{figure}[tb!]
\vspace{2ex}
\begin{center}
{\small

\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Graph $H(V_h$, $E_h)$.\\
{\sl Output:\/} The set of star-feature $F$ of $H$.\\
\bcc \quad $C:=\emptyset$; $F:=\emptyset$;\\
\icc \quad $H'(V_h', E_h'):=H(V_h, E_h)$;\\
\icc \quad while $E_h'$ is not empty do\\
\icc \quad\quad pick any $(u, v) \in E_h'$;\\
\icc \quad\quad $C:=C \cup \{(u, v)\}$;\\
\icc \quad\quad remove all edges incident to either $u$ or $v$ in $H'$.\\
\icc \quad for each node $w$ in $C$ do\\
\icc \quad\quad construct star feature $f$ takes $w$ as the center node in $H$;\\
\icc \quad\quad $F:=F \cup f$;\\
\icc return $F$;\\

}
\vspace{-2.5ex} \myhrule
}
\end{center}
\vspace{-4ex}
\caption{Algorithm StarMin} \label{star-min-alg}
\vspace{-3ex}
\end{figure}

There is another scene that users have the chance to specify a number, indicating how many star-features necessarily to be selected from the given graph. It requires the fixed number of star-features we select should have strong pruning power, representing as much structural information as possible. This is another feature selection strategy we will consider next.

\etitle{$K$-star coverage maximization problem}. Given a graph $H(V_h, E_h)$ and a user specified integer $K$, $K$-star coverage maximization problem is to select a set of star-features $F$ from $H$, with the union of edges of star-features in $F$ covering as many edges as possible in $E_h$.

\begin{theorem}
\label{thm-k-star-max-complexity}
Given a graph $H(V_h, E_h)$, two positive integers $K$ and $\xi$, it is \NP-complete to determine whether there exists a $K$ item star-feature set $F$, in which the number of the union of edges of the star-features is no smaller than $\xi$.
\end{theorem}

\textbf{Approximation hardness:}

\begin{theorem}
\label{thm-star-mini-complexity}
There exists a 3/4-approximation algorithm for the $K$-star coverage maximization problem.
\end{theorem}

We present the 3/4-approximation algorithm in Fig.~\ref{k-star-max-alg}.

\begin{figure}[tb!]
\vspace{2ex}
\begin{center}
{\small

\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Graph $H(V_h$, $E_h)$, a positive integer $K$.\\
{\sl Output:\/} The set of star-feature $F$ of $H$.\\
\bcc \quad $C:=\emptyset$; $F:=\emptyset$;\\
\icc \quad for $i=1$ to $K$ do\\
\icc \quad\quad select node $v$ from $H$ while the number of edges $C \cup \{v\}$ \\covers is maximized ;\\
\icc \quad for each node $w$ in $C$ do\\
\icc \quad\quad construct star feature $f$ takes $w$ as the center node in $H$;\\
\icc \quad\quad $F:=F \cup f$;\\
\icc return $F$;\\

}
\vspace{-2.5ex} \myhrule
}
\end{center}
\vspace{-4ex}
\caption{Algorithm K-StarMax} \label{k-star-max-alg}
\vspace{-3ex}
\end{figure}

\textcolor[rgb]{1.00,0.00,0.00}{\textbf{Remark.}
Establish the filtering power standards of star features.
1. Covering more edges
2. Covering more nodes}

\stitle{Hybrid Star Index Structure}.

In last section, for each ball $\ball{v, r}$ in data graph $G$, we construct a star-feature set $F$. When a pattern graph $P$ comes, we construct the corresponding star-feature set $FP$ and compare it with $F$. If $P$ and $\ball{v, r}$ are matched via extended graph simulation, for each star-feature $fp$ in $FP$, there must exist a corresponding $f$ in $F$ such that $fp$ is a substructure of $f$. That is, the local structure represented by $fp$ in $P$ must be preserved by $f$ in $\ball{v, r}$. Therefore, we need to check all the star-features in $FP$ to see whether there exist the corresponding structures in $\ball{v, r}$ preserving the local structure, such that we can remove the false positives in the filtering process. However, a question arises, as the structure comparison operation is expensive, how can we implement the checking process efficiently? In this section, we propose Hybrid-Star-Index-Structure to encode the local information of star-features selected in last step, improving the speed of comparison operation in filtering process to a large extent.

\etitle{Index structure for small label data graph}

We will present a encoding method, for the case when the number of labels appearing in data graph is small, which encodes the local information taken by the star to numerical space. For each star-feature, it generates a bit string with fixed-length, called \textbf{Star-fingerprint}, providing a convenient way to execute filtering process just on those star fingerprints, with no need referring to the originally star-feature structures.

\begin{definition} {\textbf{Star-fingerprint.}}
\label{def-ind-str-small-label}
Given a data ball $\ball{v, r}$ in $G$ and the corresponding star-feature set $F=\{s_1, s_2,..., s_m\}$ of the ball, for any star-feature $s_i$ $(1 \leq i \leq m)$ in $F$, the star-fingerprint $starfig(s_i)$ of $s_i$ is a two-tuples $<C,N>$, where $C$ denotes the center node with id and label of star $s_i$, and $N$ is a length-$L$ bit string, denoting the neighbor labels, where $L$ is the total number of labels appearing in $G$, and each bit indicates the appearance of the corresponding label in neighbors.
\end{definition}

By Definition~\ref{def-ind-str-small-label}, in the two-tuples $<C,N>$, $C$ is to denote the center node and $N$ is to denote the neighbor labels of center node. For each distinct neighbor label, it sets the corresponding position element in the bit string to 1, indicating there exists at least one neighbor node carrying the label. For example, Fig~\ref{fig-starfingerprint-example} shows an example on how to generate the star-fingerprint.

\begin{figure}[tb!]
\begin{center}
\includegraphics[scale=0.4]{./fig/star-fingerprint.eps}
\caption{Star Fingerprint}
\label{fig-starfingerprint-example}
\end{center}
\end{figure}

\begin{prop}
\label{prop-star-fingerprint-condition}
Given a data graph $G$, a pattern graph $P$, and a positive integer $r$, if subgraph $G_{s}$ of $G$ is a {\em valid group} for $P$ \wrt $r$, then for each vertex $v$ in $P$, whose star-feature is $s_v$, and star-fingerprint $starfig(s_v)$ is $<C_p,N_p>$, there must exist a matched vertex $u$ in $G_{s}$, whose star-feature is $s_u$, and star-fingerprint $starfig(s_u)$ is $<C_g,N_g>$. The two star fingerprints must satisfy the following two conditions: 1)$l(C_p)=l(C_g)$; 2)$N_p \wedge N_g = N_p$.
\end{prop}

By proposition~\ref{prop-star-fingerprint-condition}, assume $G_{s}$ of $G$ is a {\em valid group} of $G$ for $P$. A vertex $v$ in $P$ is matched with a vertex $u$ in $G_{s}$. The vertices $v$ and $u$ are matched via extended graph simulation requires the two conditions hold, because according to extended graph simulation, the labels of $v$ and $u$ must be same (condition 1); and the labels of neighbors of $v$ must be a subset of the labels of neighbors of $u$ (condition 2).

\begin{theorem} {\textbf{Star-fingerprint Pruning 1.}}
\label{thm-star-fingerprint-pruning}
Given a data ball $\ball{v, r}$ of $G$ and a pattern graph $P$, for each vertex $v$ in $P$ with star-feature $s_v$, if there exists no vertex $u$ in $\ball{v, r}$ with star-feature $s_u$, where fingerprints $starfig(s_v)$ and $starfig(s_u)$ satisfy the two conditions in proposition~\ref{prop-star-fingerprint-condition}, there must exist no {\em valid group} in $\ball{v, r}$ of $G$ for $P$.
\end{theorem}

Apparently, this is a feature to feature comparison, and we can prune the set of balls cannot have a valid group inside quickly according to the pruning rule proposed in  theorem~\ref{thm-star-fingerprint-pruning}. It has a good performance when the length-$L$ bit string is short, as the comparison between two fingerprints can be executed by a bitwise AND operation in $O(L)$ time.

\etitle{Index structure for large label data graph}

When the number of labels appearing in data graph is really large, it is inconvenient to adopt the star-fingerprint method to represent the star feature. That is, when $L$ is large, adopting the $L$-length bit string is not efficient for the star feature expression and feature to feature comparison. Therefore, we will present another encoding method for representing star-features extracted from the data graph with large number of labels. For each star-feature, it generates a bit string with specified length, called \textbf{Star-bloomfilter}. This is a method based on the space-efficient data structure \textbf{bloom filter}, both reducing the storage space requirement and improving filtering speed.

A Bloom filter is a length-$X$ bit string. Given a set of elements and a query item, the bloom filter is used to check whether the query element is contained in the set. There are also $k$ predefined hash functions, each of which hashes an item to one of the $X$ positions with a uniform random distribution. For each element, feed it to each of the $k$ hash functions to get $k$ bit positions, and set the bits at all these positions to 1. To query whether there exists an element in the set, just feed it to each of the $k$ hash functions to get $k$ bit positions, check whether all these bits are set to 1. If there exists any position the bit is 0, then the element is not in the set. If it were, then the element has a high probability in the set, but there may exist ``false positives" due to collisions in hash functions. By this observation, given a query graph and a data ball, when executing the feature to feature comparison, say $f$ in data ball and $fp$ in query graph, we can use a bloom filter to encode the neighbor label set of $s$, and check for each neighbor label in $fp$, whether it is contained in $s$ by checking the bloom filter. Finally, we can filter out a set of unmatched data balls in advance.

\begin{definition} {\textbf{Star-bloomfilter.}}
\label{def-ind-str-large-label}
Given a data ball $\ball{v, r}$ in $G$ and the corresponding star-feature set $F=\{s_1, s_1,..., s_m\}$  of the ball, for each star-feature $s_i$ $(1 \leq i \leq m)$ in $F$, the star-bloomfilter $starblm(s_i)$ of $s_i$ is a two-tuples $<C,N>$, where $C$ denotes the center node with id and label of star $s_i$, and $N$ is a length-$X$ bit string bloom filter, denoting the neighbor labels, where $X$ is a user specified number.
\end{definition}

By Definition~\ref{def-ind-str-large-label}, in the two-tuples $<C,N>$, $C$ is to denote the center node and $N$ is to denote the neighbor labels of center node. For each distinct neighbor label, by the set of $k$ hash functions, it sets the corresponding $k$ position element in the bit string to 1, indicating there exists at least one neighbor node carrying the label. For example, Fig~\ref{fig-bloomfilter-example} shows an example on how to generate the star-bloomfilter.

\begin{figure}[tb!]
\begin{center}
\includegraphics[scale=0.4]{./fig/star-bloomfilter.eps}
\caption{Star Bloomfilter}
\label{fig-bloomfilter-example}
\end{center}
\end{figure}

\begin{prop}
\label{prop-star-bloomfilter-condition}
Given a databall graph $G$, a pattern graph $P$, and a positive integer $r$, if subgraph $G_{s}$ of $G$ is a {\em valid group} for $P$ \wrt $r$. Then for each vertex $v$ in $P$, whose neighbor label set is $lset$, there must exists a matched vertex $u$ in $G_{s}$, whose star-feature is $s_u$, and star-bloomfilter $starblm(s_u)$ is $<C_g,N_g>$. They must satisfy the following two conditions: 1)$l(v)=l(C_g)$; 2)for each item in $lset$, feed it to each of the $k$ hash functions to get $k$ bit positions in $N_g$, all the $k$ bits are set to 1.
\end{prop}

By proposition~\ref{prop-star-bloomfilter-condition}, assume $G_{s}$ of $G$ is a {\em valid group} of $G$ for $P$. A vertex $v$ in $P$ is matched with a vertex $u$ in $G_{s}$. The vertices $v$ and $u$ are matched via extended graph simulation requires the two conditions hold, because according to extended graph simulation, the labels of $v$ and $u$ must be same (condition 1); and the labels of neighbors of $v$ must be a subset of the labels of neighbors of $u$ (condition 2).

\begin{theorem} {\textbf{Star-bloomfilter Pruning 2.}}
\label{thm-star-bloomfilter-pruning}
Given a data ball $\ball{v, r}$ of $G$ and a pattern graph $P$, for a vertex $v$ in $P$, if there exists no vertex $u$ in $\ball{v, r}$ with star-feature $s_u$, where $v$ and bloomfilter $starblm(s_u)$ of $u$ satisfy the two conditions in proposition~\ref{prop-star-bloomfilter-condition}, there must exist no {\em valid group} in $\ball{v, r}$ of $G$ for $P$.
\end{theorem}

Obviously, when the label number $L$ is small, we can use the length-$L$ star-fingerprint bit string, in which each bit represents a label directly; when the label number $L$ is large, we can reduce the storage space of a star feature encoding string significantly by utilizing bloomfilter data structure, from length-$L$ star-fingerprint bit string to length-$X$ star-bloomfilter bit string by using hash functions.

\textcolor[rgb]{1.00,0.00,0.00}{\textbf{Remark.}
Probability analyze for bloomfilter}

\stitle{Index structure for the whole data ball(Graph Code)}.

The above ``star to star" pruning process is time-consuming. We will next provide some quick pruning rules based on graph code. Such that when a query graph comes, we could execute ``graph to graph" filtering first, quickly pruning out the set of candidates obviously cannot match with query graph in the first filtering phase, and then employ the ``star to star" filtering with stronger pruning capability. We know that extended graph simulation preserves label and number relationship between data graph and pattern graph, so we can take those two characters as a pruning rule. In the first filtering phase, we could efficiently eliminate the set of candidates which violate the label and number constraints taken by pattern graph. Then in the second phase, we further check whether the candidates preserve the structural constraints taken by pattern graph by making the ``star to star" validation.

In this section we will present a encoding method for data balls, which encodes the label and node number information taken by the ball to numerical space. For each data ball, it generates a list , called \textbf{Graph-code}.

\begin{definition} {\textbf{Graph-code.}}
\label{def-ind-graph-code-arr}
Given a data ball $\ball{v, r}$ of $G$, the graph-code $B$ of $\hat{G}$ is a list. Each item in the list is a two-tuple $<Lab, Num>$, where $Lab$ indicates there exists at least one node in $\hat{G}$ labeled with $Lab$, and $Num$ denotes there are $Num$ nodes carrying the label $Lab$.
\end{definition}

Fig.~\ref{fig-graphcode-example} shows an example on how to generate the Graph code. \textcolor[rgb]{0.00,0.00,1.00}{MORE examples, combine with star-feature.}

\begin{figure}[tb!]
\begin{center}
\includegraphics[scale=0.5]{./fig/graph-code.eps}
\caption{Graph Code}
\label{fig-graphcode-example}
\end{center}
\end{figure}

\begin{prop}
\label{prop-graph-code-condition}
Given a data graph $G$, a pattern graph $P$, and a positive integer $r$, if subgraph $G_{s}$ of $G$ is a {\em valid group} for $P$ \wrt $r$, and is contained in $\ball{v, r}$. The graph code $B_p$ of $P$ and the graph code $B_g$ of $\ball{v, r}$ must satisfy the following conditions:  for each item $<Lab_p,Num_p>$ in $B_p$, there must exist the corresponding item $<Lab_g,Num_g>$ in $B_g$ with 1) $Lab_p=Lab_g$, and 2) $Num_p \leq Num_g$.
\end{prop}

By proposition~\ref{prop-graph-code-condition}, assume $G_{s}$ of $G$ is a {\em valid group} of $G$ for $P$, and is contained in $\ball{v, r}$. $P$ and $G_{s}$ in $\ball{v, r}$ match via extended graph simulation requires the above conditions hold. Because according to extended graph simulation, each label $l$ contained in $P$ must be contained in $\ball{v, r}$, and the number of nodes labeled with $l$ must satisfy the lower bound requirement in $P$.

\begin{theorem} {\textbf{Graph-code Pruning 3.}}
\label{thm-graph-code-pruning}
Given a data ball $\ball{v, r}$ of $G$ and a pattern graph $P$, if there exists no subgraph $G_s$ in $\ball{v, r}$, where graph-code $B_p$ of $P$ and $B_g$ of $\ball{v, r}$ satisfy the conditions in proposition~\ref{prop-graph-code-condition}, there must exist no {\em valid group} in $\ball{v, r}$ for $P$.
\end{theorem}

Apparently, this is a graph to graph comparison, and we can efficiently prune out the set of candidates which violate the label and number constraints taken by pattern graph. It has a good performance as the comparison between two lists can be executed by linear scanning operation in $O(l_p+l_g)$ time ($l_p$ is the number of labels in $P$, and $l_g$ is the average number of labels among all the balls? Does average work?).

\subsection{(Online:) Improving Early Termination}

In order to accelerate the speed of finding match results, we combine the top-k early termination process with filtering method. Given a data graph $G$, we first generate the set of balls $ball_1$, $ball_2$,..., $ball_n$, with upper bounds $U_1$, $U_2$,..., $U_n$ ($U_1 \leq U_2,..., \leq U_n$ ), and then extract features from each ball and construct the indices. When given a pattern graph $P$, we first extract the set of features and establish the indices for $P$, and then perform the filtering process with the indices, eliminating the set of balls that cannot have matched subgraphs inside \wrt $P$. Then we execute the top-$k$ procedure, finding out the set of matches. The main steps are as below.

\stitle{Step1: Data graph Preprocess}. Generate the set of balls with upper bounds and feature indices.

\stitle{Step2: Pattern graph preprocess}. Extract features and establish index.

\stitle{Step3: Graph Code (node label and node number) filtering}. First filtering phase according to graph code pruning rule.

\stitle{Step4: Star-feature filtering}. Second filtering phase according to star-feature pruning rule.

\stitle{Step5: Top-k process}. Find out top-k match results of $G$.

\subsection{Putting Things Together}

title for last section

### 2017-10-05 TF-vldb2018/full/sec-appendix.tex

@@
 
-The satisfiability of patterns $P$ can be checked by treating $P$ as both data and pattern graphs, and computing the maximum match relation $M$ in $P$ for $P$, via graph simulation.
-Indeed, pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. 
-Observe that computing graph simulation and the size of $M$ is bounded by $|P|^2$.
+We will prove the proposition by providing the $O(|P|^2)$ time algorithm, along with its correctness proof.
+
+\vspace{-1.5ex}
+The satisfiability of patterns $P$ can be checked by the following algorithm:
+(a) Compute the maximum match relation $\Reps$ of $P \eps P$;
+(b) Check for each $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, whether $x_v \leq y_u$ holds.
+One can verify that step (a) is in $O(|P|^2)$ time by invoking procedure~\ref{alg-rsim}; and step (b) can be checked in $O(|P|^2)$ time as the size of $M$ is bounded by $|P|^2$.
+Thus the algorithm is overall in $O(|P|^2)$ time.
+
+\vspace{-1.5ex}
+We next prove the correctness of the algorithm.
+
+\vspace{-1.5ex}
+(I) We firstly prove that the when the algorithm outputs ``yes", then pattern $P$ is indeed satisfiable.
+This is correct since if the algorithm outputs ``yes", \ie $P \eps P$ \wrt $\Reps$ and capacity bounds in $\Reps$ are satisfied, there must exist a data graph $G$ such that $P \eeps G$.
+$G$ can be derived by (i) computing equivalent classes of nodes in $P$ based on $\Reps$, such that $u$ and $w$ are in the same class iff both $(u, w)\in \Reps$ and $(w, u)\in \Reps$;
+(ii) creating a set of nodes for each equivalent class, where the cardinality of the set falls in the intersection of capacity bounds on nodes in the equivalent class; and
+(iii) connecting the nodes belong to two equivalent classes iff there exist edges in $P$ connecting two pattern nodes which belong to the same two equivalent classes.
+We also set $r$ to be the radius of $G$. One can verify that $P \eeps G$.
+
+\begin{figure*}[tb!]
+	%\begin{widepage}
+	\vspace{-1.5ex}
+	\begin{center}
+		\hspace{-8ex}
+		\begin{minipage}[t]{0.4\textwidth}
+			\vspace{2ex}
+			\begin{center}
+				\subfigure[{Unboundedness of unit data update}]{\label{fig-inc-complexity-data}
+					\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}}
+			\end{center}
+			\vspace{-3.5ex}
+		\end{minipage}
+		\hspace{20ex}
+		\begin{minipage}[t]{0.4\textwidth}
+			%\vspace{-20.3ex}
+			\begin{center}
+				\subfigure[{Unboundedness of unit pattern update}]{\label{fig-inc-complexity-pattern}
+					\includegraphics[scale=0.28]{./fig/inc-complexity-proof-pattern.eps}}
+			\end{center}
+			\vspace{-3.5ex}
+		\end{minipage}
+	\end{center}
+	\vspace{-3ex}
+	%\caption{Performance evaluation of algorithm \optgrouprec for top-$k$ team formation}
+	%\label{exp-semantic-effectiveness-citation}
+	%\end{widepage}
+	\vspace{-2.0ex}
+\end{figure*}
+
+\vspace{-1.5ex}
+(II) We then prove that when the algorithm outputs ``no", then pattern $P$ is unsatisfiable.
+If the algorithm outputs ``no", then either (i) $P \not\eps P$ or (ii) $P \eps P$ but capacity bounds are not satisfied.
+We will prove this by contradiction.
+We consider case (i) $P \not\eps P$ and assume that $P$ is satisfiable in this case.
+For convenience, we use $P_1 \not\eps P_2$ to denote $P \not\eps P$, while $P_1$, $P_2$ and $P$ are exactly same.
+From that $P$ is satisfiable, we know that there exists a data graph $G$ such that $P_1 \eeps G$, $P_2 \eeps G$ and $P_1 \eeps G_s$, where $G_s$ is the perfect subgraph in $G$.
+By the definition of team simulation and graph simulation, from $P_2 \eeps G$, we know that $G_s \eps P_2$ holds;
+from $P_1 \eeps G_s$, we know that $P_1 \eps G_s$ holds; and 
+from $P_1 \eps G_s$ and  $G_s \eps P_2$, we know that $P_1 \eeps P_2$ holds.
+This contradicts the assumption.
+We then consider case (ii), \ie $P \eps P$ \wrt $\Reps$ while there exists $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v > y_u$, and assume that $P$ is satisfiable.
+From $P$ is satisfiable, we know that there exists a data graph $G$ such that $P \eeps G$.
+From $P \eps P$, we know that for any nodes $w$ in $G$, if $w$ matches with the pattern node $v$, then it must match with the pattern node $u$, that is, the number of data nodes match with $u$ is larger than that of data nodes match with $v$.
+However, this contradicts that the upper bound of $u$ ($y_u$) is smaller than the lower bound of $v$ ($x_v$).
+
+%By (I) and (II), we have proven that the algorithm is correct.
 
@@
 
-\vspace{-2.3ex}
+\vspace{-1.3ex}
 \stitle{Proofs of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
@@
 
+%\vspace{-1.5ex}
+%\begin{figure}[h]
+%	\label{fig-inc-complexity-data}
+%	\begin{center}
+%		\includegraphics[scale=0.3]{./fig/inc-complexity-proof-data.eps}
+%	\end{center}
+%	\vspace{-3ex}
+%	\caption{Unboundedness of unit data update}
+%	\vspace{-2ex}
+%\end{figure}
+
 \vspace{-1.5ex}
-\begin{figure}[ht!]
-\label{fig-inc-complexity-data}
-\begin{center}
-\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}
-\end{center}
-\vspace{-3ex}
-\caption{Unboundedness of unit data update}
-\vspace{-4ex}
-\end{figure}
-
 \etitle{(I) \dynteamF\, is unbounded for unit data update}.
@@
 
-\vspace{-1.5ex}
+\vspace{-1.0ex}
 That is, \dynteamF\, is unbounded even for $k=1$ and unit data update.
@@
 
-\vspace{-1ex}
-\begin{figure}[ht!]
-\label{fig-inc-complexity-pattern}
-\begin{center}
-\includegraphics[scale=0.31]{./fig/inc-complexity-proof-pattern.eps}
-\end{center}
-\vspace{-3ex}
-\caption{Unboundedness of unit pattern update}
-\vspace{-4ex}
-\end{figure}
+%\vspace{-1ex}
+%\begin{figure}[h!]
+%	\label{fig-inc-complexity-pattern}
+%	\begin{center}
+%		\includegraphics[scale=0.3]{./fig/inc-complexity-proof-pattern.eps}
+%	\end{center}
+%	\vspace{-3ex}
+%	\caption{Unboundedness of unit pattern update}
+%	\vspace{-2ex}
+%\end{figure}
 
-\vspace{-1ex}
+\vspace{-1.5ex}
 \etitle{(II) \dynteamF\, is unbounded for unit pattern update}.
@@
 
-\vspace{-1.5ex}
+\vspace{-1.0ex}
 (1) and (2) together prove that \dynteamF\, is unbounded even for $k=1$ and unit pattern or data update.
@@
 
+\vspace{4ex}
 \noindent
@@
 
-\begin{figure*}[tb!]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\vspace{1ex}
+\noindent
+{\large \textbf{Appendix C: Detailed Correctness \& Complexity Analysis}}
+\label{sec-apd-complexity}
+
+\noindent
+{\textbf{1. Algorithm \incp (Section~\ref{subsec-Qinc})}}
+
+The correctness of \incp \wrt $\Delta P$ is assured by
+the correctness of (a) \identifyaffball (by Proposition~\ref{prop-canaffballs});
+(b) \incmatch, which is assured by the correctness of \rgraphsim that has been proved in Section~\ref{sec-tsimAlg}, and the correctness of of \patedgeinsert. Indeed, \patedgeinsert only removes
+nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
+(c) \comb, whose analysis follows the same way as that for \patedgeinsert; and
+(d) the early return property (by Lemma~\ref{lemma-approximation-bound}).
+
+\vspace{-1.5ex}
+Procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$ time, where it takes $O(2^{h}\cdot|\Delta P|)$ time to update \bfc, $O(2^{h}\cdot h)$ to do the AND-operation, and $O(||\affballsx||)$ to identify \affballsx.
+%Thus, procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$.
+As $h$ is typically small, \eg 2 to 5, thus \identifyaffball is in $O(|\Delta P|+||\affballsx||)$;
+\patedgeinsert is in $O(|M(P_{fi}, \ball{[v,r]})|+|V_{P_{fi}}||E_{\ball{[v,r]}}|)$ time.
+Indeed, the recursive process for checking invalid nodes in $M(P_{fi}, \ball{[v,r]})$ is bounded by $O(|V_{P_{fi}}||E_{\ball{[v,r]}}|)$,
+and the process to update $M(P_{fi}, \ball{[v,r]})$ is bounded by the size of its changes, which is monotonically decreasing;
+According to \patedgeinsert,
+\comb is in $O(|\bigcup^{h}_{i=1} rM(P_{fi}\oplus\Delta P_{fi},\ball{[v,r]})|+r|V_{P\oplus \Delta P}||E_{\ball{[v,r]}}|)$ time.
+
+\vspace{-1.5ex}
+Putting these together, algorithm \incp is in
+$O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|+r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|) + r|P \oplus \Delta P||\affballsx|$ +$|\Delta P|)$ time \wrt $\Delta P$.
+
+\noindent
+{\textbf{2. Algorithm \incd (Section~\ref{subsec-Ginc})}}
+
+The correctness of \incd \wrt $\Delta G$ is assured by the correctness of
+\identifyaffball (by Proposition~\ref{prop-affected-datainc}) and procedures \incmatch and \comb,
+which can be proved along the same lines as for pattern updates.
+
+\vspace{-1.5ex}
+One can verify that \identifyaffball is in $O(|\affballsx| + |\Delta G|)$,
+\incmatch for all fragments and all \affballsx is in $O(|P||\affballsx|)$ time, and \comb is in $O(\bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|$ + $r|V_{P}||E_{\widehat{G\oplus\Delta G}}|)$ time.
+Therefore, algorithm \incd is in
+$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|+r|P||\affballsx| + |\Delta G|)$ time \wrt $\Delta G$.
+
+\vspace{1ex}
+\noindent
+{\large \textbf{Appendix D: Extra Experiments}}
+\label{sec-apd-exp}
+
+\vspace{-0.5ex}
+
+We also used another real-life dataset {\em \youtube}~\cite{youtubeWeb} for experimental verification.
+It contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos.
+We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.
+
+\vspace{-1.5ex}
+The experimental results on \youtube are reported here.
+
+\vspace{-1.8ex}
+\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis, \denalk on \youtube \wrt four quality measures.
+The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.
+We find \optgrouprec strikes a balance at capturing the practical requirements.
+
+\vspace{-1.8ex}
+\stitle{Exp-2: Efficiency of \inc for one set of updates}.
+Varying the amount of updates in one update set from 4.5\% to 49.5\% for pattern updates, 2.5\% to 27.5\% (resp.
+3\% to 33\%) for data insertions and hybrid data updates (resp.
+data deletions), and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous pattern and data updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
+We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%).
+%for hybrid pattern, hybrid data, and simultaneous pattern and data updates.
+
+\vspace{-1.8ex}
+\stitle{Exp-3: Efficiency of \inc for continuous sets of updates}. We generated 5 sets of updates,
+varying the amount of updates from 4.5\% to 27\% for pattern updates, 2.5\% to 15\% for data updates,
+and (4.5\%, 2.5\%) to (22.5\%, 12.5\%) for simultaneous pattern and data updates.
+We evaluated the average time took by \inc to process these sets of updates one by one.
+The results are reported in Fig.~\ref{fig-exp-patinc-multi-youtube} to~\ref{fig-exp-hyb-datapat-multi-youtube}.
+We find \inc outperforms \optgrouprec when changes are no more than 27\%, 10\% and (13.5\%, 7.5\%) for continuous pattern, data and simultaneous updates respectively.
+
+\vspace{-1.8ex}
+\stitle{Exp-4: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-youtube-extraspace},
+it takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which need 114MB space to store itself,
+\ie 50.8\% compared with the original dataset.
+
+\begin{figure*}[t!]
 	%\begin{widepage}
@@
 \end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\vspace{1ex}
-\noindent
-{\large \textbf{Appendix C: Detailed Correctness \& Complexity Analysis}}
-\label{sec-apd-complexity}
-
-\noindent
-{\textbf{1. Algorithm \incp (Section~\ref{subsec-Qinc})}}
-
-The correctness of \incp \wrt $\Delta P$ is assured by
-the correctness of (a) \identifyaffball (by Proposition~\ref{prop-canaffballs});
-(b) \incmatch, which is assured by the correctness of \rgraphsim that has been proved in Section~\ref{sec-tsimAlg}, and the correctness of of \patedgeinsert. Indeed, \patedgeinsert only removes
-nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
-(c) \comb, whose analysis follows the same way as that for \patedgeinsert; and
-(d) the early return property (by Lemma~\ref{lemma-approximation-bound}).
-
-\vspace{-1.5ex}
-Procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$ time, where it takes $O(2^{h}\cdot|\Delta P|)$ time to update \bfc, $O(2^{h}\cdot h)$ to do the AND-operation, and $O(||\affballsx||)$ to identify \affballsx.
-%Thus, procedure \identifyaffball runs in $O(2^{h}\cdot(|\Delta P|+h) +||\affballsx||)$.
-As $h$ is typically small, \eg 2 to 5, thus \identifyaffball is in $O(|\Delta P|+||\affballsx||)$;
-\patedgeinsert is in $O(|M(P_{fi}, \ball{[v,r]})|+|V_{P_{fi}}||E_{\ball{[v,r]}}|)$ time.
-Indeed, the recursive process for checking invalid nodes in $M(P_{fi}, \ball{[v,r]})$ is bounded by $O(|V_{P_{fi}}||E_{\ball{[v,r]}}|)$,
-and the process to update $M(P_{fi}, \ball{[v,r]})$ is bounded by the size of its changes, which is monotonically decreasing;
-According to \patedgeinsert,
-\comb is in $O(|\bigcup^{h}_{i=1} rM(P_{fi}\oplus\Delta P_{fi},\ball{[v,r]})|+r|V_{P\oplus \Delta P}||E_{\ball{[v,r]}}|)$ time.
-
-\vspace{-1.5ex}
-Putting these together, algorithm \incp is in
-$O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|+r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|) + r|P \oplus \Delta P||\affballsx|$ +$|\Delta P|)$ time \wrt $\Delta P$.
-
-\noindent
-{\textbf{2. Algorithm \incd (Section~\ref{subsec-Ginc})}}
-
-The correctness of \incd \wrt $\Delta G$ is assured by the correctness of
-\identifyaffball (by Proposition~\ref{prop-affected-datainc}) and procedures \incmatch and \comb,
-which can be proved along the same lines as for pattern updates.
-
-\vspace{-1.5ex}
-One can verify that procedure \identifyaffball is in $O(|\affballsx|)$,
-\incmatch for all fragments and all \affballsx is in $O(|P||\affballsx|)$ time, and \comb is in $O(\bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|$ + $r|V_{P}||E_{\widehat{G\oplus\Delta G}}|)$ time.
-Therefore, algorithm \incd is in
-$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|+r|P||\affballsx|)$ time \wrt $\Delta G$.
-
-\vspace{1ex}
-\noindent
-{\large \textbf{Appendix D: Extra Experiments}}
-\label{sec-apd-exp}
-
-\vspace{-0.5ex}
-
-We also used another real-life dataset {\em \youtube}~\cite{youtubeWeb} for experimental verification.
-It contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos.
-We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.
-
-\vspace{-1.5ex}
-The experimental results on \youtube are reported here.
-
-\vspace{-1.8ex}
-\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis, \denalk on \youtube \wrt four quality measures.
-The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.
-We find \optgrouprec strikes a balance at capturing the practical requirements.
-
-\vspace{-1.8ex}
-\stitle{Exp-2: Efficiency of \inc for one set of updates}.
-Varying the amount of updates in one update set from 4.5\% to 49.5\% for pattern updates, 2.5\% to 27.5\% (resp.
-3\% to 33\%) for data insertions and hybrid data updates (resp.
-data deletions), and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous pattern and data updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
-We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%).
-%for hybrid pattern, hybrid data, and simultaneous pattern and data updates.
-
-\vspace{-1.8ex}
-\stitle{Exp-3: Efficiency of \inc for continuous sets of updates}. We generated 5 sets of updates,
-varying the amount of updates from 4.5\% to 27\% for pattern updates, 2.5\% to 15\% for data updates,
-and (4.5\%, 2.5\%) to (22.5\%, 12.5\%) for simultaneous pattern and data updates.
-We evaluated the average time took by \inc to process these sets of updates one by one.
-The results are reported in Fig.~\ref{fig-exp-patinc-multi-youtube} to~\ref{fig-exp-hyb-datapat-multi-youtube}.
-We find \inc outperforms \optgrouprec when changes are no more than 27\%, 10\% and (13.5\%, 7.5\%) for continuous pattern, data and simultaneous updates respectively.
-
-\vspace{-1.8ex}
-\stitle{Exp-4: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-youtube-extraspace},
-it takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which need 114MB space to store itself,
-\ie 50.8\% compared with the original dataset.

### 2017-10-06 Gruba/01-intro.tex

@@
 
-The contributions of this work include:
-\begin{itemize}
-\item We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model in literature.
-\item We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/recent interests and explicit/implicit interests.
-\item We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.
-\end{itemize}
+\stitle{Contributions.}  The contributions of this work include:
 
-The rest of this paper is organized as follows.
+\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model in literature.
+
+\stab(2) We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/recent interests and explicit/implicit interests.
+
+\stab(3) We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.
+
+\stitle{Organization.} The rest of this paper is organized as follows.
 Section \ref{sec:overv} first gives the problem formulation and subsequently overviews \sys{}'s components, principle of which are detailed in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.

### 2017-10-06 Gruba/10-appendix.tex

\newpage
\section{Appendix}
\label{sec:appendix}

### 2017-10-06 Gruba/05-gm.tex

@@
-\section{Group Modeler}
+\section{Group based Behavior Modelling}
 \label{sec:gm}
@@
 \begin{itemize}
-	\item \textit{User Part} contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.
-	\item \textit{Blog Part} consists of a metric $C_h$, referring to the correlation between blog contents and recent events returned by Ring \refe{}.
+	\item \textit{User Info}: contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.
+	\item \textit{Blog Info}: consists of a metric $C_h$, referring to the correlation between blog contents and recent events returned by Ring \refe{}.
 $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}).
 Specifically, each event could be viewed as a topic $t$, over which the correlation of a blog $b$ could be obtained by formula \ref{eq:simbt}.
-	\item \textit{Interaction Part} includes three correlation metrics.
+	\item \textit{Interaction Info}: includes three correlation metrics.
 They are of blog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.

### 2017-10-06 Gruba/06-perf.tex

@@
 \centering
-\includegraphics[width=.96\linewidth]{figures/Interests}
-\caption{Testing Results with Various $\alpha$ \tbc{}}
+\includegraphics[width=.7\linewidth]{figures/Interests}
+\caption{Testing Results with Various $\alpha$.}
 \label{fig:fe}
@@
 \centering
-\includegraphics[width=.96\linewidth]{figures/clustering}
-\caption{Silhouette Coefficient Values for Various Cluster Numbers over Different Testing Datasets \tbc{}}
+\includegraphics[width=.7\linewidth]{figures/clustering}
+\caption{Silhouette Coefficient Values for Various Cluster Numbers over Different Testing Datasets.}
 \label{fig:uc}
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
     \label{fig:10-a}
-    \includegraphics[width=0.4\textwidth]{figures/precision.eps}}
-  \hspace{1in}
+    \includegraphics[width=0.3\textwidth]{figures/precision.eps}}
+  %\hspace{1in}
   \subfigure[Recall]{
     \label{fig:10-b}
-    \includegraphics[width=0.4\textwidth]{figures/recall.eps}}
-  \hspace{1in}
+    \includegraphics[width=0.3\textwidth]{figures/recall.eps}}
+  %\hspace{1in}
   \subfigure[$F_1$ Score]{
     \label{fig:10-c}
-    \includegraphics[width=0.4\textwidth]{figures/F-Measure.eps}}
-  \caption{Performance of \sys{} Versus LRC-BQ \tbc{}}
+    \includegraphics[width=0.3\textwidth]{figures/F-Measure.eps}}
+  \caption{Performance of \sys{} Versus LRC-BQ.}
   \label{fig:10}
-\end{figure}
+\end{figure*}
 
@@
     \label{fig:11-a}
-    \includegraphics[width=0.4\textwidth]{figures/precisionofdifferentfeatures.eps}}
-  \hspace{1in}
+    \includegraphics[width=0.3\textwidth]{figures/precisionofdifferentfeatures.eps}}
+  %\hspace{1in}
   \subfigure[Recall]{
     \label{fig:11-b}
-    \includegraphics[width=0.4\textwidth]{figures/recallofdifferentfeatures.eps}}
-  \hspace{1in}
+    \includegraphics[width=0.3\textwidth]{figures/recallofdifferentfeatures.eps}}
+  %\hspace{1in}
   \subfigure[$F_1$ Score]{
     \label{fig:11-c}
-    \includegraphics[width=0.4\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
-  \caption{\sys{} Performance of Using Various Data Items for Modeling \tbc{}}
+    \includegraphics[width=0.3\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
+  \caption{\sys{} Performance of Using Various Data Items for Modeling.}
   \label{fig:11}
-\end{figure}
+\end{figure*}

### 2017-10-06 TF-vldb2018/full/sec-appendix.tex

@@
 and then removes nodes from $\matchs(u)$ iteratively (lines 3-7).
-A node $w$ is removed from $\matchs(u)$ if there is a adjacent node $u'$ of $u$,
+A node $w$ is removed from $\matchs(u)$ if there is an adjacent node $u'$ of $u$,
 but there exists no adjacent node $w'$ of $w$ such that $w'\in \matchs(u')$.
@@
 (b) Check for each $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, whether $x_v \leq y_u$ holds.
-One can verify that step (a) is in $O(|P|^2)$ time by invoking procedure~\ref{alg-rsim}; and step (b) can be checked in $O(|P|^2)$ time as the size of $M$ is bounded by $|P|^2$.
+One can verify that step (a) is in $O(|P|^2)$ time by invoking procedure \rgraphsim; and step (b) can be checked in $O(|P|^2)$ time as the size of $M$ is bounded by $|P|^2$.
 Thus the algorithm is overall in $O(|P|^2)$ time.
@@
 \vspace{-1.5ex}
-(I) We firstly prove that the when the algorithm outputs ``yes", then pattern $P$ is indeed satisfiable.
+(I) We firstly prove that when the algorithm outputs ``yes", then pattern $P$ is indeed satisfiable.
 This is correct since if the algorithm outputs ``yes", \ie $P \eps P$ \wrt $\Reps$ and capacity bounds in $\Reps$ are satisfied, there must exist a data graph $G$ such that $P \eeps G$.
@@
 		\begin{minipage}[t]{0.4\textwidth}
-			%\vspace{-20.3ex}
+			\vspace{-0.6ex}
 			\begin{center}
 				\subfigure[{Unboundedness of unit pattern update}]{\label{fig-inc-complexity-pattern}
-					\includegraphics[scale=0.28]{./fig/inc-complexity-proof-pattern.eps}}
+					\includegraphics[scale=0.29]{./fig/inc-complexity-proof-pattern.eps}}
 			\end{center}
@@
 We will prove this by contradiction.
-We consider case (i) $P \not\eps P$ and assume that $P$ is satisfiable in this case.
+We consider case (i) $P \not\eps P$ and assume that $P$ is satisfiable.
 For convenience, we use $P_1 \not\eps P_2$ to denote $P \not\eps P$, while $P_1$, $P_2$ and $P$ are exactly same.
 From that $P$ is satisfiable, we know that there exists a data graph $G$ such that $P_1 \eeps G$, $P_2 \eeps G$ and $P_1 \eeps G_s$, where $G_s$ is the perfect subgraph in $G$.
-By the definition of team simulation and graph simulation, from $P_2 \eeps G$, we know that $G_s \eps P_2$ holds;
-from $P_1 \eeps G_s$, we know that $P_1 \eps G_s$ holds; and 
-from $P_1 \eps G_s$ and  $G_s \eps P_2$, we know that $P_1 \eeps P_2$ holds.
+By the definition of team simulation and graph simulation, from $P_2 \eeps G$, we know that $G_s \eps P_2$;
+from $P_1 \eeps G_s$, we know that $P_1 \eps G_s$; and 
+from $P_1 \eps G_s$ and  $G_s \eps P_2$, we know that $P_1 \eps P_2$.
 This contradicts the assumption.
-We then consider case (ii), \ie $P \eps P$ \wrt $\Reps$ while there exists $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v > y_u$, and assume that $P$ is satisfiable.
+We then consider case (ii), $P \eps P$ \wrt $\Reps$ while there exists $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, and $x_v > y_u$, and assume that $P$ is satisfiable.
 From $P$ is satisfiable, we know that there exists a data graph $G$ such that $P \eeps G$.
-From $P \eps P$, we know that for any nodes $w$ in $G$, if $w$ matches with the pattern node $v$, then it must match with the pattern node $u$, that is, the number of data nodes match with $u$ is larger than that of data nodes match with $v$.
+From $P \eps P$ \wrt $\Reps$ and $(u, v)\in \Reps$, we know that for any nodes $w$ in $G$, if $w$ matches the pattern node $v$, then it must match the pattern node $u$, that is, the number of data nodes match $u$ is larger than that of data nodes match $v$.
 However, this contradicts that the upper bound of $u$ ($y_u$) is smaller than the lower bound of $v$ ($x_v$).
-
-%By (I) and (II), we have proven that the algorithm is correct.
+%From (I) and (II) the correctness of the algorithm follows.
 
@@
 We will prove Theorem~\ref{thm-tsim-radius} (1) firstly.
-We know that $P\eps \ball{[v, t]}$, and suppose that $M_t$ is a binary match relation for $P$ in $\ball{[v, t]}$.
+We know that $P\eps \ball{[v, t]}$, and suppose that $M_t$ is the maximum match relation for $P$ in $\ball{[v, t]}$.
 Since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, 
@@
 $(u, v) \in M_r$ holds, where $v$ is the matched data node of $u$ in $\ball{[v, r]}$, \ie $M_t \subset M_r$.
-Since $M_t$ is a match relation for $P$ in $\ball{[v, t]}$ and $M_t \subset M_r$, by the definition of graph simulation, then $P\eps \ball{[v, r]}$ and $M_r$ is a match relation for $P$ in $\ball{[v, r]}$.
+Since $M_t$ is the maximum match relation for $P$ in $\ball{[v, t]}$ and $M_t \subset M_r$, by the definition of graph simulation, then $P\eps \ball{[v, r]}$ and $M_r$ is a match relation for $P$ in $\ball{[v, r]}$.
 
@@
 	\label{lemma-innerball}
-	For any data graphs $G_1$ and $G_2$, pattern graph $P$. If $G_1$ is a subgraph of $G_2$,
+	For any data graphs $G_1$ and $G_2$, and pattern graph $P$, if $G_1$ is a subgraph of $G_2$,
 	then $M_1 \subset M_2$, where $M_i$ $(i=1,2)$ is the maximum match relation for $P$ in $G_i$ via graph simulation. 
@@
 \vspace{-1.3ex}
-\stitle{Proofs of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
+\stitle{Proof of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
 We know that $G_1$ is a subgraph of $G_2$, and suppose $M_1 \not\subset M_2$.
@@
 remove invalid matches from the initialized match relations $M$.
-Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, so $(u, v)$ is removed from $M_2$.
-As $G_1$ is a subgraph of $G_2$, so $(u, v)$ should also be removed from $M_1$, 
+Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, $(u, v)$ is removed from $M_2$.
+Since $G_1$ is a subgraph of $G_2$, $(u, v)$ should also be removed from $M_1$, 
 such that $(u, v) \not\in M_1$.
@@
 
-\vspace{-2ex}
+\vspace{-1.5ex}
 \etitle{Upper bound.} We show the \NP upper bound by providing an \NP algorithm to determine whether there exists an $h$-fragmentation of $P$.\,Given $P$, the algorithm works as follows.
@@
 \revise{
-\vspace{-2.5ex}
+\vspace{-1.5ex}
 \etitle{Lower bound.}
@@
 	%\end{widepage}
-	%\vspace{-0.5ex}
+	\vspace{-3.0ex}
 \end{figure*}

### 2017-10-06 TF-vldb2018/full/sec-appendix.tex

@@
 The process to compute maximum match relations for graph simulation is a recursive process to 
-remove invalid matches from the initialized match relations $M$.
+remove unmatched nodes from the initialized match relations $M$.
 Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, $(u, v)$ is removed from $M_2$.
@@
 Graph simulation is an iterative process to remove unmatched nodes from the candidate nodes,
-as illustrated in Fig.~\ref{alg-rsim} (lines~1-6).
+as illustrated in procedure \rgraphsim in Fig.~\ref{alg-rsim}.
 We utilize $M_{C}^{k}$ (resp. $M_{i}^{k}$, $M^{k}$) to denote the match relation for $P^{C}$ (resp. $P_{fi}$, $P$) in $\ball{}$ in the $kth$ iteration.
@@
 \sstab{(1)} For $k=0$, \ie the initialization step of graph simulation algorithm,
-the algorithm computes the set of candidate matches for each pattern node with the same label.
+the algorithm computes the set of candidate matches for each pattern node.
 As $P$ and $P^{C}$ have exactly the same node set, we have $M^{0}= M_{C}^{0}$.
@@
 \vspace{-1.8ex}
-\sstab{(2)} For $k=n$ $(n\geq 0)$, if $M^{n}\subseteq M_{C}^{n}$ exists, we prove $M^{n+1}\subseteq M_{C}^{n+1}$ exists in the $(n+1)th$ iteration.
-Suppose both $(u,w)\in M^{n}$ and $(u,w)\in M_{C}^{n}$ exist,
-and in the $(n+1)th$ iteration, $(u,w)$ is removed from $M_{C}^{n}$ if there is a adjacent node $u'$ of $u$ in $P_{C}$,
+\sstab{(2)} For $k=n$ $(n\geq 0)$, if $M^{n}\subseteq M_{C}^{n}$ holds, we prove $M^{n+1}\subseteq M_{C}^{n+1}$ holds in the $(n+1)th$ iteration.
+Suppose both $(u,w)\in M^{n}$ and $(u,w)\in M_{C}^{n}$ hold,
+and in the $(n+1)th$ iteration, $(u,w)$ is removed from $M_{C}^{n}$ if there is an adjacent node $u'$ of $u$ in $P_{C}$,
 but there exists no adjacent node $w'$ of $w$ in $G$ such that $(u',w')\in M_{C}^{n}$.
@@
 
-The proposition is correct as when $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
-\identifyaffball identifies \affballsx who already match with each fragment of $P$;
+The proposition is correct as when $\Delta P$ comes, the perfect subgraphs must reside in the balls that match all pattern fragments of $P\oplus \Delta P$.
+\identifyaffball identifies \affballsx who already match all fragments of $P$;
 Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
-there must exist an update in $\Delta P$ on $P_{fi}$,
-such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
-Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.
+there must exist an edge/node deletion in $\Delta P$ on $P_{fi}$,
+such that the ball may match the updated fragment $P_{fi}\oplus \Delta P$.
+Thus, \identifyaffball filters out the balls that cannot not match at least one fragment of $P$, and there are no deletion updates on the fragment.
 
@@
 The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
-\identifyaffball filters out the balls that cannot match all $h$ pattern fragments,	and there are no data updates on the ball.
+\identifyaffball filters out the balls that cannot match all pattern fragments,	and there are no data updates on the ball.
 
@@
 nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
-(c) \comb, whose analysis follows the same way as that for \patedgeinsert; and
+(c) \comb, whose analysis follows the same way as that of \patedgeinsert; and
 (d) the early return property (by Lemma~\ref{lemma-approximation-bound}).

### 2017-10-07 TF-vldb2018/full/sec-appendix.tex

@@
 			\begin{center}
-				\subfigure[{Unboundedness of unit data update}]{\label{fig-inc-complexity-data}
+				\subfigure[{Unit data update}]{\label{fig-inc-complexity-data}
 					\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}}
 			\end{center}
-			\vspace{-3.5ex}
+			\vspace{-2.5ex}
 		\end{minipage}
@@
 			\begin{center}
-				\subfigure[{Unboundedness of unit pattern update}]{\label{fig-inc-complexity-pattern}
+				\subfigure[{Unit pattern update}]{\label{fig-inc-complexity-pattern}
 					\includegraphics[scale=0.29]{./fig/inc-complexity-proof-pattern.eps}}
 			\end{center}
-			\vspace{-3.5ex}
+			\vspace{-2.5ex}
 		\end{minipage}
 	\end{center}
-	\vspace{-3ex}
-	%\caption{Performance evaluation of algorithm \optgrouprec for top-$k$ team formation}
-	%\label{exp-semantic-effectiveness-citation}
+	\vspace{-4ex}
+	\caption{Unboundedness of unit data and pattern update}
+	\label{proof-patdata-inc}
 	%\end{widepage}
-	\vspace{-2.0ex}
+	\vspace{-3.0ex}
 \end{figure*}
@@
 %Following \cite{Reps96, FanWW13-tods},
-Consider the following pattern and data graph, and unit data updates.
+Consider the following pattern and data graph, and unit data updates, as shown in Fig.~\ref{proof-patdata-inc} (a).
 Let data graph $G$ consist of two chains ($a_1$, $b_1$, $c_1$, \ldots, $a_n$, $b_n$, $c_n$) and ($a_{n+1}$, $b_{n+1}$, $c_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$) where $a_i$, $b_i$ and $c_i$ have labels $A$, $B$ and $C$ respectively.
@@
 \etitle{(II) \dynteamF\, is unbounded for unit pattern update}.
-Consider the following pattern and data graph, and unit pattern updates.
+Consider the following pattern and data graph, and unit pattern updates, as shown in Fig.~\ref{proof-patdata-inc} (b).
 Let data graph $G$ be a cycle ($a'_1$, $b'_1$, $c'_1$, $d'_1$, \ldots, $a'_m$, $b'_m$, $c'_m$, $d'_m$, $a'_1$),
@@
 
-\vspace{4ex}
 \noindent
@@
 \vspace{-0.5ex}
-
-We also used another real-life dataset {\em \youtube}~\cite{youtubeWeb} for experimental verification.
-It contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos.
-We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.
-
-\vspace{-1.5ex}
 The experimental results on \youtube are reported here.
@@
 \vspace{-1.8ex}
-\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis, \denalk on \youtube \wrt four quality measures.
+\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis and \denalk on \youtube \wrt four quality measures.
 The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.

### 2017-10-07 TF-vldb2018/full/sec-appendix.tex

@@
 \vspace{-1.8ex}
-\stitle{Exp-2: Efficiency of \inc for one set of updates}.
+\stitle{Exp-2: Efficiency of \inc for single set of updates}.
 Varying the amount of updates in one update set from 4.5\% to 49.5\% for pattern updates, 2.5\% to 27.5\% (resp.
@@
 data deletions), and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous pattern and data updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
-We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%).
+We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%), respectively.
 %for hybrid pattern, hybrid data, and simultaneous pattern and data updates.

### 2017-10-07 TF-vldb2018/full/sec-appendix.tex

@@
 
-\vspace{-1.5ex}
+%\vspace{-0.5ex}
 \etitle{(I) \dynteamF\, is unbounded for unit data update}.
 %Following \cite{Reps96, FanWW13-tods},
-Consider the following pattern and data graph, and unit data updates, as shown in Fig.~\ref{proof-patdata-inc} (a).
+Consider the following pattern and data graph, as shown in Fig.~\ref{proof-patdata-inc} (a), and unit data updates.
 Let data graph $G$ consist of two chains ($a_1$, $b_1$, $c_1$, \ldots, $a_n$, $b_n$, $c_n$) and ($a_{n+1}$, $b_{n+1}$, $c_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$) where $a_i$, $b_i$ and $c_i$ have labels $A$, $B$ and $C$ respectively.
@@
 \etitle{(II) \dynteamF\, is unbounded for unit pattern update}.
-Consider the following pattern and data graph, and unit pattern updates, as shown in Fig.~\ref{proof-patdata-inc} (b).
+Consider the following pattern and data graph, as shown in Fig.~\ref{proof-patdata-inc} (b), and unit pattern updates.
 Let data graph $G$ be a cycle ($a'_1$, $b'_1$, $c'_1$, $d'_1$, \ldots, $a'_m$, $b'_m$, $c'_m$, $d'_m$, $a'_1$),
@@
 \vspace{-1.8ex}
-\stitle{Exp-3: Efficiency of \inc for continuous sets of updates}. We generated 5 sets of updates,
-varying the amount of updates from 4.5\% to 27\% for pattern updates, 2.5\% to 15\% for data updates,
+\stitle{Exp-3: Efficiency of \inc for continuous sets of updates}. We generated 5 sets of hybrid updates,
+varying the amount of updates in each set from 4.5\% to 27\% for pattern updates, 2.5\% to 15\% for data updates,
 and (4.5\%, 2.5\%) to (22.5\%, 12.5\%) for simultaneous pattern and data updates.
-We evaluated the average time took by \inc to process these sets of updates one by one.
+We tested the average time took by \inc to process all these sets one by one.
 The results are reported in Fig.~\ref{fig-exp-patinc-multi-youtube} to~\ref{fig-exp-hyb-datapat-multi-youtube}.
-We find \inc outperforms \optgrouprec when changes are no more than 27\%, 10\% and (13.5\%, 7.5\%) for continuous pattern, data and simultaneous updates respectively.
+We find \inc outperforms \optgrouprec when changes are no more than 27\%, 10\% and (13.5\%, 7.5\%) for continuous pattern, data and simultaneous pattern and data updates, respectively.
 
@@
 \stitle{Exp-4: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-youtube-extraspace},
-it takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which need 114MB space to store itself,
+it takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which needs 114MB space to store itself,
 \ie 50.8\% compared with the original dataset.

### 2017-10-07 TF-vldb2018/full/sec-appendix.tex

@@
 %Following \cite{Reps96, FanWW13-tods},
-Consider the following pattern and data graph, as shown in Fig.~\ref{proof-patdata-inc} (a), and unit data updates.
+Consider the following pattern and data graph, as shown in Fig.~\ref{proof-patdata-inc}(a), and unit data updates.
 Let data graph $G$ consist of two chains ($a_1$, $b_1$, $c_1$, \ldots, $a_n$, $b_n$, $c_n$) and ($a_{n+1}$, $b_{n+1}$, $c_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$) where $a_i$, $b_i$ and $c_i$ have labels $A$, $B$ and $C$ respectively.
@@
 \etitle{(II) \dynteamF\, is unbounded for unit pattern update}.
-Consider the following pattern and data graph, as shown in Fig.~\ref{proof-patdata-inc} (b), and unit pattern updates.
+Consider the following pattern and data graph, as shown in Fig.~\ref{proof-patdata-inc}(b), and unit pattern updates.
 Let data graph $G$ be a cycle ($a'_1$, $b'_1$, $c'_1$, $d'_1$, \ldots, $a'_m$, $b'_m$, $c'_m$, $d'_m$, $a'_1$),

### 2017-10-08 TF-vldb2018/full/sec-appendix.tex

@@
 
-\noindent
-{\textbf{5. Proof of Proposition~\ref{prop-fragmentation}}}
-
-The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
-is to decide whether there exists a fragmentation \{${P}_{f1}$, \ldots, $P_{fh}$, $C$\} such that,
-(a) $\max_i |P_{fi}| \leq r_1\cdot\frac{|P|}{h}$ and (b) $|C|\leq r_2|P|$.
-
-\vspace{-1.5ex}
-\etitle{Upper bound.} We show the \NP upper bound by providing an \NP algorithm to determine whether there exists an $h$-fragmentation of $P$.\,Given $P$, the algorithm works as follows.
-\looseness=-1
-
-\vspace{-1.8ex}
-\sstab{(1)} Guess an $h$-fragmentation ${\cal P}_h$ of $P$.
-
-\vspace{-1.8ex}
-\sstab{(2)} Check whether it satisfies restrictions of $r_1$ and $r_2$ (conditions (a) and (b) in the definition of $\kw{dOFGP}$).
-If so, return yes, otherwise go to the first step and guess another instance.
-
-\vspace{-1.5ex}
-The algorithm is in \NP since step~(2) can be checked in \PTIME (liner time, indeed).
-
-\revise{
-\vspace{-1.5ex}
-\etitle{Lower bound.}
-We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
-by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.
-
-\vspace{-1ex}
-An instance of the minimum cut problem is given an undirected graph $H=(V_{H},E_{H})$ and a positive integer $m$,
-to find a set $S \subseteq E_{H}$ of edges whose removal leaves two disjoint connected components, with $|S|\leq m$.
-
-\vspace{-1ex}
-Given an instance of the minimum cut problem,
-we construct an instance of $h$-fragmentation problem.
-It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
-Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.}
-
-\eat{%%%% Wrong proof %%%
-\vspace{-2.5ex}
-\etitle{Lower bound.}
-We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
-by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.
-
-\vspace{-2ex}
-An instance of the minimum cut problem is given an undirected graph $H=(V_{H},E_{H})$ and a positive integer $m$,
-to find a set $S \subseteq E_{H}$ of edges whose removal leaves two disjoint connected components, with $|S|\leq m$.
-
-\vspace{-2ex}
-Given an instance of the minimum cut problem,
-we construct an instance of $h$-fragmentation problem.
-It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
-Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.
-}%%EAT
-
-\noindent
-{\textbf{6. Proof of Proposition~\ref{prop-canaffballs}}}
-
-The proposition is correct as when $\Delta P$ comes, the perfect subgraphs must reside in the balls that match all pattern fragments of $P\oplus \Delta P$.
-\identifyaffball identifies \affballsx who already match all fragments of $P$;
-Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
-there must exist an edge/node deletion in $\Delta P$ on $P_{fi}$,
-such that the ball may match the updated fragment $P_{fi}\oplus \Delta P$.
-Thus, \identifyaffball filters out the balls that cannot not match at least one fragment of $P$, and there are no deletion updates on the fragment.
-
-\noindent
-{\textbf{7. Proof of Proposition~\ref{prop-affected-datainc}}}
-
-The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
-\identifyaffball filters out the balls that cannot match all pattern fragments,	and there are no data updates on the ball.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\noindent
+{\textbf{5. Proof of Proposition~\ref{prop-fragmentation}}}
+
+The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
+is to decide whether there exists a fragmentation \{${P}_{f1}$, \ldots, $P_{fh}$, $C$\} such that,
+(a) $\max_i |P_{fi}| \leq r_1\frac{|P|}{h}$ and (b) $|C|\leq r_2|P|$.
+
+\vspace{-1.5ex}
+\etitle{Upper bound.} We show the \NP upper bound by providing an \NP algorithm to determine whether there exists an $h$-fragmentation of $P$.\,Given $P$, the algorithm works as follows.
+\looseness=-1
+
+\vspace{-1.8ex}
+\sstab{(1)} Guess an $h$-fragmentation ${\cal P}_h$ of $P$.
+
+\vspace{-1.8ex}
+\sstab{(2)} Check whether it satisfies restrictions of $r_1$ and $r_2$ (conditions (a) and (b) in the definition of $\kw{dOFGP}$).
+If so, return yes, otherwise go to the first step and guess another instance.
+
+\vspace{-1.5ex}
+The algorithm is in \NP since step~(2) can be checked in \PTIME (liner time, indeed).
+
+\vspace{-1.5ex}
+\etitle{Lower bound}.
+We next show that $\kw{dOFGP}(P, h, r_1, r_2)$ is \NP-hard by
+reduction from the 3\SAT\ problem. An instance of 3\SAT\ is a formula
+$\psi = C_{1}\land \ldots \land C_{m}$, where each $C_{i}$ is a
+disjunction of three literals, \ie $C_{i} = \ell_{1}^{i}\lor
+\ell^{i}_{2}\lor \ell^{i}_{3} (i\in [1, m])$, in which
+$\ell_{j}^{i}(j\in [1, 3])$ is either a variable $x_{k}$ or the
+negation of variable $\bar x_{k} (k\in [1, n])$ from a universal set $U =
+\{x_{1}, \ldots, x_{n}\}$ of variables. Given a $\psi$, 3\SAT\ is to decide
+whether $\psi$ is satisfiable, \ie there exists a truth assignment $\mu$ to
+variables in $U$ such that $\psi$ is \True\ under $\mu$. It is known that 3\SAT\
+is \NP-complete~\cite{Papa1994}.
+
+\vspace{-1.5ex}
+Given $\psi$ of 3\SAT, we next construct an instance of $\kw{dOFGP}$, \ie a
+pattern graph $P$, the number of fragments $h$, and two ratios $r_{1}$ and
+$r_{2}$, such that $\psi$ is satisfiable if and only if $\kw{dOFGP}(P, h,
+r_{1}, r_{2})$ is \True.
+
+\vspace{-1.5ex}
+\eetitle{(1) Pattern graph $P$}. Pattern $P$ is constructed in two steps:
+(1.a) construct a graph $P'$; and (1.b) expand $P'$ to $P$. We below
+describe the two steps.
+
+\vspace{-1.5ex}
+\sstab
+(1.a) $P'$ is constructed as follows. 
+First, for each $C_{i} (i\in [1, m])$, construct a set $V_{i}$ of
+three nodes $u_{1}^{i}$, $u_{2}^{i}$, and $u_{3}^{i}$, yielding $3m$ nodes in
+$V_{1}$, \ldots, $V_{m}$. Intuitively, node $u^{i}_{j}(i\in [1, m], j\in
+[1, 3])$ is to encode literal $\ell_{j}^{i}$. 
+Then connect nodes as follows: for each $i, j \in [1, m]$ and $i\neq j$, connect
+$u^{i}_{s}$ in $V_{i}$ and $u^{j}_{t}$ in $V_{j}$ ($s, t\in [1, 3]$) if they do not encode
+complement literals, \ie $\ell^{j}_{t} \neq \bar \ell^{i}_{s}$. In other words,
+$u^{j}_{t}$ and $u^{i}_{s}$ are not connected only when $\ell^{i}_{s} = x$ and
+$\ell^{j}_{t} = \bar x$ or $\ell^{i}_{s} = \bar x$ and
+$\ell^{j}_{t} = x$  for some $x \in U$.
+
+%One can verify the following property.
+
+%Property (I): $\psi$ is satisfiable if and only if $P'$ has an $m$-clique.
+
+\vspace{-1.5ex}
+\sstab
+(1.b) We next expand $P'$ to $P$ as follows. For each node set $V_{i}$
+constructed in $P'$, connect it with an $(m-2)$-clique $K_{i}$, such that 
+each node $u^{i}_{j}(j\in [1,3])$ in $V_{i}$ is connected to every node in
+the clique $K_{i}$.
+
+%Hence $P$ has $(m-2) * m + 3m = m^{2}+m$ nodes and $(C_{m-2}^{2}+3*(m-2))*m + $
+%One can verify the following property.
+
+%Property (II): $P$ has
+
+\vspace{-1.5ex}
+\eetitle{(2) $h$}.  Let $h = m + 1$.
+
+\vspace{-2ex}
+\eetitle{(3) $r_{1}$}. Let $r_{1} = (m+1)*(C_{m}^{2}+m)/|P|$, \ie
+$r_{1}*\dfrac{|P|}{h} = C_{m}^{2}+m$ is the size of a $m$-clique.
+
+\vspace{-1.5ex}
+\eetitle{(4) $r_{2}$}. Let $r_{2} = \dfrac{|E_{P}| - (C_{m}^{2} + m) -
+	m*(C_{m}^{2} + m -1)}{|P|}$.
+
+\vspace{-1.0ex}
+One can verify that $\psi$ is satisfiable if and only if $P$ has an $h$-fragmentation $P_{1}$,
+\ldots, $P_{h}$ such that $max_{i}|P_{i}|\leq r_{1}*\frac{|P|}{h} (i\in [1, h])$
+and $|C|\leq r_{2}*|P|$.
+This indeed is verified by using the following properties of
+the above construction:
+
+\vspace{-2.5ex}
+\bi
+\item[$\circ$] $\psi$ is satisfiable if and only if $P'$ has an $m$-clique; 
+\item[$\circ$] $P$ has a unique $m+1$ fragmentation satisfying that
+(i) an $m$-clique is the largest fragment and
+(ii) cut is no larger than $|E_{P}| - (C_{m}^{2} + m) -
+m*(C_{m}^{2} + m -1)$: the $m$-clique fragment must come from $P'$, which
+leaves the $m$ extended $(m-2)$-clique as the remaining $m$ fragments, each
+of size equal to that of an $m$-clique minus 1.
+\ei
+
+\noindent
+{\textbf{6. Proof of Proposition~\ref{prop-canaffballs}}}
+
+The proposition is correct as when $\Delta P$ comes, the perfect subgraphs must reside in the balls that match all pattern fragments of $P\oplus \Delta P$.
+\identifyaffball identifies \affballsx who already match all fragments of $P$;
+Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
+there must exist an edge/node deletion in $\Delta P$ on $P_{fi}$,
+such that the ball may match the updated fragment $P_{fi}\oplus \Delta P$.
+Thus, \identifyaffball filters out the balls that cannot not match at least one fragment of $P$, and there are no deletion updates on the fragment.
+
+\noindent
+{\textbf{7. Proof of Proposition~\ref{prop-affected-datainc}}}
+
+The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
+\identifyaffball filters out the balls that cannot match all pattern fragments,	and there are no data updates on the ball.
+
 \vspace{1ex}
@@
 $O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|+r|P||\affballsx| + |\Delta G|)$ time \wrt $\Delta G$.
-
-\vspace{1ex}
-\noindent
-{\large \textbf{Appendix D: Extra Experiments}}
-\label{sec-apd-exp}
-
-\vspace{-0.5ex}
-The experimental results on \youtube are reported here.
-
-\vspace{-1.8ex}
-\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis and \denalk on \youtube \wrt four quality measures.
-The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.
-We find \optgrouprec strikes a balance at capturing the practical requirements.
-
-\vspace{-1.8ex}
-\stitle{Exp-2: Efficiency of \inc for single set of updates}.
-Varying the amount of updates in one update set from 4.5\% to 49.5\% for pattern updates, 2.5\% to 27.5\% (resp.
-3\% to 33\%) for data insertions and hybrid data updates (resp.
-data deletions), and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous pattern and data updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
-We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%), respectively.
-%for hybrid pattern, hybrid data, and simultaneous pattern and data updates.
-
-\vspace{-1.8ex}
-\stitle{Exp-3: Efficiency of \inc for continuous sets of updates}. We generated 5 sets of hybrid updates,
-varying the amount of updates in each set from 4.5\% to 27\% for pattern updates, 2.5\% to 15\% for data updates,
-and (4.5\%, 2.5\%) to (22.5\%, 12.5\%) for simultaneous pattern and data updates.
-We tested the average time took by \inc to process all these sets one by one.
-The results are reported in Fig.~\ref{fig-exp-patinc-multi-youtube} to~\ref{fig-exp-hyb-datapat-multi-youtube}.
-We find \inc outperforms \optgrouprec when changes are no more than 27\%, 10\% and (13.5\%, 7.5\%) for continuous pattern, data and simultaneous pattern and data updates, respectively.
-
-\vspace{-1.8ex}
-\stitle{Exp-4: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-youtube-extraspace},
-it takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which needs 114MB space to store itself,
-\ie 50.8\% compared with the original dataset.
 
@@
 \end{figure*}
+
+\noindent
+{\large \textbf{Appendix D: Extra Experiments}}
+\label{sec-apd-exp}
+
+\vspace{-0.5ex}
+The experimental results on \youtube are reported here.
+
+\vspace{-1.8ex}
+\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis and \denalk on \youtube \wrt four quality measures.
+The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.
+We find \optgrouprec strikes a balance at capturing the practical requirements.
+
+\vspace{-1.8ex}
+\stitle{Exp-2: Efficiency of \inc for single set of updates}.
+Varying the amount of updates in one update set from 4.5\% to 49.5\% for pattern updates, 2.5\% to 27.5\% (resp.
+3\% to 33\%) for data insertions and hybrid data updates (resp.
+data deletions), and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous pattern and data updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
+We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%), respectively.
+%for hybrid pattern, hybrid data, and simultaneous pattern and data updates.
+
+\vspace{-1.8ex}
+\stitle{Exp-3: Efficiency of \inc for continuous sets of updates}. We generated 5 sets of hybrid updates,
+varying the amount of updates in each set from 4.5\% to 27\% for pattern updates, 2.5\% to 15\% for data updates,
+and (4.5\%, 2.5\%) to (22.5\%, 12.5\%) for simultaneous pattern and data updates.
+We tested the average time took by \inc to process all these sets one by one.
+The results are reported in Fig.~\ref{fig-exp-patinc-multi-youtube} to~\ref{fig-exp-hyb-datapat-multi-youtube}.
+We find \inc outperforms \optgrouprec when changes are no more than 27\%, 10\% and (13.5\%, 7.5\%) for continuous pattern, data and simultaneous pattern and data updates, respectively.
+
+\vspace{-1.8ex}
+\stitle{Exp-4: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-youtube-extraspace},
+it takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which needs 114MB space to store itself,
+\ie 50.8\% compared with the original dataset.

### 2017-10-09 TF-vldb2018/sec-tsim.tex

@@
 %\vspace{-4ex}
-\subsection{Team Formation}
+\subsection{Team Simulation}
 \label{subsec-extsim}
@@
 Note that for traditional patterns~\cite{Galla06, b-matching,FanLMTWW10,FanCount16}, bounds are typically carried on edges, not on nodes.
-
 We also also denote data and pattern graphs as $G(V$, $E)$ and $P(V_{P}$, $E_{P})$ respectively.
@@
 
+\vspace{-1ex}
 \stitle{Remarks}.
@@
 
-\sstab(2) Different from strong simulation with balls having a fixed radius (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is flexible, and is only less than a user specified upper bound.
+\sstab(2) Different from strong simulation with a fixed radius for balls (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is auto-adjustable, having a user specified upper bound only.
 
@@
  It is worth mentioning that \dynteamF{} covers a broad range of dynamic situations,
-\ie handling continuous separate and simultaneous pattern and data updates.
+\ie handling continuously separate and simultaneous pattern and data updates.
 

### 2017-10-09 TF-vldb2018/sec-tsim.tex

@@
 
-\sstab(2) Different from strong simulation with a fixed radius for balls (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is auto-adjustable, having a user specified upper bound only.
+\sstab(2) Different from strong simulation with a fixed radius for balls (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of balls is auto-adjustable, having a user specified upper bound only.
 

### 2017-10-09 Gruba/07-rela.tex

@@
 \label{sec:rela}
+
+In this section, we will introduce the related work of user modeling in social network from the aspects of user features analysis, user groups mining and user behaviors modeling.
+Social media users's features we mentioned here include users's basic information, behavior features and interests features.\par
+
+Users's basic information we mentioned here include the users's gender, age, region, occupation and other personal information.
+There are many researches for analyzing users's basic information, such as users's racial information analysis \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, users's gender inference \cite{IEEEexample:conf/emnlp/CiotSR13}, users's actual age inference \cite{IEEEexample:conf/icde/ParkHHL09}, user policy orientation analysis (e.g.
+\cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private}), user's geo-location and occupation mining \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}, etc.
+Here, we did not do basic information mining for users.
+We used the user's basic information as important features for user clustering and behavior modeling.
+\par
+
+Social medias users's behaviors mainly refers to the tweeting and retweeting behaviors.
+Users's behaviors also have certain characteristics and regularity, which have been proved by a lot of existing work.
+Jiang et al.
+proposed a behavior dynamics model \cite{IEEEexample:jiang2013understanding}, theoretical analysis shows this model can properly explain various heavy-tailed inter-event time distributions, including a regular power law and some non-power-law deviations.
+Guo Z et al.\cite{IEEEexample:conf/music/GuoLTL12} analyzed the behavior of microblog users, the difference between the activity of users in different periods, and obtained the distribution of individual behavior on time.
+Pravallika Devineni et al.
+analyzed the wall activities of users focusing on identifying common patterns and proposed PowerWall distribution \cite{IEEEexample:journals/snam/DevineniKFF17}.
+What's more, it helped them spot surprising behaviors and anomalies.
+Considering the regularity of user behavior on time, we extracted characteristics of the user behavior as important features for user clustering and behavior modeling.\par
+
+As for users's interest, many methods has been proposed to do interests extraction.
+Zhiyuan et al.\cite{IEEEexample:journals/fcsc/LiuCS12} modeled users's interests through mining keywords.
+They extracted keywords from the users's microblogs by the combination of words frequency and translation model.
+Xu Z et al.\cite{IEEEexample:conf/webi/XuLXY11} proposed a method which extended user topic model to analyze users's interests.
+Michelson M et al.\cite{IEEEexample:conf/and/MichelsonM10} analyzed interests  based on a knowledge base.
+They used a knowledge base to identify and classify the entities in twitters of one user, then generate the user's interests category subtree to express his interests.
+Lim K H et al.\cite{IEEEexample:conf/wikis/LimD13} analyzed the celebrities a user mentioned, then they got the preference degree of the user in different interests categories.
+Bhattacharya P et al.\cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} proposed a method to extract a user's interests by analyzing the experts he followed.
+By digging a list of certain topics of the custom experts the user follows, they got the user's interests profiling.
+Wei Feng et al.\cite{IEEEexample:conf/icde/FengW14} studied the methods mapping tweets to hashtags to get users's preferences for hashtags.
+The existing methods for interest extraction have some shortcomings.
+The granularity of the result obtained by the methods based on keyword extraction is too small, and the result obtained by the user topic model is implicit and difficult to display.
+What's more, for the lack of a complete knowledge base, it's not easy to do interests extraction by using knowledge base.
+To solve the problems, we employed a cell lexicon to express user's interest.
+What's more, we combined Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF to extract the distribution of users's interest.\par
+
+There have also many studies on the user groups analysis.
+Some researches studied how to classify users under a specific situation.
+For instance, Marco Pennacchiotti et al.\cite{IEEEexample:conf/icwsm/PennacchiottiP11} classified users by race, political tendencies and so on.
+\cite{IEEEexample:journals/tkdd/ZhangCFLYZY17} analyzed the evolution of social groups, such as Facebook groups and Wechat groups, and proposed a new model for group evolution, which can provide insights about different evolution patterns of social groups.
+Xin Wang et al.
+\cite{IEEEexample:conf/aaai/WangDNGEB16} implemented a time-varying factorization to measure the user-group affinity for recommending groups to users.
+In addition, research for users community mining is a hot spot.
+Jaewon Yang et al.\cite{IEEEexample:conf/wsdm/YangL13} proposed a method based on non-negative matrix decomposition to mine user community.
+Yiye Ruan et al.\cite{IEEEexample:conf/www/RuanFP13} considered user's friends and user's text content into their method when measuring the similarity between users for clustering.
+He et al.
+\cite{IEEEexample:he2014overlapping}
+only considered the relationship between friends, and used the edge aggregation coefficient as a measure of clustering.
+Hiroaki Shiokawa et al.\cite{IEEEexample:conf/aaai/ShiokawaFO13} used the modular degree as a clustering standard and proposed an incremental algorithm to mine user community.
+As we can see, current analysis of user groups are diverse.
+However, users in social networks have multiple features, and many existing methods do not take advantage of these features to group users.
+Here we took user's basic, behavioral and interest information into account when performing user clustering, and we got distinguish groups with different statistical characteristics.\par
+
+As for behavior modeling, Jing Zhang et al.\cite{IEEEexample:journals/tkdd/ZhangTLLX15} proposed a method of analyzing users's retweeting behavior from the perspective of influence.
+Some researchers (e.g.
+\cite{IEEEexample:conf/wsdm/FengW13}, \cite{IEEEexample:conf/ijcai/ZhangLTCL13}) find that the user's reposting behavior is largely influenced by the relationship between friends, so they consider user's friend structure information into their models.
+Bo Jiang et al.
+\cite{IEEEexample:conf/cikm/JiangLSW15} proposed a method that combined matrix decomposition and microblogs clustering to analyze the user's reposting behavior.
+Zhang et al.\cite{IEEEexample:zhang2015retweet} proposed non-parametric statistical models to combine structural, textual, and temporal information together to predict reposting behavior.
+Considering the situation that users's not reposting does not mean that users are not interested in it, the users may just did not see it, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} applied a collaborative filtering method to the reposting behavior analysis.
+Maria Giatsoglou et al.
+explore the identification of fraudulent and genuine retweet threads and developed a realistic generator that mimics the behaviors of both honest and fraudulent users \cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15}.
+Suhas Ranganath et al.
+\cite{IEEEexample:journals/corr/RanganathMHTL15} were inspired by sociological theories of protest participation and proposed a framework to predict from the user¡¯s past status messages and interactions whether the next post of the user will be a declaration of protest.
+They evaluated the framework using data from Twitter on protests during the recent Nigerian elections and demonstrated that it could effectively work.
+Considering the fact that the amount of users in Social Medias is so huge, modeling for each user is not a good idea.
+However, modeling for a single user may make the model too particular.
+In addition, modeling for the whole users makes our model inaccuracy.
+So we divided users into several groups by users clustering. Then we get different behavior model for each group users respectively. \par

### 2017-10-09 Gruba/00-abstr.tex

\begin{abstract}
Social media applications are emerging, with rapidly growing users and large numbers of \retd{} blogs every minute.
The variety among users makes it difficult to model their \retg{} activities.
Obviously, it is not suitable to cover the overall users by a single model \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
Meanwhile, building one model per user is not practical.
To this end, this paper presents a novel solution, of which the principle is to model the \retg{} behavior over user groups.
Our approach, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests, which results deep analyses towards the \retg{} behavior and proper models in the end.
We have evaluated the performance of \sys{} by datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.
\end{abstract}
% behavior and activity in this paper are interchangeable

### 2017-10-09 Gruba/03-fe.tex

@@
 
-\section{Feature Extractor}
+\section{Feature Extraction}
 \label{sec:fe}
@@
 \centering
+\begin{small}
 \caption{Illustration of Variables in Info Feature}
@@
 \end{tabular}
+\end{small}
 \end{table}
@@
 \centering
+\begin{small}
 \caption{Category of Info}
@@
 
-\textit{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF \refe{} to calculate the weight distribution of words in blog $b$: 
+\textit{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in blog $b$:
 \begin{equation}

### 2017-10-09 Gruba/05-gm.tex

@@
 	\item \textit{User Info}: contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.
-	\item \textit{Blog Info}: consists of a metric $C_h$, referring to the correlation between blog contents and recent events returned by Ring \refe{}.
+	\item \textit{Blog Info}: consists of a metric $C_h$, referring to the correlation between blog contents and recent events returned by Ring \cite{IEEEexample:ring}.
 $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}).

### 2017-10-09 Gruba/06-perf.tex

@@
 
-We have employed a real-world dataset Sina \refe{} that consists of 24 million blogs that are associated with 43.5K users.
+We have employed a real-world dataset Sina that consists of 24 million blogs that are associated with 43.5K users.
 
@@
 in User Cluster, we studied the clustering solutions with the minimum/maximum number of clusters 2 and 10;
-in Behavior Modeler, a user's recent 30 days blogs are used for short-term interest analysis and popular words of the latest 24 hours are returned by Ring \refe{} as the Big Thing keyword.
+in Behavior Modeler, a user's recent 30 days blogs are used for short-term interest analysis and popular words of the latest 24 hours are returned by Ring as the Hot Event keywords.
 
@@
 \centering
-\includegraphics[width=.7\linewidth]{figures/clustering}
+\includegraphics[width=.85\linewidth]{figures/clustering}
 \caption{Silhouette Coefficient Values for Various Cluster Numbers over Different Testing Datasets.}
@@
 %
-Fig.\ \ref{fig:10} shows the performance of \sys{} against state of the art approach LRC-BQ \refe{}.
+Fig.\ \ref{fig:10} shows the performance of \sys{} against state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
 We compare the metrics of precision, recall, as well as $F_1$ score.
-LRC-BQ \refe{} does not deal with user grouping.
-Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering), but also examine \sys{} versus LRC-BQ \refe{} in the case that all users are in mono group (i.e., ``All-Users'').
+LRC-BQ does not deal with user grouping.
+Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering), but also examine \sys{} versus LRC-BQ in the case that all users are in mono group (i.e., ``All-Users'').
 The results are interesting in that:
 \begin{itemize}
-	\item With user clustering, \sys{} performs better than LRC-BQ \refe{} in most cases.
-	\item For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ \refe{}.
+	\item With user clustering, \sys{} performs better than LRC-BQ in most cases.
+	\item For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ.
 \end{itemize}
@@
     \label{fig:10-a}
-    \includegraphics[width=0.3\textwidth]{figures/precision.eps}}
+    \includegraphics[width=0.32\textwidth]{figures/precision.eps}}
   %\hspace{1in}
@@
     \label{fig:10-b}
-    \includegraphics[width=0.3\textwidth]{figures/recall.eps}}
+    \includegraphics[width=0.32\textwidth]{figures/recall.eps}}
   %\hspace{1in}
@@
     \label{fig:10-c}
-    \includegraphics[width=0.3\textwidth]{figures/F-Measure.eps}}
+    \includegraphics[width=0.32\textwidth]{figures/F-Measure.eps}}
   \caption{Performance of \sys{} Versus LRC-BQ.}
@@
     \label{fig:11-a}
-    \includegraphics[width=0.3\textwidth]{figures/precisionofdifferentfeatures.eps}}
+    \includegraphics[width=0.32\textwidth]{figures/precisionofdifferentfeatures.eps}}
   %\hspace{1in}
@@
     \label{fig:11-b}
-    \includegraphics[width=0.3\textwidth]{figures/recallofdifferentfeatures.eps}}
+    \includegraphics[width=0.32\textwidth]{figures/recallofdifferentfeatures.eps}}
   %\hspace{1in}
@@
     \label{fig:11-c}
-    \includegraphics[width=0.3\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
+    \includegraphics[width=0.32\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
   \caption{\sys{} Performance of Using Various Data Items for Modeling.}

### 2017-10-09 Gruba/03-fe.tex

@@
 
-\textit{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA \refe{} to result the word weight distribution of blog $b$.
-Unlike TF-IDF \refe{}, Twitter-LDA \refe{} first trains the overall blogs, allocating each blog with a \textit{tag}.
+\textit{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA \ref{IEEEexample:zhao2011comparing} to result the word weight distribution of blog $b$.
+Unlike TF-IDF, Twitter-LDA first trains the overall blogs, allocating each blog with a \textit{tag}.
 %
@@
 
-\textit{Step 5:} TF-IDF \refe{} based similarity is calculated.
+\textit{Step 5:} TF-IDF based similarity is calculated.
 For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
@@
 
-\textit{Step 6:} Accordingly, Twitter-LDA \refe{} based similarity is available.
+\textit{Step 6:} Accordingly, Twitter-LDA based similarity is available.
 Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
@@
 \end{equation}
-where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF \refe{} and Twitter-LDA \refe{}.
+where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.
 Go to \textit{Step 8}.

### 2017-10-10 Gruba/04-uc.tex
v4.0
v4.0

@@
-\section{User Clusterer}
+\section{User Clustering}
 \label{sec:uc}
@@
 
-The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best coefficient value ($v$ in line \ref{opti}).
+The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
 In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
-then, each user obtains a coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
-finally, the averaged coefficient value of all users serves as the coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).
+then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
+finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).
 
 \begin{algorithm}[t]
+\begin{small}
 \caption{User Clustering in \sys{}}
@@
 		\State out-cluster distance $d_o(u)$
-		\State coefficient value $v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$ \label{v-e}
+		\State Silhouette coefficient value $v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$ \label{v-e}
 	\EndFor
@@
 \end{algorithmic}
+\end{small}
 \end{algorithm}
 
-Next, we shall now first detail how \sys{} performs the clustering task and subsequently illustrate the computation regarding the metric of coefficient value.
+Next, we shall now first detail how \sys{} performs the clustering task and subsequently illustrate the computation regarding the metric of Silhouette coefficient value.
 
@@
 
-In \sys{}, the clustering rests on an optimized K-Prototype \refe{} algorithm, named K-Gru in this work. 
+In \sys{}, the clustering rests on an optimized K-Prototype \cite{IEEEexample:huang1997clustering} algorithm, named K-Gru in this work.
 Similar as K-Prototype, K-Gru randomly selects the cluster kernels among samples and employs the minimum distance between them to determine an initial result, upon which the clustering tasks are iterated until the results are stable.
@@
 \centering
+\begin{small}
 \caption{Types of Dimensional Data in \textit{Feature Data} Vector}
@@
 \label{eq:vd}
-D_v(Y^{\ast}, Z^{\ast}) = \sum_{\substack{e}} Y^{\ast}_e \cdot Z^{\ast}_e
+D_v(Y^{\ast}, Z^{\ast}) = 1- \sum_{\substack{e}} Y^{\ast}_e \cdot Z^{\ast}_e
 \end{equation}
@@
 
-\subsection{Coefficient Metric Computation}
+\subsection{Silhouette Coefficient Metric Computation}
 \label{sec:compu}
 
-In \sys{}, coefficient value serves as the fundamental criteria for the optimal clustering selection.
+In \sys{}, Silhouette coefficient value serves as the fundamental criteria for the optimal clustering selection.
 Providing a clustering result, each user is associated with a cluster.
@@
 \label{def:coef}
-The coefficient value $v(u)$ is thus concluded:
+The Silhouette coefficient value $v(u)$ is thus concluded:
 \begin{equation}
@@
 Intuitively, a good clustering solution should result bigger $d_o$ and smaller $d_i$, such that samples with obvious differences go to various clusters and vice versa.
-When $d_o$ is far more than $d_i$, coefficient value approaches to 1.
-Hence, the larger coefficient value is, the better clustering performs, by which the optimal solution is selected.
+When $d_o$ is far more than $d_i$, Silhouette coefficient value approaches to 1.
+Hence, the larger Silhouette coefficient value is, the better clustering performs, by which the optimal solution is selected.

### 2017-10-10 Gruba/07-rela.tex
v4.0
v4.0

--- 2017-09-30 Gruba/07-rela.tex
@@
-\section{\textcolor{red}{Related Work}}
+\section{Related Work}
 \label{sec:rela}
+
+%In this section, we will introduce the related work of user modeling in social network from the aspects of user features analysis, user groups mining and user behaviors modeling.
+Social media users's features we mentioned here include users's basic information, behavior features and interests features.\par
+
+%Users's basic information we mentioned here include the users's gender, age, region, occupation and other personal information.
+There are many researches for analyzing users's basic information, such as users's racial information analysis \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, users's gender inference \cite{IEEEexample:conf/emnlp/CiotSR13}, users's actual age inference \cite{IEEEexample:conf/icde/ParkHHL09}, user policy orientation analysis (e.g.
+\cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private}), user's geo-location and occupation mining \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}, etc.
+Here, we did not do basic information mining for users.
+We used the user's basic information as important features for user clustering and behavior modeling.
+\par
+
+%Social medias users's behaviors mainly refers to the tweeting and retweeting behaviors.
+Users's behaviors also have certain characteristics and regularity, which have been proved by a lot of existing work.
+Jiang et al.
+proposed a behavior dynamics model \cite{IEEEexample:jiang2013understanding}, theoretical analysis shows this model can properly explain various heavy-tailed inter-event time distributions, including a regular power law and some non-power-law deviations.
+Guo Z et al.\cite{IEEEexample:conf/music/GuoLTL12} analyzed the behavior of microblog users, the difference between the activity of users in different periods, and obtained the distribution of individual behavior on time.
+Pravallika Devineni et al.
+analyzed the wall activities of users focusing on identifying common patterns and proposed PowerWall distribution \cite{IEEEexample:journals/snam/DevineniKFF17}.
+What's more, it helped them spot surprising behaviors and anomalies.
+Considering the regularity of user behavior on time, we extracted characteristics of the user behavior as important features for user clustering and behavior modeling.\par
+
+%As for users's interest, many methods has been proposed to do interests extraction.
+Zhiyuan et al.\cite{IEEEexample:journals/fcsc/LiuCS12} modeled users's interests through mining keywords.
+They extracted keywords from the users's microblogs by the combination of words frequency and translation model.
+Xu Z et al.\cite{IEEEexample:conf/webi/XuLXY11} proposed a method which extended user topic model to analyze users's interests.
+Michelson M et al.\cite{IEEEexample:conf/and/MichelsonM10} analyzed interests  based on a knowledge base.
+They used a knowledge base to identify and classify the entities in twitters of one user, then generate the user's interests category subtree to express his interests.
+Lim K H et al.\cite{IEEEexample:conf/wikis/LimD13} analyzed the celebrities a user mentioned, then they got the preference degree of the user in different interests categories.
+Bhattacharya P et al.\cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} proposed a method to extract a user's interests by analyzing the experts he followed.
+By digging a list of certain topics of the custom experts the user follows, they got the user's interests profiling.
+Wei Feng et al.\cite{IEEEexample:conf/icde/FengW14} studied the methods mapping tweets to hashtags to get users's preferences for hashtags.
+The existing methods for interest extraction have some shortcomings.
+The granularity of the result obtained by the methods based on keyword extraction is too small, and the result obtained by the user topic model is implicit and difficult to display.
+What's more, for the lack of a complete knowledge base, it's not easy to do interests extraction by using knowledge base.
+To solve the problems, we employed a cell lexicon to express user's interest.
+What's more, we combined Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF to extract the distribution of users's interest.\par
+
+%There have also many studies on the user groups analysis.
+Some researches studied how to classify users under a specific situation.
+For instance, Marco Pennacchiotti et al.\cite{IEEEexample:conf/icwsm/PennacchiottiP11} classified users by race, political tendencies and so on.
+\cite{IEEEexample:journals/tkdd/ZhangCFLYZY17} analyzed the evolution of social groups, such as Facebook groups and Wechat groups, and proposed a new model for group evolution, which can provide insights about different evolution patterns of social groups.
+Xin Wang et al.
+\cite{IEEEexample:conf/aaai/WangDNGEB16} implemented a time-varying factorization to measure the user-group affinity for recommending groups to users.
+In addition, research for users community mining is a hot spot.
+Jaewon Yang et al.\cite{IEEEexample:conf/wsdm/YangL13} proposed a method based on non-negative matrix decomposition to mine user community.
+Yiye Ruan et al.\cite{IEEEexample:conf/www/RuanFP13} considered user's friends and user's text content into their method when measuring the similarity between users for clustering.
+He et al.
+\cite{IEEEexample:he2014overlapping}
+%only considered the relationship between friends, and used the edge aggregation coefficient as a measure of clustering.
+Hiroaki Shiokawa et al.\cite{IEEEexample:conf/aaai/ShiokawaFO13} used the modular degree as a clustering standard and proposed an incremental algorithm to mine user community.
+As we can see, current analysis of user groups are diverse.
+However, users in social networks have multiple features, and many existing methods do not take advantage of these features to group users.
+Here we took user's basic, behavioral and interest information into account when performing user clustering, and we got distinguish groups with different statistical characteristics.\par
+
+%As for behavior modeling, Jing Zhang et al.\cite{IEEEexample:journals/tkdd/ZhangTLLX15} proposed a method of analyzing users's retweeting behavior from the perspective of influence.
+Some researchers (e.g.
+\cite{IEEEexample:conf/wsdm/FengW13}, \cite{IEEEexample:conf/ijcai/ZhangLTCL13}) find that the user's reposting behavior is largely influenced by the relationship between friends, so they consider user's friend structure information into their models.
+Bo Jiang et al.
+\cite{IEEEexample:conf/cikm/JiangLSW15} proposed a method that combined matrix decomposition and microblogs clustering to analyze the user's reposting behavior.
+Zhang et al.\cite{IEEEexample:zhang2015retweet} proposed non-parametric statistical models to combine structural, textual, and temporal information together to predict reposting behavior.
+Considering the situation that users's not reposting does not mean that users are not interested in it, the users may just did not see it, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} applied a collaborative filtering method to the reposting behavior analysis.
+Maria Giatsoglou et al.
+explore the identification of fraudulent and genuine retweet threads and developed a realistic generator that mimics the behaviors of both honest and fraudulent users \cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15}.
+Suhas Ranganath et al.
+\cite{IEEEexample:journals/corr/RanganathMHTL15} were inspired by sociological theories of protest participation and proposed a framework to predict from the user¡¯s past status messages and interactions whether the next post of the user will be a declaration of protest.
+They evaluated the framework using data from Twitter on protests during the recent Nigerian elections and demonstrated that it could effectively work.
+Considering the fact that the amount of users in Social Medias is so huge, modeling for each user is not a good idea.
+However, modeling for a single user may make the model too particular.
+In addition, modeling for the whole users makes our model inaccuracy.
+%So we divided users into several groups by users clustering. Then we get different behavior model for each group users respectively. \par
+
+In this section, we shall review related work in literature mainly from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
+As aforementioned, \sys{} leverages the user features of basic info, behavior and interest.
+
+With respect to feature analysis, there have been existed works of mining users' info, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
+Our work, however, does not focus on the mining process per se; we use the mined info as the input for user clustering and group modeling.
+
+Studies of behavior analysis put emphasis on exploring the characteristics.
+For example, \cite{IEEEexample:jiang2013understanding} proposed a model that can properly explain various time distributions of user behaviors by theoretical analysis;
+\cite{IEEEexample:conf/music/GuoLTL12} studied the user activity distribution of one day/week;
+\cite{IEEEexample:journals/snam/DevineniKFF17} provided the PowerWall distribution of Facebook users, identifying a number of surprising behaviors and anomalies.
+Considering the behavior characteristics, \sys{} makes use of them to feed the modeling process.
+
+There have been established work of extracting user interests.
+\cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of blogs with the aid of word frequency and machine translation.  
+\cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain use interests. 
+Also, \cite{IEEEexample:conf/and/MichelsonM10} used a knowledge base and \cite{IEEEexample:conf/icde/FengW14} provided a solution of using hashtag for interest analysis. 
+\cite{IEEEexample:conf/wikis/LimD13} summarized user interest by exploring the mentioned celebrities; 
+Similarly, \cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} leveraged the followed experts to result interest characteristics.
+Unlike the existed solutions, \sys{} employs a cell lexicon to properly express user interest in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF \refe{} are employed.
+
+Approaches of grouping users in social network could fall into a variety of categories.
+\cite{IEEEexample:conf/icwsm/PennacchiottiP11} grouped users by the info of race, political view and etc. 
+\cite{IEEEexample:journals/tkdd/ZhangCFLYZY17} studied the social groups on Facebook and Wechat, resulting various patterns of group evolution.
+\cite{IEEEexample:conf/aaai/WangDNGEB16} proposed a time-varying factor to measure the affinity between users and groups such that proper group proposals are recommended.
+More recent studies also look into mining user communities.
+\cite{IEEEexample:conf/wsdm/YangL13} employed matrix decomposition to mine user community;
+\cite{IEEEexample:conf/www/RuanFP13} and \cite{IEEEexample:he2014overlapping} considered followees info for user clustering; 
+\cite{IEEEexample:conf/aaai/ShiokawaFO13} proposed an incremental algorithm to mine user community using modular degree as the clustering yardstick. 
+Providing the diversity of user features, \sys{} employs feature of info, behavior and interest into user clustering.
+
+The main problem of current approaches for behavior modeling lies in that the model is for either the overall users or a single user. 
+\cite{IEEEexample:journals/tkdd/ZhangTLLX15, IEEEexample:conf/wsdm/FengW13, IEEEexample:conf/ijcai/ZhangLTCL13} discovered that users' \retg{} behavior is largely influenced by their followees, whereas \cite{IEEEexample:conf/cikm/JiangLSW15} employed matrix decomposition, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} used collaborative filtering methods and \cite{IEEEexample:zhang2015retweet} leveraged statistical models for \retg{} analysis.
+\cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15} and \cite{IEEEexample:journals/corr/RanganathMHTL15} focused on identifying whether the \retg{} is fraudulent or of protest. 
+Whereas our work \sys{} builds the \retg{} model for each user group, instead of the mono model for all users or one model per user.

### 2017-10-10 Gruba/00-abstr.tex
v4.1
v4.1

@@
 The variety among users makes it difficult to model their \retg{} activities.
-Obviously, it is not suitable to cover the overall users by a single model \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
+Obviously, it is not suitable to cover the overall users by a single model.% \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
 Meanwhile, building one model per user is not practical.

### 2017-10-10 Gruba/01-intro.tex
v4.1
v4.1

@@
 
-Social media is overwhelming nowadays, with massive users on Facebook \refe{}, Twitter \refe{} and Weibo \refe{} while the number of users keeps increasing.
+Social media is overwhelming nowadays, with massive users on Facebook, Twitter and Weibo while the number of users keeps increasing.
 These users behave variously, knowledge of which is significant in recommendation system, activity prediction and Big Thing analysis.
-Hence emerges the demand of developing systems and algorithms that could properly model user behaviors, which has attracted the attention from both academia and industry.
+Hence emerges the demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.
 
-Central to user behavior modeling, is the need to choose the unit of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating these units.
+Central to user behavior modeling, is the need to choose the unit of model (i.e., how many users share one model; for example, the mono model for all users, one model per user, etc), as well as the variety of features to be selected for differentiating these units.
 Already, there exist work of building a single model for all the users \refe{}.
@@
 The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
+%
+As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics. 
 Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well.
-As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
+The main challenge is to properly model user groups upon behavior analysis.
 
-\stitle{Contributions.}  The contributions of this work include:
+\stitle{Contributions.}  
+This work contributes as follows:
 

### 2017-10-10 Gruba/02-overview.tex
v4.1
v4.1

@@
 The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
-
+%
 Informally, providing a set of users $\{U\}$ and the associated blogs $\{B\}$, as well as a blog query $b$ and a follower of $O(b)$ written as $f$, i.e., $f \in R_s(O(b))$, \sys{} shall build a \retg{} model for $(\{U\},\ \{B\})$, upon which Y/N is returned regarding whether $f$ shall \ret{} $b$.
@@
 \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
-Figure \ref{fig:framework} shows the architectural components of \sys{}, comprising three subsystems: Data Storage, Processing Runtime and Profile Demonstrator.
+Figure \ref{fig:framework} shows the architectural components of \sys{}, mainly comprising three subsystems: Data Storage, the central Processing Runtime and Profile Demonstrator.
 
@@
 \centering
-\includegraphics[width=.96\linewidth]{figures/architecture}
+\includegraphics[width=.75\linewidth]{figures/architecture}
 \caption{\sys{} Architecture}
@@
 
-\textbf{Data Storage.} The underlying Data Storage subsystem stores data to be processed by \sys{}, i.e., data of blogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
+\stitle{Data Storage.} The underlying Data Storage subsystem stores data to be processed by \sys{}, i.e., data of blogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
 
-\textbf{Processing Runtime.}
+\stitle{Processing Runtime.}
 In the heart of \sys{} lies the Processing Runtime subsystem, which consists of three major components as follows.
-\begin{enumerate}
-	\item Feature Extractor: By coalescing the blog data, each user is depicted by a bunch of features, which are grouped into three categories.
+%\begin{enumerate}
+
+	\stab(1)  Feature Extractor: By coalescing the blog data, each user is depicted by a bunch of features, which are grouped into three categories.
 They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests).
 These features are extracted from the stored data by Feature Extractor and serve as the input of User Clusterer.
-	\item User Clusterer: Providing the user-based features, User Clusterer takes charge of the clustering task such that each user falls into a proper group. 
-	\item Group Modeler: For each group obtained by User Clusterer, Group Modeler employs both positive and negative samples to train a model, over which the testing of users' \retg{} behavior is performed.
-\end{enumerate}
 
-\textbf{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator subsystem for visualization. 
+	\stab(2)  User Clusterer: Providing the user-based features, User Clusterer takes charge of the clustering task such that each user falls into a proper group.
+
+	\stab(3)  Group Modeler: For each group obtained by User Clusterer, Group Modeler employs both positive and negative samples (i.e., blogs that were or weren't \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
+%\end{enumerate}
+
+\stitle{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator subsystem for visualization.
 For the time being, Profile Demonstrator presents \tbc{}.

### 2017-10-10 Gruba/03-fe.tex
v4.1
v4.1

@@
 
-\textit{Step 1:} Each blog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.
+\stitle{Step 1:} Each blog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.
 
-\textit{Step 2:} Explicit interests are explored. Specifically, every word $w$ is sent to match each cell word $c$ of lexicon topics.
+\stitle{Step 2:} Explicit interests are explored. Specifically, every word $w$ is sent to match each cell word $c$ of lexicon topics.
 If $w$ and $c$ are identical, $sim(w, c) = 1$.
@@
 
-If none of $sim(b, t)$ could meet the threshold, i.e., explicit interest discovery over user $u$ fails, go to \textit{Step 3} and \textit{Step 4} in parallel, so as to ``mine'' the implicit interests of $u$.
+If none of $sim(b, t)$ could meet the threshold, i.e., explicit interest discovery over user $u$ fails, go to \textbf{Step 3} and \textbf{Step 4} in parallel, so as to ``mine'' the implicit interests of $u$.
 
-\textit{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in blog $b$:
+\stitle{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in blog $b$:
 \begin{equation}
@@
 Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight} (see Definition \ref{eq:tf}).
-Go to \textit{Step 5}.
+Go to \textbf{Step 5}.
 
-\textit{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA \ref{IEEEexample:zhao2011comparing} to result the word weight distribution of blog $b$.
+\stitle{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing} 
+\refe{}
+to result the word weight distribution of blog $b$.
 Unlike TF-IDF, Twitter-LDA first trains the overall blogs, allocating each blog with a \textit{tag}.
@@
 \end{equation}
-where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ by default).
+where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
 %
 Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
-Go to \textit{Step 6}.
+Go to \textbf{Step 6}.
 
-\textit{Step 5:} TF-IDF based similarity is calculated.
+\stitle{Step 5:} TF-IDF based similarity is calculated.
 For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
@@
 \end{equation}
-where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and:
+where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \refe{}.
+Go to \textbf{Step 7}.
+
+\begin{comment}
+:
 \begin{equation}
@@
 \end{equation}
-Go to \textit{Step 7}.
+\end{comment}
 
-\textit{Step 6:} Accordingly, Twitter-LDA based similarity is available.
+\stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
 Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
@@
 \end{equation}
-where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and:
+where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector \refe{}.
+Go to \textbf{Step 7}.
+
+\begin{comment}
+:
 \begin{equation}
@@
 \end{equation}
-Go to \textit{Step 7}.
+\end{comment}
 
-\textit{Step 7:} Hence, the similarity of a blog $b$ against a lexicon topic $t$ is given by:
+\stitle{Step 7:} Hence, the similarity of a blog $b$ against a lexicon topic $t$ is given by:
 \begin{equation}
@@
 where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.
-Go to \textit{Step 8}.
+Go to \textbf{Step 8}.
 
-\textit{Step 8:} Repeat the above steps (Step 1 to Step 7) for the blog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
+\stitle{Step 8:} Repeat the above steps (Step 1 to Step 7) for the blog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
 Such computation further extends to all the blogs owned by user $u$, such that:

### 2017-10-10 Gruba/04-uc.tex
v4.1
v4.1

@@
 Algorithm \ref{alg:uc} illustrates such overall procedure.
-
+%
 The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
@@
 
-Next, we shall now first detail how \sys{} performs the clustering task and subsequently illustrate the computation regarding the metric of Silhouette coefficient value.
+Next, we shall now first detail how \sys{} performs the clustering task and subsequently illustrate the computation for the metric of Silhouette coefficient value.
 
@@
 \begin{small}
-\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
+%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
+\caption{Dimension Types in \textit{Feature Data} Vector}
 \vspace{0.3cm}
@@
 Providing a clustering result, each user is associated with a cluster.
+
 For a given user $u$ of cluster $l$, we employ the vector $Y$ to denote the \textit{Feature Data} as in formula \ref{eq:fu-flat}.

### 2017-10-10 Gruba/05-gm.tex
v4.1
v4.1

--- 2017-10-06 Gruba/05-gm.tex
@@
 \label{def:gm-it}
-An item $E$ involves a blog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of $b$'s owner.
+An item $E$ involves a blog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of  the owner of blog $b$.
 \begin{equation}
@@
 And the data of item $E$ could be further divided into three parts.
-\begin{itemize}
-	\item \textit{User Info}: contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.
-	\item \textit{Blog Info}: consists of a metric $C_h$, referring to the correlation between blog contents and recent events returned by Ring \refe{}.
-$C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}).
-Specifically, each event could be viewed as a topic $t$, over which the correlation of a blog $b$ could be obtained by formula \ref{eq:simbt}.
-	\item \textit{Interaction Info}: includes three correlation metrics.
+%\begin{itemize}
+
+	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.
+
+	\stab(2) \stitle{Blog Info} considers the correlation between blog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}.
+The correlation metric $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}).
+Each event could be viewed as a topic $t$, over which the correlation of a blog $b$ could be obtained by formula \ref{eq:simbt}.
+
+	\stab(3) \stitle{Interaction Info} includes three correlation metrics.
 They are of blog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.
 long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent blogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
-\end{itemize}
+%\end{itemize}
 As a result, the obtained group model could learn what does a positive/negative item look like over each metric mentioned above.

### 2017-10-10 Gruba/06-perf.tex
v4.1
v4.1

@@
 \label{sec:perf}
+
+In this section, we shall first detail the experimental setting of machine info, dataset and parameters; and then present the result and analysis, showing the benefit of \sys{} against state of the art approaches.
 
@@
 Experiments were run on a machine with two Intel Xeon E5C2630 2.4GHz CPUs and 64 GB of Memory, running 64 bit Windows 7 professional system.
-
+%
 We have employed a real-world dataset Sina that consists of 24 million blogs that are associated with 43.5K users.
@@
 
-\textbf{Feature Extractor}
+\stitle{Feature Extractor}
 %
@@
 
-\textbf{User Clusterer}
+\stitle{User Clusterer}
 %
@@
 
-\textbf{Behavior Modeler}
+\stitle{Behavior Modeler}
 %
@@
 The results are interesting in that:
-\begin{itemize}
-	\item With user clustering, \sys{} performs better than LRC-BQ in most cases.
-	\item For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ.
-\end{itemize}
+%\begin{itemize}
+
+	\stab(1) With user clustering, \sys{} performs better than LRC-BQ in most cases.
+
+	\stab(2) For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ.
+%\end{itemize}
 

### 2017-10-10 Gruba/03-fe.tex

@@
 \stitle{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing}
-\refe{}
+\cite{IEEEexample:zhao2011comparing}
 to result the word weight distribution of blog $b$.
@@
 \end{equation}
-where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \refe{}.
+where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
 Go to \textbf{Step 7}.
@@
 \end{equation}
-where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector \refe{}.
+where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
 Go to \textbf{Step 7}.

### 2017-10-10 Gruba/07-rela.tex

@@
 Similarly, \cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} leveraged the followed experts to result interest characteristics.
-Unlike the existed solutions, \sys{} employs a cell lexicon to properly express user interest in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF \refe{} are employed.
+Unlike the existed solutions, \sys{} employs a cell lexicon to properly express user interest in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF are employed.
 

### 2017-10-10 Gruba/06-perf.tex

@@
 \end{figure*}
+
+\stitle{Case Study for Feature Extraction}
+In this section, we show the results of our demo system for user features extraction.
+Considering the huge amount of users, we carefully selected one typical user for analysis.
+Here we chose Mary(a famous drama and movie actor in China) as a representative.
+The features extraction result for Mary is displayed in Fig.\ \ref{fig:userFeatures}.
+Then we can see the basic information of Mary from the result. Her nickname is Actor Mary(演员马丽) and she is from Beijing(北京). 
+The number of followers of Mary is much more than the number of her friends.
+The Sina Microblog tag she made for herself is "actor"(演员).
+As the result of the long-term interest extraction shows, she is interested in stage performances(舞台喝彩), drama performances(话剧表演),films(电影光影) and so on, which is consistent with her actual situation.
+What's more, the probability distribution of tweeting and retweeting behavior on different time periods in one day indicates that her activities at night is much more than daytime.
+The time interval distribution of her behaviors is also shown in Fig.\ \ref{fig:userFeatures}. The time interval is mostly distributed within 48 hours, which indicates that she is a active user.
+We developed a function for querying user's short-term interest. 
+Here we queried Mary's short-term interest between 09/01/2016 and 09/30/2016, and got it as shown in Fig.\ \ref{fig:userFeatures}.
+We analyzed her microblogs in the this period, she has been working tirelessly to promote the drama "Earl of Oolong Mountain"(基督山伯爵).
+So the results are in line with expectations.
+
+\begin{figure}
+  \centering
+  \subfigure{
+      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/1.eps}}
+  \subfigure{
+      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/2.eps}}
+  \subfigure{
+      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/3.eps}}
+  \subfigure{
+      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/4.eps}}
+  \subfigure{
+      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/5.eps}}
+  \subfigure{
+      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/6.eps}}
+  \subfigure{
+  \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/7.eps}}
+  \subfigure{
+  \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/8.eps}}
+  \caption{Visualization for User Features.}
+  \label{fig:userFeatures} %% label for entire figure
+\end{figure}

### 2017-10-10 Gruba/10-appendix.tex

@@
 \newpage
-\section{Appendix}
+\section{Appendix: Extra Experiments}
 \label{sec:appendix}
+
+\subsection{Case Study for Feature Extraction}
+
+\subsection{Case Study for User Clustering}
+
+We carefully analyzed the four groups we obtained through users clustering.
+(1)Most of users of the group one(as shown in Fig.\ref{fig:subfig1}) are male(男), and they are mainly distributed in Beijing(北京).
+What's more, most of these users have similar amount of friends and followers.
+The most active time of this group are mainly distributed between 10 am and 12 am.
+(2)The users of group two(as shown in Fig.\ref{fig:subfig2}) are mostly female(女), they are also mainly distributed in Beijing(北京).
+Most of these users also have similar amount of friends and followers as group one.
+The most active time of this group are mainly distributed between 22 pm and 24 pm.
+(3)The users of group three(as shown in Fig.\ref{fig:subfig3}) are mostly male(男), and they are distributed in a wide range of provinces.
+Most of users have the number of followers far more than friends.
+The most active time of this user group are mainly distributed both in 10-12 am and 22-24 pm.
+(4)Most users of group four(as shown in Fig.\ref{fig:subfig4}) are female(女), and they are distributed in a wide range of provinces as group three.
+Most of these users have the number of followers far more than friends.
+And the most active time of these users are mainly distributed between 22 pm and 24 pm.
+We also found that the distribution of the number of users's microblogs of four groups is similar with each other.
+We visualized the group's long-term interest using words cloud, the interest difference between groups is obvious.
+As we can see, the group one and group three have similar interests.
+
+\begin{figure}
+  \centering
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/11.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/12.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/13.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/14.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/15.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/16.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/17.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/18.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/19.eps}}
+  \caption{The Statistics of User Group One}
+  \label{fig:subfig1} %% label for entire figure
+\end{figure}
+
+\begin{figure}
+  \centering
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/21.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/22.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/23.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/24.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/25.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/26.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/27.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/28.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/29.eps}}
+  \caption{The Statistics of User Group Two}
+  \label{fig:subfig2} %% label for entire figure
+\end{figure}
+\begin{figure}
+  \centering
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/31.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/32.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/33.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/34.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/35.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/36.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/37.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/38.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/39.eps}}
+  \caption{The Statistics of User Group Three}
+  \label{fig:subfig3} %% label for entire figure
+\end{figure}
+\begin{figure}
+  \centering
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/41.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/42.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/43.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/44.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/45.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/46.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/47.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/48.eps}}
+  \subfigure{
+      \includegraphics[width=0.15\textwidth]{IMAGE/group-images/49.eps}}
+  \caption{The Statistics of User Group Four}
+  \label{fig:subfig4} %% label for entire figure
+\end{figure}

### 2017-10-11 Gruba/03-fe.tex

@@
 Different from the straightforward notions of \textit{Info Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
-In short, with a given lexicon consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the probability that the said user matches a \textit{topic}.
+In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the probability that the said user matches a \textit{topic}.
 

### 2017-10-11 Gruba/04-uc.tex

@@
 
-Given two numerical vectors $Y'\ = (y'_0, y'_1, ...)$ and $Z'\ = (z'_0, z'_1, ...)$, the \od{} \refe{} between $Y'$ and $Z'$ is given by :
+Given two numerical vectors $Y'\ = (y'_0, y'_1, ...)$ and $Z'\ = (z'_0, z'_1, ...)$, the \od{} \cite{IEEEexample:books/mk/HanKP2011} between $Y'$ and $Z'$ is given by :
 %
@@
 
-As to the categorical vectors $Y''\ = (y''_0, y''_1, ...)$ and  $Z''\ = (z''_0, z''_1, ...)$, the \hd{} \refe{} of $Y''$ and $Z''$ is:
+As to the categorical vectors $Y''\ = (y''_0, y''_1, ...)$ and  $Z''\ = (z''_0, z''_1, ...)$, the \hd{} \cite{IEEEexample:huang1997clustering} of $Y''$ and $Z''$ is:
 %
@@
 
-Regarding two vectors where each dimension is a normalized vector per se, Cosine Similarity \refe{} is leveraged to compute the distance.
+Regarding two vectors where each dimension is a normalized vector per se, Cosine Similarity is leveraged to compute the distance.
 Then, the distance between such two vectors $Y^{\ast}\ = (Y^{\ast}_0, Y^{\ast}_1, ...)$ and $Z^{\ast}\ = (Z^{\ast}_0, Z^{\ast}_1, ...)$ is:

### 2017-10-11 Gruba/05-gm.tex

@@
 %\end{itemize}
-As a result, the obtained group model could learn what does a positive/negative item look like over each metric mentioned above.
+In this paper, we see modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem.
+The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
+As a result, the obtained group behavior model could learn what does a positive/negative item look like over each metric mentioned above.\par

### 2017-10-11 Gruba/01-intro.tex
v4.2
v4.2

@@
 
-Central to user behavior modeling, is the need to choose the unit of model (i.e., how many users share one model; for example, the mono model for all users, one model per user, etc), as well as the variety of features to be selected for differentiating these units.
-Already, there exist work of building a single model for all the users \refe{}.
+Central to user behavior modeling, is the need to choose the granularity of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating these units.
+Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
 Apparently, such model bears the limitation of being coarse.
@@
 Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well. 
-The main challenge is to properly model user groups upon behavior analysis.
+In the realm of social network behavior research, few work has been done towards making use of grouping, which however has been proved to be effective in other fields.
+This motivates us to explore the incorporation of user grouping into the \retg{} behavior modeling, filling the gap of existed studies in literature.
 

### 2017-10-11 Gruba/02-overview.tex
v4.2
v4.2

@@
 We consider people's \retg{} behavior in social media.
-For simplicity, with a given user, we assume that blogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
+For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
 All our results could straightforwardly generalize to alternative candidate scopes.
@@
 \label{def:blog}
-A blog $B = (O, T, M, R)$ consists of the owner $O$ (a.k.a.
-user in this paper) to whom $B$ belongs (either created or \retd{}), the timestamp $T$ showing when $B$ is generated, the blog message $M$ and a bit $R$ denoting $B$ is \retd{} (1) or originally created (0) by the owner $O$.
+A microblog $Mb = (O, T, M, flag)$ consists of the owner $O$ (a.k.a.
+user in this paper) to whom $Mb$ belongs (either created or \retd{}), the timestamp $T$ showing when $Mb$ is generated, the microblog message $M$ and a bit $flag$ denoting $Mb$ is \retd{} (1) or originally created (0) by the owner $O$.
 \end{definition}
@@
 \label{def:user}
-A user $U = (B_s, R_s, E_s)$ consists of three sets regarding the user's blogs $B_s$, followers $R_s$ and followees $E_s$ separately.
+A user $u = (B_u, R_u, E_u)$ consists of three sets regarding the user's microblogs $B_u$, followers $R_u$ and followees $E_u$ separately.
 Each follower/followee per se refers to a user.
@@
 
-The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
+%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
+By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = Mb.O$ and $Mb \in B_u$
 %
-Informally, providing a set of users $\{U\}$ and the associated blogs $\{B\}$, as well as a blog query $b$ and a follower of $O(b)$ written as $f$, i.e., $f \in R_s(O(b))$, \sys{} shall build a \retg{} model for $(\{U\},\ \{B\})$, upon which Y/N is returned regarding whether $f$ shall \ret{} $b$.
+Informally, providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} shall build a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$.
 
@@
 
-\stitle{Data Storage.} The underlying Data Storage subsystem stores data to be processed by \sys{}, i.e., data of blogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
+\stitle{Sina Microblog Data.} It is the data to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
 
-\stitle{Processing Runtime.}
-In the heart of \sys{} lies the Processing Runtime subsystem, which consists of three major components as follows.
+\stitle{Key Modules.}
+In the heart of \sys{} lies the Key Modules, which consists of three major components as follows.
 %\begin{enumerate}
 
-	\stab(1)  Feature Extractor: By coalescing the blog data, each user is depicted by a bunch of features, which are grouped into three categories.
+	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories.
 They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests).
-These features are extracted from the stored data by Feature Extractor and serve as the input of User Clusterer.
+These features are extracted from the stored data by Feature Extraction and serve as the input of User Clustering.
 
-	\stab(2)  User Clusterer: Providing the user-based features, User Clusterer takes charge of the clustering task such that each user falls into a proper group.
+	\stab(2)  User Clustering: Providing the user-based features, User Clustering takes charge of the clustering task such that each user falls into a proper group.
 
-	\stab(3)  Group Modeler: For each group obtained by User Clusterer, Group Modeler employs both positive and negative samples (i.e., blogs that were or weren't \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
+	\stab(3)  Group Modeling: For each group obtained by User Clustering, Group Modeling employs both positive and negative samples (i.e., microblogs that were labeled with \retd{} and not \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
 %\end{enumerate}

### 2017-10-11 Gruba/03-fe.tex
v4.2
v4.2

@@
 
-With the underlying data in Data Storage subsystem, Feature Extractor is responsible for ``mining'' the user characteristics, resulting three features for each user.
+With the underlying data in Data Storage subsystem, Feature Extraction is responsible for ``mining'' the user characteristics, resulting three features for each user.
 These features are \textit{Info Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Info Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.
@@
 where each variable is illustrated in Table \ref{tbl:fe-info}.
-Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} blogs and blogs that are originally created by the user.
+Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.
 
@@
  						&                       									\\	\midrule
-\#$B_s$				& number of blogs owned by the user				\\	\midrule
+\#$B_s$				& number of microblogs owned by the user				\\	\midrule
 \multirow{2}{*}{$R_{oc}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#(B_s | R(B)==1)}{\#(B_s | R(B)==0)}$}	\\
@@
 \begin{itemize}
-	\item a value showing the average number of \retd{} blogs per week: $\#W_r$
+	\item a value showing the average number of \retd{} microblogs per week: $\#W_r$
 	\item a normalized vector regarding the time distribution of a user's \retg{} behavior: $P_t\ = (p'_0,\ p'_1,\ ...,\ p'_{11})$, where $p'_0$ is the probability that the \retg{} activity happens from 0am to 2am, $p'_1$ is the probability that the \retg{} activity happens from 2am to 4am, and so on.
-	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_g\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} blogs is within 1 min.
+	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_g\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} microblogs is within 1 min.
 Ditto for $p''_1$ (1 min to 1 hour), $p''_2$ (1 to 12 hours), $p''_3$ (12 to 24 hours), $p''_4$ (24 to 48 hours) and  $p''_5$ (more than 48 hours).
@@
 %used \label{def:blog} previously
-With a given user $u$, each blog $b \in B_s(u)$ could be decomposed into a set of words $\{w\}$, i.e., $b = \{w\}$.
+With a given user $u$, each microblog $b \in B_s(u)$ could be decomposed into a set of words $\{w\}$, i.e., $b = \{w\}$.
 \end{definition}
@@
 In \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
-Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a blog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, \{t\})$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.
+Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, \{t\})$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.
 
@@
 
-\stitle{Step 1:} Each blog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.
+\stitle{Step 1:} Each microblog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.
 
@@
 
-If $sim(b, t)$ satisfies a certain threshold (3 by default) , topic $t$ is labeled to blog $b$;
+If $sim(b, t)$ satisfies a certain threshold (3 by default) , topic $t$ is labeled to microblog $b$;
 the user $u$ is then discovered having an explicit interest (topic) $t$.
@@
 
-\stitle{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in blog $b$:
+\stitle{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in microblog $b$:
 \begin{equation}
@@
 \end{equation}
-in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in blog $b$ and $|b|$ the total occurrences of all words in $b$.
-Ditto for $|D_i|$ and $|D|$, except that the scope is the overall dataset, rather than a single blog $b$.
+in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$ and $|b|$ the total occurrences of all words in $b$.
+Ditto for $|D_i|$ and $|D|$, except that the scope is the overall dataset, rather than a single microblog $b$.
 
@@
 \cite{IEEEexample:zhao2011comparing}
-to result the word weight distribution of blog $b$.
-Unlike TF-IDF, Twitter-LDA first trains the overall blogs, allocating each blog with a \textit{tag}.
+to result the word weight distribution of microblog $b$.
+Unlike TF-IDF, Twitter-LDA first trains the overall microblogs, allocating each microblog with a \textit{tag}.
 %
@@
 \end{equation}
-where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
+where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in microblogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
 %
@@
 
-\stitle{Step 7:} Hence, the similarity of a blog $b$ against a lexicon topic $t$ is given by:
+\stitle{Step 7:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is given by:
 \begin{equation}
@@
 
-\stitle{Step 8:} Repeat the above steps (Step 1 to Step 7) for the blog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
-Such computation further extends to all the blogs owned by user $u$, such that:
+\stitle{Step 8:} Repeat the above steps (Step 1 to Step 7) for the microblog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
+Such computation further extends to all the microblogs owned by user $u$, such that:
 $\forall b_m \in B_s(u)$, $\forall t_k \in L$, there exists a similarity of $sim(b_m, t_k)$.

### 2017-10-11 Gruba/04-uc.tex
v4.2
v4.2

@@
 
-Providing the \textit{Feature Data}, User Clusterer takes the charge of grouping each user concerned into a proper cluster.
+Providing the \textit{Feature Data}, User Clustering takes the charge of grouping each user concerned into a proper cluster.
 Algorithm \ref{alg:uc} illustrates such overall procedure.
@@
 %
-Recall the sample data for User Clusterer, i.e., \textit{Feature Data} in form of vectors (see formula \ref{eq:fu-flat}), of which the data type regarding each dimension is shown as Table \ref{tbl:data-type}.
+Recall the sample data for User Clustering, i.e., \textit{Feature Data} in form of vectors (see formula \ref{eq:fu-flat}), of which the data type regarding each dimension is shown as Table \ref{tbl:data-type}.
 

### 2017-10-11 Gruba/05-gm.tex
v4.2
v4.2

@@
-\section{Group based Behavior Modelling}
+\section{Group based Behavior Modeling}
 \label{sec:gm}
@@
 Recall the central problem of \sys{}, where the \retg{} behaviors of users are modeled.
-Specifically, such model is built by Group Modeler for each user group and thus named as group model.
+Specifically, such model is built by Group Modeling for each user group and thus named as group model.
 To avoid ambiguity, we shall use the term of \textit{items} to denote the data for training the group model.
@@
 \label{def:gm-it}
-An item $E$ involves a blog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of  the owner of blog $b$.
+An item $E$ involves a microblog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of  the owner of microblog $b$.
 \begin{equation}
@@
 
-	\stab(2) \stitle{Blog Info} considers the correlation between blog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}.
+	\stab(2) \stitle{Microblog Info} considers the correlation between microblog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}.
 The correlation metric $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}).
-Each event could be viewed as a topic $t$, over which the correlation of a blog $b$ could be obtained by formula \ref{eq:simbt}.
+Each event could be viewed as a topic $t$, over which the correlation of a microblog $b$ could be obtained by formula \ref{eq:simbt}.
 
 	\stab(3) \stitle{Interaction Info} includes three correlation metrics.
-They are of blog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.
-long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent blogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
+They are of microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.
+long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
 %\end{itemize}

### 2017-10-11 Gruba/06-perf.tex
v4.2
v4.2

@@
 %
-We have employed a real-world dataset Sina that consists of 24 million blogs that are associated with 43.5K users.
+We have employed a real-world dataset Sina that consists of 24 million microblogs that are associated with 43.5K users.
 
 With respect to the parameters of \sys{}, we use the default values as mentioned in previous sections.
-Particularly, in Feature Extractor, for practical reason, we employed a smaller testing dataset to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature};
+Particularly, in Feature Extraction, for practical reason, we employed a smaller testing dataset to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature};
 in User Cluster, we studied the clustering solutions with the minimum/maximum number of clusters 2 and 10;
-in Behavior Modeler, a user's recent 30 days blogs are used for short-term interest analysis and popular words of the latest 24 hours are returned by Ring as the Hot Event keywords.
+in Behavior Modeling, a user's recent 30 days microblogs are used for short-term interest analysis and popular words of the latest 24 hours are returned by Ring as the Hot Event keywords.
 
@@
 
-\stitle{Feature Extractor}
+\stitle{Feature Extraction}
 %
 Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
-Apparently, \sys{} results the optimal results when $\alpha$ is 0.7, upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million blogs.
+Apparently, \sys{} results the optimal results when $\alpha$ is 0.7, upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million microblogs.
 
@@
 
-\stitle{User Clusterer}
+\stitle{User Clustering}
 %
@@
 
-\stitle{Behavior Modeler}
+\stitle{Behavior Modeling}
 %
@@
 Fig.\ \ref{fig:11} explores the performance of \sys{} when using alternative data items for modeling.
-By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), blogs (MI) and interactions (II).
+By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), microblogs (MI) and interactions (II).
 How about using other combinations of the above item(s)?
@@
 The features extraction result for Mary is displayed in Fig.\ \ref{fig:userFeatures}.
-Then we can see the basic information of Mary from the result. Her nickname is Actor Mary(演员马丽) and she is from Beijing(北京). 
+Then we can see the basic information of Mary from the result. Her nickname is Actor Mary(ÑÝÔ±ÂíÀö) and she is from Beijing(±±¾©). 
 The number of followers of Mary is much more than the number of her friends.
-The Sina Microblog tag she made for herself is "actor"(演员).
-As the result of the long-term interest extraction shows, she is interested in stage performances(舞台喝彩), drama performances(话剧表演),films(电影光影) and so on, which is consistent with her actual situation.
+The Sina Microblog tag she made for herself is "actor"(ÑÝÔ±).
+As the result of the long-term interest extraction shows, she is interested in stage performances(ÎèÌ¨ºÈ²Ê), drama performances(»°¾ç±íÑÝ),films(µçÓ°¹âÓ°) and so on, which is consistent with her actual situation.
 What's more, the probability distribution of tweeting and retweeting behavior on different time periods in one day indicates that her activities at night is much more than daytime.
@@
 Here we queried Mary's short-term interest between 09/01/2016 and 09/30/2016, and got it as shown in Fig.\ \ref{fig:userFeatures}.
-We analyzed her microblogs in the this period, she has been working tirelessly to promote the drama "Earl of Oolong Mountain"(基督山伯爵).
+We analyzed her microblogs in the this period, she has been working tirelessly to promote the drama "Earl of Oolong Mountain"(»ù¶½É½²®¾ô).
 So the results are in line with expectations.

### 2017-10-11 Gruba/07-rela.tex
v4.2
v4.2

@@
 There have been established work of extracting user interests.
-\cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of blogs with the aid of word frequency and machine translation.
+\cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of microblogs with the aid of word frequency and machine translation.
 \cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain use interests.

### 2017-10-11 Gruba/00-abstr.tex
v4.2
v4.2
v4.3
v4.3

--- 2017-10-09 Gruba/00-abstr.tex
@@
 \begin{abstract}
-Social media applications are emerging, with rapidly growing users and large numbers of \retd{} blogs every minute.
+Social media applications are emerging, with rapidly growing users and large numbers of \retd{} microblogs every minute.
 The variety among users makes it difficult to model their \retg{} activities.
-Obviously, it is not suitable to cover the overall users by a single model \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
+Obviously, it is not suitable to cover the overall users by a single model. % \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
 Meanwhile, building one model per user is not practical.

### 2017-10-11 Gruba/01-intro.tex
v4.3
v4.3

@@
 
-Central to user behavior modeling, is the need to choose the granularity of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating these units.
+Central to user behavior modeling, is the need to choose the granularity of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating users. 
 Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
@@
 Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well. 
-In the realm of social network behavior research, few work has been done towards making use of grouping, which however has been proved to be effective in other fields.
+In the realm of social network behavior modeling, few work has been done over grouping, which however has been proved to be effective in other fields such as economic research.
 This motivates us to explore the incorporation of user grouping into the \retg{} behavior modeling, filling the gap of existed studies in literature.
@@
 
-\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model in literature.
+\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model as in existed research.
 

### 2017-10-11 Gruba/02-overview.tex
v4.3
v4.3

@@
 We consider people's \retg{} behavior in social media.
-For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
-All our results could straightforwardly generalize to alternative candidate scopes.
+%For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
+For simplicity, assuming the microblogs that a user can \ret{} come from those owned by his/her followees.
+
+%All our results could straightforwardly generalize to alternative candidate scopes.
 %e.g., the like/unlike behavior against the candidate of remarking [double check the network language; register a Facebook]
@@
 \label{def:blog}
-A microblog $Mb = (O, T, M, flag)$ consists of the owner $O$ (a.k.a.
-user in this paper) to whom $Mb$ belongs (either created or \retd{}), the timestamp $T$ showing when $Mb$ is generated, the microblog message $M$ and a bit $flag$ denoting $Mb$ is \retd{} (1) or originally created (0) by the owner $O$.
+A microblog $M_b = (O, T, M, flag)$ consists of the owner $O$ (a.k.a.
+user in this paper) to whom $M_b$ belongs (either created or \retd{}), the timestamp $T$ showing when $M_b$ is generated, the microblog message $M$ and a bit $flag$ denoting $M_b$ is \retd{} (1) or originally created (0) by the owner $O$.
 \end{definition}
@@
 %The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
-By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = Mb.O$ and $Mb \in B_u$
+By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = M_b.O$ and $M_b \in B_u$. 
 %
@@
 \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
-Figure \ref{fig:framework} shows the architectural components of \sys{}, mainly comprising three subsystems: Data Storage, the central Processing Runtime and Profile Demonstrator.
+Figure \ref{fig:framework} shows the architectural components of \sys{}, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.
 
@@
 \centering
-\includegraphics[width=.75\linewidth]{figures/architecture}
+\includegraphics[width=.75\linewidth]{figures/architecture.pdf}
 \caption{\sys{} Architecture}
@@
 \stitle{Key Modules.}
-In the heart of \sys{} lies the Key Modules, which consists of three major components as follows.
+In the heart of \sys{} lies Key Modules, which consists of three major components.
 %\begin{enumerate}
@@
 	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories.
-They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests).
-These features are extracted from the stored data by Feature Extraction and serve as the input of User Clustering.
+They are features of \textit{Basics} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests).
+These features are extracted from the stored data by Feature Extraction module and serve as the input of User Clustering module.
 
@@
 
-	\stab(3)  Group Modeling: For each group obtained by User Clustering, Group Modeling employs both positive and negative samples (i.e., microblogs that were labeled with \retd{} and not \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
+	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling employs both positive and negative samples (i.e., microblogs that were labeled with \retd{} and not \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
 %\end{enumerate}
 
-\stitle{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator subsystem for visualization.
-For the time being, Profile Demonstrator presents \tbc{}.
+\stitle{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator for visualization.
+%For the time being, Profile Demonstrator presents \tbc{}.

### 2017-10-11 Gruba/03-fe.tex
v4.3
v4.3

@@
 
-With the underlying data in Data Storage subsystem, Feature Extraction is responsible for ``mining'' the user characteristics, resulting three features for each user.
-These features are \textit{Info Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Info Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.
+With the underlying Sina Microblog Data, Feature Extraction is responsible for ``mining'' the user characteristics, resulting three features for each user.
+These features are \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.
 
-\subsection{Info Feature}
+\subsection{Basic Feature}
 
-\textit{Info Feature} employs a vector $I$ to cover the basic info of user.
+\textit{Basic Feature} employs a vector $I$ to cover the basic info of user.
 \begin{equation}
 \label{eq:info}
-	I = (\#R_s,\ \#E_s,\ R_{ee},\ \#B_s,\ R_{oc},\ U_t)
+	I = (\#R_u,\ \#E_u,\ R_{ee},\ \ U_t)
 \end{equation}
 where each variable is illustrated in Table \ref{tbl:fe-info}.
-Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.
+%Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.
 
@@
 \begin{small}
-\caption{Illustration of Variables in Info Feature}
+\caption{Illustration of Variables in Basic Feature}
 \vspace{0.3cm}
@@
 \multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
-\#$R_s$				& number of followers				\\	\midrule
-\#$E_s$				& number of followees				\\	\midrule
-\multirow{2}{*}{$R_{ee}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#R_s}{\#E_s}$}	\\
- 						&                       									\\	\midrule
-\#$B_s$				& number of microblogs owned by the user				\\	\midrule
-\multirow{2}{*}{$R_{oc}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#(B_s | R(B)==1)}{\#(B_s | R(B)==0)}$}	\\
+\#$R_u$				& number of followers				\\	\midrule
+\#$E_u$				& number of followees				\\	\midrule
+\multirow{4}{*}{$R_{ee}$} & \multirow{2}{*}{a ratio defined as the number of followers} \\
+                   &                     \\
+                   & \multirow{2}{*}{over that of followees, i.e., $\frac{\#R_u}{\#E_u}$} \\
                    & 						\\	\midrule
@@
 \begin{small}
-\caption{Category of Info}
+\caption{Category of User Type}
 \vspace{0.3cm}
@@
 \multicolumn{1}{c}{\textbf{value}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
-0                       & $\#E_s \le 50 \ \& \ \#R_s \le 50$				\\	\midrule
-\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_s}{\#R_s} \ \ge 5$}	\\
+0                       & $\#E_u \le 50 \ \& \ \#R_u \le 50$				\\	\midrule
+\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
  						&                       									\\	\midrule
-\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_s}{\#E_s} \ \ge 5$}  \\
+\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
 						&															\\	\midrule
@@
 
-Unlike \textit{Info Feature}, \textit{Behavior Feature} shows several statistics regarding the user's \retg{} behavior.
+Unlike \textit{Basic Feature}, \textit{Behavior Feature} shows several statistics regarding the user's \retg{} behavior.
 Such statistics include:
 \begin{itemize}
+	\item a value for the number of owned microblogs $\#B_u$
+	\item a ratio $R_{oc}$ that is defined as the number of \retd{} microblogs over that of originally created, i.e., $\frac{\#(B_u | flag ==1)}{\#(B_u | flag ==0)}$
 	\item a value showing the average number of \retd{} microblogs per week: $\#W_r$
@@
 
-Different from the straightforward notions of \textit{Info Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
+Different from the straightforward notions of \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
 In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the probability that the said user matches a \textit{topic}.
@@
 \label{def:lexi}
-A lexicon $L = \{t\}$ consists of a set of topics while each topic $t = \{c\}$ is associated with a list of cell words $\{c\}$. Each cell word $c$ refers to one unique word in $L$.
+A lexicon $L$ consists of a set of topics $t$ such that each topic is associated with a set of cell words $c$. Each cell word depicts an aspect of the topic.
 \end{definition}
@@
 %used \label{def:blog} previously
-With a given user $u$, each microblog $b \in B_s(u)$ could be decomposed into a set of words $\{w\}$, i.e., $b = \{w\}$.
+With a given user $u$, each microblog $b \in B_u$ could be decomposed into a set of words $w$.
 \end{definition}
@@
 
+Next, we shall present the ``mining'' process for interest features. 
+In short, \sys{} employs a well established lexicon to discover the explicit interests of users.
+In case no proper explicit interests are found, TF-IDF and Twitter-LDA are leveraged to explore the implicit interests, during which word2vector participates to provide the similarity between two words.
+
 In \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
-Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, \{t\})$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.
+Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, t)$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.
 
@@
 
-\stitle{Step 1:} Each microblog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.
+\stitle{Step 1:} Each microblog of $u$ is decomposed into a word set. %, i.e., $b = \{w\}$ where $b \in B_s(u)$.
 
@@
 \end{equation}
-where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
+%where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, 
+where $W_w$ is a set of $(w'_i, p'_i)$, $t$ covers each $c_j$, 
+and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
 Go to \textbf{Step 7}.
@@
 \end{equation}
-where $I$, $H$ and $P_f$ refer to \textit{Info Feature}, \textit{Behavior Feature} and \textit{Interest Feature} separately (see formulas \ref{eq:info}, \ref{eq:beha} and \ref{def:inte}).
+where $I$, $H$ and $P_f$ refer to \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature} separately (see formulas \ref{eq:info}, \ref{eq:beha} and \ref{def:inte}).
 And it could be written as a vector:

### 2017-10-11 Gruba/04-uc.tex
v4.3
v4.3

@@
 \multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
-numerical data				& $\#R_s$, $\#E_s$, $R_{ee}$, $\#B_s$, $R_{oc}$, $\#W_r$				\\	\midrule
+numerical data				& $\#R_u$, $\#E_u$, $R_{ee}$, $\#B_u$, $R_{oc}$, $\#W_r$				\\	\midrule
 categorical data			& $U_t$				\\	\midrule

### 2017-10-11 Gruba/05-gm.tex
v4.3
v4.3

@@
 \label{def:gm-it}
-An item $E$ involves a microblog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of  the owner of microblog $b$.
+An item $E$ involves a microblog $b$ and a user $f$ such that $f\ \in R_{b.O}$, i.e., $f$ is a follower of  the owner of microblog $b$.
 \begin{equation}
@@
 
-	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.
+	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{\#$R_u$, \#$E_u$, $R_{ee}$, \#$B_u$, \#$W_r$\}.
 

### 2017-10-12 Gruba/06-perf.tex

@@
 The features extraction result for Mary is displayed in Fig.\ \ref{fig:userFeatures}.
-Then we can see the basic information of Mary from the result. Her nickname is Actor Mary(ÑÝÔ±ÂíÀö) and she is from Beijing(±±¾©). 
+Then we can see the basic information of Mary from the result. Her nickname is Actor Mary(演员马丽) and she is from Beijing(北京).
 The number of followers of Mary is much more than the number of her friends.
-The Sina Microblog tag she made for herself is "actor"(ÑÝÔ±).
-As the result of the long-term interest extraction shows, she is interested in stage performances(ÎèÌ¨ºÈ²Ê), drama performances(»°¾ç±íÑÝ),films(µçÓ°¹âÓ°) and so on, which is consistent with her actual situation.
+The Sina Microblog tag she made for herself is "actor"(演员).
+As the result of the long-term interest extraction shows, she is interested in stage performances(舞台表演), drama performances(话剧表演),films(电影光影) and so on, which is consistent with her actual situation.
 What's more, the probability distribution of tweeting and retweeting behavior on different time periods in one day indicates that her activities at night is much more than daytime.
@@
 Here we queried Mary's short-term interest between 09/01/2016 and 09/30/2016, and got it as shown in Fig.\ \ref{fig:userFeatures}.
-We analyzed her microblogs in the this period, she has been working tirelessly to promote the drama "Earl of Oolong Mountain"(»ù¶½É½²®¾ô).
+We analyzed her microblogs in the this period, she has been working tirelessly to promote the drama "Earl of Oolong Mountain"(乌龙山伯爵).
 So the results are in line with expectations.

### 2017-10-13 Gruba/01-intro.tex

@@
 
-Social media is overwhelming nowadays, with massive users on Facebook, Twitter and Weibo while the number of users keeps increasing.
-These users behave variously, knowledge of which is significant in recommendation system, activity prediction and Big Thing analysis.
-Hence emerges the demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.
+Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users.
+These users behave variously, knowledge of which is significant for various applications such as recommendation system and activity analysis.
+Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.
 
-Central to user behavior modeling, is the need to choose the granularity of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating users. 
+Central to user behavior modeling, is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
 Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
@@
 
-The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
+The key driver of our work is the observation that in social media applications, users could fall into groups and each group shares representative behaviors.
 %
 As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
-Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well. 
-In the realm of social network behavior modeling, few work has been done over grouping, which however has been proved to be effective in other fields such as economic research.
-This motivates us to explore the incorporation of user grouping into the \retg{} behavior modeling, filling the gap of existed studies in literature.
+Particularly, we study the \retg{} behavior of users and our work can be readily generalized to other behaviors of like and comment as well.
+In the realm of social network behavior modeling, few work has been done over grouping, which however has been proved to be effective in other fields such as economic behavior analysis.
+This motivates us to incorporate user grouping into the \retg{} behavior modeling, filling the gap of existed studies that build a single model for all users.
 
-\stitle{Contributions.}
-This work contributes as follows:
+The contributions of our work are as follows:
 
@@
 
-\stitle{Organization.} The rest of this paper is organized as follows.
+Our paper is organized as follows.
 Section \ref{sec:overv} first gives the problem formulation and subsequently overviews \sys{}'s components, principle of which are detailed in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.

### 2017-10-13 Gruba/01-intro.tex

@@
 Our paper is organized as follows.
-Section \ref{sec:overv} first gives the problem formulation and subsequently overviews \sys{}'s components, principle of which are detailed in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
+Section \ref{sec:overv} gives the problem formulation and system overviews, followed by detailed explanations in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
 Section \ref{sec:perf} provides the performance evaluation.

### 2017-10-13 Gruba/00-abstr.tex

@@
 \begin{abstract}
-Social media applications are emerging, with rapidly growing users and large numbers of \retd{} microblogs every minute.
-The variety among users makes it difficult to model their \retg{} activities.
+%Social media applications are emerging, with rapidly growing users and large numbers of \retd{} microblogs every minute.
+The variety among massive users makes it difficult to model their \retg{} activities.
 Obviously, it is not suitable to cover the overall users by a single model. % \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
@@
 Our approach, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
-Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests, which results deep analyses towards the \retg{} behavior and proper models in the end.
-We have evaluated the performance of \sys{} by datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.
+Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests.
+%, which results deep analyses towards the \retg{} behavior and proper models in the end.
+We have evaluated the performance of \sys{} using datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.
 \end{abstract}

### 2017-10-13 Gruba/02-overview.tex

@@
-\section{\sys{} Overview}
+\section{Overview of System \sys{}}
 \label{sec:overv}
@@
 %
-Informally, providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} shall build a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$.
+Informally, providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} shall build a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$ or not.
 
@@
 
-\begin{figure}[!htb]
+\begin{figure}[tb!]
 \centering
@@
 \stitle{Key Modules.}
-In the heart of \sys{} lies Key Modules, which consists of three major components.
+\sys{} consists of three key modules.
 %\begin{enumerate}

### 2017-10-13 Gruba/02-overview.tex

@@
 \centering
-\includegraphics[width=.75\linewidth]{figures/architecture.pdf}
+\includegraphics[width=.7\linewidth]{figures/architecture.pdf}
 \caption{\sys{} Architecture}
@@
 
-\stitle{Sina Microblog Data.} It is the data to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
+\stitle{Sina Microblog Data.} It is the data to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definitions} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
 

### 2017-10-13 Gruba/03-fe.tex

@@
 
-\begin{table}[!htb]
+\begin{table}[tb!]
 \centering
@@
 \toprule
-\multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
+\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
 \#$R_u$				& number of followers				\\	\midrule
 \#$E_u$				& number of followees				\\	\midrule
-\multirow{4}{*}{$R_{ee}$} & \multirow{2}{*}{a ratio defined as the number of followers} \\
-                   &                     \\
-                   & \multirow{2}{*}{over that of followees, i.e., $\frac{\#R_u}{\#E_u}$} \\
-                   & 						\\	\midrule
+                    & a ratio defined as the number of followers over \\  
+\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
 $U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
@@
 \toprule
-\multicolumn{1}{c}{\textbf{value}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
-0                       & $\#E_u \le 50 \ \& \ \#R_u \le 50$				\\	\midrule
+\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
+0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
 \multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\

### 2017-10-13 Gruba/01-intro.tex

@@
 Our paper is organized as follows.
-Section \ref{sec:overv} gives the problem formulation and system overviews, followed by detailed explanations in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
+Section \ref{sec:overv} gives the problem formulation and system overview, followed by detailed explanations in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm}.
 Section \ref{sec:perf} provides the performance evaluation.

### 2017-10-13 Gruba/01-intro.tex

@@
 Section \ref{sec:overv} gives the problem formulation and system overview, followed by detailed explanations in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm}.
-Section \ref{sec:perf} provides the performance evaluation.
-Related work is presented in Section \ref{sec:rela}.
-Finally, Section \ref{sec:conclu} concludes the work.
+Section \ref{sec:perf} is performance evaluation, followed by
+related work in Section \ref{sec:rela} and conclusion in Section \ref{sec:conclu}.

### 2017-10-13 Gruba/02-overview.tex

@@
 \label{def:blog}
-A microblog $M_b = (O, T, M, flag)$ consists of the owner $O$ (a.k.a.
-user in this paper) to whom $M_b$ belongs (either created or \retd{}), the timestamp $T$ showing when $M_b$ is generated, the microblog message $M$ and a bit $flag$ denoting $M_b$ is \retd{} (1) or originally created (0) by the owner $O$.
+A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a.
+user in this paper) to whom $M_b$ belongs (either created or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally created (0) by $O$.
 \end{definition}
@@
 \label{def:user}
-A user $u = (B_u, R_u, E_u)$ consists of three sets regarding the user's microblogs $B_u$, followers $R_u$ and followees $E_u$ separately.
-Each follower/followee per se refers to a user.
+A user $u = (B_u, R_u, E_u)$ consists of three sets regarding the user's microblogs $B_u$, followers $R_u$ and followees $E_u$, in which each follower/followee per se refers to a user.
 \end{definition}
@@
 \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
-Figure \ref{fig:framework} shows the architectural components of \sys{}, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.
+Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.
 
@@
 \centering
-\includegraphics[width=.7\linewidth]{figures/architecture.pdf}
+\includegraphics[width=.67\linewidth]{figures/architecture.pdf}
+\vspace{-1ex}
 \caption{\sys{} Architecture}
 \label{fig:framework}
+\vspace{-4ex}
 \end{figure}
@@
 They are features of \textit{Basics} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests).
-These features are extracted from the stored data by Feature Extraction module and serve as the input of User Clustering module.
+These features are extracted from the stored  Sina Weibo data by Feature Extraction module, and serve as the input of the User Clustering module.
 
@@
 
-	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling employs both positive and negative samples (i.e., microblogs that were labeled with \retd{} and not \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
+	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling builds a  model by employing both positive and negative samples (i.e., microblogs that are labeled with \retd{} and not \retd{}), over which the testing of users' \retg{} behavior is performed.
 %\end{enumerate}
@@
 %For the time being, Profile Demonstrator presents \tbc{}.
+
+System  \sys{} models user behaviors over groups instead of the mono model for all users.
+
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Illustration of Variables in Basic Feature}
+\vspace{0.3cm}
+\label{tbl:fe-info}
+\begin{tabular}{ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
+\#$R_u$				& number of followers				\\	\midrule
+\#$E_u$				& number of followees				\\	\midrule
+                    & a ratio defined as the number of followers over \\
+\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
+$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
+\end{tabular}
+\end{small}
+\vspace{-3ex}
+\end{table}
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Category of User Type}
+\vspace{0.3cm}
+\label{tbl:ucate}
+\begin{tabular}{ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
+0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
+\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
+ 						&                       									\\	\midrule
+\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
+						&															\\	\midrule
+3                   	& other cases 												\\ \bottomrule
+\end{tabular}
+\end{small}
+\end{table}

### 2017-10-13 Gruba/03-fe.tex

@@
 %Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.
-
-\begin{table}[tb!]
-\centering
-\begin{small}
-\caption{Illustration of Variables in Basic Feature}
-\vspace{0.3cm}
-\label{tbl:fe-info}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
-\#$R_u$				& number of followers				\\	\midrule
-\#$E_u$				& number of followees				\\	\midrule
-                    & a ratio defined as the number of followers over \\  
-\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
-$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
-\end{tabular}
-\end{small}
-\end{table}
-
-%mutex category
-%type 0 is assumed to be representative
-
-%replace 50 and 5 by variables of threshold
-
-\begin{table}[tb!]
-\centering
-\begin{small}
-\caption{Category of User Type}
-\vspace{0.3cm}
-\label{tbl:ucate}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
-0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
-\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
- 						&                       									\\	\midrule
-\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
-						&															\\	\midrule
-3                   	& other cases 												\\ \bottomrule
-\end{tabular}
-\end{small}
-\end{table}
 

### 2017-10-13 Gruba/02-overview.tex

@@
 %
-Informally, providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} shall build a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$ or not.
+Providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} builds a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$ or not.
 
@@
 
-System  \sys{} models user behaviors over groups instead of the mono model for all users.
+The distinctive feature of System  \sys{} is to model user \retg{} behaviors over groups instead of the mono model for all users.
 

### 2017-10-13 Gruba/02-overview.tex

@@
 
-\stitle{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator for visualization.
+\stitle{Demonstrator.} At the top layer of \sys{}, it is the Demonstrator for visualizing all aspects of the system, e.g., profiling of user groups.
 %For the time being, Profile Demonstrator presents \tbc{}.
 
-The distinctive feature of System  \sys{} is to model user \retg{} behaviors over groups instead of the mono model for all users.
+As shown above, the distinctive feature of System  \sys{} is to model user \retg{} behaviors over groups instead of the mono model for all users.
 

### 2017-10-13 Gruba/01-intro.tex

@@
 
-Central to user behavior modeling, is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
+Central to user behavior modeling is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
 Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.

### 2017-10-13 Gruba/02-overview.tex

@@
 \label{def:user}
-A user $u = (B_u, R_u, E_u)$ consists of three sets regarding the user's microblogs $B_u$, followers $R_u$ and followees $E_u$, in which each follower/followee per se refers to a user.
+Given a user $u$, $B_u$, $R_u$ and $E_u$ represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee per se refers to a user.
 \end{definition}
@@
 By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = M_b.O$ and $M_b \in B_u$.
-%
-Providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} builds a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$ or not.
+
+Providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower $f$ of its onwer $b.O$, i.e., $f \in R_{b.O}$, system \sys{} builds a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ \ret{s} $b$ or not.
 
 \subsection{\sys{} Framework}
-\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
+System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
 Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.
@@
 \caption{Illustration of Variables in Basic Feature}
-\vspace{0.3cm}
+%\vspace{0.3cm}
 \label{tbl:fe-info}
@@
 \caption{Category of User Type}
-\vspace{0.3cm}
+%\vspace{0.3cm}
 \label{tbl:ucate}
@@
 \end{small}
+\vspace{-2ex}
 \end{table}

### 2017-10-13 Gruba/02-overview.tex

@@
 %The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
-By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = M_b.O$ and $M_b \in B_u$.
+Note that $M_b.O$ is a user, and $B_u$ is a set of $M_b$.
 
@@
 \subsection{\sys{} Framework}
-System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
+System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media, and 
 Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.
@@
 	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories.
-They are features of \textit{Basics} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests).
+They are features of \textit{Basics} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., long and short term interests, as well as explicit and implicit interests).
 These features are extracted from the stored  Sina Weibo data by Feature Extraction module, and serve as the input of the User Clustering module.

### 2017-10-13 Gruba/02-overview.tex

@@
 
-	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling builds a  model by employing both positive and negative samples (i.e., microblogs that are labeled with \retd{} and not \retd{}), over which the testing of users' \retg{} behavior is performed.
+	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling builds a  model by employing both positive and negative samples (i.e., microblogs labeled with \retd{} and not \retd{}), on which the user \retg{} behaviors are also tested.
 %\end{enumerate}

### 2017-10-13 Gruba/02-overview.tex

@@
 %The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
-Note that $M_b.O$ is a user, and $B_u$ is a set of $M_b$.
+Note that $M_b.O$ is a user $u$, and $B_u$ is a set of $M_b$.
 
@@
 
-\stitle{Sina Microblog Data.} It is the data to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definitions} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
+\stitle{Sina Microblog Data.} It is the data crawled to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definitions} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
 

### 2017-10-13 Gruba/02-overview.tex

@@
                     & a ratio defined as the number of followers over \\
-\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
+\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
 $U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule

### 2017-10-13 Gruba/02-overview.tex

@@
 \label{def:user}
-Given a user $u$, $B_u$, $R_u$ and $E_u$ represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee per se refers to a user.
+Given a user $u$, we adopt $B_u$, $R_u$ and $E_u$ to represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee per se refers to a user.
 \end{definition}

### 2017-10-13 Gruba/03-fe.tex

@@
 \label{eq:info}
-	I = (\#R_u,\ \#E_u,\ R_{ee},\ \ U_t)
+	I = (G_u,\ P_u,\ \#R_u,\ \#E_u,\ R_{ee},\ \ U_t)
 \end{equation}
@@
 %Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.
+
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Illustration of Variables in Basic Feature}
+\vspace{0.3cm}
+\label{tbl:fe-info}
+\begin{tabular}{ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
+$G_u$				& gender of user $u$				\\	\midrule
+$P_u$				& province of user $u$				\\	\midrule
+\#$R_u$				& number of followers				\\	\midrule
+\#$E_u$				& number of followees				\\	\midrule
+                    & a ratio defined as the number of followers over \\  
+\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
+$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
+\end{tabular}
+\end{small}
+\end{table}
 
@@
 	\item a ratio $R_{oc}$ that is defined as the number of \retd{} microblogs over that of originally created, i.e., $\frac{\#(B_u | flag ==1)}{\#(B_u | flag ==0)}$
-	\item a value showing the average number of \retd{} microblogs per week: $\#W_r$
-	\item a normalized vector regarding the time distribution of a user's \retg{} behavior: $P_t\ = (p'_0,\ p'_1,\ ...,\ p'_{11})$, where $p'_0$ is the probability that the \retg{} activity happens from 0am to 2am, $p'_1$ is the probability that the \retg{} activity happens from 2am to 4am, and so on.
-	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_g\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} microblogs is within 1 min.
+	\item values showing the average number of \retd{} and \twe{} microblogs per week: $\#W_r$, $\#W_t$
+	\item a normalized vector regarding the time distribution of a user's \retg{} behavior: $P_{rt}\ = (p'_0,\ p'_1,\ ...,\ p'_{11})$, where $p'_0$ is the probability that the \retg{} activity happens from 0am to 2am, $p'_1$ is the probability that the \retg{} activity happens from 2am to 4am, and so on.
+    \item a normalized vector regarding the time distribution of a user's \twtg{} behavior: $P_{tt}$, obtained as $P_{rt}$.
+
+	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_{rg}\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} microblogs is within 1 min.
 Ditto for $p''_1$ (1 min to 1 hour), $p''_2$ (1 to 12 hours), $p''_3$ (12 to 24 hours), $p''_4$ (24 to 48 hours) and  $p''_5$ (more than 48 hours).
+    \item a normalized vector with respect to the gap distribution of a user's \twtg{} behavior: $P_{tg}$, obtained as $P_{rg}$.
 \end{itemize}
@@
 \label{eq:beha}
-	H = (\#W_r,\ P_t,\ P_g)
+	H = (\#B_u, R_{oc},\ \#W_r,\ P_{rt},\ P_{rg},\ \#W_t,\ P_{tt},\ P_{tg})
 \end{equation}
-where $\#W_r$, $P_t$ and $P_g$ are illustrated as above.
+% where $\#B_u$, $R_{oc}$, $\#W_r$, $P_t$ and $P_g$ are illustrated as above.
 
@@
 Different from the straightforward notions of \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
-In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the probability that the said user matches a \textit{topic}.
+In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the degree that the said user is interested in the corresponding \textit{topic}.
 
@@
 In short, \sys{} employs a well established lexicon to discover the explicit interests of users.
-In case no proper explicit interests are found, TF-IDF and Twitter-LDA are leveraged to explore the implicit interests, during which word2vector participates to provide the similarity between two words.
+In case no proper explicit interests are found, TF-IDF(term-frequency and inverse document-frequency) and Twitter-LDA \cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector participates to provide the similarity between two words.
 
@@
 
-\stitle{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in microblog $b$:
+\stitle{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF to calculate the weight distribution of words in microblog $b$:
 \begin{equation}
@@
 \stitle{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing}
-\cite{IEEEexample:zhao2011comparing}
 to result the word weight distribution of microblog $b$.
@@
 \label{eq:fu-flat}
-	F(u) = (\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)
+	F(u) = (G_u,\ P_u, \#R_s, \#E_s, R_{ee}, U_t, \#B_u,\ R_{oc},\ \#W_r,\ P_{rt},\ P_{rg},\ \#W_t,\ P_{tt},\ P_{tg}, P_f)
+%(\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)
 \end{equation}

### 2017-10-13 Gruba/02-overview.tex

@@
 A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a.
-user in this paper) to whom $M_b$ belongs (either created or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally created (0) by $O$.
+user in this paper) to whom $M_b$ belongs (either created or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally \tw{} (0) by $O$.
 \end{definition}
@@
 \centering
-\includegraphics[width=.67\linewidth]{figures/architecture.pdf}
+\includegraphics[width=.67\linewidth]{figures/architecture.eps}
 \vspace{-1ex}
@@
 \multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
+$G_u$				& gender of user $u$				\\	\midrule
+$P_u$				& province of user $u$				\\	\midrule
 \#$R_u$				& number of followers				\\	\midrule
@@
                     & a ratio defined as the number of followers over \\
-\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
+\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
 $U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
@@
 \end{small}
-\vspace{-3ex}
 \end{table}
+
 \begin{table}[tb!]

### 2017-10-13 Gruba/03-fe.tex

@@
 
-\begin{table}[tb!]
-\centering
-\begin{small}
-\caption{Illustration of Variables in Basic Feature}
-\vspace{0.3cm}
-\label{tbl:fe-info}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
-$G_u$				& gender of user $u$				\\	\midrule
-$P_u$				& province of user $u$				\\	\midrule
-\#$R_u$				& number of followers				\\	\midrule
-\#$E_u$				& number of followees				\\	\midrule
-                    & a ratio defined as the number of followers over \\  
-\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
-$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
-\end{tabular}
-\end{small}
-\end{table}
-
 \subsection{Behavior Feature}
@@
 	\item a value for the number of owned microblogs $\#B_u$
-	\item a ratio $R_{oc}$ that is defined as the number of \retd{} microblogs over that of originally created, i.e., $\frac{\#(B_u | flag ==1)}{\#(B_u | flag ==0)}$
-	\item values showing the average number of \retd{} and \twe{} microblogs per week: $\#W_r$, $\#W_t$
-	\item a normalized vector regarding the time distribution of a user's \retg{} behavior: $P_{rt}\ = (p'_0,\ p'_1,\ ...,\ p'_{11})$, where $p'_0$ is the probability that the \retg{} activity happens from 0am to 2am, $p'_1$ is the probability that the \retg{} activity happens from 2am to 4am, and so on.
-    \item a normalized vector regarding the time distribution of a user's \twtg{} behavior: $P_{tt}$, obtained as $P_{rt}$.
+	\item a ratio $R_{oc}$ that is defined as the number of \retd{} microblogs over that of originally \twd{}, i.e., $\frac{\#(B_u | flag ==1)}{\#(B_u | flag ==0)}$
+	\item values showing the average number of \retd{} and \twd{} microblogs per week: $\#W_r$, $\#W_t$
+	\item normalized vectors regarding the time distribution of a user's \retg{}/\twg{} behavior: $P_{rt}\ = (p'_{r0},\ p'_{r1},\ ...,\ p'_{r11})$, $P_{tt}\ = (p'_{t0},\ p'_{t1},\ ...,\ p'_{t11})$, where $p'_{r0}$/$p'_{t0}$ is the probability that the \retg{}/\twg{} activity happens from 0am to 2am, $p'_{r1}$/$p'_{t1}$ is the probability that the \retg{}/\twg{} activity happens from 2am to 4am, and so on.
 
-	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_{rg}\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} microblogs is within 1 min.
-Ditto for $p''_1$ (1 min to 1 hour), $p''_2$ (1 to 12 hours), $p''_3$ (12 to 24 hours), $p''_4$ (24 to 48 hours) and  $p''_5$ (more than 48 hours).
-    \item a normalized vector with respect to the gap distribution of a user's \twtg{} behavior: $P_{tg}$, obtained as $P_{rg}$.
+	\item normalized vectors with respect to the gap distribution of a user's \retg{}/\twg{} behavior: $P_{rg}\ = (p''_{r0},\ p''_{r1},\ ...,\ p''_{r5})$, $P_{tg}\ = (p''_{t0},\ p''_{t1},\ ...,\ p''_{t5})$, in which $p''_{r0}$/$p''_{t0}$ is the probability that the gap between two \retd{}/\twg{} microblogs is within 1 min.
+Ditto for $p''_{r1}$/$p''_{t1}$ (1 min to 1 hour), $p''_{r2}$/$p''_{t2}$ (1 to 12 hours), $p''_{r3}$/$p''_{t3}$ (12 to 24 hours), $p''_{r4}$/$p''_{t4}$ (24 to 48 hours) and  $p''_{r5}$/$p''_{t5}$ (more than 48 hours).
 \end{itemize}
@@
 \label{eq:beha}
-	H = (\#B_u, R_{oc},\ \#W_r,\ P_{rt},\ P_{rg},\ \#W_t,\ P_{tt},\ P_{tg})
+	H = (\#B_u, R_{oc},\ \#W_r,\ P_{rt},\\
+    P_{rg},\ \#W_t,\ P_{tt},\ P_{tg})
 \end{equation}
@@
 Different from the straightforward notions of \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
-In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the degree that the said user is interested in the corresponding \textit{topic}.
+In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the degree that the said user is interested with the corresponding \textit{topic}.
 
@@
 \label{eq:fu-flat}
-	F(u) = (G_u,\ P_u, \#R_s, \#E_s, R_{ee}, U_t, \#B_u,\ R_{oc},\ \#W_r,\ P_{rt},\ P_{rg},\ \#W_t,\ P_{tt},\ P_{tg}, P_f)
+	F(u) = (G_u, P_u, \#R_s, \#E_s, R_{ee}, U_t, \#B_u, R_{oc},\\
+    \#W_r, P_{rt}, P_{rg}, \#W_t, P_{tt}, P_{tg}, P_f)
 %(\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)

### 2017-10-13 Gruba/02-overview.tex

@@
 A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a.
-user in this paper) to whom $M_b$ belongs (either created or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally \tw{} (0) by $O$.
+user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally \tw{} (0) by $O$.
 \end{definition}

### 2017-10-13 Gruba/02-overview.tex

@@
 %This section shall look into the principle of each component in Processing Runtime subsystem, putting forth a full-fledged system.
+
+\subsection{\sys{} Framework}
+System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media, and
+Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.
+
+\begin{figure}[tb!]
+\centering
+\includegraphics[width=.67\linewidth]{figures/architecture.eps}
+\vspace{-1ex}
+\caption{\sys{} Architecture}
+\label{fig:framework}
+\vspace{-5ex}
+\end{figure}
 
@@
 
-\subsection{\sys{} Framework}
-System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media, and
-Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.
-
-\begin{figure}[tb!]
-\centering
-\includegraphics[width=.67\linewidth]{figures/architecture.eps}
-\vspace{-1ex}
-\caption{\sys{} Architecture}
-\label{fig:framework}
-\vspace{-4ex}
-\end{figure}
-
 % #like and #comment are saved; could generalize \sys{} to model the liking behavior (among commented blogs)
@@
 \end{comment}
+
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Illustration of Variables in Basic Feature}
+%\vspace{0.3cm}
+\label{tbl:fe-info}
+\begin{tabular}{ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
+$G_u$				& gender of user $u$				\\	\midrule
+$P_u$				& province of user $u$				\\	\midrule
+\#$R_u$				& number of followers				\\	\midrule
+\#$E_u$				& number of followees				\\	\midrule
+                    & a ratio defined as the number of followers  \\
+\raisebox{1.5ex}{$R_{ee}$}  & over that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
+$U_t$					& user type (as illustrated in Table \ref{tbl:ucate})			\\ \bottomrule
+\end{tabular}
+\end{small}
+\vspace{-2ex}
+\end{table}
+
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Category of User Type}
+%\vspace{0.3cm}
+\label{tbl:ucate}
+\begin{tabular}{ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
+0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
+\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
+ 						&                       									\\	\midrule
+\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
+						&															\\	\midrule
+3                   	& other cases 												\\ \bottomrule
+\end{tabular}
+\end{small}
+\vspace{-2ex}
+\end{table}
 
@@
 As shown above, the distinctive feature of System  \sys{} is to model user \retg{} behaviors over groups instead of the mono model for all users.
-
-\begin{table}[tb!]
-\centering
-\begin{small}
-\caption{Illustration of Variables in Basic Feature}
-%\vspace{0.3cm}
-\label{tbl:fe-info}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
-$G_u$				& gender of user $u$				\\	\midrule
-$P_u$				& province of user $u$				\\	\midrule
-\#$R_u$				& number of followers				\\	\midrule
-\#$E_u$				& number of followees				\\	\midrule
-                    & a ratio defined as the number of followers over \\
-\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
-$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
-\end{tabular}
-\end{small}
-\end{table}
-
-\begin{table}[tb!]
-\centering
-\begin{small}
-\caption{Category of User Type}
-%\vspace{0.3cm}
-\label{tbl:ucate}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
-0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
-\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
- 						&                       									\\	\midrule
-\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
-						&															\\	\midrule
-3                   	& other cases 												\\ \bottomrule
-\end{tabular}
-\end{small}
-\vspace{-2ex}
-\end{table}

### 2017-10-13 Gruba/02-overview.tex

@@
 
-We consider people's \retg{} behavior in social media.
+We consider the \retg{} behavior of users in social media.
 %For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
@@
                     & a ratio defined as the number of followers  \\
-\raisebox{1.5ex}{$R_{ee}$}  & over that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
-$U_t$					& user type (as illustrated in Table \ref{tbl:ucate})			\\ \bottomrule
+\raisebox{1.5ex}{$R_{ee,u}$}  & over that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
+$U_{t,u}$					& user type (as illustrated in Table \ref{tbl:ucate})			\\ \bottomrule
 \end{tabular}

### 2017-10-13 Gruba/03-fe.tex

@@
-% jing @ 0927
-% back to algorithm for interest features
-% add motivation, intuition, etc
-
-%clear points
-%road map
-%detail of each step, with motivation
-
 \section{Feature Extraction}
@@
 
-With the underlying Sina Microblog Data, Feature Extraction is responsible for ``mining'' the user characteristics, resulting three features for each user.
-These features are \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.
+With the underlying Sina Microblog Data, the Feature Extraction module is responsible for ``mining'' the user characteristics, and produces three classes of features for each user: \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, referred to as  \textit{Feature Data} in \sys{}.
+%, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.
 
@@
 
-\textit{Basic Feature} employs a vector $I$ to cover the basic info of user.
+The \textit{Basic Feature} employs a vector $I$ to depict the basic characteristics of a user $u$.
 \begin{equation}
 \label{eq:info}
-	I = (G_u,\ P_u,\ \#R_u,\ \#E_u,\ R_{ee},\ \ U_t)
+	I_u = (G_u, P_u, \#R_u, \#E_u, R_{ee,u}, U_{t,u}),
 \end{equation}
-where each variable is illustrated in Table \ref{tbl:fe-info}.
+in which the variable details are illustrated in Table \ref{tbl:fe-info}.
 %Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.
@@
 
-Unlike \textit{Basic Feature}, \textit{Behavior Feature} shows several statistics regarding the user's \retg{} behavior.
-Such statistics include:
-\begin{itemize}
-	\item a value for the number of owned microblogs $\#B_u$
-	\item a ratio $R_{oc}$ that is defined as the number of \retd{} microblogs over that of originally \twd{}, i.e., $\frac{\#(B_u | flag ==1)}{\#(B_u | flag ==0)}$
-	\item values showing the average number of \retd{} and \twd{} microblogs per week: $\#W_r$, $\#W_t$
-	\item normalized vectors regarding the time distribution of a user's \retg{}/\twg{} behavior: $P_{rt}\ = (p'_{r0},\ p'_{r1},\ ...,\ p'_{r11})$, $P_{tt}\ = (p'_{t0},\ p'_{t1},\ ...,\ p'_{t11})$, where $p'_{r0}$/$p'_{t0}$ is the probability that the \retg{}/\twg{} activity happens from 0am to 2am, $p'_{r1}$/$p'_{t1}$ is the probability that the \retg{}/\twg{} activity happens from 2am to 4am, and so on.
+Unlike \textit{Basic Feature}, the \textit{Behavior Feature} of a user $u$ is certain statistics regarding the \retg{} behavior of $u$, shown below:
 
-	\item normalized vectors with respect to the gap distribution of a user's \retg{}/\twg{} behavior: $P_{rg}\ = (p''_{r0},\ p''_{r1},\ ...,\ p''_{r5})$, $P_{tg}\ = (p''_{t0},\ p''_{t1},\ ...,\ p''_{t5})$, in which $p''_{r0}$/$p''_{t0}$ is the probability that the gap between two \retd{}/\twg{} microblogs is within 1 min.
+\sstab(a) the number of owned microblogs $\#B_u$,
+
+\sstab(b) the ratio $R_{oc,u}$ that is the number of \retd{} microblogs over that of originally \twd{}, i.e., $\frac{\#(B_u | flag ==1)}{\#(B_u | flag ==0)}$,
+
+\sstab(c) the average number of \retd{} and \twd{} microblogs per week: $\#W_{r,u}$ and $\#W_{t,u}$,
+
+\sstab(d) the normalized vectors regarding the time distribution of a user's \retg{}/\twg{} behavior: $P_{rt,u}\ = (p'_{r0},\ p'_{r1},\ ...,\ p'_{r11})$, $P_{tt,u}\ = (p'_{t0},\ p'_{t1},\ ...,\ p'_{t11})$, where $p'_{r0}$/$p'_{t0}$ is the probability that the \retg{}/\twg{} activity happens from 0am to 2am, $p'_{r1}$/$p'_{t1}$ is the probability that the \retg{}/\twg{} activity happens from 2am to 4am, and so on, and
+
+\sstab(e) the normalized vectors with respect to the gap distribution of a user's \retg{}/\twg{} behavior: $P_{rg,u}\ = (p''_{r0},\ p''_{r1},\ ...,\ p''_{r5})$, $P_{tg,u}\ = (p''_{t0},\ p''_{t1},\ ...,\ p''_{t5})$, in which $p''_{r0}$/$p''_{t0}$ is the probability that the gap between two \retd{}/\twg{} microblogs is within 1 min.
 Ditto for $p''_{r1}$/$p''_{t1}$ (1 min to 1 hour), $p''_{r2}$/$p''_{t2}$ (1 to 12 hours), $p''_{r3}$/$p''_{t3}$ (12 to 24 hours), $p''_{r4}$/$p''_{t4}$ (24 to 48 hours) and  $p''_{r5}$/$p''_{t5}$ (more than 48 hours).
-\end{itemize}
 
-Hence, \textit{Behavior Feature} $H$ per user comes with:
+In summary, the \textit{Behavior Feature} $H_u$ of user $u$ consists of the following:
+
 \begin{equation}
 \label{eq:beha}
-	H = (\#B_u, R_{oc},\ \#W_r,\ P_{rt},\\
-    P_{rg},\ \#W_t,\ P_{tt},\ P_{tg})
+(\#B_u, R_{oc,u}, \#W_{r,u}, P_{rt,u}, P_{rg,u}, \#W_{t,u}, P_{tt,u}, P_{tg,u}).
 \end{equation}
+
 % where $\#B_u$, $R_{oc}$, $\#W_r$, $P_t$ and $P_g$ are illustrated as above.
@@
 \label{eq:fu-flat}
+\begin{aligned}
 	F(u) = (G_u, P_u, \#R_s, \#E_s, R_{ee}, U_t, \#B_u, R_{oc},\\
@@
 %(\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)
+\end{aligned}
 \end{equation}

### 2017-10-13 Gruba/04-uc.tex

@@
 \multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
-numerical data				& $\#R_u$, $\#E_u$, $R_{ee}$, $\#B_u$, $R_{oc}$, $\#W_r$				\\	\midrule
-categorical data			& $U_t$				\\	\midrule
-normalized vectors			& $P_t$, $P_g$, $P_f$			\\ \bottomrule
+numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$,\\
+                            &  $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$				\\	\midrule
+categorical data			& $G_u$,$P_u$,$U_{t,u}$				\\	\midrule
+normalized vectors			& $P_{rt,u}$, $P_{rg,u}$,$P_{tt,u}$,$P_{tg,u}$,$P_{f,u}$			\\ \bottomrule
 \end{tabular}
@@
     H_e\ (1\ or\ 0)       	& \quad \text{if } Y_e/Z_e \text{ is categorical}\\
-    Y_e \cdot Z_e  		& \quad \text{if } Y_e/Z_e \text{ is of normalized vector}
+    1 - Y_e \cdot Z_e  		& \quad \text{if } Y_e/Z_e \text{ is of normalized vector}
   \end{cases}

### 2017-10-13 Gruba/04-uc.tex

@@
 
-As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers, categories and normalized vectors.
+As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers(normalized to 0-1 range), categories and normalized vectors.
 For simplicity, we shall first illustrate the distance calculation of the simple vectors with mono data type on each dimension and then demonstrate that of complex vectors in K-Gru.

### 2017-10-13 Gruba/05-gm.tex

@@
 
-	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{\#$R_u$, \#$E_u$, $R_{ee}$, \#$B_u$, \#$W_r$\}.
+	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{$G_u$, $P_u$,\#$R_u$, \#$E_u$, $R_{ee,u}$ \}.
 
-	\stab(2) \stitle{Microblog Info} considers the correlation between microblog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}.
-The correlation metric $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}).
-Each event could be viewed as a topic $t$, over which the correlation of a microblog $b$ could be obtained by formula \ref{eq:simbt}.
+	\stab(2) \stitle{Microblog Info} refers to metrics related to the microblog $b$.
+The number of times the $b$ be retweeted, be commented, be liked and the length of the microblog contents are considered.
+What's more, we also considers the correlation between microblog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}.
+The correlation metric $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_{f,u}$ in formula \ref{eq:inte}).
+Each event could be viewed as a topic $t$, over which the correlation of a microblog $b$ could be obtained by formula \ref{eq:sim-tw1}.
 
-	\stab(3) \stitle{Interaction Info} includes three correlation metrics.
-They are of microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.
-long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
+	\stab(3) \stitle{Interaction Info} includes seven correlation metrics.
+They are of \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.
+long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
 %\end{itemize}
+
 In this paper, we see modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem.

### 2017-10-13 Gruba/03-fe.tex

@@
 \stitle{Step 5:} TF-IDF based similarity is calculated.
-For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
+%For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined %as:
+%\begin{equation}
+%\label{eq:sim-tf1}
+%sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
+%\end{equation}
+%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.
+%Go to \textbf{Step 7}.
+
+For example, the similarity of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as formula \ref{eq:sim-tf1}.
+Here $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, $VEC_{W_f}$ is defined as formula \ref{eq:sum-tf1}, $VEC_t$ is defined as formula \ref{eq:sum-lexion}, where $N_t$ is the word count in topic $t$ and $vec[w]$ is the word vector of word $w$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
 \begin{equation}
 \label{eq:sim-tf1}
-sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
+%\cdot
+sim(W_f, t) = VEC_{W_f} \cdot VEC_t
+%\sum_{\substack{i}} p_i*sim(w_i, t)
 \end{equation}
-where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
-Go to \textbf{Step 7}.
+\begin{equation}
+\label{eq:sum-tf1}
+%\cdot
+VEC_{W_f} = \sum_{\substack{i}} p_i*vec[w_i]
+%\sum_{\substack{i}} p_i*sim(w_i, t)
+\end{equation}
+\begin{equation}
+\label{eq:sum-lexion}
+%\cdot
+VEC_t = \sum_{\substack{j}} \frac{1}{N_t}*vec[c_j]
+%\sum_{\substack{i}} p_i*sim(w_i, t)
+\end{equation}
+
+%and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$
+%Go to \textbf{Step 7}.
 
@@
 \stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
+%Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined %as:
+%\begin{equation}
+%\label{eq:sim-tw1}
+%sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
+%\end{equation}
+%%%where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$,
+%where $W_w$ is a set of $(w'_i, p'_i)$, $t$ covers each $c_j$,
+%and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
+%Go to \textbf{Step 7}.
+
 Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
@@
 \label{eq:sim-tw1}
-sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
+sim(W_w, t) = VEC_{W_w} \cdot VEC_t
 \end{equation}
-%where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$,
-where $W_w$ is a set of $(w'_i, p'_i)$, $t$ covers each $c_j$,
-and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
-Go to \textbf{Step 7}.
+%%%where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$,
+where $W_w$ is a set of $(w'_i, p'_i)$, $t$ covers each $c_j$, and $VEC_{W_w}$ can be obtained similarly as $VEC_{W_f}$.
 

### 2017-10-13 Gruba/05-gm.tex

@@
 
+%	\stab(2) \stitle{Microblog Info} refers to metrics related to the microblog $b$.
+The number of times the $b$ be retweeted, be %commented, be liked and the length of the microblog contents are considered.
+What's more, we also considers the correlation between %microblog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}.
+The correlation metric $C_h$ is in %the form of a normalized vector with each dimension represents one event (similar as $P_{f,u}$ in formula \ref{eq:inte}).
+Each event %could be viewed as a topic $t$, over which the correlation of a microblog $b$ could be obtained by formula \ref{eq:sim-tw1}.
+
 \stab(2) \stitle{Microblog Info} refers to metrics related to the microblog $b$.
-The number of times the $b$ be retweeted, be commented, be liked and the length of the microblog contents are considered.
-What's more, we also considers the correlation between microblog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}.
-The correlation metric $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_{f,u}$ in formula \ref{eq:inte}).
-Each event could be viewed as a topic $t$, over which the correlation of a microblog $b$ could be obtained by formula \ref{eq:sim-tw1}.
+%The number of times the $b$ has been retweeted, commented, liked and the length of the microblog contents are considered.
+The number that $b$ has been retweeted, commented, liked and the length of $b.M$ (microblog message) are considered.
+What's more, we consider the correlation between $b$ and recent event, where the latter is expressed as several core words returned by Ring \cite{IEEEexample:ring}.
+Here we compute \textit{TF-IDF weight} $W_f$ of $b.M$, and get correlation metric $C_h$ of $b$ and event by formula \ref{eq:sim-tf1}.
 
-	\stab(3) \stitle{Interaction Info} includes seven correlation metrics.
-They are of \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.
-long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
+%	\stab(3) \stitle{Interaction Info} includes seven correlation metrics.
+They are of \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, %microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.
+long-term/stable interest in this work), $b$ versus %$u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, %and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
 %\end{itemize}
+	\stab(3) \stitle{Interaction Info} includes seven correlation metrics: \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.
+long-term/stable interest in this work), and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
+%In addition, the correlation between microblog contents and $u$'s short-term interest mined from $u$'s recent microblogs (e.g., within 30 days) is also taken in consideration.
+%In addition, the correlation between microblog contents and $u$'s short-term interest is also taken in consideration. The short-term %interest is expressed as
+In addition, we consider $u$'s short-term interest, which is mined from $u$'s recent microblogs (e.g., within 30 days) and calculated by \textit{TF-IDF}, namely $W_s$. 
+The correlation between microblog and $u$'s short-term interest is computed by $W_f$ and $W_s$ (using formula \ref{eq:sim-tf1}).
+%%
 
-In this paper, we see modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem.
-The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
+In this paper, we view modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem.
+The advantage of classification model lies in that it could integrate different features conveniently.
+%The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
 As a result, the obtained group behavior model could learn what does a positive/negative item look like over each metric mentioned above.\par

### 2017-10-13 Gruba/03-fe.tex

--- 2017-10-13 Gruba/03-fe.tex
@@
 
-With the underlying Sina Microblog Data, the Feature Extraction module is responsible for ``mining'' the user characteristics, and produces three classes of features for each user: \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, referred to as  \textit{Feature Data} in \sys{}.
+With the underlying Sina Microblog Data, the Feature Extraction module is responsible for mining the user characteristics, and produces three classes of features for each user: \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, referred to as  \textit{Feature Data} in \sys{}.
 %, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.
@@
 
-Different from the straightforward notions of \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
-In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the degree that the said user is interested with the corresponding \textit{topic}.
+Different from the slightly straightforward \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users with their interested topics.
+In short, with a given lexicon (made by some professionals) consisting of several \textit{topics}, the interest feature of a user $u$ is a normalized vector, in which each entry refers to the degree that $u$ is interested in the corresponding \textit{topic}.
 
@@
 \label{def:lexi}
-A lexicon $L$ consists of a set of topics $t$ such that each topic is associated with a set of cell words $c$. Each cell word depicts an aspect of the topic.
+A lexicon $L$ consists of a set of topics $t$ such that each topic is associated with a set of cell words $c$, in which each cell word depicts an aspect of the topic.
 \end{definition}
@@
 %used \label{def:blog} previously
-With a given user $u$, each microblog $b \in B_u$ could be decomposed into a set of words $w$.
+For a user $u$, each microblog $b \in B_u$ is represented by a set of words $w$.
 \end{definition}
@@
 \label{def:inte}
-The interest feature of a given user is a normalized vector
+The interest feature $P_u$ of a user $u$ is a normalized vector
 \begin{equation}
 \label{eq:inte}
-P_f\ = (p_0,\ p_1,\ ...,\ p_{x-1})
+(p_0, p_1, \ldots, p_{x-1})
 \end{equation}
-in which the said user matches $x$ \textit{topics} in lexicon and $p_i$ refers to the similarity of the user and each matched topic (interest).
-The definition of such similarity shall be detailed in each scenario (explicit/implicit interest analysis, towards words/topics, etc).
+in which user $u$ matches $x$ \textit{topics} in lexicon $L$, and $p_i$ refers to the degree that $u$ is interested in topic $i$.
 \end{definition}
 
-Next, we shall present the ``mining'' process for interest features.
-In short, \sys{} employs a well established lexicon to discover the explicit interests of users.
-In case no proper explicit interests are found, TF-IDF(term-frequency and inverse document-frequency) and Twitter-LDA \cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector participates to provide the similarity between two words.
+The similarity $p_i$¡¡$(i\in[0, x-1])$ will be detailed in each scenario (explicit/implicit interest analysis, towards words/topics, etc).
 
-In \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
-Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, t)$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.
+In system \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
+Hence, the similarity $sim(w, c)$ of a word pair ($w$, $c$) could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user $u$ versus each topic $t$ in lexicon $sim(u, t)$; topics with similarity satisfying certain thresholds are allocated to user $u$ and constitute the interests of $u$.
 
-For instance, the following steps depict the ``mining'' process of the interest feature $P_f$ for a user $u$.
+System \sys{} employs a well established lexicon to discover the explicit interests of users.
+In case when no proper explicit interests are found, TF-IDF (Term-Frequency and Inverse Document-Frequency) and Twitter-LDA \cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector \cite{IEEEexample:mikolov2013distributed} is adopted to measure the similarity between two words.
+We now present the detailed process for mining the interest features of a user $u$.
 
-\stitle{Step 1:} Each microblog of $u$ is decomposed into a word set. %, i.e., $b = \{w\}$ where $b \in B_s(u)$.
+%For instance, the following steps depict the ``mining'' process of the interest feature $P_f$ for a user $u$.
 
-\stitle{Step 2:} Explicit interests are explored. Specifically, every word $w$ is sent to match each cell word $c$ of lexicon topics.
-If $w$ and $c$ are identical, $sim(w, c) = 1$.
-Otherwise, $sim(w, c) = 0$.
-As to the similarity of $b$ against a lexicon topic $t$, it is:
+\stitle{Step 1:} Each microblog $b$ in $B_u$ of user $u$ is decomposed into a word set $WS$. %, i.e., $b = \{w\}$ where $b \in B_s(u)$.
+
+\stitle{Step 2:} Explicit interests are explored. Specifically, every word $w$ in $WS$ is sent to match each cell word $c$ of lexicon topics.
+If $w$ and $c$ are identical, $sim(w, c) = 1$, and $sim(w, c) = 0$, otherwise.
+The similarity of $b$ with a lexicon topic $t$ is defined as
 \begin{equation}
 \label{eq:bt}
-sim(b, t) = \sum_{\substack{i, j}} sim(w_i, c_j)
+sim(b, t) = \sum_{\substack{i, j}} sim(w_i, c_j).
 \end{equation}
-where $sim(w_i, c_j)$ refers to the similarity of a word pair.
 
-If $sim(b, t)$ satisfies a certain threshold (3 by default) , topic $t$ is labeled to microblog $b$;
+%where $sim(w_i, c_j)$ refers to the similarity of a word pair.
+
+If $sim(b, t)$ satisfies a certain threshold (3 by default), topic $t$ is labeled to microblog $b$;
 the user $u$ is then discovered having an explicit interest (topic) $t$.
-Thus, by looking into the similarity of $b$ against all topics in lexicon, the explicit interests of $u$ is returned, in the form of interest feature (see Definition \ref{def:inte}).
+Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).
 
-If none of $sim(b, t)$ could meet the threshold, i.e., explicit interest discovery over user $u$ fails, go to \textbf{Step 3} and \textbf{Step 4} in parallel, so as to ``mine'' the implicit interests of $u$.
+\stitle{Step 3:}.
+If the $sim(b, t)$ in {\bf Step 2} cannot meet the threshold, i.e., explicit interest discovery over user $u$ fails, the implicit interests of user $u$ are further mined, by running the following steps 3.1$\&$3.2 in parallel.
 
-\stitle{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF to calculate the weight distribution of words in microblog $b$:
+\etitle{Step 3.1:} A metric \textit{TF-IDF weight} $W_f$ is computed by employing TF-IDF to calculate the weight distribution of words in microblog $b$:
 \begin{equation}
 \label{eq:tf}
-W_f = \{(w_i, p_i)\}
+W_f = \{(w_i, p_i)\},
 \end{equation}
@@
 \label{eq:tf-w}
-p''_i = \frac{|b_i|}{|b|} * log(\frac{|D_i|}{|D|})
+p''_i = \frac{|b_i|}{|b|} * \log(\frac{|D_i|}{|D|}),
 \end{equation}
-in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$ and $|b|$ the total occurrences of all words in $b$.
+in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$, and $|b|$ the total occurrences of all words in $b$.
 Ditto for $|D_i|$ and $|D|$, except that the scope is the overall dataset, rather than a single microblog $b$.
 
-Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight} (see Definition \ref{eq:tf}).
-Go to \textbf{Step 5}.
+Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.
 
-\stitle{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing}
+TF-IDF based similarity is then calculated.
+For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
+\begin{equation}
+\label{eq:sim-tf1}
+sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t),
+\end{equation}
+where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
+
+\etitle{Step 3.2:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained by using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing}
 to result the word weight distribution of microblog $b$.
@@
 \label{eq:tw-tag}
-W_t = \{(w'_i, p'_i)\}
+W_t = \{(w'_i, p'_i)\},
 \end{equation}
@@
 Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
-Go to \textbf{Step 6}.
 
-\stitle{Step 5:} TF-IDF based similarity is calculated.
-For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
-\begin{equation}
-\label{eq:sim-tf1}
-sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
-\end{equation}
-where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
-Go to \textbf{Step 7}.
-
-\begin{comment}
-:
-\begin{equation}
-\label{eq:sim-tf2}
-sim(w_i, t) = \sum_{\substack{j}} sim(w_i, c_j)
-\end{equation}
-\end{comment}
-
-\stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
-Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
-\begin{equation}
-\label{eq:sim-tw1}
-sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
-\end{equation}
-%where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$,
-where $W_w$ is a set of $(w'_i, p'_i)$, $t$ covers each $c_j$,
-and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
-Go to \textbf{Step 7}.
-
-\begin{comment}
-:
-\begin{equation}
-\label{eq:sim-tw2}
-sim(w'_i, t) = \sum_{\substack{j}} sim(w'_i, c_j)
-\end{equation}
-\end{comment}
-
-\stitle{Step 7:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is given by:
+\stitle{Step 4:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is given by:
 \begin{equation}
 \label{eq:simbt}
-sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t)
+sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t),
 \end{equation}
 where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.
-Go to \textbf{Step 8}.
 
-\stitle{Step 8:} Repeat the above steps (Step 1 to Step 7) for the microblog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
+\stitle{Step 5:} Repeat Steps 1 to 4 for the microblog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
 Such computation further extends to all the microblogs owned by user $u$, such that:
@@
 \label{eq:simul}
-S(u, L) = (s_0,\ s_1,\ ...,\ s_{n-1})
+S(u, L) = (s_0, s_1, \ldots,\ s_{n-1}),
 \end{equation}
@@
 
-Among the $n$ dimensions of $S(u,\ L)$, those with top $x$ (3 in \sys{}) similarity values are selected to label the implicit interests of user $u$, which results an $x$ dimensional vector $P_f$ as described in Definition \ref{def:inte}.
+Among the $n$ dimensions of $S(u,\ L)$, those with top $x$ (3 in \sys{}) similarity values are selected to label the implicit interests of user $u$, which results an $x$ dimensional vector $P_u$ as described in Definition \ref{def:inte}.
 Similarly, interest features of all users are returned.
 
-As a result, the \textit{Feature Data} for every user $u$, written as $F(u)$, is given by:
+As a result, the \textit{Feature Data} $F_u$ for a user $u$ is
 \begin{equation}
 \label{eq:fu}
-	F(u) = (I,\ H,\ P_f)
+	F_u = (I_u, H_u, P_u),
 \end{equation}
-where $I$, $H$ and $P_f$ refer to \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature} separately (see formulas \ref{eq:info}, \ref{eq:beha} and \ref{def:inte}).
-And it could be written as a vector:
-\begin{equation}
-\label{eq:fu-flat}
-\begin{aligned}
-	F(u) = (G_u, P_u, \#R_s, \#E_s, R_{ee}, U_t, \#B_u, R_{oc},\\
-    \#W_r, P_{rt}, P_{rg}, \#W_t, P_{tt}, P_{tg}, P_f)
+where $I_u$, $H_u$ and $P_u$ are the \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature} of $u$, respectively.
+
+%And it could be written as a vector
+%\begin{equation}
+%\label{eq:fu-flat}
+%\begin{aligned}
+%	F(u) = (G_u, P_u, \#R_s, \#E_s, R_{ee}, U_t, \#B_u, R_{oc},\\
+%    \#W_r, P_{rt}, P_{rg}, \#W_t, P_{tt}, P_{tg}, P_f),
 %(\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)
-\end{aligned}
-\end{equation}
-where each dimension refers to a data item of \sys{}.
+%\end{aligned}
+%\end{equation}
+%where each entry refers to a data item of \sys{}.

### 2017-10-13 Gruba/04-uc.tex

@@
 
-Providing the \textit{Feature Data}, User Clustering takes the charge of grouping each user concerned into a proper cluster.
-Algorithm \ref{alg:uc} illustrates such overall procedure.
+Providing the \textit{Feature Data}, the User Clustering module takes the charge of grouping each user concerned into a proper cluster,
+as illustrated in  Algorithm \ref{alg:uc}.
 %
@@
 \label{alg:uc}
-
 \begin{algorithmic}[1]
-\State Input: \textit{Feature Data} of users $\{F(u)\}$, the minimum/maximum number of clusters $N_i$ and $N_a$
+\State Input: \textit{Feature Data} $F$  of a set of users, the minimum/maximum number of clusters $N_i$ and $N_a$
 \State Output: Optimal user clustering result $R$
-\\
+\vspace{1ex}
 \ForAll {$t \in [N_i, N_a]$} \label{enu}
-	\State group users $\{u\}$ into $t$ clusters by $\{F(u)\}$ \label{task}
-	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$ \label{l}
+	\State group users into $t$ clusters by $F$; \label{task}
+	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
 	\ForAll {$u \in \{u\}$}
-		\State in-cluster distance $d_i(u)$ \label{v-b}
-		\State out-cluster distance $d_o(u)$
-		\State Silhouette coefficient value $v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$ \label{v-e}
+		\State in-cluster distance $d_i(u)$ \label{v-b};
+		\State out-cluster distance $d_o(u)$;
+		\State Silhouette coefficient value $v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
 	\EndFor
-	\State $v(t)\ =\ Avg\{v(u)\}$ \label{avg}
+	\State $v(t)\ :=\ Avg\{v(u)\}$; \label{avg}
 \EndFor
-\If {$v(a)\ ==\ \ Max\{v(t)\}$} \label{opti}
-	\State $R$ = $R'(a)$
+\If {$v(a)\ =\ \ Max\{v(t)\}$}; \label{opti}
+	\State $R$ := $R'(a)$;
 \EndIf
-\State \bfseries{return} $R$
+\State \bfseries{return} $R$.
 \end{algorithmic}

### 2017-10-13 Gruba/03-fe.tex

@@
 TF-IDF based similarity is then calculated.
-For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
+%For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined %as:
+%\begin{equation}
+%\label{eq:sim-tf1}
+%sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t),
+%\end{equation}
+%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.
+For example, the similarity of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as formula \ref{eq:sim-tf1}.
+Here $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, $VEC_{W_f}$ is defined as formula \ref{eq:sum-tf1}, $VEC_t$ is defined as formula \ref{eq:sum-lexion},
+where $N_t$ is the number of words in topic $t$ and $vec[w]$ is the word vector of word $w$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
 \begin{equation}
 \label{eq:sim-tf1}
-sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t),
+sim(W_f, t) = VEC_{W_f} \cdot VEC_t
 \end{equation}
-where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
+\begin{equation}
+\label{eq:sum-tf1}
+VEC_{W_f} = \sum_{\substack{i}} p_i*vec[w_i]
+\end{equation}
+\begin{equation}
+\label{eq:sum-lexion}
+VEC_t = \sum_{\substack{j}} \frac{1}{N_t}*vec[c_j]
+\end{equation}
+%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.
 

### 2017-10-13 Gruba/04-uc.tex

@@
 		\State out-cluster distance $d_o(u)$;
-		\State Silhouette coefficient value $v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
+		\State Silhouette coefficient value $v(u)\ :=\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
 	\EndFor
@@
 %
-Recall the sample data for User Clustering, i.e., \textit{Feature Data} in form of vectors (see formula \ref{eq:fu-flat}), of which the data type regarding each dimension is shown as Table \ref{tbl:data-type}.
+Recall the sample data for User Clustering, i.e., \textit{Feature Data} in form of vectors (see formula \ref{eq:fu}), of which the data type regarding each dimension is shown as Table \ref{tbl:data-type}.
 
@@
 \caption{Dimension Types in \textit{Feature Data} Vector}
-\vspace{0.3cm}
+%\vspace{0.3cm}
 \label{tbl:data-type}
@@
 \toprule
-\multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
+\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
 numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$,\\
                             &  $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$				\\	\midrule
-categorical data			& $G_u$,$P_u$,$U_{t,u}$				\\	\midrule
-normalized vectors			& $P_{rt,u}$, $P_{rg,u}$,$P_{tt,u}$,$P_{tg,u}$,$P_{f,u}$			\\ \bottomrule
+categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
+normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_{f,u}$			\\ \bottomrule
 \end{tabular}
@@
 
-As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers(normalized to 0-1 range), categories and normalized vectors.
-For simplicity, we shall first illustrate the distance calculation of the simple vectors with mono data type on each dimension and then demonstrate that of complex vectors in K-Gru.
+As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers (normalized to 0-1 range), categories and normalized vectors.
+For simplicity, we shall first illustrate the distance calculation of the simple vectors with a mono data type on each dimension, and then demonstrate that of complex vectors.
 
-Given two numerical vectors $Y'\ = (y'_0, y'_1, ...)$ and $Z'\ = (z'_0, z'_1, ...)$, the \od{} \cite{IEEEexample:books/mk/HanKP2011} between $Y'$ and $Z'$ is given by :
+For numerical vectors $Y'\ = (y'_0, y'_1, \ldots)$ and $Z'\ = (z'_0, z'_1, \ldots)$, the \od{} \cite{IEEEexample:books/mk/HanKP2011} between $Y'$ and $Z'$ is given by :
 %
@@
 
-As to the categorical vectors $Y''\ = (y''_0, y''_1, ...)$ and  $Z''\ = (z''_0, z''_1, ...)$, the \hd{} \cite{IEEEexample:huang1997clustering} of $Y''$ and $Z''$ is:
+For categorical vectors $Y''\ = (y''_0, y''_1, \ldots)$ and  $Z''\ = (z''_0, z''_1, \ldots)$, the \hd{} \cite{IEEEexample:huang1997clustering} of $Y''$ and $Z''$ is:
 %
@@
 \label{eq:hd}
-D_h(Y'', Z'') = \sum_{\substack{e}} H_e
+D_h(Y'', Z'') = \sum_{\substack{e}} H_e,
 \end{equation}
-where $H_e$ refers to the \hd{} over each dimension, with $H_e\ =\ 1$ if $y''_e$ and $z''_e$ share the identical value, and $H_e\ =\ 0$ otherwise.
+where $H_e$ refers to the \hd{} over each dimension, with $H_e = 1$ if $y''_e$ and $z''_e$ share the identical value, and $H_e = 0$, otherwise.
 
@@
 
-Hence, the said distance regarding the complex vectors ($Y\ =\ (Y_0, Y_1, ...)$ and $Z\ =\ (Z_0, Z_1, ...)$ ) in K-Gru, named \gd{}, could be deduced as:
+Putting these together, the distance regarding the complex vectors $Y\ =\ (Y_0, Y_1, ...)$ and $Z\ =\ (Z_0, Z_1, ...)$ in K-Gru, referred to as \gd{}, is defined as:
 %
@@
   \begin{cases}
-    (Y_e - Z_e)^2       & \quad \text{if } Y_e/Z_e \text{ is numerical}\\
-    H_e\ (1\ or\ 0)       	& \quad \text{if } Y_e/Z_e \text{ is categorical}\\
-    1 - Y_e \cdot Z_e  		& \quad \text{if } Y_e/Z_e \text{ is of normalized vector}
+    (Y_e - Z_e)^2       &  \text{if } Y_e/Z_e \text{ is numerical}\\
+    H_e\ (1\ or\ 0)       	&  \text{if } Y_e/Z_e \text{ is categorical}\\
+    1 - Y_e \cdot Z_e  		&  \text{if } Y_e/Z_e \text{ is of normalized vector}
   \end{cases}
@@
 
-In \sys{}, Silhouette coefficient value serves as the fundamental criteria for the optimal clustering selection.
+In system \sys{}, the Silhouette coefficient metric serves as the fundamental criteria for deriving an optimal clustering result.
 Providing a clustering result, each user is associated with a cluster.
 
-For a given user $u$ of cluster $l$, we employ the vector $Y$ to denote the \textit{Feature Data} as in formula \ref{eq:fu-flat}.
+%For a user $u$ of cluster $l$, we employ the vector $Y$ to denote the \textit{Feature Data} as in formula \ref{eq:fu}.
 
@@
 \label{def:di}
-The in-cluster distance $d_i(u)$ is the average distance to all the other users in the same cluster, i.e., $\forall u'' \in l$ \& $u \neq u''$:
+The in-cluster distance $d_i(u)$ is the average distance to all the other users in the same cluster:
 \begin{equation}
-	d_i(u) = Avg\{D_g(Y_u, Y_u'')\}
+	d_i(u) = Avg\{D_g(F_u, F_u'')\ |\ u'' \in l \wedge  u \neq u''\}.
 \end{equation}
@@
 \label{def:do}
-The out-cluster distance $d_o(u)$ is measured as the minimum of the distances $\{d^{\ast}\}$ between $u$ and other clusters ($\forall l' \neq l$), i.e.:
+The out-cluster distance $d_o(u)$ is measured as the minimum of the distances $\{d^{\ast}\}$ between $u$ and other clusters:
 \begin{equation}
-	d_o(u) = Min\{d^{\ast}(u, l')\}
+	d_o(u) = Min\{d^{\ast}(u, l')\ |\  l' \neq l \},
 \end{equation}
@@
 \begin{equation}
-	d^{\ast}(u, l') = Avg\{D_g(Y_u, Y_u')\}\ \forall u' \in l'
+	d^{\ast}(u, l') = Avg\{D_g(Y_u, Y_u') \ | \ u' \in l'\}.
 \end{equation}
@@
 \label{def:coef}
-The Silhouette coefficient value $v(u)$ is thus concluded:
+The Silhouette coefficient value $v(u)$ is defined as:
 \begin{equation}
 \label{eq:coef}
-v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}	
+v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}.	
 \end{equation}
@@
 
-Intuitively, a good clustering solution should result bigger $d_o$ and smaller $d_i$, such that samples with obvious differences go to various clusters and vice versa.
+Intuitively, a good clustering solution should have a bigger $d_o$ and a smaller $d_i$, such that samples with obvious differences go to various clusters and vice versa.
 When $d_o$ is far more than $d_i$, Silhouette coefficient value approaches to 1.

### 2017-10-13 Gruba/05-gm.tex

@@
 Recall the central problem of \sys{}, where the \retg{} behaviors of users are modeled.
-Specifically, such model is built by Group Modeling for each user group and thus named as group model.
+Specifically, such model is built by the Group Modeling module for each user group and thus named as group model.
 To avoid ambiguity, we shall use the term of \textit{items} to denote the data for training the group model.
@@
 
-And the data of item $E$ could be further divided into three parts.
+And the data of item $E$ consists of three parts.
 %\begin{itemize}
@@
 The number that $b$ has been retweeted, commented, liked and the length of $b.M$ (microblog message) are considered.
-What's more, we consider the correlation between $b$ and recent event, where the latter is expressed as several core words returned by Ring \cite{IEEEexample:ring}.
+What is more, we consider the correlation between $b$ and recent event, where the latter is expressed as several core words returned by Ring \cite{IEEEexample:ring}.
 Here we compute \textit{TF-IDF weight} $W_f$ of $b.M$, and get correlation metric $C_h$ of $b$ and event by formula \ref{eq:sim-tf1}.
@@
 %\end{itemize}
-	\stab(3) \stitle{Interaction Info} includes seven correlation metrics: \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a.
+	\stab(3) \stitle{Interaction Info} includes seven correlation metrics: \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_u$ (a.k.a.
 long-term/stable interest in this work), and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
@@
 
-In this paper, we view modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem.
-The advantage of classification model lies in that it could integrate different features conveniently.
+The modeling of retweeting behavior of groups is treated as a classification problem, and utilize the random forest classifier to attack it.
+The advantage of this classification model lies in that it could integrate different features conveniently, and
 %The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
-As a result, the obtained group behavior model could learn what does a positive/negative item look like over each metric mentioned above.\par
+the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above.

### 2017-10-13 Gruba/08-conclu.tex
v4.3
v4.3

--- 2017-09-30 Gruba/08-conclu.tex
@@
-\section{\textcolor{red}{Conclusions}}
+\section{Conclusions}
 \label{sec:conclu}
+
+In this work, we have presented \sys{}, a system to model the \retg{} behavior of users in social media.
+\sys{} departures from existing work by grouping users into clusters, during which features of basics, behavior and interests are extracted.
+Specially, we have studied interest features from various perspectives, such as long-term/recent interests and explicit/implicit interests.
+Finally, we have provided a performance evaluation of \sys{} by using real-world datasets to demonstrate the benefits of our system \sys{}.

### 2017-10-13 Gruba/06-perf.tex

@@
 Considering the huge amount of users, we carefully selected one typical user for analysis.
-Here we chose Mary(a famous drama and movie actor in China) as a representative.
-The features extraction result for Mary is displayed in Fig.\ \ref{fig:userFeatures}.
-Then we can see the basic information of Mary from the result. Her nickname is Actor Mary(演员马丽) and she is from Beijing(北京).
-The number of followers of Mary is much more than the number of her friends.
-The Sina Microblog tag she made for herself is "actor"(演员).
-As the result of the long-term interest extraction shows, she is interested in stage performances(舞台表演), drama performances(话剧表演),films(电影光影) and so on, which is consistent with her actual situation.
-What's more, the probability distribution of tweeting and retweeting behavior on different time periods in one day indicates that her activities at night is much more than daytime.
-The time interval distribution of her behaviors is also shown in Fig.\ \ref{fig:userFeatures}. The time interval is mostly distributed within 48 hours, which indicates that she is a active user.
-We developed a function for querying user's short-term interest.
-Here we queried Mary's short-term interest between 09/01/2016 and 09/30/2016, and got it as shown in Fig.\ \ref{fig:userFeatures}.
-We analyzed her microblogs in the this period, she has been working tirelessly to promote the drama "Earl of Oolong Mountain"(乌龙山伯爵).
-So the results are in line with expectations.
+Here we chose Mary(a famous drama and movie actress in China) as an example.
+The feature extraction result for Mary is depicted in Fig.\ \ref{fig:userFeatures}.
+Then we can see the basic information of Mary in Sub-Fig.\ \ref{fig:userFeatures:uf-1}: her nickname is Actress Mary (演员马丽) and she is from Beijing (北京).
+Mary has more followers than followees.
+The Sina Microblog tag she made for herself is ``actress'' (演员).
+As to the long-term interest, she is interested with stage performance (舞台表演), drama (话剧表演),film (电影光影) and so on as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-2}, which is consistent with her tag.
+The probability distribution of tweeting and retweeting indicates that she is more active at night than daytime as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-3} and \ref{fig:userFeatures:uf-4}.
+According to Sub-Fig.\ \ref{fig:userFeatures:uf-5} and \ref{fig:userFeatures:uf-6}, the interval between her two tweeted/retweeted microblogs is mostly within 48 hours, showing she is an active user.
+Mary's short-term interest, e.g.
+from 09/01/2016 to 09/30/2016, is shown in Sub-Fig.\ \ref{fig:userFeatures:uf-7}, which indicates she had been busy with promoting the drama ``Earl of Oolong Mountain'' (乌龙山伯爵).
+So the results are in line with expectations, as drama (话剧) and stage (舞台) in Sub-Fig.\ \ref{fig:userFeatures:uf-7}.
 
-\begin{figure}
+\begin{figure*}
   \centering
   \subfigure{
-      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/1.eps}}
+      \label{fig:userFeatures:uf-1}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
   \subfigure{
-      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/2.eps}}
+      \label{fig:userFeatures:uf-2}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
   \subfigure{
-      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/3.eps}}
+      \label{fig:userFeatures:uf-3}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
   \subfigure{
-      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/4.eps}}
+      \label{fig:userFeatures:uf-4}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
   \subfigure{
-      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/5.eps}}
+      \label{fig:userFeatures:uf-5}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
   \subfigure{
-      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/6.eps}}
+      \label{fig:userFeatures:uf-6}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
   \subfigure{
-  \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/7.eps}}
+      \label{fig:userFeatures:uf-7}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
   \subfigure{
-  \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/8.eps}}
+      \label{fig:userFeatures:uf-8}
+      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
   \caption{Visualization for User Features.}
   \label{fig:userFeatures} %% label for entire figure
-\end{figure}
+\end{figure*}

### 2017-10-13 Gruba/10-appendix.tex

--- 2017-10-06 Gruba/10-appendix.tex
@@
 \newpage
-\section{Appendix}
+\section{Appendix: Extra Experiments}
 \label{sec:appendix}
+
+%\subsection{Case Study for Feature Extraction}
+
+\subsection{Case Study for User Clustering}
+
+In this section, we show the results of our demo system for User Clustering. We carefully analyzed the statistical information of four groups obtained from user clustering.
+
+\stab(1) Most users of group one are male (as shown in Sub-Fig.
+\ref{fig:subfig1:fig11}), and Sub-Fig.
+\ref{fig:subfig1:fig12} shows that they are mainly in Beijing(北京).
+Most of them have number of followees similar as followers (as shown in Sub-Fig.
+\ref{fig:subfig1:fig14}).
+The most active time of this group is mainly between 10 am and 12 am (as shown in Sub-Fig.
+\ref{fig:subfig1:fig15} and \ref{fig:subfig1:fig16}).
+
+\stab(2) The users of group two are mostly female (as shown in Sub-Fig.
+\ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Sub-Fig.
+\ref{fig:subfig2:fig22}).
+Similar as group one, most of them have number of followees close to followers (as shown in Sub-Fig.
+\ref{fig:subfig2:fig24}).
+The most active time of this group is mainly between 10 pm and 12 pm (as shown in Sub-Fig.
+\ref{fig:subfig2:fig25} and \ref{fig:subfig2:fig26}).
+
+\stab(3) Most users of group three are male (as shown in Sub-Fig.
+\ref{fig:subfig3:fig31}).
+They come from a wide range of provinces (as shown in Sub-Fig.
+\ref{fig:subfig3:fig32}).
+Most of them have number of followers far more than followees (as shown in Sub-Fig.
+\ref{fig:subfig3:fig34}).
+The most active time of this group is mainly in 10-12 am and 10-12 pm (as shown in Sub-Fig.
+\ref{fig:subfig3:fig35} and \ref{fig:subfig3:fig36}).
+
+\stab(4) Most users of group four are female (as shown in Sub-Fig.
+\ref{fig:subfig4:fig41}), and they come from a wide range of provinces just as group three (as shown in Sub-Fig.
+\ref{fig:subfig4:fig42}).
+Most of these users have number of followers far more than followees (as shown in Sub-Fig.
+\ref{fig:subfig4:fig44}).
+And the most active time of these users is mainly between 10 pm and 12 pm (as shown in Sub-Fig.
+\ref{fig:subfig4:fig45} and \ref{fig:subfig4:fig46}).
+
+According to Sub-Fig. \ref{fig:subfig1:fig13}, \ref{fig:subfig2:fig23}, \ref{fig:subfig3:fig33} and \ref{fig:subfig4:fig43}, 
+the number distribution of microblogs for four groups is similar with each other.
+We visualized each group's long-term interest expressed as words cloud (shown in Sub-Fig.
+\ref{fig:subfig1:fig19}, \ref{fig:subfig2:fig29}, \ref{fig:subfig3:fig39} and \ref{fig:subfig4:fig49}), as we can see, group one and group three have similar interest.
+
+\begin{figure*}
+  \centering
+  \subfigure{
+  \label{fig:subfig1:fig11}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/11.eps}}
+  \subfigure{
+  \label{fig:subfig1:fig12}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/12.eps}}
+  \subfigure{
+  \label{fig:subfig1:fig13}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/13.eps}}
+  \subfigure{
+  \label{fig:subfig1:fig14}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/14.eps}}
+  \subfigure{
+  \label{fig:subfig1:fig15}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/15.eps}}
+  \subfigure{
+  \label{fig:subfig1:fig16}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/16.eps}}
+  \subfigure{
+  \label{fig:subfig1:fig17}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/17.eps}}
+  \subfigure{
+  \label{fig:subfig1:fig18}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/18.eps}}
+  \subfigure{
+  \label{fig:subfig1:fig19}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/19.eps}}
+  \caption{The Statistics of User Group One}
+  \label{fig:subfig1} %% label for entire figure
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \subfigure{
+  \label{fig:subfig2:fig21}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/21.eps}}
+  \subfigure{
+  \label{fig:subfig2:fig22}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/22.eps}}
+  \subfigure{
+  \label{fig:subfig2:fig23}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/23.eps}}
+  \subfigure{
+  \label{fig:subfig2:fig24}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/24.eps}}
+  \subfigure{
+  \label{fig:subfig2:fig25}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/25.eps}}
+  \subfigure{
+  \label{fig:subfig2:fig26}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/26.eps}}
+  \subfigure{
+  \label{fig:subfig2:fig27}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/27.eps}}
+  \subfigure{
+  \label{fig:subfig2:fig28}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/28.eps}}
+  \subfigure{
+  \label{fig:subfig2:fig29}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/29.eps}}
+  \caption{The Statistics of User Group Two}
+  \label{fig:subfig2} %% label for entire figure
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \subfigure{
+  \label{fig:subfig3:fig31}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/31.eps}}
+  \subfigure{
+  \label{fig:subfig3:fig32}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/32.eps}}
+  \subfigure{
+  \label{fig:subfig3:fig33}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/33.eps}}
+  \subfigure{
+  \label{fig:subfig3:fig34}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/34.eps}}
+  \subfigure{
+  \label{fig:subfig3:fig35}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/35.eps}}
+  \subfigure{
+  \label{fig:subfig3:fig36}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/36.eps}}
+  \subfigure{
+  \label{fig:subfig3:fig37}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/37.eps}}
+  \subfigure{
+  \label{fig:subfig3:fig38}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/38.eps}}
+  \subfigure{
+  \label{fig:subfig3:fig39}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/39.eps}}
+  \caption{The Statistics of User Group Three}
+  \label{fig:subfig3} %% label for entire figure
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \subfigure{
+  \label{fig:subfig4:fig41}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/41.eps}}
+  \subfigure{
+  \label{fig:subfig4:fig42}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/42.eps}}
+  \subfigure{
+  \label{fig:subfig4:fig43}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/43.eps}}
+  \subfigure{
+  \label{fig:subfig4:fig44}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/44.eps}}
+  \subfigure{
+  \label{fig:subfig4:fig45}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/45.eps}}
+  \subfigure{
+  \label{fig:subfig4:fig46}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/46.eps}}
+  \subfigure{
+  \label{fig:subfig4:fig47}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/47.eps}}
+  \subfigure{
+  \label{fig:subfig4:fig48}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/48.eps}}
+  \subfigure{
+  \label{fig:subfig4:fig49}
+      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/49.eps}}
+  \caption{The Statistics of User Group Four}
+  \label{fig:subfig4} %% label for entire figure
+\end{figure*}

### 2017-10-14 Gruba/06-perf.tex

@@
 
-In this section, we shall first detail the experimental setting of machine info, dataset and parameters; and then present the result and analysis, showing the benefit of \sys{} against state of the art approaches.
+In this section, we shall first detail the experimental setting, and we then present the evaluation result and analysis, showing the benefit of \sys{} against state of the art approaches.
 
@@
 %
-We have employed a real-world dataset Sina that consists of 24 million microblogs that are associated with 43.5K users.
+We have employed a real-world dataset Sina Weibo that consists of 24 million microblogs that are associated with 43.5K users.
 
 With respect to the parameters of \sys{}, we use the default values as mentioned in previous sections.
-Particularly, in Feature Extraction, for practical reason, we employed a smaller testing dataset to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature};
-in User Cluster, we studied the clustering solutions with the minimum/maximum number of clusters 2 and 10;
-in Behavior Modeling, a user's recent 30 days microblogs are used for short-term interest analysis and popular words of the latest 24 hours are returned by Ring as the Hot Event keywords.
+Particularly, for the Feature Extraction module, for practical reasons, we employed a smaller testing dataset to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature};
+For the User Cluster module, we studied the clustering solutions with the minimum/maximum number of clusters 2 and 10;
+For the Behavior Modeling module, the recent 30 days microblogs of users are used for their short-term interest analysis, 
+and popular words in the latest 24 hours are returned by Ring as the Hot Event keywords \cite{IEEEexample:ring}.
 
 \subsection{Result and Analysis}
-Next, we shall report the performance of \sys{} over each component.
+Next, we shall report the performance of system \sys{} over each component.
 
-\stitle{Feature Extraction}
+\stitle{Exp-1: Feature Extraction}
 %
 Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
-Apparently, \sys{} results the optimal results when $\alpha$ is 0.7, upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million microblogs.
+System \sys{} reaches the optimal results when $\alpha$ is 0.7,
+upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million microblogs.
+In general, it performs well when $\alpha$ falls into $[0, 0.8]$.
 
-\begin{figure}[!htb]
+\stitle{Exp-2: User Clustering}
+%
+Fig.\ \ref{fig:uc} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
+Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
+Except for \textit{Data1}, solutions for \textit{\{Data2,\ldots, Data5\}} are the best for 4 clusters.
+
+\begin{figure}[tb!]
 \centering
@@
 \label{fig:fe}
+\vspace{-1ex}
 \end{figure}
 
-\stitle{User Clustering}
-%
-Fig.\ \ref{fig:uc} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number from 2 to 10.
-Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users and \textit{Data1,...,5} contains 10K randomly selected users each.
-Except for \textit{Data1}, solutions with 4 clusters sweep.
-
-\begin{figure}[!htb]
+\begin{figure}[tb!]
 \centering
@@
 \label{fig:uc}
+\vspace{-2ex}
 \end{figure}
 
-\stitle{Behavior Modeling}
-%
-Fig.\ \ref{fig:10} shows the performance of \sys{} against state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
-We compare the metrics of precision, recall, as well as $F_1$ score.
-LRC-BQ does not deal with user grouping.
-Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering), but also examine \sys{} versus LRC-BQ in the case that all users are in mono group (i.e., ``All-Users'').
-The results are interesting in that:
-%\begin{itemize}
-
-	\stab(1) With user clustering, \sys{} performs better than LRC-BQ in most cases.
-
-	\stab(2) For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ.
-%\end{itemize}
-
-\begin{figure*}
+\begin{figure*}[tb!]
   \centering
@@
 \end{figure*}
+
+\stitle{Exp-3: Behavior Modeling}
+%
+Fig.\ \ref{fig:10} shows the performance of \sys{} against the state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
+We evaluate the performance using the metrics of precision, recall, and $F_1$ score.
+LRC-BQ does not deal with user grouping.
+Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering), 
+but also examine \sys{} versus LRC-BQ in the case that all users are in a single group (i.e., ``All-Users'').
+The results show that:
+%\begin{itemize}
+
+	\stab(1) With user clustering, \sys{} performs better than LRC-BQ in most cases.
+
+	\stab(2) For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ.
+%\end{itemize}
 
@@
   \label{fig:11}
+  \vspace{-1ex}
 \end{figure*}
 
-\stitle{Case Study for Feature Extraction}
+\stitle{Exp-4: Case Study for Feature Extraction}
 In this section, we show the results of our demo system for user features extraction.

### 2017-10-14 Gruba/06-perf.tex

@@
 \stitle{Exp-4: Case Study for Feature Extraction}
-In this section, we show the results of our demo system for user features extraction.
+In this test, we show the results of our demo system for user features extraction.
+%
 Considering the huge amount of users, we carefully selected one typical user for analysis.
-Here we chose Mary(a famous drama and movie actress in China) as an example.
+Here we chose Mary (a famous drama and movie actress in China) as an example.
+
 The feature extraction result for Mary is depicted in Fig.\ \ref{fig:userFeatures}.

### 2017-10-14 Gruba/07-rela.tex
v4.3
v4.3

@@
 
-In this section, we shall review related work in literature mainly from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
-As aforementioned, \sys{} leverages the user features of basic info, behavior and interest.
+In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
+As aforementioned, \sys{} leverages the user features of basics, behavior and interest.
 

### 2017-10-14 Gruba/10-appendix.tex

@@
 
-In this section, we show the results of our demo system for User Clustering. We carefully analyzed the statistical information of four groups obtained from user clustering.
+In this section, we show the results of our system \sys{} for User Clustering. We carefully analyzed the statistical information of four groups obtained from user clustering.
 
@@
 \ref{fig:subfig2:fig22}).
-Similar as group one, most of them have number of followees close to followers (as shown in Sub-Fig.
+Similar as group one, most of them have followees close to followers (as shown in Sub-Fig.
 \ref{fig:subfig2:fig24}).

### 2017-10-14 Gruba/10-appendix.tex

@@
 \ref{fig:subfig1:fig12} shows that they are mainly in Beijing(北京).
-Most of them have number of followees similar as followers (as shown in Sub-Fig.
+The amount of their followees is mostly similar as their followers (as shown in Sub-Fig.
 \ref{fig:subfig1:fig14}).
@@
 
-\stab(2) The users of group two are mostly female (as shown in Sub-Fig.
+\stab(2) Mostly users of group two are  female (as shown in Sub-Fig.
 \ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Sub-Fig.
 \ref{fig:subfig2:fig22}).
-Similar as group one, most of them have followees close to followers (as shown in Sub-Fig.
+Similar to group one, most of them have followees close to followers (as shown in Sub-Fig.
 \ref{fig:subfig2:fig24}).
@@
 \ref{fig:subfig4:fig42}).
-Most of these users have number of followers far more than followees (as shown in Sub-Fig.
+Most of these users have the amount  of followers far more than followees (as shown in Sub-Fig.
 \ref{fig:subfig4:fig44}).
@@
 
-According to Sub-Fig. \ref{fig:subfig1:fig13}, \ref{fig:subfig2:fig23}, \ref{fig:subfig3:fig33} and \ref{fig:subfig4:fig43},
+According to Sub-Figs. \ref{fig:subfig1:fig13}, \ref{fig:subfig2:fig23}, \ref{fig:subfig3:fig33} and \ref{fig:subfig4:fig43},
 the number distribution of microblogs for four groups is similar with each other.
-We visualized each group's long-term interest expressed as words cloud (shown in Sub-Fig.
-\ref{fig:subfig1:fig19}, \ref{fig:subfig2:fig29}, \ref{fig:subfig3:fig39} and \ref{fig:subfig4:fig49}), as we can see, group one and group three have similar interest.
+We visualize each group's long-term interest expressed as words cloud (shown in Sub-Figs.
+\ref{fig:subfig1:fig19}, \ref{fig:subfig2:fig29}, \ref{fig:subfig3:fig39} and \ref{fig:subfig4:fig49}).
+As we can see, group one and group three have similar interests.
 

### 2017-10-14 Gruba/07-rela.tex

@@
 
-With respect to feature analysis, there have been existed works of mining users' info, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
-Our work, however, does not focus on the mining process per se; we use the mined info as the input for user clustering and group modeling.
+With respect to feature analysis, there have been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
+Our work, however, does not focus on the mining process per se; we use the mined features as the input for user clustering and group based behavior modeling.
 
@@
 Similarly, \cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} leveraged the followed experts to result interest characteristics.
-Unlike the existed solutions, \sys{} employs a cell lexicon to properly express user interest in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF are employed.
+Different from these existing solutions, \sys{} employs a cell lexicon to properly express user interests, in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF are employed.
 
-Approaches of grouping users in social network could fall into a variety of categories.
+Approaches of grouping users in social networks could fall into a variety of categories.
 \cite{IEEEexample:conf/icwsm/PennacchiottiP11} grouped users by the info of race, political view and etc.
@@
 \cite{IEEEexample:conf/aaai/ShiokawaFO13} proposed an incremental algorithm to mine user community using modular degree as the clustering yardstick.
-Providing the diversity of user features, \sys{} employs feature of info, behavior and interest into user clustering.
+Providing the diversity of user features, \sys{} employs basic, behavior and interest features into user clustering.
 

### 2017-10-14 Gruba/07-rela.tex

@@
 
-With respect to feature analysis, there have been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
-Our work, however, does not focus on the mining process per se; we use the mined features as the input for user clustering and group based behavior modeling.
+For feature analysis, there has been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
+Our work, however, does not focus on the mining process, but uses the mined features as the input for user clustering and group based behavior modeling.
 

### 2017-10-14 Gruba/02-overview.tex

@@
 \label{sec:overv}
-
-%This section shall look into the principle of each component in Processing Runtime subsystem, putting forth a full-fledged system.
-
-\subsection{\sys{} Framework}
-System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media, and
-Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.
-
-\begin{figure}[tb!]
-\centering
-\includegraphics[width=.67\linewidth]{figures/architecture.eps}
-\vspace{-1ex}
-\caption{\sys{} Architecture}
-\label{fig:framework}
-\vspace{-5ex}
-\end{figure}
 
@@
 
+\begin{figure}[tb!]
+\centering
+\includegraphics[width=.7\linewidth]{figures/architecture.eps}
+\vspace{-1ex}
+\caption{\sys{} Architecture}
+\label{fig:framework}
+\vspace{-2ex}
+\end{figure}
+
+%This section shall look into the principle of each component in Processing Runtime subsystem, putting forth a full-fledged system.
+
+\subsection{\sys{} Framework}
+System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media, and
+Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.
+
 % #like and #comment are saved; could generalize \sys{} to model the liking behavior (among commented blogs)
@@
 \end{comment}
-
-\begin{table}[tb!]
-\centering
-\begin{small}
-\caption{Illustration of Variables in Basic Feature}
-%\vspace{0.3cm}
-\label{tbl:fe-info}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
-$G_u$				& gender of user $u$				\\	\midrule
-$P_u$				& province of user $u$				\\	\midrule
-\#$R_u$				& number of followers				\\	\midrule
-\#$E_u$				& number of followees				\\	\midrule
-                    & a ratio defined as the number of followers  \\
-\raisebox{1.5ex}{$R_{ee,u}$}  & over that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
-$U_{t,u}$					& user type (as illustrated in Table \ref{tbl:ucate})			\\ \bottomrule
-\end{tabular}
-\end{small}
-\vspace{-2ex}
-\end{table}
-
-\begin{table}[tb!]
-\centering
-\begin{small}
-\caption{Category of User Type}
-%\vspace{0.3cm}
-\label{tbl:ucate}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
-0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
-\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
- 						&                       									\\	\midrule
-\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
-						&															\\	\midrule
-3                   	& other cases 												\\ \bottomrule
-\end{tabular}
-\end{small}
-\vspace{-2ex}
-\end{table}
 

### 2017-10-14 Gruba/03-fe.tex

@@
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Illustration of Variables in Basic Feature}
+\vspace{0.3cm}
+\label{tbl:fe-info}
+\begin{tabular}{ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
+$G_u$				& gender of user $u$				\\	\midrule
+$P_u$				& province of user $u$				\\	\midrule
+\#$R_u$				& number of followers				\\	\midrule
+\#$E_u$				& number of followees				\\	\midrule
+                    & a ratio defined as the number of followers  \\
+\raisebox{1.5ex}{$R_{ee,u}$}  & over that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
+$U_{t,u}$					& user type (as illustrated in Table \ref{tbl:ucate})			\\ \bottomrule
+\end{tabular}
+\end{small}
+\vspace{-1ex}
+\end{table}
+
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Category of User Type}
+\vspace{0.3cm}
+\label{tbl:ucate}
+\begin{tabular}{ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
+0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
+\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
+ 						&                       									\\	\midrule
+\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
+						&															\\	\midrule
+3                   	& other cases 												\\ \bottomrule
+\end{tabular}
+\end{small}
+\vspace{-1ex}
+\end{table}
+
 \section{Feature Extraction}
@@
 \label{eq:sim-tf1}
-sim(W_f, t) = VEC_{W_f} \cdot VEC_t
+sim(W_f, t) = VEC_{W_f} \cdot VEC_t, where
 \end{equation}
@@
 \label{eq:sum-tf1}
-VEC_{W_f} = \sum_{\substack{i}} p_i*vec[w_i]
+VEC_{W_f} = \sum_{\substack{i}} p_i*vec[w_i], and
 \end{equation}
@@
 \label{eq:sum-lexion}
-VEC_t = \sum_{\substack{j}} \frac{1}{N_t}*vec[c_j]
+VEC_t = \sum_{\substack{j}} \frac{1}{N_t}*vec[c_j].
 \end{equation}
@@
 \label{eq:simul-2}
-s_k = \sum_{\substack{m}} sim(b_m, t_k)
+s_k = \sum_{\substack{m}} sim(b_m, t_k).
 \end{equation}

### 2017-10-14 Gruba/01-intro.tex

@@
 
-\stab(2) We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/recent interests and explicit/implicit interests.
+\stab(2) We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/short-term interests and explicit/implicit interests.
 
@@
 Section \ref{sec:perf} is performance evaluation, followed by
-related work in Section \ref{sec:rela} and conclusion in Section \ref{sec:conclu}.
+related work in Section \ref{sec:rela} and conclusions in Section \ref{sec:conclu}.

### 2017-10-14 Gruba/01-intro.tex

@@
 Central to user behavior modeling is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
-Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
+Already, there exist works of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
 Apparently, such model bears the limitation of being coarse.

### 2017-10-14 Gruba/03-fe.tex

@@
-\begin{table}[tb!]
-\centering
-\begin{small}
-\caption{Illustration of Variables in Basic Feature}
-\vspace{0.3cm}
-\label{tbl:fe-info}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
-$G_u$				& gender of user $u$				\\	\midrule
-$P_u$				& province of user $u$				\\	\midrule
-\#$R_u$				& number of followers				\\	\midrule
-\#$E_u$				& number of followees				\\	\midrule
-                    & a ratio defined as the number of followers  \\
-\raisebox{1.5ex}{$R_{ee,u}$}  & over that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
-$U_{t,u}$					& user type (as illustrated in Table \ref{tbl:ucate})			\\ \bottomrule
-\end{tabular}
-\end{small}
-\vspace{-1ex}
-\end{table}
-
 \begin{table}[tb!]

### 2017-10-14 Gruba/06-perf.tex

@@
 The feature extraction result for Mary is depicted in Fig.\ \ref{fig:userFeatures}.
-Then we can see the basic information of Mary in Sub-Fig.\ \ref{fig:userFeatures:uf-1}: her nickname is Actress Mary (演员马丽) and she is from Beijing (北京).
+Then we can see the basic information of Mary in Fig.\ \ref{fig:userFeatures:uf-1}: her nickname is Actress Mary (演员马丽) and she is from Beijing (北京).
 Mary has more followers than followees.
 The Sina Microblog tag she made for herself is ``actress'' (演员).
-As to the long-term interest, she is interested with stage performance (舞台表演), drama (话剧表演),film (电影光影) and so on as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-2}, which is consistent with her tag.
-The probability distribution of tweeting and retweeting indicates that she is more active at night than daytime as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-3} and \ref{fig:userFeatures:uf-4}.
-According to Sub-Fig.\ \ref{fig:userFeatures:uf-5} and \ref{fig:userFeatures:uf-6}, the interval between her two tweeted/retweeted microblogs is mostly within 48 hours, showing she is an active user.
+As to the long-term interest, she is interested with stage performance (舞台表演), drama (话剧表演),film (电影光影) and so on as shown in Fig.\ \ref{fig:userFeatures:uf-2}, which is consistent with her tag.
+The probability distribution of tweeting and retweeting indicates that she is more active at night than daytime as shown in Fig.\ \ref{fig:userFeatures:uf-3} and \ref{fig:userFeatures:uf-4}.
+According to Fig.\ \ref{fig:userFeatures:uf-5} and \ref{fig:userFeatures:uf-6}, the interval between her two tweeted/retweeted microblogs is mostly within 48 hours, showing she is an active user.
 Mary's short-term interest, e.g.
-from 09/01/2016 to 09/30/2016, is shown in Sub-Fig.\ \ref{fig:userFeatures:uf-7}, which indicates she had been busy with promoting the drama ``Earl of Oolong Mountain'' (乌龙山伯爵).
-So the results are in line with expectations, as drama (话剧) and stage (舞台) in Sub-Fig.\ \ref{fig:userFeatures:uf-7}.
+from 09/01/2016 to 09/30/2016, is shown in Fig.\ \ref{fig:userFeatures:uf-7}, which indicates she had been busy with promoting the drama ``Earl of Oolong Mountain'' (乌龙山伯爵).
+So the results are in line with expectations, as drama (话剧) and stage (舞台) in Fig.\ \ref{fig:userFeatures:uf-7}.
 
@@
   \centering
-  \subfigure{
+  \subfigure[]{
       \label{fig:userFeatures:uf-1}
       \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
-  \subfigure{
+  \subfigure[]{
       \label{fig:userFeatures:uf-2}
       \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
-  \subfigure{
+  \subfigure[]{
       \label{fig:userFeatures:uf-3}
       \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
-  \subfigure{
+  \subfigure[]{
       \label{fig:userFeatures:uf-4}
       \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
-  \subfigure{
+  \subfigure[]{
       \label{fig:userFeatures:uf-5}
       \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
-  \subfigure{
+  \subfigure[]{
       \label{fig:userFeatures:uf-6}
       \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
-  \subfigure{
+  \subfigure[]{
       \label{fig:userFeatures:uf-7}
       \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
-  \subfigure{
+  \subfigure[]{
       \label{fig:userFeatures:uf-8}

### 2017-10-14 Gruba/10-appendix.tex

@@
-\newpage
-\section{Appendix: Extra Experiments}
+\section*{Appendix: Extra Experiments}
 \label{sec:appendix}
@@
 %\subsection{Case Study for Feature Extraction}
-
-\subsection{Case Study for User Clustering}
-
-In this section, we show the results of our system \sys{} for User Clustering. We carefully analyzed the statistical information of four groups obtained from user clustering.
-
-\stab(1) Most users of group one are male (as shown in Sub-Fig.
-\ref{fig:subfig1:fig11}), and Sub-Fig.
-\ref{fig:subfig1:fig12} shows that they are mainly in Beijing(北京).
-The amount of their followees is mostly similar as their followers (as shown in Sub-Fig.
-\ref{fig:subfig1:fig14}).
-The most active time of this group is mainly between 10 am and 12 am (as shown in Sub-Fig.
-\ref{fig:subfig1:fig15} and \ref{fig:subfig1:fig16}).
-
-\stab(2) Mostly users of group two are  female (as shown in Sub-Fig.
-\ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Sub-Fig.
-\ref{fig:subfig2:fig22}).
-Similar to group one, most of them have followees close to followers (as shown in Sub-Fig.
-\ref{fig:subfig2:fig24}).
-The most active time of this group is mainly between 10 pm and 12 pm (as shown in Sub-Fig.
-\ref{fig:subfig2:fig25} and \ref{fig:subfig2:fig26}).
-
-\stab(3) Most users of group three are male (as shown in Sub-Fig.
-\ref{fig:subfig3:fig31}).
-They come from a wide range of provinces (as shown in Sub-Fig.
-\ref{fig:subfig3:fig32}).
-Most of them have number of followers far more than followees (as shown in Sub-Fig.
-\ref{fig:subfig3:fig34}).
-The most active time of this group is mainly in 10-12 am and 10-12 pm (as shown in Sub-Fig.
-\ref{fig:subfig3:fig35} and \ref{fig:subfig3:fig36}).
-
-\stab(4) Most users of group four are female (as shown in Sub-Fig.
-\ref{fig:subfig4:fig41}), and they come from a wide range of provinces just as group three (as shown in Sub-Fig.
-\ref{fig:subfig4:fig42}).
-Most of these users have the amount  of followers far more than followees (as shown in Sub-Fig.
-\ref{fig:subfig4:fig44}).
-And the most active time of these users is mainly between 10 pm and 12 pm (as shown in Sub-Fig.
-\ref{fig:subfig4:fig45} and \ref{fig:subfig4:fig46}).
-
-According to Sub-Figs. \ref{fig:subfig1:fig13}, \ref{fig:subfig2:fig23}, \ref{fig:subfig3:fig33} and \ref{fig:subfig4:fig43},
-the number distribution of microblogs for four groups is similar with each other.
-We visualize each group's long-term interest expressed as words cloud (shown in Sub-Figs.
-\ref{fig:subfig1:fig19}, \ref{fig:subfig2:fig29}, \ref{fig:subfig3:fig39} and \ref{fig:subfig4:fig49}).
-As we can see, group one and group three have similar interests.
-
 \begin{figure*}
   \centering
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig1:fig11}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/11.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig1:fig12}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/12.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig1:fig13}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/13.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig1:fig14}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/14.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig1:fig15}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/15.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig1:fig16}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/16.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig1:fig17}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/17.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig1:fig18}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/18.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig1:fig19}
@@
 
+\subsection*{Exp-5: Case Study for User Clustering}
+
+In this section, we show the results of our system \sys{} for User Clustering. We carefully analyzed the statistical information of four groups obtained from user clustering.
+
+\stab(1) Most users of group one are male (as shown in Fig.
+\ref{fig:subfig1:fig11}), and Fig.
+\ref{fig:subfig1:fig12} shows that they are mainly in Beijing(北京).
+The amount of their followees is mostly similar as their followers (as shown in Fig.
+\ref{fig:subfig1:fig14}).
+The most active time of this group is mainly between 10 am and 12 am (as shown in Fig.
+\ref{fig:subfig1:fig15} and \ref{fig:subfig1:fig16}).
+
+\stab(2) Mostly users of group two are  female (as shown in Fig.
+\ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Fig.
+\ref{fig:subfig2:fig22}).
+Similar to group one, most of them have followees close to followers (as shown in Fig.
+\ref{fig:subfig2:fig24}).
+The most active time of this group is mainly between 10 pm and 12 pm (as shown in Fig.
+\ref{fig:subfig2:fig25} and \ref{fig:subfig2:fig26}).
+
+\stab(3) Most users of group three are male (as shown in Fig.
+\ref{fig:subfig3:fig31}).
+They come from a wide range of provinces (as shown in Fig.
+\ref{fig:subfig3:fig32}).
+Most of them have number of followers far more than followees (as shown in Fig.
+\ref{fig:subfig3:fig34}).
+The most active time of this group is mainly in 10-12 am and 10-12 pm (as shown in Fig.
+\ref{fig:subfig3:fig35} and \ref{fig:subfig3:fig36}).
+
+\stab(4) Most users of group four are female (as shown in Fig.
+\ref{fig:subfig4:fig41}), and they come from a wide range of provinces just as group three (as shown in Fig.
+\ref{fig:subfig4:fig42}).
+Most of these users have the amount  of followers far more than followees (as shown in Fig.
+\ref{fig:subfig4:fig44}).
+And the most active time of these users is mainly between 10 pm and 12 pm (as shown in Fig.
+\ref{fig:subfig4:fig45} and \ref{fig:subfig4:fig46}).
+
+According to Fig. \ref{fig:subfig1:fig13}, \ref{fig:subfig2:fig23}, \ref{fig:subfig3:fig33} and \ref{fig:subfig4:fig43},
+the number distribution of microblogs for four groups is similar with each other.
+We visualize each group's long-term interest expressed as words cloud (shown in Figs.
+\ref{fig:subfig1:fig19}, \ref{fig:subfig2:fig29}, \ref{fig:subfig3:fig39} and \ref{fig:subfig4:fig49}).
+As we can see, group one and group three have similar interests.
+
 \begin{figure*}
   \centering
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig2:fig21}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/21.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig2:fig22}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/22.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig2:fig23}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/23.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig2:fig24}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/24.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig2:fig25}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/25.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig2:fig26}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/26.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig2:fig27}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/27.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig2:fig28}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/28.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig2:fig29}
@@
   \centering
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig3:fig31}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/31.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig3:fig32}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/32.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig3:fig33}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/33.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig3:fig34}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/34.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig3:fig35}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/35.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig3:fig36}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/36.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig3:fig37}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/37.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig3:fig38}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/38.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig3:fig39}
@@
   \centering
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig4:fig41}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/41.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig4:fig42}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/42.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig4:fig43}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/43.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig4:fig44}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/44.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig4:fig45}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/45.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig4:fig46}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/46.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig4:fig47}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/47.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig4:fig48}
       \includegraphics[width=0.23\textwidth]{IMAGE/group-images/48.eps}}
-  \subfigure{
+  \subfigure[]{
   \label{fig:subfig4:fig49}

### 2017-12-17 DASFAA_2018/Gruba/00-abstr.tex

--- 2017-10-13 Gruba/00-abstr.tex
@@
 To this end, this paper presents a novel solution, of which the principle is to model the \retg{} behavior over user groups.
-Our approach, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
-Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests.
+Our system, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
+Particularly, we look into the user interest from different perspectives including long-term/short-term interests and explicit/implicit interests.
 %, which results deep analyses towards the \retg{} behavior and proper models in the end.

### 2017-12-17 DASFAA_2018/Gruba/07-rela.tex

--- 2017-10-14 Gruba/07-rela.tex
@@
 The main problem of current approaches for behavior modeling lies in that the model is for either the overall users or a single user.
-\cite{IEEEexample:journals/tkdd/ZhangTLLX15, IEEEexample:conf/wsdm/FengW13, IEEEexample:conf/ijcai/ZhangLTCL13} discovered that users' \retg{} behavior is largely influenced by their followees, whereas \cite{IEEEexample:conf/cikm/JiangLSW15} employed matrix decomposition, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} used collaborative filtering methods and \cite{IEEEexample:zhang2015retweet} leveraged statistical models for \retg{} analysis.
+\cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13} discovered that users' \retg{} behavior is largely influenced by their followees, whereas \cite{IEEEexample:conf/cikm/JiangLSW15} employed matrix decomposition, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} used collaborative filtering methods and \cite{IEEEexample:zhang2015retweet} leveraged statistical models for \retg{} analysis.
 \cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15} and \cite{IEEEexample:journals/corr/RanganathMHTL15} focused on identifying whether the \retg{} is fraudulent or of protest.

### 2017-12-24 DASFAA_2018/Gruba/00-abstr.tex

@@
 %, which results deep analyses towards the \retg{} behavior and proper models in the end.
-We have evaluated the performance of \sys{} using datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.
+We have evaluated the performance of \sys{} using datasets of real-world social networking applications, and shown its benefits.
+
+\keywords{user grouping \middot social networks \middot behavior modeling}
 \end{abstract}

### 2017-12-24 DASFAA_2018/Gruba/01-intro.tex

--- 2017-10-14 Gruba/01-intro.tex
@@
 
-Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users.
+\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, have attracted  massive users.
 These users behave variously, knowledge of which is significant for various applications such as recommendation system and activity analysis.
@@
 Central to user behavior modeling is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
-Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
+Already, there exist works of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
 Apparently, such model bears the limitation of being coarse.
@@
 
-\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model as in existed research.
+\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of a single model for all users.
 
@@
 
-\stab(3) We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.
+\stab(3) We offer a clustering method K-Gru to deal with complex vectors, serving as an extension for standard K-Prototype algorithm.
+
+\stab(4) We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.
 

### 2017-12-24 DASFAA_2018/Gruba/02-overview.tex

--- 2017-10-14 Gruba/02-overview.tex
@@
 
-We consider the \retg{} behavior of users in social media.
+\par We consider the \retg{} behavior of users in social media.
 %For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
@@
 A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a.
-user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally \tw{} (0) by $O$.
+user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} or originally tweeted by $O$.
+Here we use 1 and 0 to denote \retd{} and  tweeted, respectively.
 \end{definition}
@@
 \label{def:user}
-Given a user $u$, we adopt $B_u$, $R_u$ and $E_u$ to represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee per se refers to a user.
+Given a user $u$, we adopt $B_u$, $R_u$ and $E_u$ to represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee is a user.
 \end{definition}
@@
 %The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
-Note that $M_b.O$ is a user $u$, and $B_u$ is a set of $M_b$.
+Note that $M_b.O$ is a user, and $B_u$ is a set of microblogs.
 
-Providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower $f$ of its onwer $b.O$, i.e., $f \in R_{b.O}$, system \sys{} builds a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ \ret{s} $b$ or not.
+Providing a set of users $\mathbb{U}$ and their associated microblogs $\mathbb{B}$, system \sys{} builds a \retg{} model for each group of  $\mathbb{U}$, such that given a microblog $b$ and a follower $f$ of its onwer $b.O$, i.e., $f \in R_{b.O}$, 1 or 0 is returned regarding whether $f$ \ret{s} $b$ or not.
 
@@
 \centering
-\includegraphics[width=.7\linewidth]{figures/architecture.eps}
+\includegraphics[width=.5\linewidth]{figures/architecture.eps}
 \vspace{-1ex}
@@
 \label{fig:framework}
-\vspace{-2ex}
+\vspace{-4ex}
 \end{figure}
@@
 
-\stitle{Sina Microblog Data.} It is the data crawled to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definitions} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
+\stitle{Sina Microblog Data.} It is the data crawled to be processed by \sys{}, i.e., data of microblogs and users.
 
@@
 
-As shown above, the distinctive feature of System  \sys{} is to model user \retg{} behaviors over groups instead of the mono model for all users.
+The distinctive feature of System  \sys{} models user \retg{} behaviors over groups instead of a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.

### 2017-12-24 DASFAA_2018/Gruba/03-fe.tex

--- 2017-10-14 Gruba/03-fe.tex
@@
-\begin{table}[tb!]
+\begin{table}[h!]
+\begin{minipage}[b]{0.6\linewidth}
 \centering
@@
 \caption{Illustration of Variables in Basic Feature}
-\vspace{0.3cm}
+\vspace{0.1cm}
 \label{tbl:fe-info}
@@
 \#$E_u$				& number of followees				\\	\midrule
-                    & a ratio defined as the number of followers  \\
-\raisebox{1.5ex}{$R_{ee,u}$}  & over that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
+                    & a ratio defined as the number of             \\	
+\raisebox{1.5ex}{$R_{ee,u}$} &followers over that of followees,i.e.,$\frac{\#R_u}{\#E_u}$                  \\  \midrule
 $U_{t,u}$		    & user type (as illustrated in Table \ref{tbl:ucate})      \\ \bottomrule		
@@
 \vspace{-1ex}
-\end{table}
-
-\begin{table}[tb!]
+\end{minipage}
+\begin{minipage}[b]{0.4\linewidth}
 \centering
@@
 \caption{Category of User Type}
-\vspace{0.3cm}
+\vspace{0.1cm}
 \label{tbl:ucate}
@@
 \multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
-0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
+0                       & $\#E_u \le 50 \ {\bf and}$   \\
+                        & $\ \#R_u \le 50$				  \\	\midrule
 \multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
@@
 \vspace{-1ex}
+\end{minipage}
 \end{table}
@@
 
-With the underlying Sina Microblog Data, the Feature Extraction module is responsible for mining the user characteristics, and produces three classes of features for each user: \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, referred to as  \textit{Feature Data} in \sys{}.
+\par With the underlying Sina Microblog Data, the Feature Extraction module is responsible for mining the user characteristics, and produces three classes of features for each user: \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, referred to as  \textit{Feature Data} in \sys{}.
 %, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.
@@
 
-Different from the slightly straightforward \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users with their interested topics.
+Different from the slightly straightforward \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users with their interested topics based on their tweeted and retweeted microblogs.
 In short, with a given lexicon (made by some professionals) consisting of several \textit{topics}, the interest feature of a user $u$ is a normalized vector, in which each entry refers to the degree that $u$ is interested in the corresponding \textit{topic}.
@@
 \label{eq:inte}
-(p_0, p_1, \ldots, p_{x-1})
+(p_0, p_1, \ldots, p_{x-1}),
 \end{equation}
@@
 
-In system \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
+In  \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
 Hence, the similarity $sim(w, c)$ of a word pair ($w$, $c$) could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user $u$ versus each topic $t$ in lexicon $sim(u, t)$; topics with similarity satisfying certain thresholds are allocated to user $u$ and constitute the interests of $u$.
@@
 System \sys{} employs a well established lexicon to discover the explicit interests of users.
-In case when no proper explicit interests are found, TF-IDF (Term-Frequency and Inverse Document-Frequency) and Twitter-LDA \cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector \cite{IEEEexample:mikolov2013distributed} is adopted to measure the similarity between two words.
-We now present the detailed process for mining the interest features of a user $u$.
+%In case when no proper explicit interests are found, TF-IDF (Term-Frequency and Inverse Document-Frequency) and Twitter-LDA %\cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector %\cite{IEEEexample:mikolov2013distributed} is adopted to measure the similarity between two words.
+When no proper explicit interests are found, two algorithms are leveraged to identify implicit interests: (1) TF-IDF (Term-Frequency and Inverse Document-Frequency) \cite{IEEEexample:books/cu/LeskovecRU14}, and (2) Twitter-LDA \cite{IEEEexample:zhao2011comparing} (a method to discover topics from Twitter, by applying the standard Latent Dirichlet Allocation (LDA) model \cite{IEEEexample:conf/jmlr/Blei03}), both of which adopt word2vector \cite{IEEEexample:mikolov2013distributed} to measure word similarity.
+
+We now explain the detailed process for mining the interest features of a user.
 
@@
 If $w$ and $c$ are identical, $sim(w, c) = 1$, and $sim(w, c) = 0$, otherwise.
+
 The similarity of $b$ with a lexicon topic $t$ is defined as
@@
 the user $u$ is then discovered having an explicit interest (topic) $t$.
-Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).
+Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (Definition \ref{def:inte}).
 
@@
 \label{eq:tf-w}
-p''_i = \frac{|b_i|}{|b|} * \log(\frac{|D_i|}{|D|}),
+p''_i = \frac{|b_i|}{|b|} * \log(\frac{|D|}{|D_i|+1}),
 \end{equation}
 in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$, and $|b|$ the total occurrences of all words in $b$.
-Ditto for $|D_i|$ and $|D|$, except that the scope is the overall dataset, rather than a single microblog $b$.
-
+$|D|$ is the total number of microblogs in the dataset and $|D_i|$ is the number of microblogs where $|b_i|$ appears.
 Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.
@@
 
-\stitle{Step 4:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is given by:
+\stitle{Step 4:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is :
 \begin{equation}

### 2017-12-24 DASFAA_2018/Gruba/04-uc.tex

--- 2017-10-13 Gruba/04-uc.tex
@@
 
-Providing the \textit{Feature Data}, the User Clustering module takes the charge of grouping each user concerned into a proper cluster,
+\par Providing the \textit{Feature Data}, the User Clustering module takes the charge of grouping each user concerned into a proper cluster,
 as illustrated in  Algorithm \ref{alg:uc}.
@@
 \ForAll {$t \in [N_i, N_a]$} \label{enu}
-	\State group users into $t$ clusters by $F$; \label{task}
+	%\State group users into $t$ clusters by $F$; 
+    \State perform K-Gru over F to get t clusters \label{task}
 	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
@@
 \EndFor
-\If {$v(a)\ =\ \ Max\{v(t)\}$}; \label{opti}
+\If {$v(a)\ =\ \ Max\{v(t)\}$} \label{opti}
 	\State $R$ := $R'(a)$;
@@
 
-\subsection{Clustering in \sys{}}
+\subsection{K-Gru: Clustering in \sys{}}
 \label{sec:cluster}
@@
 
-\begin{table}[!htb]
-\centering
-\begin{small}
-%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
-\caption{Dimension Types in \textit{Feature Data} Vector}
-%\vspace{0.3cm}
-\label{tbl:data-type}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
-numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$,\\
-                            &  $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$				\\	\midrule
-categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
-normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_{f,u}$			\\ \bottomrule
-\end{tabular}
-\end{small}
-\end{table}
-
 As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers (normalized to 0-1 range), categories and normalized vectors.
-For simplicity, we shall first illustrate the distance calculation of the simple vectors with a mono data type on each dimension, and then demonstrate that of complex vectors.
+For simplicity, we shall first illustrate the distance calculation of the simple vectors with a single data type on each dimension, and then demonstrate that of complex vectors.
 
@@
 \label{eq:od}
-D_n(Y', Z') = \sum_{\substack{e}} (y_e - z_e)^2
+D_n(Y', Z') = \sum_{\substack{e}} (y_e - z_e)^2.
 \end{equation}
@@
 \label{eq:vd}
-D_v(Y^{\ast}, Z^{\ast}) = 1- \sum_{\substack{e}} Y^{\ast}_e \cdot Z^{\ast}_e
+D_v(Y^{\ast}, Z^{\ast}) = 1- \sum_{\substack{e}} Y^{\ast}_e \cdot Z^{\ast}_e,
 \end{equation}
@@
 \label{eq:gd}
-D_g(Y, Z) = \sum_{\substack{e}} G_e
+D_g(Y, Z) = \sum_{\substack{e}} G_e,
 \end{equation}
@@
 \label{sec:compu}
+
+\begin{table}[tb!]
+\centering
+\begin{small}
+%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
+\caption{Dimension Types in \textit{Feature Data} Vector}
+%\vspace{0.1cm}
+\label{tbl:data-type}
+\begin{tabular}{ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
+numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$, $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$               \\	\midrule 				
+categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
+normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_u$			\\ \bottomrule
+\end{tabular}
+\end{small}
+\end{table}
 

### 2017-12-24 DASFAA_2018/Gruba/05-gm.tex

--- 2017-10-13 Gruba/05-gm.tex
@@
 
-Recall the central problem of \sys{}, where the \retg{} behaviors of users are modeled.
+\par Recall the central problem of \sys{}, where the \retg{} behaviors of users are modeled.
 Specifically, such model is built by the Group Modeling module for each user group and thus named as group model.
@@
 
-	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{$G_u$, $P_u$,\#$R_u$, \#$E_u$, $R_{ee,u}$ \}.
+	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{$G_u$, $P_u$, \#$R_u$, \#$E_u$, $R_{ee,u}$\}.
 
@@
 
-The modeling of retweeting behavior of groups is treated as a classification problem, and utilize the random forest classifier to attack it.
+The modeling of retweeting behavior of groups is treated as a classification problem, and utilize the random forest classifier to address it.
+Details for random forest \cite{IEEEexample:conf/icdar/Ho1995} are omitted here for space reason.
 The advantage of this classification model lies in that it could integrate different features conveniently, and
@@
 the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above.
+
+Here we use accuracy to evaluate our model.
+To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$.
+For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0.
+If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0.
+If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0.
+If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0.
+Formally, accuracy is defined as:
+
+\begin{equation}
+\label{eq:def-presision}
+accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }.
+\end{equation}

### 2017-12-24 DASFAA_2018/Gruba/06-perf.tex

--- 2017-10-14 Gruba/06-perf.tex
@@
 
-In this section, we shall first detail the experimental setting, and we then present the evaluation result and analysis, showing the benefit of \sys{} against state of the art approaches.
+\par In this section, we shall first detail the experimental setting, and we then present the evaluation result and analysis, showing the benefit of \sys{} against state of the art approaches.
 
@@
 With respect to the parameters of \sys{}, we use the default values as mentioned in previous sections.
-Particularly, for the Feature Extraction module, for practical reasons, we employed a smaller testing dataset to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature};
+Particularly, for the Feature Extraction module, for practical reasons, we employed a smaller testing dataset (with manually labeled topics for yardstick) to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature};
 For the User Cluster module, we studied the clustering solutions with the minimum/maximum number of clusters 2 and 10;
@@
 
-\stitle{Exp-1: Feature Extraction}
+\stitle{Exp-1: Interest Extraction}
 %
 Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
+We report the interest accuracy with various $\alpha$ values.
+Suppose that the label set manually labeled for each microblog is $A$, the label set that our method labeled is $B$.
+The interest accuracy is defined as $\frac{ A \cap B }{ A \cup B }$.
+
 System \sys{} reaches the optimal results when $\alpha$ is 0.7,
@@
 %
-Fig.\ \ref{fig:uc} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
+Fig.\ \ref{fig:10-c} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
 Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
@@
 
-\begin{figure}[tb!]
-\centering
-\includegraphics[width=.7\linewidth]{figures/Interests}
-\caption{Testing Results with Various $\alpha$.}
-\label{fig:fe}
-\vspace{-1ex}
-\end{figure}
+%\begin{figure}[tb!]
+%  \centering
+%  \subfigure[Tests with Various $\alpha$.]{
+%    \label{fig:fe}
+%\includegraphics[width=.355\linewidth]{figures/Interests}}
+%  \hspace{0.5in}
+%   \subfigure[Silhouette Coefficient Tests.]{
+%    \label{fig:10-c}
+%  \includegraphics[width=.355\linewidth]{figures/clustering}}
+%  \caption{Performance of \sys{} Versus LRC-BQ.}
+%    \label{fig:fig-1}
+%\end{figure}
 
@@
 \centering
-\includegraphics[width=.85\linewidth]{figures/clustering}
-\caption{Silhouette Coefficient Values for Various Cluster Numbers over Different Testing Datasets.}
-\label{fig:uc}
-\vspace{-2ex}
+\begin{minipage}{.5\textwidth}
+  \centering
+\includegraphics[width=.85\linewidth]{figures/Interests}
+\caption{Interest Extraction: Varying $\alpha$.}
+\label{fig:fe}
+\end{minipage}%
+\begin{minipage}{.5\textwidth}
+  \centering
+\includegraphics[width=.8\linewidth]{figures/clustering}
+\caption{Silhouette Coefficient Tests.}
+\label{fig:10-c} 
+\end{minipage}
 \end{figure}
 
+\begin{figure*}[tb!]
+%\centering
+  \subfigure[\sys{} Vs. LRC-BQ]{
+    \label{fig:10-a}
+    %\vspace{2ex}
+    \includegraphics[width=0.5\textwidth]{figures/precision-1.eps}}
+ % \hspace{0.5in}
+   \subfigure[Varying Items]{
+   %\vspace{2ex}
+    \label{fig:11-a}
+  \includegraphics[width=0.5\textwidth]{figures/precisionofdifferentfeatures.eps}}
+  %\vspace{-1ex}
+  \caption{Accuracy Evaluation.}
+  \label{fig:fig-2}
+  \vspace{-4ex}
+\end{figure*}
+
+\begin{comment}
 \begin{figure*}[tb!]
@@
     \label{fig:10-a}
-    \includegraphics[width=0.32\textwidth]{figures/precision.eps}}
+    \includegraphics[width=0.315\textwidth]{figures/precision.eps}}
   %\hspace{1in}
@@
     \label{fig:10-b}
-    \includegraphics[width=0.32\textwidth]{figures/recall.eps}}
+    \includegraphics[width=0.315\textwidth]{figures/recall.eps}}
   %\hspace{1in}
@@
     \label{fig:10-c}
-    \includegraphics[width=0.32\textwidth]{figures/F-Measure.eps}}
+    \includegraphics[width=0.315\textwidth]{figures/F-Measure.eps}}
   \caption{Performance of \sys{} Versus LRC-BQ.}
   \label{fig:10}
+\vspace{-4ex}
 \end{figure*}
+\end{comment}
 
@@
 %
-Fig.\ \ref{fig:10} shows the performance of \sys{} against the state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
-We evaluate the performance using the metrics of precision, recall, and $F_1$ score.
+Fig.\ \ref{fig:10-a} shows the performance of \sys{} against the state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
+We evaluate the performance using the metrics of accuracy.
 LRC-BQ does not deal with user grouping.
@@
 
-	\stab(2) For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ.
+	\stab(2) For \sys{}, having user clustering is better than the alternative single group. Ditto for LRC-BQ.
 %\end{itemize}
 
-Fig.\ \ref{fig:11} explores the performance of \sys{} when using alternative data items for modeling.
+Fig.\ \ref{fig:11-a} explores the performance of \sys{} when using alternative data items for modeling.
 By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), microblogs (MI) and interactions (II).
-How about using other combinations of the above item(s)?
-As shown in Fig.\ \ref{fig:11}, the default setting wins in most cases.
+%How about using other combinations of the above item(s)?
+As shown in Fig.\ \ref{fig:11-a}, the default setting wins in most cases.
 
+\begin{comment}
 \begin{figure*}
@@
     \label{fig:11-a}
-    \includegraphics[width=0.32\textwidth]{figures/precisionofdifferentfeatures.eps}}
+    \includegraphics[width=0.315\textwidth]{figures/precisionofdifferentfeatures.eps}}
   %\hspace{1in}
@@
     \label{fig:11-b}
-    \includegraphics[width=0.32\textwidth]{figures/recallofdifferentfeatures.eps}}
+    \includegraphics[width=0.315\textwidth]{figures/recallofdifferentfeatures.eps}}
   %\hspace{1in}
@@
     \label{fig:11-c}
-    \includegraphics[width=0.32\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
+    \includegraphics[width=0.315\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
   \caption{\sys{} Performance of Using Various Data Items for Modeling.}
   \label{fig:11}
-  \vspace{-1ex}
+  \vspace{-4ex}
+\end{figure*}
+\end{comment}
+
+\begin{figure*}[tb!]
+\vspace{-2ex}
+  \centering
+  \subfigure[]{
+      \label{fig:userFeatures:uf-1}
+      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/1.eps}}
+  \subfigure[]{
+      \label{fig:userFeatures:uf-2}
+      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/2.eps}}
+  \subfigure[]{
+      \label{fig:userFeatures:uf-3}
+      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/3.eps}}
+  \subfigure[]{
+      \label{fig:userFeatures:uf-4}
+      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/4.eps}}
+  \subfigure[]{
+      \label{fig:userFeatures:uf-5}
+      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/5.eps}}
+  \subfigure[]{
+      \label{fig:userFeatures:uf-6}
+      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/6.eps}}
+  \subfigure[]{
+      \label{fig:userFeatures:uf-7}
+      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/7.eps}}
+  \subfigure[]{
+      \label{fig:userFeatures:uf-8}
+      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/8.eps}}
+  \caption{Visualization for User Features.}
+  \label{fig:userFeatures} %% label for entire figure
+  \vspace{-4ex}
 \end{figure*}
@@
 
-\begin{figure*}
-  \centering
-  \subfigure[]{
-      \label{fig:userFeatures:uf-1}
-      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
-  \subfigure[]{
-      \label{fig:userFeatures:uf-2}
-      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
-  \subfigure[]{
-      \label{fig:userFeatures:uf-3}
-      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
-  \subfigure[]{
-      \label{fig:userFeatures:uf-4}
-      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
-  \subfigure[]{
-      \label{fig:userFeatures:uf-5}
-      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
-  \subfigure[]{
-      \label{fig:userFeatures:uf-6}
-      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
-  \subfigure[]{
-      \label{fig:userFeatures:uf-7}
-      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
-  \subfigure[]{
-      \label{fig:userFeatures:uf-8}
-      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
-  \caption{Visualization for User Features.}
-  \label{fig:userFeatures} %% label for entire figure
-\end{figure*}
+%\noindent\textbf{Summary}. %From these experimental results we find the followings.
+%(1) We design a novel method to extract users' explicit/implicit interests, and case studies show that our method is effective.
+%(2) In this paper, we offer a clustering method K-Gru to deal with complex vectors. And it helps us find a reasonable clustering result.
+%
+To conclude, by modeling user behaviors over groups instead of a single model for all users such as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%.
+What deserves to be mentioned is that the performance of LRC-BQ is also improved significantly by user clustering.

### 2017-12-24 DASFAA_2018/Gruba/07-rela.tex

@@
 
-In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
+\par In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
 As aforementioned, \sys{} leverages the user features of basics, behavior and interest.
 
-For feature analysis, there has been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
+For feature analysis, there has been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14} and occupation \cite{IEEEexample:conf/icde/FanCTWC16}.
 Our work, however, does not focus on the mining process, but uses the mined features as the input for user clustering and group based behavior modeling.
@@
 The main problem of current approaches for behavior modeling lies in that the model is for either the overall users or a single user.
-\cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13} discovered that users' \retg{} behavior is largely influenced by their followees, whereas \cite{IEEEexample:conf/cikm/JiangLSW15} employed matrix decomposition, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} used collaborative filtering methods and \cite{IEEEexample:zhang2015retweet} leveraged statistical models for \retg{} analysis.
+\cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13} discovered that users' \retg{} behavior is largely influenced by their followees, whereas \cite{IEEEexample:conf/cikm/JiangLSW15} employed matrix decomposition, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} used collaborative filtering methods and \cite{IEEEexample:zhang2015retweet} leveraged statistical models for \retg{} analysis.
 \cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15} and \cite{IEEEexample:journals/corr/RanganathMHTL15} focused on identifying whether the \retg{} is fraudulent or of protest.
-Whereas our work \sys{} builds the \retg{} model for each user group, instead of the mono model for all users or one model per user.
+Whereas our work \sys{} builds the \retg{} model for each user group, instead of a single model for all users or one model per user.

### 2017-12-24 DASFAA_2018/Gruba/08-conclu.tex

--- 2017-10-13 Gruba/08-conclu.tex
@@
 
-In this work, we have presented \sys{}, a system to model the \retg{} behavior of users in social media.
+\par In this work, we have presented \sys{}, a system to model the \retg{} behavior of users in social media.
 \sys{} departures from existing work by grouping users into clusters, during which features of basics, behavior and interests are extracted.
-Specially, we have studied interest features from various perspectives, such as long-term/recent interests and explicit/implicit interests.
+Specially, we have studied interest features from various perspectives, such as long-term/short-term interests and explicit/implicit interests.
 Finally, we have provided a performance evaluation of \sys{} by using real-world datasets to demonstrate the benefits of our system \sys{}.

### 2018-02-24 DASFAA18_CR/Gruba_final/02-overview.tex

--- 2017-12-24 DASFAA_2018/Gruba/02-overview.tex
@@
 A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a.
-user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} or originally tweeted by $O$.
-Here we use 1 and 0 to denote \retd{} and  tweeted, respectively.
+user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} or originally \tw{} by $O$.
+Here we use 1 and 0 to denote \retd{} and  \tw{}, respectively.
 \end{definition}
@@
 \centering
-\includegraphics[width=.5\linewidth]{figures/architecture.eps}
+\includegraphics[width=.7\linewidth]{figures/architecture.eps}
 \vspace{-1ex}

### 2018-02-24 DASFAA18_CR/Gruba_final/04-uc.tex

--- 2017-12-24 DASFAA_2018/Gruba/04-uc.tex
@@
 The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
-In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
+In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task} to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
 then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
@@
 \ForAll {$t \in [N_i, N_a]$} \label{enu}
-	%\State group users into $t$ clusters by $F$; 
-    \State perform K-Gru over F to get t clusters \label{task}
+	%\State group users into $t$ clusters by $F$; \label{task}
+    \State perform K-Gru over F to get t clusters
 	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
@@
 
+\begin{table}[tb!]
+\centering
+\begin{small}
+%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
+\caption{Dimension Types in \textit{Feature Data} Vector}
+\vspace{0.1cm}
+\label{tbl:data-type}
+\begin{tabular}{ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
+numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$, $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$               \\	\midrule 				
+categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
+normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_u$			\\ \bottomrule
+\end{tabular}
+\end{small}
+\end{table}
+
 As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers (normalized to 0-1 range), categories and normalized vectors.
-For simplicity, we shall first illustrate the distance calculation of the simple vectors with a single data type on each dimension, and then demonstrate that of complex vectors.
+For simplicity, we shall first illustrate the distance calculation of the simple vectors with a mono data type on each dimension, and then demonstrate that of complex vectors.
 
@@
 \end{equation}
-where $H_e$ refers to the \hd{} over each dimension, with $H_e = 1$ if $y''_e$ and $z''_e$ share the identical value, and $H_e = 0$, otherwise.
+where $H_e$ refers to the \hd{} over each dimension, with $H_e = 0$ if $y''_e$ and $z''_e$ share the identical value, and $H_e = 1$, otherwise.
 
@@
 \label{eq:vd}
-D_v(Y^{\ast}, Z^{\ast}) = 1- \sum_{\substack{e}} Y^{\ast}_e \cdot Z^{\ast}_e,
+D_v(Y^{\ast}, Z^{\ast}) = 1- Y^{\ast}_e \cdot Z^{\ast}_e,
 \end{equation}
@@
 \label{sec:compu}
-
-\begin{table}[tb!]
-\centering
-\begin{small}
-%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
-\caption{Dimension Types in \textit{Feature Data} Vector}
-%\vspace{0.1cm}
-\label{tbl:data-type}
-\begin{tabular}{ll}
-\toprule
-\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
-numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$, $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$               \\	\midrule 				
-categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
-normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_u$			\\ \bottomrule
-\end{tabular}
-\end{small}
-\end{table}
 

### 2018-02-24 DASFAA18_CR/Gruba_final/05-gm.tex

--- 2017-12-24 DASFAA_2018/Gruba/05-gm.tex
@@
 
-	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{$G_u$, $P_u$, \#$R_u$, \#$E_u$, $R_{ee,u}$\}.
+	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{$G_u$, $P_u$,\#$R_u$, \#$E_u$, $R_{ee,u}$\}.
 
@@
 %The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
-the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above.
-
+the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above. \par
 Here we use accuracy to evaluate our model.
@@
 If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0.
-Formally, accuracy is defined as:
+So the accuracy can be defined as:
 
@@
 \label{eq:def-presision}
-accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }.
+accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }
 \end{equation}
+
+We use accuracy to test results of using various $\alpha$ values. Suppose the label set we manually labeled for each microblog is $A$, the label set our method labeled is $B$.
+The accuracy can be defined as:
+\begin{equation}
+\label{eq:def-accuracy}
+accuracy = \frac{ A \cap B }{ A \cup B }
+\end{equation}
+
+To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$.
+For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0.
+If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0.
+If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0.
+If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0.
+So the accuracy can be defined as:
+
+\begin{equation}
+\label{eq:def-presision}
+accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }
+\end{equation}

### 2018-02-24 DASFAA18_CR/Gruba_final/06-perf.tex

--- 2017-12-24 DASFAA_2018/Gruba/06-perf.tex
@@
 
-\stitle{Exp-1: Interest Extraction}
+\stitle{Exp-1: Feature Extraction}
 %
 Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
-We report the interest accuracy with various $\alpha$ values.
-Suppose that the label set manually labeled for each microblog is $A$, the label set that our method labeled is $B$.
-The interest accuracy is defined as $\frac{ A \cap B }{ A \cup B }$.
-
 System \sys{} reaches the optimal results when $\alpha$ is 0.7,
@@
 
+\begin{figure*}[tb!]
+  \centering
+  \subfigure[Tests with Various $\alpha$.]{
+    \label{fig:fe}
+\includegraphics[width=.355\linewidth]{figures/Interests}}
+  \hspace{0.5in}
+   \subfigure[Silhouette Coefficient Tests.]{
+    \label{fig:10-c}
+  \includegraphics[width=.355\linewidth]{figures/clustering}}
+%  \caption{Performance of \sys{} Versus LRC-BQ.}
+    \label{fig:fig-1}
+    \vspace{-4ex}
+\end{figure*}
+
 %\begin{figure}[tb!]
-%  \centering
-%  \subfigure[Tests with Various $\alpha$.]{
-%    \label{fig:fe}
-%\includegraphics[width=.355\linewidth]{figures/Interests}}
-%  \hspace{0.5in}
-%   \subfigure[Silhouette Coefficient Tests.]{
-%    \label{fig:10-c}
-%  \includegraphics[width=.355\linewidth]{figures/clustering}}
-%  \caption{Performance of \sys{} Versus LRC-BQ.}
-%    \label{fig:fig-1}
+%\centering
+%\includegraphics[width=.315\linewidth]{figures/Interests}
+%\caption{Testing Results with Various $\alpha$.}
+%\label{fig:fe}
+%\vspace{-4ex}
 %\end{figure}
 
-\begin{figure}[tb!]
-\centering
-\begin{minipage}{.5\textwidth}
-  \centering
-\includegraphics[width=.85\linewidth]{figures/Interests}
-\caption{Interest Extraction: Varying $\alpha$.}
-\label{fig:fe}
-\end{minipage}%
-\begin{minipage}{.5\textwidth}
-  \centering
-\includegraphics[width=.8\linewidth]{figures/clustering}
-\caption{Silhouette Coefficient Tests.}
-\label{fig:10-c} 
-\end{minipage}
-\end{figure}
+%\begin{figure}[tb!]
+%\centering
+%\includegraphics[width=.315\linewidth]{figures/clustering}
+%\caption{Silhouette Coefficient Tests.}
+%\label{fig:uc}
+%\vspace{-5ex}
+%\end{figure}
 
 \begin{figure*}[tb!]
-%\centering
-  \subfigure[\sys{} Vs. LRC-BQ]{
+\centering
+  \subfigure[Accuracy of \sys{} Versus LRC-BQ.]{
     \label{fig:10-a}
-    %\vspace{2ex}
-    \includegraphics[width=0.5\textwidth]{figures/precision-1.eps}}
- % \hspace{0.5in}
-   \subfigure[Varying Items]{
-   %\vspace{2ex}
+    \includegraphics[width=0.355\textwidth]{figures/precision-1.eps}}
+  \hspace{0.5in}
+   \subfigure[Accuracy of Using Various Data Items for Modeling of \sys{}.]{
     \label{fig:11-a}
-  \includegraphics[width=0.5\textwidth]{figures/precisionofdifferentfeatures.eps}}
-  %\vspace{-1ex}
-  \caption{Accuracy Evaluation.}
+  \includegraphics[width=0.45\textwidth]{figures/precisionofdifferentfeatures.eps}}
+  \caption{Performance of \sys{} }
   \label{fig:fig-2}
@@
 By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), microblogs (MI) and interactions (II).
-%How about using other combinations of the above item(s)?
+How about using other combinations of the above item(s)?
 As shown in Fig.\ \ref{fig:11-a}, the default setting wins in most cases.
@@
 
-\begin{figure*}[tb!]
-\vspace{-2ex}
+\begin{figure*}
   \centering
@@
       \label{fig:userFeatures:uf-1}
-      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/1.eps}}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
   \subfigure[]{
       \label{fig:userFeatures:uf-2}
-      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/2.eps}}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
   \subfigure[]{
       \label{fig:userFeatures:uf-3}
-      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/3.eps}}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
   \subfigure[]{
       \label{fig:userFeatures:uf-4}
-      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/4.eps}}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
   \subfigure[]{
       \label{fig:userFeatures:uf-5}
-      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/5.eps}}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
   \subfigure[]{
       \label{fig:userFeatures:uf-6}
-      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/6.eps}}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
   \subfigure[]{
       \label{fig:userFeatures:uf-7}
-      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/7.eps}}
+      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
   \subfigure[]{
       \label{fig:userFeatures:uf-8}
-      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/8.eps}}
+      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
   \caption{Visualization for User Features.}
@@
 
-%\noindent\textbf{Summary}. %From these experimental results we find the followings.
-%(1) We design a novel method to extract users' explicit/implicit interests, and case studies show that our method is effective.
-%(2) In this paper, we offer a clustering method K-Gru to deal with complex vectors. And it helps us find a reasonable clustering result.
-%
-To conclude, by modeling user behaviors over groups instead of a single model for all users such as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%.
-What deserves to be mentioned is that the performance of LRC-BQ is also improved significantly by user clustering.
+\textbf{Summary}. From these experimental results we find the followings.
+(1) We design a novel method to extract users' explicit/implicit interests.
+And we tested various $\alpha$ to get a good performance.
+The visualization for a typical user shows that our method can make sense.
+(2) In this paper, we offer a clustering method K-Gru to deal with complex vectors. And it helps us find a reasonable clustering result.
+(3) By modeling user behaviors over groups instead of a single model for all users as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%.
+What deserves to be mentioned is that the performance of LRC-BQ also improved a lot by user clustering.

### 2018-02-24 DASFAA18_CR/Gruba_final/10-appendix.tex

--- 2017-10-14 Gruba/10-appendix.tex
@@
-\section*{Appendix: Extra Experiments}
-\label{sec:appendix}
+%\section*{Appendix: Extra Experiments}
+%\label{sec:appendix}
 
 %\subsection{Case Study for Feature Extraction}
+
 \begin{figure*}
@@
 \end{figure*}
-
 \subsection*{Exp-5: Case Study for User Clustering}
 
-In this section, we show the results of our system \sys{} for User Clustering. We carefully analyzed the statistical information of four groups obtained from user clustering.
+In this section, we show the results of \sys{} for User Clustering. We carefully analyzed the statistical information of four groups obtained from user clustering.
 
@@
 \end{figure*}
+
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Variables}
+\vspace{0.1cm}
+\label{tbl:Variables1}
+\begin{tabular}{lll}
+\toprule
+\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	& \multicolumn{1}{l}{\textbf{Section}} \\	\midrule \midrule
+$M_b$             & a microblog     	  &2			\\	\midrule
+$O$               & owner of a microblog           	  &2			\\	\midrule
+$T$               & the generated time of a microblog	  &2			\\	\midrule
+$M$               & the message context of a microblog	  &2			\\	\midrule
+$flag$            & flag denoting $M_b$ is retweeted (1) or originally tweet (0) by O	  &2			\\	\midrule
+$u$               & user $u$	  &2			\\	\midrule
+$B_u$             & microblogs of user $u$	  &2			\\	\midrule
+$R_u$             & followers of user $u$	  &2			\\	\midrule
+$E_u$             & followees of user $u$	  &2			\\	\midrule
+$\mathbb{U}$      & a set of users	  &2			\\	\midrule
+$\mathbb{B}$      & a set of microblogs	  &2			\\	\midrule
+$b$               & a microblog	  &2			\\	\midrule
+$f$               & a follower	  &2			\\	\midrule
+$G_u$				& gender of user $u$		        &3       		\\	\midrule
+$P_u$				& province of user $u$				&3              \\	\midrule
+                    & a ratio defined as the number     &         \\	
+                    & of followers over that of         &3         \\		
+\raisebox{1.5ex}{$R_{ee,u}$}  &followees,i.e.,$\frac{\#R_u}{\#E_u}$       &      \\  \midrule
+$U_{t,u}$		    & user type (as illustrated in Table \ref{tbl:ucate}) &3        \\ \midrule	
+$R_{oc,u}$          & ratio that is the number of retweeted microblogs over that of originally tweeted	  &3			\\	\midrule
+$W_{r,u}$           & average number of retweeted microblogs per week	  &3			\\	\midrule
+$W_{t,u}$           & average number of tweeted microblogs per week	  &3			\\	\midrule
+$P_{rt,u}$          & normalized vector regarding the time distribution of a user’s retweeting  behavior	  &3			\\	\midrule
+$P_{tt,u}$          & normalized vector regarding the time distribution of a user’s tweeting  behavior	  &3			\\	\midrule
+$P_{rg,u}$          & normalized vector with respect to the gap distribution of a user’s retweeting behavior	  &3			\\	\midrule
+$P_{tg,u}$          & normalized vector with respect to the gap distribution of a user’s tweeting behavior	  &3			\\	\midrule
+$L$                 & A lexicon consists of a set of topics	  &3			\\	\midrule
+$t$                 & A topic in $L$	  &3			\\	\midrule
+$c$                 & A cell word in $L$	  &3			\\	\midrule
+$P_u$               & The interest feature of a user $u$	  &3			\\	\midrule
+$WS$                & a word set	  &3			\\	\midrule
+$W_f$               & a metric TF-IDF weight	  &3			\\	\midrule
+$b_i$               & the occurrences of word $w_i$ in microblog $b$	  &3			\\	\midrule
+$|D_i|$             & the number of microblogs which contains word $w_i$	  &3			\\	\midrule
+$|D|$               & the number of all microblogs	  &3			\\	\midrule
+$N_t$               & the number of words in topic $t$	  &3			\\	\midrule
+$W_w$               & A metric Twitter-LDA weight	  &3			\\ \bottomrule
+\end{tabular}
+\end{small}
+\end{table}
+
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Variables}
+\vspace{0.1cm}
+\label{tbl:Variables2}
+\begin{tabular}{lll}
+\toprule
+\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	& \multicolumn{1}{l}{\textbf{Section}} \\	\midrule \midrule
+$\alpha$            & a parameter set flexible priorities between TF-IDF and Twitter-LDA	  &3			\\	\midrule
+$t_k$               & a topic in $L$	  &3			\\	\midrule
+$b_m$               & a microblog of user $u$	  &3			\\	\midrule
+$B_s(u)$            & microblogs of user $u$	  &3			\\	\midrule
+$s_k$               & overall similarity of user $u$ over topic $t_k$	  &3			\\	\midrule
+
+$Y'$,$Z'$           & numerical vectors	  &4			\\	\midrule
+$Y''$,$Z''$          & categorical vectors	  &4			\\	\midrule
+$Y^{\ast}$,$Z^{\ast}$     & vectors where each dimension is a normalized vector per se	  &4			\\	\midrule
+$d_i(u)$            & the average distance to all the other users in the same cluster	  &4			\\	\midrule
+$d_o(u)$            & the minimum of the distances between $u$ and other clusters	  &4			\\	\midrule
+$v(u)$              & The Silhouette coefficient value	  &4			\\	\midrule
+
+$E$                 & An item $E$ involves a microblog $b$ and a user $f$ such that $f\ \in R_{b.O}$	  &5			\\	\midrule
+$C_h$               & the correlation metric $C_h$ of $b$ and event	  &5			\\	\midrule
+$W_s$               & $u$'s short-term interest	  &5			\\ \bottomrule
+\end{tabular}
+\end{small}
+\end{table}
+
+\begin{table}[tb!]
+\centering
+\begin{small}
+\caption{Variables}
+\vspace{0.1cm}
+\label{tbl:Variables2}
+\begin{tabular}{ll|ll}
+\toprule
+\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}
+& \multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}} \\	\midrule \midrule
+$L$                 & A lexicon consists of a set of topics	
+&$t$                 & A topic in $L$	 			\\	\midrule
+$c$                 & A cell word in $L$	
+&$P_u$               & The interest feature of a user $u$	 			\\	\midrule
+$WS$                & a word set	 			
+&$W_f$               & a metric TF-IDF weight				\\	\midrule
+$b_i$               & the occurrences of word $w_i$ in microblog $b$	
+&$|D_i|$             & the number of microblogs which contains word $w_i$			\\	\midrule
+$|D|$               & the number of all microblogs
+&$N_t$               & the number of words in topic $t$				\\	\midrule
+$W_w$               & A metric Twitter-LDA weight
+&$\alpha$            & a parameter set flexible priorities between TF-IDF and Twitter-LDA			\\	\midrule
+$t_k$               & a topic in $L$	
+&$b_m$               & a microblog of user $u$			\\	\midrule
+$B_s(u)$            & microblogs of user $u$	
+&$s_k$               & overall similarity of user $u$ over topic $t_k$			\\	\bottomrule
+\end{tabular}
+\end{small}
+\end{table}
+
+\begin{table}[]
+\centering
+\caption{My caption}
+\label{my-label}
+\begin{tabular}{|l|l|l|l|}
+\hline
+\alpha & accuracy & precision & recall &  \\ \hline
+0	&0.488500	&0.636667	&0.560833     \\ \hline
+0.1	&0.479167	&0.633333	&0.557500     \\ \hline
+0.2	&0.481333	&0.636667	&0.564167     \\ \hline
+0.3	&0.506500	&0.663333	&0.588333     \\ \hline
+0.4	&0.497167	&0.660000	&0.587500     \\ \hline
+0.5	&0.497583	&0.666667	&0.600833     \\ \hline
+0.6	&0.524417	&0.693333	&0.622500     \\ \hline
+0.7	&0.576583	&0.720000	&0.649167     \\ \hline
+0.8	&0.502250	&0.650000	&0.590833     \\ \hline
+0.9	&0.450583	&0.596667	&0.550833     \\ \hline
+1	&0.396417	&0.536667	&0.501667     \\ \hline
+\end{tabular}
+\end{table}

### 2018-02-24 DASFAA18_CR/Gruba_final/06-perf.tex

@@
 Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
+We report the interest accuracy with various $\alpha$ values. Suppose the label set manually labeled for each microblog is $A$, the label set our method labeled is $B$.
+The interest accuracy is defined as $\frac{ A \cap B }{ A \cup B }$.
+
 System \sys{} reaches the optimal results when $\alpha$ is 0.7,
@@
 Except for \textit{Data1}, solutions for \textit{\{Data2,\ldots, Data5\}} are the best for 4 clusters.
-
-\begin{figure*}[tb!]
-  \centering
-  \subfigure[Tests with Various $\alpha$.]{
-    \label{fig:fe}
-\includegraphics[width=.355\linewidth]{figures/Interests}}
-  \hspace{0.5in}
-   \subfigure[Silhouette Coefficient Tests.]{
-    \label{fig:10-c}
-  \includegraphics[width=.355\linewidth]{figures/clustering}}
-%  \caption{Performance of \sys{} Versus LRC-BQ.}
-    \label{fig:fig-1}
-    \vspace{-4ex}
-\end{figure*}
 
@@
   \centering
+  \subfigure[Tests with Various $\alpha$.]{
+    \label{fig:fe}
+\includegraphics[width=.355\linewidth]{figures/Interests}}
+  \hspace{0.5in}
+   \subfigure[Silhouette Coefficient Tests.]{
+    \label{fig:10-c}
+  \includegraphics[width=.355\linewidth]{figures/clustering}}
+%  \caption{Performance of \sys{} Versus LRC-BQ.}
+    \label{fig:fig-1}
+
   \subfigure[Accuracy of \sys{} Versus LRC-BQ.]{
@@
   \label{fig:userFeatures} %% label for entire figure
-  \vspace{-4ex}
+  \vspace{-2ex}
 \end{figure*}
@@
 
-\textbf{Summary}. From these experimental results we find the followings.
-(1) We design a novel method to extract users' explicit/implicit interests.
-And we tested various $\alpha$ to get a good performance.
-The visualization for a typical user shows that our method can make sense.
-(2) In this paper, we offer a clustering method K-Gru to deal with complex vectors. And it helps us find a reasonable clustering result.
-(3) By modeling user behaviors over groups instead of a single model for all users as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%.
-What deserves to be mentioned is that the performance of LRC-BQ also improved a lot by user clustering.
+To conclude, by modeling user behaviors over groups instead of a single model for all users such as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%.
+What deserves to be mentioned is that the performance of LRC-BQ is also improved significantly by user clustering.

### 2018-02-24 DASFAA_2018/CR/Gruba_final/03-fe.tex

--- 2017-12-24 DASFAA_2018/Gruba/03-fe.tex
@@
 \label{def:lexi}
-A lexicon $L$ consists of a set of topics $t$ such that each topic is associated with a set of cell words $c$, in which each cell word depicts an aspect of the topic.
+A lexicon $L$ consists of a set of topics $\gamma$ such that each topic is associated with a set of cell words $c$, in which each cell word depicts an aspect of the topic.
 \end{definition}
@@
 In  \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
-Hence, the similarity $sim(w, c)$ of a word pair ($w$, $c$) could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user $u$ versus each topic $t$ in lexicon $sim(u, t)$; topics with similarity satisfying certain thresholds are allocated to user $u$ and constitute the interests of $u$.
+Hence, the similarity $sim(w, c)$ of a word pair ($w$, $c$) could be generalized to the similarity of a microblog against one topic $sim(b, \gamma)$, and finally to a user $u$ versus each topic $\gamma$ in lexicon $sim(u, \gamma)$; topics with similarity satisfying certain thresholds are allocated to user $u$ and constitute the interests of $u$.
 
@@
 %In case when no proper explicit interests are found, TF-IDF (Term-Frequency and Inverse Document-Frequency) and Twitter-LDA %\cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector %\cite{IEEEexample:mikolov2013distributed} is adopted to measure the similarity between two words.
-When no proper explicit interests are found, two algorithms are leveraged to identify implicit interests: (1) TF-IDF (Term-Frequency and Inverse Document-Frequency) \cite{IEEEexample:books/cu/LeskovecRU14}, and (2) Twitter-LDA \cite{IEEEexample:zhao2011comparing} (a method to discover topics from Twitter, by applying the standard Latent Dirichlet Allocation (LDA) model \cite{IEEEexample:conf/jmlr/Blei03}), both of which adopt word2vector \cite{IEEEexample:mikolov2013distributed} to measure word similarity.
+When no proper explicit interests are found, two algorithms are leveraged to identify implicit interests: (1) TF-IDF (Term-Frequency and Inverse Document-Frequency), and (2) Twitter-LDA \cite{IEEEexample:zhao2011comparing} (a method to discover topics from Twitter, by applying the standard Latent Dirichlet Allocation (LDA) model \cite{IEEEexample:conf/jmlr/Blei03}), both of which adopt word2vector \cite{IEEEexample:mikolov2013distributed} to measure word similarity.
 
@@
 
-The similarity of $b$ with a lexicon topic $t$ is defined as
+The similarity of $b$ with a lexicon topic $\gamma$ is defined as
 \begin{equation}
 \label{eq:bt}
-sim(b, t) = \sum_{\substack{i, j}} sim(w_i, c_j).
+sim(b, \gamma) = \sum_{\substack{i, j}} sim(w_i, c_j).
 \end{equation}
@@
 
-If $sim(b, t)$ satisfies a certain threshold (3 by default), topic $t$ is labeled to microblog $b$;
-the user $u$ is then discovered having an explicit interest (topic) $t$.
-Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (Definition \ref{def:inte}).
+If $sim(b, \gamma)$ satisfies a certain threshold (3 by default), topic $\gamma$ is labeled to microblog $b$;
+the user $u$ is then discovered having an explicit interest (topic) $\gamma$.
+Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).
 
 \stitle{Step 3:}.
-If the $sim(b, t)$ in {\bf Step 2} cannot meet the threshold, i.e., explicit interest discovery over user $u$ fails, the implicit interests of user $u$ are further mined, by running the following steps 3.1$\&$3.2 in parallel.
+If the $sim(b, \gamma)$ in {\bf Step 2} cannot meet the threshold, i.e., explicit interest discovery over user $u$ fails, the implicit interests of user $u$ are further mined, by running the following steps 3.1$\&$3.2 in parallel.
 
@@
 in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$, and $|b|$ the total occurrences of all words in $b$.
-$|D|$ is the total number of microblogs in the dataset and $|D_i|$ is the number of microblogs where $|b_i|$ appears.
+$|D|$ is the total number of microblogs in the dataset and $|D_i|$ is the number of microblogs where $w_i$ appears.
 Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.
@@
 %where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.
-For example, the similarity of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as formula \ref{eq:sim-tf1}.
-Here $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, $VEC_{W_f}$ is defined as formula \ref{eq:sum-tf1}, $VEC_t$ is defined as formula \ref{eq:sum-lexion},
-where $N_t$ is the number of words in topic $t$ and $vec[w]$ is the word vector of word $w$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
+For example, the similarity of $W_f$ over a single topic $\gamma$ in lexicon, written as $sim(W_f, \gamma)$, is defined as formula \ref{eq:sim-tf1}.
+Here $W_f = \{(w_i, p_i)\}$, $\gamma = \{c_j\}$, $VEC_{W_f}$ is defined as formula \ref{eq:sum-tf1}, $VEC_t$ is defined as formula \ref{eq:sum-lexion},
+where $N_{\gamma}$ is the number of words in topic $\gamma$ and $vec[w]$ is the word vector of word $w$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
 \begin{equation}
 \label{eq:sim-tf1}
-sim(W_f, t) = VEC_{W_f} \cdot VEC_t, where
+sim(W_f, \gamma) = VEC_{W_f} \cdot VEC_t, where
 \end{equation}
@@
 \label{eq:sum-lexion}
-VEC_t = \sum_{\substack{j}} \frac{1}{N_t}*vec[c_j].
+VEC_t = \sum_{\substack{j}} \frac{1}{N_{\gamma}}*vec[c_j].
 \end{equation}
@@
 
-\stitle{Step 4:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is :
+\stitle{Step 4:} Hence, the similarity of a microblog $b$ against a lexicon topic $\gamma$ is given by:
 \begin{equation}
 \label{eq:simbt}
-sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t),
+sim(b, \gamma) = \alpha * sim(W_f, \gamma) + (1 - \alpha) * sim(W_t, \gamma),
 \end{equation}
@@
 
-\stitle{Step 5:} Repeat Steps 1 to 4 for the microblog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
+\stitle{Step 5:} Repeat Steps 1 to 4 for the microblog $b$ over every topic in lexicon, i.e., $\forall {\gamma}_k \in L$ results one similarity value of $sim(b, {\gamma}_k)$.
 Such computation further extends to all the microblogs owned by user $u$, such that:
-$\forall b_m \in B_s(u)$, $\forall t_k \in L$, there exists a similarity of $sim(b_m, t_k)$.
-Hence, the overall similarity of user $u$ over lexicon topics $\{t\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
+$\forall b_m \in B_s(u)$, $\forall {\gamma}_k \in L$, there exists a similarity of $sim(b_m, {\gamma}_k)$.
+Hence, the overall similarity of user $u$ over lexicon topics $\{\gamma\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
 \begin{equation}
@@
 \end{equation}
-where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic $t_k$, which is given by:
+where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic ${\gamma}_k$, which is given by:
 \begin{equation}
 \label{eq:simul-2}
-s_k = \sum_{\substack{m}} sim(b_m, t_k).
+s_k = \sum_{\substack{m}} sim(b_m, {\gamma}_k).
 \end{equation}

### 2018-02-24 DASFAA_2018/CR/Gruba_final/05-gm.tex

--- 2018-02-24 DASFAA18_CR/Gruba_final/05-gm.tex
@@
 \begin{equation}
-\label{eq:def-presision}
+\label{eq:def-precision1}
 accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }
 \end{equation}
-
-We use accuracy to test results of using various $\alpha$ values. Suppose the label set we manually labeled for each microblog is $A$, the label set our method labeled is $B$.
-The accuracy can be defined as:
-\begin{equation}
-\label{eq:def-accuracy}
-accuracy = \frac{ A \cap B }{ A \cup B }
-\end{equation}
-
-To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$.
-For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0.
-If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0.
-If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0.
-If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0.
-So the accuracy can be defined as:
-
-\begin{equation}
-\label{eq:def-presision}
-accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }
-\end{equation}

### 2018-02-24 DASFAA_2018/CR/Gruba_final/01-intro.tex

--- 2017-12-24 DASFAA_2018/Gruba/01-intro.tex
@@
 
-\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, have attracted  massive users.
-These users behave variously, knowledge of which is significant for various applications such as recommendation system and activity analysis.
+\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users~\cite{DBLP:journals/fcsc/MaLHLH16,DBLP:journals/tkde/DuanMAMH17,DBLP:conf/icde/HuAMH16}.
+These users behave variously, knowledge of whom is significant for various applications such as recommendation system and activity analysis.
 Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.

### 2018-02-24 DASFAA_2018/CR/Gruba_final/01-intro.tex

@@
 
-\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users~\cite{DBLP:journals/fcsc/MaLHLH16,DBLP:journals/tkde/DuanMAMH17,DBLP:conf/icde/HuAMH16}.
+\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users~\cite{DBLP:journals/fcsc/MaLHLH16,DBLP:journals/tkde/DuanMAMH17,DBLP:conf/icde/HuAMH16,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
 These users behave variously, knowledge of whom is significant for various applications such as recommendation system and activity analysis.

### 2018-02-24 DASFAA_2018/CR/Gruba_final/01-intro.tex

@@
 These users behave variously, knowledge of whom is significant for various applications such as recommendation system and activity analysis.
-Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.
+Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry~\cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:conf/cikm/JiangLSW15,IEEEexample:conf/sigir/JiangLSLLMW16,IEEEexample:zhang2015retweet,IEEEexample:conf/pakdd/GiatsoglouCSFV15,IEEEexample:journals/corr/RanganathMHTL15}
 

### 2018-02-25 DASFAA_2018/CR/Gruba_final/02-overview.tex

--- 2018-02-24 DASFAA18_CR/Gruba_final/02-overview.tex
@@
 A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a.
-user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} or originally \tw{} by $O$.
+user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message content $M$, and $flag$ denoting $M_b$ is \retd{} or originally \tw{} by $O$.
 Here we use 1 and 0 to denote \retd{} and  \tw{}, respectively.
@@
 \centering
-\includegraphics[width=.7\linewidth]{figures/architecture.eps}
-\vspace{-1ex}
+\includegraphics[width=.6\linewidth]{figures/architecture.eps}
+%\vspace{-1ex}
 \caption{\sys{} Architecture}
 \label{fig:framework}
-\vspace{-4ex}
+\vspace{-2ex}
 \end{figure}

### 2018-02-25 DASFAA_2018/CR/Gruba_final/03-fe.tex

@@
 
-\sstab(e) the normalized vectors with respect to the gap distribution of a user's \retg{}/\twg{} behavior: $P_{rg,u}\ = (p''_{r0},\ p''_{r1},\ ...,\ p''_{r5})$, $P_{tg,u}\ = (p''_{t0},\ p''_{t1},\ ...,\ p''_{t5})$, in which $p''_{r0}$/$p''_{t0}$ is the probability that the gap between two \retd{}/\twg{} microblogs is within 1 min.
+\sstab(e) the normalized vectors with respect to the gap distribution of a user's \retg{}/\twg{} behavior: $P_{rg,u}\ = (p''_{r0},\ p''_{r1},\ ...,\ p''_{r5})$, $P_{tg,u}\ = (p''_{t0},\ p''_{t1},\ ...,\ p''_{t5})$, in which $p''_{r0}$/$p''_{t0}$ is the probability that the gap between two \retd{}/\twd{} microblogs is within 1 min.
 Ditto for $p''_{r1}$/$p''_{t1}$ (1 min to 1 hour), $p''_{r2}$/$p''_{t2}$ (1 to 12 hours), $p''_{r3}$/$p''_{t3}$ (12 to 24 hours), $p''_{r4}$/$p''_{t4}$ (24 to 48 hours) and  $p''_{r5}$/$p''_{t5}$ (more than 48 hours).
@@
 If $sim(b, \gamma)$ satisfies a certain threshold (3 by default), topic $\gamma$ is labeled to microblog $b$;
-the user $u$ is then discovered having an explicit interest (topic) $\gamma$.
+the user $u$ is then discovered having an explicit interest (topic $\gamma$).
 Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).

### 2018-02-25 DASFAA_2018/CR/Gruba_final/06-perf.tex

--- 2018-02-24 DASFAA18_CR/Gruba_final/06-perf.tex
@@
 
-\par In this section, we shall first detail the experimental setting, and we then present the evaluation result and analysis, showing the benefit of \sys{} against state of the art approaches.
+\par In this section, we shall first detail the experimental setting, and we then present the evaluation results and analyses, showing the benefit of \sys{} against state of the art approaches.
 
@@
 
-\subsection{Result and Analysis}
+\subsection{Results and Analyses}
 Next, we shall report the performance of system \sys{} over each component.
@@
 
+\begin{figure}[H]
+\begin{minipage}[t]{0.45\linewidth}
+\centering
+ \hspace{1.5in}
+\includegraphics[width=1\textwidth]{figures/Interests}
+\caption{Interest Extraction: Varying $\alpha$.}\label{fig:fe}
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.45\linewidth}
+\centering
+ \hspace{1.5in}
+\includegraphics[width=1\textwidth]{figures/clustering}
+\caption{Silhouette Coefficient Tests.}\label{fig:10-c}
+\end{minipage}
+\end{figure}
+
 \stitle{Exp-2: User Clustering}
 %
-Fig.\ \ref{fig:10-c} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
+Fig.\ \ref{fig:10-c} depicts the Silhouette coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
 Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
@@
 %\end{figure}
-
-\begin{figure*}[tb!]
-  \centering
-  \subfigure[Tests with Various $\alpha$.]{
-    \label{fig:fe}
-\includegraphics[width=.355\linewidth]{figures/Interests}}
-  \hspace{0.5in}
-   \subfigure[Silhouette Coefficient Tests.]{
-    \label{fig:10-c}
-  \includegraphics[width=.355\linewidth]{figures/clustering}}
-%  \caption{Performance of \sys{} Versus LRC-BQ.}
-    \label{fig:fig-1}
-
-  \subfigure[Accuracy of \sys{} Versus LRC-BQ.]{
-    \label{fig:10-a}
-    \includegraphics[width=0.355\textwidth]{figures/precision-1.eps}}
-  \hspace{0.5in}
-   \subfigure[Accuracy of Using Various Data Items for Modeling of \sys{}.]{
-    \label{fig:11-a}
-  \includegraphics[width=0.45\textwidth]{figures/precisionofdifferentfeatures.eps}}
-  \caption{Performance of \sys{} }
-  \label{fig:fig-2}
-  \vspace{-4ex}
-\end{figure*}
 
@@
 %\end{itemize}
+
+\begin{figure*}[tb!]
+  \centering
+  \subfigure[\sys{} Versus LRC-BQ.]{
+    \label{fig:10-a}
+    \includegraphics[width=0.37\textwidth]{figures/precision-2.eps}}
+  \hspace{0.6in}
+   \subfigure[Various Data Items for \sys{}.]{
+    \label{fig:11-a}
+  \includegraphics[width=0.45\textwidth]{figures/precisionofdifferentfeatures-1.eps}}
+  \caption{Performance of \sys{} }
+\end{figure*}
 

### 2018-02-25 DASFAA_2018/CR/Gruba_final/07-rela.tex

--- 2017-12-24 DASFAA_2018/Gruba/07-rela.tex
@@
 
-\par In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
+\par In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behaviors within the realm of social network modeling.
 As aforementioned, \sys{} leverages the user features of basics, behavior and interest.
@@
 \cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of microblogs with the aid of word frequency and machine translation.
-\cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain use interests.
-Also, \cite{IEEEexample:conf/and/MichelsonM10} used a knowledge base and \cite{IEEEexample:conf/icde/FengW14} provided a solution of using hashtag for interest analysis.
+\cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain user interests.
+Also, \cite{IEEEexample:conf/and/MichelsonM10} used a knowledge base and \cite{IEEEexample:conf/icde/FengW14} provided a solution of using hashtags for interest analysis.
 \cite{IEEEexample:conf/wikis/LimD13} summarized user interest by exploring the mentioned celebrities;
@@
 More recent studies also look into mining user communities.
-\cite{IEEEexample:conf/wsdm/YangL13} employed matrix decomposition to mine user community;
+\cite{IEEEexample:conf/wsdm/YangL13} employed matrix decomposition to mine user communities;
 \cite{IEEEexample:conf/www/RuanFP13} and \cite{IEEEexample:he2014overlapping} considered followees info for user clustering;
-\cite{IEEEexample:conf/aaai/ShiokawaFO13} proposed an incremental algorithm to mine user community using modular degree as the clustering yardstick.
+\cite{IEEEexample:conf/aaai/ShiokawaFO13} proposed an incremental algorithm to mine user communities using modular degree as the clustering yardstick.
 Providing the diversity of user features, \sys{} employs basic, behavior and interest features into user clustering.
@@
 \cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15} and \cite{IEEEexample:journals/corr/RanganathMHTL15} focused on identifying whether the \retg{} is fraudulent or of protest.
-Whereas our work \sys{} builds the \retg{} model for each user group, instead of a single model for all users or one model per user.
+Whereas our work \sys{} builds the \retg{} model for each user group, instead of the mono model for all users or one model per user.

### 2018-03-02 DASFAA_2018/CR/Gruba_final/01-intro.tex

@@
 
-\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users~\cite{DBLP:journals/fcsc/MaLHLH16,DBLP:journals/tkde/DuanMAMH17,DBLP:conf/icde/HuAMH16,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
+\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, have attracted  massive users~\cite{DBLP:journals/fcsc/MaLHLH16,DBLP:journals/tkde/DuanMAMH17,DBLP:conf/icde/HuAMH16,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
 These users behave variously, knowledge of whom is significant for various applications such as recommendation system and activity analysis.
@@
 As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
-Particularly, we study the \retg{} behavior of users and our work can be readily generalized to other behaviors of like and comment as well.
+Particularly, we study the \retg{} behavior of users and our work can be readily generalized to other behaviors of ``likes'' and ``comments'' as well.
 In the realm of social network behavior modeling, few work has been done over grouping, which however has been proved to be effective in other fields such as economic behavior analysis.
-This motivates us to incorporate user grouping into the \retg{} behavior modeling, filling the gap of existed studies that build a single model for all users.
+This motivates us to incorporate user grouping into the \retg{} behavior modeling, filling the gap of existing studies that build a single model for all users.
 

### 2018-03-02 DASFAA_2018/CR/Gruba_final/02-overview.tex

@@
 %For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
-For simplicity, assuming the microblogs that a user can \ret{} come from those owned by his/her followees.
+For simplicity, assuming the microblogs that a user can \ret{} come from those owned by her/his followees.
 
@@
 A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a.
-user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message content $M$, and $flag$ denoting $M_b$ is \retd{} or originally \tw{} by $O$.
+user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message content $M$, and $flag$ denoting $M_b$ is \retd{} or originally \twd{} by $O$.
 Here we use 1 and 0 to denote \retd{} and  \tw{}, respectively.

### 2018-03-02 DASFAA_2018/CR/Gruba_final/03-fe.tex

@@
 the user $u$ is then discovered having an explicit interest (topic $\gamma$).
-Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).
+Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ are derived, in the form of interest feature (see Definition \ref{def:inte}).
 
@@
 $|D|$ is the total number of microblogs in the dataset and $|D_i|$ is the number of microblogs where $w_i$ appears.
-Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.
+Hence, each word $w_i$ shall get an initial weight $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.
 
@@
 %
-Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
+Subsequently, $W_t$ is leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
 
@@
 Such computation further extends to all the microblogs owned by user $u$, such that:
-$\forall b_m \in B_s(u)$, $\forall {\gamma}_k \in L$, there exists a similarity of $sim(b_m, {\gamma}_k)$.
+$\forall b_m \in B_u$, $\forall {\gamma}_k \in L$, there exists a similarity of $sim(b_m, {\gamma}_k)$.
 Hence, the overall similarity of user $u$ over lexicon topics $\{\gamma\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:

### 2018-03-02 DASFAA_2018/CR/Gruba_final/05-gm.tex

@@
 In addition, we consider $u$'s short-term interest, which is mined from $u$'s recent microblogs (e.g., within 30 days) and calculated by \textit{TF-IDF}, namely $W_s$.
-The correlation between microblog and $u$'s short-term interest is computed by $W_f$ and $W_s$ (using formula \ref{eq:sim-tf1}).
+The correlation between microblog $b$ and $u$'s short-term interest is computed by $W_f$ and $W_s$ (using formula \ref{eq:sim-tf1}).
 %%
 
-The modeling of retweeting behavior of groups is treated as a classification problem, and utilize the random forest classifier to address it.
+The modeling of retweeting behavior of groups is treated as a classification problem, and we utilize the random forest classifier to address it.
 Details for random forest \cite{IEEEexample:conf/icdar/Ho1995} are omitted here for space reason.

### 2018-03-02 DASFAA_2018/CR/Gruba_final/06-perf.tex

@@
 %
-Fig.\ \ref{fig:10-c} depicts the Silhouette coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
+Fig.\ \ref{fig:10-c} depicts the Silhouette coefficient values of multiple clustering solutions, with the cluster number varied from 2 to 10.
 Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
@@
 LRC-BQ does not deal with user grouping.
-Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering),
+Hence, we not only study the modeling effectiveness per group (i.e., ``Group-One/Two/Three/Four'' with user clustering),
 but also examine \sys{} versus LRC-BQ in the case that all users are in a single group (i.e., ``All-Users'').
